### 2021-11-02 index.Rmd
wip

---
title: "Online analysis supplement"
description: |
  A global study of adolescents’ digital technology adoption and its associations with well-being and mental health
author:
  - name: Matti Vuorre
    url: https://vuorre.netlify.app
    affiliation: Oxford Internet Institute
    affiliation_url: https://www.oii.ox.ac.uk/people/matti-vuorre/
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    fig_width: 8
    fig_height: 6
    fig_retina: 2
    dev: "ragg_png"
    code_folding: true
---

## Preface

This document details the analyses supporting *A global study of adolescents’ digital technology adoption and its associations with well-being and mental health* (Vuorre & Prybylski, in preparation).

We downloaded the relevant data from sources to data-raw. We cannot share the data here but indicate below how and when each data table was obtained.

## Settings

We first load the required R packages and set some options for the resulting document.

```{r settings}
# Packages
library(readxl)
library(brms)
library(ragg)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(parameters)
library(countrycode)
library(multidplyr)
library(lme4)
library(emmeans)
library(plotly)
library(knitr)
library(patchwork)
library(bayestestR)
library(lubridate)
library(haven)
library(janitor)
library(broom)
library(kableExtra)
library(ggbeeswarm)
library(ggstance)
library(sysfonts)
library(tidyverse)

# Knitr options
opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  cache = TRUE,
  error = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.retina = 2
)

# Plotting theme
Font <- "Titillium Web"
if (!(Font %in% font_families())) font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_size = 12, 
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4,4,4,4, "pt"))
    )
)

# MCMC settings
options(brms.backend = "cmdstanr")
# Run this to delete fitted models and refit
# unlink(list.files(pattern = "brm-.*\\.rds"))

# parallel computations
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
cluster <- new_cluster(MAX_CORES)
cluster_library(cluster, c("lme4", "dplyr", "stringr"))

# Create directory for intermediate files
dir.create("output", FALSE)
```

## Data cleaning

### ITU

- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>

```{r}
# Read and reshape fixed broadband data
itu_fixed <- read_excel(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Read and reshape mobile broadband data
itu_mobile <- read_excel(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Percent using internet
itu_percent <- read_excel(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("Year", "Variable")) %>% 
  pivot_wider(names_from = Variable) %>% 
  mutate(value = as.numeric(value))

# Merge to one table in wide format (oldest on left to include all years)
itu <- left_join(
  select(itu_percent, Country, Year, Internet = value),
  select(itu_fixed, Country, Year, Fixed = value)
) %>% 
  left_join(
    select(itu_mobile, Country, Year, Mobile = value)
  ) %>% 
  mutate(across(-Country, as.numeric))

# values (1-100) to proportions (0-1)
itu <- itu %>% 
  mutate(across(c(Fixed, Mobile, Internet), function(x) x/100))

# Standardise country names
# This drops six small regions not recognised by countryname()
itu <- itu %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)
```

Remove countries with no internet data

```{r}
itu_countries_missing <- itu %>% 
  group_by(Country) %>% 
  summarise(
    years = n(), 
    missing_fixed = sum(is.na(Fixed)),
    missing_mobile = sum(is.na(Mobile)),
    missing_internet = sum(is.na(Internet))
  ) %>% 
  filter(
    missing_fixed == years | 
      missing_mobile == years |
      missing_internet == years
  )
itu_countries_missing <- itu_countries_missing %>% 
  filter(
    missing_fixed==years & 
      missing_mobile==years & missing_internet==years
  ) %>% 
  select(Country)
itu <- anti_join(itu, itu_countries_missing)
```

Missing values

```{r}
# Calculate numbers of missing values for fixed (2004-) and mobile (2007-)
bind_rows(
  select(itu, Internet) %>% 
    naniar::miss_var_summary(),
  filter(itu, Year >= 2004) %>% 
    select(Fixed) %>% 
    naniar::miss_var_summary(),
  filter(itu, Year >= 2007) %>% 
    select(Mobile) %>% 
    naniar::miss_var_summary()
) %>% 
  mutate(pct_miss = percent(pct_miss/100)) %>% 
  kbl(caption = "ITU Missingness") %>% 
  kable_styling(full_width = FALSE)
```

Impute missing values. We first replace missing initial values with zeros, assuming that they were not logged because practically zero. Then proceed with linear interpolation from there.

```{r}
library(imputeTS)

itu <- itu %>% 
  group_by(Country) %>% 
  # If first value is missing, replace with zero
  mutate(
    i = 1:n(),
    across(
      c(Internet, Fixed, Mobile), 
      .fns = list(
        i = possibly(function(x) if_else(is.na(x) & i==1, 0, x), otherwise = NaN)
      )
    )
  ) %>% 
  # Linear interpolation
  mutate(
    across(
      c(Internet_i, Fixed_i, Mobile_i), 
      possibly(function(x) na_interpolation(x), otherwise = NaN)
    )
  ) %>% 
  # Remove variables before they existed
  mutate(
    Fixed_i = if_else(Year < 2004, NaN, Fixed_i),
    Mobile_i = if_else(Year < 2007, NaN, Mobile_i)
  ) %>% 
  # Remove unnecessary index variable
  select(-i) %>% 
  ungroup()

# Don't impute observations forward (unless they are zeroes in the beginning)
itu <- itu %>% 
  mutate(
    across(
      ends_with("_i"), 
      ~if_else(.x == lag(.x) & .x!=0, NaN, .x)
    )
  )

# Examine output
itu <- itu %>% 
  select(
    Country, Year, 
    starts_with("Internet"),
    starts_with("Fixed"),
    starts_with("Mobile")
  )
# itu %>% 
#   mutate(across(-c(Country, Year), ~percent(.x, .001))) %>% 
#   View

# Replace old variables with imputed
itu <- itu %>% 
  select(-c(Internet, Fixed, Mobile)) %>% 
  rename_with(~str_replace(.x, "_i", ""))
```

### GBD

The Global Burden of Disease data CSVs were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02.

```{r gbd-data-clean}
# Load data files and merge to one table
# We need names and IDs because there are two Georgias
gbd <- list.files(
  "data-raw/GBD/gbd-2021-11-02/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()

# Cleaning

# prevalence (total number of cases)
# "Rate": Total cases per 100,000 population
# We convert this to a percentage
distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>% 
  mutate(across(c(val, upper, lower), ~.x/1000))

# Clean cause names
distinct(gbd, cause)
gbd <- gbd %>% 
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Self-harm"
    )
  )

# Harmonise names with other datasets and capitalize
gbd <- gbd %>% 
  rename(
    Country = location,
    Year = year,
    Sex = sex,
    Age = age,
    Cause = cause
  )

# Harmonise country names
# Check where new name doesn't match with proposed new name
# gbd %>%
#   distinct(Country) %>%
#   mutate(Country2 = countryname(Country)) %>%
#   filter(Country!=Country2 | is.na(Country2)) %>%
#   arrange(Country) %>%
#   View()
# Replace old with new standard name, drop where new name doesn't exist
gbd <- gbd %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)
```

### World bank

```{r}
wb <- read_csv(
  "data-raw/world-bank/population/API_SP.POP.TOTL_DS2_en_csv_v2_2163507.csv", 
  skip = 3
)
wb <- wb %>% 
  select(Country = `Country Name`, `2000`:`2019`) %>%
  pivot_longer(-Country, names_to = "Year", values_to = "Pop") %>% 
  mutate(Year = as.numeric(Year))

wb <- wb %>% 
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)
```

### GLOBE Regions

We group the countries into GLOBE regions.

```{r}
regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>% 
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(Country = str_remove_all(Country, "\\*")) %>% 
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(Country = countryname(Country)) %>% 
  drop_na(Country)

distinct(itu, Country)
distinct(regions, Region)

# ITU countries not present in region data
filter(
  distinct(itu, Country), 
  !(Country %in% unique(regions$Country))
) %>% 
  arrange(Country) %>% 
  write_csv("data-raw/Regions/ITU-countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
regions <- read_csv(
  "data-raw/Regions/ITU-countries-without-region-filled.csv"
) %>% 
  select(Country, Region) %>% 
  bind_rows(regions) %>% 
  drop_na(Region)

# GBD countries not present in region data
filter(
  distinct(gbd, Country),
  !(Country %in% unique(regions$Country))
) %>% 
  arrange(Country) %>% 
  write_csv("data-raw/Regions/GBD-countries-without-region.csv")

# Load in above filled with regions

# Shorter name for plots
regions <- regions %>% 
  mutate(Region = if_else(Region=="Sub-Sahara Africa", "Africa", Region))

# Reorder labels
regions <- regions %>% 
  mutate(
    Region = factor(
      Region,
      levels = c(
        "Africa", "Latin America", "Anglo", "Arab", 
        "Confucian Asia", "Southern Asia", "Eastern Europe", 
        "Germanic Europe", "Latin Europe", "Nordic Europe"
      )
    )
  )

# Format labels to use line breaks instead of spaces
levels(regions$Region) <- str_replace_all(levels(regions$Region), " ", "\n")

# Remove duplicated countries
regions %>% 
  count(Country, sort = TRUE)
regions <- distinct(regions)

# We then use these regions
itu <- itu %>% 
  left_join(regions)
```

## Complete study dataset

We end up with a dataset that has predictors (internet access) at the level of country and year. Outcomes are also at the level of country and year, but additionally vary by sex and age group.

```{r}
# For models, we rescale year; centred at 2013 and one unit indicates 2007 to 2019
itu <- itu %>% 
  mutate(Time = (Year - 2013) / 12)

# Create predictor, lagged and centered on 2013
itu <- itu %>% 
  arrange(Country, Year) %>% 
  group_by(Country) %>% 
  mutate(Internet1 = lag(Internet, 1)) %>% 
  mutate(Internet1 = Internet1 - Internet1[Year==2013]) %>%
  ungroup()

# Merge data sets
d <- left_join(itu, gbd)

# What to do with countries with no outcomes--drop
d <- d %>% 
  drop_na(Cause)

# Contrast code sex
d$Sex <- factor(d$Sex)
contrasts(d$Sex) <- c(-.5, .5)
```

We also save a synthetic version of this dataset to better enable others to reproduce our analytical procedures:

```{r synth-data-create}

```

## Describe

### Internet use trends

```{r}
# Mean users in first and last year
itu %>% 
  filter(Year %in% c(2000, 2020)) %>% 
  group_by(Year) %>% 
  summarise(mean(Internet, na.rm = TRUE))
# Regions
itu %>% 
  filter(Year == 2020) %>% 
  group_by(Region, Year) %>% 
  summarise(m = mean(Internet, na.rm = TRUE)) %>% 
  arrange(m)
itu %>% drop_na(Internet) %>% {length(unique(.$Country))}
```

```{r}
# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
p_itu <- itu %>% 
  mutate(Year = make_date(Year)) %>% 
  # Do something about countries with no region if they have outcome data
  drop_na(Region) %>% 
  pivot_longer(c(Fixed, Mobile, Internet), names_to = "Type") %>% 
  mutate(Type = factor(Type, levels = c("Internet", "Fixed", "Mobile"))) %>% 
  ggplot(
    aes(
      x = Year, 
      y = value, 
      group = interaction(Type, Country)
    )
  ) +
  coord_cartesian(ylim = c(0, 1.00)) +
  scale_y_continuous(
    "Internet users (or subscriptions) / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  scale_x_date(
    breaks = breaks_width("5 years"),
    labels = label_date("'%y")
  ) +
  geom_line(size = .25, col = "dodgerblue4") +
  facet_grid(Type~Region) +
  theme(legend.position = "none")
agg_png("output/Fig-ITU.png", height = 1200, width = 3200, res = 300)
p_itu
dev.off()
agg_png("output/Fig-ITU-internet.png", height = 1200, width = 3200, res = 300)
p_itu %+% 
  (filter(p_itu$data, Type == "Internet") %>% 
     mutate(Region = str_replace(Region, "\n", " "))) + 
  scale_y_continuous(
    "Internet users / population",
    breaks = c(0, .25, .5, .75, 1),
    labels = percent,
    expand = expansion(c(0.02, 0.1))
  ) +
  facet_wrap("Region", nrow = 2)
dev.off()
```

### Mental health

```{r}
d_young <- d %>% 
  drop_na(Region) %>% 
  filter(Age %in% c("10 to 14", "15 to 19", "20 to 24"))

pa <- d_young %>% 
  ggplot(aes(Year, val, group = Country, col = Region)) +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .4) +
  facet_grid(Cause~Region, scales = "free_y") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank()
  )
pb <- d_young %>% 
  ggplot(aes(Year, val, col = Age, lty = Sex)) +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(
    "Rate in 100 people",
    breaks = pretty_breaks()
  ) +
  scale_x_continuous(
    breaks = c(2000, 2005, 2010, 2015, 2020),
    labels = c("'00", "'05", "'10", "'15", "'20")
  ) +
  stat_summary(fun = mean, geom = "line", size = .5) +
  facet_grid(Cause~Region, scales = "free_y")

p_gbd <- (pa / pb) +
  plot_annotation(tag_levels = "A")

p_gbd

ggsave(
  "output/Fig-GBD.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

## Model 1: Temporal trends

We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.

### GBD lm

Estimate OLS for each cause for country-sex-age specific estimates

```{r fit-gbd-time-lm}
file_path <- "output/lm-gbd-time.rds"
if (!file.exists(file_path)) {
  fits_lm <- d_young %>% 
    group_by(Cause) %>% 
    partition(cluster) %>% 
    summarise(
      fit = list(
        lm(
          val ~ 0 + Country:Sex:Age + Time:Country:Sex:Age,
          data = cur_data_all()
        )
      )
    ) %>% 
    collect() %>% 
    ungroup()
  write_rds(fits_lm, file_path)
} else {
  fits_lm <- read_rds(file_path)
}
```

```{r}
tidy(fits_lm$fit[[1]])
# Get country-sex-age specific parameters
fits_lm %>% 
  mutate(out = map(fit, tidy))
```

### GBD lme4

```{r fit-gbd-time-lmer}
# Fit GBD time lmer models
file_path <- "output/lme-gbd-time.rds"
if (!file.exists(file_path)) {
  fits_lme <- d_young %>% 
    group_by(Cause) %>% 
    partition(cluster) %>% 
    summarise(
      fit = list(
        lmer(
          val ~ 0 + Sex:Age + Time:Sex:Age + 
            (0 + Sex:Age + Time:Sex:Age | Region) +
            (0 + Sex:Age + Time:Sex:Age | Country),
          data = cur_data_all()
        )
      )
    ) %>% 
    collect() %>% 
    ungroup()
  write_rds(fits_lme, file_path)
} else {
  fits_lme <- read_rds(file_path)
}
```

```{r}
# lmer parameters
```

We want to visualise cluster-specific coefficients, but this is hard with lme4. Attempt

```{r}
# Get country-, region-, and age-specific parameters

# Create scatterplots
```

### GBD brms

Shall we fit multiple times: First without interaction with age, gender, then see if those matter?

```{r fit-gbd-time-brms}
fit_empty <- brm(
  val ~ Time * Sex + 
    (1 + Time * Sex | Country) +
    (1 + Time * Sex | Region) +
    (1 + Time * Sex | Age),
  data = filter(d, Cause == "Depression"),
  file = "output/brm-gbd-time-empty",
  chains = 0,
  threads = 3,
)

# cluster_copy(cluster, "fit_empty")
fits_brm <- d %>% 
  group_by(Cause) %>% 
  summarise(
    fit = list(
      update(
        fit_empty,
        newdata = cur_data_all(),
        chains = 4,
        cores = 4,
        iter = 1600,
        warmup = 800,
        refresh = 10,
        threads = 3,
        file = str_glue("output/brm-gbd-time-{cur_group()}")
      )
    )
  ) %>%
  ungroup()
```

Fixed effects

```{r}
tmp <- fits_brm %>% 
  mutate(
    parameters = map(
      fit,
      ~posterior_summary(., pars = c("b_", "sd_", "cor_"))
    )
  )
tmp %>% 
  select(-fit) %>% 
  unnest(parameters) %>% 
  filter(!str_detect(Parameter, "cor_"), Parameter != "sigma") %>% 
  separate(
    Parameter, c("Parameter", "Group", "Term"), 
    sep = "_", 
    extra = "merge"
  ) %>%
  mutate(Term = coalesce(Term, Group)) %>% 
  mutate(Group = if_else(Parameter == "b", "", Group)) %>% 
  mutate(Term = str_remove(Term, "_")) %>% 
  ggplot(aes(Median, Term, color = Cause)) +
  geom_vline(xintercept = 0, size = .2, lty = 2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodgev(.4)
  ) +
  facet_nested(~ Parameter + Group)

# Fixed-effects plot
fixef_draws <- fits_brm %>% 
  mutate(
    samples = map(
      fit, 
      ~emtrends(.x, "Sex", "Time") %>% 
        gather_emmeans_draws()
    )
  ) %>% 
  select(-fit)
fixef_draws
p_gbd_m1 <- fixef_draws %>% 
  unnest(samples) %>% 
  ggplot(aes(.value/1.2, Cause, col = Sex, fill = Sex)) +
  scale_x_continuous(
    "Change / decade [95%CI]",
    breaks = pretty_breaks()
  ) +
  scale_color_brewer("Sex", palette = "Set1", aesthetics = c("color", "fill")) +
  geom_vline(xintercept = 0, size = .2, lty = 2) +
  stat_pointinterval(
    position = position_dodgev(.3),
    .width = c(.8, .95),
    size = .5
  ) +
  stat_halfeye(
    position = position_dodgev(.3), normalize = "panels",
    alpha = .4, point_interval = NULL, show.legend = FALSE
  )
p_gbd_m1
```

Plot of fixed and random effects

```{r}
# These strings make hypothesis() calculate sex-specific slopes given my contrast codes for Sex
h_sex <- c(
  "Female" = "Time + Time:Sex1*-.5 = 0",
  "Male" = "Time + Time:Sex1*.5 = 0"
)
# Summaries of fixed effects
fixef_summary <- fits_brm %>% 
  mutate(
    out = map(
      fit,
      ~hypothesis(.x, h_sex) %>% 
        .$hypothesis
    )
  ) %>% 
  select(-fit)
# Summaries of random effects for age and country groupings
# Get just average (across sexes) effects of time for random effects
h_avg <- c("Average" = "Time = 0")
ranef_summary <- fits_brm %>% 
  expand_grid(G = c("Age", "Country")) %>% 
  mutate(
    out = map2(
      fit, G,
      ~hypothesis(.x, h_avg, scope = "coef", group = .y) %>% 
        .$hypothesis
    )
  ) %>% 
  select(-fit)

p1 <- fixef_summary %>% 
  unnest(out) %>% 
  ggplot(aes(Estimate, Cause, col = Hypothesis)) +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    position = position_dodgev(.4)
  ) +
  theme(legend.position = "none")

p2 <- ranef_summary %>% 
  filter(G == "Age") %>% 
  unnest(out) %>% 
  ggplot(aes(Estimate, Cause, col = Group)) +
  scale_color_viridis_d() +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    position = position_dodgev(.4),
    size = .4, fatten = 1.5
  ) +
  guides(color = guide_legend(nrow = 4)) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "bottom", 
    legend.title = element_blank()
  )

p3 <- ranef_summary %>% 
  filter(G == "Country") %>% 
  unnest(out) %>% 
  left_join(distinct(d, Country, Region), by = c("Group" = "Country")) %>% 
  ggplot(aes(Estimate, Cause, col = Region)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = CI.Lower, xmax = CI.Upper),
    position = position_dodgev(.4),
    size = .4, fatten = 1.5
  ) +
  guides(color = guide_legend(nrow = 4)) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )

p1 / (p2 | p3)
```

```{r}
# Plot of age random + fixed
# Age
p_gbd_m2 <- ranef_summary %>% 
  filter(G == "Age") %>% 
  unnest(out) %>% 
  pivot_wider(names_from = Hypothesis, values_from = Estimate:Star) %>% 
  ggplot(aes(Estimate_Female, Estimate_Male)) +
  geom_blank(aes(Estimate_Male, Estimate_Female)) +
  scale_x_continuous(
    "Change [Females]",
    breaks = pretty_breaks(3)
  ) +
  scale_y_continuous(
    "Change [Males]",
    breaks = pretty_breaks(3)
  ) +
  scale_color_viridis_d("Age") +
  geom_vline(xintercept = 0, size = .2, lty = 2) +
  geom_hline(yintercept = 0, size = .2, lty = 2) +
  geom_abline(size = .2) +
  geom_point(aes(col = Group)) +
  # Male summary
  geom_pointrange(
    data = fixef_summary %>% 
      unnest(out) %>% 
      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
    aes(ymin = CI.Lower_Male, ymax = CI.Upper_Male)
  ) +
  # Female summary
  geom_pointrange(
    data = fixef_summary %>% 
      unnest(out) %>% 
      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
    aes(xmin = CI.Lower_Female, xmax = CI.Upper_Female)
  ) +
  facet_wrap("Cause", nrow = 1, scales = "free") +
  theme(aspect.ratio = 1)
# Country
p_gbd_m3 <- ranef_summary %>% 
  filter(G == "Country") %>% 
  unnest(out) %>% 
  pivot_wider(names_from = Hypothesis, values_from = Estimate:Star) %>%
  left_join(distinct(d, Country, Region), by = c("Group" = "Country")) %>% 
  ggplot(aes(Estimate_Female, Estimate_Male)) +
  geom_blank(aes(Estimate_Male, Estimate_Female)) +
  scale_x_continuous(
    "Change [Females]",
    breaks = pretty_breaks(3)
  ) +
  scale_y_continuous(
    "Change [Males]",
    breaks = pretty_breaks(3)
  ) +
  geom_vline(xintercept = 0, size = .2, lty = 2) +
  geom_hline(yintercept = 0, size = .2, lty = 2) +
  geom_abline(size = .2) +
  geom_point(shape = 1, aes(col = Region)) +
  # Male summary
  geom_pointrange(
    data = fixef_summary %>% 
      unnest(out) %>% 
      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
    aes(ymin = CI.Lower_Male, ymax = CI.Upper_Male)
  ) +
  # Female summary
  geom_pointrange(
    data = fixef_summary %>% 
      unnest(out) %>% 
      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
    aes(xmin = CI.Lower_Female, xmax = CI.Upper_Female)
  ) +
  facet_wrap("Cause", nrow = 1, scales = "free") +
  theme(aspect.ratio = 1)
```

```{r}
((p_gbd_m3 | p_gbd_m2) & theme(legend.position = "none")) +
  plot_annotation(tag_levels = "A")
```

Add these plots to a single figure with data

```{r}
pa <- (p_gbd_1 / p_gbd_2) +
  plot_layout(heights = c(4.5, 5.5))
pb <- (p_gbd_3 / p_gbd_4) &
  guides(
    color = guide_legend(
      override.aes = list(size = 1),
      ncol = 1,
      revese = TRUE
    )
  ) &
  plot_layout(heights = c(3, 7))
pc <- (p_gbd_m3 + theme(legend.position = "none") | 
         p_gbd_m2 + theme(legend.position = "none")) &
  theme(axis.text = element_text(size = 8))
p_gbd <- ((pa | pb) / pc) + 
  plot_layout(heights = c(8.8, 1.2)) +
  plot_annotation(tag_levels = "A")

agg_png(
  "output/Fig-GBD-with-parameters.png",
  height = 2600, width = 3600, res = 300
)
p_gbd
dev.off()
```

## Model 2: Associations

### Figure

```{r}
d %>% 
  filter(
    Region == "Anglo",
    Sex == "Female",
    Age == "15 to 19"
  ) %>% 
  ggplot(aes(Internet1, val, col = Country)) +
  scale_x_continuous(
    "Internet users at previous year"
  ) +
  scale_y_continuous(
    "Rate"
  ) +
  geom_point() +
  geom_smooth(method = "lm", se = F, size = .2) +
  facet_wrap("Cause", scales = "free_y")
```

### GBD~Internet lme4

```{r}
# Fit GBD internet lmer models
file_path <- "output/lme-gbd-internet.rds"
if (!file.exists(file_path)) {
  fits_lme <- d %>% 
    group_by(Cause) %>% 
    partition(cluster) %>% 
    summarise(
      fit = list(
        lmer(
          val ~ (Time + Internet1) * Sex + 
            (1 + (Time + Internet1) * Sex | Region) +
            (1 + (Time + Internet1) * Sex | Country) +
            (1 + (Time + Internet1) * Sex | Age),
          data = cur_data_all()
        )
      )
    ) %>% 
    collect() %>% 
    ungroup()
  write_rds(fits_lme, file_path)
} else {
  fits_lme <- read_rds(file_path)
}
```

```{r}
x <- lmer(
  val ~ (Time + Internet1) * Sex + 
    (1 | Region) +
    (1 | Country) +
    (1 | Age),
  data = d %>% filter(Cause == "Depression") %>% slice_sample(prop = .1)
)
summary(x)

dm <- d %>% 
  mutate(
    Fixed = Fixed - mean(Fixed, na.rm = TRUE),
    Mobile = Mobile - mean(Mobile, na.rm = TRUE)
  )
dm <- dm %>% 
  pivot_longer(
    c(Fixed, Mobile), 
    names_to = "Internet", 
    values_to = "Subscriptions"
  )

# tidy function for lm's that fail
tidy_na <- possibly(
  function(x) bind_cols(tidy(x, conf.int = TRUE), nobs = nobs(x)), 
  tibble(estimate = NA)
)

cluster_copy(cluster, "tidy_na")
m1 <- dm %>% 
  group_by(Region, Country, Sex, Age, Cause, Internet) %>% 
  partition(cluster) %>%
  summarise(
    tidy_na(lm(val ~ Year + Subscriptions + lag(Subscriptions)))
  ) %>% 
  collect() %>%
  ungroup()
m1
coefs <- tmp %>% 
  summarise(
    Model1 = list(
      tidy_na(lm(Depression ~ Year, data = cur_data()))
    ),
    Model2 = list(
      tidy_na(lm(Depression ~ Year + lag(fixed), data = cur_data()))
    ),
    Model3 = list(
      tidy_na(lm(Depression ~ Year + lag(fixed) + fixed, data = cur_data()))
    )
  )
coefs %>% 
  pivot_longer(Model1:Model3) %>% 
  unnest(value) %>% 
  filter(term != "(Intercept)") %>% 
  filter(Country %in% sample(coefs$Country, 20)) %>% 
  ggplot(aes(estimate, Country, col = name)) +
  geom_point() +
  facet_wrap("term", nrow = 1, scales = "free_x")
```

## Model 2: Heterogeneity

Examine model 2's parameter heterogeneity across clusters.

### 2021-11-03 index.Rmd
Reparameterise gbd time models

@@
 library(tidybayes)
+library(naniar)
 library(ggdist)
@@
       panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4,4,4,4, "pt"))
+      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
     )
@@
 # Run this to delete fitted models and refit
-# unlink(list.files(pattern = "brm-.*\\.rds"))
+# unlink(list.files(pattern = "output/brm-.*\\.rds"))
 
 # parallel computations
-MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
-if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
+MAX_CORES <- parallel::detectCores(logical = TRUE) / 2
 cluster <- new_cluster(MAX_CORES)
@@
   select(itu, Internet) %>% 
-    naniar::miss_var_summary(),
+    miss_var_summary(),
   filter(itu, Year >= 2004) %>% 
     select(Fixed) %>% 
-    naniar::miss_var_summary(),
+    miss_var_summary(),
   filter(itu, Year >= 2007) %>% 
     select(Mobile) %>% 
-    naniar::miss_var_summary()
+    miss_var_summary()
 ) %>% 
@@
   theme(legend.position = "none")
-agg_png("output/Fig-ITU.png", height = 1200, width = 3200, res = 300)
+
 p_itu
-dev.off()
-agg_png("output/Fig-ITU-internet.png", height = 1200, width = 3200, res = 300)
+ggsave(
+  "output/Fig-ITU.png", 
+  device = agg_png,
+  height = 2400, width = 3200, res = 300, units = "px"
+)
+
 p_itu %+% 
@@
   facet_wrap("Region", nrow = 2)
-dev.off()
+ggsave(
+  "output/Fig-ITU-internet.png", 
+  device = agg_png,
+  height = 1200, width = 3200, res = 300, units = "px"
+)
 ```
@@
 p_gbd
-
 ggsave(
@@
 fit_empty <- brm(
-  val ~ Time * Sex + 
-    (1 + Time * Sex | Country) +
-    (1 + Time * Sex | Region) +
-    (1 + Time * Sex | Age),
-  data = filter(d, Cause == "Depression"),
+  val ~ 0 + Sex:Age + Time:Sex:Age + 
+    (0 + Sex:Age + Time:Sex:Age | Country) +
+    (0 + Sex:Age + Time:Sex:Age | Region),
+  data = filter(d_young, Cause == "Depression"),
   file = "output/brm-gbd-time-empty",
@@
 
-# cluster_copy(cluster, "fit_empty")
-fits_brm <- d %>% 
+fits_brm <- d_young %>% 
   group_by(Cause) %>% 

### 2021-11-05 index.Rmd
analyses wip

@@
     code_folding: true
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-We downloaded the relevant data from sources to data-raw. We cannot share the data here but indicate below how and when each data table was obtained.
+It is written in R Markdown and therefore contains all the code required for reproducing our computations.
+However some parts of the code were parallelised to work best with our local setup, so having e.g.
+a different number of cores will significantly impact the run-time of this script.
+
+Therefore we recommend reproducing the analyses by running them in interactive mode, and changing the parallelisation parameters by hand to best fit your setup.
 
@@
 
-```{r settings}
+```{r packages-settings}
+#| results: 'hide'
 # Packages
 library(readxl)
+library(ggtext)
+library(janitor)
 library(brms)
+library(gtsummary)
+library(imputeTS)
+library(broom.mixed)
 library(ragg)
@@
 library(countrycode)
-library(multidplyr)
 library(lme4)
@@
 
-# parallel computations
-MAX_CORES <- parallel::detectCores(logical = TRUE) / 2
-cluster <- new_cluster(MAX_CORES)
-cluster_library(cluster, c("lme4", "dplyr", "stringr"))
-
 # Create directory for intermediate files
@@
 
-### ITU
-
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>
-
-```{r}
-# Read and reshape fixed broadband data
-itu_fixed <- read_excel(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
-  sheet = 2,
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("Year", "Variable")) %>% 
-  pivot_wider(names_from = Variable) %>% 
-  mutate(value = as.numeric(value))
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_excel(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
-  sheet = 2,
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("Year", "Variable")) %>% 
-  pivot_wider(names_from = Variable) %>% 
-  mutate(value = as.numeric(value))
-
-# Percent using internet
-itu_percent <- read_excel(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("Year", "Variable")) %>% 
-  pivot_wider(names_from = Variable) %>% 
-  mutate(value = as.numeric(value))
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- left_join(
-  select(itu_percent, Country, Year, Internet = value),
-  select(itu_fixed, Country, Year, Fixed = value)
-) %>% 
-  left_join(
-    select(itu_mobile, Country, Year, Mobile = value)
-  ) %>% 
-  mutate(across(-Country, as.numeric))
-
-# values (1-100) to proportions (0-1)
-itu <- itu %>% 
-  mutate(across(c(Fixed, Mobile, Internet), function(x) x/100))
-
-# Standardise country names
-# This drops six small regions not recognised by countryname()
-itu <- itu %>% 
-  mutate(Country = countryname(Country)) %>% 
-  drop_na(Country)
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-```
-
-Remove countries with no internet data
-
-```{r}
-itu_countries_missing <- itu %>% 
-  group_by(Country) %>% 
-  summarise(
-    years = n(), 
-    missing_fixed = sum(is.na(Fixed)),
-    missing_mobile = sum(is.na(Mobile)),
-    missing_internet = sum(is.na(Internet))
-  ) %>% 
-  filter(
-    missing_fixed == years | 
-      missing_mobile == years |
-      missing_internet == years
-  )
-itu_countries_missing <- itu_countries_missing %>% 
-  filter(
-    missing_fixed==years & 
-      missing_mobile==years & missing_internet==years
-  ) %>% 
-  select(Country)
-itu <- anti_join(itu, itu_countries_missing)
-```
-
-Missing values
-
-```{r}
-# Calculate numbers of missing values for fixed (2004-) and mobile (2007-)
-bind_rows(
-  select(itu, Internet) %>% 
-    miss_var_summary(),
-  filter(itu, Year >= 2004) %>% 
-    select(Fixed) %>% 
-    miss_var_summary(),
-  filter(itu, Year >= 2007) %>% 
-    select(Mobile) %>% 
-    miss_var_summary()
-) %>% 
-  mutate(pct_miss = percent(pct_miss/100)) %>% 
-  kbl(caption = "ITU Missingness") %>% 
-  kable_styling(full_width = FALSE)
-```
-
-Impute missing values. We first replace missing initial values with zeros, assuming that they were not logged because practically zero. Then proceed with linear interpolation from there.
-
-```{r}
-library(imputeTS)
-
-itu <- itu %>% 
-  group_by(Country) %>% 
-  # If first value is missing, replace with zero
-  mutate(
-    i = 1:n(),
-    across(
-      c(Internet, Fixed, Mobile), 
-      .fns = list(
-        i = possibly(function(x) if_else(is.na(x) & i==1, 0, x), otherwise = NaN)
-      )
-    )
-  ) %>% 
-  # Linear interpolation
-  mutate(
-    across(
-      c(Internet_i, Fixed_i, Mobile_i), 
-      possibly(function(x) na_interpolation(x), otherwise = NaN)
-    )
-  ) %>% 
-  # Remove variables before they existed
-  mutate(
-    Fixed_i = if_else(Year < 2004, NaN, Fixed_i),
-    Mobile_i = if_else(Year < 2007, NaN, Mobile_i)
-  ) %>% 
-  # Remove unnecessary index variable
-  select(-i) %>% 
-  ungroup()
-
-# Don't impute observations forward (unless they are zeroes in the beginning)
-itu <- itu %>% 
-  mutate(
-    across(
-      ends_with("_i"), 
-      ~if_else(.x == lag(.x) & .x!=0, NaN, .x)
-    )
-  )
-
-# Examine output
-itu <- itu %>% 
-  select(
-    Country, Year, 
-    starts_with("Internet"),
-    starts_with("Fixed"),
-    starts_with("Mobile")
-  )
-# itu %>% 
-#   mutate(across(-c(Country, Year), ~percent(.x, .001))) %>% 
-#   View
-
-# Replace old variables with imputed
-itu <- itu %>% 
-  select(-c(Internet, Fixed, Mobile)) %>% 
-  rename_with(~str_replace(.x, "_i", ""))
-```
-
-### GBD
-
-The Global Burden of Disease data CSVs were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02.
-
-```{r gbd-data-clean}
+We downloaded the relevant data from sources to `data-raw/`. We cannot share the data here but indicate below how and when each data table was obtained.
+
+### Global Burden of Disease
+
+The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`.
+We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript.
+Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.
+
+```{r gbd-data-load}
 # Load data files and merge to one table
-# We need names and IDs because there are two Georgias
 gbd <- list.files(
@@
   read_csv()
-
+```
+
+We then ensure that the correct variables were downloaded, and then clean this data.
+
+```{r gbd-data-clean}
 # Cleaning
 
-# prevalence (total number of cases)
-# "Rate": Total cases per 100,000 population
-# We convert this to a percentage
-distinct(gbd, measure, metric)
+# First step is to clean names in all data sets
+gbd <- clean_names(gbd)
+
+# Confirm that correct measures were downloaded:
+# - prevalence: Total number of cases
+# - rate: Total cases per 100,000 population
+#   - We convert this to a percentage
+# distinct(gbd, measure, metric)
 gbd <- select(gbd, -metric, -measure)
@@
 # Clean cause names
-distinct(gbd, cause)
+# distinct(gbd, cause)
 gbd <- gbd %>% 
@@
       cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Self-harm"
-    )
-  )
-
-# Harmonise names with other datasets and capitalize
+      cause == "Self-harm" ~ "Selfharm"
+    )
+  )
+
+# Harmonise variable names with other datasets
 gbd <- gbd %>% 
-  rename(
-    Country = location,
-    Year = year,
-    Sex = sex,
-    Age = age,
-    Cause = cause
-  )
-
-# Harmonise country names
-# Check where new name doesn't match with proposed new name
-# gbd %>%
-#   distinct(Country) %>%
-#   mutate(Country2 = countryname(Country)) %>%
-#   filter(Country!=Country2 | is.na(Country2)) %>%
-#   arrange(Country) %>%
-#   View()
-# Replace old with new standard name, drop where new name doesn't exist
+  rename(country = location)
+
+# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
 gbd <- gbd %>% 
-  mutate(Country = countryname(Country)) %>% 
-  drop_na(Country)
-```
-
-### World bank
-
-```{r}
-wb <- read_csv(
-  "data-raw/world-bank/population/API_SP.POP.TOTL_DS2_en_csv_v2_2163507.csv", 
-  skip = 3
-)
-wb <- wb %>% 
-  select(Country = `Country Name`, `2000`:`2019`) %>%
-  pivot_longer(-Country, names_to = "Year", values_to = "Pop") %>% 
-  mutate(Year = as.numeric(Year))
-
-wb <- wb %>% 
-  mutate(Country = countryname(Country)) %>% 
-  drop_na(Country)
-```
-
-### GLOBE Regions
-
-We group the countries into GLOBE regions.
+  mutate(se = (upper-lower) / (1.96*2)) %>%
+  select(-c(upper, lower))
+```
+
+Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric.
+We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
+There is a harmonised name for each GBD country, and 27 country names are harmonised.
+
+```{r gbd-harmonise-countries}
+# Check what names were changed and if any don't have harmonised counterpart
+gbd %>%
+  distinct(country) %>% 
+  arrange(country) %>%
+  mutate(
+    country_harmonised = countryname(country, destination = "cldr.short.en")
+  ) %>% 
+  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
+  kbl() %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  scroll_box(width = "500px", height = "400px")
+# Harmonise old names after verifying above that none are dropped
+gbd <- gbd %>% 
+  mutate(country = countryname(country, destination = "cldr.short.en"))
+```
+
+### Gallup World Poll
+
+GWP cleaning goes here.
+
+### International Telecommunication Union
+
+The internet adoption data were downloaded from the ITU website in October 2021, and placed with their original file names to `data-raw/ITU/`. The specific URLs for obtaining the data files are
+
+- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
+- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
+- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>
+
+We first load, reshape, and merge these datasets.
+
+```{r itu-load-clean}
+# Read and reshape fixed broadband data
+itu_fixed <- read_xlsx(
+  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
+  sheet = 2,
+  col_types = "text"
+) %>% 
+  pivot_longer(-c(Indicator, Country)) %>% 
+  separate(name, into = c("year", "variable")) %>% 
+  pivot_wider(names_from = variable) %>% 
+  mutate(fixed = as.numeric(value)) %>% 
+  select(country = Country, year, fixed)
+
+# Read and reshape mobile broadband data
+itu_mobile <- read_xlsx(
+  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
+  sheet = 2,
+  col_types = "text"
+) %>% 
+  pivot_longer(-c(Indicator, Country)) %>% 
+  separate(name, into = c("year", "variable")) %>% 
+  pivot_wider(names_from = variable) %>% 
+  mutate(mobile = as.numeric(value)) %>% 
+  select(country = Country, year, mobile)
+
+# Percent using internet
+itu_percent <- read_xlsx(
+  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
+  col_types = "text"
+) %>% 
+  pivot_longer(-c(Indicator, Country)) %>% 
+  separate(name, into = c("year", "variable")) %>% 
+  pivot_wider(names_from = variable) %>% 
+  mutate(internet = as.numeric(value)) %>% 
+  select(country = Country, year, internet)
+
+# Merge to one table in wide format (oldest on left to include all years)
+itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
+
+# values (1-100) to proportions (0-1) and years to numbers
+itu <- itu %>% 
+  mutate(across(c(internet, fixed, mobile), function(x) x/100)) %>% 
+  mutate(year = as.numeric(year))
+
+# Drop tables
+rm(itu_fixed, itu_mobile, itu_percent)
+```
+
+Then harmonise country names as above, and drop countries that don't exist in outcomes.
+
+```{r itu-harmonise-countries}
+# Check what names were changed and if any don't have harmonised counterpart
+itu %>%
+  distinct(country) %>% 
+  arrange(country) %>%
+  mutate(
+    country_harmonised = countryname(country, destination = "cldr.short.en")
+  ) %>% 
+  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
+  kbl() %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  scroll_box(width = "500px", height = "400px")
+
+# Harmonise old names after verifying above that none are dropped
+itu <- itu %>% 
+  mutate(country = countryname(country, destination = "cldr.short.en"))
+
+# These countries don't exist in outcomes
+itu %>%
+  distinct(country) %>% 
+  anti_join(distinct(gbd, country)) %>% 
+  kbl() %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  scroll_box(width = "500px", height = "400px")
+
+# Drop them
+itu <- itu %>% 
+  filter(country %in% unique(gbd$country))
+```
+
+#### Missingness
+
+Remove countries with no observations
+
+```{r}
+itu <- itu %>% 
+  group_by(country) %>% 
+  mutate(nobs = sum(!is.na(internet))) %>% 
+  ungroup() %>% 
+  filter(nobs > 0) %>% 
+  select(-nobs)
+```
+
+There are some missing values in the data; in the Internet variable these are mainly in the first or last years of each country's time-series.
+This needs to be changed to calculate by-variable (with appropriate time-spans) when adding mobile and fixed
+
+```{r}
+miss_var_summary(itu)
+```
+
+We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values.
+
+```{r itu-impute}
+itu <- itu %>% 
+  group_by(country) %>% 
+  # Find first and last year with internet data in each country
+  mutate(
+    min_year = year[min(which(!is.na(internet)))],
+    max_year = year[max(which(!is.na(internet)))]
+  ) %>%
+  # Interpolate values linearly
+  # use possibly() to avoid errors for countries with no data
+  # Add variables to c() to impute for fixed and mobile broadband
+  mutate(
+    across(
+      c(internet), 
+      possibly(
+        function(x) na_interpolation(x, maxgap = Inf), 
+        # If function errors, provide original internet value
+        otherwise = internet
+      )
+    )
+  ) %>% 
+  # Take out projected (non-intermediate) imputed values
+  mutate(
+    internet = if_else(
+      between(year, unique(min_year), unique(max_year)), 
+      internet, 
+      NaN
+    )
+  ) %>% 
+  ungroup() %>% 
+  select(-min_year, -max_year)
+```
+
+We see that 96 intermediate internet use values were imputed to the time series.
+
+```{r}
+miss_var_summary(itu)
+```
+
+### Complete study dataset
+
+#### GLOBE regions
+
+We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
+This allows us to eg.
+present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
+We use the extended GLOBE regions following Jebb et al.
+(2020), and had to manually add labels to some countries that were not grouped in those studies.
 
@@
   # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(Country = str_remove_all(Country, "\\*")) %>% 
+  mutate(country = str_remove_all(country, "\\*")) %>% 
   # Standardize country names
   # This drops Nagorno-Karabakh Republic
-  mutate(Country = countryname(Country)) %>% 
-  drop_na(Country)
-
-distinct(itu, Country)
-distinct(regions, Region)
-
-# ITU countries not present in region data
+  mutate(country = countryname(country)) %>% 
+  drop_na(country)
+
+# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
+regions <- distinct(regions, region, country)
+
+# Countries in our dataset not present in region data
 filter(
-  distinct(itu, Country), 
-  !(Country %in% unique(regions$Country))
-) %>% 
-  arrange(Country) %>% 
-  write_csv("data-raw/Regions/ITU-countries-without-region.csv")
+  distinct(gbd, country), 
+  !(country %in% unique(regions$country))
+) %>% 
+  arrange(country) %>% 
+  write_csv("data-raw/Regions/GBD-countries-without-region.csv")
 
 # I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-regions <- read_csv(
-  "data-raw/Regions/ITU-countries-without-region-filled.csv"
-) %>% 
-  select(Country, Region) %>% 
-  bind_rows(regions) %>% 
-  drop_na(Region)
-
-# GBD countries not present in region data
-filter(
-  distinct(gbd, Country),
-  !(Country %in% unique(regions$Country))
-) %>% 
-  arrange(Country) %>% 
-  write_csv("data-raw/Regions/GBD-countries-without-region.csv")
-
-# Load in above filled with regions
+
+# Load our manually filled region data
+regions_filled <- read_csv(
+  "data-raw/Regions/GBD-countries-without-region-filled.csv"
+) 
+```
+
+We then combine all the region tables, clean region names, and join to our data
+
+```{r}
+# Combine Jebb et al GLOBE regions and our manually added ones
+regions <- regions %>% 
+  bind_rows(
+    regions_filled %>% 
+      mutate(Note = "Filled")
+  ) %>% 
+  arrange(region, country)
 
@@
 regions <- regions %>% 
-  mutate(Region = if_else(Region=="Sub-Sahara Africa", "Africa", Region))
-
-# Reorder labels
-regions <- regions %>% 
-  mutate(
-    Region = factor(
-      Region,
-      levels = c(
-        "Africa", "Latin America", "Anglo", "Arab", 
-        "Confucian Asia", "Southern Asia", "Eastern Europe", 
-        "Germanic Europe", "Latin Europe", "Nordic Europe"
-      )
-    )
-  )
-
-# Format labels to use line breaks instead of spaces
-levels(regions$Region) <- str_replace_all(levels(regions$Region), " ", "\n")
-
-# Remove duplicated countries
+  mutate(region = if_else(region=="Sub-Sahara Africa", "Africa", region))
+
+# Format regions to factors and use line breaks instead of spaces
+regions$region <- factor(regions$region)
+levels(regions$region) <- str_replace_all(levels(regions$region), " ", "\n")
+
+# Display table of regions and countries
 regions %>% 
-  count(Country, sort = TRUE)
-regions <- distinct(regions)
-
-# We then use these regions
+  kbl(caption = "All countries and regions.") %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  scroll_box(width = "500px", height = "400px")
+
+regions <- select(regions, -Note)
+```
+
+#### Create predictors
+
+We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.
+
+```{r}
+# For models, we rescale year; centred at 2013 and one unit indicates decade
 itu <- itu %>% 
-  left_join(regions)
-```
-
-## Complete study dataset
-
-We end up with a dataset that has predictors (internet access) at the level of country and year. Outcomes are also at the level of country and year, but additionally vary by sex and age group.
-
-```{r}
-# For models, we rescale year; centred at 2013 and one unit indicates 2007 to 2019
+  mutate(time = (year - 2013) / 10)
+
+# Create predictor: Lagged effect of 10% increase in internet
 itu <- itu %>% 
-  mutate(Time = (Year - 2013) / 12)
-
-# Create predictor, lagged and centered on 2013
+  arrange(country, year) %>% 
+  group_by(country) %>% 
+  mutate(i1 = lag(internet*10, 1)) %>% 
+  ungroup()
+
+# Centering within and between countries
 itu <- itu %>%
-  arrange(Country, Year) %>% 
-  group_by(Country) %>% 
-  mutate(Internet1 = lag(Internet, 1)) %>% 
-  mutate(Internet1 = Internet1 - Internet1[Year==2013]) %>%
-  ungroup()
-
-# Merge data sets
-d <- left_join(itu, gbd)
-
-# What to do with countries with no outcomes--drop
-d <- d %>% 
-  drop_na(Cause)
+  bmlm::isolate("i1", by = "country", which = "both")
+```
+
+#### Create tables
+
+Here, we join the ITU table to the GBD table.
+Note this appropriately duplicates the country-specific predictor values to the demographic groups within each country.
+We then create a table specific to young people.
+
+We also join regions to the data.
+
+```{r}
+# Add regions to data tables
+itu <- left_join(itu, regions)
+gbd <- left_join(gbd, regions)
+
+# Merge data tables
+gbd <- left_join(gbd, itu)
 
 # Contrast code sex
-d$Sex <- factor(d$Sex)
-contrasts(d$Sex) <- c(-.5, .5)
+gbd$sex <- factor(gbd$sex)
+contrasts(gbd$sex) <- c(-.5, .5)
+
+# Focus on young people
+gbd_all <- gbd
+gbd <- gbd %>% 
+  filter(age %in% c("15 to 19", "20 to 24"))
+
+# Contrast code binary age in young data set
+gbd$age <- factor(gbd$age)
+contrasts(gbd$age) <- c(-.5, .5)
+
+# Young data in wide format
+gbd_wide <- gbd %>%
+  pivot_wider(names_from = cause, values_from = c(val, se))
+names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
 ```
@@
 ```{r}
-# Mean users in first and last year
 itu %>% 
-  filter(Year %in% c(2000, 2020)) %>% 
-  group_by(Year) %>% 
-  summarise(mean(Internet, na.rm = TRUE))
-# Regions
+  filter(year %in% c(2001, 2019)) %>% 
+  select(region, country, year, internet) %>% 
+  pivot_wider(names_from = year, values_from = internet) %>% 
+  select(-country) %>% 
+  tbl_summary(by = region) %>% 
+  add_overall()
 itu %>% 
-  filter(Year == 2020) %>% 
-  group_by(Region, Year) %>% 
-  summarise(m = mean(Internet, na.rm = TRUE)) %>% 
-  arrange(m)
-itu %>% drop_na(Internet) %>% {length(unique(.$Country))}
+  group_by(country) %>% 
+  summarise(x = sum(!is.na(internet))) %>% 
+  arrange(x)
 ```
@@
 # Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
-p_itu <- itu %>% 
-  mutate(Year = make_date(Year)) %>% 
-  # Do something about countries with no region if they have outcome data
-  drop_na(Region) %>% 
-  pivot_longer(c(Fixed, Mobile, Internet), names_to = "Type") %>% 
-  mutate(Type = factor(Type, levels = c("Internet", "Fixed", "Mobile"))) %>% 
-  ggplot(
-    aes(
-      x = Year, 
-      y = value, 
-      group = interaction(Type, Country)
-    )
-  ) +
+itu %>% 
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(x = year, y = internet, group = country)) +
   coord_cartesian(ylim = c(0, 1.00)) +
-  scale_y_continuous(
-    "Internet users (or subscriptions) / population",
-    breaks = c(0, .25, .5, .75, 1),
-    labels = percent,
-    expand = expansion(c(0.02, 0.1))
-  ) +
-  scale_x_date(
-    breaks = breaks_width("5 years"),
-    labels = label_date("'%y")
-  ) +
-  geom_line(size = .25, col = "dodgerblue4") +
-  facet_grid(Type~Region) +
-  theme(legend.position = "none")
-
-p_itu
-ggsave(
-  "output/Fig-ITU.png", 
-  device = agg_png,
-  height = 2400, width = 3200, res = 300, units = "px"
-)
-
-p_itu %+% 
-  (filter(p_itu$data, Type == "Internet") %>% 
-     mutate(Region = str_replace(Region, "\n", " "))) + 
   scale_y_continuous(
@@
   ) +
-  facet_wrap("Region", nrow = 2)
+  scale_x_date(
+    breaks = breaks_width("5 years"),
+    labels = label_date("'%y")
+  ) +
+  geom_line(size = .25, col = "dodgerblue4") +
+  facet_wrap(~region, nrow = 2) +
+  theme(legend.position = "none")
 ggsave(
-  "output/Fig-ITU-internet.png", 
+  "output/Fig-ITU.png", 
   device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
+  height = 1400, width = 3200, res = 300, units = "px"
 )
@@
 ```{r}
-d_young <- d %>% 
-  drop_na(Region) %>% 
-  filter(Age %in% c("10 to 14", "15 to 19", "20 to 24"))
-
-pa <- d_young %>% 
-  ggplot(aes(Year, val, group = Country, col = Region)) +
+pa <- gbd %>% 
+  ggplot(aes(year, val, group = country, col = region)) +
   scale_y_continuous(
@@
   ) +
-  stat_summary(fun = mean, geom = "line", size = .4) +
-  facet_grid(Cause~Region, scales = "free_y") +
+  stat_summary(fun = mean, geom = "line", size = .5) +
+  facet_grid(cause~region, scales = "free_y") +
   theme(
@@
   )
-pb <- d_young %>% 
-  ggplot(aes(Year, val, col = Age, lty = Sex)) +
-  scale_color_brewer(palette = "Dark2") +
+pb <- gbd %>% 
+  mutate(Group = str_glue("{sex} ({age})")) %>% 
+  ggplot(aes(year, val, col = Group)) +
+  scale_color_brewer(palette = "Paired") +
   scale_y_continuous(
@@
   scale_x_continuous(
+    "Year",
     breaks = c(2000, 2005, 2010, 2015, 2020),
@@
   ) +
-  stat_summary(fun = mean, geom = "line", size = .5) +
-  facet_grid(Cause~Region, scales = "free_y")
+  stat_summary(fun = mean, geom = "line", size = .6) +
+  facet_grid(cause~region, scales = "free_y")
 
@@
 
-### GBD lm
-
-Estimate OLS for each cause for country-sex-age specific estimates
-
-```{r fit-gbd-time-lm}
-file_path <- "output/lm-gbd-time.rds"
+We first fit the models using lme4 because they are big and therefore would be very slow with brms.
+
+### GBD
+
+#### lme4
+
+```{r fit-gbd-time-lme4}
+# These take about 5-20 minutes each
+# run in parallel in background jobs
+# recommended to conduct this in interactive mode (rstudio)
+file_path <- "output/lme4-gbd-time.rds"
 if (!file.exists(file_path)) {
-  fits_lm <- d_young %>% 
-    group_by(Cause) %>% 
-    partition(cluster) %>% 
-    summarise(
-      fit = list(
-        lm(
-          val ~ 0 + Country:Sex:Age + Time:Country:Sex:Age,
-          data = cur_data_all()
-        )
-      )
-    ) %>% 
-    collect() %>% 
-    ungroup()
-  write_rds(fits_lm, file_path)
-} else {
-  fits_lm <- read_rds(file_path)
-}
-```
-
-```{r}
-tidy(fits_lm$fit[[1]])
-# Get country-sex-age specific parameters
-fits_lm %>% 
-  mutate(out = map(fit, tidy))
-```
-
-### GBD lme4
-
-```{r fit-gbd-time-lmer}
-# Fit GBD time lmer models
-file_path <- "output/lme-gbd-time.rds"
-if (!file.exists(file_path)) {
-  fits_lme <- d_young %>% 
-    group_by(Cause) %>% 
-    partition(cluster) %>% 
-    summarise(
-      fit = list(
-        lmer(
-          val ~ 0 + Sex:Age + Time:Sex:Age + 
-            (0 + Sex:Age + Time:Sex:Age | Region) +
-            (0 + Sex:Age + Time:Sex:Age | Country),
-          data = cur_data_all()
-        )
-      )
-    ) %>% 
-    collect() %>% 
-    ungroup()
-  write_rds(fits_lme, file_path)
-} else {
-  fits_lme <- read_rds(file_path)
-}
-```
-
-```{r}
-# lmer parameters
-```
-
-We want to visualise cluster-specific coefficients, but this is hard with lme4. Attempt
-
-```{r}
-# Get country-, region-, and age-specific parameters
-
-# Create scatterplots
-```
-
-### GBD brms
-
-Shall we fit multiple times: First without interaction with age, gender, then see if those matter?
-
-```{r fit-gbd-time-brms}
-fit_empty <- brm(
-  val ~ 0 + Sex:Age + Time:Sex:Age + 
-    (0 + Sex:Age + Time:Sex:Age | Country) +
-    (0 + Sex:Age + Time:Sex:Age | Region),
-  data = filter(d_young, Cause == "Depression"),
-  file = "output/brm-gbd-time-empty",
-  chains = 0,
-  threads = 3,
-)
-
-fits_brm <- d_young %>% 
-  group_by(Cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_empty,
-        newdata = cur_data_all(),
-        chains = 4,
-        cores = 4,
-        iter = 1600,
-        warmup = 800,
-        refresh = 10,
-        threads = 3,
-        file = str_glue("output/brm-gbd-time-{cur_group()}")
-      )
-    )
-  ) %>%
-  ungroup()
-```
-
-Fixed effects
-
-```{r}
-tmp <- fits_brm %>% 
-  mutate(
-    parameters = map(
-      fit,
-      ~posterior_summary(., pars = c("b_", "sd_", "cor_"))
-    )
-  )
-tmp %>% 
+  library(job)
+  job({fit_anx <- lmer(
+    Anxiety ~ 1 + time * sex * age + 
+      (1 + time * sex * age | region) +
+      (1 + time * sex * age | country),
+    data = gbd_wide
+  )}, title = "Anxiety time (lmer)")
+  job({fit_dep <- lmer(
+    Depression ~ 1 + time * sex * age + 
+      (1 + time * sex * age | region) +
+      (1 + time * sex * age | country),
+    data = gbd_wide
+  )}, title = "Depression time (lmer)")
+  job({fit_sel <- lmer(
+    Selfharm ~ 1 + time * sex * age + 
+      (1 + time * sex * age | region) +
+      (1 + time * sex * age | country),
+    data = gbd_wide
+  )}, title = "Self harm time (lmer)")
+  fits_lmer <- distinct(gbd, cause) %>% 
+    mutate(fit = list(fit_anx, fit_dep, fit_sel))
+  write_rds(fits_lmer, file_path)
+} else {fits_lmer <- read_rds(file_path)}
+```
+
+Plot fixed effects and by demographic
+
+```{r}
+# Fixed effects parameters
+fixed_effects <- fits_lmer %>% 
+  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
   select(-fit) %>% 
-  unnest(parameters) %>% 
-  filter(!str_detect(Parameter, "cor_"), Parameter != "sigma") %>% 
-  separate(
-    Parameter, c("Parameter", "Group", "Term"), 
-    sep = "_", 
-    extra = "merge"
-  ) %>%
-  mutate(Term = coalesce(Term, Group)) %>% 
-  mutate(Group = if_else(Parameter == "b", "", Group)) %>% 
-  mutate(Term = str_remove(Term, "_")) %>% 
-  ggplot(aes(Median, Term, color = Cause)) +
-  geom_vline(xintercept = 0, size = .2, lty = 2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodgev(.4)
-  ) +
-  facet_nested(~ Parameter + Group)
-
-# Fixed-effects plot
-fixef_draws <- fits_brm %>% 
-  mutate(
-    samples = map(
-      fit, 
-      ~emtrends(.x, "Sex", "Time") %>% 
-        gather_emmeans_draws()
-    )
-  ) %>% 
-  select(-fit)
-fixef_draws
-p_gbd_m1 <- fixef_draws %>% 
-  unnest(samples) %>% 
-  ggplot(aes(.value/1.2, Cause, col = Sex, fill = Sex)) +
-  scale_x_continuous(
-    "Change / decade [95%CI]",
-    breaks = pretty_breaks()
-  ) +
-  scale_color_brewer("Sex", palette = "Set1", aesthetics = c("color", "fill")) +
-  geom_vline(xintercept = 0, size = .2, lty = 2) +
-  stat_pointinterval(
-    position = position_dodgev(.3),
-    .width = c(.8, .95),
-    size = .5
-  ) +
-  stat_halfeye(
-    position = position_dodgev(.3), normalize = "panels",
-    alpha = .4, point_interval = NULL, show.legend = FALSE
-  )
-p_gbd_m1
-```
-
-Plot of fixed and random effects
-
-```{r}
-# These strings make hypothesis() calculate sex-specific slopes given my contrast codes for Sex
-h_sex <- c(
-  "Female" = "Time + Time:Sex1*-.5 = 0",
-  "Male" = "Time + Time:Sex1*.5 = 0"
-)
-# Summaries of fixed effects
-fixef_summary <- fits_brm %>% 
+  unnest(out) %>% 
+  standardize_names() %>% 
+  as_tibble() %>% 
+  filter(
+    Effects == "fixed", 
+    Parameter != "(Intercept)"
+  ) 
+# Fixed effects per demographic
+fixed_effects_demographics <- fits_lmer %>% 
   mutate(
@@
       fit,
-      ~hypothesis(.x, h_sex) %>% 
-        .$hypothesis
-    )
-  ) %>% 
-  select(-fit)
-# Summaries of random effects for age and country groupings
-# Get just average (across sexes) effects of time for random effects
-h_avg <- c("Average" = "Time = 0")
-ranef_summary <- fits_brm %>% 
-  expand_grid(G = c("Age", "Country")) %>% 
+      ~emtrends(.x, var = "time", by = c("sex", "age")) %>% 
+        parameters() %>% 
+        as.data.frame()
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  standardize_names() %>% 
+  as_tibble() %>% 
+  mutate(Parameter = str_glue("{sex}\n({age})"))
+
+# Random effects parameters
+random_effects <- fits_lmer %>% 
   mutate(
-    out = map2(
-      fit, G,
-      ~hypothesis(.x, h_avg, scope = "coef", group = .y) %>% 
-        .$hypothesis
-    )
-  ) %>% 
-  select(-fit)
-
-p1 <- fixef_summary %>% 
+    coef_region = map(
+      fit, 
+      ~bind_rows(
+        coef(.x)$region %>% 
+        as.data.frame() %>% 
+        rownames_to_column("region"),
+        coef(.x)$country %>% 
+        as.data.frame() %>% 
+        rownames_to_column("country"),
+        .id = "cluster"
+      ) %>% 
+        mutate(cluster = factor(cluster, labels = c("region", "country")))
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(coef_region) %>% 
+  mutate(Type = "Effects") %>%
+  select(-`(Int      ,nc ercept)`)
+
+# Calculate random demographics time effects
+random_effects %>% 
+  mutate(
+    `Male (20 to 24)` = time + `time:sex1`*.5 + `time:sex1:age1`*.25
+  )
+
+pivot_longer(
+    c(`(Intercept)`:`time:sex1:age1`, `Male (20 to 24)`:`Female (15 to 19)`), 
+    names_to = "Parameter", 
+    values_to = "Coefficient"
+    )
+
+bind_rows(
+  fixed_effects,
+  fixed_effects_demographics, 
+  .id = "Type"
+) %>% 
+  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
+  mutate(Parameter = fct_inorder(Parameter)) %>%
+  mutate(cause = factor(cause)) %>% 
+  rowwise() %>% 
+  mutate(
+    sig = factor(
+      !between(0, CI_low, CI_high), 
+      levels = c(TRUE, FALSE)
+    )
+  ) %>% 
+  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
+  scale_color_discrete(
+    "Outcome"
+  ) +
+  scale_x_continuous(
+    "Estimate (95%CI)"
+  ) +
+  scale_shape_manual(values = c(19, 21)) +
+  geom_vline(xintercept = 0, size = .2, alpha = .2) +
+  geom_point(
+    data = random_effects %>% 
+      filter(cluster == "country"), 
+    shape = 1, size = .15, alpha = .2,
+    position = position_dodge2v(.5)
+    ) +
+  geom_pointrangeh(
+    aes(xmin = CI_low, xmax = CI_high),
+    position = position_dodge2v(.5),
+    fill = "white", size = .3, fatten = 5
+  ) +
+  guides(shape = "none") +
+  facet_wrap("Type", ncol = 2, scales = "free") +
+  theme(axis.title.y = element_blank())
+```
+
+#### brms
+
+```{r fit-gbd-time-brms, eval = FALSE}
+# bf_gbd_time <- bf(
+#   mvbind(
+#     val_Depression,
+#     val_Anxiety,
+#     val_Self_harm
+#   ) ~ 1 + Time +
+#     (1 + Time || region) +
+#     (1 + Time || country)
+# ) +
+#   set_rescor(FALSE)
+# 
+# fit_gbd_time <- brm(
+#   bf_gbd_time,
+#   gbd_y_w,
+#   file = "output/brm-gbd-time-mv",
+#   chains = 5,
+#   cores = 5,
+#   iter = 300, warmup = 150, refresh = 10,
+#   threads = 2,
+#   control = list(adapt_delta = .9, max_treedepth = 15)
+# )
+
+bf_gbd_time_demos <- bf(
+  mvbind(
+    Depression,
+    Anxiety,
+    Selfharm
+  ) ~ 1 + Time * Sex * Age +
+    (1 + Time * Sex * Age || region) +
+    (1 + Time * Sex * Age || country)
+) +
+  set_rescor(FALSE)
+
+p <- prior(normal(0, 1), class = b, resp = Anxiety) +
+  prior(normal(0, 1), class = b, resp = Depression) +
+  prior(normal(0, 1), class = b, resp = Selfharm) +
+  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
+  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
+  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)
+
+fit_gbd_time_demos <- brm(
+  bf_gbd_time_demos,
+  gbd_y_w,
+  prior = p,
+  file = "output/brm-gbd-time-mv-demos",
+  chains = 5,
+  cores = 5,
+  iter = 250, warmup = 150, refresh = 10,
+  threads = 2,
+  control = list(adapt_delta = .9, max_treedepth = 15)
+)
+```
+
+##### Plot: Average effects of time
+
+```{r eval = FALSE}
+fixef(fit_gbd_time) %>%
+  as.data.frame() %>% 
+  rownames_to_column("Parameter") %>% 
+  as_tibble()
+
+h <- paste(
+  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
+  "= 0"
+)
+
+# Prepare average samples
+time_avg <- hypothesis(fit_gbd_time, h)
+time_avg_samples <- time_avg$samples
+names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
+time_avg_samples <- time_avg_samples %>% 
+  pivot_longer(everything(), names_to = "Parameter") %>% 
+  mutate(region = "Average")
+
+# Prepare region samples
+time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
+time_region_samples <- time_region$samples
+names(time_region_samples) <- paste(
+  time_region$hypothesis$Hypothesis, 
+  time_region$hypothesis$Group, sep = ":"
+)
+time_region_samples <- time_region_samples %>% 
+  pivot_longer(everything(), names_to = "Parameter") %>% 
+  separate(Parameter, c("Parameter", "region"), sep = ":")
+
+# Prepare country point estimates
+time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
+time_country_hypothesis <- time_country$hypothesis %>% 
+  rename(country = Group, Parameter = Hypothesis)
+time_country_hypothesis <- left_join(
+  time_country_hypothesis, 
+  distinct(fit_gbd_time$data, country, region)
+)
+
+time_sum <- bind_rows(
+  time_region$hypothesis,
+  time_avg$hypothesis %>% mutate(Group = "Average")
+) %>% 
+  as_tibble() %>% 
+  rename(region = Group, Parameter = Hypothesis)
+
+bind_rows(
+  time_region_samples,
+  time_avg_samples
+) %>% 
+  mutate(region = fct_relevel(region, "Average")) %>% 
+  mutate(Average = region == "Average") %>% 
+  ggplot(aes(value/10, region)) +
+  scale_y_discrete(
+    expand = expansion(c(0.025, 0.075)),
+    labels = function(x) ifelse(x == "Average", "**Average**", x)
+  ) +
+  scale_x_continuous(
+    "Estimated yearly change",
+    breaks = pretty_breaks(5)
+  ) +
+  scale_alpha_manual(values = c(.5, 1)) +
+  geom_vline(xintercept = 0, size = .2, alpha = .25) +
+  stat_eye(
+    side = "top",
+    aes(col = region, fill = region, alpha = Average),
+    point_interval = NULL,
+    normalize = "panels", 
+    height = .75
+  ) +
+  geom_pointrangeh(
+    data = time_sum,
+    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
+    size = .3, fatten = 1.4
+  ) +
+  geom_point(
+    data = time_country_hypothesis,
+    aes(col = region, x = Estimate/10), 
+    size = .5,
+    alpha = .25,
+    position = position_nudge(y = -.05)
+  ) +
+  facet_wrap(
+    "Parameter", ncol = 3, scales = "free_x",
+    labeller = as_labeller(
+      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
+  ) +
+  theme(
+    axis.text.y = element_markdown(),
+    legend.position = "none",
+    axis.title.y = element_blank()
+  )
+ggsave(
+  "output/Fig-brm-time-forest.png", 
+  device = agg_png,
+  height = 1200, width = 3200, res = 300, units = "px"
+)
+```
+
+## Model 2: Associations
+
+This model expands the above to add internet adoption as a predictor.
+
+### GBD
+
+#### Figure
+
+```{r}
+gbd %>% 
+  ggplot(
+    aes(
+      x = i1_cw/10, 
+      y = val, 
+      col = region, fill = region
+    )
+  ) +
+  geom_point(size = .25, alpha = .1) +
+  stat_smooth(method = "lm", alpha = .2, size = .3) +
+  # stat_summary(fun = mean, geom = "line", size = .25) +
+  facet_grid(Cause~region, scales = "free_y") +
+  theme(legend.position = "none")
+```
+
+#### lme4
+
+```{r fit-gbd-internet-lme4}
+# These take about 1-3 hours each
+# run in parallel in background jobs
+# recommended to conduct this in interactive mode (rstudio)
+file_path <- "output/lme4-gbd-internet.rds"
+if (!file.exists(file_path)) {
+  library(job)
+  job({fit_anx <- lmer(
+    Anxiety ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
+      (1 + time * sex * age + i1_cw * sex * age | region) +
+      (1 + time * sex * age + i1_cw * sex * age | country),
+    data = gbd_wide
+  )}, title = "Anxiety internet (lmer)")
+  job({fit_dep <- lmer(
+    Depression ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
+      (1 + time * sex * age + i1_cw * sex * age | region) +
+      (1 + time * sex * age + i1_cw * sex * age | country),
+    data = gbd_wide
+  )}, title = "Depression internet (lmer)")
+  job({fit_sel <- lmer(
+    Selfharm ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
+      (1 + time * sex * age + i1_cw * sex * age | region) +
+      (1 + time * sex * age + i1_cw * sex * age | country),
+    data = gbd_wide
+  )}, title = "Self harm internet (lmer)")
+  fits_lmer <- distinct(gbd, cause) %>% 
+    mutate(fit = list(fit_anx, fit_dep, fit_sel))
+  write_rds(fits_lmer, file_path)
+} else {fits_lmer <- read_rds(file_path)}
+```
+
+```{r}
+fits_lmer %>% 
+  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
+  select(-fit) %>% 
   unnest(out) %>% 
-  ggplot(aes(Estimate, Cause, col = Hypothesis)) +
-  scale_color_brewer(palette = "Set1") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
-    position = position_dodgev(.4)
-  ) +
-  theme(legend.position = "none")
-
-p2 <- ranef_summary %>% 
-  filter(G == "Age") %>% 
-  unnest(out) %>% 
-  ggplot(aes(Estimate, Cause, col = Group)) +
-  scale_color_viridis_d() +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
-    position = position_dodgev(.4),
-    size = .4, fatten = 1.5
-  ) +
-  guides(color = guide_legend(nrow = 4)) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_blank(),
-    legend.position = "bottom", 
-    legend.title = element_blank()
-  )
-
-p3 <- ranef_summary %>% 
-  filter(G == "Country") %>% 
-  unnest(out) %>% 
-  left_join(distinct(d, Country, Region), by = c("Group" = "Country")) %>% 
-  ggplot(aes(Estimate, Cause, col = Region)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI.Lower, xmax = CI.Upper),
-    position = position_dodgev(.4),
-    size = .4, fatten = 1.5
-  ) +
-  guides(color = guide_legend(nrow = 4)) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_blank(),
-    legend.position = "bottom",
-    legend.title = element_blank()
-  )
-
-p1 / (p2 | p3)
-```
-
-```{r}
-# Plot of age random + fixed
-# Age
-p_gbd_m2 <- ranef_summary %>% 
-  filter(G == "Age") %>% 
-  unnest(out) %>% 
-  pivot_wider(names_from = Hypothesis, values_from = Estimate:Star) %>% 
-  ggplot(aes(Estimate_Female, Estimate_Male)) +
-  geom_blank(aes(Estimate_Male, Estimate_Female)) +
-  scale_x_continuous(
-    "Change [Females]",
-    breaks = pretty_breaks(3)
-  ) +
-  scale_y_continuous(
-    "Change [Males]",
-    breaks = pretty_breaks(3)
-  ) +
-  scale_color_viridis_d("Age") +
-  geom_vline(xintercept = 0, size = .2, lty = 2) +
-  geom_hline(yintercept = 0, size = .2, lty = 2) +
-  geom_abline(size = .2) +
-  geom_point(aes(col = Group)) +
-  # Male summary
-  geom_pointrange(
-    data = fixef_summary %>% 
-      unnest(out) %>% 
-      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
-    aes(ymin = CI.Lower_Male, ymax = CI.Upper_Male)
-  ) +
-  # Female summary
-  geom_pointrange(
-    data = fixef_summary %>% 
-      unnest(out) %>% 
-      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
-    aes(xmin = CI.Lower_Female, xmax = CI.Upper_Female)
-  ) +
-  facet_wrap("Cause", nrow = 1, scales = "free") +
-  theme(aspect.ratio = 1)
-# Country
-p_gbd_m3 <- ranef_summary %>% 
-  filter(G == "Country") %>% 
-  unnest(out) %>% 
-  pivot_wider(names_from = Hypothesis, values_from = Estimate:Star) %>%
-  left_join(distinct(d, Country, Region), by = c("Group" = "Country")) %>% 
-  ggplot(aes(Estimate_Female, Estimate_Male)) +
-  geom_blank(aes(Estimate_Male, Estimate_Female)) +
-  scale_x_continuous(
-    "Change [Females]",
-    breaks = pretty_breaks(3)
-  ) +
-  scale_y_continuous(
-    "Change [Males]",
-    breaks = pretty_breaks(3)
-  ) +
-  geom_vline(xintercept = 0, size = .2, lty = 2) +
-  geom_hline(yintercept = 0, size = .2, lty = 2) +
-  geom_abline(size = .2) +
-  geom_point(shape = 1, aes(col = Region)) +
-  # Male summary
-  geom_pointrange(
-    data = fixef_summary %>% 
-      unnest(out) %>% 
-      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
-    aes(ymin = CI.Lower_Male, ymax = CI.Upper_Male)
-  ) +
-  # Female summary
-  geom_pointrange(
-    data = fixef_summary %>% 
-      unnest(out) %>% 
-      pivot_wider(names_from = Hypothesis, values_from = Estimate:Star),
-    aes(xmin = CI.Lower_Female, xmax = CI.Upper_Female)
-  ) +
-  facet_wrap("Cause", nrow = 1, scales = "free") +
-  theme(aspect.ratio = 1)
-```
-
-```{r}
-((p_gbd_m3 | p_gbd_m2) & theme(legend.position = "none")) +
-  plot_annotation(tag_levels = "A")
-```
-
-Add these plots to a single figure with data
-
-```{r}
-pa <- (p_gbd_1 / p_gbd_2) +
-  plot_layout(heights = c(4.5, 5.5))
-pb <- (p_gbd_3 / p_gbd_4) &
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 1),
-      ncol = 1,
-      revese = TRUE
-    )
-  ) &
-  plot_layout(heights = c(3, 7))
-pc <- (p_gbd_m3 + theme(legend.position = "none") | 
-         p_gbd_m2 + theme(legend.position = "none")) &
-  theme(axis.text = element_text(size = 8))
-p_gbd <- ((pa | pb) / pc) + 
-  plot_layout(heights = c(8.8, 1.2)) +
-  plot_annotation(tag_levels = "A")
-
-agg_png(
-  "output/Fig-GBD-with-parameters.png",
-  height = 2600, width = 3600, res = 300
-)
-p_gbd
-dev.off()
-```
-
-## Model 2: Associations
-
-### Figure
-
-```{r}
-d %>% 
-  filter(
-    Region == "Anglo",
-    Sex == "Female",
-    Age == "15 to 19"
-  ) %>% 
-  ggplot(aes(Internet1, val, col = Country)) +
-  scale_x_continuous(
-    "Internet users at previous year"
-  ) +
-  scale_y_continuous(
-    "Rate"
-  ) +
-  geom_point() +
-  geom_smooth(method = "lm", se = F, size = .2) +
-  facet_wrap("Cause", scales = "free_y")
-```
-
-### GBD~Internet lme4
-
-```{r}
-# Fit GBD internet lmer models
-file_path <- "output/lme-gbd-internet.rds"
-if (!file.exists(file_path)) {
-  fits_lme <- d %>% 
-    group_by(Cause) %>% 
-    partition(cluster) %>% 
-    summarise(
-      fit = list(
-        lmer(
-          val ~ (Time + Internet1) * Sex + 
-            (1 + (Time + Internet1) * Sex | Region) +
-            (1 + (Time + Internet1) * Sex | Country) +
-            (1 + (Time + Internet1) * Sex | Age),
-          data = cur_data_all()
-        )
-      )
-    ) %>% 
-    collect() %>% 
-    ungroup()
-  write_rds(fits_lme, file_path)
-} else {
-  fits_lme <- read_rds(file_path)
-}
-```
-
-```{r}
-x <- lmer(
-  val ~ (Time + Internet1) * Sex + 
-    (1 | Region) +
-    (1 | Country) +
-    (1 | Age),
-  data = d %>% filter(Cause == "Depression") %>% slice_sample(prop = .1)
-)
-summary(x)
-
-dm <- d %>% 
-  mutate(
-    Fixed = Fixed - mean(Fixed, na.rm = TRUE),
-    Mobile = Mobile - mean(Mobile, na.rm = TRUE)
-  )
-dm <- dm %>% 
-  pivot_longer(
-    c(Fixed, Mobile), 
-    names_to = "Internet", 
-    values_to = "Subscriptions"
-  )
-
-# tidy function for lm's that fail
-tidy_na <- possibly(
-  function(x) bind_cols(tidy(x, conf.int = TRUE), nobs = nobs(x)), 
-  tibble(estimate = NA)
-)
-
-cluster_copy(cluster, "tidy_na")
-m1 <- dm %>% 
-  group_by(Region, Country, Sex, Age, Cause, Internet) %>% 
-  partition(cluster) %>%
-  summarise(
-    tidy_na(lm(val ~ Year + Subscriptions + lag(Subscriptions)))
-  ) %>% 
-  collect() %>%
-  ungroup()
-m1
-coefs <- tmp %>% 
-  summarise(
-    Model1 = list(
-      tidy_na(lm(Depression ~ Year, data = cur_data()))
-    ),
-    Model2 = list(
-      tidy_na(lm(Depression ~ Year + lag(fixed), data = cur_data()))
-    ),
-    Model3 = list(
-      tidy_na(lm(Depression ~ Year + lag(fixed) + fixed, data = cur_data()))
-    )
-  )
-coefs %>% 
-  pivot_longer(Model1:Model3) %>% 
-  unnest(value) %>% 
-  filter(term != "(Intercept)") %>% 
-  filter(Country %in% sample(coefs$Country, 20)) %>% 
-  ggplot(aes(estimate, Country, col = name)) +
-  geom_point() +
-  facet_wrap("term", nrow = 1, scales = "free_x")
-```
-
-## Model 2: Heterogeneity
-
-Examine model 2's parameter heterogeneity across clusters.
+  filter(term == "i1_cw")
+```
+
+#### brms
+
+```{r fit-gbd-internet-brms, eval = FALSE}
+# bf_gbd_internet <- bf(
+#   mvbind(
+#     val_Depression,
+#     val_Anxiety,
+#     val_Self_harm
+#   ) ~ 1 + Time + i1_cw + i1_cb +
+#     (1 + Time + i1_cw || region)
+#   (1 + Time + i1_cw || country)
+# ) +
+#   set_rescor(FALSE)
+# 
+# fit_gbd_internet <- brm(
+#   bf_gbd_internet,
+#   gbd_y_w,
+#   file = "output/brm-gbd-internet-mv",
+#   chains = 5,
+#   cores = 5,
+#   iter = 300, warmup = 150, refresh = 10,
+#   threads = 2,
+#   control = list(adapt_delta = .9, max_treedepth = 15)
+# )
+
+bf_gbd_internet_demos <- bf(
+  mvbind(
+    Depression,
+    Anxiety,
+    Selfharm
+  ) ~ 1 + Time * Sex * Age + i1_cw * Sex * Age + i1_cb +
+    (1 + Time * Sex * Age + i1_cw * Sex * Age || region) +
+    (1 + Time * Sex * Age + i1_cw * Sex * Age || country)
+) +
+  set_rescor(FALSE)
+
+p <- prior(normal(0, 1), class = b, resp = Anxiety) +
+  prior(normal(0, 1), class = b, resp = Depression) +
+  prior(normal(0, 1), class = b, resp = Selfharm) +
+  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
+  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
+  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)
+
+fit_gbd_internet_demos <- brm(
+  bf_gbd_internet_demos,
+  gbd_y_w,
+  prior = p,
+  file = "output/brm-gbd-internet-mv-demos",
+  chains = 5,
+  cores = 5,
+  iter = 250, warmup = 150, refresh = 10,
+  threads = 2,
+  control = list(adapt_delta = .9, max_treedepth = 15)
+)
+```

### 2021-11-08 index.Rmd
Add new timeseries plot

@@
 
+### Multiple lines
+
+Here we create two plots. One to show all main variables' time trends for each region, and country within region. Then, show the outcome time trends for top internet trend in each region.
+
+```{r}
+pa <- bind_rows(
+  gbd %>% 
+    group_by(region, country, year, cause) %>% 
+    summarise(mean = mean(val/100)),
+  itu %>% 
+    group_by(region, country, year) %>% 
+    summarise(mean = mean(internet, na.rm = TRUE)) %>% 
+    mutate(cause = "Internet")
+) %>% 
+  ungroup() %>% 
+  mutate(cause = fct_relevel(cause, "Internet")) %>% 
+  mutate(year = make_date(year)) %>% 
+  ggplot(aes(year, mean, color = cause)) +
+  scale_color_brewer(
+    "Variable",
+    palette = "Set1", direction = -1
+  ) +
+  scale_y_continuous(
+    "Rate",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015)), 
+    date_labels = "'%y", 
+    expand = expansion(.02)
+  ) +
+  geom_line(aes(group = interaction(country, cause)), alpha = .25, size = .4) +
+  stat_summary(fun = mean, geom = "line", size = .6) +
+  facet_grid(cause~region, scales = "free_y") +
+  theme(legend.position = "none")
+
+# Get top 1 internet trend country in each region
+top_trends <- gbd %>% 
+  semi_join(distinct(itu, country)) %>% 
+  group_by(region, country) %>% 
+  summarise(tidy(lm(internet ~ time, data = cur_data_all()))) %>% 
+  filter(term == "time") %>% 
+  group_by(region) %>% 
+  slice_max(order_by = estimate, n = 1)
+pb <- gbd %>% 
+  filter(country %in% top_trends$country) %>%
+  mutate(country = factor(country, levels = top_trends$country)) %>% 
+  mutate(Group = str_glue("{sex} ({age})")) %>% 
+  mutate(year = make_date(year)) %>% 
+  ggplot(aes(year, val/100, col = Group)) +
+  scale_color_brewer(palette = "Paired") +
+  scale_y_continuous(
+    "Rate",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015)), 
+    date_labels = "'%y", 
+    expand = expansion(.02)
+  ) +
+  stat_summary(fun = mean, geom = "line", size = .6) +
+  facet_grid(cause~country, scales = "free_y")
+
+(pa + theme(axis.title.x = element_blank())) / 
+  pb * 
+  theme(panel.spacing = unit(2, "pt")) +
+  plot_layout(heights = c(4, 3)) +
+  plot_annotation(tag_levels = "A")
+ggsave(
+  "output/Fig-all-vars-timeseries.png", 
+  device = agg_png,
+  height = 2400, width = 3600, res = 300, units = "px"
+)
+```
+
 ## Model 1: Temporal trends

### 2021-11-10 index.Rmd
Way more models.

--- 2021-11-05 index.Rmd
@@
 
-```{r}
+```{r eval = FALSE}
 pa <- gbd %>% 
@@
 
-# Calculate random demographics time effects
-random_effects %>% 
-  mutate(
-    `Male (20 to 24)` = time + `time:sex1`*.5 + `time:sex1:age1`*.25
-  )
-
-pivot_longer(
-    c(`(Intercept)`:`time:sex1:age1`, `Male (20 to 24)`:`Female (15 to 19)`), 
-    names_to = "Parameter", 
-    values_to = "Coefficient"
-    )
-
 bind_rows(
@@
   geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_point(
-    data = random_effects %>% 
-      filter(cluster == "country"), 
-    shape = 1, size = .15, alpha = .2,
-    position = position_dodge2v(.5)
-    ) +
   geom_pointrangeh(
@@
 
-```{r fit-gbd-time-brms, eval = FALSE}
-# bf_gbd_time <- bf(
-#   mvbind(
-#     val_Depression,
-#     val_Anxiety,
-#     val_Self_harm
-#   ) ~ 1 + Time +
-#     (1 + Time || region) +
-#     (1 + Time || country)
-# ) +
-#   set_rescor(FALSE)
-# 
-# fit_gbd_time <- brm(
-#   bf_gbd_time,
-#   gbd_y_w,
-#   file = "output/brm-gbd-time-mv",
-#   chains = 5,
-#   cores = 5,
-#   iter = 300, warmup = 150, refresh = 10,
-#   threads = 2,
-#   control = list(adapt_delta = .9, max_treedepth = 15)
-# )
-
-bf_gbd_time_demos <- bf(
-  mvbind(
-    Depression,
-    Anxiety,
-    Selfharm
-  ) ~ 1 + Time * Sex * Age +
-    (1 + Time * Sex * Age || region) +
-    (1 + Time * Sex * Age || country)
-) +
+correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
+
+note we use beta so transform edge values
+
+we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
+
+##### Time: Main effects
+
+We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
+
+$$
+\begin{align*}
+y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\
+
+\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
+  \beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\
+
+i_{i[c][r]} &\sim 
+  \text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\
+
+\mu^i_{i[c][r]} &= \text{logit}(
+  \beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
+  \beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\
+
+\left[\begin{array}{c}
+\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
+\end{array}\right] 
+&\sim MVN(
+\left[\begin{array}{c}
+0 \\ 0 \\ 0 \\ 0
+\end{array}\right],
+\Sigma^c
+),
+
+\left[\begin{array}{c}
+\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
+\end{array}\right] 
+\sim MVN(
+\left[\begin{array}{c}
+0 \\ 0 \\ 0 \\ 0
+\end{array}\right],
+\Sigma^r
+)
+\end{align*}
+$$
+
+```{r}
+# Transform edge proportions to fit beta distribution
+gbd_10 <- gbd_wide %>% 
+  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999999, internet))
+
+# Define a model of internet proportion over time
+bf_int <- bf(
+  internet ~ 1 + time + 
+    (1 + time |c| country) +
+    (1 + time |r| region), 
+  family = Beta()
+)
+
+# Define models of outcomes
+bf_anx <- bf(
+  Anxiety ~ 1 + time + sex + age + 
+    (1 + time + sex + age |c| country) +
+    (1 + time + sex + age |r| region),
+  family = gaussian()
+)
+bf_dep <- bf(
+  Depression ~ 1 + time + sex + age + 
+    (1 + time + sex + age |c| country) +
+    (1 + time + sex + age |r| region),
+  family = gaussian()
+)
+bf_sel <- bf(
+  Selfharm ~ 1 + time + sex + age + 
+    (1 + time + sex + age |c| country) +
+    (1 + time + sex + age |r| region),
+  family = gaussian()
+)
+
+bf_time_mv <- bf(
+  mvbind(Depression, Anxiety, Selfharm) ~ 
+    1 + time +
+    (1 + time |c| country) +
+    (1 + time | region),
+  family = gaussian()
+) +
+  bf_int +
   set_rescor(FALSE)
 
-p <- prior(normal(0, 1), class = b, resp = Anxiety) +
-  prior(normal(0, 1), class = b, resp = Depression) +
-  prior(normal(0, 1), class = b, resp = Selfharm) +
-  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
-  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
-  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)
-
-fit_gbd_time_demos <- brm(
-  bf_gbd_time_demos,
-  gbd_y_w,
-  prior = p,
-  file = "output/brm-gbd-time-mv-demos",
-  chains = 5,
-  cores = 5,
-  iter = 250, warmup = 150, refresh = 10,
-  threads = 2,
-  control = list(adapt_delta = .9, max_treedepth = 15)
-)
-```
-
-##### Plot: Average effects of time
+# Fit models in background (need 12 cores)
+file_path <- "brm-time-main-effects"
+if (!file.exists(file_path)) {
+  job::job({
+    fit_anx <- brm(
+      bf_int + bf_anx + set_rescor(FALSE),
+      data = gbd_10,
+      file = "output/brm-gbd-time-anxiety",
+      chains = 4,
+      cores = 4,
+      iter = 1000, warmup = 600, refresh = 10,
+      threads = 1,
+      control = list(adapt_delta = .9)
+    )
+  }, title = "Fitting brms anxiety")
+  job::job({
+    fit_dep <- brm(
+      bf_int + bf_dep + set_rescor(FALSE),
+      data = gbd_10,
+      file = "output/brm-gbd-time-depression",
+      chains = 4,
+      cores = 4,
+      iter = 1000, warmup = 600, refresh = 10,
+      threads = 1,
+      control = list(adapt_delta = .9)
+    )
+  }, title = "Fitting brms depression")
+  fit_sel <- brm(
+    bf_int + bf_sel + set_rescor(FALSE),
+    data = gbd_10,
+    file = "output/brm-gbd-time-selfharm",
+    chains = 4,
+    cores = 4,
+    iter = 1000, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+  fits_brm_time_main <- tibble(
+    outcome = c("Anxiety", "Depression", "Selfharm"),
+    fit = list(fit_anx, fit_dep, fit_sel)
+  )
+  write_rds(fits_brm_time_main, file_path)
+} else {fits_brm_time_main <- read_rds(file_path)}
+```
+
+##### Time: Interactions
+
+```{r}
+# Define models of outcomes
+bf_anx <- bf(
+  Anxiety ~ 1 + time * sex + time * age + 
+    (1 + time * sex + time * age |c| country) +
+    (1 + time * sex + time * age |r| region),
+  family = gaussian()
+)
+bf_dep <- bf(
+  Depression ~ 1 + time + sex + age + 
+    (1 + time * sex + time * age |c| country) +
+    (1 + time * sex + time * age |r| region),
+  family = gaussian()
+)
+bf_sel <- bf(
+  Selfharm ~ 1 + time + sex + age + 
+    (1 + time * sex + time * age |c| country) +
+    (1 + time * sex + time * age |r| region),
+  family = gaussian()
+)
+
+# Fit models
+file_path <- "brm-time-interactions"
+if (!file.exists(file_path)) {
+  job::job({
+    fit_anx <- brm(
+      bf_int + bf_anx + set_rescor(FALSE),
+      data = gbd_10,
+      file = "output/brm-gbd-time-anxiety-int2",
+      chains = 4,
+      cores = 4,
+      iter = 1000, warmup = 600, refresh = 10,
+      threads = 1,
+      control = list(adapt_delta = .9)
+    )
+  }, title = "Fitting brms anxiety")
+  job::job({
+    fit_dep <- brm(
+      bf_int + bf_dep + set_rescor(FALSE),
+      data = gbd_10,
+      file = "output/brm-gbd-time-depression-int2",
+      chains = 4,
+      cores = 4,
+      iter = 1000, warmup = 600, refresh = 10,
+      threads = 1,
+      control = list(adapt_delta = .9)
+    )
+  }, title = "Fitting brms depression")
+  fit_sel <- brm(
+    bf_int + bf_sel + set_rescor(FALSE),
+    data = gbd_10,
+    file = "output/brm-gbd-time-selfharm-int2",
+    chains = 4,
+    cores = 4,
+    iter = 1000, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+  fits_brm_time_interactions <- tibble(
+    outcome = c("Anxiety", "Depression", "Selfharm"),
+    fit = list(fit_anx, fit_dep, fit_sel)
+  )
+  write_rds(fits_brm_time_interactions, file_path)
+} else {fits_brm_time_interactions <- read_rds(file_path)}
+```
+
+Model comparison using waic shows that interactive model is favored across the board.
+
+```{r eval = FALSE}
+waics <- left_join(
+  rename(fits_brm_time_main, fit_main = fit),
+  rename(fits_brm_time_interactions, fit_intr = fit)
+) %>% 
+  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
+waics$waic[[3]]
+```
+
+Show main effects
+
+Plot fixed effects and by demographic
+
+```{r}
+# Fixed effects parameters
+fixed_effects <- fits_brm_time_interactions %>% 
+  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  standardize_names() %>% 
+  as_tibble() %>% 
+  filter(
+    Effects == "fixed", 
+    Parameter != "(Intercept)"
+  ) 
+# Fixed effects per demographic
+fixed_effects_demographics <- fits_brm_time_interactions %>% 
+  mutate(
+    out = map2(
+      fit, outcome,
+      ~emtrends(
+        .x, 
+        var = "time", 
+        by = c("sex", "age"), 
+        resp = .y
+      ) %>% 
+        parameters() %>% 
+        as.data.frame()
+    )
+  )
+fixed_effects_demographics %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  standardize_names() %>% 
+  as_tibble() %>% 
+  mutate(Parameter = str_glue("{sex}\n({age})"))
+
+# Random effects parameters
+random_effects <- fits_lmer %>% 
+  mutate(
+    coef_region = map(
+      fit, 
+      ~bind_rows(
+        coef(.x)$region %>% 
+          as.data.frame() %>% 
+          rownames_to_column("region"),
+        coef(.x)$country %>% 
+          as.data.frame() %>% 
+          rownames_to_column("country"),
+        .id = "cluster"
+      ) %>% 
+        mutate(cluster = factor(cluster, labels = c("region", "country")))
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(coef_region) %>% 
+  mutate(Type = "Effects") %>%
+  select(-`(Int      ,nc ercept)`)
+
+bind_rows(
+  fixed_effects,
+  fixed_effects_demographics, 
+  .id = "Type"
+) %>% 
+  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
+  mutate(Parameter = fct_inorder(Parameter)) %>%
+  mutate(cause = factor(cause)) %>% 
+  rowwise() %>% 
+  mutate(
+    sig = factor(
+      !between(0, CI_low, CI_high), 
+      levels = c(TRUE, FALSE)
+    )
+  ) %>% 
+  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
+  scale_color_discrete(
+    "Outcome"
+  ) +
+  scale_x_continuous(
+    "Estimate (95%CI)"
+  ) +
+  scale_shape_manual(values = c(19, 21)) +
+  geom_vline(xintercept = 0, size = .2, alpha = .2) +
+  geom_pointrangeh(
+    aes(xmin = CI_low, xmax = CI_high),
+    position = position_dodge2v(.5),
+    fill = "white", size = .3, fatten = 5
+  ) +
+  guides(shape = "none") +
+  facet_wrap("Type", ncol = 2, scales = "free") +
+  theme(axis.title.y = element_blank())
+```
+
+```{r}
+library(modelbased)
+x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
+tmp <- fits_brm %>% 
+  mutate(
+    # Average effect
+    avg = map2(
+      fit, 
+      Outcome, 
+      ~hypothesis(.x, str_glue("{.y}_time = 0"))
+    ),
+    # By country effect
+    by_country = map2(
+      fit, 
+      Outcome, 
+      ~hypothesis(
+        .x, str_glue("{.y}_time = 0"), 
+        scope = "coef", group = "country"
+      )
+    ),
+    # By region effect
+    by_region = map2(
+      fit, 
+      Outcome, 
+      ~hypothesis(
+        .x, str_glue("{.y}_time = 0"), 
+        scope = "coef", group = "region"
+      )
+    )
+  ) %>% 
+  select(-fit)
+
+tmp %>% 
+  select(Outcome, avg) %>% 
+  mutate(avg = map(avg, ))
+
+tmp$by_region[[1]] %>% str
+
+h <- paste(
+  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
+  "= 0"
+)
+
+# Prepare average samples
+time_avg <- hypothesis(fit_gbd_time, h)
+time_avg_samples <- time_avg$samples
+names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
+time_avg_samples <- time_avg_samples %>% 
+  pivot_longer(everything(), names_to = "Parameter") %>% 
+  mutate(region = "Average")
+
+# Prepare region samples
+time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
+time_region_samples <- time_region$samples
+names(time_region_samples) <- paste(
+  time_region$hypothesis$Hypothesis, 
+  time_region$hypothesis$Group, sep = ":"
+)
+time_region_samples <- time_region_samples %>% 
+  pivot_longer(everything(), names_to = "Parameter") %>% 
+  separate(Parameter, c("Parameter", "region"), sep = ":")
+
+# Prepare country point estimates
+time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
+time_country_hypothesis <- time_country$hypothesis %>% 
+  rename(country = Group, Parameter = Hypothesis)
+time_country_hypothesis <- left_join(
+  time_country_hypothesis, 
+  distinct(fit_gbd_time$data, country, region)
+)
+
+time_sum <- bind_rows(
+  time_region$hypothesis,
+  time_avg$hypothesis %>% mutate(Group = "Average")
+) %>% 
+  as_tibble() %>% 
+  rename(region = Group, Parameter = Hypothesis)
+
+bind_rows(
+  time_region_samples,
+  time_avg_samples
+) %>% 
+  mutate(region = fct_relevel(region, "Average")) %>% 
+  mutate(Average = region == "Average") %>% 
+  ggplot(aes(value/10, region)) +
+  scale_y_discrete(
+    expand = expansion(c(0.025, 0.075)),
+    labels = function(x) ifelse(x == "Average", "**Average**", x)
+  ) +
+  scale_x_continuous(
+    "Estimated yearly change",
+    breaks = pretty_breaks(5)
+  ) +
+  scale_alpha_manual(values = c(.5, 1)) +
+  geom_vline(xintercept = 0, size = .2, alpha = .25) +
+  stat_eye(
+    side = "top",
+    aes(col = region, fill = region, alpha = Average),
+    point_interval = NULL,
+    normalize = "panels", 
+    height = .75
+  ) +
+  geom_pointrangeh(
+    data = time_sum,
+    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
+    size = .3, fatten = 1.4
+  ) +
+  geom_point(
+    data = time_country_hypothesis,
+    aes(col = region, x = Estimate/10), 
+    size = .5,
+    alpha = .25,
+    position = position_nudge(y = -.05)
+  ) +
+  facet_wrap(
+    "Parameter", ncol = 3, scales = "free_x",
+    labeller = as_labeller(
+      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
+  ) +
+  theme(
+    axis.text.y = element_markdown(),
+    legend.position = "none",
+    axis.title.y = element_blank()
+  )
+ggsave(
+  "output/Fig-brm-time-forest.png", 
+  device = agg_png,
+  height = 1200, width = 3200, res = 300, units = "px"
+)
+```
+
+##### Internet: Main effects
+
+```{r}
+# Define models of outcomes
+bf_anx <- bf(
+  Anxiety ~ 1 + time + sex + age + i1_cw + i1_cb +
+    (1 + time + sex + age + i1_cw |c| country) +
+    (1 + time + sex + age + i1_cw |r| region),
+  family = gaussian()
+)
+bf_dep <- bf(
+  Depression ~ 1 + time + sex + age + i1_cw + i1_cb +
+    (1 + time + sex + age + i1_cw |c| country) +
+    (1 + time + sex + age + i1_cw |r| region),
+  family = gaussian()
+)
+bf_sel <- bf(
+  Selfharm ~ 1 + time + sex + age + i1_cw + i1_cb + 
+    (1 + time + sex + age + i1_cw |c| country) +
+    (1 + time + sex + age + i1_cw |r| region),
+  family = gaussian()
+)
+
+# Fit models in background (need 12 cores)
+job::job({
+  fit_anx <- brm(
+    bf_int + bf_anx + set_rescor(FALSE),
+    data = gbd_10,
+    file = "output/brm-gbd-time-internet-anxiety",
+    chains = 4,
+    cores = 4,
+    iter = 1000, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+}, title = "Fitting brms anxiety")
+job::job({
+  fit_dep <- brm(
+    bf_int + bf_dep + set_rescor(FALSE),
+    data = gbd_10,
+    file = "output/brm-gbd-time-internet-depression",
+    chains = 4,
+    cores = 4,
+    iter = 1000, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+}, title = "Fitting brms depression")
+fit_sel <- brm(
+  bf_int + bf_sel + set_rescor(FALSE),
+  data = gbd_10,
+  file = "output/brm-gbd-time-internet-selfharm",
+  chains = 4,
+  cores = 4,
+  iter = 1000, warmup = 600, refresh = 10,
+  threads = 1,
+  control = list(adapt_delta = .9)
+)
+```
+
+##### Internet: Interactions
+
+```{r}
+# Define models of outcomes
+bf_anx <- bf(
+  Anxiety ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  family = gaussian()
+)
+bf_dep <- bf(
+  Depression ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  family = gaussian()
+)
+bf_sel <- bf(
+  Selfharm ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  family = gaussian()
+)
+
+# Fit models in background (need 12 cores)
+job::job({
+  fit_anx <- brm(
+    bf_anx,
+    data = gbd_wide,
+    file = "output/brm-gbd-time-internet-anxiety-int2",
+    chains = 4,
+    cores = 4,
+    iter = 1200, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+}, title = "Fitting brms anxiety")
+job::job({
+  fit_dep <- brm(
+    bf_dep,
+    data = gbd_wide,
+    file = "output/brm-gbd-time-internet-depression-int2",
+    chains = 4,
+    cores = 4,
+    iter = 1200, warmup = 600, refresh = 10,
+    threads = 1,
+    control = list(adapt_delta = .9)
+  )
+}, title = "Fitting brms depression")
+fit_sel <- brm(
+  bf_sel,
+  data = gbd_wide,
+  file = "output/brm-gbd-time-internet-selfharm-int2",
+  chains = 4,
+  cores = 4,
+  iter = 1200, warmup = 600, refresh = 10,
+  threads = 1,
+  control = list(adapt_delta = .9)
+)
+```
+
+###### Plot: Average effects of time
 
@@
     Selfharm
-  ) ~ 1 + Time * Sex * Age + i1_cw * Sex * Age + i1_cb +
-    (1 + Time * Sex * Age + i1_cw * Sex * Age || region) +
-    (1 + Time * Sex * Age + i1_cw * Sex * Age || country)
+  ) ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
+    (1 + time * sex * age + i1_cw * sex * age | country)
 ) +
@@
 
-p <- prior(normal(0, 1), class = b, resp = Anxiety) +
-  prior(normal(0, 1), class = b, resp = Depression) +
-  prior(normal(0, 1), class = b, resp = Selfharm) +
-  prior(student_t(7, 0, .5), class = sd, resp = Anxiety) +
-  prior(student_t(7, 0, .5), class = sd, resp = Depression) +
-  prior(student_t(7, 0, .5), class = sd, resp = Selfharm)
-
-fit_gbd_internet_demos <- brm(
+p <- prior(normal(0, 3), class = b, resp = Anxiety) +
+  prior(normal(0, 3), class = b, resp = Depression) +
+  prior(normal(0, 3), class = b, resp = Selfharm) +
+  prior(student_t(7, 0, 1), class = sd, resp = Anxiety) +
+  prior(student_t(7, 0, 1), class = sd, resp = Depression) +
+  prior(student_t(7, 0, 1), class = sd, resp = Selfharm)
+
+job::job({fit_gbd_internet_demos <- brm(
   bf_gbd_internet_demos,
-  gbd_y_w,
+  gbd_wide,
   prior = p,
@@
   cores = 5,
-  iter = 250, warmup = 150, refresh = 10,
-  threads = 2,
+  iter = 450, warmup = 300, refresh = 10,
+  threads = 1,
   control = list(adapt_delta = .9, max_treedepth = 15)
-)
-```
+)}, title = "brms internet")
+```

### 2021-11-10 index.Rmd
wip

--- 2021-11-10 index.Rmd
@@
   mutate(year = make_date(year)) %>%
-  ggplot(aes(x = year, y = internet, group = country)) +
+  ggplot(aes(x = year, y = internet)) +
   coord_cartesian(ylim = c(0, 1.00)) +
   scale_y_continuous(
-    "Internet users / population",
+    "Internet users",
     breaks = c(0, .25, .5, .75, 1),
@@
   ) +
-  geom_line(size = .25, col = "dodgerblue4") +
-  facet_wrap(~region, nrow = 2) +
+  geom_line(
+    aes(group = country),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line", 
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_wrap(~region, nrow = 1) +
   theme(legend.position = "none")
@@
   device = agg_png,
-  height = 1400, width = 3200, res = 300, units = "px"
+  height = 600, width = 3200, res = 300, units = "px"
+)
+```
+
+```{r}
+itu %>% 
+  mutate(year = make_date(year)) %>%
+  mutate(mobile = if_else(mobile > 1.50, NaN, mobile)) %>% 
+  pivot_longer(internet:mobile) %>% 
+  mutate(name = str_to_title(name)) %>% 
+  mutate(name = fct_inorder(name)) %>% 
+  ggplot(aes(x = year, y = value)) +
+  # coord_cartesian(ylim = c(0, 1.00)) +
+  scale_y_continuous(
+    "Users or subscriptions",
+    # breaks = c(0, .25, .5, .75, 1),
+    labels = percent,
+    expand = expansion(c(0.025, 0.05))
+  ) +
+  scale_x_date(
+    breaks = breaks_width("5 years"),
+    labels = label_date("'%y")
+  ) +
+  # Ensure all axes go up to 100%
+  geom_blank(
+    data = tibble(
+      region = "Africa", 
+      country = NA, 
+      value = 1, 
+      year = make_date(2001))
+  ) +
+  geom_line(
+    aes(group = country),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line", 
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_grid(name~region, scales = "free_y") +
+  theme(
+    legend.position = "none",
+    panel.spacing = unit(2, "pt")
   )
@@
   "output/Fig-GBD.png", 
+  device = agg_png,
+  height = 2400, width = 3600, res = 300, units = "px"
+)
+```
+
+### Multiple lines
+
+Here we create two plots.
+One to show all main variables' time trends for each region, and country within region.
+Then, show the outcome time trends for top internet trend in each region.
+Maybe put first in main text and second in appendix.
+
+First, variables with one region per panel.
+
+```{r}
+# Add pseudo GWP to figure plot out
+pseudo_gwp <-
+  bind_rows(
+    distinct(gbd, region, year) %>% 
+      crossing(
+        cause = fct_inorder(
+          c(
+            "Negative\nexperiences", 
+            "Positive\nexperiences", 
+            "Life\nsatisfaction"
+          )
+        )
+      )
+  )
+p_vars <- bind_rows(
+  pseudo_gwp,
+  gbd %>% 
+    group_by(region, country, year, cause) %>% 
+    summarise(mean = mean(val/100))
+) %>% 
+  ungroup() %>% 
+  mutate(cause = fct_inorder(cause)) %>% 
+  mutate(year = make_date(year)) %>% 
+  ggplot(aes(year, mean)) +
+  scale_color_brewer(
+    "Variable",
+    palette = "Set1", direction = -1
+  ) +
+  scale_y_continuous(
+    "Rate or scale score",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015)), 
+    date_labels = "'%y", 
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country, cause)), 
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line", 
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_grid(cause~region, scales = "free_y") +
+  theme(
+    legend.position = "none",
+    panel.spacing = unit(2, "pt")
+  )
+p_vars
+ggsave(
+  "output/Fig-vars-timeseries.png", 
+  device = agg_png,
+  height = 2400, width = 3600, res = 300, units = "px"
+)
+```
+
+```{r}
+# Get top 1 internet trend country in each region
+top_trends <- gbd %>% 
+  semi_join(distinct(itu, country)) %>% 
+  group_by(region, country) %>% 
+  summarise(tidy(lm(internet ~ time, data = cur_data_all()))) %>% 
+  filter(term == "time") %>% 
+  group_by(region) %>% 
+  slice_max(order_by = estimate, n = 1)
+pb <- gbd %>% 
+  filter(country %in% top_trends$country) %>%
+  mutate(country = factor(country, levels = top_trends$country)) %>% 
+  mutate(Group = str_glue("{sex} ({age})")) %>% 
+  mutate(year = make_date(year)) %>% 
+  ggplot(aes(year, val/100, col = Group)) +
+  scale_color_brewer(palette = "Paired") +
+  scale_y_continuous(
+    "Rate",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015)), 
+    date_labels = "'%y", 
+    expand = expansion(.02)
+  ) +
+  stat_summary(fun = mean, geom = "line", size = .6) +
+  facet_grid(cause~country, scales = "free_y")
+
+(pa + theme(axis.title.x = element_blank())) / 
+  pb * 
+  theme(panel.spacing = unit(2, "pt")) +
+  plot_layout(heights = c(4, 3)) +
+  plot_annotation(tag_levels = "A")
+ggsave(
+  "output/Fig-all-vars-timeseries.png", 
   device = agg_png,
@@
 
-# Fit models in background (need 12 cores)
-file_path <- "brm-time-main-effects"
-if (!file.exists(file_path)) {
-  job::job({
+# Fit models
 fit_anx <- brm(
@@
 )
-  }, title = "Fitting brms anxiety")
-  job::job({
 fit_dep <- brm(
@@
 )
-  }, title = "Fitting brms depression")
 fit_sel <- brm(
@@
 )
-  write_rds(fits_brm_time_main, file_path)
-} else {fits_brm_time_main <- read_rds(file_path)}
+
+```
+
+Coefficients
+
+```{r}
+fits_brm_time_main %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
+        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  # filter(str_detect(Parameter, "_time$")) %>% 
+  kbl(digits = 3) %>% 
+  kable_minimal(full_width = FALSE)
+```
+
+Revisit figure of temporal trends with coefficients
+
+```{r}
+tmp_pars <- fits_brm_time_main %>% 
+  mutate(
+    out = map2(
+      fit, 
+      outcome,
+      ~hypothesis(
+        .x, 
+        c(str_glue("{.y}_time = 0")),
+        scope = "coef",
+        group = "region"
+      )$hypothesis
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  # Internet trend is estimated in all models keep first
+  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
+  mutate(across(where(is.numeric), ~round(., 3))) %>% 
+  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
+  select(cause = Hypothesis, region = Group, result) %>% 
+  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))
+
+p_vars +
+  geom_richtext(
+    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
+    aes(x = make_date(2000), y = Inf, label = result),
+    size = 2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
+    family = Font,
+    fill = NA, label.color = NA
+  )
+ggsave(
+  "output/Fig-vars-timeseries-estimates.png", 
+  device = agg_png,
+  height = 2400, width = 3600, res = 300, units = "px"
+)
+```
+
+Calculate country coefficients and show scatterplots
+
+```{r time-correlation-anxiety}
+# Get average and region
+r_region_anxiety <- fit_anx %>% 
+  spread_draws(
+    b_Anxiety_time, 
+    b_internet_time,
+    r_region__Anxiety[region, term],
+    r_region__internet[region, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by replacing dot with line break
+  mutate(region = str_replace(region, "\\.", "\n"))
+
+# Then country
+r_country_anxiety <- fit_anx %>% 
+  spread_draws(
+    r_country__Anxiety[country, term],
+    r_country__internet[country, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by taking labels from original names
+  mutate(
+    country = factor(
+      country, 
+      labels = sort(unique(fit_anx$data$country))
+    )
+  ) %>% 
+  left_join(distinct(gbd, region, country))
+
+# Calculate country coefficients
+country_anxiety <- left_join(r_country_anxiety, r_region_anxiety) %>% 
+  mutate(
+    internet = b_internet_time + r_region__internet + r_country__internet,
+    anxiety = b_Anxiety_time + r_region__Anxiety + r_country__Anxiety
+  ) %>% 
+  group_by(country, region) %>% 
+  median_qi(internet, anxiety)
+
+country_anxiety_ellipse <- spread_draws(
+  fit_anx,
+  b_Anxiety_time, b_internet_time,
+  cor_country__internet_time__Anxiety_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_country__internet_time__Anxiety_time, 
+        y = b_internet_time, 
+        z = b_Anxiety_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+region_anxiety_ellipse <- spread_draws(
+  fit_anx,
+  b_Anxiety_time, b_internet_time,
+  cor_region__internet_time__Anxiety_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_region__internet_time__Anxiety_time, 
+        y = b_internet_time, 
+        z = b_Anxiety_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+country_anxiety_cor <- fit_anx %>%
+  as_draws_df(
+    variable = c(
+      "cor_country__internet_time__Anxiety_time",
+      "cor_region__internet_time__Anxiety_time"
+    ),
+    regex = TRUE
+  ) %>% 
+  as_tibble()
+country_anxiety_result <- country_anxiety_cor %>%   
+  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
+
+p_cor_country_anx <- country_anxiety %>% 
+  ggplot(aes(internet, anxiety)) +
+  # geom_path(
+  #   data = region_anxiety_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
+  # ) +
+  # geom_path(
+  #   data = country_anxiety_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
+  # ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_hline(yintercept = 0, lty = 2, size = .2) +
+  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
+  scale_x_continuous(
+    "Linear internet trend",
+    breaks = pretty_breaks()
+  ) +
+  scale_y_continuous(
+    "Linear anxiety trend",
+    breaks = pretty_breaks()
+  ) +
+  geom_richtext(
+    data = country_anxiety_result %>% 
+      filter(variable == "cor_country__internet_time__Anxiety_time"),
+    aes(x = -Inf, y = Inf, label = result),
+    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
+    family = Font,
+    fill = NA, label.color = NA
+  ) +
+  theme(aspect.ratio = 1)
+```
+
+```{r time-correlation-depression}
+# Get average and region
+r_region_depression <- fit_dep %>% 
+  spread_draws(
+    b_Depression_time, 
+    b_internet_time,
+    r_region__Depression[region, term],
+    r_region__internet[region, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by replacing dot with line break
+  mutate(region = str_replace(region, "\\.", "\n"))
+
+# Then country
+r_country_depression <- fit_dep %>% 
+  spread_draws(
+    r_country__Depression[country, term],
+    r_country__internet[country, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by taking labels from original names
+  mutate(
+    country = factor(
+      country, 
+      labels = sort(unique(fit_dep$data$country))
+    )
+  ) %>% 
+  left_join(distinct(gbd, region, country))
+
+# Calculate country coefficients
+country_depression <- left_join(r_country_depression, r_region_depression) %>% 
+  mutate(
+    internet = b_internet_time + r_region__internet + r_country__internet,
+    depression = b_Depression_time + r_region__Depression + r_country__Depression
+  ) %>% 
+  group_by(country, region) %>% 
+  median_qi(internet, depression)
+
+country_depression_ellipse <- spread_draws(
+  fit_dep,
+  b_Depression_time, b_internet_time,
+  cor_country__internet_time__Depression_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_country__internet_time__Depression_time, 
+        y = b_internet_time, 
+        z = b_Depression_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+region_depression_ellipse <- spread_draws(
+  fit_dep,
+  b_Depression_time, b_internet_time,
+  cor_region__internet_time__Depression_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_region__internet_time__Depression_time, 
+        y = b_internet_time, 
+        z = b_Depression_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+country_depression_cor <- fit_dep %>%
+  as_draws_df(
+    variable = c(
+      "cor_country__internet_time__Depression_time",
+      "cor_region__internet_time__Depression_time"
+    ),
+    regex = TRUE
+  ) %>% 
+  as_tibble()
+country_depression_result <- country_depression_cor %>%   
+  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
+
+p_cor_country_dep <- country_depression %>% 
+  ggplot(aes(internet, depression)) +
+  # geom_path(
+  #   data = region_depression_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
+  # ) +
+  # geom_path(
+  #   data = country_depression_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
+  # ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_hline(yintercept = 0, lty = 2, size = .2) +
+  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
+  scale_x_continuous(
+    "Linear internet trend",
+    breaks = pretty_breaks()
+  ) +
+  scale_y_continuous(
+    "Linear depression trend",
+    breaks = pretty_breaks()
+  ) +
+  geom_richtext(
+    data = country_depression_result %>% 
+      filter(variable == "cor_country__internet_time__Depression_time"),
+    aes(x = -Inf, y = Inf, label = result),
+    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
+    family = Font,
+    fill = NA, label.color = NA
+  ) +
+  theme(aspect.ratio = 1)
+```
+
+```{r time-correlation-selfharm}
+# Get average and region
+r_region_selfharm <- fit_sel %>% 
+  spread_draws(
+    b_Selfharm_time, 
+    b_internet_time,
+    r_region__Selfharm[region, term],
+    r_region__internet[region, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by replacing dot with line break
+  mutate(region = str_replace(region, "\\.", "\n"))
+
+# Then country
+r_country_selfharm <- fit_sel %>% 
+  spread_draws(
+    r_country__Selfharm[country, term],
+    r_country__internet[country, term]
+  ) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  # Fix names by taking labels from original names
+  mutate(
+    country = factor(
+      country, 
+      labels = sort(unique(fit_sel$data$country))
+    )
+  ) %>% 
+  left_join(distinct(gbd, region, country))
+
+# Calculate country coefficients
+country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
+  mutate(
+    internet = b_internet_time + r_region__internet + r_country__internet,
+    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
+  ) %>% 
+  group_by(country, region) %>% 
+  median_qi(internet, selfharm)
+
+country_selfharm_ellipse <- spread_draws(
+  fit_sel,
+  b_Selfharm_time, b_internet_time,
+  cor_country__internet_time__Selfharm_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_country__internet_time__Selfharm_time, 
+        y = b_internet_time, 
+        z = b_Selfharm_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+region_selfharm_ellipse <- spread_draws(
+  fit_sel,
+  b_Selfharm_time, b_internet_time,
+  cor_region__internet_time__Selfharm_time, 
+  ndraws = 100
+) %>% 
+  mutate(
+    e = pmap(
+      list(
+        x = cor_region__internet_time__Selfharm_time, 
+        y = b_internet_time, 
+        z = b_Selfharm_time
+      ), 
+      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        as_tibble()
+    )
+  ) %>% 
+  unnest(e)
+
+country_selfharm_cor <- fit_sel %>%
+  as_draws_df(
+    variable = c(
+      "cor_country__internet_time__Selfharm_time",
+      "cor_region__internet_time__Selfharm_time"
+    ),
+    regex = TRUE
+  ) %>% 
+  as_tibble()
+country_selfharm_result <- country_selfharm_cor %>%   
+  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
+
+p_cor_country_sel <- country_selfharm %>% 
+  ggplot(aes(internet, selfharm)) +
+  # geom_path(
+  #   data = region_selfharm_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
+  # ) +
+  # geom_path(
+  #   data = country_selfharm_ellipse, 
+  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
+  # ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_hline(yintercept = 0, lty = 2, size = .2) +
+  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
+  scale_x_continuous(
+    "Linear internet trend",
+    breaks = pretty_breaks()
+  ) +
+  scale_y_continuous(
+    "Linear selfharm trend",
+    breaks = pretty_breaks()
+  ) +
+  geom_richtext(
+    data = country_selfharm_result %>% 
+      filter(variable == "cor_country__internet_time__Selfharm_time"),
+    aes(x = -Inf, y = Inf, label = result),
+    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
+    family = Font,
+    fill = NA, label.color = NA
+  ) +
+  theme(aspect.ratio = 1)
+```
+
+```{r}
+p_cor_country_anx + theme(axis.title.x = element_blank()) | 
+  p_cor_country_dep | 
+  p_cor_country_sel + theme(axis.title.x = element_blank())
 ```
@@
 # Fit models
-file_path <- "brm-time-interactions"
-if (!file.exists(file_path)) {
-  job::job({
 fit_anx <- brm(
@@
 )
-  write_rds(fits_brm_time_interactions, file_path)
-} else {fits_brm_time_interactions <- read_rds(file_path)}
+```
+
+Coefficients
+
+```{r}
+fits_brm_time_interactions %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
+        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  # filter(str_detect(Parameter, "_time$")) %>% 
+  kbl(digits = 2) %>% 
+  kable_minimal(full_width = FALSE)
 ```
@@
 # Fit models in background (need 12 cores)
-job::job({
 fit_anx <- brm(
@@
 )
-}, title = "Fitting brms anxiety")
-job::job({
 fit_dep <- brm(
@@
 )
-}, title = "Fitting brms depression")
 fit_sel <- brm(
@@
 )
+fits_brm_internet_main <- tibble(
+  outcome = c("Anxiety", "Depression", "Selfharm"),
+  fit = list(fit_anx, fit_dep, fit_sel)
+)
+```
+
+Coefficients
+
+```{r}
+fits_brm_internet_main %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
+        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  filter(str_detect(variable, "_i1_cw|b$")) %>% 
+  kbl(digits = 3) %>% 
+  kable_minimal(full_width = FALSE)
+```
+
+Different levels
+
+```{r}
+# Get average and region
+r_selfharm <- fit_sel %>% 
+  spread_draws(
+    b_Selfharm_i1_cw, 
+    r_region__Selfharm[region, term]
+  ) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  # Fix names by replacing dot with line break
+  mutate(region = str_replace(region, "\\.", "\n"))
+
+fit_sel %>% 
+  spread_draws(
+    r_country__Selfharm[country, term]
+    )
+
+# Calculate country coefficients
+r_selfharm <- r_selfharm %>% 
+  mutate(
+    b_average = b_Selfharm_i1_cw,
+    b_region = b_average + r_region__Selfharm,
+    b_country = b_region + r_country__Selfharm
+  )
+
+r_selfharm %>% 
+  distinct(.draw, b_average) %>% 
+  mutate(region = "Average") %>% 
+  ggplot(aes(b_average, region)) +
+  stat_halfeye(size = 1, fill = "dodgerblue4") +
+  stat_halfeye(
+    data = r_selfharm %>% 
+      distinct(.draw, region, b_region),
+    aes(b_region),
+    size = 1, fill = "dodgerblue1"
+  ) +
+  geom_point(
+    data = 
+  )
+r_selfharm %>% 
+  group_by(region, country) %>% 
+  median_qi(b_country)
 ```

### 2021-11-12 index.Rmd
wip

@@
 library(gtsummary)
+library(ellipse)
 library(imputeTS)
@@
 names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
+
+# Transform edge proportions to fit beta distribution
+gbd_10 <- gbd_wide %>% 
+  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999999, internet))
 ```
@@
 ```{r}
-# Transform edge proportions to fit beta distribution
-gbd_10 <- gbd_wide %>% 
-  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999999, internet))
-
 # Define a model of internet proportion over time
@@
 
+A figure of coefficients
+
+```{r}
+anx_draws <- spread_draws(
+  fit_anx, 
+  b_Anxiety_time, r_region__Anxiety[region, term] | region
+) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_Anxiety_time) %>% 
+  mutate(outcome = "Anxiety")
+dep_draws <- spread_draws(
+  fit_dep, 
+  b_Depression_time, r_region__Depression[region, term] | region
+) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_Depression_time) %>% 
+  mutate(outcome = "Depression")
+sel_draws <- spread_draws(
+  fit_sel, 
+  b_Selfharm_time, r_region__Selfharm[region, term] | region
+) %>% 
+  filter(term == "time") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_Selfharm_time) %>% 
+  mutate(outcome = "Selfharm")
+
+p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
+  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
+  mutate(region = fct_relevel(factor(region), "Average")) %>% 
+  mutate(outcome = factor(outcome)) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
+  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
+  scale_alpha_manual(values = c(.5, .9)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels"
+  ) +
+  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown(),
+    legend.position = "none"
+  )
+p_time_main_coefs
+```
+
+###### Correlations
+
 Calculate country coefficients and show scatterplots
@@
 ```{r time-correlation-anxiety}
-# Get average and region
-r_region_anxiety <- fit_anx %>% 
+# Function to wrangle draws at multiple levels and create scatterplots + ellipses
+draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
+  # Get average and region-specific slopes
+  r_region_draws <- fit %>% 
     spread_draws(
-    b_Anxiety_time, 
+      {{beta}}, 
       b_internet_time,
-    r_region__Anxiety[region, term],
+      {{r_region}}[region, term],
       r_region__internet[region, term]
@@
   # Then country
-r_country_anxiety <- fit_anx %>% 
+  r_country_draws <- fit %>% 
     spread_draws(
-    r_country__Anxiety[country, term],
+      {{r_country}}[country, term],
       r_country__internet[country, term]
@@
         country, 
-      labels = sort(unique(fit_anx$data$country))
+        labels = sort(unique(fit$data$country))
       )
@@
   # Calculate country coefficients
-country_anxiety <- left_join(r_country_anxiety, r_region_anxiety) %>% 
+  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
     mutate(
       internet = b_internet_time + r_region__internet + r_country__internet,
-    anxiety = b_Anxiety_time + r_region__Anxiety + r_country__Anxiety
+      outcome = {{beta}} + {{r_region}} + {{r_country}}
     ) %>% 
     group_by(country, region) %>% 
-  median_qi(internet, anxiety)
-
-country_anxiety_ellipse <- spread_draws(
-  fit_anx,
-  b_Anxiety_time, b_internet_time,
-  cor_country__internet_time__Anxiety_time, 
+    median_qi(internet, outcome)
+
+  # Create country ellipse data
+  country_ellipse <- spread_draws(
+    fit,
+    {{beta}}, 
+    b_internet_time,
+    {{sd_country}},
+    sd_country__internet_time,
+    {{cor_country}}, 
     ndraws = 100
   ) %>% 
+    rename(
+      cor = {{cor_country}}, 
+      sd_outcome = {{sd_country}},
+      sd_i = sd_country__internet_time,
+      b_outcome = {{beta}},
+      b_i = b_internet_time
+    ) %>% 
     mutate(
       e = pmap(
-      list(
-        x = cor_country__internet_time__Anxiety_time, 
-        y = b_internet_time, 
-        z = b_Anxiety_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
+        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
+        function(cor, sd_a, sd_i, b_a, b_i) 
+          ellipse(
+            cor, 
+            scale = c(sd_i, sd_outcome), 
+            centre = c(b_i, b_outcome), 
+            level = .90
+          ) %>% 
           as_tibble()
@@
 
-region_anxiety_ellipse <- spread_draws(
-  fit_anx,
-  b_Anxiety_time, b_internet_time,
-  cor_region__internet_time__Anxiety_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Anxiety_time, 
-        y = b_internet_time, 
-        z = b_Anxiety_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_anxiety_cor <- fit_anx %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Anxiety_time",
-      "cor_region__internet_time__Anxiety_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_anxiety_result <- country_anxiety_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
+  # Correlation
+  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
+    median_qi(.width = .90) %>% 
     mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_anx <- country_anxiety %>% 
-  ggplot(aes(internet, anxiety)) +
-  # geom_path(
-  #   data = region_anxiety_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_anxiety_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
+    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}
+
+  # Plot
+  country_coefs %>% 
+    ggplot(aes(internet, outcome)) +
+    geom_path(
+      data = country_ellipse,
+      aes(x = x, y = y), 
+      alpha = .2, size = .1, col = "dodgerblue1"
+    ) +
     geom_vline(xintercept = 0, lty = 2, size = .2) +
     geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
+    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
     scale_x_continuous(
-    "Linear internet trend",
+      "Internet trend",
       breaks = pretty_breaks()
@@
     scale_y_continuous(
-    "Linear anxiety trend",
       breaks = pretty_breaks()
     ) +
-  geom_richtext(
-    data = country_anxiety_result %>% 
-      filter(variable == "cor_country__internet_time__Anxiety_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
+    annotate(
+      "text",
+      x = Inf, y = Inf, label = country_cor_result,
+      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
+      family = Font
+    )
+}
+```
+
+```{r}
+p_cor_country_anx <- draw_scatterplot(
+  fit_anx, 
+  b_Anxiety_time, 
+  r_region__Anxiety, 
+  r_country__Anxiety,
+  sd_country__Anxiety_time,
+  cor_country__internet_time__Anxiety_time
+) + labs(y = "Anxiety trend")
+p_cor_country_dep <- draw_scatterplot(
+  fit_dep, 
+  b_Depression_time, 
+  r_region__Depression, 
+  r_country__Depression,
+  sd_country__Depression_time,
+  cor_country__internet_time__Depression_time
+) + labs(y = "Depression trend")
+p_cor_country_sel <- draw_scatterplot(
+  fit_sel, 
+  b_Selfharm_time, 
+  r_region__Selfharm, 
+  r_country__Selfharm,
+  sd_country__Selfharm_time,
+  cor_country__internet_time__Selfharm_time
+) + labs(y = "Self-harm trend")
+```
+
+```{r}
+p_time_main_correlations <- p_cor_country_anx |
+  p_cor_country_dep |
+  p_cor_country_sel
+
+(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
+  p_time_main_correlations
+
+p_time_main_coefs /
+  p_time_main_correlations
 ```
@@
 # Fit models in background (need 12 cores)
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
+job::job({fit_anx <- brm(
+  bf_anx,
   data = gbd_10,
@@
   cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
+  iter = 1200, warmup = 600, refresh = 10,
   threads = 1,
   control = list(adapt_delta = .9)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
+)})
+job::job({fit_dep <- brm(
+  bf_dep,
   data = gbd_10,
@@
   cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
+  iter = 1200, warmup = 600, refresh = 10,
   threads = 1,
   control = list(adapt_delta = .9)
-)
+)})
 fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
+  bf_sel,
   data = gbd_10,
@@
 
-Different levels
-
-```{r}
-# Get average and region
-r_selfharm <- fit_sel %>% 
-  spread_draws(
-    b_Selfharm_i1_cw, 
-    r_region__Selfharm[region, term]
+###### Fitted lines
+
+Plot of fitted lines
+
+```{r}
+draws_country_anx <- epred_draws(
+  fit_anx, 
+  gbd_wide %>% 
+    filter(country %in% sort(unique(fit_anx$data$country))) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
+    (1 + time + sex + age + i1_cw |c| country), 
+  ndraws = 100,
+  resp = "Anxiety"
+)
+
+draws_country_dep <- epred_draws(
+  fit_dep, 
+  gbd_wide %>% 
+    filter(country %in% sort(unique(fit_dep$data$country))) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
+    (1 + time + sex + age + i1_cw |c| country), 
+  ndraws = 30,
+  resp = "Depression"
+)
+
+draws_country_sel <- epred_draws(
+  fit_sel, 
+  gbd_wide %>% 
+    filter(country %in% sort(unique(fit_sel$data$country))) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
+    (1 + time + sex + age + i1_cw |c| country), 
+  ndraws = 30,
+  resp = "Selfharm"
+)
+
+draws_region_anx <- epred_draws(
+  fit_anx, 
+  distinct(fit_anx$data, region, sex, age, i1_cb) %>% 
+    group_by(region) %>% 
+    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
+    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
+  ndraws = 30,
+  resp = "Anxiety"
+) %>% 
+  mutate(outcome = "Anxiety")
+
+draws_region_dep <- epred_draws(
+  fit_dep, 
+  distinct(fit_dep$data, region, sex, age, i1_cb) %>%
+    group_by(region) %>% 
+    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
+    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
+  ndraws = 30,
+  resp = "Depression"
+) %>% 
+  mutate(outcome = "Depression")
+
+draws_region_sel <- epred_draws(
+  fit_sel, 
+  distinct(fit_sel$data, region, sex, age, i1_cb) %>% 
+    group_by(region) %>% 
+    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
+    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
+    mutate(time = 0),
+  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
+  ndraws = 30,
+  resp = "Selfharm"
+) %>% 
+  mutate(outcome = "Self-harm")
+
+draws_region <- bind_rows(
+  draws_region_anx, draws_region_dep, draws_region_sel
+) %>% 
+  group_by(outcome, region, i1_cw) %>% 
+  median_qi(.epred)
+
+bind_rows(
+  draws_country_anx %>% mutate(outcome = "Anxiety"),
+  draws_country_dep %>% mutate(outcome = "Depression"),
+  draws_country_sel %>% mutate(outcome = "Self-harm")
+) %>% 
+  group_by(country) %>% 
+  # mutate(i1_cw2 = i1_cw/10 + mean(internet, na.rm = T)) %>% 
+  ungroup() %>% 
+  ggplot(aes(i1_cw, .epred)) +
+  scale_x_continuous(
+    "Previous year's internet adoption relative to country average in 2000-2020",
+    breaks = pretty_breaks(3),
+    labels = function(x) percent(x/10, 1)
+  ) +
+  scale_y_continuous(
+    "Estimated rate",
+    breaks = pretty_breaks()
+  ) +
+  geom_ribbon(
+    data = draws_region,
+    aes(ymin = .lower, ymax = .upper),
+    fill = "dodgerblue4", size = .6, alpha = .2
+  ) +
+  geom_line(
+    data = draws_region,
+    col = "dodgerblue4", size = .6
+  ) +
+  stat_summary(
+    fun=mean, geom = "line",
+    aes(group = country), 
+    size = .4, alpha = .25, col = "dodgerblue1"
+  ) +
+  facet_grid(outcome~region, scales = "free_y") +
+  theme(panel.spacing = unit(2, "pt"))
+```
+
+###### Forest plots
+
+figure of coefficients forest plot
+
+```{r}
+anx_draws <- spread_draws(
+  fit_anx, 
+  b_Anxiety_i1_cw, r_region__Anxiety[region, term] | region
 ) %>% 
@@
   ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-fit_sel %>% 
-  spread_draws(
-    r_country__Selfharm[country, term]
-    )
-
-# Calculate country coefficients
-r_selfharm <- r_selfharm %>% 
-  mutate(
-    b_average = b_Selfharm_i1_cw,
-    b_region = b_average + r_region__Selfharm,
-    b_country = b_region + r_country__Selfharm
-  )
-
-r_selfharm %>% 
-  distinct(.draw, b_average) %>% 
-  mutate(region = "Average") %>% 
-  ggplot(aes(b_average, region)) +
-  stat_halfeye(size = 1, fill = "dodgerblue4") +
+  select(-term) %>% 
+  rename(Average = b_Anxiety_i1_cw) %>% 
+  mutate(outcome = "Anxiety")
+dep_draws <- spread_draws(
+  fit_dep, 
+  b_Depression_i1_cw, r_region__Depression[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_Depression_i1_cw) %>% 
+  mutate(outcome = "Depression")
+sel_draws <- spread_draws(
+  fit_sel, 
+  b_Selfharm_i1_cw, r_region__Selfharm[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_Selfharm_i1_cw) %>% 
+  mutate(outcome = "Selfharm")
+
+results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  group_by(outcome) %>% 
+  summarise(parameters(cur_data()[-c(1:3)])) %>% 
+  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))
+
+p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
+  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
+  mutate(region = fct_relevel(factor(region), "Average")) %>% 
+  mutate(outcome = factor(outcome)) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
+  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
+  scale_alpha_manual(values = c(.5, .9)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_y_discrete(expand = expansion(c(0.01, .1))) +
+  scale_x_continuous(
+    "Estimated association to internet adoption", 
+    breaks = pretty_breaks(), 
+    expand = expansion(c(.1, .5))
+  ) +
   stat_halfeye(
-    data = r_selfharm %>% 
-      distinct(.draw, region, b_region),
-    aes(b_region),
-    size = 1, fill = "dodgerblue1"
-  ) +
-  geom_point(
-    data = 
-  )
-r_selfharm %>% 
-  group_by(region, country) %>% 
-  median_qi(b_country)
+    point_interval = NULL, normalize = "panels", height = .75
+  ) +
+  geom_text(
+    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
+    aes(
+      x = Inf, 
+      label = str_glue("{Median} [{CI_low}, {CI_high}]")
+    )
+  ) +
+  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown(),
+    legend.position = "none"
+  )
+
+(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
+  p_internet_main_coefs
 ```
@@
 
-# Fit models in background (need 12 cores)
-job::job({
+# Fit models
 fit_anx <- brm(
@@
 )
-```
-
-###### Plot: Average effects of time
-
-```{r eval = FALSE}
-fixef(fit_gbd_time) %>%
-  as.data.frame() %>% 
-  rownames_to_column("Parameter") %>% 
-  as_tibble()
-
-h <- paste(
-  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
-  "= 0"
-)
-
-# Prepare average samples
-time_avg <- hypothesis(fit_gbd_time, h)
-time_avg_samples <- time_avg$samples
-names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
-time_avg_samples <- time_avg_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  mutate(region = "Average")
-
-# Prepare region samples
-time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
-time_region_samples <- time_region$samples
-names(time_region_samples) <- paste(
-  time_region$hypothesis$Hypothesis, 
-  time_region$hypothesis$Group, sep = ":"
-)
-time_region_samples <- time_region_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  separate(Parameter, c("Parameter", "region"), sep = ":")
-
-# Prepare country point estimates
-time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
-time_country_hypothesis <- time_country$hypothesis %>% 
-  rename(country = Group, Parameter = Hypothesis)
-time_country_hypothesis <- left_join(
-  time_country_hypothesis, 
-  distinct(fit_gbd_time$data, country, region)
-)
-
-time_sum <- bind_rows(
-  time_region$hypothesis,
-  time_avg$hypothesis %>% mutate(Group = "Average")
-) %>% 
-  as_tibble() %>% 
-  rename(region = Group, Parameter = Hypothesis)
-
-bind_rows(
-  time_region_samples,
-  time_avg_samples
-) %>% 
-  mutate(region = fct_relevel(region, "Average")) %>% 
-  mutate(Average = region == "Average") %>% 
-  ggplot(aes(value/10, region)) +
-  scale_y_discrete(
-    expand = expansion(c(0.025, 0.075)),
-    labels = function(x) ifelse(x == "Average", "**Average**", x)
-  ) +
-  scale_x_continuous(
-    "Estimated yearly change",
-    breaks = pretty_breaks(5)
-  ) +
-  scale_alpha_manual(values = c(.5, 1)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .25) +
-  stat_eye(
-    side = "top",
-    aes(col = region, fill = region, alpha = Average),
-    point_interval = NULL,
-    normalize = "panels", 
-    height = .75
-  ) +
-  geom_pointrangeh(
-    data = time_sum,
-    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
-    size = .3, fatten = 1.4
-  ) +
-  geom_point(
-    data = time_country_hypothesis,
-    aes(col = region, x = Estimate/10), 
-    size = .5,
-    alpha = .25,
-    position = position_nudge(y = -.05)
-  ) +
-  facet_wrap(
-    "Parameter", ncol = 3, scales = "free_x",
-    labeller = as_labeller(
-      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
-  ) +
-  theme(
-    axis.text.y = element_markdown(),
-    legend.position = "none",
-    axis.title.y = element_blank()
-  )
-ggsave(
-  "output/Fig-brm-time-forest.png", 
-  device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
-)
-```
-
-## Model 2: Associations
-
-This model expands the above to add internet adoption as a predictor.
-
-### GBD
-
-#### Figure
-
-```{r}
-gbd %>% 
-  ggplot(
-    aes(
-      x = i1_cw/10, 
-      y = val, 
-      col = region, fill = region
-    )
-  ) +
-  geom_point(size = .25, alpha = .1) +
-  stat_smooth(method = "lm", alpha = .2, size = .3) +
-  # stat_summary(fun = mean, geom = "line", size = .25) +
-  facet_grid(Cause~region, scales = "free_y") +
-  theme(legend.position = "none")
-```
-
-#### lme4
-
-```{r fit-gbd-internet-lme4}
-# These take about 1-3 hours each
-# run in parallel in background jobs
-# recommended to conduct this in interactive mode (rstudio)
-file_path <- "output/lme4-gbd-internet.rds"
-if (!file.exists(file_path)) {
-  library(job)
-  job({fit_anx <- lmer(
-    Anxiety ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Anxiety internet (lmer)")
-  job({fit_dep <- lmer(
-    Depression ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Depression internet (lmer)")
-  job({fit_sel <- lmer(
-    Selfharm ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Self harm internet (lmer)")
-  fits_lmer <- distinct(gbd, cause) %>% 
-    mutate(fit = list(fit_anx, fit_dep, fit_sel))
-  write_rds(fits_lmer, file_path)
-} else {fits_lmer <- read_rds(file_path)}
-```
-
-```{r}
-fits_lmer %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
+fits_brm_internet_interactions <- tibble(
+  outcome = c("Anxiety", "Depression", "Selfharm"),
+  fit = list(fit_anx, fit_dep, fit_sel)
+)
+```
+
+Coefficients
+
+```{r}
+fits_brm_internet_interactions %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
+        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
+    )
+  ) %>% 
   select(-fit) %>% 
   unnest(out) %>% 
-  filter(term == "i1_cw")
-```
-
-#### brms
-
-```{r fit-gbd-internet-brms, eval = FALSE}
-# bf_gbd_internet <- bf(
-#   mvbind(
-#     val_Depression,
-#     val_Anxiety,
-#     val_Self_harm
-#   ) ~ 1 + Time + i1_cw + i1_cb +
-#     (1 + Time + i1_cw || region)
-#   (1 + Time + i1_cw || country)
+  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
+  kbl(digits = 3) %>% 
+  kable_minimal(full_width = FALSE)
+```
+
+Model comparisons
+
+```{r}
+tmp <- left_join(
+  fits_brm_internet_main,
+  fits_brm_internet_interactions %>% rename(fit_i = fit)
+) %>% 
+  mutate(comp = map2(fit, fit_i, waic))
+
+```
+
+###### Forest plots
+
+figure of coefficients forest plot
+
+```{r}
+anx_draws <- spread_draws(
+  fit_anx, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Anxiety")
+dep_draws <- spread_draws(
+  fit_dep, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Depression")
+sel_draws <- spread_draws(
+  fit_sel, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Selfharm")
+
+results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  group_by(outcome) %>% 
+  summarise(parameters(cur_data()[-c(1:3)])) %>% 
+  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))
+
+p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
+  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
+  mutate(region = fct_relevel(factor(region), "Average")) %>% 
+  mutate(outcome = factor(outcome)) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
+  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
+  scale_alpha_manual(values = c(.4, .8)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_y_discrete(expand = expansion(c(0.01, .1))) +
+  scale_x_continuous(
+    "Magnitude of association between internet adoption and well-being", 
+    breaks = pretty_breaks(), 
+    expand = expansion(c(.1, .5))
+  ) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels", 
+    height = .75, adjust = 1.5
+  ) +
+  stat_pointinterval(
+    alpha = 1, .width = c(.9),
+    interval_size = .5,
+    point_size = 1.5,
+    fill = "white",
+    aes(shape = after_stat(xmin > 0 | xmax < 0)),
+    position = position_nudge(0, -.025)
+  ) +
+  geom_text(
+    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
+    aes(
+      x = Inf, 
+      label = str_glue("{Median} [{CI_low}, {CI_high}]")
+    )
+  ) +
+  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown(),
+    legend.position = "none"
+  )
+
+(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
+  p_internet_main_coefs
+```
+
+Between country?
+
+```{r}
+pred_data <- gbd_wide %>% 
+  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
+  filter(country %in% sort(unique(fit_anx$data$country)))
+
+tmp <- epred_draws(
+  fit_anx, pred_data, re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
+)
+
+tmp %>% 
+  group_by(region, country, i1_cb) %>% 
+  summarise(mean(.epred))
+
+conditional_effects(fit_anx, "i1_cb")
+
+gbd_wide %>% 
+  group_by(country) %>% 
+  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
+  ggplot(aes(i1_cb, anx)) +
+  geom_point() +
+  stat_smooth()
+
+filter(country %in% sort(unique(fit_anx$data$country))) %>% 
+  mutate(time = 0) %>% 
+  group_by(country) %>% 
+  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
+  filter(i1_cw %in% c(xmin, xmax)) %>% 
+  ungroup()
+```
+
+Sex and Age
+
+```{r}
+# Get some stuff and transform :)
+get_draws <- function(fit) {
+  draws_region <- spread_draws(
+    fit, 
+    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
+    r_region[region, term] | term
+  ) %>% 
+    mutate(
+      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
+      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
+      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
+      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
+      Age = `age1:i1_cw` + `b_age1:i1_cw`,
+      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
+    ) %>% 
+    select(region, `15 to 19`:Sex)
+
+  draws_avg <- spread_draws(
+    fit, 
+    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
+  ) %>% 
+    mutate(
+      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
+      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
+      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
+      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
+      Age = `b_age1:i1_cw`,
+      Sex = `b_sex1:i1_cw`
+    ) %>% 
+    mutate(region = "**Average**") %>% 
+    select(region, `15 to 19`:Sex)
+
+  draws <- bind_rows(
+    "regions" = draws_region,
+    "average" = draws_avg, 
+    .id = "Level"
+  ) %>% 
+    mutate(region = str_replace(region, "\\.", "\n")) %>% 
+    ungroup()
+  draws
+}
+
+draws <- bind_rows(
+  "Anxiety" = get_draws(fit_anx),
+  "Depression" = get_draws(fit_dep),
+  "Selfharm" = get_draws(fit_sel),
+  .id = "outcome"
+)
+
+draws_sum <- draws %>% 
+  select(outcome, region, Age, Sex) %>% 
+  group_by(outcome, region) %>% 
+  summarise(
+    describe_posterior(
+      cur_data(), centrality = "mean", test = "pd"
+    )
+  ) %>% 
+  rename(panel = Parameter) %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+draws %>% 
+  select(outcome, Level, region, `15 to 19`:Male) %>% 
+  pivot_longer(-c(region, Level, outcome), names_to = "Group") %>% 
+  mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
+  mutate(
+    side = if_else(Group %in% c("15 to 19", "Female"), "top", "bottom")
+  ) %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = fct_relevel(region, "**Average**")) %>% 
+  ggplot(aes(value, region, col = Group, fill = Group)) +
+  scale_alpha_manual(values = c(.6, .3)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_shape_manual(
+    values = c(21, 19), guide = "none"
+    ) +
+  scale_y_discrete(expand = expansion(c(0.1, 0.1))) +
+  scale_x_continuous(
+    "Magnitude of association between internet adoption and well-being", 
+    breaks = pretty_breaks(), 
+    expand = expansion(c(0, .05))
+  ) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels", 
+    height = .75, adjust = 1.5,
+    aes(side = side, group = side, alpha = Level), 
+    show.legend = FALSE
+  ) +
+  stat_pointinterval(
+    alpha = 1, .width = c(.9),
+    interval_size = .33,
+    point_size = 1.25,
+    fill = "white",
+    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
+    position = position_dodgev(.25), key_glyph = draw_key_point
+  ) +
+  geom_richtext(
+    data = draws_sum %>% 
+      mutate(Group = NA) %>% 
+      filter(outcome %in% c("Anxiety", "Depression", "Selfharm")),
+    aes(
+      x = Inf, 
+      label = str_glue("*d* = {Mean} (p<sup>d</sup> = {percent(pd, 1)})")
+    ),
+    size = 2.5, hjust = 1,
+    family = Font,
+    fill = NA, label.color = NA,
+    show.legend = FALSE
+  ) +
+  facet_grid2(panel ~ outcome, scales = "free_x", axes = "x") +
+  guides(
+    alpha = "none"
+  ) +
+  theme(
+    legend.position = "right",
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown()
+  )
+```
+
+###### Fitted lines
+
+Plot of fitted lines
+
+```{r}
+# Prediction dataframe: Min and max vals are enough for line
+pred_data <- gbd_wide %>% 
+  filter(country %in% sort(unique(fit_anx$data$country))) %>% 
+  mutate(time = 0) %>% 
+  group_by(country) %>% 
+  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
+  filter(i1_cw %in% c(xmin, xmax)) %>% 
+  ungroup()
+draws_country_anx <- epred_draws(
+  fit_anx, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Anxiety"
+)
+
+draws_country_dep <- epred_draws(
+  fit_dep, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Depression"
+)
+
+draws_country_sel <- epred_draws(
+  fit_sel, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Selfharm"
+)
+
+pred_data_region <- pred_data %>% 
+  distinct(region, sex, age, i1_cb) %>% 
+  group_by(region) %>% 
+  mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
+  crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
+  mutate(time = 0)
+
+draws_region_anx <- epred_draws(
+  fit_anx, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Anxiety"
+) %>% 
+  mutate(outcome = "Anxiety")
+
+draws_region_dep <- epred_draws(
+  fit_dep, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Depression"
+) %>% 
+  mutate(outcome = "Depression")
+
+draws_region_sel <- epred_draws(
+  fit_sel, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Selfharm"
+) %>% 
+  mutate(outcome = "Self-harm")
+
+means_country <- bind_rows(
+  draws_country_anx %>% mutate(outcome = "Anxiety"),
+  draws_country_dep %>% mutate(outcome = "Depression"),
+  draws_country_sel %>% mutate(outcome = "Self-harm")
+) %>% 
+  group_by(outcome, region, country, i1_cw) %>% 
+  summarise(.epred = mean(.epred))
+
+means_region <- bind_rows(
+  draws_region_anx, draws_region_dep, draws_region_sel
+) %>% 
+  group_by(outcome, region, i1_cw) %>% 
+  mean_qi(.epred, .width = .9)
+
+means_region <- pseudo_gwp %>% 
+  distinct(region, outcome=cause) %>% 
+  bind_rows(means_region) %>% 
+  mutate(outcome = fct_inorder(factor(outcome)))
+
+pseudo_gwp %>% 
+  distinct(region, outcome=cause) %>% 
+  bind_rows(means_country) %>% 
+  mutate(outcome = fct_inorder(factor(outcome))) %>% 
+  ggplot(aes(i1_cw, .epred)) +
+  scale_x_continuous(
+    "Previous year's internet adoption relative to country average in 2000-2020",
+    breaks = c(-3.5, 0, 3.5),
+    labels = function(x) percent(x/10, 1)
+  ) +
+  scale_y_continuous(
+    "Estimated rate or scale score",
+    breaks = pretty_breaks()
+  ) +
+  geom_blank() +
+  geom_ribbon(
+    data = means_region,
+    aes(ymin = .lower, ymax = .upper),
+    alpha = .15, fill = "dodgerblue4"
+  ) +
+  geom_line(
+    data = means_region,
+    col = "dodgerblue4", size = .6
+  ) +
+  geom_line(
+    aes(group = country), 
+    size = .4, alpha = .35, col = "dodgerblue1"
+  ) +
+  # geom_text(
+  #   data = bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  #     group_by(outcome) %>% 
+  #     summarise(parameters(cur_data()[-c(1:3)])) %>% 
+  #     mutate(region = str_replace(Parameter, "\\.", "\n")) %>% 
+  #     mutate(outcome = if_else(outcome=="Selfharm", "Self-harm", outcome)) %>% 
+  #     filter(region != "Average") %>% 
+  #     mutate(across(where(is.numeric), ~round(., 2))),
+  #   aes(x = -Inf, y = Inf, label = str_glue("{Median}\n[{CI_low}, {CI_high}]")),
+  #   col = "dodgerblue4", size = 2, vjust = 1.1, hjust = -0.1, family = Font
   # ) +
-#   set_rescor(FALSE)
-# 
-# fit_gbd_internet <- brm(
-#   bf_gbd_internet,
-#   gbd_y_w,
-#   file = "output/brm-gbd-internet-mv",
-#   chains = 5,
-#   cores = 5,
-#   iter = 300, warmup = 150, refresh = 10,
-#   threads = 2,
-#   control = list(adapt_delta = .9, max_treedepth = 15)
-# )
-
-bf_gbd_internet_demos <- bf(
-  mvbind(
-    Depression,
-    Anxiety,
-    Selfharm
-  ) ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-    (1 + time * sex * age + i1_cw * sex * age | country)
-) +
-  set_rescor(FALSE)
-
-p <- prior(normal(0, 3), class = b, resp = Anxiety) +
-  prior(normal(0, 3), class = b, resp = Depression) +
-  prior(normal(0, 3), class = b, resp = Selfharm) +
-  prior(student_t(7, 0, 1), class = sd, resp = Anxiety) +
-  prior(student_t(7, 0, 1), class = sd, resp = Depression) +
-  prior(student_t(7, 0, 1), class = sd, resp = Selfharm)
-
-job::job({fit_gbd_internet_demos <- brm(
-  bf_gbd_internet_demos,
-  gbd_wide,
-  prior = p,
-  file = "output/brm-gbd-internet-mv-demos",
-  chains = 5,
-  cores = 5,
-  iter = 450, warmup = 300, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9, max_treedepth = 15)
-)}, title = "brms internet")
-```
+facet_grid(outcome~region, scales = "free_y") +
+  theme(panel.spacing = unit(2, "pt"))
+```

### 2021-11-15 index.Rmd
use common opts

@@
 library(haven)
-library(janitor)
 library(broom)
@@
 options(brms.backend = "cmdstanr")
+hmc <- list(iter = 2250, warmup = 1000, refresh = 50, d = .9)
 # Run this to delete fitted models and refit
@@
 
-bf_time_mv <- bf(
-  mvbind(Depression, Anxiety, Selfharm) ~ 
-    1 + time +
-    (1 + time |c| country) +
-    (1 + time | region),
-  family = gaussian()
-) +
-  bf_int +
-  set_rescor(FALSE)
-
 # Fit models
@@
   cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
+  iter = hmc$iter, warmup = hmc$warmup, 
+  refresh = hmc$refresh,
+  control = list(adapt_delta = hmc$d)
 )
@@
 )
-
 ```
@@
 
-Revisit figure of temporal trends with coefficients
+Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000
 
@@
   unnest(out) %>% 
-  # Internet trend is estimated in all models keep first
+  # Internet trend is estimated in all models--keep first
   distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
-  mutate(across(where(is.numeric), ~round(., 3))) %>% 
-  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
+  # Transform back to rates in 100k
+  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
+  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
   select(cause = Hypothesis, region = Group, result) %>% 
@@
     aes(x = make_date(2000), y = Inf, label = result),
-    size = 2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
+    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
     family = Font,
@@
 ```{r}
-p_time_main_correlations <- p_cor_country_anx |
+p_time_main_correlations <- (p_cor_country_anx |
   p_cor_country_dep |
-  p_cor_country_sel
+  p_cor_country_sel) &
+  # Transform to rate in 100k
+  scale_y_continuous(labels = function(x) x*1000)
 
@@
 # Fit models in background (need 12 cores)
-job::job({fit_anx <- brm(
+fit_anx <- brm(
   bf_anx,
@@
   cores = 4,
-  iter = 1200, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)})
-job::job({fit_dep <- brm(
+  iter = hmc$iter, warmup = hmc$warmup, 
+  refresh = hmc$refresh,
+  control = list(adapt_delta = hmc$d)
+)
+fit_dep <- brm(
   bf_dep,
@@
   cores = 4,
-  iter = 1200, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)})
+  iter = hmc$iter, warmup = hmc$warmup, 
+  refresh = hmc$refresh,
+  control = list(adapt_delta = hmc$d)
+)
 fit_sel <- brm(
@@
   cores = 4,
-  iter = 1200, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
+  iter = hmc$iter, warmup = hmc$warmup, 
+  refresh = hmc$refresh,
+  control = list(adapt_delta = hmc$d)
 )

### 2021-11-15 index.Rmd
customise bookdown output

--- 2021-11-10 index.Rmd
@@
 ---
-title: "Online analysis supplement"
+title: "Global study of well-being and internet adoption | Online analysis supplement"
 description: |
-  A global study of adolescents’ digital technology adoption and its associations with well-being and mental health
-author:
-  - name: Matti Vuorre
-    url: https://vuorre.netlify.app
-    affiliation: Oxford Internet Institute
-    affiliation_url: https://www.oii.ox.ac.uk/people/matti-vuorre/
+  Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
+author: "<a href='https://vuorre.netlify.app'>Matti Vuorre</a> & Andy Przybylski"
 date: "`r Sys.Date()`"
-output:
-  distill::distill_article:
-    toc: true
-    toc_depth: 3
-    toc_float: true
-    fig_width: 8
-    fig_height: 6
-    fig_retina: 2
-    dev: "ragg_png"
-    code_folding: true
-editor_options: 
-  chunk_output_type: console
+site: bookdown::bookdown_site
+output: bookdown::bs4_book
+url: https://digital-wellbeing.github.io/global-wbmh
+biblio-style: apalike
 ---
 
-## Preface
+This repository ([GitHub](https://github.com/digital-wellbeing/global-wbmh) / [OSF](https://osf.io/ys7m9/)) contains the code and synthetic datasets required to reproduce all analyses reported in our manuscript, *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, in preparation).
+These analyses are presented in the [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh).
 
-This document details the analyses supporting *A global study of adolescents’ digital technology adoption and its associations with well-being and mental health* (Vuorre & Prybylski, in preparation).
+## Materials
 
-It is written in R Markdown and therefore contains all the code required for reproducing our computations.
-However some parts of the code were parallelised to work best with our local setup, so having e.g.
-a different number of cores will significantly impact the run-time of this script.
+- [Preprint]()  
+  - A publicly available version of our manuscript in advance of peer-review and formal publication
+- [GitHub repository](https://github.com/digital-wellbeing/global-wbmh)  
+  - A version controlled repository containing all the raw data and code in this project
+- [OSF repository](https://osf.io/ys7m9/)  
+  - An archived permanent copy of the GitHub repository
+- [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)
+  - The output document of our analyses
 
-Therefore we recommend reproducing the analyses by running them in interactive mode, and changing the parallelisation parameters by hand to best fit your setup.
+## Reproducibility
 
-## Settings
+The code that we used to clean and analyse the data are organised in R Markdown (`.Rmd`) files in this directory, which are meant to be run in the sequence indicated by their numeric prefixes.
+To run all the cleaning and analyses, and compile the resulting document ([the online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)), run `bookdown::render_book()` in R or click "Build Book" in the RStudio IDE.
 
-We first load the required R packages and set some options for the resulting document.
+### Docker
 
-```{r packages-settings}
-#| results: 'hide'
-# Packages
-library(readxl)
-library(ggtext)
-library(janitor)
-library(brms)
-library(gtsummary)
-library(imputeTS)
-library(broom.mixed)
-library(ragg)
-library(scales)
-library(ggh4x)
-library(tidybayes)
-library(naniar)
-library(ggdist)
-library(parameters)
-library(countrycode)
-library(lme4)
-library(emmeans)
-library(plotly)
-library(knitr)
-library(patchwork)
-library(bayestestR)
-library(lubridate)
-library(haven)
-library(janitor)
-library(broom)
-library(kableExtra)
-library(ggbeeswarm)
-library(ggstance)
-library(sysfonts)
-library(tidyverse)
+To ensure the reproducibility of our analyses, you can use Docker:
 
-# Knitr options
-opts_chunk$set(
-  echo = TRUE,
-  warning = FALSE,
-  cache = TRUE,
-  error = FALSE,
-  message = FALSE,
-  fig.align = "center",
-  fig.retina = 2
-)
-
-# Plotting theme
-Font <- "Titillium Web"
-if (!(Font %in% font_families())) font_add_google(Font, Font)
-theme_set(
-  theme_linedraw(
-    base_size = 12, 
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-# MCMC settings
-options(brms.backend = "cmdstanr")
-# Run this to delete fitted models and refit
-# unlink(list.files(pattern = "output/brm-.*\\.rds"))
-
-# Create directory for intermediate files
-dir.create("output", FALSE)
+Build the Docker image
+```
+docker build \
+    --build-arg R_VERSION=4.1.1 \
+    --build-arg RENV_VERSION=0.14.0 \
+    -t global-wbmh .
 ```
 
-## Data cleaning
-
-We downloaded the relevant data from sources to `data-raw/`. We cannot share the data here but indicate below how and when each data table was obtained.
-
-### Global Burden of Disease
-
-The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`.
-We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript.
-Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.
-
-```{r gbd-data-load}
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/gbd-2021-11-02/", 
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>% 
-  read_csv()
+Run the container and render output
 ```
-
-We then ensure that the correct variables were downloaded, and then clean this data.
-
-```{r gbd-data-clean}
-# Cleaning
-
-# First step is to clean names in all data sets
-gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
-# - prevalence: Total number of cases
-# - rate: Total cases per 100,000 population
-#   - We convert this to a percentage
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
-gbd <- gbd %>% 
-  mutate(across(c(val, upper, lower), ~.x/1000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>% 
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>% 
-  rename(country = location)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
-gbd <- gbd %>% 
-  mutate(se = (upper-lower) / (1.96*2)) %>%
-  select(-c(upper, lower))
+docker run \
+    --rm \
+    -v "$(pwd):/home/" \
+    -v "/home/renv/library" \
+    -e MAX_CORES=1 \
+    global-wbmh \
+    R -e 'renv::restore(prompt = FALSE); rmarkdown::render("index.Rmd")'
 ```
-
-Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric.
-We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
-There is a harmonised name for each GBD country, and 27 country names are harmonised.
-
-```{r gbd-harmonise-countries}
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>% 
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>% 
-  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
-  kbl() %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  scroll_box(width = "500px", height = "400px")
-# Harmonise old names after verifying above that none are dropped
-gbd <- gbd %>% 
-  mutate(country = countryname(country, destination = "cldr.short.en"))
-```
-
-### Gallup World Poll
-
-GWP cleaning goes here.
-
-### International Telecommunication Union
-
-The internet adoption data were downloaded from the ITU website in October 2021, and placed with their original file names to `data-raw/ITU/`. The specific URLs for obtaining the data files are
-
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>
-
-We first load, reshape, and merge these datasets.
-
-```{r itu-load-clean}
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
-  sheet = 2,
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("year", "variable")) %>% 
-  pivot_wider(names_from = variable) %>% 
-  mutate(fixed = as.numeric(value)) %>% 
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
-  sheet = 2,
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("year", "variable")) %>% 
-  pivot_wider(names_from = variable) %>% 
-  mutate(mobile = as.numeric(value)) %>% 
-  select(country = Country, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>% 
-  pivot_longer(-c(Indicator, Country)) %>% 
-  separate(name, into = c("year", "variable")) %>% 
-  pivot_wider(names_from = variable) %>% 
-  mutate(internet = as.numeric(value)) %>% 
-  select(country = Country, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
-itu <- itu %>% 
-  mutate(across(c(internet, fixed, mobile), function(x) x/100)) %>% 
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-```
-
-Then harmonise country names as above, and drop countries that don't exist in outcomes.
-
-```{r itu-harmonise-countries}
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>% 
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>% 
-  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
-  kbl() %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  scroll_box(width = "500px", height = "400px")
-
-# Harmonise old names after verifying above that none are dropped
-itu <- itu %>% 
-  mutate(country = countryname(country, destination = "cldr.short.en"))
-
-# These countries don't exist in outcomes
-itu %>%
-  distinct(country) %>% 
-  anti_join(distinct(gbd, country)) %>% 
-  kbl() %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  scroll_box(width = "500px", height = "400px")
-
-# Drop them
-itu <- itu %>% 
-  filter(country %in% unique(gbd$country))
-```
-
-#### Missingness
-
-Remove countries with no observations
-
-```{r}
-itu <- itu %>% 
-  group_by(country) %>% 
-  mutate(nobs = sum(!is.na(internet))) %>% 
-  ungroup() %>% 
-  filter(nobs > 0) %>% 
-  select(-nobs)
-```
-
-There are some missing values in the data; in the Internet variable these are mainly in the first or last years of each country's time-series.
-This needs to be changed to calculate by-variable (with appropriate time-spans) when adding mobile and fixed
-
-```{r}
-miss_var_summary(itu)
-```
-
-We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values.
-
-```{r itu-impute}
-itu <- itu %>% 
-  group_by(country) %>% 
-  # Find first and last year with internet data in each country
-  mutate(
-    min_year = year[min(which(!is.na(internet)))],
-    max_year = year[max(which(!is.na(internet)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  # Add variables to c() to impute for fixed and mobile broadband
-  mutate(
-    across(
-      c(internet), 
-      possibly(
-        function(x) na_interpolation(x, maxgap = Inf), 
-        # If function errors, provide original internet value
-        otherwise = internet
-      )
-    )
-  ) %>% 
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    internet = if_else(
-      between(year, unique(min_year), unique(max_year)), 
-      internet, 
-      NaN
-    )
-  ) %>% 
-  ungroup() %>% 
-  select(-min_year, -max_year)
-```
-
-We see that 96 intermediate internet use values were imputed to the time series.
-
-```{r}
-miss_var_summary(itu)
-```
-
-### Complete study dataset
-
-#### GLOBE regions
-
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
-
-```{r}
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
-) %>% 
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>% 
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>% 
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in our dataset not present in region data
-filter(
-  distinct(gbd, country), 
-  !(country %in% unique(regions$country))
-) %>% 
-  arrange(country) %>% 
-  write_csv("data-raw/Regions/GBD-countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/GBD-countries-without-region-filled.csv"
-) 
-```
-
-We then combine all the region tables, clean region names, and join to our data
-
-```{r}
-# Combine Jebb et al GLOBE regions and our manually added ones
-regions <- regions %>% 
-  bind_rows(
-    regions_filled %>% 
-      mutate(Note = "Filled")
-  ) %>% 
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>% 
-  mutate(region = if_else(region=="Sub-Sahara Africa", "Africa", region))
-
-# Format regions to factors and use line breaks instead of spaces
-regions$region <- factor(regions$region)
-levels(regions$region) <- str_replace_all(levels(regions$region), " ", "\n")
-
-# Display table of regions and countries
-regions %>% 
-  kbl(caption = "All countries and regions.") %>% 
-  kable_minimal(full_width = FALSE) %>% 
-  scroll_box(width = "500px", height = "400px")
-
-regions <- select(regions, -Note)
-```
-
-#### Create predictors
-
-We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.
-
-```{r}
-# For models, we rescale year; centred at 2013 and one unit indicates decade
-itu <- itu %>% 
-  mutate(time = (year - 2013) / 10)
-
-# Create predictor: Lagged effect of 10% increase in internet
-itu <- itu %>% 
-  arrange(country, year) %>% 
-  group_by(country) %>% 
-  mutate(i1 = lag(internet*10, 1)) %>% 
-  ungroup()
-
-# Centering within and between countries
-itu <- itu %>%
-  bmlm::isolate("i1", by = "country", which = "both")
-```
-
-#### Create tables
-
-Here, we join the ITU table to the GBD table.
-Note this appropriately duplicates the country-specific predictor values to the demographic groups within each country.
-We then create a table specific to young people.
-
-We also join regions to the data.
-
-```{r}
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-
-# Merge data tables
-gbd <- left_join(gbd, itu)
-
-# Contrast code sex
-gbd$sex <- factor(gbd$sex)
-contrasts(gbd$sex) <- c(-.5, .5)
-
-# Focus on young people
-gbd_all <- gbd
-gbd <- gbd %>% 
-  filter(age %in% c("15 to 19", "20 to 24"))
-
-# Contrast code binary age in young data set
-gbd$age <- factor(gbd$age)
-contrasts(gbd$age) <- c(-.5, .5)
-
-# Young data in wide format
-gbd_wide <- gbd %>%
-  pivot_wider(names_from = cause, values_from = c(val, se))
-names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
-```
-
-We also save a synthetic version of this dataset to better enable others to reproduce our analytical procedures:
-
-```{r synth-data-create}
-
-```
-
-## Describe
-
-### Internet use trends
-
-```{r}
-itu %>% 
-  filter(year %in% c(2001, 2019)) %>% 
-  select(region, country, year, internet) %>% 
-  pivot_wider(names_from = year, values_from = internet) %>% 
-  select(-country) %>% 
-  tbl_summary(by = region) %>% 
-  add_overall()
-itu %>% 
-  group_by(country) %>% 
-  summarise(x = sum(!is.na(internet))) %>% 
-  arrange(x)
-```
-
-```{r}
-# Plot predictors from their own table--values are repeated in data that includes outcomes due to age and sex groups for each year and country
-itu %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(x = year, y = internet)) +
-  coord_cartesian(ylim = c(0, 1.00)) +
-  scale_y_continuous(
-    "Internet users",
-    breaks = c(0, .25, .5, .75, 1),
-    labels = percent,
-    expand = expansion(c(0.02, 0.1))
-  ) +
-  scale_x_date(
-    breaks = breaks_width("5 years"),
-    labels = label_date("'%y")
-  ) +
-  geom_line(
-    aes(group = country),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line", 
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_wrap(~region, nrow = 1) +
-  theme(legend.position = "none")
-ggsave(
-  "output/Fig-ITU.png", 
-  device = agg_png,
-  height = 600, width = 3200, res = 300, units = "px"
-)
-```
-
-```{r}
-itu %>% 
-  mutate(year = make_date(year)) %>%
-  mutate(mobile = if_else(mobile > 1.50, NaN, mobile)) %>% 
-  pivot_longer(internet:mobile) %>% 
-  mutate(name = str_to_title(name)) %>% 
-  mutate(name = fct_inorder(name)) %>% 
-  ggplot(aes(x = year, y = value)) +
-  # coord_cartesian(ylim = c(0, 1.00)) +
-  scale_y_continuous(
-    "Users or subscriptions",
-    # breaks = c(0, .25, .5, .75, 1),
-    labels = percent,
-    expand = expansion(c(0.025, 0.05))
-  ) +
-  scale_x_date(
-    breaks = breaks_width("5 years"),
-    labels = label_date("'%y")
-  ) +
-  # Ensure all axes go up to 100%
-  geom_blank(
-    data = tibble(
-      region = "Africa", 
-      country = NA, 
-      value = 1, 
-      year = make_date(2001))
-  ) +
-  geom_line(
-    aes(group = country),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line", 
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(name~region, scales = "free_y") +
-  theme(
-    legend.position = "none",
-    panel.spacing = unit(2, "pt")
-  )
-```
-
-### Mental health
-
-```{r eval = FALSE}
-pa <- gbd %>% 
-  ggplot(aes(year, val, group = country, col = region)) +
-  scale_y_continuous(
-    "Rate in 100 people",
-    breaks = pretty_breaks()
-  ) +
-  scale_x_continuous(
-    breaks = c(2000, 2005, 2010, 2015, 2020),
-    labels = c("'00", "'05", "'10", "'15", "'20")
-  ) +
-  stat_summary(fun = mean, geom = "line", size = .5) +
-  facet_grid(cause~region, scales = "free_y") +
-  theme(
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-pb <- gbd %>% 
-  mutate(Group = str_glue("{sex} ({age})")) %>% 
-  ggplot(aes(year, val, col = Group)) +
-  scale_color_brewer(palette = "Paired") +
-  scale_y_continuous(
-    "Rate in 100 people",
-    breaks = pretty_breaks()
-  ) +
-  scale_x_continuous(
-    "Year",
-    breaks = c(2000, 2005, 2010, 2015, 2020),
-    labels = c("'00", "'05", "'10", "'15", "'20")
-  ) +
-  stat_summary(fun = mean, geom = "line", size = .6) +
-  facet_grid(cause~region, scales = "free_y")
-
-p_gbd <- (pa / pb) +
-  plot_annotation(tag_levels = "A")
-
-p_gbd
-ggsave(
-  "output/Fig-GBD.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-### Multiple lines
-
-Here we create two plots.
-One to show all main variables' time trends for each region, and country within region.
-Then, show the outcome time trends for top internet trend in each region.
-Maybe put first in main text and second in appendix.
-
-First, variables with one region per panel.
-
-```{r}
-# Add pseudo GWP to figure plot out
-pseudo_gwp <-
-  bind_rows(
-    distinct(gbd, region, year) %>% 
-      crossing(
-        cause = fct_inorder(
-          c(
-            "Negative\nexperiences", 
-            "Positive\nexperiences", 
-            "Life\nsatisfaction"
-          )
-        )
-      )
-  )
-p_vars <- bind_rows(
-  pseudo_gwp,
-  gbd %>% 
-    group_by(region, country, year, cause) %>% 
-    summarise(mean = mean(val/100))
-) %>% 
-  ungroup() %>% 
-  mutate(cause = fct_inorder(cause)) %>% 
-  mutate(year = make_date(year)) %>% 
-  ggplot(aes(year, mean)) +
-  scale_color_brewer(
-    "Variable",
-    palette = "Set1", direction = -1
-  ) +
-  scale_y_continuous(
-    "Rate or scale score",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    breaks = make_date(c(2005, 2010, 2015)), 
-    date_labels = "'%y", 
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, cause)), 
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line", 
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(cause~region, scales = "free_y") +
-  theme(
-    legend.position = "none",
-    panel.spacing = unit(2, "pt")
-  )
-p_vars
-ggsave(
-  "output/Fig-vars-timeseries.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-```{r}
-# Get top 1 internet trend country in each region
-top_trends <- gbd %>% 
-  semi_join(distinct(itu, country)) %>% 
-  group_by(region, country) %>% 
-  summarise(tidy(lm(internet ~ time, data = cur_data_all()))) %>% 
-  filter(term == "time") %>% 
-  group_by(region) %>% 
-  slice_max(order_by = estimate, n = 1)
-pb <- gbd %>% 
-  filter(country %in% top_trends$country) %>%
-  mutate(country = factor(country, levels = top_trends$country)) %>% 
-  mutate(Group = str_glue("{sex} ({age})")) %>% 
-  mutate(year = make_date(year)) %>% 
-  ggplot(aes(year, val/100, col = Group)) +
-  scale_color_brewer(palette = "Paired") +
-  scale_y_continuous(
-    "Rate",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    breaks = make_date(c(2005, 2010, 2015)), 
-    date_labels = "'%y", 
-    expand = expansion(.02)
-  ) +
-  stat_summary(fun = mean, geom = "line", size = .6) +
-  facet_grid(cause~country, scales = "free_y")
-
-(pa + theme(axis.title.x = element_blank())) / 
-  pb * 
-  theme(panel.spacing = unit(2, "pt")) +
-  plot_layout(heights = c(4, 3)) +
-  plot_annotation(tag_levels = "A")
-ggsave(
-  "output/Fig-all-vars-timeseries.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-## Model 1: Temporal trends
-
-We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.
-
-We first fit the models using lme4 because they are big and therefore would be very slow with brms.
-
-### GBD
-
-#### lme4
-
-```{r fit-gbd-time-lme4}
-# These take about 5-20 minutes each
-# run in parallel in background jobs
-# recommended to conduct this in interactive mode (rstudio)
-file_path <- "output/lme4-gbd-time.rds"
-if (!file.exists(file_path)) {
-  library(job)
-  job({fit_anx <- lmer(
-    Anxiety ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Anxiety time (lmer)")
-  job({fit_dep <- lmer(
-    Depression ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Depression time (lmer)")
-  job({fit_sel <- lmer(
-    Selfharm ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Self harm time (lmer)")
-  fits_lmer <- distinct(gbd, cause) %>% 
-    mutate(fit = list(fit_anx, fit_dep, fit_sel))
-  write_rds(fits_lmer, file_path)
-} else {fits_lmer <- read_rds(file_path)}
-```
-
-Plot fixed effects and by demographic
-
-```{r}
-# Fixed effects parameters
-fixed_effects <- fits_lmer %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  filter(
-    Effects == "fixed", 
-    Parameter != "(Intercept)"
-  ) 
-# Fixed effects per demographic
-fixed_effects_demographics <- fits_lmer %>% 
-  mutate(
-    out = map(
-      fit,
-      ~emtrends(.x, var = "time", by = c("sex", "age")) %>% 
-        parameters() %>% 
-        as.data.frame()
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  mutate(Parameter = str_glue("{sex}\n({age})"))
-
-# Random effects parameters
-random_effects <- fits_lmer %>% 
-  mutate(
-    coef_region = map(
-      fit, 
-      ~bind_rows(
-        coef(.x)$region %>% 
-          as.data.frame() %>% 
-          rownames_to_column("region"),
-        coef(.x)$country %>% 
-          as.data.frame() %>% 
-          rownames_to_column("country"),
-        .id = "cluster"
-      ) %>% 
-        mutate(cluster = factor(cluster, labels = c("region", "country")))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(coef_region) %>% 
-  mutate(Type = "Effects") %>%
-  select(-`(Int      ,nc ercept)`)
-
-bind_rows(
-  fixed_effects,
-  fixed_effects_demographics, 
-  .id = "Type"
-) %>% 
-  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
-  mutate(Parameter = fct_inorder(Parameter)) %>%
-  mutate(cause = factor(cause)) %>% 
-  rowwise() %>% 
-  mutate(
-    sig = factor(
-      !between(0, CI_low, CI_high), 
-      levels = c(TRUE, FALSE)
-    )
-  ) %>% 
-  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
-  scale_color_discrete(
-    "Outcome"
-  ) +
-  scale_x_continuous(
-    "Estimate (95%CI)"
-  ) +
-  scale_shape_manual(values = c(19, 21)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodge2v(.5),
-    fill = "white", size = .3, fatten = 5
-  ) +
-  guides(shape = "none") +
-  facet_wrap("Type", ncol = 2, scales = "free") +
-  theme(axis.title.y = element_blank())
-```
-
-#### brms
-
-correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
-
-note we use beta so transform edge values
-
-we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
-
-##### Time: Main effects
-
-We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
-
-$$
-\begin{align*}
-y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\
-
-\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
-\beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\
-
-i_{i[c][r]} &\sim 
-\text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\
-
-\mu^i_{i[c][r]} &= \text{logit}(
-\beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
-\beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\
-
-\left[\begin{array}{c}
-\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
-\end{array}\right] 
-&\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^c
-),
-
-\left[\begin{array}{c}
-\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
-\end{array}\right] 
-\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^r
-)
-\end{align*}
-$$
-
-```{r}
-# Transform edge proportions to fit beta distribution
-gbd_10 <- gbd_wide %>% 
-  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999999, internet))
-
-# Define a model of internet proportion over time
-bf_int <- bf(
-  internet ~ 1 + time + 
-    (1 + time |c| country) +
-    (1 + time |r| region), 
-  family = Beta()
-)
-
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-
-bf_time_mv <- bf(
-  mvbind(Depression, Anxiety, Selfharm) ~ 
-    1 + time +
-    (1 + time |c| country) +
-    (1 + time | region),
-  family = gaussian()
-) +
-  bf_int +
-  set_rescor(FALSE)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-anxiety",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-depression",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-selfharm",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fits_brm_time_main <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-
-```
-
-Coefficients
-
-```{r}
-fits_brm_time_main %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Revisit figure of temporal trends with coefficients
-
-```{r}
-tmp_pars <- fits_brm_time_main %>% 
-  mutate(
-    out = map2(
-      fit, 
-      outcome,
-      ~hypothesis(
-        .x, 
-        c(str_glue("{.y}_time = 0")),
-        scope = "coef",
-        group = "region"
-      )$hypothesis
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # Internet trend is estimated in all models keep first
-  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
-  mutate(across(where(is.numeric), ~round(., 3))) %>% 
-  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
-  select(cause = Hypothesis, region = Group, result) %>% 
-  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))
-
-p_vars +
-  geom_richtext(
-    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
-    aes(x = make_date(2000), y = Inf, label = result),
-    size = 2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  )
-ggsave(
-  "output/Fig-vars-timeseries-estimates.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-Calculate country coefficients and show scatterplots
-
-```{r time-correlation-anxiety}
-# Get average and region
-r_region_anxiety <- fit_anx %>% 
-  spread_draws(
-    b_Anxiety_time, 
-    b_internet_time,
-    r_region__Anxiety[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_anxiety <- fit_anx %>% 
-  spread_draws(
-    r_country__Anxiety[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_anx$data$country))
-    )
-  ) %>% 
-  left_join(distinct(gbd, region, country))
-
-# Calculate country coefficients
-country_anxiety <- left_join(r_country_anxiety, r_region_anxiety) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    anxiety = b_Anxiety_time + r_region__Anxiety + r_country__Anxiety
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, anxiety)
-
-country_anxiety_ellipse <- spread_draws(
-  fit_anx,
-  b_Anxiety_time, b_internet_time,
-  cor_country__internet_time__Anxiety_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Anxiety_time, 
-        y = b_internet_time, 
-        z = b_Anxiety_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_anxiety_ellipse <- spread_draws(
-  fit_anx,
-  b_Anxiety_time, b_internet_time,
-  cor_region__internet_time__Anxiety_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Anxiety_time, 
-        y = b_internet_time, 
-        z = b_Anxiety_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_anxiety_cor <- fit_anx %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Anxiety_time",
-      "cor_region__internet_time__Anxiety_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_anxiety_result <- country_anxiety_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_anx <- country_anxiety %>% 
-  ggplot(aes(internet, anxiety)) +
-  # geom_path(
-  #   data = region_anxiety_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_anxiety_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear anxiety trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_anxiety_result %>% 
-      filter(variable == "cor_country__internet_time__Anxiety_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r time-correlation-depression}
-# Get average and region
-r_region_depression <- fit_dep %>% 
-  spread_draws(
-    b_Depression_time, 
-    b_internet_time,
-    r_region__Depression[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_depression <- fit_dep %>% 
-  spread_draws(
-    r_country__Depression[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_dep$data$country))
-    )
-  ) %>% 
-  left_join(distinct(gbd, region, country))
-
-# Calculate country coefficients
-country_depression <- left_join(r_country_depression, r_region_depression) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    depression = b_Depression_time + r_region__Depression + r_country__Depression
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, depression)
-
-country_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_country__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_region__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_depression_cor <- fit_dep %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Depression_time",
-      "cor_region__internet_time__Depression_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_depression_result <- country_depression_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_dep <- country_depression %>% 
-  ggplot(aes(internet, depression)) +
-  # geom_path(
-  #   data = region_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear depression trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_depression_result %>% 
-      filter(variable == "cor_country__internet_time__Depression_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r time-correlation-selfharm}
-# Get average and region
-r_region_selfharm <- fit_sel %>% 
-  spread_draws(
-    b_Selfharm_time, 
-    b_internet_time,
-    r_region__Selfharm[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_selfharm <- fit_sel %>% 
-  spread_draws(
-    r_country__Selfharm[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_sel$data$country))
-    )
-  ) %>% 
-  left_join(distinct(gbd, region, country))
-
-# Calculate country coefficients
-country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, selfharm)
-
-country_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_country__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_region__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_selfharm_cor <- fit_sel %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Selfharm_time",
-      "cor_region__internet_time__Selfharm_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_selfharm_result <- country_selfharm_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_sel <- country_selfharm %>% 
-  ggplot(aes(internet, selfharm)) +
-  # geom_path(
-  #   data = region_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear selfharm trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_selfharm_result %>% 
-      filter(variable == "cor_country__internet_time__Selfharm_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r}
-p_cor_country_anx + theme(axis.title.x = element_blank()) | 
-  p_cor_country_dep | 
-  p_cor_country_sel + theme(axis.title.x = element_blank())
-```
-
-##### Time: Interactions
-
-```{r}
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time * sex + time * age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-anxiety-int2",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-depression-int2",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-selfharm-int2",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fits_brm_time_interactions <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-```
-
-Coefficients
-
-```{r}
-fits_brm_time_interactions %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 2) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Model comparison using waic shows that interactive model is favored across the board.
-
-```{r eval = FALSE}
-waics <- left_join(
-  rename(fits_brm_time_main, fit_main = fit),
-  rename(fits_brm_time_interactions, fit_intr = fit)
-) %>% 
-  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
-waics$waic[[3]]
-```
-
-Show main effects
-
-Plot fixed effects and by demographic
-
-```{r}
-# Fixed effects parameters
-fixed_effects <- fits_brm_time_interactions %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  filter(
-    Effects == "fixed", 
-    Parameter != "(Intercept)"
-  ) 
-# Fixed effects per demographic
-fixed_effects_demographics <- fits_brm_time_interactions %>% 
-  mutate(
-    out = map2(
-      fit, outcome,
-      ~emtrends(
-        .x, 
-        var = "time", 
-        by = c("sex", "age"), 
-        resp = .y
-      ) %>% 
-        parameters() %>% 
-        as.data.frame()
-    )
-  )
-fixed_effects_demographics %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  mutate(Parameter = str_glue("{sex}\n({age})"))
-
-# Random effects parameters
-random_effects <- fits_lmer %>% 
-  mutate(
-    coef_region = map(
-      fit, 
-      ~bind_rows(
-        coef(.x)$region %>% 
-          as.data.frame() %>% 
-          rownames_to_column("region"),
-        coef(.x)$country %>% 
-          as.data.frame() %>% 
-          rownames_to_column("country"),
-        .id = "cluster"
-      ) %>% 
-        mutate(cluster = factor(cluster, labels = c("region", "country")))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(coef_region) %>% 
-  mutate(Type = "Effects") %>%
-  select(-`(Int      ,nc ercept)`)
-
-bind_rows(
-  fixed_effects,
-  fixed_effects_demographics, 
-  .id = "Type"
-) %>% 
-  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
-  mutate(Parameter = fct_inorder(Parameter)) %>%
-  mutate(cause = factor(cause)) %>% 
-  rowwise() %>% 
-  mutate(
-    sig = factor(
-      !between(0, CI_low, CI_high), 
-      levels = c(TRUE, FALSE)
-    )
-  ) %>% 
-  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
-  scale_color_discrete(
-    "Outcome"
-  ) +
-  scale_x_continuous(
-    "Estimate (95%CI)"
-  ) +
-  scale_shape_manual(values = c(19, 21)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodge2v(.5),
-    fill = "white", size = .3, fatten = 5
-  ) +
-  guides(shape = "none") +
-  facet_wrap("Type", ncol = 2, scales = "free") +
-  theme(axis.title.y = element_blank())
-```
-
-```{r}
-library(modelbased)
-x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
-tmp <- fits_brm %>% 
-  mutate(
-    # Average effect
-    avg = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(.x, str_glue("{.y}_time = 0"))
-    ),
-    # By country effect
-    by_country = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "country"
-      )
-    ),
-    # By region effect
-    by_region = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "region"
-      )
-    )
-  ) %>% 
-  select(-fit)
-
-tmp %>% 
-  select(Outcome, avg) %>% 
-  mutate(avg = map(avg, ))
-
-tmp$by_region[[1]] %>% str
-
-h <- paste(
-  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
-  "= 0"
-)
-
-# Prepare average samples
-time_avg <- hypothesis(fit_gbd_time, h)
-time_avg_samples <- time_avg$samples
-names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
-time_avg_samples <- time_avg_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  mutate(region = "Average")
-
-# Prepare region samples
-time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
-time_region_samples <- time_region$samples
-names(time_region_samples) <- paste(
-  time_region$hypothesis$Hypothesis, 
-  time_region$hypothesis$Group, sep = ":"
-)
-time_region_samples <- time_region_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  separate(Parameter, c("Parameter", "region"), sep = ":")
-
-# Prepare country point estimates
-time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
-time_country_hypothesis <- time_country$hypothesis %>% 
-  rename(country = Group, Parameter = Hypothesis)
-time_country_hypothesis <- left_join(
-  time_country_hypothesis, 
-  distinct(fit_gbd_time$data, country, region)
-)
-
-time_sum <- bind_rows(
-  time_region$hypothesis,
-  time_avg$hypothesis %>% mutate(Group = "Average")
-) %>% 
-  as_tibble() %>% 
-  rename(region = Group, Parameter = Hypothesis)
-
-bind_rows(
-  time_region_samples,
-  time_avg_samples
-) %>% 
-  mutate(region = fct_relevel(region, "Average")) %>% 
-  mutate(Average = region == "Average") %>% 
-  ggplot(aes(value/10, region)) +
-  scale_y_discrete(
-    expand = expansion(c(0.025, 0.075)),
-    labels = function(x) ifelse(x == "Average", "**Average**", x)
-  ) +
-  scale_x_continuous(
-    "Estimated yearly change",
-    breaks = pretty_breaks(5)
-  ) +
-  scale_alpha_manual(values = c(.5, 1)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .25) +
-  stat_eye(
-    side = "top",
-    aes(col = region, fill = region, alpha = Average),
-    point_interval = NULL,
-    normalize = "panels", 
-    height = .75
-  ) +
-  geom_pointrangeh(
-    data = time_sum,
-    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
-    size = .3, fatten = 1.4
-  ) +
-  geom_point(
-    data = time_country_hypothesis,
-    aes(col = region, x = Estimate/10), 
-    size = .5,
-    alpha = .25,
-    position = position_nudge(y = -.05)
-  ) +
-  facet_wrap(
-    "Parameter", ncol = 3, scales = "free_x",
-    labeller = as_labeller(
-      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
-  ) +
-  theme(
-    axis.text.y = element_markdown(),
-    legend.position = "none",
-    axis.title.y = element_blank()
-  )
-ggsave(
-  "output/Fig-brm-time-forest.png", 
-  device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
-)
-```
-
-##### Internet: Main effects
-
-```{r}
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time + sex + age + i1_cw + i1_cb +
-    (1 + time + sex + age + i1_cw |c| country) +
-    (1 + time + sex + age + i1_cw |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + i1_cw + i1_cb +
-    (1 + time + sex + age + i1_cw |c| country) +
-    (1 + time + sex + age + i1_cw |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + i1_cw + i1_cb + 
-    (1 + time + sex + age + i1_cw |c| country) +
-    (1 + time + sex + age + i1_cw |r| region),
-  family = gaussian()
-)
-
-# Fit models in background (need 12 cores)
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-internet-anxiety",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-internet-depression",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-internet-selfharm",
-  chains = 4,
-  cores = 4,
-  iter = 1000, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-fits_brm_internet_main <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-```
-
-Coefficients
-
-```{r}
-fits_brm_internet_main %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  filter(str_detect(variable, "_i1_cw|b$")) %>% 
-  kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Different levels
-
-```{r}
-# Get average and region
-r_selfharm <- fit_sel %>% 
-  spread_draws(
-    b_Selfharm_i1_cw, 
-    r_region__Selfharm[region, term]
-  ) %>% 
-  filter(term == "i1_cw") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-fit_sel %>% 
-  spread_draws(
-    r_country__Selfharm[country, term]
-    )
-
-# Calculate country coefficients
-r_selfharm <- r_selfharm %>% 
-  mutate(
-    b_average = b_Selfharm_i1_cw,
-    b_region = b_average + r_region__Selfharm,
-    b_country = b_region + r_country__Selfharm
-  )
-
-r_selfharm %>% 
-  distinct(.draw, b_average) %>% 
-  mutate(region = "Average") %>% 
-  ggplot(aes(b_average, region)) +
-  stat_halfeye(size = 1, fill = "dodgerblue4") +
-  stat_halfeye(
-    data = r_selfharm %>% 
-      distinct(.draw, region, b_region),
-    aes(b_region),
-    size = 1, fill = "dodgerblue1"
-  ) +
-  geom_point(
-    data = 
-  )
-r_selfharm %>% 
-  group_by(region, country) %>% 
-  median_qi(b_country)
-```
-
-##### Internet: Interactions
-
-```{r}
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb + 
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  family = gaussian()
-)
-
-# Fit models in background (need 12 cores)
-job::job({
-  fit_anx <- brm(
-    bf_anx,
-    data = gbd_wide,
-    file = "output/brm-gbd-time-internet-anxiety-int2",
-    chains = 4,
-    cores = 4,
-    iter = 1200, warmup = 600, refresh = 10,
-    threads = 1,
-    control = list(adapt_delta = .9)
-  )
-}, title = "Fitting brms anxiety")
-job::job({
-  fit_dep <- brm(
-    bf_dep,
-    data = gbd_wide,
-    file = "output/brm-gbd-time-internet-depression-int2",
-    chains = 4,
-    cores = 4,
-    iter = 1200, warmup = 600, refresh = 10,
-    threads = 1,
-    control = list(adapt_delta = .9)
-  )
-}, title = "Fitting brms depression")
-fit_sel <- brm(
-  bf_sel,
-  data = gbd_wide,
-  file = "output/brm-gbd-time-internet-selfharm-int2",
-  chains = 4,
-  cores = 4,
-  iter = 1200, warmup = 600, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9)
-)
-```
-
-###### Plot: Average effects of time
-
-```{r eval = FALSE}
-fixef(fit_gbd_time) %>%
-  as.data.frame() %>% 
-  rownames_to_column("Parameter") %>% 
-  as_tibble()
-
-h <- paste(
-  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
-  "= 0"
-)
-
-# Prepare average samples
-time_avg <- hypothesis(fit_gbd_time, h)
-time_avg_samples <- time_avg$samples
-names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
-time_avg_samples <- time_avg_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  mutate(region = "Average")
-
-# Prepare region samples
-time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
-time_region_samples <- time_region$samples
-names(time_region_samples) <- paste(
-  time_region$hypothesis$Hypothesis, 
-  time_region$hypothesis$Group, sep = ":"
-)
-time_region_samples <- time_region_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  separate(Parameter, c("Parameter", "region"), sep = ":")
-
-# Prepare country point estimates
-time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
-time_country_hypothesis <- time_country$hypothesis %>% 
-  rename(country = Group, Parameter = Hypothesis)
-time_country_hypothesis <- left_join(
-  time_country_hypothesis, 
-  distinct(fit_gbd_time$data, country, region)
-)
-
-time_sum <- bind_rows(
-  time_region$hypothesis,
-  time_avg$hypothesis %>% mutate(Group = "Average")
-) %>% 
-  as_tibble() %>% 
-  rename(region = Group, Parameter = Hypothesis)
-
-bind_rows(
-  time_region_samples,
-  time_avg_samples
-) %>% 
-  mutate(region = fct_relevel(region, "Average")) %>% 
-  mutate(Average = region == "Average") %>% 
-  ggplot(aes(value/10, region)) +
-  scale_y_discrete(
-    expand = expansion(c(0.025, 0.075)),
-    labels = function(x) ifelse(x == "Average", "**Average**", x)
-  ) +
-  scale_x_continuous(
-    "Estimated yearly change",
-    breaks = pretty_breaks(5)
-  ) +
-  scale_alpha_manual(values = c(.5, 1)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .25) +
-  stat_eye(
-    side = "top",
-    aes(col = region, fill = region, alpha = Average),
-    point_interval = NULL,
-    normalize = "panels", 
-    height = .75
-  ) +
-  geom_pointrangeh(
-    data = time_sum,
-    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
-    size = .3, fatten = 1.4
-  ) +
-  geom_point(
-    data = time_country_hypothesis,
-    aes(col = region, x = Estimate/10), 
-    size = .5,
-    alpha = .25,
-    position = position_nudge(y = -.05)
-  ) +
-  facet_wrap(
-    "Parameter", ncol = 3, scales = "free_x",
-    labeller = as_labeller(
-      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
-  ) +
-  theme(
-    axis.text.y = element_markdown(),
-    legend.position = "none",
-    axis.title.y = element_blank()
-  )
-ggsave(
-  "output/Fig-brm-time-forest.png", 
-  device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
-)
-```
-
-## Model 2: Associations
-
-This model expands the above to add internet adoption as a predictor.
-
-### GBD
-
-#### Figure
-
-```{r}
-gbd %>% 
-  ggplot(
-    aes(
-      x = i1_cw/10, 
-      y = val, 
-      col = region, fill = region
-    )
-  ) +
-  geom_point(size = .25, alpha = .1) +
-  stat_smooth(method = "lm", alpha = .2, size = .3) +
-  # stat_summary(fun = mean, geom = "line", size = .25) +
-  facet_grid(Cause~region, scales = "free_y") +
-  theme(legend.position = "none")
-```
-
-#### lme4
-
-```{r fit-gbd-internet-lme4}
-# These take about 1-3 hours each
-# run in parallel in background jobs
-# recommended to conduct this in interactive mode (rstudio)
-file_path <- "output/lme4-gbd-internet.rds"
-if (!file.exists(file_path)) {
-  library(job)
-  job({fit_anx <- lmer(
-    Anxiety ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Anxiety internet (lmer)")
-  job({fit_dep <- lmer(
-    Depression ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Depression internet (lmer)")
-  job({fit_sel <- lmer(
-    Selfharm ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-      (1 + time * sex * age + i1_cw * sex * age | region) +
-      (1 + time * sex * age + i1_cw * sex * age | country),
-    data = gbd_wide
-  )}, title = "Self harm internet (lmer)")
-  fits_lmer <- distinct(gbd, cause) %>% 
-    mutate(fit = list(fit_anx, fit_dep, fit_sel))
-  write_rds(fits_lmer, file_path)
-} else {fits_lmer <- read_rds(file_path)}
-```
-
-```{r}
-fits_lmer %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  filter(term == "i1_cw")
-```
-
-#### brms
-
-```{r fit-gbd-internet-brms, eval = FALSE}
-# bf_gbd_internet <- bf(
-#   mvbind(
-#     val_Depression,
-#     val_Anxiety,
-#     val_Self_harm
-#   ) ~ 1 + Time + i1_cw + i1_cb +
-#     (1 + Time + i1_cw || region)
-#   (1 + Time + i1_cw || country)
-# ) +
-#   set_rescor(FALSE)
-# 
-# fit_gbd_internet <- brm(
-#   bf_gbd_internet,
-#   gbd_y_w,
-#   file = "output/brm-gbd-internet-mv",
-#   chains = 5,
-#   cores = 5,
-#   iter = 300, warmup = 150, refresh = 10,
-#   threads = 2,
-#   control = list(adapt_delta = .9, max_treedepth = 15)
-# )
-
-bf_gbd_internet_demos <- bf(
-  mvbind(
-    Depression,
-    Anxiety,
-    Selfharm
-  ) ~ 1 + time * sex * age + i1_cw * sex * age + i1_cb +
-    (1 + time * sex * age + i1_cw * sex * age | country)
-) +
-  set_rescor(FALSE)
-
-p <- prior(normal(0, 3), class = b, resp = Anxiety) +
-  prior(normal(0, 3), class = b, resp = Depression) +
-  prior(normal(0, 3), class = b, resp = Selfharm) +
-  prior(student_t(7, 0, 1), class = sd, resp = Anxiety) +
-  prior(student_t(7, 0, 1), class = sd, resp = Depression) +
-  prior(student_t(7, 0, 1), class = sd, resp = Selfharm)
-
-job::job({fit_gbd_internet_demos <- brm(
-  bf_gbd_internet_demos,
-  gbd_wide,
-  prior = p,
-  file = "output/brm-gbd-internet-mv-demos",
-  chains = 5,
-  cores = 5,
-  iter = 450, warmup = 300, refresh = 10,
-  threads = 1,
-  control = list(adapt_delta = .9, max_treedepth = 15)
-)}, title = "brms internet")
-```

### 2021-11-15 _common.R
Add common options

@@ -1,0 +1,31 @@
+# Set global options here
+
+# Global knitr options
+library(ragg)
+knitr::opts_chunk$set(
+  echo = TRUE,
+  warning = FALSE,
+  cache = TRUE,
+  error = FALSE,
+  message = FALSE,
+  fig.align = "center",
+  fig.width = 8,
+  dev = "ragg_png",
+  fig.retina = 2
+)
+
+# Plotting theme
+library(sysfonts)
+library(ggplot2)
+Font <- "Titillium Web"
+if (!(Font %in% font_families())) font_add_google(Font, Font)
+theme_set(
+  theme_linedraw(
+    base_size = 12,
+    base_family = Font
+  ) +
+    theme(
+      panel.grid = element_blank(),
+      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
+    )
+)

### 2021-11-15 01-clean.Rmd
Split analysis to separate documents

# Clean and prepare

## Settings

We first load the required R packages and set some options for the resulting document.

```{r packages}
#| results: 'hide'
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(janitor)
library(countrycode)
library(kableExtra)
library(tidyverse)

# Create directory for intermediate files
dir.create("output", FALSE)
```

## Data cleaning

We downloaded the relevant data from sources to `data-raw/`. We cannot share the data here but indicate below how and when each data table was obtained.

### Global Burden of Disease

The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`. We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript. Next we load all tables (inside downloaded `.zip` files, there may be more than one depending on size of downloaded table) inside the directory.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/gbd-2021-11-02/", 
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>% 
  read_csv()
```

We then ensure that the correct variables were downloaded, and then clean this data.

```{r gbd-data-clean}
# Cleaning

# First step is to clean names in all data sets
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# - prevalence: Total number of cases
# - rate: Total cases per 100,000 population
#   - We convert this to a percentage
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>% 
  mutate(across(c(val, upper, lower), ~.x/1000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>% 
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>% 
  rename(country = location)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
gbd <- gbd %>% 
  mutate(se = (upper-lower) / (1.96*2)) %>%
  select(-c(upper, lower))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")
# Harmonise old names after verifying above that none are dropped
gbd <- gbd %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))
```

### Gallup World Poll

GWP cleaning goes here.

### International Telecommunication Union

The internet adoption data were downloaded from the ITU website in October 2021, and placed with their original file names to `data-raw/ITU/`. The specific URLs for obtaining the data files are

- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>

We first load, reshape, and merge these datasets.

```{r itu-load-clean}
# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(fixed = as.numeric(value)) %>% 
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx", 
  sheet = 2,
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(mobile = as.numeric(value)) %>% 
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>% 
  pivot_longer(-c(Indicator, Country)) %>% 
  separate(name, into = c("year", "variable")) %>% 
  pivot_wider(names_from = variable) %>% 
  mutate(internet = as.numeric(value)) %>% 
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>% 
  mutate(across(c(internet, fixed, mobile), function(x) x/100)) %>% 
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)
```

Then harmonise country names as above, and drop countries that don't exist in outcomes.

```{r itu-harmonise-countries}
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>% 
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>% 
  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Harmonise old names after verifying above that none are dropped
itu <- itu %>% 
  mutate(country = countryname(country, destination = "cldr.short.en"))

# These countries don't exist in outcomes
itu %>%
  distinct(country) %>% 
  anti_join(distinct(gbd, country)) %>% 
  kbl() %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

# Drop them
itu <- itu %>% 
  filter(country %in% unique(gbd$country))
```

#### Missingness

Remove countries with no observations

```{r}
itu <- itu %>% 
  group_by(country) %>% 
  mutate(nobs = sum(!is.na(internet))) %>% 
  ungroup() %>% 
  filter(nobs > 0) %>% 
  select(-nobs)
```

There are some missing values in the data; in the Internet variable these are mainly in the first or last years of each country's time-series. This needs to be changed to calculate by-variable (with appropriate time-spans) when adding mobile and fixed

```{r}
miss_var_summary(itu)
```

We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values.

```{r itu-impute}
itu <- itu %>% 
  group_by(country) %>% 
  # Find first and last year with internet data in each country
  mutate(
    min_year = year[min(which(!is.na(internet)))],
    max_year = year[max(which(!is.na(internet)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  # Add variables to c() to impute for fixed and mobile broadband
  mutate(
    across(
      c(internet), 
      possibly(
        function(x) na_interpolation(x, maxgap = Inf), 
        # If function errors, provide original internet value
        otherwise = internet
      )
    )
  ) %>% 
  # Take out projected (non-intermediate) imputed values
  mutate(
    internet = if_else(
      between(year, unique(min_year), unique(max_year)), 
      internet, 
      NaN
    )
  ) %>% 
  ungroup() %>% 
  select(-min_year, -max_year)
```

We see that 96 intermediate internet use values were imputed to the time series.

```{r}
miss_var_summary(itu)
```

### Complete study dataset

#### GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r}
regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>% 
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>% 
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>% 
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in our dataset not present in region data
filter(
  distinct(gbd, country), 
  !(country %in% unique(regions$country))
) %>% 
  arrange(country) %>% 
  write_csv("data-raw/Regions/GBD-countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/GBD-countries-without-region-filled.csv"
) 
```

We then combine all the region tables, clean region names, and join to our data

```{r}
# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>% 
  bind_rows(
    regions_filled %>% 
      mutate(Note = "Filled")
  ) %>% 
  arrange(region, country)

# Shorter name for plots
regions <- regions %>% 
  mutate(region = if_else(region=="Sub-Sahara Africa", "Africa", region))

# Format regions to factors and use line breaks instead of spaces
regions$region <- factor(regions$region)
levels(regions$region) <- str_replace_all(levels(regions$region), " ", "\n")

# Display table of regions and countries
regions %>% 
  kbl(caption = "All countries and regions.") %>% 
  kable_minimal(full_width = FALSE) %>% 
  scroll_box(width = "500px", height = "400px")

regions <- select(regions, -Note)
```

#### Create predictors

We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.

```{r}
# For models, we rescale year; centred at 2013 and one unit indicates decade
itu <- itu %>% 
  mutate(time = (year - 2013) / 10)

# Create predictor: Lagged effect of 10% increase in internet
itu <- itu %>% 
  arrange(country, year) %>% 
  group_by(country) %>% 
  mutate(i1 = lag(internet*10, 1)) %>% 
  ungroup()

# Centering within and between countries
itu <- itu %>%
  bmlm::isolate("i1", by = "country", which = "both")
```

#### Create tables

Here, we join the ITU table to the GBD table. Note this appropriately duplicates the country-specific predictor values to the demographic groups within each country. We then create a table specific to young people.

We also join regions to the data.

```{r}
# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)

# Merge data tables
gbd <- left_join(gbd, itu)

# Contrast code sex
gbd$sex <- factor(gbd$sex)
contrasts(gbd$sex) <- c(-.5, .5)

# Focus on young people
gbd_all <- gbd
gbd <- gbd %>% 
  filter(age %in% c("15 to 19", "20 to 24"))

# Contrast code binary age in young data set
gbd$age <- factor(gbd$age)
contrasts(gbd$age) <- c(-.5, .5)

# Young data in wide format
gbd_wide <- gbd %>%
  pivot_wider(names_from = cause, values_from = c(val, se))
names(gbd_wide) <- str_remove(names(gbd_wide), "val_")

# Transform edge proportions to fit beta distribution
gbd_10 <- gbd_wide %>% 
  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
  mutate(internet = if_else(internet == 1, .9999999999, internet))
```

We also save a synthetic version of this dataset to better enable others to reproduce our analytical procedures:

```{r synth-data-create}

```

## Save tables

We then save the tables for later use in `data/`.

### 2021-11-15 03-time.Rmd
Split analysis to separate documents

# Time trends

```{r packages}
#| results: 'hide'
# Packages
library(ggtext)
library(brms)
library(ellipse)
library(broom.mixed)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(parameters)
library(lme4)
library(emmeans)
library(patchwork)
library(bayestestR)
library(lubridate)
library(broom)
library(kableExtra)
library(ggstance)
library(tidyverse)

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(iter = 2250, warmup = 1000, refresh = 50, d = .9)
# Run this to delete fitted models and refit
# unlink(list.files(pattern = "output/brm-.*\\.rds"))
```

## Model 1: Temporal trends

We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.

We first fit the models using lme4 because they are big and therefore would be very slow with brms.

### GBD

#### lme4

```{r fit-gbd-time-lme4}
# These take about 5-20 minutes each
# run in parallel in background jobs
# recommended to conduct this in interactive mode (rstudio)
file_path <- "output/lme4-gbd-time.rds"
if (!file.exists(file_path)) {
  library(job)
  job({fit_anx <- lmer(
    Anxiety ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Anxiety time (lmer)")
  job({fit_dep <- lmer(
    Depression ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Depression time (lmer)")
  job({fit_sel <- lmer(
    Selfharm ~ 1 + time * sex * age + 
      (1 + time * sex * age | region) +
      (1 + time * sex * age | country),
    data = gbd_wide
  )}, title = "Self harm time (lmer)")
  fits_lmer <- distinct(gbd, cause) %>% 
    mutate(fit = list(fit_anx, fit_dep, fit_sel))
  write_rds(fits_lmer, file_path)
} else {fits_lmer <- read_rds(file_path)}
```

Plot fixed effects and by demographic

```{r}
# Fixed effects parameters
fixed_effects <- fits_lmer %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_lmer %>% 
  mutate(
    out = map(
      fit,
      ~emtrends(.x, var = "time", by = c("sex", "age")) %>% 
        parameters() %>% 
        as.data.frame()
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

# Random effects parameters
random_effects <- fits_lmer %>% 
  mutate(
    coef_region = map(
      fit, 
      ~bind_rows(
        coef(.x)$region %>% 
          as.data.frame() %>% 
          rownames_to_column("region"),
        coef(.x)$country %>% 
          as.data.frame() %>% 
          rownames_to_column("country"),
        .id = "cluster"
      ) %>% 
        mutate(cluster = factor(cluster, labels = c("region", "country")))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(coef_region) %>% 
  mutate(Type = "Effects") %>%
  select(-`(Int      ,nc ercept)`)

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

#### brms

correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix

note we use beta so transform edge values

we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow

##### Time: Main effects

We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.

$$
\begin{align*}
y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\

\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
\beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\

i_{i[c][r]} &\sim 
\text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\

\mu^i_{i[c][r]} &= \text{logit}(
\beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
\beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\

\left[\begin{array}{c}
\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
\end{array}\right] 
&\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^c
),

\left[\begin{array}{c}
\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
\end{array}\right] 
\sim MVN(
\left[\begin{array}{c}
0 \\ 0 \\ 0 \\ 0
\end{array}\right],
\Sigma^r
)
\end{align*}
$$

```{r}
# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_time_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000

```{r}
tmp_pars <- fits_brm_time_main %>% 
  mutate(
    out = map2(
      fit, 
      outcome,
      ~hypothesis(
        .x, 
        c(str_glue("{.y}_time = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # Internet trend is estimated in all models--keep first
  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
  # Transform back to rates in 100k
  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause = Hypothesis, region = Group, result) %>% 
  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))

p_vars +
  geom_richtext(
    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
ggsave(
  "output/Fig-vars-timeseries-estimates.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

A figure of coefficients

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_time, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_time) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_time, r_region__Depression[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_time) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_time, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_time) %>% 
  mutate(outcome = "Selfharm")

p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels"
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
p_time_main_coefs
```

###### Correlations

Calculate country coefficients and show scatterplots

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      {{beta}}, 
      b_internet_time,
      {{r_region}}[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

  # Then country
  r_country_draws <- fit %>% 
    spread_draws(
      {{r_country}}[country, term],
      r_country__internet[country, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by taking labels from original names
    mutate(
      country = factor(
        country, 
        labels = sort(unique(fit$data$country))
      )
    ) %>% 
    left_join(distinct(gbd, region, country))

  # Calculate country coefficients
  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
    mutate(
      internet = b_internet_time + r_region__internet + r_country__internet,
      outcome = {{beta}} + {{r_region}} + {{r_country}}
    ) %>% 
    group_by(country, region) %>% 
    median_qi(internet, outcome)

  # Create country ellipse data
  country_ellipse <- spread_draws(
    fit,
    {{beta}}, 
    b_internet_time,
    {{sd_country}},
    sd_country__internet_time,
    {{cor_country}}, 
    ndraws = 100
  ) %>% 
    rename(
      cor = {{cor_country}}, 
      sd_outcome = {{sd_country}},
      sd_i = sd_country__internet_time,
      b_outcome = {{beta}},
      b_i = b_internet_time
    ) %>% 
    mutate(
      e = pmap(
        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
        function(cor, sd_a, sd_i, b_a, b_i) 
          ellipse(
            cor, 
            scale = c(sd_i, sd_outcome), 
            centre = c(b_i, b_outcome), 
            level = .90
          ) %>% 
          as_tibble()
      )
    ) %>% 
    unnest(e)

  # Correlation
  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
    median_qi(.width = .90) %>% 
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}

  # Plot
  country_coefs %>% 
    ggplot(aes(internet, outcome)) +
    geom_path(
      data = country_ellipse,
      aes(x = x, y = y), 
      alpha = .2, size = .1, col = "dodgerblue1"
    ) +
    geom_vline(xintercept = 0, lty = 2, size = .2) +
    geom_hline(yintercept = 0, lty = 2, size = .2) +
    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
    scale_x_continuous(
      "Internet trend",
      breaks = pretty_breaks()
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    ) +
    annotate(
      "text",
      x = Inf, y = Inf, label = country_cor_result,
      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
      family = Font
    )
}
```

```{r}
p_cor_country_anx <- draw_scatterplot(
  fit_anx, 
  b_Anxiety_time, 
  r_region__Anxiety, 
  r_country__Anxiety,
  sd_country__Anxiety_time,
  cor_country__internet_time__Anxiety_time
) + labs(y = "Anxiety trend")
p_cor_country_dep <- draw_scatterplot(
  fit_dep, 
  b_Depression_time, 
  r_region__Depression, 
  r_country__Depression,
  sd_country__Depression_time,
  cor_country__internet_time__Depression_time
) + labs(y = "Depression trend")
p_cor_country_sel <- draw_scatterplot(
  fit_sel, 
  b_Selfharm_time, 
  r_region__Selfharm, 
  r_country__Selfharm,
  sd_country__Selfharm_time,
  cor_country__internet_time__Selfharm_time
) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- (p_cor_country_anx |
  p_cor_country_dep |
  p_cor_country_sel) &
  # Transform to rate in 100k
  scale_y_continuous(labels = function(x) x*1000)

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_time_main_correlations

p_time_main_coefs /
  p_time_main_correlations
```

```{r time-correlation-depression}
# Get average and region
r_region_depression <- fit_dep %>% 
  spread_draws(
    b_Depression_time, 
    b_internet_time,
    r_region__Depression[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_depression <- fit_dep %>% 
  spread_draws(
    r_country__Depression[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_dep$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_depression <- left_join(r_country_depression, r_region_depression) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    depression = b_Depression_time + r_region__Depression + r_country__Depression
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, depression)

country_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_country__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_depression_ellipse <- spread_draws(
  fit_dep,
  b_Depression_time, b_internet_time,
  cor_region__internet_time__Depression_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Depression_time, 
        y = b_internet_time, 
        z = b_Depression_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_depression_cor <- fit_dep %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Depression_time",
      "cor_region__internet_time__Depression_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_depression_result <- country_depression_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_dep <- country_depression %>% 
  ggplot(aes(internet, depression)) +
  # geom_path(
  #   data = region_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_depression_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear depression trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_depression_result %>% 
      filter(variable == "cor_country__internet_time__Depression_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r time-correlation-selfharm}
# Get average and region
r_region_selfharm <- fit_sel %>% 
  spread_draws(
    b_Selfharm_time, 
    b_internet_time,
    r_region__Selfharm[region, term],
    r_region__internet[region, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by replacing dot with line break
  mutate(region = str_replace(region, "\\.", "\n"))

# Then country
r_country_selfharm <- fit_sel %>% 
  spread_draws(
    r_country__Selfharm[country, term],
    r_country__internet[country, term]
  ) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  # Fix names by taking labels from original names
  mutate(
    country = factor(
      country, 
      labels = sort(unique(fit_sel$data$country))
    )
  ) %>% 
  left_join(distinct(gbd, region, country))

# Calculate country coefficients
country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
  mutate(
    internet = b_internet_time + r_region__internet + r_country__internet,
    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
  ) %>% 
  group_by(country, region) %>% 
  median_qi(internet, selfharm)

country_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_country__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_country__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

region_selfharm_ellipse <- spread_draws(
  fit_sel,
  b_Selfharm_time, b_internet_time,
  cor_region__internet_time__Selfharm_time, 
  ndraws = 100
) %>% 
  mutate(
    e = pmap(
      list(
        x = cor_region__internet_time__Selfharm_time, 
        y = b_internet_time, 
        z = b_Selfharm_time
      ), 
      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
        as_tibble()
    )
  ) %>% 
  unnest(e)

country_selfharm_cor <- fit_sel %>%
  as_draws_df(
    variable = c(
      "cor_country__internet_time__Selfharm_time",
      "cor_region__internet_time__Selfharm_time"
    ),
    regex = TRUE
  ) %>% 
  as_tibble()
country_selfharm_result <- country_selfharm_cor %>%   
  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))

p_cor_country_sel <- country_selfharm %>% 
  ggplot(aes(internet, selfharm)) +
  # geom_path(
  #   data = region_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
  # ) +
  # geom_path(
  #   data = country_selfharm_ellipse, 
  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
  # ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
  scale_x_continuous(
    "Linear internet trend",
    breaks = pretty_breaks()
  ) +
  scale_y_continuous(
    "Linear selfharm trend",
    breaks = pretty_breaks()
  ) +
  geom_richtext(
    data = country_selfharm_result %>% 
      filter(variable == "cor_country__internet_time__Selfharm_time"),
    aes(x = -Inf, y = Inf, label = result),
    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  ) +
  theme(aspect.ratio = 1)
```

```{r}
p_cor_country_anx + theme(axis.title.x = element_blank()) | 
  p_cor_country_dep | 
  p_cor_country_sel + theme(axis.title.x = element_blank())
```

##### Time: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time * sex + time * age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-depression-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = gbd_10,
  file = "output/brm-gbd-time-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_time_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 2) %>% 
  kable_minimal(full_width = FALSE)
```

Model comparison using waic shows that interactive model is favored across the board.

```{r eval = FALSE}
waics <- left_join(
  rename(fits_brm_time_main, fit_main = fit),
  rename(fits_brm_time_interactions, fit_intr = fit)
) %>% 
  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
waics$waic[[3]]
```

Show main effects

Plot fixed effects and by demographic

```{r}
# Fixed effects parameters
fixed_effects <- fits_brm_time_interactions %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_brm_time_interactions %>% 
  mutate(
    out = map2(
      fit, outcome,
      ~emtrends(
        .x, 
        var = "time", 
        by = c("sex", "age"), 
        resp = .y
      ) %>% 
        parameters() %>% 
        as.data.frame()
    )
  )
fixed_effects_demographics %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

# Random effects parameters
random_effects <- fits_lmer %>% 
  mutate(
    coef_region = map(
      fit, 
      ~bind_rows(
        coef(.x)$region %>% 
          as.data.frame() %>% 
          rownames_to_column("region"),
        coef(.x)$country %>% 
          as.data.frame() %>% 
          rownames_to_column("country"),
        .id = "cluster"
      ) %>% 
        mutate(cluster = factor(cluster, labels = c("region", "country")))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(coef_region) %>% 
  mutate(Type = "Effects") %>%
  select(-`(Int      ,nc ercept)`)

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

```{r}
library(modelbased)
x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
tmp <- fits_brm %>% 
  mutate(
    # Average effect
    avg = map2(
      fit, 
      Outcome, 
      ~hypothesis(.x, str_glue("{.y}_time = 0"))
    ),
    # By country effect
    by_country = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "country"
      )
    ),
    # By region effect
    by_region = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "region"
      )
    )
  ) %>% 
  select(-fit)

tmp %>% 
  select(Outcome, avg) %>% 
  mutate(avg = map(avg, ))

tmp$by_region[[1]] %>% str

h <- paste(
  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
  "= 0"
)

# Prepare average samples
time_avg <- hypothesis(fit_gbd_time, h)
time_avg_samples <- time_avg$samples
names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
time_avg_samples <- time_avg_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  mutate(region = "Average")

# Prepare region samples
time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
time_region_samples <- time_region$samples
names(time_region_samples) <- paste(
  time_region$hypothesis$Hypothesis, 
  time_region$hypothesis$Group, sep = ":"
)
time_region_samples <- time_region_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  separate(Parameter, c("Parameter", "region"), sep = ":")

# Prepare country point estimates
time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
time_country_hypothesis <- time_country$hypothesis %>% 
  rename(country = Group, Parameter = Hypothesis)
time_country_hypothesis <- left_join(
  time_country_hypothesis, 
  distinct(fit_gbd_time$data, country, region)
)

time_sum <- bind_rows(
  time_region$hypothesis,
  time_avg$hypothesis %>% mutate(Group = "Average")
) %>% 
  as_tibble() %>% 
  rename(region = Group, Parameter = Hypothesis)

bind_rows(
  time_region_samples,
  time_avg_samples
) %>% 
  mutate(region = fct_relevel(region, "Average")) %>% 
  mutate(Average = region == "Average") %>% 
  ggplot(aes(value/10, region)) +
  scale_y_discrete(
    expand = expansion(c(0.025, 0.075)),
    labels = function(x) ifelse(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Estimated yearly change",
    breaks = pretty_breaks(5)
  ) +
  scale_alpha_manual(values = c(.5, 1)) +
  geom_vline(xintercept = 0, size = .2, alpha = .25) +
  stat_eye(
    side = "top",
    aes(col = region, fill = region, alpha = Average),
    point_interval = NULL,
    normalize = "panels", 
    height = .75
  ) +
  geom_pointrangeh(
    data = time_sum,
    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
    size = .3, fatten = 1.4
  ) +
  geom_point(
    data = time_country_hypothesis,
    aes(col = region, x = Estimate/10), 
    size = .5,
    alpha = .25,
    position = position_nudge(y = -.05)
  ) +
  facet_wrap(
    "Parameter", ncol = 3, scales = "free_x",
    labeller = as_labeller(
      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
  ) +
  theme(
    axis.text.y = element_markdown(),
    legend.position = "none",
    axis.title.y = element_blank()
  )
ggsave(
  "output/Fig-brm-time-forest.png", 
  device = agg_png,
  height = 1200, width = 3200, res = 300, units = "px"
)
```

### 2021-11-15 04-internet.Rmd
Split analysis to separate documents

# Internet as predictor

```{r packages}
#| results: 'hide'
# Packages

```

##### Internet: Main effects

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + i1_cw + i1_cb +
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + i1_cw + i1_cb +
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + i1_cw + i1_cb + 
    (1 + time + sex + age + i1_cw |c| country) +
    (1 + time + sex + age + i1_cw |r| region),
  family = gaussian()
)

# Fit models in background (need 12 cores)
fit_anx <- brm(
  bf_anx,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-anxiety",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_dep,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-depression",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_sel,
  data = gbd_10,
  file = "output/brm-gbd-time-internet-selfharm",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_internet_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_internet_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

###### Fitted lines

Plot of fitted lines

```{r}
draws_country_anx <- epred_draws(
  fit_anx, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_anx$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 100,
  resp = "Anxiety"
)

draws_country_dep <- epred_draws(
  fit_dep, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_dep$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 30,
  resp = "Depression"
)

draws_country_sel <- epred_draws(
  fit_sel, 
  gbd_wide %>% 
    filter(country %in% sort(unique(fit_sel$data$country))) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region) + 
    (1 + time + sex + age + i1_cw |c| country), 
  ndraws = 30,
  resp = "Selfharm"
)

draws_region_anx <- epred_draws(
  fit_anx, 
  distinct(fit_anx$data, region, sex, age, i1_cb) %>% 
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Anxiety"
) %>% 
  mutate(outcome = "Anxiety")

draws_region_dep <- epred_draws(
  fit_dep, 
  distinct(fit_dep$data, region, sex, age, i1_cb) %>%
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Depression"
) %>% 
  mutate(outcome = "Depression")

draws_region_sel <- epred_draws(
  fit_sel, 
  distinct(fit_sel$data, region, sex, age, i1_cb) %>% 
    group_by(region) %>% 
    mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
    crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
    mutate(time = 0),
  re_formula = ~(1 + time + sex + age + i1_cw |r| region),
  ndraws = 30,
  resp = "Selfharm"
) %>% 
  mutate(outcome = "Self-harm")

draws_region <- bind_rows(
  draws_region_anx, draws_region_dep, draws_region_sel
) %>% 
  group_by(outcome, region, i1_cw) %>% 
  median_qi(.epred)

bind_rows(
  draws_country_anx %>% mutate(outcome = "Anxiety"),
  draws_country_dep %>% mutate(outcome = "Depression"),
  draws_country_sel %>% mutate(outcome = "Self-harm")
) %>% 
  group_by(country) %>% 
  # mutate(i1_cw2 = i1_cw/10 + mean(internet, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot(aes(i1_cw, .epred)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = pretty_breaks(3),
    labels = function(x) percent(x/10, 1)
  ) +
  scale_y_continuous(
    "Estimated rate",
    breaks = pretty_breaks()
  ) +
  geom_ribbon(
    data = draws_region,
    aes(ymin = .lower, ymax = .upper),
    fill = "dodgerblue4", size = .6, alpha = .2
  ) +
  geom_line(
    data = draws_region,
    col = "dodgerblue4", size = .6
  ) +
  stat_summary(
    fun=mean, geom = "line",
    aes(group = country), 
    size = .4, alpha = .25, col = "dodgerblue1"
  ) +
  facet_grid(outcome~region, scales = "free_y") +
  theme(panel.spacing = unit(2, "pt"))
```

###### Forest plots

figure of coefficients forest plot

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_i1_cw, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_i1_cw, r_region__Depression[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_i1_cw, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Estimated association to internet adoption", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", height = .75
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

##### Internet: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time*sex + time*age + i1_cw*sex + i1_cw*age + i1_cb + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country) +
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_anx,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_dep,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-depression-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_sel,
  data = gbd_wide,
  file = "output/brm-gbd-time-internet-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  refresh = hmc$refresh,
  control = list(adapt_delta = hmc$d)
)
fits_brm_internet_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

Coefficients

```{r}
fits_brm_internet_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Model comparisons

```{r}
tmp <- left_join(
  fits_brm_internet_main,
  fits_brm_internet_interactions %>% rename(fit_i = fit)
) %>% 
  mutate(comp = map2(fit, fit_i, waic))

```

###### Forest plots

figure of coefficients forest plot

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .5,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, -.025)
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

Between country?

```{r}
pred_data <- gbd_wide %>% 
  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
  filter(country %in% sort(unique(fit_anx$data$country)))

tmp <- epred_draws(
  fit_anx, pred_data, re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
)

tmp %>% 
  group_by(region, country, i1_cb) %>% 
  summarise(mean(.epred))

conditional_effects(fit_anx, "i1_cb")

gbd_wide %>% 
  group_by(country) %>% 
  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
  ggplot(aes(i1_cb, anx)) +
  geom_point() +
  stat_smooth()

filter(country %in% sort(unique(fit_anx$data$country))) %>% 
  mutate(time = 0) %>% 
  group_by(country) %>% 
  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
  filter(i1_cw %in% c(xmin, xmax)) %>% 
  ungroup()
```

Sex and Age

```{r}
# Get some stuff and transform :)
get_draws <- function(fit) {
  draws_region <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
    r_region[region, term] | term
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
      Age = `age1:i1_cw` + `b_age1:i1_cw`,
      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
    ) %>% 
    select(region, `15 to 19`:Sex)

  draws_avg <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
      Age = `b_age1:i1_cw`,
      Sex = `b_sex1:i1_cw`
    ) %>% 
    mutate(region = "**Average**") %>% 
    select(region, `15 to 19`:Sex)

  draws <- bind_rows(
    "regions" = draws_region,
    "average" = draws_avg, 
    .id = "Level"
  ) %>% 
    mutate(region = str_replace(region, "\\.", "\n")) %>% 
    ungroup()
  draws
}

draws <- bind_rows(
  "Anxiety" = get_draws(fit_anx),
  "Depression" = get_draws(fit_dep),
  "Selfharm" = get_draws(fit_sel),
  .id = "outcome"
)

draws_sum <- draws %>% 
  select(outcome, region, Age, Sex) %>% 
  group_by(outcome, region) %>% 
  summarise(
    describe_posterior(
      cur_data(), centrality = "mean", test = "pd"
    )
  ) %>% 
  rename(panel = Parameter) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))

draws %>% 
  select(outcome, Level, region, `15 to 19`:Male) %>% 
  pivot_longer(-c(region, Level, outcome), names_to = "Group") %>% 
  mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
  mutate(
    side = if_else(Group %in% c("15 to 19", "Female"), "top", "bottom")
  ) %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = fct_relevel(region, "**Average**")) %>% 
  ggplot(aes(value, region, col = Group, fill = Group)) +
  scale_alpha_manual(values = c(.6, .3)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(
    values = c(21, 19), guide = "none"
    ) +
  scale_y_discrete(expand = expansion(c(0.1, 0.1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(0, .05))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5,
    aes(side = side, group = side, alpha = Level), 
    show.legend = FALSE
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .33,
    point_size = 1.25,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
    position = position_dodgev(.25), key_glyph = draw_key_point
  ) +
  geom_richtext(
    data = draws_sum %>% 
      mutate(Group = NA) %>% 
      filter(outcome %in% c("Anxiety", "Depression", "Selfharm")),
    aes(
      x = Inf, 
      label = str_glue("*d* = {Mean} (p<sup>d</sup> = {percent(pd, 1)})")
    ),
    size = 2.5, hjust = 1,
    family = Font,
    fill = NA, label.color = NA,
    show.legend = FALSE
  ) +
  facet_grid2(panel ~ outcome, scales = "free_x", axes = "x") +
  guides(
    alpha = "none"
  ) +
  theme(
    legend.position = "right",
    axis.title.y = element_blank(),
    axis.text.y = element_markdown()
  )
```

###### Fitted lines

Plot of fitted lines

```{r}
# Prediction dataframe: Min and max vals are enough for line
pred_data <- gbd_wide %>% 
  filter(country %in% sort(unique(fit_anx$data$country))) %>% 
  mutate(time = 0) %>% 
  group_by(country) %>% 
  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
  filter(i1_cw %in% c(xmin, xmax)) %>% 
  ungroup()
draws_country_anx <- epred_draws(
  fit_anx, 
  pred_data,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
  ndraws = 100,
  resp = "Anxiety"
)

draws_country_dep <- epred_draws(
  fit_dep, 
  pred_data,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
  ndraws = 100,
  resp = "Depression"
)

draws_country_sel <- epred_draws(
  fit_sel, 
  pred_data,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
  ndraws = 100,
  resp = "Selfharm"
)

pred_data_region <- pred_data %>% 
  distinct(region, sex, age, i1_cb) %>% 
  group_by(region) %>% 
  mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
  crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
  mutate(time = 0)

draws_region_anx <- epred_draws(
  fit_anx, 
  pred_data_region,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  ndraws = 100,
  resp = "Anxiety"
) %>% 
  mutate(outcome = "Anxiety")

draws_region_dep <- epred_draws(
  fit_dep, 
  pred_data_region,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  ndraws = 100,
  resp = "Depression"
) %>% 
  mutate(outcome = "Depression")

draws_region_sel <- epred_draws(
  fit_sel, 
  pred_data_region,
  re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
  ndraws = 100,
  resp = "Selfharm"
) %>% 
  mutate(outcome = "Self-harm")

means_country <- bind_rows(
  draws_country_anx %>% mutate(outcome = "Anxiety"),
  draws_country_dep %>% mutate(outcome = "Depression"),
  draws_country_sel %>% mutate(outcome = "Self-harm")
) %>% 
  group_by(outcome, region, country, i1_cw) %>% 
  summarise(.epred = mean(.epred))

means_region <- bind_rows(
  draws_region_anx, draws_region_dep, draws_region_sel
) %>% 
  group_by(outcome, region, i1_cw) %>% 
  mean_qi(.epred, .width = .9)

means_region <- pseudo_gwp %>% 
  distinct(region, outcome=cause) %>% 
  bind_rows(means_region) %>% 
  mutate(outcome = fct_inorder(factor(outcome)))

pseudo_gwp %>% 
  distinct(region, outcome=cause) %>% 
  bind_rows(means_country) %>% 
  mutate(outcome = fct_inorder(factor(outcome))) %>% 
  ggplot(aes(i1_cw, .epred)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = c(-3.5, 0, 3.5),
    labels = function(x) percent(x/10, 1)
  ) +
  scale_y_continuous(
    "Estimated rate or scale score",
    breaks = pretty_breaks()
  ) +
  geom_blank() +
  geom_ribbon(
    data = means_region,
    aes(ymin = .lower, ymax = .upper),
    alpha = .15, fill = "dodgerblue4"
  ) +
  geom_line(
    data = means_region,
    col = "dodgerblue4", size = .6
  ) +
  geom_line(
    aes(group = country), 
    size = .4, alpha = .35, col = "dodgerblue1"
  ) +
  # geom_text(
  #   data = bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  #     group_by(outcome) %>% 
  #     summarise(parameters(cur_data()[-c(1:3)])) %>% 
  #     mutate(region = str_replace(Parameter, "\\.", "\n")) %>% 
  #     mutate(outcome = if_else(outcome=="Selfharm", "Self-harm", outcome)) %>% 
  #     filter(region != "Average") %>% 
  #     mutate(across(where(is.numeric), ~round(., 2))),
  #   aes(x = -Inf, y = Inf, label = str_glue("{Median}\n[{CI_low}, {CI_high}]")),
  #   col = "dodgerblue4", size = 2, vjust = 1.1, hjust = -0.1, family = Font
  # ) +
facet_grid(outcome~region, scales = "free_y") +
  theme(panel.spacing = unit(2, "pt"))
```

### 2021-11-15 01-clean.Rmd
Add GBD data

@@
 
-# Create directory for intermediate files
+# Create directory for output files (e.g. plots)
 dir.create("output", FALSE)
+
+# Create directory for intermediate data
+dir.create("data", FALSE)
 ```
@@
 
-The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/gbd-2021-11-02/`.
+The Global Burden of Disease data were downloaded from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
+We include those files in the repository as (permitted by the license](http://ghdx.healthdata.org/):
+
+>"Data made available for download by IHME can be used, shared, modified, or built upon by non-commercial users via the Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International License.
+Please refer to our terms and conditions for additional details."
+
 We selected the relevant locations, age groups, years, and causes from the data tool as detailed in the manuscript.
@@
 gbd <- list.files(
-  "data-raw/GBD/gbd-2021-11-02/", 
+  "data-raw/GBD/", 
   pattern = ".zip", full.names = TRUE, recursive = TRUE
@@
 gbd <- left_join(gbd, itu)
+```
 
-# Contrast code sex
-gbd$sex <- factor(gbd$sex)
-contrasts(gbd$sex) <- c(-.5, .5)
+Our primary analysis is about young people but we also look at older groups for supplemental comparison, so we split data here.
 
-# Focus on young people
+```{r}
 gbd_all <- gbd
 gbd <- gbd %>% 
-  filter(age %in% c("15 to 19", "20 to 24"))
-
-# Contrast code binary age in young data set
-gbd$age <- factor(gbd$age)
-contrasts(gbd$age) <- c(-.5, .5)
-
-# Young data in wide format
-gbd_wide <- gbd %>%
-  pivot_wider(names_from = cause, values_from = c(val, se))
-names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
-
-# Transform edge proportions to fit beta distribution
-gbd_10 <- gbd_wide %>% 
-  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999999, internet))
+  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
 ```
 
-We also save a synthetic version of this dataset to better enable others to reproduce our analytical procedures:
+We also save a synthetic version of the gwp dataset to better enable others to reproduce our analytical procedures:
 
@@
 We then save the tables for later use in `data/`.
+
+```{r}
+write_rds(gbd, "data/gbd.rds")
+write_rds(gbd_all, "data/gbd_all_ages.rds")
+write_rds(itu, "data/itu.rds")
+```

### 2021-11-15 index.Rmd
clean yaml

@@
 ---
-title: "Global study of well-being and internet adoption | Online analysis supplement"
+title: Global study of well-being and internet adoption | Online analysis supplement
 description: |
   Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
-author: "<a href='https://vuorre.netlify.app'>Matti Vuorre</a> & Andy Przybylski"
+author: Matti Vuorre & Andy Przybylski
 date: "`r Sys.Date()`"
@@
 ---
+
+# Preface
 

### 2021-11-15 _lme4-time.Rmd
save lmer code

--- 2021-11-15 03-time.Rmd
@@
-# Time trends
+This script implements the 3-way interactive time model with lme4.
 
-```{r packages}
-#| results: 'hide'
-# Packages
-library(ggtext)
-library(brms)
-library(ellipse)
-library(broom.mixed)
-library(scales)
-library(ggh4x)
-library(tidybayes)
-library(ggdist)
-library(parameters)
-library(lme4)
-library(emmeans)
-library(patchwork)
-library(bayestestR)
-library(lubridate)
-library(broom)
-library(kableExtra)
-library(ggstance)
-library(tidyverse)
-
-# MCMC settings
-options(brms.backend = "cmdstanr")
-hmc <- list(iter = 2250, warmup = 1000, refresh = 50, d = .9)
-# Run this to delete fitted models and refit
-# unlink(list.files(pattern = "output/brm-.*\\.rds"))
-```
-
-## Model 1: Temporal trends
-
-We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.
-
-We first fit the models using lme4 because they are big and therefore would be very slow with brms.
-
-### GBD
+Takes several hours.
 
@@
 ```{r fit-gbd-time-lme4}
-# These take about 5-20 minutes each
-# run in parallel in background jobs
+# run in parallel in background jobs using job()
 # recommended to conduct this in interactive mode (rstudio)
@@
 ```
-
-#### brms
-
-correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
-
-note we use beta so transform edge values
-
-we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
-
-##### Time: Main effects
-
-We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
-
-$$
-\begin{align*}
-y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\
-
-\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
-\beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\
-
-i_{i[c][r]} &\sim 
-\text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\
-
-\mu^i_{i[c][r]} &= \text{logit}(
-\beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
-\beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\
-
-\left[\begin{array}{c}
-\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
-\end{array}\right] 
-&\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^c
-),
-
-\left[\begin{array}{c}
-\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
-\end{array}\right] 
-\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^r
-)
-\end{align*}
-$$
-
-```{r}
-# Define a model of internet proportion over time
-bf_int <- bf(
-  internet ~ 1 + time + 
-    (1 + time |c| country) +
-    (1 + time |r| region), 
-  family = Beta()
-)
-
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-anxiety",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-depression",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-selfharm",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fits_brm_time_main <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-```
-
-Coefficients
-
-```{r}
-fits_brm_time_main %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000
-
-```{r}
-tmp_pars <- fits_brm_time_main %>% 
-  mutate(
-    out = map2(
-      fit, 
-      outcome,
-      ~hypothesis(
-        .x, 
-        c(str_glue("{.y}_time = 0")),
-        scope = "coef",
-        group = "region"
-      )$hypothesis
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # Internet trend is estimated in all models--keep first
-  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
-  # Transform back to rates in 100k
-  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
-  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
-  select(cause = Hypothesis, region = Group, result) %>% 
-  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))
-
-p_vars +
-  geom_richtext(
-    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
-    aes(x = make_date(2000), y = Inf, label = result),
-    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  )
-ggsave(
-  "output/Fig-vars-timeseries-estimates.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-A figure of coefficients
-
-```{r}
-anx_draws <- spread_draws(
-  fit_anx, 
-  b_Anxiety_time, r_region__Anxiety[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Anxiety_time) %>% 
-  mutate(outcome = "Anxiety")
-dep_draws <- spread_draws(
-  fit_dep, 
-  b_Depression_time, r_region__Depression[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Depression_time) %>% 
-  mutate(outcome = "Depression")
-sel_draws <- spread_draws(
-  fit_sel, 
-  b_Selfharm_time, r_region__Selfharm[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Selfharm_time) %>% 
-  mutate(outcome = "Selfharm")
-
-p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
-  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
-  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
-  mutate(region = fct_relevel(factor(region), "Average")) %>% 
-  mutate(outcome = factor(outcome)) %>% 
-  mutate(is_average = region == "Average") %>% 
-  mutate(region = str_replace(region, "\\.", " ")) %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.5, .9)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels"
-  ) +
-  facet_wrap("outcome", nrow = 1, scales = "free_x") +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-p_time_main_coefs
-```
-
-###### Correlations
-
-Calculate country coefficients and show scatterplots
-
-```{r time-correlation-anxiety}
-# Function to wrangle draws at multiple levels and create scatterplots + ellipses
-draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
-  # Get average and region-specific slopes
-  r_region_draws <- fit %>% 
-    spread_draws(
-      {{beta}}, 
-      b_internet_time,
-      {{r_region}}[region, term],
-      r_region__internet[region, term]
-    ) %>% 
-    filter(term == "time") %>% 
-    ungroup() %>% 
-    # Fix names by replacing dot with line break
-    mutate(region = str_replace(region, "\\.", "\n"))
-
-  # Then country
-  r_country_draws <- fit %>% 
-    spread_draws(
-      {{r_country}}[country, term],
-      r_country__internet[country, term]
-    ) %>% 
-    filter(term == "time") %>% 
-    ungroup() %>% 
-    # Fix names by taking labels from original names
-    mutate(
-      country = factor(
-        country, 
-        labels = sort(unique(fit$data$country))
-      )
-    ) %>% 
-    left_join(distinct(gbd, region, country))
-
-  # Calculate country coefficients
-  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
-    mutate(
-      internet = b_internet_time + r_region__internet + r_country__internet,
-      outcome = {{beta}} + {{r_region}} + {{r_country}}
-    ) %>% 
-    group_by(country, region) %>% 
-    median_qi(internet, outcome)
-
-  # Create country ellipse data
-  country_ellipse <- spread_draws(
-    fit,
-    {{beta}}, 
-    b_internet_time,
-    {{sd_country}},
-    sd_country__internet_time,
-    {{cor_country}}, 
-    ndraws = 100
-  ) %>% 
-    rename(
-      cor = {{cor_country}}, 
-      sd_outcome = {{sd_country}},
-      sd_i = sd_country__internet_time,
-      b_outcome = {{beta}},
-      b_i = b_internet_time
-    ) %>% 
-    mutate(
-      e = pmap(
-        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
-        function(cor, sd_a, sd_i, b_a, b_i) 
-          ellipse(
-            cor, 
-            scale = c(sd_i, sd_outcome), 
-            centre = c(b_i, b_outcome), 
-            level = .90
-          ) %>% 
-          as_tibble()
-      )
-    ) %>% 
-    unnest(e)
-
-  # Correlation
-  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
-    median_qi(.width = .90) %>% 
-    mutate(across(where(is.numeric), ~round(., 2))) %>%
-    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}
-
-  # Plot
-  country_coefs %>% 
-    ggplot(aes(internet, outcome)) +
-    geom_path(
-      data = country_ellipse,
-      aes(x = x, y = y), 
-      alpha = .2, size = .1, col = "dodgerblue1"
-    ) +
-    geom_vline(xintercept = 0, lty = 2, size = .2) +
-    geom_hline(yintercept = 0, lty = 2, size = .2) +
-    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-    scale_x_continuous(
-      "Internet trend",
-      breaks = pretty_breaks()
-    ) +
-    scale_y_continuous(
-      breaks = pretty_breaks()
-    ) +
-    annotate(
-      "text",
-      x = Inf, y = Inf, label = country_cor_result,
-      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
-      family = Font
-    )
-}
-```
-
-```{r}
-p_cor_country_anx <- draw_scatterplot(
-  fit_anx, 
-  b_Anxiety_time, 
-  r_region__Anxiety, 
-  r_country__Anxiety,
-  sd_country__Anxiety_time,
-  cor_country__internet_time__Anxiety_time
-) + labs(y = "Anxiety trend")
-p_cor_country_dep <- draw_scatterplot(
-  fit_dep, 
-  b_Depression_time, 
-  r_region__Depression, 
-  r_country__Depression,
-  sd_country__Depression_time,
-  cor_country__internet_time__Depression_time
-) + labs(y = "Depression trend")
-p_cor_country_sel <- draw_scatterplot(
-  fit_sel, 
-  b_Selfharm_time, 
-  r_region__Selfharm, 
-  r_country__Selfharm,
-  sd_country__Selfharm_time,
-  cor_country__internet_time__Selfharm_time
-) + labs(y = "Self-harm trend")
-```
-
-```{r}
-p_time_main_correlations <- (p_cor_country_anx |
-  p_cor_country_dep |
-  p_cor_country_sel) &
-  # Transform to rate in 100k
-  scale_y_continuous(labels = function(x) x*1000)
-
-(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
-    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
-    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  p_time_main_correlations
-
-p_time_main_coefs /
-  p_time_main_correlations
-```
-
-```{r time-correlation-depression}
-# Get average and region
-r_region_depression <- fit_dep %>% 
-  spread_draws(
-    b_Depression_time, 
-    b_internet_time,
-    r_region__Depression[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_depression <- fit_dep %>% 
-  spread_draws(
-    r_country__Depression[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_dep$data$country))
-    )
-  ) %>% 
-  left_join(distinct(gbd, region, country))
-
-# Calculate country coefficients
-country_depression <- left_join(r_country_depression, r_region_depression) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    depression = b_Depression_time + r_region__Depression + r_country__Depression
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, depression)
-
-country_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_country__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_region__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_depression_cor <- fit_dep %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Depression_time",
-      "cor_region__internet_time__Depression_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_depression_result <- country_depression_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_dep <- country_depression %>% 
-  ggplot(aes(internet, depression)) +
-  # geom_path(
-  #   data = region_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear depression trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_depression_result %>% 
-      filter(variable == "cor_country__internet_time__Depression_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r time-correlation-selfharm}
-# Get average and region
-r_region_selfharm <- fit_sel %>% 
-  spread_draws(
-    b_Selfharm_time, 
-    b_internet_time,
-    r_region__Selfharm[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_selfharm <- fit_sel %>% 
-  spread_draws(
-    r_country__Selfharm[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_sel$data$country))
-    )
-  ) %>% 
-  left_join(distinct(gbd, region, country))
-
-# Calculate country coefficients
-country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, selfharm)
-
-country_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_country__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_region__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_selfharm_cor <- fit_sel %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Selfharm_time",
-      "cor_region__internet_time__Selfharm_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_selfharm_result <- country_selfharm_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_sel <- country_selfharm %>% 
-  ggplot(aes(internet, selfharm)) +
-  # geom_path(
-  #   data = region_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear selfharm trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_selfharm_result %>% 
-      filter(variable == "cor_country__internet_time__Selfharm_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r}
-p_cor_country_anx + theme(axis.title.x = element_blank()) | 
-  p_cor_country_dep | 
-  p_cor_country_sel + theme(axis.title.x = element_blank())
-```
-
-##### Time: Interactions
-
-```{r}
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time * sex + time * age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-anxiety-int2",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-depression-int2",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
-  file = "output/brm-gbd-time-selfharm-int2",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
-  control = list(adapt_delta = hmc$d)
-)
-fits_brm_time_interactions <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-```
-
-Coefficients
-
-```{r}
-fits_brm_time_interactions %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 2) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Model comparison using waic shows that interactive model is favored across the board.
-
-```{r eval = FALSE}
-waics <- left_join(
-  rename(fits_brm_time_main, fit_main = fit),
-  rename(fits_brm_time_interactions, fit_intr = fit)
-) %>% 
-  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
-waics$waic[[3]]
-```
-
-Show main effects
-
-Plot fixed effects and by demographic
-
-```{r}
-# Fixed effects parameters
-fixed_effects <- fits_brm_time_interactions %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  filter(
-    Effects == "fixed", 
-    Parameter != "(Intercept)"
-  ) 
-# Fixed effects per demographic
-fixed_effects_demographics <- fits_brm_time_interactions %>% 
-  mutate(
-    out = map2(
-      fit, outcome,
-      ~emtrends(
-        .x, 
-        var = "time", 
-        by = c("sex", "age"), 
-        resp = .y
-      ) %>% 
-        parameters() %>% 
-        as.data.frame()
-    )
-  )
-fixed_effects_demographics %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  mutate(Parameter = str_glue("{sex}\n({age})"))
-
-# Random effects parameters
-random_effects <- fits_lmer %>% 
-  mutate(
-    coef_region = map(
-      fit, 
-      ~bind_rows(
-        coef(.x)$region %>% 
-          as.data.frame() %>% 
-          rownames_to_column("region"),
-        coef(.x)$country %>% 
-          as.data.frame() %>% 
-          rownames_to_column("country"),
-        .id = "cluster"
-      ) %>% 
-        mutate(cluster = factor(cluster, labels = c("region", "country")))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(coef_region) %>% 
-  mutate(Type = "Effects") %>%
-  select(-`(Int      ,nc ercept)`)
-
-bind_rows(
-  fixed_effects,
-  fixed_effects_demographics, 
-  .id = "Type"
-) %>% 
-  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
-  mutate(Parameter = fct_inorder(Parameter)) %>%
-  mutate(cause = factor(cause)) %>% 
-  rowwise() %>% 
-  mutate(
-    sig = factor(
-      !between(0, CI_low, CI_high), 
-      levels = c(TRUE, FALSE)
-    )
-  ) %>% 
-  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
-  scale_color_discrete(
-    "Outcome"
-  ) +
-  scale_x_continuous(
-    "Estimate (95%CI)"
-  ) +
-  scale_shape_manual(values = c(19, 21)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodge2v(.5),
-    fill = "white", size = .3, fatten = 5
-  ) +
-  guides(shape = "none") +
-  facet_wrap("Type", ncol = 2, scales = "free") +
-  theme(axis.title.y = element_blank())
-```
-
-```{r}
-library(modelbased)
-x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
-tmp <- fits_brm %>% 
-  mutate(
-    # Average effect
-    avg = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(.x, str_glue("{.y}_time = 0"))
-    ),
-    # By country effect
-    by_country = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "country"
-      )
-    ),
-    # By region effect
-    by_region = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "region"
-      )
-    )
-  ) %>% 
-  select(-fit)
-
-tmp %>% 
-  select(Outcome, avg) %>% 
-  mutate(avg = map(avg, ))
-
-tmp$by_region[[1]] %>% str
-
-h <- paste(
-  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
-  "= 0"
-)
-
-# Prepare average samples
-time_avg <- hypothesis(fit_gbd_time, h)
-time_avg_samples <- time_avg$samples
-names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
-time_avg_samples <- time_avg_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  mutate(region = "Average")
-
-# Prepare region samples
-time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
-time_region_samples <- time_region$samples
-names(time_region_samples) <- paste(
-  time_region$hypothesis$Hypothesis, 
-  time_region$hypothesis$Group, sep = ":"
-)
-time_region_samples <- time_region_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  separate(Parameter, c("Parameter", "region"), sep = ":")
-
-# Prepare country point estimates
-time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
-time_country_hypothesis <- time_country$hypothesis %>% 
-  rename(country = Group, Parameter = Hypothesis)
-time_country_hypothesis <- left_join(
-  time_country_hypothesis, 
-  distinct(fit_gbd_time$data, country, region)
-)
-
-time_sum <- bind_rows(
-  time_region$hypothesis,
-  time_avg$hypothesis %>% mutate(Group = "Average")
-) %>% 
-  as_tibble() %>% 
-  rename(region = Group, Parameter = Hypothesis)
-
-bind_rows(
-  time_region_samples,
-  time_avg_samples
-) %>% 
-  mutate(region = fct_relevel(region, "Average")) %>% 
-  mutate(Average = region == "Average") %>% 
-  ggplot(aes(value/10, region)) +
-  scale_y_discrete(
-    expand = expansion(c(0.025, 0.075)),
-    labels = function(x) ifelse(x == "Average", "**Average**", x)
-  ) +
-  scale_x_continuous(
-    "Estimated yearly change",
-    breaks = pretty_breaks(5)
-  ) +
-  scale_alpha_manual(values = c(.5, 1)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .25) +
-  stat_eye(
-    side = "top",
-    aes(col = region, fill = region, alpha = Average),
-    point_interval = NULL,
-    normalize = "panels", 
-    height = .75
-  ) +
-  geom_pointrangeh(
-    data = time_sum,
-    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
-    size = .3, fatten = 1.4
-  ) +
-  geom_point(
-    data = time_country_hypothesis,
-    aes(col = region, x = Estimate/10), 
-    size = .5,
-    alpha = .25,
-    position = position_nudge(y = -.05)
-  ) +
-  facet_wrap(
-    "Parameter", ncol = 3, scales = "free_x",
-    labeller = as_labeller(
-      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
-  ) +
-  theme(
-    axis.text.y = element_markdown(),
-    legend.position = "none",
-    axis.title.y = element_blank()
-  )
-ggsave(
-  "output/Fig-brm-time-forest.png", 
-  device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
-)
-```

### 2021-11-15 01-clean.Rmd
clean analyses

@@
 library(naniar)
+library(scales)
 library(janitor)
@@
 
-## Data cleaning
-
-We downloaded the relevant data from sources to `data-raw/`. We cannot share the data here but indicate below how and when each data table was obtained.
-
-### Global Burden of Disease
+## Global Burden of Disease
 
@@
 
-### Gallup World Poll
+## Gallup World Poll
 
@@
 
-### International Telecommunication Union
+## International Telecommunication Union
 
-The internet adoption data were downloaded from the ITU website in October 2021, and placed with their original file names to `data-raw/ITU/`. The specific URLs for obtaining the data files are
+We first download the data files from the ITU website (in November 2021).
+Note that new versions may be posted subsequent to this, in which case the URLs would change and should then be changed here too to update the analyses with latest data.
 
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/PercentIndividualsUsingInternet.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx>
-- <https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx>
+```{r itu-download}
+# Download data sets from the ITU website if not yet downloaded
+if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
+  dir.create("data-raw/ITU")
+  download.file(
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx", 
+    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
+  )
+  download.file(
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
+    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
+  )
+  download.file(
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
+    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
+  )
+}
+```
 
-We first load, reshape, and merge these datasets.
+We then read and reshape the ITU data
 
-```{r itu-load-clean}
+```{r itu-clean}
 # Read and reshape fixed broadband data
@@
 
-#### Missingness
+### Missingness
 
@@
 
-There are some missing values in the data; in the Internet variable these are mainly in the first or last years of each country's time-series.
-This needs to be changed to calculate by-variable (with appropriate time-spans) when adding mobile and fixed
-
-```{r}
-miss_var_summary(itu)
-```
-
-We then impute missing values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values.
+We then impute missing values to the internet adoption timeseries.
+We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.
 
 ```{r itu-impute}
-itu <- itu %>% 
-  group_by(country) %>% 
-  # Find first and last year with internet data in each country
+# Reshape to easily impute all variables
+itu_long <- itu %>%
+  pivot_longer(c(internet, fixed, mobile))
+
+# Impute by country and variable
+itu_long <- itu_long %>%
+  group_by(country, name) %>% 
+  # Find first and last year with this variable in each country
+  # so as to prevent extrapolation
   mutate(
-    min_year = year[min(which(!is.na(internet)))],
-    max_year = year[max(which(!is.na(internet)))]
+    min_year = year[min(which(!is.na(value)))],
+    max_year = year[max(which(!is.na(value)))]
   ) %>%
@@
   # use possibly() to avoid errors for countries with no data
-  # Add variables to c() to impute for fixed and mobile broadband
   mutate(
     across(
-      c(internet), 
-      possibly(
+      value, 
+      .fns = list(
+        i = possibly(
           function(x) na_interpolation(x, maxgap = Inf), 
-        # If function errors, provide original internet value
-        otherwise = internet
+          otherwise = NaN
+        )
       )
@@
   mutate(
-    internet = if_else(
+    value_i = if_else(
       between(year, unique(min_year), unique(max_year)), 
-      internet, 
+      value_i, 
       NaN
@@
 
-We see that 96 intermediate internet use values were imputed to the time series.
+Here is a summary of how many values were imputed
 
 ```{r}
-miss_var_summary(itu)
+itu_long %>%   
+  group_by(name) %>% 
+  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>% 
+  summarise(
+    n_miss_orig = sum(is.na(value) & year >= min_year),
+    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
+    n_miss_imp = sum(is.na(value_i) & year >= min_year),
+    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
+    imputed = n_miss_orig - n_miss_imp
+  )
 ```
 
-### Complete study dataset
+We then replace the original values with the imputed ones
 
-#### GLOBE regions
+```{r}
+itu <- itu_long %>% 
+  mutate(value = value_i) %>% 
+  select(-value_i) %>% 
+  pivot_wider()
+rm(itu_long)
+```
+
+## GLOBE regions
 
@@
 regions_filled <- read_csv(
-  "data-raw/Regions/GBD-countries-without-region-filled.csv"
+  "data-raw/Regions/ITU-countries-without-region-filled.csv"
 ) 
@@
 
-#### Create predictors
-
-We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.
-
-```{r}
-# For models, we rescale year; centred at 2013 and one unit indicates decade
-itu <- itu %>% 
-  mutate(time = (year - 2013) / 10)
-
-# Create predictor: Lagged effect of 10% increase in internet
-itu <- itu %>% 
-  arrange(country, year) %>% 
-  group_by(country) %>% 
-  mutate(i1 = lag(internet*10, 1)) %>% 
-  ungroup()
-
-# Centering within and between countries
-itu <- itu %>%
-  bmlm::isolate("i1", by = "country", which = "both")
-```
-
-#### Create tables
+## Join tables
 
@@
 
-We also save a synthetic version of the gwp dataset to better enable others to reproduce our analytical procedures:
-
-```{r synth-data-create}
-
-```
-
 ## Save tables

### 2021-11-15 03-time.Rmd
clean analyses

@@
 
+```{r}
+itu <- read_rds("data/itu.rds")
+gbd <- read_rds("data/gbd.rds") # 10 to 24 year olds
+```
+
+## Reshape data for models
+
+### Create predictors
+
+We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.
+
+```{r}
+# For models, year is centred at 
+itu <- itu %>% 
+  mutate(time = (year - 2013) / 10)
+
+# Create predictor: Lagged effect of 10% increase in internet
+itu <- itu %>% 
+  arrange(country, year) %>% 
+  group_by(country) %>% 
+  mutate(i1 = lag(internet*10, 1)) %>% 
+  ungroup()
+
+# Centering within and between countries
+itu %>%
+  bmlm::isolate("i1", by = "country", which = "both")
+
+tibble(
+  id = c(1,1,1,2,2,2,3,3,3),
+  x = c(1,2,3,4,5,6,7,8,9)
+) %>% 
+  bmlm::isolate("x", by = "id", which = "both") %>% 
+  group_by(id) %>% 
+  mutate(x_cb2 = mean(x), x_cw2 = x - x_cb2) %>% 
+  ungroup() %>% 
+  mutate(x_cb2 = x_cb2 - mean(x))
+```
+
+```{r}
+# Contrast code sex
+gbd$sex <- factor(gbd$sex)
+contrasts(gbd$sex) <- c(-.5, .5)
+
+# [todo] set mid age category as reference
+
+# GBD in wide format
+gbd_wide <- gbd %>%
+  pivot_wider(names_from = cause, values_from = c(val, se))
+names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
+
+# Transform edge proportions to fit beta distribution
+gbd_10 <- gbd_wide %>% 
+  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999999, internet))
+```
+
 ## Model 1: Temporal trends
@@
 
-We first fit the models using lme4 because they are big and therefore would be very slow with brms.
-
 ### GBD
-
-#### lme4
-
-```{r fit-gbd-time-lme4}
-# These take about 5-20 minutes each
-# run in parallel in background jobs
-# recommended to conduct this in interactive mode (rstudio)
-file_path <- "output/lme4-gbd-time.rds"
-if (!file.exists(file_path)) {
-  library(job)
-  job({fit_anx <- lmer(
-    Anxiety ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Anxiety time (lmer)")
-  job({fit_dep <- lmer(
-    Depression ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Depression time (lmer)")
-  job({fit_sel <- lmer(
-    Selfharm ~ 1 + time * sex * age + 
-      (1 + time * sex * age | region) +
-      (1 + time * sex * age | country),
-    data = gbd_wide
-  )}, title = "Self harm time (lmer)")
-  fits_lmer <- distinct(gbd, cause) %>% 
-    mutate(fit = list(fit_anx, fit_dep, fit_sel))
-  write_rds(fits_lmer, file_path)
-} else {fits_lmer <- read_rds(file_path)}
-```
-
-Plot fixed effects and by demographic
-
-```{r}
-# Fixed effects parameters
-fixed_effects <- fits_lmer %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  filter(
-    Effects == "fixed", 
-    Parameter != "(Intercept)"
-  ) 
-# Fixed effects per demographic
-fixed_effects_demographics <- fits_lmer %>% 
-  mutate(
-    out = map(
-      fit,
-      ~emtrends(.x, var = "time", by = c("sex", "age")) %>% 
-        parameters() %>% 
-        as.data.frame()
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  mutate(Parameter = str_glue("{sex}\n({age})"))
-
-# Random effects parameters
-random_effects <- fits_lmer %>% 
-  mutate(
-    coef_region = map(
-      fit, 
-      ~bind_rows(
-        coef(.x)$region %>% 
-          as.data.frame() %>% 
-          rownames_to_column("region"),
-        coef(.x)$country %>% 
-          as.data.frame() %>% 
-          rownames_to_column("country"),
-        .id = "cluster"
-      ) %>% 
-        mutate(cluster = factor(cluster, labels = c("region", "country")))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(coef_region) %>% 
-  mutate(Type = "Effects") %>%
-  select(-`(Int      ,nc ercept)`)
-
-bind_rows(
-  fixed_effects,
-  fixed_effects_demographics, 
-  .id = "Type"
-) %>% 
-  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
-  mutate(Parameter = fct_inorder(Parameter)) %>%
-  mutate(cause = factor(cause)) %>% 
-  rowwise() %>% 
-  mutate(
-    sig = factor(
-      !between(0, CI_low, CI_high), 
-      levels = c(TRUE, FALSE)
-    )
-  ) %>% 
-  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
-  scale_color_discrete(
-    "Outcome"
-  ) +
-  scale_x_continuous(
-    "Estimate (95%CI)"
-  ) +
-  scale_shape_manual(values = c(19, 21)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodge2v(.5),
-    fill = "white", size = .3, fatten = 5
-  ) +
-  guides(shape = "none") +
-  facet_wrap("Type", ncol = 2, scales = "free") +
-  theme(axis.title.y = element_blank())
-```
 
@@
 $$
+
+[todo] only pick the itu data for the internet model
 

### 2021-11-15 03-time.Rmd
More edits

@@
 
-## Reshape data for models
-
-### Create predictors
-
-We then create predictors (centered, lagged, rescaled) for models in the ITU dataset.
-
-```{r}
-# For models, year is centred at 
+## Prepare data for models
+
+We prepare the predictors
+- center year on 2019 (last year in outcome data)
+- create 1-year lagged internet adoption variables
+
+```{r}
+# For models, year is centred at 2019
 itu <- itu %>% 
-  mutate(time = (year - 2013) / 10)
-
-# Create predictor: Lagged effect of 10% increase in internet
+  mutate(year = year - 2019)
+
+# Create lagged predictors
 itu <- itu %>% 
@@
   group_by(country) %>% 
-  mutate(i1 = lag(internet*10, 1)) %>% 
-  ungroup()
+  mutate(
+    across(
+      c(internet, fixed, mobile), 
+      list(`1` = ~lag(., 1)), 
+      .names = "{str_sub(.col, 1, 1)}{.fn}"
+    )
+  )
 
 # Centering within and between countries
-itu %>%
-  bmlm::isolate("i1", by = "country", which = "both")
-
-tibble(
-  id = c(1,1,1,2,2,2,3,3,3),
-  x = c(1,2,3,4,5,6,7,8,9)
-) %>% 
-  bmlm::isolate("x", by = "id", which = "both") %>% 
-  group_by(id) %>% 
-  mutate(x_cb2 = mean(x), x_cw2 = x - x_cb2) %>% 
+itu <- itu %>%
+  group_by(country) %>% 
+  mutate(
+    i1_cb = mean(i1_cb), # Country average
+    i1_cw = i1 - i1_cb # Year-specific deviation from country average
+  ) %>% 
   ungroup() %>% 
-  mutate(x_cb2 = x_cb2 - mean(x))
+  # Grand-mean center the country averages
+  mutate(i1_cb = i1_cb - mean(i1))
 ```
@@
 
+Merge tables
+
+```{r}
+dat <- left_join(gbd, itu)
+```
+
 ## Model 1: Temporal trends
@@
 
-### GBD
-
-#### brms
+## GBD
+
+### brms
 

### 2021-11-15 _common.R

@@ -15,10 +15,10 @@ knitr::opts_chunk$set(
 )
 
 # Plotting theme
-library(sysfonts)
 library(ggplot2)
+# Use better font if available
 Font <- "Titillium Web"
-if (!(Font %in% font_families())) font_add_google(Font, Font)
+if (require(extrafont) & !(Font %in% extrafont::fonts())) Font <- ""
 theme_set(
   theme_linedraw(
     base_size = 12,

### 2021-11-18 01-clean.Rmd
More edits
wip

@@
 
+Note we transform the outcome values to proportions so can harmonise easier across all variables
+
 ```{r gbd-data-clean}
@@
 # - rate: Total cases per 100,000 population
-#   - We convert this to a percentage
+#   - We convert this to a proportion
 # distinct(gbd, measure, metric)
@@
 gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~.x/1000))
+  mutate(across(c(val, upper, lower), ~.x/100000))
 
@@
 
+## Covariates
+
+Human Development Index
+
 ## GLOBE regions
@@
 regions_filled <- read_csv(
-  "data-raw/Regions/ITU-countries-without-region-filled.csv"
+  "data-raw/Regions/GBD-countries-without-region-filled.csv"
 ) 
@@
 gbd <- left_join(gbd, regions)
-
-# Merge data tables
-gbd <- left_join(gbd, itu)
 ```

### 2021-11-18 03-time.Rmd
wip

@@
 library(brms)
+library(cmdstanr)
 library(ellipse)
@@
 library(ggdist)
+library(posterior)
 library(parameters)
@@
 library(ggstance)
+library(multidplyr)
 library(tidyverse)
@@
 options(brms.backend = "cmdstanr")
-hmc <- list(iter = 2250, warmup = 1000, refresh = 50, d = .9)
+hmc <- list(
+  chains = 6,
+  cores = 6,
+  threads = 2,
+  iter = 300, 
+  warmup = 200,
+  refresh = 10,
+  adapt_delta = .9, 
+  max_treedepth = 10
+)
+
+# Parallelisation options: I have hard coded 12 cores here
+# n_cores <- 12
+# n_workers <- floor(n_cores / 4) # 4 chains always
+# cluster <- new_cluster(n_workers)
+# cluster_library(cluster, c("stringr", "dplyr"))
+
 # Run this to delete fitted models and refit
@@
 
-We prepare the predictors
-- center year on 2019 (last year in outcome data)
+Preparing the variables:
+
+- Transform edge values of internet variable to fit beta
+- center year on 2010 (roughly in the middle)
+  - Intercept and simple effects at 2010
+  - 1 unit: year
 - create 1-year lagged internet adoption variables
-
-```{r}
-# For models, year is centred at 2019
+  - Intercepts are country/grand means
+  - 1 unit: 100%
+- Contrast code factors
+
+```{r data-prepare}
+# Predictors
+
+# Transform edge proportions to fit beta distribution
 itu <- itu %>% 
-  mutate(year = year - 2019)
+  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999, internet))
 
@@
   mutate(
-    i1_cb = mean(i1_cb), # Country average
+    i1_cb = mean(i1, na.rm = TRUE), # Country average
     i1_cw = i1 - i1_cb # Year-specific deviation from country average
@@
   # Grand-mean center the country averages
-  mutate(i1_cb = i1_cb - mean(i1))
-```
-
-```{r}
-# Contrast code sex
-gbd$sex <- factor(gbd$sex)
-contrasts(gbd$sex) <- c(-.5, .5)
-
-# [todo] set mid age category as reference
-
-# GBD in wide format
-gbd_wide <- gbd %>%
-  pivot_wider(names_from = cause, values_from = c(val, se))
-names(gbd_wide) <- str_remove(names(gbd_wide), "val_")
-
-# Transform edge proportions to fit beta distribution
-gbd_10 <- gbd_wide %>% 
-  mutate(internet = if_else(internet == 0, .0000000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999999, internet))
-```
-
-Merge tables
-
-```{r}
+  mutate(i1_cb = i1_cb - mean(i1, na.rm = TRUE))
+
+# Outcomes
+
+# Merge predictors to outcomes
 dat <- left_join(gbd, itu)
-```
-
-## Model 1: Temporal trends
-
-We then model the mental health and well-being outcomes over time allowing for heterogeneity across locations and demographic groups.
-
-## GBD
-
-### brms
-
-correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
-
-note we use beta so transform edge values
-
-we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
-
-##### Time: Main effects
-
-We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
+
+# Center and scale year, and contrast code factors
+dat <- dat %>% 
+  mutate(year = (year - 2010) / 10)
+dat$sex <- factor(dat$sex)
+contrasts(dat$sex) <- "contr.sum"
+dat$age <- factor(dat$age)
+contrasts(dat$age) <- "contr.sum"
+
+# For brms multivariate data subsetting: variable to indicate unique ITU values
+dat <- dat %>% 
+  group_by(country, year) %>% 
+  mutate(itu = 1:n() == 1) %>% 
+  ungroup()
+```
+
+All the outcome variables are proportions (0-1) at this point. This creates problems with the HMC because the self-harm rates are so low. HMC works better with variables roughly on the unit scale.
+
+```{r}
+# Save this so its easy to use later to back-transform
+dat %>%
+  group_by(cause) %>%
+  summarise(median = median(val), min = min(val), max = max(val))
+
+# Important: do this for both val AND se
+# Multiply by 1000
+dat <- dat %>% 
+  group_by(cause) %>% 
+  mutate(across(val:se, ~.x*1000)) %>% 
+  ungroup()
+
+dat %>%
+  group_by(cause) %>%
+  summarise(median = median(val), min = min(val), max = max(val))
+
+# # It is then easy to back-transform
+# dat %>% 
+#   left_join(dat_scales) %>% 
+#   group_by(cause) %>% 
+#   mutate(
+#     val = rescale(val, to = c(unique(min), unique(max))),
+#     se = rescale(val, to = c(unique(min), unique(max)))
+#   ) %>% 
+#   summarise(median = median(val), min = min(val), max = max(val))
+```
+
+## Model 1
+
+The first model addresses our first research question: To what extent did the outcomes change over time. It will also answer whether changes were different across the demographic groups.
+
+It will also begin to address the issue of associations between internet adoption and well-being, by including a correlation between the country-specific trends in internet adoption and outcomes.
+
+We fit three incrementally more complex versions of this model. First, without demographic covariates, second with, and third with the two-way interactions with time.
+
+We fit the model separately for each outcome.
+
+### Model 1a
+
+Model 1a is a multivariate multilevel model of internet adoption and outcome (e.g.
+Anxiety) over time.
+The intercepts and coefficients of time are allowed to vary across regions and countries, with a shared correlation matrix of the random effects across the two outcomes.
+
+Internet adoption is treated as Beta-distributed. Outcome rates, the GBD estimates, are treated as Gaussian with a known standard error, resulting in a "meta-regression" model of the outcomes.
 
@@
 \begin{align*}
-y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\
+y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}v_i) \\
 
@@
 
-i_{i[c][r]} &\sim 
-\text{Beta}(\mu^i_{i[c][r]}, \phi^i) \\
-
-\mu^i_{i[c][r]} &= \text{logit}(
-\beta^{i}_{0} + \gamma^{i}_{0[c]} + \delta^{i}_{0[r]} +
-\beta^i_{1}\text{t}_i + \gamma^{i}_{1[c]}\text{t}_i + \delta^{i}_{1[r]}\text{t}_i) \\
+x_{i[c][r]} &\sim 
+\text{Beta}(\mu^x_{i[c][r]}, \phi^x) \\
+
+\mu^x_{i[c][r]} &= \text{logit}(
+\beta^{x}_{0} + \gamma^{x}_{0[c]} + \delta^{x}_{0[r]} +
+\beta^x_{1}\text{t}_i + \gamma^{x}_{1[c]}\text{t}_i + \delta^{x}_{1[r]}\text{t}_i) \\
 
 \left[\begin{array}{c}
-\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^i_{0[c]} \\ \gamma^i_{1[c]}
+\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^x_{0[c]} \\ \gamma^x_{1[c]}
 \end{array}\right] 
@@
 \left[\begin{array}{c}
-\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^i_{0[r]} \\ \delta^i_{1[r]}
+\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^x_{0[r]} \\ \delta^x_{1[r]}
 \end{array}\right] 
@@
 
-[todo] only pick the itu data for the internet model
+We then define the model formulas in brms' formula syntax.
+First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
+To do this we use `resp_subset(itu)`, which includes only unique rows of ITU data in the model.
+The `|c|` and `|r|` separating the random effects from their grouping factors indicate a shared correlation matrix, also indicated in the next model formula.
+
+```{r}
+# Define a model of internet proportion over year
+bf_itu <- bf(
+  internet | resp_subset(itu) ~ 
+    year + 
+    (year |c| country) +
+    (year |r| region), 
+  family = Beta()
+)
+```
+
+Here, we specify the outcome model.
+Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
+Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
+In addition, it leads to the residual variance to be estimated.
+
+```{r}
+# Define models of outcomes
+bf_1a <- bf(
+  val | resp_se(se, sigma = TRUE) ~ 
+    year + 
+    (year |c| country) +
+    (year |r| region),
+  family = gaussian()
+)
+```
+
+We then compile the model once, such that it can be updated with subsets of the data (the different outcomes) without having to compile again.
+
+```{r}
+fit_1a <- brm(
+  bf_itu + bf_1a + set_rescor(FALSE),
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-1a"
+)
+```
+
+Then fit the model. Note we don't need this for now because the relevant estimates are provided by model 1c.
+
+```{r eval = FALSE}
+fits_1a <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_1a, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup,
+        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
+        file = str_glue("output/brm-1a-{cur_group()}")
+      )
+    )
+  )
+```
+
+### Model 1b
+
+Model 1b is as 1a but we include age (10 to 14, 15 to 19, 20 to 24) and sex as covariates.
+
+```{r}
+bf_1b <- bf(
+  val | resp_se(se, sigma = TRUE) ~ 
+    year + sex + age + 
+    (year + sex + age |c| country) +
+    (year + sex + age |r| region),
+  family = gaussian()
+)
+```
+
+Then fit the model as above, first compiling and then updating for each outcome. Note not fitted for now--relevant estimates are in model 1c.
+
+```{r}
+fit_1b <- brm(
+  bf_itu + bf_1b + set_rescor(FALSE),
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-1b"
+)
+
+fits_1b <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_1b, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup,
+        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
+        file = str_glue("output/brm-1b-{cur_group()}")
+      )
+    )
+  )
+```
+
+### Model 1c
+
+Model 1c further expands 1b to include the two-way interactive terms between age and year, and sex and year.
+Thus we get age and sex-specific trajectories over time.
+We reuse the prior distributions from 1b.
+
+This takes about 3.5 hours per 1000 iterations (per model).
+
+```{r}
+bf_1c <- bf(
+  val | resp_se(se, sigma = TRUE) ~ 
+    year * sex + year * age + 
+    (year * sex + year * age |c| country) +
+    (year * sex + year * age |r| region),
+  family = gaussian()
+)
+
+fit_1c <- brm(
+  bf_itu + bf_1c + set_rescor(FALSE),
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-1c"
+)
+
+fits_1c <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_1c, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-1c-{cur_group()}")
+      )
+    )
+  )
+
+```
+
+### Checking
+
+Diagnostics: convergence and effective samples size
+
+```{r}
+f1d <- fits_1c %>% 
+  mutate(
+    out = 
+      map(
+        fit, 
+        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
+          summarise_draws(samples = length, default_convergence_measures())
+        )
+    ) %>% 
+  select(-fit) %>% 
+  unnest(out)
+f1d %>%  
+  kbl(
+    caption = "HMC Diagnostics, Model 1c",
+    digits = c(0,0,0,2,0,0)
+  ) %>% 
+  kable_paper(html_font = Font) %>% 
+  column_spec(
+    4, 
+    color = "white",
+    background = spec_color(
+      f1d$rhat, 
+      direction = 1, 
+      option = "C", 
+      end = .7
+    )
+  )
+```
+
+### Summary
+
+We then display the model's population-level parameters
+
+```{r}
+fits_1 <- reduce(
+  list(
+    fits_1a %>% rename(fit_1a = fit), 
+    fits_1b %>% rename(fit_1b = fit),
+    fits_1c %>% rename(fit_1c = fit)
+  ), 
+  left_join
+) %>% 
+  pivot_longer(fit_1a:fit_1c, names_to = "model", values_to = "fit")
+fits_1 %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
+        summarise_draws(
+          mean, quantile, rhat, 
+          .args = list(probs = c(.025, .975))
+        )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(
+    result = str_glue(
+      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
+    )
+  ) %>% 
+  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
+  pivot_wider(names_from = model, values_from = result) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font)
+```
+
+## Model 2
+
+Model 2 is a modification of Model 1.
+First, we now switch to looking at internet use more specifically as a predictor, and therefore implement a univariate model of each outcome.
+Second, we include within- and between-country centred 1-year-lagged internet adoption values as predictors in the model.
+
+We fit this model in two increasingly complex forms, corresponding to models 1b and 1c, but with the addition of the internet adoption predictors, and one outcome model only.
+
+2c takes about 5 hours per 1000 iterations.
+
+```{r}
+bf_2b <- bf(
+  val | resp_se(se, sigma = TRUE) ~ 
+    year + sex + age + i1_cw + i1_cb +
+    (year + sex + age + i1_cw | country) +
+    (year + sex + age + i1_cw | region),
+  family = gaussian()
+)
+fit_2b <- brm(
+  bf_2b,
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-2b"
+)
+fits_2b <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_2b, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2b-{cur_group()}")
+      )
+    )
+  )
+
+bf_2c <- bf(
+  val | se(se, sigma = TRUE) ~ 
+    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
+  family = gaussian()
+)
+
+fit_2c <- brm(
+  bf_2c,
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-2c"
+)
+
+fits_2c <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_2c, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup,
+        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
+        file = str_glue("output/brm-2c-{cur_group()}")
+      )
+    )
+  )
+```
+
+### Checking
+
+Diagnostics: convergence and effective samples size
+
+```{r}
+f2d <- fits_2c %>% 
+  mutate(
+    out = 
+      map(
+        fit, 
+        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
+          summarise_draws(samples = length, default_convergence_measures())
+        )
+    ) %>% 
+  select(-fit) %>% 
+  unnest(out)
+f2d %>%  
+  kbl(
+    caption = "HMC Diagnostics, Model 2c",
+    digits = c(0,0,0,2,0,0)
+  ) %>% 
+  kable_paper(html_font = Font, full_width = FALSE) %>% 
+  column_spec(
+    4, 
+    color = "white",
+    background = spec_color(
+      f2d$rhat, 
+      direction = 1, 
+      option = "C", 
+      end = .7
+    )
+  ) %>% 
+  scroll_box(height = "600px", width = "800px")
+```
+
+### Summary
+
+We then display the model's population-level parameters
+
+```{r}
+fits_2 <- reduce(
+  list(
+    fits_2b %>% rename(fit_2b = fit), 
+    fits_2c %>% rename(fit_2c = fit)
+  ), 
+  left_join
+) %>% 
+  pivot_longer(fit_2b:fit_2c, names_to = "model", values_to = "fit")
+fits_2 %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
+        summarise_draws(
+          mean, quantile, rhat, 
+          .args = list(probs = c(.025, .975))
+        )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(
+    result = str_glue(
+      "b = {mean} ({`2.5%`}, {`97.5%`}) [rhat = {round(rhat, 2)}]"
+    )
+  ) %>% 
+  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
+  pivot_wider(names_from = model, values_from = result) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font)
+```
+
+## OLD
+
+### brms
+
+correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
+
+note we use beta so transform edge values
+
+we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
+
+##### Time: Main effects
+
+We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
 
@@
   bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-anxiety",
@@
   iter = hmc$iter, warmup = hmc$warmup, 
-  refresh = hmc$refresh,
   control = list(adapt_delta = hmc$d)
@@
   bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-depression",
@@
   bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-selfharm",
@@
     ) %>% 
-    left_join(distinct(gbd, region, country))
+    left_join(distinct(dat, region, country))
 
@@
   ) %>% 
-  left_join(distinct(gbd, region, country))
+  left_join(distinct(dat, region, country))
 
@@
   bf_int + bf_anx + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-anxiety-int2",
@@
   bf_int + bf_dep + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-depression-int2",
@@
   bf_int + bf_sel + set_rescor(FALSE),
-  data = gbd_10,
+  data = dat_10,
   file = "output/brm-gbd-time-selfharm-int2",

### 2021-11-18 04-internet.Rmd
clean analyses
wip

@@
 
+```
+
+## OLD
+
+```{r}
+gbd <- read_rds("data/gbd.rds")
 ```

### 2021-11-18 _common.R

@@ -18,7 +18,6 @@ knitr::opts_chunk$set(
 library(ggplot2)
 # Use better font if available
 Font <- "Titillium Web"
-if (require(extrafont) & !(Font %in% extrafont::fonts())) Font <- ""
 theme_set(
   theme_linedraw(
     base_size = 12,

### 2021-11-18 01-clean.Rmd
Add HDI

@@
 
+This data set was downloaded from <http://hdr.undp.org/en/indicators/137506#> in November 2021, and shared here under the terms of use <http://hdr.undp.org/en/content/copyright-and-terms-use>.
+
+```{r}
+hdi <- read_csv("data-raw/HDI/Human Development Index (HDI).csv", skip = 5) %>% 
+  # Get rid of weird empty columns
+  select(c(1, 2, seq(3, 61, by = 2)), country = Country) %>%
+  # Keep countries only
+  drop_na(`HDI Rank`) %>% 
+  select(-`HDI Rank`) %>% 
+  pivot_longer(-1, names_to = "year", values_to = "hdi") %>% 
+  mutate(across(year:hdi, as.numeric)) %>% 
+  filter(year >= 2000)
+
+# Replace broken string
+hdi$country[46]
+hdi$country[46] <- "Côte d’Ivoire"
+
+# Harmonise names
+hdi <- hdi %>% 
+  mutate(country = countryname(country))
+```
+
 ## GLOBE regions

### 2021-11-18 03-analysis.Rmd
Reorganise analyses

--- 2021-11-18 03-time.Rmd
@@
 library(ggstance)
-library(multidplyr)
 library(tidyverse)
@@
 
-## Model 2
-
-Model 2 is a modification of Model 1.
-First, we now switch to looking at internet use more specifically as a predictor, and therefore implement a univariate model of each outcome.
-Second, we include within- and between-country centred 1-year-lagged internet adoption values as predictors in the model.
-
-We fit this model in two increasingly complex forms, corresponding to models 1b and 1c, but with the addition of the internet adoption predictors, and one outcome model only.
-
-2c takes about 5 hours per 1000 iterations.
-
-```{r}
-bf_2b <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + sex + age + i1_cw + i1_cb +
-    (year + sex + age + i1_cw | country) +
-    (year + sex + age + i1_cw | region),
-  family = gaussian()
-)
-fit_2b <- brm(
-  bf_2b,
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-2b"
-)
-fits_2b <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_2b, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2b-{cur_group()}")
-      )
-    )
-  )
-
-bf_2c <- bf(
-  val | se(se, sigma = TRUE) ~ 
-    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-fit_2c <- brm(
-  bf_2c,
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-2c"
-)
-
-fits_2c <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_2c, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
-        file = str_glue("output/brm-2c-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Checking
-
-Diagnostics: convergence and effective samples size
-
-```{r}
-f2d <- fits_2c %>% 
-  mutate(
-    out = 
-      map(
-        fit, 
-        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
-          summarise_draws(samples = length, default_convergence_measures())
-        )
-    ) %>% 
-  select(-fit) %>% 
-  unnest(out)
-f2d %>%  
-  kbl(
-    caption = "HMC Diagnostics, Model 2c",
-    digits = c(0,0,0,2,0,0)
-  ) %>% 
-  kable_paper(html_font = Font, full_width = FALSE) %>% 
-  column_spec(
-    4, 
-    color = "white",
-    background = spec_color(
-      f2d$rhat, 
-      direction = 1, 
-      option = "C", 
-      end = .7
-    )
-  ) %>% 
-  scroll_box(height = "600px", width = "800px")
-```
-
-### Summary
-
-We then display the model's population-level parameters
-
-```{r}
-fits_2 <- reduce(
-  list(
-    fits_2b %>% rename(fit_2b = fit), 
-    fits_2c %>% rename(fit_2c = fit)
-  ), 
-  left_join
-) %>% 
-  pivot_longer(fit_2b:fit_2c, names_to = "model", values_to = "fit")
-fits_2 %>% 
+### Figure: Timecourses and parameters
+
+```{r}
+
+tmp_coefs <- fits_1c %>% 
   mutate(
@@
       fit, 
-      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
-        summarise_draws(
-          mean, quantile, rhat, 
-          .args = list(probs = c(.025, .975))
-        )
+      ~hypothesis(
+        .x, 
+        # Rescale coefficient here to years on %
+        c(str_glue("val_year = 0")),
+        scope = "coef",
+        group = "region"
+      )$hypothesis
     )
@@
   mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(
-    result = str_glue(
-      "b = {mean} ({`2.5%`}, {`97.5%`}) [rhat = {round(rhat, 2)}]"
-    )
-  ) %>% 
-  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = model, values_from = result) %>% 
-  kbl() %>% 
-  kable_paper(html_font = Font)
-```
-
-## OLD
-
-### brms
-
-correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix
-
-note we use beta so transform edge values
-
-we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow
-
-##### Time: Main effects
-
-We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.
-
-```{r}
-# Define a model of internet proportion over time
-bf_int <- bf(
-  internet ~ 1 + time + 
-    (1 + time |c| country) +
-    (1 + time |r| region), 
-  family = Beta()
-)
-
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time + sex + age |c| country) +
-    (1 + time + sex + age |r| region),
-  family = gaussian()
-)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-anxiety",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  control = list(adapt_delta = hmc$d)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-depression",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  control = list(adapt_delta = hmc$d)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-selfharm",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  control = list(adapt_delta = hmc$d)
-)
-fits_brm_time_main <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
-```
-
-Coefficients
-
-```{r}
-fits_brm_time_main %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000
-
-```{r}
-tmp_pars <- fits_brm_time_main %>% 
-  mutate(
-    out = map2(
-      fit, 
-      outcome,
-      ~hypothesis(
-        .x, 
-        c(str_glue("{.y}_time = 0")),
-        scope = "coef",
-        group = "region"
-      )$hypothesis
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  # Internet trend is estimated in all models--keep first
-  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
-  # Transform back to rates in 100k
-  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
   mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
-  select(cause = Hypothesis, region = Group, result) %>% 
-  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))
-
-p_vars +
+  select(cause, region = Group, result)
+tmp_coefs
+pseudo_gwp <-
+  bind_rows(
+    distinct(gbd, region, year, val = NA) %>% 
+      crossing(
+        cause = fct_inorder(
+          c(
+            "Negative\nexperiences", 
+            "Positive\nexperiences", 
+            "Life\nsatisfaction"
+          )
+        )
+      )
+  )
+
+# Stack data sets
+# Assume all outcomes are proportions (0-1)
+dat_all <- bind_rows(
+  pseudo_gwp,
+  gbd,
+  itu %>% mutate(cause = "Internet", val = internet)
+) %>% 
+  mutate(cause = fct_inorder(cause)) %>% 
+  group_by(region, country, year, cause) %>% 
+  summarise(mean = mean(val, na.rm = TRUE)) %>% 
+  ungroup()
+
+# Draw small multiples figure, outcomes x regions
+dat_all %>% 
+  mutate(year = make_date(year)) %>% 
+  ggplot(aes(year, mean)) +
+  scale_y_continuous(
+    "Value",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2000, 2005, 2010, 2015)), 
+    date_labels = "'%y", 
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country, cause)), 
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line", 
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_grid(cause~region, scales = "free_y") +
+  theme(
+    legend.position = "none",
+    panel.spacing = unit(3, "pt")
+  ) +
   geom_richtext(
-    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
+    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
     aes(x = make_date(2000), y = Inf, label = result),
@@
   )
-ggsave(
-  "output/Fig-vars-timeseries-estimates.png", 
-  device = agg_png,
-  height = 2400, width = 3600, res = 300, units = "px"
-)
-```
-
-A figure of coefficients
-
-```{r}
-anx_draws <- spread_draws(
-  fit_anx, 
-  b_Anxiety_time, r_region__Anxiety[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Anxiety_time) %>% 
-  mutate(outcome = "Anxiety")
-dep_draws <- spread_draws(
-  fit_dep, 
-  b_Depression_time, r_region__Depression[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Depression_time) %>% 
-  mutate(outcome = "Depression")
-sel_draws <- spread_draws(
-  fit_sel, 
-  b_Selfharm_time, r_region__Selfharm[region, term] | region
-) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_Selfharm_time) %>% 
-  mutate(outcome = "Selfharm")
-
-p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
-  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
-  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
-  mutate(region = fct_relevel(factor(region), "Average")) %>% 
-  mutate(outcome = factor(outcome)) %>% 
-  mutate(is_average = region == "Average") %>% 
-  mutate(region = str_replace(region, "\\.", " ")) %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.5, .9)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels"
-  ) +
-  facet_wrap("outcome", nrow = 1, scales = "free_x") +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-p_time_main_coefs
-```
-
-###### Correlations
+```
+
+### Figure: Correlations
 
@@
     spread_draws(
-      {{beta}}, 
-      b_internet_time,
-      {{r_region}}[region, term],
+      b_val_year, 
+      b_internet_year,
+      r_region__val[region, term],
       r_region__internet[region, term]
     ) %>% 
-    filter(term == "time") %>% 
+    filter(term == "year") %>% 
     ungroup() %>% 
@@
     spread_draws(
-      {{r_country}}[country, term],
+      r_country__val[country, term],
       r_country__internet[country, term]
     ) %>% 
-    filter(term == "time") %>% 
+    filter(term == "year") %>% 
     ungroup() %>% 
@@
     mutate(
-      internet = b_internet_time + r_region__internet + r_country__internet,
-      outcome = {{beta}} + {{r_region}} + {{r_country}}
+      internet = b_internet_year + r_region__internet + r_country__internet,
+      outcome = b_val_year + r_region__val + r_country__val
     ) %>% 
@@
     fit,
-    {{beta}}, 
-    b_internet_time,
-    {{sd_country}},
-    sd_country__internet_time,
-    {{cor_country}}, 
+    b_val_year, 
+    b_internet_year,
+    sd_country__val_year,
+    sd_country__internet_year,
+    cor_country__internet_year__val_year, 
     ndraws = 100
@@
     rename(
-      cor = {{cor_country}}, 
-      sd_outcome = {{sd_country}},
-      sd_i = sd_country__internet_time,
-      b_outcome = {{beta}},
-      b_i = b_internet_time
+      cor = cor_country__internet_year__val_year, 
+      sd_outcome = sd_country__val_year,
+      sd_i = sd_country__internet_year,
+      b_outcome = b_val_year,
+      b_i = b_internet_year
     ) %>% 
@@
   # Correlation
-  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
+  country_cor_result <- spread_draws(fit, cor_country__internet_year__val_year) %>% 
     median_qi(.width = .90) %>% 
@@
 ```{r}
-p_cor_country_anx <- draw_scatterplot(
-  fit_anx, 
-  b_Anxiety_time, 
-  r_region__Anxiety, 
-  r_country__Anxiety,
-  sd_country__Anxiety_time,
-  cor_country__internet_time__Anxiety_time
-) + labs(y = "Anxiety trend")
-p_cor_country_dep <- draw_scatterplot(
-  fit_dep, 
-  b_Depression_time, 
-  r_region__Depression, 
-  r_country__Depression,
-  sd_country__Depression_time,
-  cor_country__internet_time__Depression_time
-) + labs(y = "Depression trend")
-p_cor_country_sel <- draw_scatterplot(
-  fit_sel, 
-  b_Selfharm_time, 
-  r_region__Selfharm, 
-  r_country__Selfharm,
-  sd_country__Selfharm_time,
-  cor_country__internet_time__Selfharm_time
-) + labs(y = "Self-harm trend")
+draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
+draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
+draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
 ```
@@
                                p_cor_country_dep |
-                               p_cor_country_sel) &
-  # Transform to rate in 100k
-  scale_y_continuous(labels = function(x) x*1000)
+                               p_cor_country_sel)
 
@@
 
-##### Time: Interactions
-
-```{r}
-# Define models of outcomes
-bf_anx <- bf(
-  Anxiety ~ 1 + time * sex + time * age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
+## Model 2
+
+Model 2 is a modification of Model 1.
+First, we now switch to looking at internet use more specifically as a predictor, and therefore implement a univariate model of each outcome.
+Second, we include within- and between-country centred 1-year-lagged internet adoption values as predictors in the model.
+
+We fit this model in two increasingly complex forms, corresponding to models 1b and 1c, but with the addition of the internet adoption predictors, and one outcome model only.
+
+2c takes about 5 hours per 1000 iterations.
+
+```{r}
+bf_2b <- bf(
+  val | resp_se(se, sigma = TRUE) ~ 
+    year + sex + age + i1_cw + i1_cb +
+    (year + sex + age + i1_cw | country) +
+    (year + sex + age + i1_cw | region),
   family = gaussian()
 )
-bf_dep <- bf(
-  Depression ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
+fit_2b <- brm(
+  bf_2b,
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-2b"
+)
+fits_2b <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_2b, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
+        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2b-{cur_group()}")
+      )
+    )
+  )
+
+bf_2c <- bf(
+  val | se(se, sigma = TRUE) ~ 
+    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
   family = gaussian()
 )
-bf_sel <- bf(
-  Selfharm ~ 1 + time + sex + age + 
-    (1 + time * sex + time * age |c| country) +
-    (1 + time * sex + time * age |r| region),
-  family = gaussian()
-)
-
-# Fit models
-fit_anx <- brm(
-  bf_int + bf_anx + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-anxiety-int2",
-  chains = 4,
-  cores = 4,
+
+fit_2c <- brm(
+  bf_2c,
+  data = filter(dat, cause == "Anxiety"),
+  chains = 0,
+  threads = hmc$threads,
+  file = "output/brm-2c"
+)
+
+fits_2c <- dat %>% 
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      update(
+        fit_2c, 
+        newdata = cur_data_all(),
+        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
         iter = hmc$iter, warmup = hmc$warmup,
-  control = list(adapt_delta = hmc$d)
-)
-fit_dep <- brm(
-  bf_int + bf_dep + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-depression-int2",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  control = list(adapt_delta = hmc$d)
-)
-fit_sel <- brm(
-  bf_int + bf_sel + set_rescor(FALSE),
-  data = dat_10,
-  file = "output/brm-gbd-time-selfharm-int2",
-  chains = 4,
-  cores = 4,
-  iter = hmc$iter, warmup = hmc$warmup, 
-  control = list(adapt_delta = hmc$d)
-)
-fits_brm_time_interactions <- tibble(
-  outcome = c("Anxiety", "Depression", "Selfharm"),
-  fit = list(fit_anx, fit_dep, fit_sel)
-)
+        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
+        file = str_glue("output/brm-2c-{cur_group()}")
+      )
+    )
+  )
+```
+
+### Checking
+
+Diagnostics: convergence and effective samples size
+
+```{r}
+f2d <- fits_2c %>% 
+  mutate(
+    out = 
+      map(
+        fit, 
+        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
+          summarise_draws(samples = length, default_convergence_measures())
+        )
+    ) %>% 
+  select(-fit) %>% 
+  unnest(out)
+f2d %>%  
+  kbl(
+    caption = "HMC Diagnostics, Model 2c",
+    digits = c(0,0,0,2,0,0)
+  ) %>% 
+  kable_paper(html_font = Font, full_width = FALSE) %>% 
+  column_spec(
+    4, 
+    color = "white",
+    background = spec_color(
+      f2d$rhat, 
+      direction = 1, 
+      option = "C", 
+      end = .7
+    )
+  ) %>% 
+  scroll_box(height = "600px", width = "800px")
+```
+
+### Summary
+
+We then display the model's population-level parameters
+
+```{r}
+fits_2 <- reduce(
+  list(
+    fits_2b %>% rename(fit_2b = fit), 
+    fits_2c %>% rename(fit_2c = fit)
+  ), 
+  left_join
+) %>% 
+  pivot_longer(fit_2b:fit_2c, names_to = "model", values_to = "fit")
+fits_2 %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
+        summarise_draws(
+          mean, quantile, rhat, 
+          .args = list(probs = c(.025, .975))
+        )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(
+    result = str_glue(
+      "b = {mean} ({`2.5%`}, {`97.5%`}) [rhat = {round(rhat, 2)}]"
+    )
+  ) %>% 
+  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
+  pivot_wider(names_from = model, values_from = result) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font)
 ```
@@
 ```{r}
-fits_brm_time_interactions %>% 
+fits_brm_internet_interactions %>% 
   mutate(
@@
       ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
+        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
     )
@@
   unnest(out) %>% 
-  # filter(str_detect(Parameter, "_time$")) %>% 
-  kbl(digits = 2) %>% 
+  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
+  kbl(digits = 3) %>% 
   kable_minimal(full_width = FALSE)
@@
 
-Model comparison using waic shows that interactive model is favored across the board.
-
-```{r eval = FALSE}
-waics <- left_join(
-  rename(fits_brm_time_main, fit_main = fit),
-  rename(fits_brm_time_interactions, fit_intr = fit)
-) %>% 
-  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
-waics$waic[[3]]
-```
-
-Show main effects
-
-Plot fixed effects and by demographic
-
-```{r}
-# Fixed effects parameters
-fixed_effects <- fits_brm_time_interactions %>% 
-  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  filter(
-    Effects == "fixed", 
-    Parameter != "(Intercept)"
-  ) 
-# Fixed effects per demographic
-fixed_effects_demographics <- fits_brm_time_interactions %>% 
-  mutate(
-    out = map2(
-      fit, outcome,
-      ~emtrends(
-        .x, 
-        var = "time", 
-        by = c("sex", "age"), 
-        resp = .y
-      ) %>% 
-        parameters() %>% 
-        as.data.frame()
-    )
-  )
-fixed_effects_demographics %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  standardize_names() %>% 
-  as_tibble() %>% 
-  mutate(Parameter = str_glue("{sex}\n({age})"))
-
-# Random effects parameters
-random_effects <- fits_lmer %>% 
-  mutate(
-    coef_region = map(
+### Forest plots
+
+figure of coefficients forest plot
+
+```{r}
+anx_draws <- spread_draws(
+  fit_anx, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Anxiety")
+dep_draws <- spread_draws(
+  fit_dep, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Depression")
+sel_draws <- spread_draws(
+  fit_sel, 
+  b_i1_cw, r_region[region, term] | region
+) %>% 
+  filter(term == "i1_cw") %>% 
+  ungroup() %>% 
+  select(-term) %>% 
+  rename(Average = b_i1_cw) %>% 
+  mutate(outcome = "Selfharm")
+
+results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  group_by(outcome) %>% 
+  summarise(parameters(cur_data()[-c(1:3)])) %>% 
+  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))
+
+p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
+  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
+  mutate(region = fct_relevel(factor(region), "Average")) %>% 
+  mutate(outcome = factor(outcome)) %>% 
+  mutate(is_average = region == "Average") %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
+  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
+  scale_alpha_manual(values = c(.4, .8)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_y_discrete(expand = expansion(c(0.01, .1))) +
+  scale_x_continuous(
+    "Magnitude of association between internet adoption and well-being", 
+    breaks = pretty_breaks(), 
+    expand = expansion(c(.1, .5))
+  ) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels", 
+    height = .75, adjust = 1.5
+  ) +
+  stat_pointinterval(
+    alpha = 1, .width = c(.9),
+    interval_size = .5,
+    point_size = 1.5,
+    fill = "white",
+    aes(shape = after_stat(xmin > 0 | xmax < 0)),
+    position = position_nudge(0, -.025)
+  ) +
+  geom_text(
+    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
+    aes(
+      x = Inf, 
+      label = str_glue("{Median} [{CI_low}, {CI_high}]")
+    )
+  ) +
+  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  theme(
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown(),
+    legend.position = "none"
+  )
+
+(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
+    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
+  p_internet_main_coefs
+```
+
+### Figure: Between country effects
+
+```{r}
+pred_data <- gbd_wide %>% 
+  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
+  filter(country %in% sort(unique(fit_anx$data$country)))
+
+tmp <- epred_draws(
+  fit_anx, pred_data, re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
+)
+
+tmp %>% 
+  group_by(region, country, i1_cb) %>% 
+  summarise(mean(.epred))
+
+conditional_effects(fit_anx, "i1_cb")
+
+gbd_wide %>% 
+  group_by(country) %>% 
+  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
+  ggplot(aes(i1_cb, anx)) +
+  geom_point() +
+  stat_smooth()
+
+filter(country %in% sort(unique(fit_anx$data$country))) %>% 
+  mutate(time = 0) %>% 
+  group_by(country) %>% 
+  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
+  filter(i1_cw %in% c(xmin, xmax)) %>% 
+  ungroup()
+```
+
+### Sex and Age
+
+```{r}
+# Get some stuff and transform :)
+get_draws <- function(fit) {
+  draws_region <- spread_draws(
     fit, 
-      ~bind_rows(
-        coef(.x)$region %>% 
-          as.data.frame() %>% 
-          rownames_to_column("region"),
-        coef(.x)$country %>% 
-          as.data.frame() %>% 
-          rownames_to_column("country"),
-        .id = "cluster"
-      ) %>% 
-        mutate(cluster = factor(cluster, labels = c("region", "country")))
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(coef_region) %>% 
-  mutate(Type = "Effects") %>%
-  select(-`(Int      ,nc ercept)`)
-
-bind_rows(
-  fixed_effects,
-  fixed_effects_demographics, 
-  .id = "Type"
-) %>% 
-  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
-  mutate(Parameter = fct_inorder(Parameter)) %>%
-  mutate(cause = factor(cause)) %>% 
-  rowwise() %>% 
-  mutate(
-    sig = factor(
-      !between(0, CI_low, CI_high), 
-      levels = c(TRUE, FALSE)
-    )
-  ) %>% 
-  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
-  scale_color_discrete(
-    "Outcome"
-  ) +
+    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
+    r_region[region, term] | term
+  ) %>% 
+    mutate(
+      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
+      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
+      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
+      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
+      Age = `age1:i1_cw` + `b_age1:i1_cw`,
+      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
+    ) %>% 
+    select(region, `15 to 19`:Sex)
+
+  draws_avg <- spread_draws(
+    fit, 
+    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
+  ) %>% 
+    mutate(
+      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
+      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
+      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
+      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
+      Age = `b_age1:i1_cw`,
+      Sex = `b_sex1:i1_cw`
+    ) %>% 
+    mutate(region = "**Average**") %>% 
+    select(region, `15 to 19`:Sex)
+
+  draws <- bind_rows(
+    "regions" = draws_region,
+    "average" = draws_avg, 
+    .id = "Level"
+  ) %>% 
+    mutate(region = str_replace(region, "\\.", "\n")) %>% 
+    ungroup()
+  draws
+}
+
+draws <- bind_rows(
+  "Anxiety" = get_draws(fit_anx),
+  "Depression" = get_draws(fit_dep),
+  "Selfharm" = get_draws(fit_sel),
+  .id = "outcome"
+)
+
+draws_sum <- draws %>% 
+  select(outcome, region, Age, Sex) %>% 
+  group_by(outcome, region) %>% 
+  summarise(
+    describe_posterior(
+      cur_data(), centrality = "mean", test = "pd"
+    )
+  ) %>% 
+  rename(panel = Parameter) %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+draws %>% 
+  select(outcome, Level, region, `15 to 19`:Male) %>% 
+  pivot_longer(-c(region, Level, outcome), names_to = "Group") %>% 
+  mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
+  mutate(
+    side = if_else(Group %in% c("15 to 19", "Female"), "top", "bottom")
+  ) %>% 
+  mutate(region = str_replace(region, "\\.", " ")) %>% 
+  mutate(region = fct_relevel(region, "**Average**")) %>% 
+  ggplot(aes(value, region, col = Group, fill = Group)) +
+  scale_alpha_manual(values = c(.6, .3)) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_shape_manual(
+    values = c(21, 19), guide = "none"
+    ) +
+  scale_y_discrete(expand = expansion(c(0.1, 0.1))) +
   scale_x_continuous(
-    "Estimate (95%CI)"
-  ) +
-  scale_shape_manual(values = c(19, 21)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .2) +
-  geom_pointrangeh(
-    aes(xmin = CI_low, xmax = CI_high),
-    position = position_dodge2v(.5),
-    fill = "white", size = .3, fatten = 5
-  ) +
-  guides(shape = "none") +
-  facet_wrap("Type", ncol = 2, scales = "free") +
-  theme(axis.title.y = element_blank())
-```
-
-```{r}
-library(modelbased)
-x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
-tmp <- fits_brm %>% 
-  mutate(
-    # Average effect
-    avg = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(.x, str_glue("{.y}_time = 0"))
+    "Magnitude of association between internet adoption and well-being", 
+    breaks = pretty_breaks(), 
+    expand = expansion(c(0, .05))
+  ) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels", 
+    height = .75, adjust = 1.5,
+    aes(side = side, group = side, alpha = Level), 
+    show.legend = FALSE
+  ) +
+  stat_pointinterval(
+    alpha = 1, .width = c(.9),
+    interval_size = .33,
+    point_size = 1.25,
+    fill = "white",
+    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
+    position = position_dodgev(.25), key_glyph = draw_key_point
+  ) +
+  geom_richtext(
+    data = draws_sum %>% 
+      mutate(Group = NA) %>% 
+      filter(outcome %in% c("Anxiety", "Depression", "Selfharm")),
+    aes(
+      x = Inf, 
+      label = str_glue("*d* = {Mean} (p<sup>d</sup> = {percent(pd, 1)})")
     ),
-    # By country effect
-    by_country = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "country"
-      )
-    ),
-    # By region effect
-    by_region = map2(
-      fit, 
-      Outcome, 
-      ~hypothesis(
-        .x, str_glue("{.y}_time = 0"), 
-        scope = "coef", group = "region"
-      )
-    )
-  ) %>% 
-  select(-fit)
-
-tmp %>% 
-  select(Outcome, avg) %>% 
-  mutate(avg = map(avg, ))
-
-tmp$by_region[[1]] %>% str
-
-h <- paste(
-  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
-  "= 0"
-)
-
-# Prepare average samples
-time_avg <- hypothesis(fit_gbd_time, h)
-time_avg_samples <- time_avg$samples
-names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
-time_avg_samples <- time_avg_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  mutate(region = "Average")
-
-# Prepare region samples
-time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
-time_region_samples <- time_region$samples
-names(time_region_samples) <- paste(
-  time_region$hypothesis$Hypothesis, 
-  time_region$hypothesis$Group, sep = ":"
-)
-time_region_samples <- time_region_samples %>% 
-  pivot_longer(everything(), names_to = "Parameter") %>% 
-  separate(Parameter, c("Parameter", "region"), sep = ":")
-
-# Prepare country point estimates
-time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
-time_country_hypothesis <- time_country$hypothesis %>% 
-  rename(country = Group, Parameter = Hypothesis)
-time_country_hypothesis <- left_join(
-  time_country_hypothesis, 
-  distinct(fit_gbd_time$data, country, region)
-)
-
-time_sum <- bind_rows(
-  time_region$hypothesis,
-  time_avg$hypothesis %>% mutate(Group = "Average")
-) %>% 
-  as_tibble() %>% 
-  rename(region = Group, Parameter = Hypothesis)
-
-bind_rows(
-  time_region_samples,
-  time_avg_samples
-) %>% 
-  mutate(region = fct_relevel(region, "Average")) %>% 
-  mutate(Average = region == "Average") %>% 
-  ggplot(aes(value/10, region)) +
-  scale_y_discrete(
-    expand = expansion(c(0.025, 0.075)),
-    labels = function(x) ifelse(x == "Average", "**Average**", x)
-  ) +
+    size = 2.5, hjust = 1,
+    family = Font,
+    fill = NA, label.color = NA,
+    show.legend = FALSE
+  ) +
+  facet_grid2(panel ~ outcome, scales = "free_x", axes = "x") +
+  guides(
+    alpha = "none"
+  ) +
+  theme(
+    legend.position = "right",
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown()
+  )
+```
+
+### Fitted lines
+
+Plot of fitted lines
+
+```{r}
+# Prediction dataframe: Min and max vals are enough for line
+pred_data <- gbd_wide %>% 
+  filter(country %in% sort(unique(fit_anx$data$country))) %>% 
+  mutate(time = 0) %>% 
+  group_by(country) %>% 
+  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
+  filter(i1_cw %in% c(xmin, xmax)) %>% 
+  ungroup()
+draws_country_anx <- epred_draws(
+  fit_anx, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Anxiety"
+)
+
+draws_country_dep <- epred_draws(
+  fit_dep, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Depression"
+)
+
+draws_country_sel <- epred_draws(
+  fit_sel, 
+  pred_data,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
+    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
+  ndraws = 100,
+  resp = "Selfharm"
+)
+
+pred_data_region <- pred_data %>% 
+  distinct(region, sex, age, i1_cb) %>% 
+  group_by(region) %>% 
+  mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
+  crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
+  mutate(time = 0)
+
+draws_region_anx <- epred_draws(
+  fit_anx, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Anxiety"
+) %>% 
+  mutate(outcome = "Anxiety")
+
+draws_region_dep <- epred_draws(
+  fit_dep, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Depression"
+) %>% 
+  mutate(outcome = "Depression")
+
+draws_region_sel <- epred_draws(
+  fit_sel, 
+  pred_data_region,
+  re_formula = 
+    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
+  ndraws = 100,
+  resp = "Selfharm"
+) %>% 
+  mutate(outcome = "Self-harm")
+
+means_country <- bind_rows(
+  draws_country_anx %>% mutate(outcome = "Anxiety"),
+  draws_country_dep %>% mutate(outcome = "Depression"),
+  draws_country_sel %>% mutate(outcome = "Self-harm")
+) %>% 
+  group_by(outcome, region, country, i1_cw) %>% 
+  summarise(.epred = mean(.epred))
+
+means_region <- bind_rows(
+  draws_region_anx, draws_region_dep, draws_region_sel
+) %>% 
+  group_by(outcome, region, i1_cw) %>% 
+  mean_qi(.epred, .width = .9)
+
+means_region <- pseudo_gwp %>% 
+  distinct(region, outcome=cause) %>% 
+  bind_rows(means_region) %>% 
+  mutate(outcome = fct_inorder(factor(outcome)))
+
+pseudo_gwp %>% 
+  distinct(region, outcome=cause) %>% 
+  bind_rows(means_country) %>% 
+  mutate(outcome = fct_inorder(factor(outcome))) %>% 
+  ggplot(aes(i1_cw, .epred)) +
   scale_x_continuous(
-    "Estimated yearly change",
-    breaks = pretty_breaks(5)
-  ) +
-  scale_alpha_manual(values = c(.5, 1)) +
-  geom_vline(xintercept = 0, size = .2, alpha = .25) +
-  stat_eye(
-    side = "top",
-    aes(col = region, fill = region, alpha = Average),
-    point_interval = NULL,
-    normalize = "panels", 
-    height = .75
-  ) +
-  geom_pointrangeh(
-    data = time_sum,
-    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
-    size = .3, fatten = 1.4
-  ) +
-  geom_point(
-    data = time_country_hypothesis,
-    aes(col = region, x = Estimate/10), 
-    size = .5,
-    alpha = .25,
-    position = position_nudge(y = -.05)
-  ) +
-  facet_wrap(
-    "Parameter", ncol = 3, scales = "free_x",
-    labeller = as_labeller(
-      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
-  ) +
-  theme(
-    axis.text.y = element_markdown(),
-    legend.position = "none",
-    axis.title.y = element_blank()
-  )
-ggsave(
-  "output/Fig-brm-time-forest.png", 
-  device = agg_png,
-  height = 1200, width = 3200, res = 300, units = "px"
-)
-```
+    "Previous year's internet adoption relative to country average in 2000-2020",
+    breaks = c(-3.5, 0, 3.5),
+    labels = function(x) percent(x/10, 1)
+  ) +
+  scale_y_continuous(
+    "Estimated rate or scale score",
+    breaks = pretty_breaks()
+  ) +
+  geom_blank() +
+  geom_ribbon(
+    data = means_region,
+    aes(ymin = .lower, ymax = .upper),
+    alpha = .15, fill = "dodgerblue4"
+  ) +
+  geom_line(
+    data = means_region,
+    col = "dodgerblue4", size = .6
+  ) +
+  geom_line(
+    aes(group = country), 
+    size = .4, alpha = .35, col = "dodgerblue1"
+  ) +
+  # geom_text(
+  #   data = bind_rows(anx_draws, dep_draws, sel_draws) %>% 
+  #     group_by(outcome) %>% 
+  #     summarise(parameters(cur_data()[-c(1:3)])) %>% 
+  #     mutate(region = str_replace(Parameter, "\\.", "\n")) %>% 
+  #     mutate(outcome = if_else(outcome=="Selfharm", "Self-harm", outcome)) %>% 
+  #     filter(region != "Average") %>% 
+  #     mutate(across(where(is.numeric), ~round(., 2))),
+  #   aes(x = -Inf, y = Inf, label = str_glue("{Median}\n[{CI_low}, {CI_high}]")),
+  #   col = "dodgerblue4", size = 2, vjust = 1.1, hjust = -0.1, family = Font
+  # ) +
+facet_grid(outcome~region, scales = "free_y") +
+  theme(panel.spacing = unit(2, "pt"))
+```

### 2021-11-18 03-analysis.Rmd
More post processing

@@
 ```{r}
+fits_2c <- tibble(
+  cause = c("Anxiety", "Depression"),
+  fit = list(read_rds("output/brm-2c-Anxiety.rds"), read_rds("output/brm-2c-Depression.rds"))
+)
 f2d <- fits_2c %>% 
@@
         fit, 
-        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
+        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
           summarise_draws(samples = length, default_convergence_measures())
@@
 ```{r}
-fits_2 <- reduce(
-  list(
-    fits_2b %>% rename(fit_2b = fit), 
-    fits_2c %>% rename(fit_2c = fit)
-  ), 
-  left_join
-) %>% 
-  pivot_longer(fit_2b:fit_2c, names_to = "model", values_to = "fit")
-fits_2 %>% 
+fits_2c %>% 
   mutate(
@@
     result = str_glue(
-      "b = {mean} ({`2.5%`}, {`97.5%`}) [rhat = {round(rhat, 2)}]"
+      "b = {mean} ({`2.5%`}, {`97.5%`})"
     )
@@
   select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = model, values_from = result) %>% 
+  pivot_wider(names_from = cause, values_from = result) %>% 
   kbl() %>% 
@@
 ```{r}
-fits_brm_internet_interactions %>% 
+tmp <- fits_2c %>% 
   mutate(
@@
       fit, 
-      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
-        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
-    )
-  ) %>% 
-  select(-fit) %>% 
+      ~emtrends(.x, var = "i1_cw", by = c("sex", "age"))
+    )
+  ) %>% 
+  select(-fit)
+tmp %>% 
+  mutate(out = map(out, ~as.data.frame(out))) %>% 
   unnest(out) %>% 
-  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
+  select(cause, sex, age, i1_cw.trend, lower.HPD, upper.HPD) %>% 
   kbl(digits = 3) %>% 

### 2021-11-18 03-analysis.Rmd
More ppc and plots

@@
 
+```{r}
+pp_check(
+  fits_1c$fit[[1]], 
+  ndraws = 30, 
+  resp = "internet", 
+  newdata = fits_1c$fit[[1]]$data
+  )
+
+pp_check(
+  fits_1c$fit[[1]], 
+  ndraws = 10, 
+  type = "dens_overlay_grouped",
+  group = "region",
+  resp = "val", 
+  newdata = fits_1c$fit[[1]]$data
+)
+```
+
 ### Summary
@@
 ```{r}
-
 tmp_coefs <- fits_1c %>% 
@@
     aes(x = make_date(2000), y = Inf, label = result),
-    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
+    size = 2.4, vjust = .9, hjust = 0.05, color = "dodgerblue4",
     family = Font,
@@
       data = country_ellipse,
-      aes(x = x, y = y), 
+      aes(x = x, y = y, group = .draw), 
       alpha = .2, size = .1, col = "dodgerblue1"
@@
 ```{r}
-draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
-draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
-draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
-```
-
-```{r}
-p_time_main_correlations <- (p_cor_country_anx |
-                               p_cor_country_dep |
-                               p_cor_country_sel)
-
+p1 <- draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
+p2 <- draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
+p3 <- draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
+```
+
+```{r}
 (wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
@@
     wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  p_time_main_correlations
-
-p_time_main_coefs /
-  p_time_main_correlations
-```
-
-```{r time-correlation-depression}
-# Get average and region
-r_region_depression <- fit_dep %>% 
-  spread_draws(
-    b_Depression_time, 
-    b_internet_time,
-    r_region__Depression[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_depression <- fit_dep %>% 
-  spread_draws(
-    r_country__Depression[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_dep$data$country))
-    )
-  ) %>% 
-  left_join(distinct(dat, region, country))
-
-# Calculate country coefficients
-country_depression <- left_join(r_country_depression, r_region_depression) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    depression = b_Depression_time + r_region__Depression + r_country__Depression
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, depression)
-
-country_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_country__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_depression_ellipse <- spread_draws(
-  fit_dep,
-  b_Depression_time, b_internet_time,
-  cor_region__internet_time__Depression_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Depression_time, 
-        y = b_internet_time, 
-        z = b_Depression_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_depression_cor <- fit_dep %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Depression_time",
-      "cor_region__internet_time__Depression_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_depression_result <- country_depression_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_dep <- country_depression %>% 
-  ggplot(aes(internet, depression)) +
-  # geom_path(
-  #   data = region_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_depression_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear depression trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_depression_result %>% 
-      filter(variable == "cor_country__internet_time__Depression_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r time-correlation-selfharm}
-# Get average and region
-r_region_selfharm <- fit_sel %>% 
-  spread_draws(
-    b_Selfharm_time, 
-    b_internet_time,
-    r_region__Selfharm[region, term],
-    r_region__internet[region, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by replacing dot with line break
-  mutate(region = str_replace(region, "\\.", "\n"))
-
-# Then country
-r_country_selfharm <- fit_sel %>% 
-  spread_draws(
-    r_country__Selfharm[country, term],
-    r_country__internet[country, term]
-  ) %>% 
-  filter(term == "time") %>% 
-  ungroup() %>% 
-  # Fix names by taking labels from original names
-  mutate(
-    country = factor(
-      country, 
-      labels = sort(unique(fit_sel$data$country))
-    )
-  ) %>% 
-  left_join(distinct(dat, region, country))
-
-# Calculate country coefficients
-country_selfharm <- left_join(r_country_selfharm, r_region_selfharm) %>% 
-  mutate(
-    internet = b_internet_time + r_region__internet + r_country__internet,
-    selfharm = b_Selfharm_time + r_region__Selfharm + r_country__Selfharm
-  ) %>% 
-  group_by(country, region) %>% 
-  median_qi(internet, selfharm)
-
-country_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_country__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_country__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-region_selfharm_ellipse <- spread_draws(
-  fit_sel,
-  b_Selfharm_time, b_internet_time,
-  cor_region__internet_time__Selfharm_time, 
-  ndraws = 100
-) %>% 
-  mutate(
-    e = pmap(
-      list(
-        x = cor_region__internet_time__Selfharm_time, 
-        y = b_internet_time, 
-        z = b_Selfharm_time
-      ), 
-      function(x, y, z) ellipse::ellipse(x, centre = c(y, z), level = .8) %>% 
-        as_tibble()
-    )
-  ) %>% 
-  unnest(e)
-
-country_selfharm_cor <- fit_sel %>%
-  as_draws_df(
-    variable = c(
-      "cor_country__internet_time__Selfharm_time",
-      "cor_region__internet_time__Selfharm_time"
-    ),
-    regex = TRUE
-  ) %>% 
-  as_tibble()
-country_selfharm_result <- country_selfharm_cor %>%   
-  summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95))) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue("{`50%`} [{`5%`}, {`95%`}]"))
-
-p_cor_country_sel <- country_selfharm %>% 
-  ggplot(aes(internet, selfharm)) +
-  # geom_path(
-  #   data = region_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue4"
-  # ) +
-  # geom_path(
-  #   data = country_selfharm_ellipse, 
-  #   aes(x=x, y=y), alpha = .2, size = .1, col = "dodgerblue1"
-  # ) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .75) +
-  scale_x_continuous(
-    "Linear internet trend",
-    breaks = pretty_breaks()
-  ) +
-  scale_y_continuous(
-    "Linear selfharm trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_richtext(
-    data = country_selfharm_result %>% 
-      filter(variable == "cor_country__internet_time__Selfharm_time"),
-    aes(x = -Inf, y = Inf, label = result),
-    size = 3, vjust = 1, hjust = -0.1, color = "dodgerblue4",
-    family = Font,
-    fill = NA, label.color = NA
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-```{r}
-p_cor_country_anx + theme(axis.title.x = element_blank()) | 
-  p_cor_country_dep | 
-  p_cor_country_sel + theme(axis.title.x = element_blank())
+  (p1 | p2 | p3)
 ```

### 2021-11-19 03-analysis.Rmd
Edits

@@
   threads = 2,
-  iter = 300, 
-  warmup = 200,
+  iter = 1500, 
+  warmup = 1000,
   refresh = 10,
-  adapt_delta = .9, 
-  max_treedepth = 10
+  adapt_delta = .95, 
+  max_treedepth = 11
 )
@@
 
-All the outcome variables are proportions (0-1) at this point. This creates problems with the HMC because the self-harm rates are so low. HMC works better with variables roughly on the unit scale.
+All the outcome variables are proportions (0-1) at this point.
+They need to be rescaled for HMC efficiency (self-harm models do not converge at this scale.) So remember to back-transform when interpreting results!
 
@@
 # Important: do this for both val AND se
-# Multiply by 1000
 dat <- dat %>% 
   group_by(cause) %>% 
-  mutate(across(val:se, ~.x*1000)) %>% 
+  mutate(across(val:se, ~.x*100)) %>% 
   ungroup()
@@
   summarise(median = median(val), min = min(val), max = max(val))
-
-# # It is then easy to back-transform
-# dat %>% 
-#   left_join(dat_scales) %>% 
-#   group_by(cause) %>% 
-#   mutate(
-#     val = rescale(val, to = c(unique(min), unique(max))),
-#     se = rescale(val, to = c(unique(min), unique(max)))
-#   ) %>% 
-#   summarise(median = median(val), min = min(val), max = max(val))
 ```
@@
 
-```{r}
+```{r eval = FALSE}
 fit_1b <- brm(
@@
 
-fit_1c <- brm(
-  bf_itu + bf_1c + set_rescor(FALSE),
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-1c"
-)
-
+# Regression coefficients
+p <- prior(normal(0, .5), class = b, resp = val) +
+  prior(normal(0, 1), class = b, coef = sex1, resp = val) +
+  # Standard deviations
+  prior(
+    student_t(7, 0, .5), 
+    class = sd, resp = val, group = region
+  ) +
+  prior(
+    student_t(7, 0, 1.5), 
+    class = sd, resp = val, group = region, coef = Intercept
+  ) +
+  prior(
+    student_t(7, 0, .5), 
+    class = sd, resp = val, group = country
+  ) +
+  prior(
+    student_t(7, 0, 1.5), 
+    class = sd, resp = val, group = country, coef = Intercept
+  ) +
+  # Correlations
+  prior(lkj(2), class = cor, group = country) +
+  prior(lkj(2), class = cor, group = region)
+
+# Compile model separately for each outcome to give independent default priors
 fits_1c <- dat %>%
@@
     fit = list(
-      update(
-        fit_1c, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
+      brm(
+        formula = bf_itu + bf_1c + set_rescor(FALSE), 
+        data = cur_data_all(),
+        prior = p,
+        sample_prior = "yes",
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
         control = list(
@@
 ```{r}
-pp_check(
-  fits_1c$fit[[1]], 
-  ndraws = 30, 
-  resp = "internet", 
-  newdata = fits_1c$fit[[1]]$data
-  )
-
-pp_check(
-  fits_1c$fit[[1]], 
+tmp <- fits_1c %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~pp_check(
+        .x, 
         ndraws = 10, 
@@
         resp = "val", 
-  newdata = fits_1c$fit[[1]]$data
+        newdata = .x$data
+      ) + facet_wrap("group", nrow = 1, scales = "free")
+    )
+  )
+wrap_plots(tmp$out, nrow = 3) &
+  scale_x_continuous(
+    breaks = pretty_breaks(2),
+    labels = function(x) percent(x/100)
   )
@@
 ```{r}
-fits_1 <- reduce(
-  list(
-    fits_1a %>% rename(fit_1a = fit), 
-    fits_1b %>% rename(fit_1b = fit),
-    fits_1c %>% rename(fit_1c = fit)
-  ), 
-  left_join
-) %>% 
-  pivot_longer(fit_1a:fit_1c, names_to = "model", values_to = "fit")
 fits_1 %>% 
@@
         # Rescale coefficient here to years on %
+        # Note self harm doesnt work now
         c(str_glue("val_year = 0")),
@@
   mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
+  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
   select(cause, region = Group, result)
@@
     aes(x = make_date(2000), y = Inf, label = result),
-    size = 2.4, vjust = .9, hjust = 0.05, color = "dodgerblue4",
+    size = 2.4, vjust = .9, hjust = 0.05, color = "black",
     family = Font,
@@
     (year + sex + age + i1_cw | region),
-  family = gaussian()
+  family = gaussian(), 
+  unused = ~ cause # Save this variable in the data frame
 )
@@
 
-fit_2c <- brm(
-  bf_2c,
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-2c"
-)
-
+# Regression coefficients
+p <- prior(normal(0, .5), class = b) +
+  prior(normal(0, 1), class = b, coef = sex1) +
+  # Standard deviations
+  prior(
+    student_t(7, 0, .5), class = sd, group = region
+  ) +
+  prior(
+    student_t(7, 0, 1.5), 
+    class = sd, group = country, coef = Intercept
+  ) +
+  prior(
+    student_t(7, 0, .5), class = sd, group = region
+  ) +
+  prior(
+    student_t(7, 0, 1.5), 
+    class = sd, resp = val, group = country, coef = Intercept
+  ) +
+  # Correlations
+  prior(lkj(2), class = cor, group = country) +
+  prior(lkj(2), class = cor, group = region)
+
+# Compile model separately for each outcome to give independent default priors
 fits_2c <- dat %>%
@@
     fit = list(
-      update(
-        fit_2c, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
+      brm(
+        formula = bf_2c, 
+        data = cur_data_all(),
+        prior = p,
+        sample_prior = "yes",
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
         file = str_glue("output/brm-2c-{cur_group()}")
@@
 ```{r}
-fits_2c <- tibble(
-  cause = c("Anxiety", "Depression"),
-  fit = list(read_rds("output/brm-2c-Anxiety.rds"), read_rds("output/brm-2c-Depression.rds"))
-)
 f2d <- fits_2c %>% 
@@
 
+```{r}
+tmp <- fits_2c %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~pp_check(
+        .x, 
+        ndraws = 10, 
+        type = "dens_overlay_grouped",
+        group = "region",
+        resp = "val", 
+        newdata = .x$data
+      ) + 
+        facet_wrap("group", nrow = 1, scales = "free_y")
+    )
+  )
+wrap_plots(tmp$out, nrow = 3) &
+  scale_x_continuous(
+    breaks = pretty_breaks(2),
+    labels = function(x) percent(x/100, 1)
+  )
+```
+
 ### Summary
@@
 ```{r}
-fits_2c %>% 
+tmp <- fits_2c %>% 
   mutate(
@@
   ) %>% 
+  rowwise() %>% 
   select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = cause, values_from = result) %>% 
+  pivot_wider(names_from = cause, values_from = result)
+tmp %>%   
   kbl() %>% 
@@
 ```{r}
-anx_draws <- spread_draws(
-  fit_anx, 
-  b_i1_cw, r_region[region, term] | region
-) %>% 
+tmp <- fits_2c %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~spread_draws(.x, b_i1_cw, r_region[region, term] | region) %>% 
         filter(term == "i1_cw") %>% 
@@
         select(-term) %>% 
-  rename(Average = b_i1_cw) %>% 
-  mutate(outcome = "Anxiety")
-dep_draws <- spread_draws(
-  fit_dep, 
-  b_i1_cw, r_region[region, term] | region
-) %>% 
-  filter(term == "i1_cw") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_i1_cw) %>% 
-  mutate(outcome = "Depression")
-sel_draws <- spread_draws(
-  fit_sel, 
-  b_i1_cw, r_region[region, term] | region
-) %>% 
-  filter(term == "i1_cw") %>% 
-  ungroup() %>% 
-  select(-term) %>% 
-  rename(Average = b_i1_cw) %>% 
-  mutate(outcome = "Selfharm")
-
-results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
-  group_by(outcome) %>% 
-  summarise(parameters(cur_data()[-c(1:3)])) %>% 
-  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
+        rename(Average = b_i1_cw) 
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out)
+
+names(tmp) <- str_replace(names(tmp), "\\.", " ")
+
+tmp_text <- tmp %>% 
+  group_by(cause) %>% 
+  summarise(parameters(cur_data()[-c(1:3)], test = "pd")) %>% 
+  rename(region = Parameter) %>% 
   mutate(is_average = region == "Average") %>% 
@@
 
-p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
-  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
-  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
-  mutate(region = fct_relevel(factor(region), "Average")) %>% 
-  mutate(outcome = factor(outcome)) %>% 
-  mutate(is_average = region == "Average") %>% 
-  mutate(region = str_replace(region, "\\.", " ")) %>% 
+p_tmp <- tmp %>% 
+  mutate(across(Africa:`Southern Asia`, ~.+Average)) %>% 
+  pivot_longer(Average:`Southern Asia`, names_to = "region") %>% 
   mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
+  mutate(region = fct_relevel(factor(region), "**Average**")) %>% 
+  mutate(cause = factor(cause)) %>% 
+  mutate(is_average = region == "**Average**") %>% 
   ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
@@
     alpha = 1, .width = c(.9),
-    interval_size = .5,
+    interval_size = 1,
     point_size = 1.5,
@@
   geom_text(
-    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
+    data = tmp_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
     aes(
@@
   ) +
-  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  facet_wrap("cause", nrow = 1, scales = "free_x") +
   theme(
@@
     wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  p_internet_main_coefs
+  p_tmp
 ```
@@
 ```{r}
-pred_data <- gbd_wide %>% 
-  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
-  filter(country %in% sort(unique(fit_anx$data$country)))
-
-tmp <- epred_draws(
-  fit_anx, pred_data, re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
-)
-
+tmp <- dat %>% 
+  group_by(region, country, cause) %>% 
+  summarise(
+    internet = mean(internet, na.rm = TRUE),
+    val = mean(val, na.rm = TRUE)
+  ) 
 tmp %>% 
-  group_by(region, country, i1_cb) %>% 
-  summarise(mean(.epred))
-
-conditional_effects(fit_anx, "i1_cb")
-
-gbd_wide %>% 
-  group_by(country) %>% 
-  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
-  ggplot(aes(i1_cb, anx)) +
+  group_by(cause, region) %>% 
+  summarise(tidy(lm(scale(val) ~ scale(internet), data = cur_data()))) %>% 
+  filter(term != "(Intercept)") 
+tmp %>% 
+  ggplot(aes(internet, val)) +
   geom_point() +
-  stat_smooth()
-
-filter(country %in% sort(unique(fit_anx$data$country))) %>% 
-  mutate(time = 0) %>% 
-  group_by(country) %>% 
-  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
-  filter(i1_cw %in% c(xmin, xmax)) %>% 
-  ungroup()
+  stat_smooth(method = "lm", se = F) +
+  facet_grid(cause~region, scales = "free_y")
+
+plot(conditional_effects(fits_2c$fit[[3]], "i1_cb"), points = TRUE)
+x <- conditional_effects(fits_2c$fit[[3]], "i1_cb")[[1]]
+
+x <- fits_2c$fit[[3]]
+y <- fitted(x)
+as_tibble(cbind(x$data, y)) %>% 
+  arrange(desc(Estimate))
 ```
@@
 ```{r}
-# Get some stuff and transform :)
-get_draws <- function(fit) {
+tmp <- fits_2c %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~emtrends(.x, var = "i1_cw", by = c("sex"), at = list(age1=0, age2=0))
+    )
+  )
+tmp$out[[1]] %>% summary
+```
+
+Calculate coefficients from contrast coded factors
+
+```{r}
+x <- fits_2c$fit[[1]]
+y <- emtrends(x, var = "i1_cw", by = c("age", "sex"))
+gather_emmeans_draws(y) %>% mean_qi()
+
+contrasts(x$data$sex)
+contrasts(x$data$age)
+h <- c(
+  `Female_10 to 14` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
+  `Female_15 to 19` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
+  `Female_20 to 24` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
+  `Male_10 to 14` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
+  `Male_15 to 19` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
+  `Male_20 to 24` = 
+    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0"
+)
+tmp_avg <- hypothesis(x, h)
+tmp_region <- hypothesis(x, h, scope = "coef", group = "region")
+```
+
+```{r}
+# Get some stuff and transform
+get_draws <- function(x) {
   draws_region <- spread_draws(
-    fit, 
-    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
+    x, 
+    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
     r_region[region, term] | term
@@
     mutate(
-      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
-      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
-      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
-      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
-      Age = `age1:i1_cw` + `b_age1:i1_cw`,
-      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
-    ) %>% 
-    select(region, `15 to 19`:Sex)
+      `10 to 14` = b_i1_cw + i1_cw + 
+        `age1:i1_cw`*1 + `b_age1:i1_cw`*1 +
+        `age2:i1_cw`*0 + `b_age2:i1_cw`*0,
+      `15 to 19` = b_i1_cw + i1_cw + 
+        `age1:i1_cw`*0 + `b_age1:i1_cw`*0 +
+        `age2:i1_cw`*1 + `b_age2:i1_cw`*1,
+      `20 to 24` = b_i1_cw + i1_cw + 
+        `age1:i1_cw`*-1 + `b_age1:i1_cw`*-1 +
+        `age2:i1_cw`*-1 + `b_age2:i1_cw`*-1,
+      Female = b_i1_cw + i1_cw + `sex1:i1_cw`*1 + `b_sex1:i1_cw`*1,
+      Male = b_i1_cw + i1_cw + `sex1:i1_cw`*-1 + `b_sex1:i1_cw`*-1,
+      Age = `20 to 24` - `10 to 14`,
+      Sex = Female - Male
+    ) %>% 
+    select(region, `10 to 14`:Sex)
 
   draws_avg <- spread_draws(
-    fit, 
-    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
-  ) %>% 
-    mutate(
-      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
-      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
-      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
-      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
-      Age = `b_age1:i1_cw`,
-      Sex = `b_sex1:i1_cw`
-    ) %>% 
-    mutate(region = "**Average**") %>% 
-    select(region, `15 to 19`:Sex)
+    x, 
+    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
+  ) %>% 
+    mutate(
+      `10 to 14` = b_i1_cw + `b_age1:i1_cw`*1 + `b_age2:i1_cw`*0,
+      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*0 + `b_age2:i1_cw`*1,
+      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*-1 + `b_age2:i1_cw`*-1,
+      Female = b_i1_cw + `b_sex1:i1_cw`*1,
+      Male = b_i1_cw + `b_sex1:i1_cw`*-1,
+      Age = `20 to 24` - `10 to 14`,
+      Sex = Female - Male
+    ) %>% 
+    select(`10 to 14`:Sex) %>% 
+    mutate(region = "**Average**")
 
@@
 
-draws <- bind_rows(
-  "Anxiety" = get_draws(fit_anx),
-  "Depression" = get_draws(fit_dep),
-  "Selfharm" = get_draws(fit_sel),
-  .id = "outcome"
-)
-
+draws <- fits_2c %>% 
+  mutate(out = map(fit, get_draws)) %>% 
+  select(-fit) %>% 
+  unnest(out)
+
+# Summaries of differences
 draws_sum <- draws %>% 
-  select(outcome, region, Age, Sex) %>% 
-  group_by(outcome, region) %>% 
+  select(cause, region, Age, Sex) %>% 
+  group_by(cause, region) %>% 
   summarise(
@@
 draws %>% 
-  select(outcome, Level, region, `15 to 19`:Male) %>% 
-  pivot_longer(-c(region, Level, outcome), names_to = "Group") %>% 
+  select(cause, Level, region, c(`10 to 14`, `20 to 24`, Female, Male)) %>% 
+  pivot_longer(-c(region, Level, cause), names_to = "Group") %>% 
   mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
   mutate(
-    side = if_else(Group %in% c("15 to 19", "Female"), "top", "bottom")
+    side = if_else(Group %in% c("10 to 14", "Female"), "top", "bottom")
   ) %>% 
@@
       mutate(Group = NA) %>% 
-      filter(outcome %in% c("Anxiety", "Depression", "Selfharm")),
+      filter(cause %in% c("Anxiety", "Depression", "Selfharm")),
     aes(
@@
   ) +
-  facet_grid2(panel ~ outcome, scales = "free_x", axes = "x") +
+  facet_grid2(panel ~ cause, scales = "free_x", axes = "x") +
   guides(
@@
 # Prediction dataframe: Min and max vals are enough for line
-pred_data <- gbd_wide %>% 
-  filter(country %in% sort(unique(fit_anx$data$country))) %>% 
-  mutate(time = 0) %>% 
+x_country <- fits_2c$fit[[1]]$data %>% 
   group_by(country) %>% 
-  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
+  mutate(
+    xmin = min(i1_cw, na.rm = TRUE), 
+    xmax = max(i1_cw, na.rm = TRUE)
+  ) %>% 
   filter(i1_cw %in% c(xmin, xmax)) %>% 
+  mutate(year = 0) %>% 
   ungroup()
-draws_country_anx <- epred_draws(
-  fit_anx, 
-  pred_data,
-  re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
-  ndraws = 100,
-  resp = "Anxiety"
-)
-
-draws_country_dep <- epred_draws(
-  fit_dep, 
-  pred_data,
-  re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
-  ndraws = 100,
-  resp = "Depression"
-)
-
-draws_country_sel <- epred_draws(
-  fit_sel, 
-  pred_data,
-  re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
-    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country), 
-  ndraws = 100,
-  resp = "Selfharm"
-)
-
-pred_data_region <- pred_data %>% 
+
+pred_country <- fits_2c %>% 
+  mutate(
+    pred_country = map(
+      fit, ~epred_draws(
+        .x, 
+        x_country,
+        ndraws = 100
+      ) %>% 
+        group_by(region, country, i1_cw) %>% 
+        mean_qi(.epred)
+    )
+  )
+
+x_region <- x_country %>% 
   distinct(region, sex, age, i1_cb) %>% 
@@
   mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
-  crossing(i1_cw = seq(-4, 4, length = 10)) %>% 
-  mutate(time = 0)
-
-draws_region_anx <- epred_draws(
-  fit_anx, 
-  pred_data_region,
+  crossing(i1_cw = seq(-.4, .4, length = 10)) %>% 
+  mutate(year = 0, se = 1)
+
+pred_region <- fits_2c %>% 
+  mutate(
+    pred_region = map(
+      fit, ~epred_draws(
+        .x, 
+        x_region,
         re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  ndraws = 100,
-  resp = "Anxiety"
-) %>% 
-  mutate(outcome = "Anxiety")
-
-draws_region_dep <- epred_draws(
-  fit_dep, 
-  pred_data_region,
-  re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  ndraws = 100,
-  resp = "Depression"
-) %>% 
-  mutate(outcome = "Depression")
-
-draws_region_sel <- epred_draws(
-  fit_sel, 
-  pred_data_region,
-  re_formula = 
-    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region),
-  ndraws = 100,
-  resp = "Selfharm"
-) %>% 
-  mutate(outcome = "Self-harm")
-
-means_country <- bind_rows(
-  draws_country_anx %>% mutate(outcome = "Anxiety"),
-  draws_country_dep %>% mutate(outcome = "Depression"),
-  draws_country_sel %>% mutate(outcome = "Self-harm")
-) %>% 
-  group_by(outcome, region, country, i1_cw) %>% 
-  summarise(.epred = mean(.epred))
-
-means_region <- bind_rows(
-  draws_region_anx, draws_region_dep, draws_region_sel
-) %>% 
-  group_by(outcome, region, i1_cw) %>% 
-  mean_qi(.epred, .width = .9)
-
-means_region <- pseudo_gwp %>% 
-  distinct(region, outcome=cause) %>% 
-  bind_rows(means_region) %>% 
-  mutate(outcome = fct_inorder(factor(outcome)))
-
-pseudo_gwp %>% 
-  distinct(region, outcome=cause) %>% 
-  bind_rows(means_country) %>% 
-  mutate(outcome = fct_inorder(factor(outcome))) %>% 
+          ~(year * sex + year * age + i1_cw * sex + i1_cw * age | region),
+        ndraws = 100
+      ) %>% 
+        group_by(region, i1_cw) %>% 
+        mean_qi(.epred)
+    )
+  )
+
+pred_region <- pred_region %>% 
+  select(-fit) %>%
+  unnest(pred_region) %>%
+  mutate(cause = fct_rev(fct_inorder(factor(cause))))
+
+pred_country %>% 
+  select(-fit) %>% 
+  unnest(pred_country) %>% 
+  bind_rows(select(pseudo_gwp, region, cause)) %>% 
+  mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
   ggplot(aes(i1_cw, .epred)) +
@@
     "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-3.5, 0, 3.5),
-    labels = function(x) percent(x/10, 1)
+    breaks = c(-.35, 0, .35),
+    labels = function(x) percent(x, 1)
   ) +
@@
   geom_ribbon(
-    data = means_region,
+    data = pred_region,
     aes(ymin = .lower, ymax = .upper),
@@
   geom_line(
-    data = means_region,
+    data = pred_region,
     col = "dodgerblue4", size = .6
@@
   # geom_text(
-  #   data = bind_rows(anx_draws, dep_draws, sel_draws) %>% 
-  #     group_by(outcome) %>% 
-  #     summarise(parameters(cur_data()[-c(1:3)])) %>% 
-  #     mutate(region = str_replace(Parameter, "\\.", "\n")) %>% 
-  #     mutate(outcome = if_else(outcome=="Selfharm", "Self-harm", outcome)) %>% 
-  #     filter(region != "Average") %>% 
-  #     mutate(across(where(is.numeric), ~round(., 2))),
-  #   aes(x = -Inf, y = Inf, label = str_glue("{Median}\n[{CI_low}, {CI_high}]")),
-  #   col = "dodgerblue4", size = 2, vjust = 1.1, hjust = -0.1, family = Font
+  #   data = tmp_text %>% 
+  #     filter(region != "**Average**") %>% 
+  #     bind_rows(select(pseudo_gwp, region, cause)) %>% 
+  #     mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
+  #     mutate(region = str_replace(region, " ", "\n")) %>% 
+  #     mutate(result = paste(Median)),
+  #   aes(x = -Inf, y = Inf, label = result),
+  #   size = 2.4, vjust = .9, hjust = 0.05, color = "black",
+  #   family = Font,
+  #   fill = NA, label.color = NA
   # ) +
-facet_grid(outcome~region, scales = "free_y") +
+  facet_grid(cause~region, scales = "free_y") +
   theme(panel.spacing = unit(2, "pt"))

### 2021-11-22 01-clean.Rmd
Fix imputation
Space

@@
 
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
+# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
 gbd <- gbd %>% 
@@
 itu <- itu_long %>% 
-  mutate(value = value_i) %>% 
+  # Pick non-missing value, from original and imputed
+  mutate(value = coalesce(value, value_i)) %>% 
   select(-value_i) %>% 

### 2021-11-22 03-analysis.Rmd
Estimate model with no SE

@@
 hmc <- list(
-  chains = 6,
-  cores = 6,
-  threads = 2,
+  chains = 4,
+  cores = 4,
+  threads = 3,
   iter = 1500, 
-  warmup = 1000,
+  warmup = 750,
   refresh = 10,
-  adapt_delta = .95, 
-  max_treedepth = 11
+  adapt_delta = .90, 
+  max_treedepth = 10
 )
@@
 
-# Regression coefficients
-p <- prior(normal(0, .5), class = b, resp = val) +
-  prior(normal(0, 1), class = b, coef = sex1, resp = val) +
-  # Standard deviations
-  prior(
-    student_t(7, 0, .5), 
-    class = sd, resp = val, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = region, coef = Intercept
-  ) +
-  prior(
-    student_t(7, 0, .5), 
-    class = sd, resp = val, group = country
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = country, coef = Intercept
-  ) +
-  # Correlations
-  prior(lkj(2), class = cor, group = country) +
-  prior(lkj(2), class = cor, group = region)
-
 # Compile model separately for each outcome to give independent default priors
@@
         data = cur_data_all(),
-        prior = p,
-        sample_prior = "yes",
         chains = hmc$chains, 
@@
 
+bf_1c_no_se <- bf(
+  val ~ 
+    year * sex + year * age + 
+    (year * sex + year * age |c| country) +
+    (year * sex + year * age |r| region),
+  family = gaussian()
+)
+
+# Compile model separately for each outcome to give independent default priors
+fits_1c <- dat %>%
+  group_by(cause) %>% 
+  summarise(
+    fit_no_se = list(
+      brm(
+        formula = bf_itu + bf_1c_no_se + set_rescor(FALSE), 
+        data = cur_data_all(),
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-1c-no-se-{cur_group()}")
+      )
+    )
+  )
 ```
@@
 
-# Regression coefficients
-p <- prior(normal(0, .5), class = b) +
-  prior(normal(0, 1), class = b, coef = sex1) +
-  # Standard deviations
-  prior(
-    student_t(7, 0, .5), class = sd, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, group = country, coef = Intercept
-  ) +
-  prior(
-    student_t(7, 0, .5), class = sd, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = country, coef = Intercept
-  ) +
-  # Correlations
-  prior(lkj(2), class = cor, group = country) +
-  prior(lkj(2), class = cor, group = region)
+bf_2c_no_se <- bf(
+  val ~ 
+    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
+  family = gaussian()
+)
 
@@
         file = str_glue("output/brm-2c-{cur_group()}")
+      )
+    )
+  )
+
+fits_2c <- dat %>%
+  group_by(cause) %>% 
+  summarise(
+    fit_no_se = list(
+      brm(
+        formula = bf_2c_no_se, 
+        data = cur_data_all(),
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2c-no-se-{cur_group()}")
       )

### 2021-11-22 03-model-estimate.Rmd
Split modelling to two files

--- 2021-11-22 03-analysis.Rmd
@@
-# Time trends
+# Model fitting
 
@@
 )
-
-# Parallelisation options: I have hard coded 12 cores here
-# n_cores <- 12
-# n_workers <- floor(n_cores / 4) # 4 chains always
-# cluster <- new_cluster(n_workers)
-# cluster_library(cluster, c("stringr", "dplyr"))
-
-# Run this to delete fitted models and refit
-# unlink(list.files(pattern = "output/brm-.*\\.rds"))
 ```
@@
 
-### Figure: Timecourses and parameters
-
-```{r}
-tmp_coefs <- fits_1c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~hypothesis(
-        .x, 
-        # Rescale coefficient here to years on %
-        # Note self harm doesnt work now
-        c(str_glue("val_year = 0")),
-        scope = "coef",
-        group = "region"
-      )$hypothesis
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
-  select(cause, region = Group, result)
-tmp_coefs
-pseudo_gwp <-
-  bind_rows(
-    distinct(gbd, region, year, val = NA) %>% 
-      crossing(
-        cause = fct_inorder(
-          c(
-            "Negative\nexperiences", 
-            "Positive\nexperiences", 
-            "Life\nsatisfaction"
-          )
-        )
-      )
-  )
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  pseudo_gwp,
-  gbd,
-  itu %>% mutate(cause = "Internet", val = internet)
-) %>% 
-  mutate(cause = fct_inorder(cause)) %>% 
-  group_by(region, country, year, cause) %>% 
-  summarise(mean = mean(val, na.rm = TRUE)) %>% 
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>% 
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    breaks = make_date(c(2000, 2005, 2010, 2015)), 
-    date_labels = "'%y", 
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, cause)), 
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line", 
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(cause~region, scales = "free_y") +
-  theme(
-    legend.position = "none",
-    panel.spacing = unit(3, "pt")
-  ) +
-  geom_richtext(
-    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
-    aes(x = make_date(2000), y = Inf, label = result),
-    size = 2.4, vjust = .9, hjust = 0.05, color = "black",
-    family = Font,
-    fill = NA, label.color = NA
-  )
-```
-
-### Figure: Correlations
-
-Calculate country coefficients and show scatterplots
-
-```{r time-correlation-anxiety}
-# Function to wrangle draws at multiple levels and create scatterplots + ellipses
-draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
-  # Get average and region-specific slopes
-  r_region_draws <- fit %>% 
-    spread_draws(
-      b_val_year, 
-      b_internet_year,
-      r_region__val[region, term],
-      r_region__internet[region, term]
-    ) %>% 
-    filter(term == "year") %>% 
-    ungroup() %>% 
-    # Fix names by replacing dot with line break
-    mutate(region = str_replace(region, "\\.", "\n"))
-
-  # Then country
-  r_country_draws <- fit %>% 
-    spread_draws(
-      r_country__val[country, term],
-      r_country__internet[country, term]
-    ) %>% 
-    filter(term == "year") %>% 
-    ungroup() %>% 
-    # Fix names by taking labels from original names
-    mutate(
-      country = factor(
-        country, 
-        labels = sort(unique(fit$data$country))
-      )
-    ) %>% 
-    left_join(distinct(dat, region, country))
-
-  # Calculate country coefficients
-  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
-    mutate(
-      internet = b_internet_year + r_region__internet + r_country__internet,
-      outcome = b_val_year + r_region__val + r_country__val
-    ) %>% 
-    group_by(country, region) %>% 
-    median_qi(internet, outcome)
-
-  # Create country ellipse data
-  country_ellipse <- spread_draws(
-    fit,
-    b_val_year, 
-    b_internet_year,
-    sd_country__val_year,
-    sd_country__internet_year,
-    cor_country__internet_year__val_year, 
-    ndraws = 100
-  ) %>% 
-    rename(
-      cor = cor_country__internet_year__val_year, 
-      sd_outcome = sd_country__val_year,
-      sd_i = sd_country__internet_year,
-      b_outcome = b_val_year,
-      b_i = b_internet_year
-    ) %>% 
-    mutate(
-      e = pmap(
-        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
-        function(cor, sd_a, sd_i, b_a, b_i) 
-          ellipse(
-            cor, 
-            scale = c(sd_i, sd_outcome), 
-            centre = c(b_i, b_outcome), 
-            level = .90
-          ) %>% 
-          as_tibble()
-      )
-    ) %>% 
-    unnest(e)
-
-  # Correlation
-  country_cor_result <- spread_draws(fit, cor_country__internet_year__val_year) %>% 
-    median_qi(.width = .90) %>% 
-    mutate(across(where(is.numeric), ~round(., 2))) %>%
-    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}
-
-  # Plot
-  country_coefs %>% 
-    ggplot(aes(internet, outcome)) +
-    geom_path(
-      data = country_ellipse,
-      aes(x = x, y = y, group = .draw), 
-      alpha = .2, size = .1, col = "dodgerblue1"
-    ) +
-    geom_vline(xintercept = 0, lty = 2, size = .2) +
-    geom_hline(yintercept = 0, lty = 2, size = .2) +
-    geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-    scale_x_continuous(
-      "Internet trend",
-      breaks = pretty_breaks()
-    ) +
-    scale_y_continuous(
-      breaks = pretty_breaks()
-    ) +
-    annotate(
-      "text",
-      x = Inf, y = Inf, label = country_cor_result,
-      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
-      family = Font
-    )
-}
-```
-
-```{r}
-p1 <- draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
-p2 <- draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
-p3 <- draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
-```
-
-```{r}
-(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
-   wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
-   wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  (p1 | p2 | p3)
-```
-
 ## Model 2
@@
 ```
-
-### Forest plots
-
-figure of coefficients forest plot
-
-```{r}
-tmp <- fits_2c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~spread_draws(.x, b_i1_cw, r_region[region, term] | region) %>% 
-        filter(term == "i1_cw") %>% 
-        ungroup() %>% 
-        select(-term) %>% 
-        rename(Average = b_i1_cw) 
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out)
-
-names(tmp) <- str_replace(names(tmp), "\\.", " ")
-
-tmp_text <- tmp %>% 
-  group_by(cause) %>% 
-  summarise(parameters(cur_data()[-c(1:3)], test = "pd")) %>% 
-  rename(region = Parameter) %>% 
-  mutate(is_average = region == "Average") %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))
-
-p_tmp <- tmp %>% 
-  mutate(across(Africa:`Southern Asia`, ~.+Average)) %>% 
-  pivot_longer(Average:`Southern Asia`, names_to = "region") %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  mutate(region = fct_relevel(factor(region), "**Average**")) %>% 
-  mutate(cause = factor(cause)) %>% 
-  mutate(is_average = region == "**Average**") %>% 
-  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(expand = expansion(c(0.01, .1))) +
-  scale_x_continuous(
-    "Magnitude of association between internet adoption and well-being", 
-    breaks = pretty_breaks(), 
-    expand = expansion(c(.1, .5))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels", 
-    height = .75, adjust = 1.5
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.9),
-    interval_size = 1,
-    point_size = 1.5,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, -.025)
-  ) +
-  geom_text(
-    data = tmp_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
-    aes(
-      x = Inf,
-      label = str_glue("{Median} [{CI_low}, {CI_high}]")
-    )
-  ) +
-  facet_wrap("cause", nrow = 1, scales = "free_x") +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-
-(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
-    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
-    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  p_tmp
-```
-
-### Figure: Between country effects
-
-```{r}
-tmp <- dat %>% 
-  group_by(region, country, cause) %>% 
-  summarise(
-    internet = mean(internet, na.rm = TRUE),
-    val = mean(val, na.rm = TRUE)
-  ) 
-tmp %>% 
-  group_by(cause, region) %>% 
-  summarise(tidy(lm(scale(val) ~ scale(internet), data = cur_data()))) %>% 
-  filter(term != "(Intercept)") 
-tmp %>% 
-  ggplot(aes(internet, val)) +
-  geom_point() +
-  stat_smooth(method = "lm", se = F) +
-  facet_grid(cause~region, scales = "free_y")
-
-plot(conditional_effects(fits_2c$fit[[3]], "i1_cb"), points = TRUE)
-x <- conditional_effects(fits_2c$fit[[3]], "i1_cb")[[1]]
-
-x <- fits_2c$fit[[3]]
-y <- fitted(x)
-as_tibble(cbind(x$data, y)) %>% 
-  arrange(desc(Estimate))
-```
-
-### Sex and Age
-
-```{r}
-tmp <- fits_2c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~emtrends(.x, var = "i1_cw", by = c("sex"), at = list(age1=0, age2=0))
-    )
-  )
-tmp$out[[1]] %>% summary
-```
-
-Calculate coefficients from contrast coded factors
-
-```{r}
-x <- fits_2c$fit[[1]]
-y <- emtrends(x, var = "i1_cw", by = c("age", "sex"))
-gather_emmeans_draws(y) %>% mean_qi()
-
-contrasts(x$data$sex)
-contrasts(x$data$age)
-h <- c(
-  `Female_10 to 14` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
-  `Female_15 to 19` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
-  `Female_20 to 24` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
-  `Male_10 to 14` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
-  `Male_15 to 19` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
-  `Male_20 to 24` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0"
-)
-tmp_avg <- hypothesis(x, h)
-tmp_region <- hypothesis(x, h, scope = "coef", group = "region")
-```
-
-```{r}
-# Get some stuff and transform
-get_draws <- function(x) {
-  draws_region <- spread_draws(
-    x, 
-    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
-    r_region[region, term] | term
-  ) %>% 
-    mutate(
-      `10 to 14` = b_i1_cw + i1_cw + 
-        `age1:i1_cw`*1 + `b_age1:i1_cw`*1 +
-        `age2:i1_cw`*0 + `b_age2:i1_cw`*0,
-      `15 to 19` = b_i1_cw + i1_cw + 
-        `age1:i1_cw`*0 + `b_age1:i1_cw`*0 +
-        `age2:i1_cw`*1 + `b_age2:i1_cw`*1,
-      `20 to 24` = b_i1_cw + i1_cw + 
-        `age1:i1_cw`*-1 + `b_age1:i1_cw`*-1 +
-        `age2:i1_cw`*-1 + `b_age2:i1_cw`*-1,
-      Female = b_i1_cw + i1_cw + `sex1:i1_cw`*1 + `b_sex1:i1_cw`*1,
-      Male = b_i1_cw + i1_cw + `sex1:i1_cw`*-1 + `b_sex1:i1_cw`*-1,
-      Age = `20 to 24` - `10 to 14`,
-      Sex = Female - Male
-    ) %>% 
-    select(region, `10 to 14`:Sex)
-
-  draws_avg <- spread_draws(
-    x, 
-    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
-  ) %>% 
-    mutate(
-      `10 to 14` = b_i1_cw + `b_age1:i1_cw`*1 + `b_age2:i1_cw`*0,
-      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*0 + `b_age2:i1_cw`*1,
-      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*-1 + `b_age2:i1_cw`*-1,
-      Female = b_i1_cw + `b_sex1:i1_cw`*1,
-      Male = b_i1_cw + `b_sex1:i1_cw`*-1,
-      Age = `20 to 24` - `10 to 14`,
-      Sex = Female - Male
-    ) %>% 
-    select(`10 to 14`:Sex) %>% 
-    mutate(region = "**Average**")
-
-  draws <- bind_rows(
-    "regions" = draws_region,
-    "average" = draws_avg, 
-    .id = "Level"
-  ) %>% 
-    mutate(region = str_replace(region, "\\.", "\n")) %>% 
-    ungroup()
-  draws
-}
-
-draws <- fits_2c %>% 
-  mutate(out = map(fit, get_draws)) %>% 
-  select(-fit) %>% 
-  unnest(out)
-
-# Summaries of differences
-draws_sum <- draws %>% 
-  select(cause, region, Age, Sex) %>% 
-  group_by(cause, region) %>% 
-  summarise(
-    describe_posterior(
-      cur_data(), centrality = "mean", test = "pd"
-    )
-  ) %>% 
-  rename(panel = Parameter) %>% 
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-draws %>% 
-  select(cause, Level, region, c(`10 to 14`, `20 to 24`, Female, Male)) %>% 
-  pivot_longer(-c(region, Level, cause), names_to = "Group") %>% 
-  mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
-  mutate(
-    side = if_else(Group %in% c("10 to 14", "Female"), "top", "bottom")
-  ) %>% 
-  mutate(region = str_replace(region, "\\.", " ")) %>% 
-  mutate(region = fct_relevel(region, "**Average**")) %>% 
-  ggplot(aes(value, region, col = Group, fill = Group)) +
-  scale_alpha_manual(values = c(.6, .3)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(
-    values = c(21, 19), guide = "none"
-  ) +
-  scale_y_discrete(expand = expansion(c(0.1, 0.1))) +
-  scale_x_continuous(
-    "Magnitude of association between internet adoption and well-being", 
-    breaks = pretty_breaks(), 
-    expand = expansion(c(0, .05))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels", 
-    height = .75, adjust = 1.5,
-    aes(side = side, group = side, alpha = Level), 
-    show.legend = FALSE
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.9),
-    interval_size = .33,
-    point_size = 1.25,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
-    position = position_dodgev(.25), key_glyph = draw_key_point
-  ) +
-  geom_richtext(
-    data = draws_sum %>% 
-      mutate(Group = NA) %>% 
-      filter(cause %in% c("Anxiety", "Depression", "Selfharm")),
-    aes(
-      x = Inf, 
-      label = str_glue("*d* = {Mean} (p<sup>d</sup> = {percent(pd, 1)})")
-    ),
-    size = 2.5, hjust = 1,
-    family = Font,
-    fill = NA, label.color = NA,
-    show.legend = FALSE
-  ) +
-  facet_grid2(panel ~ cause, scales = "free_x", axes = "x") +
-  guides(
-    alpha = "none"
-  ) +
-  theme(
-    legend.position = "right",
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown()
-  )
-```
-
-### Fitted lines
-
-Plot of fitted lines
-
-```{r}
-# Prediction dataframe: Min and max vals are enough for line
-x_country <- fits_2c$fit[[1]]$data %>% 
-  group_by(country) %>% 
-  mutate(
-    xmin = min(i1_cw, na.rm = TRUE), 
-    xmax = max(i1_cw, na.rm = TRUE)
-  ) %>% 
-  filter(i1_cw %in% c(xmin, xmax)) %>% 
-  mutate(year = 0) %>% 
-  ungroup()
-
-pred_country <- fits_2c %>% 
-  mutate(
-    pred_country = map(
-      fit, ~epred_draws(
-        .x, 
-        x_country,
-        ndraws = 100
-      ) %>% 
-        group_by(region, country, i1_cw) %>% 
-        mean_qi(.epred)
-    )
-  )
-
-x_region <- x_country %>% 
-  distinct(region, sex, age, i1_cb) %>% 
-  group_by(region) %>% 
-  mutate(i1_cb = mean(i1_cb, na.rm = T)) %>% 
-  crossing(i1_cw = seq(-.4, .4, length = 10)) %>% 
-  mutate(year = 0, se = 1)
-
-pred_region <- fits_2c %>% 
-  mutate(
-    pred_region = map(
-      fit, ~epred_draws(
-        .x, 
-        x_region,
-        re_formula = 
-          ~(year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-        ndraws = 100
-      ) %>% 
-        group_by(region, i1_cw) %>% 
-        mean_qi(.epred)
-    )
-  )
-
-pred_region <- pred_region %>% 
-  select(-fit) %>%
-  unnest(pred_region) %>%
-  mutate(cause = fct_rev(fct_inorder(factor(cause))))
-
-pred_country %>% 
-  select(-fit) %>% 
-  unnest(pred_country) %>% 
-  bind_rows(select(pseudo_gwp, region, cause)) %>% 
-  mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
-  ggplot(aes(i1_cw, .epred)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimated rate or scale score",
-    breaks = pretty_breaks()
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = pred_region,
-    aes(ymin = .lower, ymax = .upper),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = pred_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country), 
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  # geom_text(
-  #   data = tmp_text %>% 
-  #     filter(region != "**Average**") %>% 
-  #     bind_rows(select(pseudo_gwp, region, cause)) %>% 
-  #     mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
-  #     mutate(region = str_replace(region, " ", "\n")) %>% 
-  #     mutate(result = paste(Median)),
-  #   aes(x = -Inf, y = Inf, label = result),
-  #   size = 2.4, vjust = .9, hjust = 0.05, color = "black",
-  #   family = Font,
-  #   fill = NA, label.color = NA
-  # ) +
-  facet_grid(cause~region, scales = "free_y") +
-  theme(panel.spacing = unit(2, "pt"))
-```

### 2021-11-22 04-model-inference.Rmd
Split modelling to two files

--- 2021-11-19 03-analysis.Rmd
@@
-# Time trends
+# Model inference
 
@@
 library(brms)
-library(cmdstanr)
-library(ellipse)
 library(broom.mixed)
@@
 library(tidyverse)
-
-# MCMC settings
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = 6,
-  cores = 6,
-  threads = 2,
-  iter = 1500, 
-  warmup = 1000,
-  refresh = 10,
-  adapt_delta = .95, 
-  max_treedepth = 11
-)
-
-# Parallelisation options: I have hard coded 12 cores here
-# n_cores <- 12
-# n_workers <- floor(n_cores / 4) # 4 chains always
-# cluster <- new_cluster(n_workers)
-# cluster_library(cluster, c("stringr", "dplyr"))
-
-# Run this to delete fitted models and refit
-# unlink(list.files(pattern = "output/brm-.*\\.rds"))
 ```
@@
 
-## Prepare data for models
+## Read models from file
 
-Preparing the variables:
-
-- Transform edge values of internet variable to fit beta
-- center year on 2010 (roughly in the middle)
-- Intercept and simple effects at 2010
-- 1 unit: year
-- create 1-year lagged internet adoption variables
-- Intercepts are country/grand means
-- 1 unit: 100%
-- Contrast code factors
-
-```{r data-prepare}
-# Predictors
-
-# Transform edge proportions to fit beta distribution
-itu <- itu %>% 
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Create lagged predictors
-itu <- itu %>% 
-  arrange(country, year) %>% 
-  group_by(country) %>% 
-  mutate(
-    across(
-      c(internet, fixed, mobile), 
-      list(`1` = ~lag(., 1)), 
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  )
-
-# Centering within and between countries
-itu <- itu %>%
-  group_by(country) %>% 
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb # Year-specific deviation from country average
-  ) %>% 
-  ungroup() %>% 
-  # Grand-mean center the country averages
-  mutate(i1_cb = i1_cb - mean(i1, na.rm = TRUE))
-
-# Outcomes
-
-# Merge predictors to outcomes
-dat <- left_join(gbd, itu)
-
-# Center and scale year, and contrast code factors
-dat <- dat %>% 
-  mutate(year = (year - 2010) / 10)
-dat$sex <- factor(dat$sex)
-contrasts(dat$sex) <- "contr.sum"
-dat$age <- factor(dat$age)
-contrasts(dat$age) <- "contr.sum"
-
-# For brms multivariate data subsetting: variable to indicate unique ITU values
-dat <- dat %>% 
-  group_by(country, year) %>% 
-  mutate(itu = 1:n() == 1) %>% 
-  ungroup()
+```{r}
+# Read models from files to data frames
 ```
 
-All the outcome variables are proportions (0-1) at this point.
-They need to be rescaled for HMC efficiency (self-harm models do not converge at this scale.) So remember to back-transform when interpreting results!
-
-```{r}
-# Save this so its easy to use later to back-transform
-dat %>%
-  group_by(cause) %>%
-  summarise(median = median(val), min = min(val), max = max(val))
-
-# Important: do this for both val AND se
-dat <- dat %>% 
-  group_by(cause) %>% 
-  mutate(across(val:se, ~.x*100)) %>% 
-  ungroup()
-
-dat %>%
-  group_by(cause) %>%
-  summarise(median = median(val), min = min(val), max = max(val))
-```
-
-## Model 1
-
-The first model addresses our first research question: To what extent did the outcomes change over time. It will also answer whether changes were different across the demographic groups.
-
-It will also begin to address the issue of associations between internet adoption and well-being, by including a correlation between the country-specific trends in internet adoption and outcomes.
-
-We fit three incrementally more complex versions of this model. First, without demographic covariates, second with, and third with the two-way interactions with time.
-
-We fit the model separately for each outcome.
-
-### Model 1a
-
-Model 1a is a multivariate multilevel model of internet adoption and outcome (e.g.
-Anxiety) over time.
-The intercepts and coefficients of time are allowed to vary across regions and countries, with a shared correlation matrix of the random effects across the two outcomes.
-
-Internet adoption is treated as Beta-distributed. Outcome rates, the GBD estimates, are treated as Gaussian with a known standard error, resulting in a "meta-regression" model of the outcomes.
-
-$$
-\begin{align*}
-y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}v_i) \\
-
-\mu^y_{i[c][r]} &= \beta^{y}_{0} + \gamma^{y}_{0[c]} + \delta^{y}_{0[r]} +
-\beta^y_{1}\text{t}_i + \gamma^{y}_{1[c]}\text{t}_i + \delta^{y}_{1[r]}\text{t}_i  \\
-
-x_{i[c][r]} &\sim 
-\text{Beta}(\mu^x_{i[c][r]}, \phi^x) \\
-
-\mu^x_{i[c][r]} &= \text{logit}(
-\beta^{x}_{0} + \gamma^{x}_{0[c]} + \delta^{x}_{0[r]} +
-\beta^x_{1}\text{t}_i + \gamma^{x}_{1[c]}\text{t}_i + \delta^{x}_{1[r]}\text{t}_i) \\
-
-\left[\begin{array}{c}
-\gamma^y_{0[c]} \\ \gamma^y_{1[c]} \\ \gamma^x_{0[c]} \\ \gamma^x_{1[c]}
-\end{array}\right] 
-&\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^c
-),
-
-\left[\begin{array}{c}
-\delta^y_{0[r]} \\ \delta^y_{1[r]} \\ \delta^x_{0[r]} \\ \delta^x_{1[r]}
-\end{array}\right] 
-\sim MVN(
-\left[\begin{array}{c}
-0 \\ 0 \\ 0 \\ 0
-\end{array}\right],
-\Sigma^r
-)
-\end{align*}
-$$
-
-We then define the model formulas in brms' formula syntax.
-First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
-To do this we use `resp_subset(itu)`, which includes only unique rows of ITU data in the model.
-The `|c|` and `|r|` separating the random effects from their grouping factors indicate a shared correlation matrix, also indicated in the next model formula.
-
-```{r}
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~ 
-    year + 
-    (year |c| country) +
-    (year |r| region), 
-  family = Beta()
-)
-```
-
-Here, we specify the outcome model.
-Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
-Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
-In addition, it leads to the residual variance to be estimated.
-
-```{r}
-# Define models of outcomes
-bf_1a <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + 
-    (year |c| country) +
-    (year |r| region),
-  family = gaussian()
-)
-```
-
-We then compile the model once, such that it can be updated with subsets of the data (the different outcomes) without having to compile again.
-
-```{r}
-fit_1a <- brm(
-  bf_itu + bf_1a + set_rescor(FALSE),
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-1a"
-)
-```
-
-Then fit the model. Note we don't need this for now because the relevant estimates are provided by model 1c.
-
-```{r eval = FALSE}
-fits_1a <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_1a, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
-        file = str_glue("output/brm-1a-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Model 1b
-
-Model 1b is as 1a but we include age (10 to 14, 15 to 19, 20 to 24) and sex as covariates.
-
-```{r}
-bf_1b <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + sex + age + 
-    (year + sex + age |c| country) +
-    (year + sex + age |r| region),
-  family = gaussian()
-)
-```
-
-Then fit the model as above, first compiling and then updating for each outcome. Note not fitted for now--relevant estimates are in model 1c.
-
-```{r eval = FALSE}
-fit_1b <- brm(
-  bf_itu + bf_1b + set_rescor(FALSE),
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-1b"
-)
-
-fits_1b <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_1b, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
-        file = str_glue("output/brm-1b-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Model 1c
-
-Model 1c further expands 1b to include the two-way interactive terms between age and year, and sex and year.
-Thus we get age and sex-specific trajectories over time.
-We reuse the prior distributions from 1b.
-
-This takes about 3.5 hours per 1000 iterations (per model).
-
-```{r}
-bf_1c <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year * sex + year * age + 
-    (year * sex + year * age |c| country) +
-    (year * sex + year * age |r| region),
-  family = gaussian()
-)
-
-# Regression coefficients
-p <- prior(normal(0, .5), class = b, resp = val) +
-  prior(normal(0, 1), class = b, coef = sex1, resp = val) +
-  # Standard deviations
-  prior(
-    student_t(7, 0, .5), 
-    class = sd, resp = val, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = region, coef = Intercept
-  ) +
-  prior(
-    student_t(7, 0, .5), 
-    class = sd, resp = val, group = country
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = country, coef = Intercept
-  ) +
-  # Correlations
-  prior(lkj(2), class = cor, group = country) +
-  prior(lkj(2), class = cor, group = region)
-
-# Compile model separately for each outcome to give independent default priors
-fits_1c <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      brm(
-        formula = bf_itu + bf_1c + set_rescor(FALSE), 
-        data = cur_data_all(),
-        prior = p,
-        sample_prior = "yes",
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-1c-{cur_group()}")
-      )
-    )
-  )
-
-```
-
-### Checking
-
-Diagnostics: convergence and effective samples size
-
-```{r}
-f1d <- fits_1c %>% 
-  mutate(
-    out = 
-      map(
-        fit, 
-        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
-          summarise_draws(samples = length, default_convergence_measures())
-      )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out)
-f1d %>%  
-  kbl(
-    caption = "HMC Diagnostics, Model 1c",
-    digits = c(0,0,0,2,0,0)
-  ) %>% 
-  kable_paper(html_font = Font) %>% 
-  column_spec(
-    4, 
-    color = "white",
-    background = spec_color(
-      f1d$rhat, 
-      direction = 1, 
-      option = "C", 
-      end = .7
-    )
-  )
-```
-
-```{r}
-tmp <- fits_1c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~pp_check(
-        .x, 
-        ndraws = 10, 
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val", 
-        newdata = .x$data
-      ) + facet_wrap("group", nrow = 1, scales = "free")
-    )
-  )
-wrap_plots(tmp$out, nrow = 3) &
-  scale_x_continuous(
-    breaks = pretty_breaks(2),
-    labels = function(x) percent(x/100)
-  )
-```
-
-### Summary
-
-We then display the model's population-level parameters
-
-```{r}
-fits_1 %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
-        summarise_draws(
-          mean, quantile, rhat, 
-          .args = list(probs = c(.025, .975))
-        )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(
-    result = str_glue(
-      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
-    )
-  ) %>% 
-  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = model, values_from = result) %>% 
-  kbl() %>% 
-  kable_paper(html_font = Font)
-```
+## Time courses
 
@@
 
-## Model 2
-
-Model 2 is a modification of Model 1.
-First, we now switch to looking at internet use more specifically as a predictor, and therefore implement a univariate model of each outcome.
-Second, we include within- and between-country centred 1-year-lagged internet adoption values as predictors in the model.
-
-We fit this model in two increasingly complex forms, corresponding to models 1b and 1c, but with the addition of the internet adoption predictors, and one outcome model only.
-
-2c takes about 5 hours per 1000 iterations.
-
-```{r}
-bf_2b <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + sex + age + i1_cw + i1_cb +
-    (year + sex + age + i1_cw | country) +
-    (year + sex + age + i1_cw | region),
-  family = gaussian(), 
-  unused = ~ cause # Save this variable in the data frame
-)
-fit_2b <- brm(
-  bf_2b,
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-2b"
-)
-fits_2b <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_2b, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2b-{cur_group()}")
-      )
-    )
-  )
-
-bf_2c <- bf(
-  val | se(se, sigma = TRUE) ~ 
-    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-# Regression coefficients
-p <- prior(normal(0, .5), class = b) +
-  prior(normal(0, 1), class = b, coef = sex1) +
-  # Standard deviations
-  prior(
-    student_t(7, 0, .5), class = sd, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, group = country, coef = Intercept
-  ) +
-  prior(
-    student_t(7, 0, .5), class = sd, group = region
-  ) +
-  prior(
-    student_t(7, 0, 1.5), 
-    class = sd, resp = val, group = country, coef = Intercept
-  ) +
-  # Correlations
-  prior(lkj(2), class = cor, group = country) +
-  prior(lkj(2), class = cor, group = region)
-
-# Compile model separately for each outcome to give independent default priors
-fits_2c <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      brm(
-        formula = bf_2c, 
-        data = cur_data_all(),
-        prior = p,
-        sample_prior = "yes",
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2c-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Checking
-
-Diagnostics: convergence and effective samples size
-
-```{r}
-f2d <- fits_2c %>% 
-  mutate(
-    out = 
-      map(
-        fit, 
-        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
-          summarise_draws(samples = length, default_convergence_measures())
-      )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out)
-f2d %>%  
-  kbl(
-    caption = "HMC Diagnostics, Model 2c",
-    digits = c(0,0,0,2,0,0)
-  ) %>% 
-  kable_paper(html_font = Font, full_width = FALSE) %>% 
-  column_spec(
-    4, 
-    color = "white",
-    background = spec_color(
-      f2d$rhat, 
-      direction = 1, 
-      option = "C", 
-      end = .7
-    )
-  ) %>% 
-  scroll_box(height = "600px", width = "800px")
-```
-
-```{r}
-tmp <- fits_2c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~pp_check(
-        .x, 
-        ndraws = 10, 
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val", 
-        newdata = .x$data
-      ) + 
-        facet_wrap("group", nrow = 1, scales = "free_y")
-    )
-  )
-wrap_plots(tmp$out, nrow = 3) &
-  scale_x_continuous(
-    breaks = pretty_breaks(2),
-    labels = function(x) percent(x/100, 1)
-  )
-```
-
-### Summary
-
-We then display the model's population-level parameters
-
-```{r}
-tmp <- fits_2c %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
-        summarise_draws(
-          mean, quantile, rhat, 
-          .args = list(probs = c(.025, .975))
-        )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(
-    result = str_glue(
-      "b = {mean} ({`2.5%`}, {`97.5%`})"
-    )
-  ) %>% 
-  rowwise() %>% 
-  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = cause, values_from = result)
-tmp %>%   
-  kbl() %>% 
-  kable_paper(html_font = Font) 
-```
+## Association with internet adoption
 

### 2021-11-22 03-model-estimate.Rmd
Refactor model fitting code

@@
 ```{r data-prepare}
-# Predictors
-
-# Transform edge proportions to fit beta distribution
-itu <- itu %>% 
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Create lagged predictors
-itu <- itu %>% 
-  arrange(country, year) %>% 
-  group_by(country) %>% 
-  mutate(
-    across(
-      c(internet, fixed, mobile), 
-      list(`1` = ~lag(., 1)), 
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  )
-
-# Centering within and between countries
-itu <- itu %>%
-  group_by(country) %>% 
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb # Year-specific deviation from country average
-  ) %>% 
-  ungroup() %>% 
-  # Grand-mean center the country averages
-  mutate(i1_cb = i1_cb - mean(i1, na.rm = TRUE))
-
-# Outcomes
-
 # Merge predictors to outcomes
@@
 contrasts(dat$age) <- "contr.sum"
-
-# For brms multivariate data subsetting: variable to indicate unique ITU values
-dat <- dat %>% 
-  group_by(country, year) %>% 
-  mutate(itu = 1:n() == 1) %>% 
-  ungroup()
 ```
 
-All the outcome variables are proportions (0-1) at this point.
-They need to be rescaled for HMC efficiency (self-harm models do not converge at this scale.) So remember to back-transform when interpreting results!
+All the outcome variables are proportions (0-1) at this point. We rescale them to percentages (0-100).
 
 ```{r}
-# Save this so its easy to use later to back-transform
-dat %>%
-  group_by(cause) %>%
-  summarise(median = median(val), min = min(val), max = max(val))
-
 # Important: do this for both val AND se
 dat <- dat %>% 
-  group_by(cause) %>% 
-  mutate(across(val:se, ~.x*100)) %>% 
-  ungroup()
-
-dat %>%
-  group_by(cause) %>%
-  summarise(median = median(val), min = min(val), max = max(val))
+  mutate(across(val:se, ~.x*100))
 ```
@@
 
-### Model 1a
+### Model 1
 
@@
 
-Internet adoption is treated as Beta-distributed. Outcome rates, the GBD estimates, are treated as Gaussian with a known standard error, resulting in a "meta-regression" model of the outcomes.
+Internet adoption is treated as Beta-distributed. Outcome rates are treated as gaussian.
+
+Prepare data for this model
+
+```{r}
+dat_model1 <- dat %>% 
+  # Transform edge proportions to fit beta distribution
+  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999, internet)) %>% 
+  # Indicate unique ITU values for MV model...
+  arrange(region, country, year, cause, sex, age) %>% 
+  # ...Use only the first internet value within a year-country
+  group_by(region, country, year) %>% 
+  mutate(itu = 1:n() == 1) %>% 
+  ungroup()
+```
 
@@
 \begin{align*}
-y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}v_i) \\
+y_{i[c][r]} &\sim \text{Normal}(\mu^y_{i[c][r]}, \sigma^{2y}) \\
 
@@
 \end{align*}
+\mathbf{\beta}
 $$
@@
 # Define models of outcomes
-bf_1a <- bf(
+bf_1 <- bf(
+  val ~ 
+    year * sex * age + 
+    (year * sex * age |c| country) +
+    (year * sex * age |r| region),
+  family = gaussian()
+)
+
+bf_1_se <- bf(
   val | resp_se(se, sigma = TRUE) ~ 
-    year + 
-    (year |c| country) +
-    (year |r| region),
+    year * sex * age + 
+    (year * sex * age |c| country) +
+    (year * sex * age |r| region),
   family = gaussian()
@@
 
-We then compile the model once, such that it can be updated with subsets of the data (the different outcomes) without having to compile again.
-
 ```{r}
-fit_1a <- brm(
-  bf_itu + bf_1a + set_rescor(FALSE),
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-1a"
-)
-```
-
-Then fit the model. Note we don't need this for now because the relevant estimates are provided by model 1c.
-
-```{r eval = FALSE}
-fits_1a <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_1a, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
-        file = str_glue("output/brm-1a-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Model 1b
-
-Model 1b is as 1a but we include age (10 to 14, 15 to 19, 20 to 24) and sex as covariates.
-
-```{r}
-bf_1b <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + sex + age + 
-    (year + sex + age |c| country) +
-    (year + sex + age |r| region),
-  family = gaussian()
-)
-```
-
-Then fit the model as above, first compiling and then updating for each outcome. Note not fitted for now--relevant estimates are in model 1c.
-
-```{r eval = FALSE}
-fit_1b <- brm(
-  bf_itu + bf_1b + set_rescor(FALSE),
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-1b"
-)
-
-fits_1b <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_1b, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup,
-        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
-        file = str_glue("output/brm-1b-{cur_group()}")
-      )
-    )
-  )
-```
-
-### Model 1c
-
-Model 1c further expands 1b to include the two-way interactive terms between age and year, and sex and year.
-Thus we get age and sex-specific trajectories over time.
-We reuse the prior distributions from 1b.
-
-This takes about 3.5 hours per 1000 iterations (per model).
-
-```{r}
-bf_1c <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year * sex + year * age + 
-    (year * sex + year * age |c| country) +
-    (year * sex + year * age |r| region),
-  family = gaussian()
-)
-
-# Compile model separately for each outcome to give independent default priors
-fits_1c <- dat %>%
+fits_1 <- dat %>%
   group_by(cause) %>% 
@@
       brm(
-        formula = bf_itu + bf_1c + set_rescor(FALSE), 
+        formula = bf_itu + bf_1 + set_rescor(FALSE), 
         data = cur_data_all(),
@@
         ),
-        file = str_glue("output/brm-1c-{cur_group()}")
+        file = str_glue("output/brm-1-{cur_group()}")
       )
@@
 
-bf_1c_no_se <- bf(
-  val ~ 
-    year * sex + year * age + 
-    (year * sex + year * age |c| country) +
-    (year * sex + year * age |r| region),
-  family = gaussian()
-)
-
-# Compile model separately for each outcome to give independent default priors
-fits_1c <- dat %>%
+fits_1 <- dat %>%
   group_by(cause) %>% 
   summarise(
-    fit_no_se = list(
+    fit_se = list(
       brm(
-        formula = bf_itu + bf_1c_no_se + set_rescor(FALSE), 
+        formula = bf_itu + bf_1_se + set_rescor(FALSE), 
         data = cur_data_all(),
@@
         ),
-        file = str_glue("output/brm-1c-no-se-{cur_group()}")
+        file = str_glue("output/brm-1-se-{cur_group()}")
       )
@@
 ```{r}
-f1d <- fits_1c %>% 
+f1d <- fits_1 %>% 
   mutate(
@@
 ```{r}
-tmp <- fits_1c %>% 
+tmp <- fits_1 %>% 
   mutate(
@@
 
+Prepare data for this model
+
+```{r}
+# Create lagged predictors
+dat <- dat %>% 
+  arrange(region, country, cause, sex, age, year) %>% 
+  group_by(region, country, cause, sex, age) %>% 
+  mutate(
+    across(
+      c(internet, fixed, mobile), 
+      list(`1` = ~lag(., 1)), 
+      .names = "{str_sub(.col, 1, 1)}{.fn}"
+    )
+  )
+
+# Centering within and between countries
+dat <- dat %>%
+  group_by(country) %>% 
+  mutate(
+    i1_cb = mean(i1, na.rm = TRUE), # Country average
+    i1_cw = i1 - i1_cb # Year-specific deviation from country average
+  ) %>% 
+  ungroup() %>% 
+  # Grand-mean center the country averages
+  mutate(i1_cb = i1_cb - mean(i1, na.rm = TRUE))
+```
+
 Model 2 is a modification of Model 1.
@@
 ```{r}
-bf_2b <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year + sex + age + i1_cw + i1_cb +
-    (year + sex + age + i1_cw | country) +
-    (year + sex + age + i1_cw | region),
-  family = gaussian(), 
-  unused = ~ cause # Save this variable in the data frame
-)
-fit_2b <- brm(
-  bf_2b,
-  data = filter(dat, cause == "Anxiety"),
-  chains = 0,
-  threads = hmc$threads,
-  file = "output/brm-2b"
-)
-fits_2b <- dat %>% 
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      update(
-        fit_2b, 
-        newdata = cur_data_all(),
-        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
-        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2b-{cur_group()}")
-      )
-    )
-  )
-
-bf_2c <- bf(
-  val | se(se, sigma = TRUE) ~ 
-    year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-bf_2c_no_se <- bf(
+bf_2 <- bf(
   val ~ 
@@
 
+bf_2_se <- bf(
+  val | se(se, sigma = TRUE) ~ 
+    year * sex * age + i1_cw * sex * age + i1_cb + 
+    (year * sex * age + i1_cw * sex * age | country) +
+    (year * sex * age + i1_cw * sex * age | region),
+  family = gaussian()
+)
+
 # Compile model separately for each outcome to give independent default priors
-fits_2c <- dat %>%
+fits_2 <- dat %>%
   group_by(cause) %>% 
@@
       brm(
-        formula = bf_2c, 
+        formula = bf_2, 
         data = cur_data_all(),
@@
         ),
-        file = str_glue("output/brm-2c-{cur_group()}")
+        file = str_glue("output/brm-2-{cur_group()}")
       )
@@
 
-fits_2c <- dat %>%
+fits_2 <- dat %>%
   group_by(cause) %>% 
   summarise(
-    fit_no_se = list(
+    fit_se = list(
       brm(
-        formula = bf_2c_no_se, 
+        formula = bf_2_se, 
         data = cur_data_all(),
@@
         ),
-        file = str_glue("output/brm-2c-no-se-{cur_group()}")
+        file = str_glue("output/brm-2-se-{cur_group()}")
       )
@@
 ```{r}
-f2d <- fits_2c %>% 
+f2d <- fits_2 %>% 
   mutate(
@@
 ```{r}
-tmp <- fits_2c %>% 
+tmp <- fits_2 %>% 
   mutate(

### 2021-11-22 03-model-estimate.Rmd
Estimate models 1 & 2

@@
   threads = 3,
-  iter = 1500, 
-  warmup = 750,
-  refresh = 10,
+  iter = 2000, 
+  warmup = 1000,
+  refresh = 50,
   adapt_delta = .90, 
@@
   val ~ 
-    year * sex * age + 
-    (year * sex * age |c| country) +
-    (year * sex * age |r| region),
+    year * sex + year * age + 
+    (year * sex + year * age |c| country) +
+    (year * sex + year * age |r| region),
   family = gaussian()
@@
 bf_1_se <- bf(
-  val | resp_se(se, sigma = TRUE) ~ 
-    year * sex * age + 
-    (year * sex * age |c| country) +
-    (year * sex * age |r| region),
-  family = gaussian()
+  bf(val | resp_se(se, sigma = TRUE) ~ 
+       year * sex + year * age +
+       (year * sex + year * age |c| country) +
+       (year * sex + year * age |r| region),
+     sigma ~ 1
+  ),
+  family = brmsfamily("gaussian", link = "log", link_sigma = "log")
 )
@@
 ```{r}
-fits_1 <- dat %>%
+fits_1 <- dat_model1 %>%
   group_by(cause) %>% 
@@
 
-fits_1 <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit_se = list(
-      brm(
-        formula = bf_itu + bf_1_se + set_rescor(FALSE), 
-        data = cur_data_all(),
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-1-se-{cur_group()}")
-      )
-    )
-  )
+# fits_1 <- dat_model1 %>%
+#   group_by(cause) %>% 
+#   summarise(
+#     fit_se = list(
+#       brm(
+#         formula = bf_itu + bf_1_se + set_rescor(FALSE), 
+#         data = cur_data_all(),
+#         chains = hmc$chains, 
+#         cores = hmc$cores, 
+#         threads = hmc$threads,
+#         iter = hmc$iter, 
+#         warmup = hmc$warmup, 
+#         refresh = hmc$refresh,
+#         control = list(
+#           adapt_delta = hmc$adapt_delta, 
+#           max_treedepth = hmc$max_treedepth
+#         ),
+#         file = str_glue("output/brm-1-se-{cur_group()}")
+#       )
+#     )
+#   )
 ```
@@
     year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
+    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
+    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
   family = gaussian()
@@
 bf_2_se <- bf(
-  val | se(se, sigma = TRUE) ~ 
-    year * sex * age + i1_cw * sex * age + i1_cb + 
-    (year * sex * age + i1_cw * sex * age | country) +
-    (year * sex * age + i1_cw * sex * age | region),
-  family = gaussian()
+  bf(val | resp_se(se, sigma = TRUE) ~ 
+       year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
+       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
+       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
+     sigma ~ 1
+  ),
+  family = brmsfamily("gaussian", link = "log", link_sigma = "log")
 )
@@
 
-fits_2 <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit_se = list(
-      brm(
-        formula = bf_2_se, 
-        data = cur_data_all(),
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2-se-{cur_group()}")
-      )
-    )
-  )
+# fits_2 <- dat %>%
+#   group_by(cause) %>% 
+#   summarise(
+#     fit_se = list(
+#       brm(
+#         formula = bf_2_se, 
+#         data = cur_data_all(),
+#         chains = hmc$chains, 
+#         cores = hmc$cores, 
+#         threads = hmc$threads,
+#         iter = hmc$iter, 
+#         warmup = hmc$warmup, 
+#         refresh = hmc$refresh,
+#         control = list(
+#           adapt_delta = hmc$adapt_delta, 
+#           max_treedepth = hmc$max_treedepth
+#         ),
+#         file = str_glue("output/brm-2-se-{cur_group()}")
+#       )
+#     )
+#   )
 ```

### 2021-11-22 04-model-inference.Rmd
Load models from file

@@
 ```{r}
-# Read models from files to data frames
+fits <- distinct(gbd, cause) %>% 
+  mutate(
+    fit1 = map(
+      cause, 
+      ~read_rds(str_glue("output/brm-1-{.x}.rds"))
+    ),
+    fit2 = map(
+      cause, 
+      ~read_rds(str_glue("output/brm-2-{.x}.rds"))
+    )
+  )
 ```
+
+## Model comparison
+
+Compare 1 and 2 to examine how much model fit / variance explained changes when the internet predictors are added.
 
@@
 ```{r}
-tmp_coefs <- fits_1c %>% 
+tmp_coefs <- fits_1 %>% 
   mutate(
@@
   unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(
+    across(
+      where(is.numeric), 
+      ~round(., 3)
+    )
+  ) %>% 
   mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
@@
 # Function to wrangle draws at multiple levels and create scatterplots + ellipses
-draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
+draw_scatterplot <- function(
+    fit, beta, r_region, r_country, sd_country, cor_country
+) {
   # Get average and region-specific slopes

### 2021-11-23 03-model-estimate.Rmd
More work on model figures

@@
 
-### Model 1
+### Estimate
 
@@
   )
-```
-
-### Summary
-
-We then display the model's population-level parameters
-
-```{r}
-fits_1 %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
-        summarise_draws(
-          mean, quantile, rhat, 
-          .args = list(probs = c(.025, .975))
-        )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(
-    result = str_glue(
-      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
-    )
-  ) %>% 
-  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = cause, values_from = result) %>% 
-  kbl() %>% 
-  kable_paper(html_font = Font)
 ```

### 2021-11-23 04-model-inference.Rmd
More work on model figures

@@
 
+```{r}
+bayes_R2(fits$fit1[[1]], resp = "val")
+# Save to file if not done yet
+model_criteria_file <- "output/models-bayes-r2.rds"
+if (!file.exists(model_criteria_file)) {
+  model_criteria <- fits %>% 
+    mutate(Year = map(fit1, ~bayes_R2(.x, resp = "val"))) %>% 
+    mutate(`Year & internet` = map(fit2, ~bayes_R2(.x, resp = "val"))) %>% 
+    select(-fit1, -fit2)
+  write_rds(model_criteria, model_criteria_file)
+} else {model_criteria <- read_rds(model_criteria_file)}
+
+# Display table
+model_criteria %>% 
+  pivot_longer(-cause, names_to = "Model") %>% 
+  mutate(value = map(value, ~as.data.frame(.) %>% rownames_to_column())) %>% 
+  unnest(value) %>% 
+  select(-Est.Error, -rowname) %>% 
+  mutate(across(where(is.numeric), ~percent(.x, .1))) %>% 
+  mutate(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]")) %>% 
+  select(cause, Model, result) %>% 
+  pivot_wider(names_from = Model, values_from = result) %>% 
+  rename(Outcome = cause) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font, full_width = FALSE)
+```
+
 ## Time courses
+
+### Parameter estimates
+
+Model's population-level parameters. Recall scales of data values: Year is in decades; internet is a proportion (0-1); and outcomes are percentages (0-100).
+
+```{r}
+fits %>% 
+  mutate(
+    out = map(
+      fit1, 
+      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
+        summarise_draws(
+          mean, quantile, rhat, 
+          .args = list(probs = c(.025, .975))
+        )
+    )
+  ) %>% 
+  select(-fit1, -fit2) %>% 
+  unnest(out) %>% 
+  # Round selfharm numbers less because so small
+  mutate(
+    across(
+      where(is.numeric), 
+      ~if_else(cause == "Selfharm", round(., 3), round(., 2)))
+  ) %>% 
+  mutate(
+    result = str_glue(
+      "{mean} ({`2.5%`}, {`97.5%`})"
+    )
+  ) %>% 
+  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
+  pivot_wider(names_from = cause, values_from = result) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font) %>% 
+  row_spec(4, bold = TRUE)
+```
 
@@
 ```{r}
-tmp_coefs <- fits_1 %>% 
+tmp_coefs <- fits %>% 
   mutate(
     out = map(
-      fit, 
+      fit1, 
       ~hypothesis(
         .x,
-        # Rescale coefficient here to years on %
-        # Note self harm doesnt work now
-        c(str_glue("val_year = 0")),
+        c("val_year = 0", "internet_year = 0"),
         scope = "coef",
@@
   ) %>% 
-  select(-fit) %>% 
+  select(-fit1, -fit2) %>% 
   unnest(out) %>% 
@@
   ) %>% 
-  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
-  select(cause, region = Group, result)
-tmp_coefs
+  # Round selfharm numbers less because so small
+  mutate(
+    across(
+      where(is.numeric), 
+      ~if_else(cause == "Selfharm", round(., 3), round(., 2)))
+  ) %>% 
+  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]'))
+
+# Remove duplicate internet estimates and reshape to long form re variable
+tmp_coefs <- tmp_coefs %>% 
+  filter(Hypothesis == "(val_year) = 0" | cause == "Anxiety") %>% 
+  mutate(
+    cause = if_else(str_detect(Hypothesis, "val_"), cause, "Internet")
+  ) %>% 
+  mutate(region = Group)
+
 pseudo_gwp <-
@@
   facet_grid(cause~region, scales = "free_y") +
-  theme(
-    legend.position = "none",
-    panel.spacing = unit(3, "pt")
-  ) +
   geom_richtext(
@@
     fill = NA, label.color = NA
+  ) +
+  theme(
+    legend.position = "none",
+    axis.title.y = element_blank(),
+    panel.spacing = unit(3, "pt")
   )
@@
   country_cor_result <- spread_draws(fit, cor_country__internet_year__val_year) %>% 
-    median_qi(.width = .90) %>% 
+    median_qi(.width = .95) %>% 
     mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
   country_coefs %>% 
-    ggplot(aes(internet, outcome)) +
+    ggplot(aes(outcome, internet)) +
     geom_path(
       data = country_ellipse,
-      aes(x = x, y = y, group = .draw), 
+      # Internet values on Y
+      aes(x = y, y = x, group = .draw), 
       alpha = .2, size = .1, col = "dodgerblue1"
@@
     geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-    scale_x_continuous(
+    scale_y_continuous(
       "Internet trend",
@@
     ) +
-    scale_y_continuous(
+    scale_x_continuous(
       breaks = pretty_breaks()
@@
       x = Inf, y = Inf, label = country_cor_result,
-      size = 4, vjust = 1.5, hjust = 1.05, color = "dodgerblue4",
+      size = 3.6, vjust = 1.5, hjust = 1.05, color = "black",
       family = Font
@@
 ```{r}
-p1 <- draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
-p2 <- draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
-p3 <- draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
+p1 <- draw_scatterplot(fits$fit1[[1]]) + labs(x = "Anxiety trend")
+p2 <- draw_scatterplot(fits$fit1[[2]]) + labs(x = "Depression trend")
+p3 <- draw_scatterplot(fits$fit1[[3]]) + labs(x = "Self-harm trend")
 ```
@@
 ```{r}
+# Same y axis
+p2 <- p2 + theme(axis.title.y = element_blank())
+p3 <- p3 + theme(axis.title.y = element_blank())
+
 (wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
@@
     wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
-  (p1 | p2 | p3)
+  ((p1 | p2 | p3) & coord_cartesian(ylim = c(-1, 5))) & 
+  theme(aspect.ratio = 1)
+```
+
+### Figure: Shrinkage
+
+Shrinkage plot
+
+```{r}
+x <- mgcv::gam(
+  internet ~ 0 + country + year:country, 
+  family = mgcv::betar, data = itu %>% mutate(year = (year-2010)/10)
+)
+lm_coefs <- fits %>% 
+  mutate(data = map(fit1, ~as_tibble(.x$data))) %>% 
+  mutate(
+    out = map(
+      data, 
+      ~tidy(
+        lm(val ~ 0 + country + year:country, data = .x)
+      )
+    )
+  ) %>% 
+  select(-fit1, -fit2, -data) %>% 
+  unnest(out)
+
+lm_coefs <- left_join(
+  tidy(x, TRUE) %>% 
+    mutate(cause = "Internet") %>% 
+    filter(str_detect(term, ":year")) %>% 
+    mutate(term = str_remove(term, "country")) %>% 
+    mutate(term = str_remove(term, ":year")) %>% 
+    select(country = term, internet_lm = estimate),
+  lm_coefs %>% 
+    filter(str_detect(term, ":year")) %>% 
+    mutate(term = str_remove(term, "country")) %>% 
+    mutate(term = str_remove(term, ":year")) %>% 
+    select(cause, country = term, outcome_lm = estimate)
+)
+bind_rows(
+  "Anxiety" = p1$data,
+  "Depression" = p2$data,
+  "Selfharm" = p3$data,
+  .id = "cause"
+) %>% 
+  ungroup() %>% 
+  left_join(lm_coefs) %>% 
+  ggplot() +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_hline(yintercept = 0, lty = 2, size = .2) +
+  geom_segment(
+    aes(
+      x = outcome_lm, xend = outcome,
+      y = internet_lm, yend = internet
+    ),
+    size = .25,
+    arrow = arrow(length = unit(4, "pt"), type = "closed")
+  ) +
+  geom_point(
+    aes(outcome, internet), 
+    col = "dodgerblue3", size = 1, alpha = .75
+  ) +
+  geom_point(
+    aes(outcome_lm, internet_lm),
+    col = "dodgerblue1", size = 1, alpha = .25
+  ) +
+  scale_y_continuous(
+    "Internet trend",
+    breaks = pretty_breaks()
+  ) +
+  scale_x_continuous(
+    "Outcome trend",
+    breaks = pretty_breaks()
+  ) +
+  facet_wrap("cause", scales = "free_x") +
+  theme(aspect.ratio = 1)
 ```
@@
 
-Coefficients
+### Parameter estimates
+
+Model's population-level parameters. Recall scales of data values: Year is in decades; internet is a proportion (0-1); and outcomes are percentages (0-100).
 
 ```{r}
-tmp <- fits_2c %>% 
+fits %>% 
   mutate(
     out = map(
-      fit, 
+      fit2, 
+      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
+        summarise_draws(
+          mean, quantile, rhat, 
+          .args = list(probs = c(.025, .975))
+        )
+    )
+  ) %>% 
+  select(-fit1, -fit2) %>% 
+  unnest(out) %>% 
+  # Round selfharm numbers less because so small
+  mutate(
+    across(
+      where(is.numeric), 
+      ~if_else(cause == "Selfharm", round(., 3), round(., 2)))
+  ) %>% 
+  mutate(
+    result = str_glue(
+      "{mean} ({`2.5%`}, {`97.5%`})"
+    )
+  ) %>% 
+  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
+  pivot_wider(names_from = cause, values_from = result) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font) %>% 
+  kable_paper(html_font = Font, full_width = FALSE)
+```
+
+### Coefficients
+
+```{r}
+tmp <- fits %>% 
+  mutate(
+    out = map(
+      fit2, 
       ~emtrends(.x, var = "i1_cw", by = c("sex", "age"))
@@
   ) %>% 
-  select(-fit)
+  select(-fit1, -fit2)
 tmp %>% 
@@
   kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
+  kable_paper(html_font = Font, full_width = FALSE)
 ```
@@
 ```{r}
-tmp <- fits_2c %>% 
+#' Create three-level data for a forest plot
+#'
+#' @param model a brmsfit Model 2
+#'
+#' @return data.frame with posterior samples of the i1_cw effect at level of regions and average, and posterior means at level of countries. Can then be filtered to display either.
+create_forest_data <- function(model) {
+  # Average
+  y_avg <- spread_draws(model, b_i1_cw) %>% 
+    mutate(region = "Average") %>% 
+    select(.draw, r_region = b_i1_cw, region)
+  # Region
+  y_region <- spread_draws(model, b_i1_cw, r_region[region, term]) %>% 
+    filter(term == "i1_cw") %>% 
+    mutate(r_region = b_i1_cw + r_region) %>% 
+    ungroup() %>% 
+    select(.draw, region, r_region) %>% 
+    mutate(region = str_replace_all(region, "\\.", "\n"))
+  # Country
+  y_country <- spread_draws(model, r_country[country, term]) %>% 
+    filter(term == "i1_cw") %>% 
+    mutate(country = str_replace_all(country, "\\.", " "))
+  y_country <- y_country %>% 
+    mean_qi(r_country) %>% 
+    # Get region names
+    left_join(distinct(model$data, region, country)) %>% 
+    # Join to region means
+    left_join(
+      y_region %>% 
+        group_by(region) %>% 
+        mean_qi(r_region) %>% 
+        select(region, r_region)
+    ) %>% 
+    mutate(r_country = r_country + r_region) %>% 
+    select(region, country, r_country)
+
+  # Common data frame
+  y <- bind_rows(
+    y_region,
+    y_avg,
+    y_country
+  )
+
+  y
+}
+
+forest_data <- fits %>% 
+  mutate(data = map(fit2, create_forest_data)) %>% 
+  select(-fit1, -fit2)
+
+forest_data <- forest_data %>% 
+  unnest(data)
+
+forest_data <- forest_data %>% 
+  mutate(region = fct_relevel(region, "Average"))
+
+forest_text <- forest_data %>% 
+  drop_na(r_region) %>% 
+  select(-c(country, r_country)) %>% 
+  pivot_wider(names_from = region, values_from = r_region) %>% 
+  group_by(cause) %>% 
+  summarise(
+    parameters(cur_data_all()[,-c(1:2)], test = "pd", centrality = "mean")
+  ) %>% 
+  mutate(region = fct_relevel(Parameter, "Average")) %>% 
+  mutate(is_average = FALSE) %>% 
   mutate(
-    out = map(
-      fit, 
-      ~spread_draws(.x, b_i1_cw, r_region[region, term] | region) %>% 
-        filter(term == "i1_cw") %>% 
-        ungroup() %>% 
-        select(-term) %>% 
-        rename(Average = b_i1_cw) 
+    across(
+      where(is.numeric), 
+      ~if_else(
+        cause=="Selfharm", 
+        format(round(., 3), nsmall = 3), 
+        format(round(., 2), nsmall = 2)
       )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out)
+    )
+  )
 
-names(tmp) <- str_replace(names(tmp), "\\.", " ")
-
-tmp_text <- tmp %>% 
-  group_by(cause) %>% 
-  summarise(parameters(cur_data()[-c(1:3)], test = "pd")) %>% 
-  rename(region = Parameter) %>% 
+p_tmp <- drop_na(forest_data, r_region) %>% 
   mutate(is_average = region == "Average") %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))
-
-p_tmp <- tmp %>% 
-  mutate(across(Africa:`Southern Asia`, ~.+Average)) %>% 
-  pivot_longer(Average:`Southern Asia`, names_to = "region") %>% 
-  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
-  mutate(region = fct_relevel(factor(region), "**Average**")) %>% 
-  mutate(cause = factor(cause)) %>% 
-  mutate(is_average = region == "**Average**") %>% 
-  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
+  ggplot(aes(r_region, region, fill = is_average)) +
   scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
@@
   scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(expand = expansion(c(0.01, .1))) +
+  scale_y_discrete(
+    expand = expansion(c(0.01, .1)),
+    labels = function(x) if_else(x == "Average", "**Average**", x)
+  ) +
   scale_x_continuous(
-    "Magnitude of association between internet adoption and well-being", 
+    "Conditional effect of 100% increase in internet adoption on outcome", 
     breaks = pretty_breaks(), 
-    expand = expansion(c(.1, .5))
+    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00"),
+    expand = expansion(c(.1, .1))
+  ) +
+  geom_point(
+    data = forest_data %>%
+      mutate(is_average = TRUE) %>% 
+      # This drops a few countries that didn't match region due to string processing above
+      drop_na(region),
+    aes(x = r_country), size = 1, col = "dodgerblue1",
+    position = position_nudge(0, -0.075), alpha = .4
   ) +
@@
     point_interval = NULL, normalize = "panels", 
-    height = .75, adjust = 1.5
+    height = .75, adjust = 1.25,
+    aes(alpha = is_average)
   ) +
@@
     interval_size = 1,
-    point_size = 1.5,
+    point_size = 1.75,
     fill = "white",
     aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, -.025)
+    position = position_nudge(0, 0)
   ) +
   geom_text(
-    data = tmp_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
+    data = forest_text, family = Font,
+    alpha = 1, size = 2.4, hjust = 1, vjust = -0.2,
     aes(
       x = Inf,
-      label = str_glue("{Median} [{CI_low}, {CI_high}]")
+      label = str_glue("{Mean} [{CI_low}, {CI_high}]")
     )
@@
 # Prediction dataframe: Min and max vals are enough for line
-x_country <- fits_2c$fit[[1]]$data %>% 
+x_country <- fits$fit2[[1]]$data %>% 
   group_by(country) %>% 
@@
 
-pred_country <- fits_2c %>% 
+pred_country <- fits %>% 
   mutate(
     pred_country = map(
-      fit, ~epred_draws(
+      fit2, ~epred_draws(
         .x, 
@@
 
-pred_region <- fits_2c %>% 
+pred_region <- fits %>% 
   mutate(
     pred_region = map(
-      fit, ~epred_draws(
+      fit2, ~epred_draws(
         .x, 
@@
 pred_region <- pred_region %>% 
-  select(-fit) %>%
+  select(-fit1, -fit2) %>%
   unnest(pred_region) %>%
@@
 pred_country %>% 
-  select(-fit) %>% 
+  select(-fit1, -fit2) %>% 
   unnest(pred_country) %>% 
-  bind_rows(select(pseudo_gwp, region, cause)) %>% 
-  mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
+  bind_rows(select(pseudo_gwp, region, cause), .) %>% 
+  mutate(cause = fct_inorder(cause)) %>%
   ggplot(aes(i1_cw, .epred)) +
@@
     "Estimated rate or scale score",
-    breaks = pretty_breaks()
+    breaks = pretty_breaks(),
+    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00")
   ) +
@@
   ) +
-  # geom_text(
-  #   data = tmp_text %>% 
-  #     filter(region != "**Average**") %>% 
-  #     bind_rows(select(pseudo_gwp, region, cause)) %>% 
-  #     mutate(cause = fct_rev(fct_inorder(factor(cause)))) %>% 
-  #     mutate(region = str_replace(region, " ", "\n")) %>% 
-  #     mutate(result = paste(Median)),
-  #   aes(x = -Inf, y = Inf, label = result),
-  #   size = 2.4, vjust = .9, hjust = 0.05, color = "black",
-  #   family = Font,
-  #   fill = NA, label.color = NA
-# ) +
   facet_grid(cause~region, scales = "free_y") +
-  theme(panel.spacing = unit(2, "pt"))
+  theme(
+    panel.spacing = unit(2, "pt"),
+    axis.title.y = element_blank()
+  )
 ```

### 2021-11-25 03-model-estimate.Rmd
Estimate fixed and mobile too.

@@
         newdata = .x$data
-      ) + facet_wrap("group", nrow = 1, scales = "free")
+      ) + 
+        facet_wrap("group", nrow = 1, scales = "free")
     )
@@
     i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb # Year-specific deviation from country average
+    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
+    f1_cb = mean(f1, na.rm = TRUE),
+    f1_cw = f1 - f1_cb,
+    m1_cb = mean(m1, na.rm = TRUE),
+    m1_cw = m1 - m1_cb,
   ) %>% 
@@
   # Grand-mean center the country averages
-  mutate(i1_cb = i1_cb - mean(i1, na.rm = TRUE))
+  mutate(
+    across(c(i1_cb, f1_cb, m1_cb), ~. - mean(., na.rm = T))
+  )
 ```
@@
     year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
+    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
   family = gaussian()
@@
        year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb + 
-       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | country) +
-       (year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb | region),
+       (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
+       (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
      sigma ~ 1
@@
 ```
+
+## Model 2 for fixed and mobile
+
+```{r}
+bf_2_f <- bf(
+  val ~ 
+    year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb + 
+    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
+    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
+  family = gaussian()
+)
+
+fits_2_f <- dat %>%
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      brm(
+        formula = bf_2_f, 
+        data = cur_data_all(),
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2-fixed-{cur_group()}")
+      )
+    )
+  )
+
+bf_2_m <- bf(
+  val ~ 
+    year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb + 
+    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
+    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
+  family = gaussian()
+)
+
+fits_2_m <- dat %>%
+  group_by(cause) %>% 
+  summarise(
+    fit = list(
+      brm(
+        formula = bf_2_m, 
+        data = cur_data_all(),
+        chains = hmc$chains, 
+        cores = hmc$cores, 
+        threads = hmc$threads,
+        iter = hmc$iter, 
+        warmup = hmc$warmup, 
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta, 
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2-mobile-{cur_group()}")
+      )
+    )
+  )
+```

### 2021-11-25 04-model-inference.Rmd
Easier code for forest plots

@@
 ```{r}
-bayes_R2(fits$fit1[[1]], resp = "val")
 # Save to file if not done yet
@@
   theme(aspect.ratio = 1)
+```
+
+### Sex and age
+
+```{r}
+x <- fits$fit1[[1]]
+get_variables(x)
+contrasts(fits$fit1[[1]]$data$sex)
+contrasts(fits$fit1[[1]]$data$age)
+
+x <- emtrends(fits$fit1[[1]], var = "year", by = c("sex", "age"), resp = "val")
+parameters(x, centrality = "mean", ci_method = "quantile", test = "pd")
+tmp <- fits_2c %>% 
+  mutate(
+    out = map(
+      fit, 
+      ~emtrends(.x, var = "i1_cw", by = c("sex"), at = list(age1=0, age2=0))
+    )
+  )
+tmp$out[[1]] %>% summary
+
+get_draws <- function(x) {
+  draws_region <- spread_draws(
+    x, 
+    b_val_year, `b_val_year:sex1`, `b_val_year:age1`, `b_val_year:age2`,
+    r_region[region, term] | term
+  ) %>% 
+    mutate(
+      `10 to 14` = val_year + b_val_year +
+        `val_year:age1`*1 + `b_val_year:age1`*1 +
+        `val_year:age2`*0 + `b_val_year:age2`*0,
+      `15 to 19` = val_year + b_val_year +
+        `val_year:age1`*0 + `b_val_year:age1`*0 +
+        `val_year:age2`*1 + `b_val_year:age2`*1,
+      `20 to 24` = val_year + b_val_year +
+        `val_year:age1`*-1 + `b_val_year:age1`*-1 +
+        `val_year:age2`*-1 + `b_val_year:age2`*-1,
+      Female = b_val_year + val_year + 
+        `val_year:sex1`*1 + `b_sex1:val_year`*1,
+      Male = val_year + b_val_year + 
+        `val_year:sex1`*-1 + `b_val_year:sex1`*-1
+    ) %>% 
+    select(region, `10 to 14`:Male)
+
+  draws_avg <- spread_draws(
+    x, 
+    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
+  ) %>% 
+    mutate(
+      `10 to 14` = b_i1_cw + `b_age1:i1_cw`*1 + `b_age2:i1_cw`*0,
+      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*0 + `b_age2:i1_cw`*1,
+      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*-1 + `b_age2:i1_cw`*-1,
+      Female = b_i1_cw + `b_sex1:i1_cw`*1,
+      Male = b_i1_cw + `b_sex1:i1_cw`*-1,
+      Age = `20 to 24` - `10 to 14`,
+      Sex = Female - Male
+    ) %>% 
+    select(`10 to 14`:Male) %>% 
+    mutate(region = "Average")
+
+  draws <- bind_rows(
+    "regions" = draws_region,
+    "average" = draws_avg, 
+    .id = "Level"
+  ) %>% 
+    mutate(region = str_replace(region, "\\.", "\n")) %>% 
+    ungroup()
+  draws
+}
 ```
@@
   summarise(
-    parameters(cur_data_all()[,-c(1:2)], test = "pd", centrality = "mean")
+    parameters(
+      cur_data_all()[,-c(1:2)], 
+      test = "pd", 
+      centrality = "mean",
+      ci_method = "quantile"
+    )
   ) %>% 
@@
     point_interval = NULL, normalize = "panels", 
-    height = .75, adjust = 1.25,
+    height = .75, adjust = 1,
     aes(alpha = is_average)
@@
   stat_pointinterval(
-    alpha = 1, .width = c(.9),
+    alpha = 1, .width = c(.95),
     interval_size = 1,
@@
   p_tmp
+```
+
+A table of smallest and greatest country-level estimates
+
+```{r}
+forest_data %>% 
+  drop_na(country) %>% 
+  select(-.draw, -r_region) %>% 
+  group_by(cause) %>% 
+  filter(
+    r_country %in% 
+      c(min(r_country, na.rm = T), max(r_country, na.rm = T))
+  ) %>% 
+  kbl() %>% 
+  kable_paper(html_font = Font, full_width = FALSE)
 ```
@@
 ```{r}
-x <- fits_2c$fit[[1]]
-y <- emtrends(x, var = "i1_cw", by = c("age", "sex"))
-gather_emmeans_draws(y) %>% mean_qi()
-
-contrasts(x$data$sex)
-contrasts(x$data$age)
+get_coefs <- function(x) {
   h <- c(
-  `Female_10 to 14` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
-  `Female_15 to 19` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
-  `Female_20 to 24` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
-  `Male_10 to 14` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
-  `Male_15 to 19` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
-  `Male_20 to 24` = 
-    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0"
-)
-tmp_avg <- hypothesis(x, h)
-tmp_region <- hypothesis(x, h, scope = "coef", group = "region")
+    `10 to 14` = 
+      "i1_cw + age1:i1_cw*1 + age2:i1_cw*0 = 0",
+    `15 to 19` = 
+      "i1_cw + age1:i1_cw*0 + age2:i1_cw*1 = 0",
+    `20 to 24` = 
+      "i1_cw + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
+    `Female` = 
+      "i1_cw + sex1:i1_cw*1 = 0",
+    `Male` = 
+      "i1_cw + sex1:i1_cw*-1 = 0"
+  )
+
+  # Average samples
+  avg_h <- hypothesis(x, h)
+  avg_s <- avg_h$samples %>% as_tibble()
+  names(avg_s) <- avg_h$hypothesis$Hypothesis  
+  avg_s <- avg_s %>% 
+    pivot_longer(everything()) %>% 
+    mutate(name = paste("Average", name, sep = "-"))
+
+  # Region samples
+  region_h <- hypothesis(x, h, scope = "coef", group = "region")
+  region_s <- region_h$samples %>% as_tibble()
+  names(region_s) <- paste(
+    region_h$hypothesis$Group, 
+    region_h$hypothesis$Hypothesis, 
+    sep = "-"
+  )
+  region_s <- region_s %>% 
+    pivot_longer(everything())
+
+  # Country means
+  country_h <- hypothesis(
+    x, h, scope = "ranef", group = "country"
+  )$hypothesis %>% 
+    as_tibble()
+  country_h <- country_h %>% 
+    left_join(
+      distinct(x$data, region, country), 
+      by = c("Group" = "country")
+    ) %>% 
+    select(region, Hypothesis, Estimate, country = Group)
+
+  # Add region coefs to country ranefs
+  country_h <- left_join(
+    country_h, 
+    region_h$hypothesis %>% 
+      rename(region = Group, coef = Estimate)
+  ) %>% 
+    mutate(Estimate = Estimate + coef)
+
+  # Join all to one data frame
+  samples <- bind_rows(avg_s, region_s) %>% 
+    separate(name, into = c("region", "Hypothesis"), sep = "-") %>% 
+    bind_rows(country_h)
+
+  # Verify that naming worked
+  # region_h$hypothesis %>% 
+  #   left_join(
+  #     samples %>% 
+  #       group_by(region, Hypothesis) %>% 
+  #       summarise(xxx = mean(value)),
+  #     by = c("Group" = "region", "Hypothesis")
+  #   ) %>% 
+  #   as_tibble() %>% 
+  #   filter(xxx != Estimate)
+
+  samples
+}
+tmp <- fits %>% 
+  mutate(out = map(fit2, get_coefs)) %>% 
+  select(-fit1, -fit2)
+
+tmp <- tmp %>% 
+  unnest(out) %>% 
+  mutate(is_average = region=="Average") %>% 
+  mutate(region = fct_relevel(region, "Average")) %>% 
+  mutate(panel = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>% 
+  mutate(
+    side = if_else(Hypothesis %in% c("10 to 14", "Female"), "top", "bottom")
+  )
+
+tmp_regions <- tmp %>% 
+  filter(is.na(country)) %>% 
+  filter(Hypothesis != "15 to 19")
+
+tmp_countries <- tmp %>% 
+  filter(!is.na(country)) %>% 
+  filter(Hypothesis != "15 to 19") %>% 
+  mutate(is_average = FALSE)
+
+tmp_text <- tmp_regions %>% 
+  select(cause, region, Hypothesis, value) %>% 
+  group_by(cause, region, Hypothesis) %>% 
+  mutate(.draw = 1:n()) %>% 
+  pivot_wider(names_from = Hypothesis, values_from = value) %>%
+  mutate(Age = `20 to 24` - `10 to 14`, Sex = Female - Male) %>% 
+  summarise(
+    parameters(
+      cur_data_all() %>% select(Age, Sex), 
+      test = "pd", 
+      centrality = "mean",
+      ci_method = "quantile"
+    )
+  ) %>% 
+  mutate(
+    across(
+      where(is.numeric), 
+      ~if_else(
+        cause=="Selfharm", 
+        format(round(., 3), nsmall = 3), 
+        format(round(., 2), nsmall = 2)
+      )
+    )
+  ) %>% 
+  mutate(is_average = region=="Average") %>% 
+  mutate(region = fct_relevel(region, "Average")) %>% 
+  mutate(panel = Parameter)
+
+tmp_regions %>%   
+  ggplot(aes(value, region, col = Hypothesis, fill = Hypothesis)) +
+  scale_alpha_manual(values = c(.3, .6)) +
+  scale_color_brewer(
+    "Group",
+    palette = "Set1",
+    aesthetics = c("color", "fill")
+  ) +
+  scale_shape_manual(
+    values = c(21, 19), guide = "none"
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_y_discrete(
+    expand = expansion(c(0.1, .1)),
+    labels = function(x) if_else(x == "Average", "**Average**", x)
+  ) +
+  scale_x_continuous(
+    "Conditional effect of 100% increase in internet adoption on outcome", 
+    breaks = pretty_breaks(), 
+    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00"),
+    expand = expansion(c(.01, .1))
+  ) +
+  stat_halfeye(
+    point_interval = NULL, normalize = "panels", 
+    height = .75, adjust = 1,
+    aes(side = side, group = side, alpha = is_average), 
+    show.legend = FALSE
+  ) +
+  # geom_point(
+  #   data = tmp_countries %>% 
+  #     drop_na(region),
+  #   aes(x = Estimate, shape = Star=="*"),
+  #   size = .5, alpha = .4, fill = "white",
+  #   position = position_dodge2v(.5)
+  # ) +
+  stat_pointinterval(
+    alpha = 1, .width = c(.95),
+    interval_size = .4,
+    point_size = 1.5,
+    fill = "white",
+    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
+    position = position_dodgev(.2), key_glyph = draw_key_point
+  ) +
+  geom_richtext(
+    data = tmp_text %>% 
+      mutate(Hypothesis = NA) %>% 
+      mutate(
+        Mean = if_else(
+          as.numeric(pd) >= .95,
+          str_glue("**{Mean}**"), 
+          Mean
+        ),
+      ),
+    aes(
+      x = Inf,
+      label = str_glue("{Mean} [{CI_low}, {CI_high}]")
+    ),
+    size = 2.5, hjust = 1, col = "black", 
+    family = Font, label.color = NA, 
+    label.padding = unit(0, "pt"),
+    show.legend = FALSE
+  ) +
+  facet_grid2(panel ~ cause, scales = "free_x", axes = "x") +
+  theme(
+    legend.position = "right",
+    axis.title.y = element_blank(),
+    axis.text.y = element_markdown()
+  )
 ```

### 2021-11-27 01-clean.Rmd
Clear unnecessary stuff

--- 2021-11-18 01-clean.Rmd
@@
 ```
-
-## Covariates
-
-Human Development Index
 

### 2021-11-28 01-clean.Rmd
Add gwp cleaning

@@
 library(janitor)
+library(haven)
+library(labelled)
 library(countrycode)
@@
 dir.create("data", FALSE)
+```
+
+## Gallup World Poll
+
+```{r}
+# First liberate the data from the slow SPSS file and save to disk
+gwp_path <- "data-raw/Gallup/gwp-processed.rds"
+if (!file.exists(gwp_path)) {
+  gwp <- read_spss(
+    "data-raw/Gallup/The_Gallup_101521.sav", 
+    col_select = c(
+      YEAR_CALENDAR, 
+      COUNTRYNEW, 
+      WPID, WP1220, WP1219,
+      WP16,
+      WP60, WP61, WP63, WP65, WP67,
+      WP68, WP69, WP70, WP71, WP74
+    )
+  )
+
+  # Get rid of SPSS attributes
+  gwp <- gwp %>% 
+    zap_labels() %>% 
+    zap_label() %>% 
+    zap_widths() %>% 
+    zap_formats()
+
+  # Save into a good format
+  write_rds(gwp, gwp_path)
+} else {gwp <- read_rds(gwp_path)}
+
+# Codes NOTE 1: yes 2: no!
+read_spss(
+  "data-raw/Gallup/The_Gallup_101521.sav", 
+  n_max = 10,
+  col_select = c(
+    WPID, WP1219,
+    WP16,
+    WP60, WP61, WP63, WP65, WP67,
+    WP68, WP69, WP70, WP71, WP74
+  )
+) %>% 
+  generate_dictionary()
+
+gwp <- gwp %>% 
+  clean_names() %>% 
+  transmute(
+    country = countrynew,
+    year = year_calendar,
+    id = wpid,
+    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
+    age = wp1220,
+    # Don't know, refused, and missing values
+    `Life\nsatisfaction` = if_else(between(wp16, 0, 10), wp16, NaN),
+    across(wp60:wp74, ~if_else(between(., 1, 2), ., NaN)),
+    # Also reverse the weird 1: yes 2: no coding here
+    across(wp60:wp74, ~3 - .)
+  )
+
+# Scale scores note rescaling
+gwp <- gwp %>% 
+  mutate(
+    `Life\nsatisfaction` = `Life\nsatisfaction` / 10,
+    `Negative\nexperiences` = 
+      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
+    `Positive\nexperiences` = 
+      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
+  ) %>% 
+  select(-c(wp60:wp74))
+
+# Categorize ages
+gwp <- gwp %>% 
+  mutate(
+    age = cut(
+      age, 
+      breaks = seq(15, 105, by = 5), 
+      include.lowest = TRUE,
+      right = FALSE,
+      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
+    ) %>% as.character()
+  )
+
+# There is one 13 year old which resulted in a NA and we drop it
+gwp <- drop_na(gwp, age)
+```
+
+Summarise gwp data
+
+```{r}
+gwp <- gwp %>% 
+  pivot_longer(
+    c(
+      `Life\nsatisfaction`, 
+      `Negative\nexperiences`, 
+      `Positive\nexperiences`
+    ), 
+    names_to = "cause", values_to = "val"
+  ) %>% 
+  group_by(country, year, sex, age, cause) %>% 
+  summarise(
+    se = sd(val, na.rm = TRUE) / sqrt(n()),
+    val = mean(val, na.rm = TRUE)
+  ) %>% 
+  ungroup()
+```
+
+Harmonise countries
+
+```{r gwp-harmonise-countries}
+# Check what names were changed and if any don't have harmonised counterpart
+gwp %>%
+  distinct(country) %>% 
+  arrange(country) %>%
+  mutate(
+    country_harmonised = countryname(country, destination = "cldr.short.en")
+  ) %>% 
+  filter(country != country_harmonised | is.na(country_harmonised)) %>% 
+  kbl() %>% 
+  kable_minimal(full_width = FALSE) %>% 
+  scroll_box(width = "500px", height = "400px")
+# Harmonise old names and replace only if harmonised name found
+gwp <- gwp %>% 
+  mutate(
+    country_harmonised = countryname(
+      country, destination = "cldr.short.en"
+    )
+  ) %>% 
+  # This picks the harmonised name if exists, otherwise original name
+  mutate(country = coalesce(country_harmonised, country)) %>% 
+  select(-country_harmonised)
+
+distinct(gwp, country)
+distinct(gwp, country) %>% filter(is.na(country))
 ```
@@
   scroll_box(width = "500px", height = "400px")
-# Harmonise old names after verifying above that none are dropped
+# Harmonise old names and replace only if harmonised name found
 gbd <- gbd %>% 
-  mutate(country = countryname(country, destination = "cldr.short.en"))
+  mutate(
+    country_harmonised = countryname(
+      country, destination = "cldr.short.en"
+    )
+  ) %>% 
+  # This picks the harmonised name if exists, otherwise original name
+  mutate(country = coalesce(country_harmonised, country)) %>% 
+  select(-country_harmonised)
+
+distinct(gbd, country)
+distinct(gbd, country) %>% filter(is.na(country))
 ```
-
-## Gallup World Poll
-
-GWP cleaning goes here.
 
@@
 
-# Harmonise old names after verifying above that none are dropped
+# Harmonise old names and replace only if harmonised name found
 itu <- itu %>% 
-  mutate(country = countryname(country, destination = "cldr.short.en"))
+  mutate(
+    country_harmonised = countryname(
+      country, destination = "cldr.short.en"
+    )
+  ) %>% 
+  # This picks the harmonised name if exists, otherwise original name
+  mutate(country = coalesce(country_harmonised, country)) %>% 
+  select(-country_harmonised)
+
+distinct(itu, country)
+distinct(itu, country) %>% filter(is.na(country))
 
@@
   distinct(country) %>% 
-  anti_join(distinct(gbd, country)) %>% 
+  mutate(gwp = country %in% unique(gwp$country)) %>% 
+  mutate(gbd = country %in% unique(gbd$country)) %>% 
+  filter(!gwp | !gbd) %>% 
   kbl() %>% 
@@
 itu <- itu %>% 
-  filter(country %in% unique(gbd$country))
+  filter(country %in% unique(gbd$country) | country %in% unique(gwp$country))
 ```
@@
 ### Missingness
-
-Remove countries with no observations
-
-```{r}
-itu <- itu %>% 
-  group_by(country) %>% 
-  mutate(nobs = sum(!is.na(internet))) %>% 
-  ungroup() %>% 
-  filter(nobs > 0) %>% 
-  select(-nobs)
-```
 
@@
 
-# Countries in our dataset not present in region data
-filter(
+# Countries in GBD not present in region data
+no_region_gbd <- filter(
   distinct(gbd, country), 
@@
 ) %>% 
+  arrange(country)
+
+# Then see what countries in GWP are without region
+no_region_gwp <- filter(
+  distinct(gwp, country), 
+  !(country %in% unique(regions$country))
+) %>% 
+  arrange(country)
+
+bind_rows(no_region_gbd, no_region_gwp) %>% 
   arrange(country) %>% 
-  write_csv("data-raw/Regions/GBD-countries-without-region.csv")
+  distinct() %>%
+  write_csv("data-raw/Regions/countries-without-region.csv")
 
@@
 regions_filled <- read_csv(
-  "data-raw/Regions/GBD-countries-without-region-filled.csv"
+  "data-raw/Regions/countries-without-region-filled.csv"
 )
@@
 gbd <- left_join(gbd, regions)
+gwp <- left_join(gwp, regions)
 ```
+
+## Create tables for young people
 
@@
 ```{r}
+gwp_all <- gwp
+gwp <- gwp %>% 
+  filter(age %in% c("15 to 19", "20 to 24"))
+
 gbd_all <- gbd
@@
 ```{r}
+write_rds(gwp, "data/gwp.rds")
+write_rds(gwp_all, "data/gwp_all_ages.rds")
 write_rds(gbd, "data/gbd.rds")

### 2021-11-28 03-model-estimate.Rmd
Include gwp in models

@@
 itu <- read_rds("data/itu.rds")
-gbd <- read_rds("data/gbd.rds") # 10 to 24 year olds
+gwp <- read_rds("data/gwp.rds")
+gbd <- read_rds("data/gbd.rds") 
 ```
@@
 
+```{r}
+# Transform edge proportions to fit beta distribution
+# when this is used as an outcome
+itu <- itu %>% 
+  mutate(ib = if_else(internet == 0, .0000001, internet)) %>% 
+  mutate(ib = if_else(internet == 1, .9999999, internet))
+
+# Create lagged predictors
+itu <- itu %>% 
+  arrange(region, country, year) %>% 
+  group_by(region, country) %>% 
+  mutate(
+    across(
+      c(internet, fixed, mobile), 
+      list(`1` = ~lag(., 1)), 
+      .names = "{str_sub(.col, 1, 1)}{.fn}"
+    )
+  )
+
+# Centering predictors within and between countries
+itu <- itu %>%
+  group_by(country) %>% 
+  mutate(
+    i1_cb = mean(i1, na.rm = TRUE), # Country average
+    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
+    f1_cb = mean(f1, na.rm = TRUE),
+    f1_cw = f1 - f1_cb,
+    m1_cb = mean(m1, na.rm = TRUE),
+    m1_cw = m1 - m1_cb,
+  ) %>% 
+  ungroup() %>% 
+  # Grand-mean center the country averages
+  mutate(
+    across(c(i1_cb, f1_cb, m1_cb), ~. - mean(., na.rm = T))
+  )
+```
+
 ```{r data-prepare}
+# Stack outcome data
+dat <- bind_rows(gwp, gbd)
+
 # Merge predictors to outcomes
-dat <- left_join(gbd, itu)
+dat <- left_join(dat, itu)
 
-# Center and scale year, and contrast code factors
+# Arrange data
+dat <- arrange(dat, region, country, year)
+
+# Center and scale year, and contrast code sex
 dat <- dat %>% 
   mutate(year = (year - 2010) / 10)
-dat$sex <- factor(dat$sex)
-contrasts(dat$sex) <- "contr.sum"
-dat$age <- factor(dat$age)
-contrasts(dat$age) <- "contr.sum"
+```
+
+Identify values to use in mv models
+
+```{r}
+# Give each outcome value a tag to ensure it is used in MV model
+dat <- dat %>% 
+  mutate(y = !is.na(val))
+
+# Indicate unique ITU values for MV model
+dat <- dat %>% 
+  # Unique values exist for each country-year
+  group_by(region, country, year) %>% 
+  mutate(itu = 1:n() == 1) %>% 
+  ungroup()
 ```
@@
   mutate(across(val:se, ~.x*100))
+```
+
+Ensure that factors are contrast coded
+
+```{r}
+dat <- dat %>% 
+  mutate(across(c(sex, age), factor))
+options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
+options()$contrasts
 ```
@@
 Prepare data for this model
-
-```{r}
-dat_model1 <- dat %>% 
-  # Transform edge proportions to fit beta distribution
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
-  mutate(internet = if_else(internet == 1, .9999999, internet)) %>% 
-  # Indicate unique ITU values for MV model...
-  arrange(region, country, year, cause, sex, age) %>% 
-  # ...Use only the first internet value within a year-country
-  group_by(region, country, year) %>% 
-  mutate(itu = 1:n() == 1) %>% 
-  ungroup()
-```
 
@@
     (year * sex + year * age |r| region),
-  family = gaussian()
+  family = gaussian(),
+  unused = ~ cause
 )
@@
   ),
-  family = brmsfamily("gaussian", link = "log", link_sigma = "log")
+  family = gaussian(),
+  unused = ~ cause
 )
@@
 ```{r}
-fits_1 <- dat_model1 %>%
+fits_1 <- dat %>%
   group_by(cause) %>% 
@@
 
-# fits_1 <- dat_model1 %>%
+# fits_1_se <- dat %>%
+#   filter(!(cause %in% c("Anxiety", "Depression", "Selfharm")))
 #   group_by(cause) %>%
@@
 
-```{r}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(region, country, cause, sex, age, year) %>% 
-  group_by(region, country, cause, sex, age) %>% 
-  mutate(
-    across(
-      c(internet, fixed, mobile), 
-      list(`1` = ~lag(., 1)), 
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  )
-
-# Centering within and between countries
-dat <- dat %>%
-  group_by(country) %>% 
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>% 
-  ungroup() %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~. - mean(., na.rm = T))
-  )
-```
-
 Model 2 is a modification of Model 1.
@@
     (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
+  family = gaussian(),
+  unused = ~ cause
 )

### 2021-11-29 03-model-estimate.Rmd
Don't estimate SE for selfharm

@@
 ```{r}
-# Transform edge proportions to fit beta distribution
-# when this is used as an outcome
-itu <- itu %>% 
-  mutate(ib = if_else(internet == 0, .0000001, internet)) %>% 
-  mutate(ib = if_else(internet == 1, .9999999, internet))
-
 # Create lagged predictors
@@
         formula = bf_itu + bf_1 + set_rescor(FALSE), 
-        data = cur_data_all(),
+        # Transform intrnet edge values
+        data = cur_data_all() %>% 
+          mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
+          mutate(internet = if_else(internet == 1, .9999999, internet)),
         chains = hmc$chains, 
@@
 
-# fits_1_se <- dat %>%
-#   filter(!(cause %in% c("Anxiety", "Depression", "Selfharm")))
-#   group_by(cause) %>%
-#   summarise(
-#     fit_se = list(
-#       brm(
-#         formula = bf_itu + bf_1_se + set_rescor(FALSE),
-#         data = cur_data_all(),
-#         chains = hmc$chains,
-#         cores = hmc$cores,
-#         threads = hmc$threads,
-#         iter = hmc$iter,
-#         warmup = hmc$warmup,
-#         refresh = hmc$refresh,
-#         control = list(
-#           adapt_delta = hmc$adapt_delta,
-#           max_treedepth = hmc$max_treedepth
-#         ),
-#         file = str_glue("output/brm-1-se-{cur_group()}")
-#       )
-#     )
-#   )
+# This does not converge with selfharm
+fits_1_se <- dat %>%
+  filter(!(cause %in% c("Selfharm"))) %>% 
+  group_by(cause) %>%
+  summarise(
+    fit_se = list(
+      brm(
+        formula = bf_itu + bf_1_se + set_rescor(FALSE),
+        data = cur_data_all(),
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-1-se-{cur_group()}")
+      )
+    )
+  )
 ```
@@
 
-# fits_2 <- dat %>%
-#   group_by(cause) %>% 
-#   summarise(
-#     fit_se = list(
-#       brm(
-#         formula = bf_2_se, 
-#         data = cur_data_all(),
-#         chains = hmc$chains, 
-#         cores = hmc$cores, 
-#         threads = hmc$threads,
-#         iter = hmc$iter, 
-#         warmup = hmc$warmup, 
-#         refresh = hmc$refresh,
-#         control = list(
-#           adapt_delta = hmc$adapt_delta, 
-#           max_treedepth = hmc$max_treedepth
-#         ),
-#         file = str_glue("output/brm-2-se-{cur_group()}")
-#       )
-#     )
-#   )
+fits_2 <- dat %>%
+  filter(!(cause %in% c("Selfharm"))) %>% 
+  group_by(cause) %>%
+  summarise(
+    fit_se = list(
+      brm(
+        formula = bf_2_se,
+        data = cur_data_all(),
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("output/brm-2-se-{cur_group()}")
+      )
+    )
+  )
 ```
@@
     (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian()
+  family = gaussian(), 
+  unused = ~ cause
 )
@@
     (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian()
+  family = gaussian(),
+  unused = ~ cause
 )

### 2021-11-29 03-model-estimate.Rmd
fix data and setting hmc options

@@
 # MCMC settings
+ncores <- min(parallel::detectCores(), 12)
+nchains <- 4
 options(brms.backend = "cmdstanr")
 hmc <- list(
-  chains = 4,
-  cores = 4,
-  threads = 3,
+  chains = nchains,
+  cores = nchains,
+  threads = ncores %/% nchains,
   iter = 2000, 
@@
 dat <- dat %>% 
-  # Unique values exist for each country-year
-  group_by(region, country, year) %>% 
+  # Unique values exist for each country-year, but must be given for each
+  # outcome
+  group_by(region, country, year, cause) %>% 
   mutate(itu = 1:n() == 1) %>% 

### 2021-11-30 03-model-estimate.Rmd
Refactor fitting: map() over models and outcomes

--- 2021-11-28 03-model-estimate.Rmd
@@
 # MCMC settings
+ncores <- min(parallel::detectCores(), 12)
+nchains <- 4
 options(brms.backend = "cmdstanr")
 hmc <- list(
-  chains = 4,
-  cores = 4,
-  threads = 3,
-  iter = 2000, 
-  warmup = 1000,
+  chains = nchains,
+  cores = nchains,
+  threads = ncores %/% nchains,
+  iter = 1000, 
+  warmup = 500,
   refresh = 50,
@@
 
+- Drop countries with no values
 - Transform edge values of internet variable to fit beta
@@
 ```{r}
-# Transform edge proportions to fit beta distribution
-# when this is used as an outcome
+countries_no_internet <- itu %>% 
+  group_by(country) %>% 
+  summarise(s = sum(internet, na.rm = TRUE)) %>% 
+  filter(s == 0)
+
 itu <- itu %>% 
-  mutate(ib = if_else(internet == 0, .0000001, internet)) %>% 
-  mutate(ib = if_else(internet == 1, .9999999, internet))
+  filter(!(country %in% countries_no_internet$country))
+
+filter(itu, internet %in% c(0, 1))
+
+itu <- itu %>% 
+  mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
+  mutate(internet = if_else(internet == 1, .9999999, internet))
 
@@
 ```{r}
-# Give each outcome value a tag to ensure it is used in MV model
-dat <- dat %>% 
-  mutate(y = !is.na(val))
-
 # Indicate unique ITU values for MV model
 dat <- dat %>% 
-  # Unique values exist for each country-year
-  group_by(region, country, year) %>% 
+  # Unique values exist for each country-year, but must be given for each
+  # outcome
+  group_by(region, country, year, cause) %>% 
   mutate(itu = 1:n() == 1) %>% 
@@
 
-## Model 1
+## Model equations
 
@@
 We fit the model separately for each outcome.
-
-### Estimate
 
@@
 )
-```
 
-```{r}
-fits_1 <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE), 
-        data = cur_data_all(),
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-1-{cur_group()}")
-      )
-    )
-  )
-
-# fits_1_se <- dat %>%
-#   filter(!(cause %in% c("Anxiety", "Depression", "Selfharm")))
-#   group_by(cause) %>%
-#   summarise(
-#     fit_se = list(
-#       brm(
-#         formula = bf_itu + bf_1_se + set_rescor(FALSE),
-#         data = cur_data_all(),
-#         chains = hmc$chains,
-#         cores = hmc$cores,
-#         threads = hmc$threads,
-#         iter = hmc$iter,
-#         warmup = hmc$warmup,
-#         refresh = hmc$refresh,
-#         control = list(
-#           adapt_delta = hmc$adapt_delta,
-#           max_treedepth = hmc$max_treedepth
-#         ),
-#         file = str_glue("output/brm-1-se-{cur_group()}")
-#       )
-#     )
-#   )
-```
-
-### Checking
-
-Diagnostics: convergence and effective samples size
-
-```{r}
-f1d <- fits_1 %>% 
-  mutate(
-    out = 
-      map(
-        fit, 
-        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
-          summarise_draws(samples = length, default_convergence_measures())
-      )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out)
-f1d %>%  
-  kbl(
-    caption = "HMC Diagnostics, Model 1c",
-    digits = c(0,0,0,2,0,0)
-  ) %>% 
-  kable_paper(html_font = Font) %>% 
-  column_spec(
-    4, 
-    color = "white",
-    background = spec_color(
-      f1d$rhat, 
-      direction = 1, 
-      option = "C", 
-      end = .7
-    )
-  )
-```
-
-```{r}
-tmp <- fits_1 %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~pp_check(
-        .x, 
-        ndraws = 10, 
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val", 
-        newdata = .x$data
-      ) + 
-        facet_wrap("group", nrow = 1, scales = "free")
-    )
-  )
-wrap_plots(tmp$out, nrow = 3) &
-  scale_x_continuous(
-    breaks = pretty_breaks(2),
-    labels = function(x) percent(x/100)
-  )
-```
-
-## Model 2
-
-Prepare data for this model
-
-Model 2 is a modification of Model 1.
-First, we now switch to looking at internet use more specifically as a predictor, and therefore implement a univariate model of each outcome.
-Second, we include within- and between-country centred 1-year-lagged internet adoption values as predictors in the model.
-
-We fit this model in two increasingly complex forms, corresponding to models 1b and 1c, but with the addition of the internet adoption predictors, and one outcome model only.
-
-2c takes about 5 hours per 1000 iterations.
-
-```{r}
 bf_2 <- bf(
@@
 
-# Compile model separately for each outcome to give independent default priors
-fits_2 <- dat %>%
+bf_2_f <- bf(
+  val ~ 
+    year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb + 
+    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
+    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
+  family = gaussian(), 
+  unused = ~ cause
+)
+
+bf_2_m <- bf(
+  val ~ 
+    year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb + 
+    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
+    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
+  family = gaussian(),
+  unused = ~ cause
+)
+```
+
+## Fit all models
+
+```{r}
+models <- tibble(
+  model = c("1", "1-se", "2", "2-se", "2-f", "2-m"),
+  formula = list(
+    bf_itu + bf_1 + set_rescor(FALSE),
+    bf_itu + bf_1_se + set_rescor(FALSE),
+    bf_2,
+    bf_2_se,
+    bf_2_f,
+    bf_2_m
+  )
+)
+fits <- dat %>% 
+  # Could nest but need this to include group key in nested tibble
   group_by(cause) %>% 
-  summarise(
-    fit = list(
+  summarise(data = list(cur_data_all())) %>% 
+  crossing(models)
+
+# Don't estimate se models for selfharm--doesn't converge
+fits <- fits %>% 
+  filter(!(cause=="Selfharm" & str_detect(model, "se")))
+
+# Estimate all models
+fits <- fits %>% 
+  mutate(
+    fit = pmap(
+      list(cause=cause, data=data, model=model, formula=formula),
+      function(cause, data, model, formula)
         brm(
-        formula = bf_2, 
-        data = cur_data_all(),
+          formula = formula,
+          data = data,
           chains = hmc$chains,
@@
           ),
-        file = str_glue("output/brm-2-{cur_group()}")
+          file = str_glue("output/brm-{model}-{cause}")
         )
@@
   )
-
-# fits_2 <- dat %>%
-#   group_by(cause) %>% 
-#   summarise(
-#     fit_se = list(
-#       brm(
-#         formula = bf_2_se, 
-#         data = cur_data_all(),
-#         chains = hmc$chains, 
-#         cores = hmc$cores, 
-#         threads = hmc$threads,
-#         iter = hmc$iter, 
-#         warmup = hmc$warmup, 
-#         refresh = hmc$refresh,
-#         control = list(
-#           adapt_delta = hmc$adapt_delta, 
-#           max_treedepth = hmc$max_treedepth
-#         ),
-#         file = str_glue("output/brm-2-se-{cur_group()}")
-#       )
-#     )
-#   )
 ```
@@
 ```{r}
-f2d <- fits_2 %>% 
+diag_1 <- fits %>% 
+  filter(model == "1") %>% 
   mutate(
@@
         fit, 
-        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
+        ~as_draws_df(., variable = "^b_|^sd_|^cor_", regex = TRUE) %>% 
           summarise_draws(samples = length, default_convergence_measures())
@@
   unnest(out)
-f2d %>%  
+diag_1 %>%  
   kbl(
-    caption = "HMC Diagnostics, Model 2c",
+    caption = "HMC Diagnostics, Model 1",
     digits = c(0,0,0,2,0,0)
   ) %>% 
-  kable_paper(html_font = Font, full_width = FALSE) %>% 
+  kable_paper(html_font = Font) %>% 
   column_spec(
@@
     background = spec_color(
-      f2d$rhat, 
+      diag_1$rhat, 
       direction = 1, 
@@
     )
-  ) %>% 
-  scroll_box(height = "600px", width = "800px")
+  )
 ```
@@
 ```{r}
-tmp <- fits_2 %>% 
+ppcheck_1 <- fits %>% 
+  filter(model == "1")
   mutate(
@@
       ) + 
-        facet_wrap("group", nrow = 1, scales = "free_y")
+        facet_wrap("group", nrow = 1, scales = "free")
     )
   )
-wrap_plots(tmp$out, nrow = 3) &
+wrap_plots(ppcheck_1$out, nrow = 6) &
   scale_x_continuous(
     breaks = pretty_breaks(2),
-    labels = function(x) percent(x/100, 1)
-  )
+    labels = function(x) percent(x/100)
+  ) &
+  theme(legend.position = "none")
 ```
-
-### Summary
-
-We then display the model's population-level parameters
-
-```{r}
-tmp <- fits_2 %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
-        summarise_draws(
-          mean, quantile, rhat, 
-          .args = list(probs = c(.025, .975))
-        )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(
-    result = str_glue(
-      "b = {mean} ({`2.5%`}, {`97.5%`})"
-    )
-  ) %>% 
-  rowwise() %>% 
-  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
-  pivot_wider(names_from = cause, values_from = result)
-tmp %>%   
-  kbl() %>% 
-  kable_paper(html_font = Font) 
-```
-
-Coefficients
-
-```{r}
-tmp <- fits_2 %>% 
-  mutate(
-    out = map(
-      fit, 
-      ~emtrends(.x, var = "i1_cw", by = c("sex", "age"))
-    )
-  ) %>% 
-  select(-fit)
-tmp %>% 
-  mutate(out = map(out, ~as.data.frame(out))) %>% 
-  unnest(out) %>% 
-  select(cause, sex, age, i1_cw.trend, lower.HPD, upper.HPD) %>% 
-  kbl(digits = 3) %>% 
-  kable_minimal(full_width = FALSE)
-```
-
-## Model 2 for fixed and mobile
-
-```{r}
-bf_2_f <- bf(
-  val ~ 
-    year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb + 
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian()
-)
-
-fits_2_f <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      brm(
-        formula = bf_2_f, 
-        data = cur_data_all(),
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2-fixed-{cur_group()}")
-      )
-    )
-  )
-
-bf_2_m <- bf(
-  val ~ 
-    year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb + 
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian()
-)
-
-fits_2_m <- dat %>%
-  group_by(cause) %>% 
-  summarise(
-    fit = list(
-      brm(
-        formula = bf_2_m, 
-        data = cur_data_all(),
-        chains = hmc$chains, 
-        cores = hmc$cores, 
-        threads = hmc$threads,
-        iter = hmc$iter, 
-        warmup = hmc$warmup, 
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta, 
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("output/brm-2-mobile-{cur_group()}")
-      )
-    )
-  )
-```

### 2021-12-17 index.qmd
Bookdown -> Quarto

---
title: "Adolescent well-being in the digital age"
author: "Matti Vuorre"
date: "`r Sys.time()`"
execute:
  eval: true
  error: true
  cache: true
  warning: false
  message: false
format: 
  html:
    monofont: Fira Code
    font-size: 1.0em
    linestretch: 1.4
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    code-link: true
toc: true
toc-depth: 4
toc-title: Contents
number-sections: false
crossref:
  fig-prefix: Figure
  tbl-prefix: Table
---

```{r document-options, include = FALSE, cache = FALSE}
# knitr options
knitr::opts_chunk$set(
  fig.align = "center",
  cache.lazy = FALSE # Fix large knitr cache
)
```

## Preface

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).

::: {.callout-note collapse="true"}
### Reproducibility

The analyses were conducted in R, and can be reproduced locally:

1.  Clone the github repo

-   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
-   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2.  Prepare the R environment

-   Terminal: `Rscript -e "renv::restore()`
-   RStudio: Click renv -> Restore Library in the Packages panel

3.  Render `index.qmd` to `index.html`

-   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
-   Terminal: `quarto render index.qmd`
-   RStudio: Open `index.qmd` and click Render

The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.

If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
:::

## Data preparation

Our analyses draw on three sources of data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021. The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019. And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.

In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:

```{r setup, cache = FALSE}

# Packages
library(readxl)
library(knitr)
library(ragg)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(ggtext)
library(dtplyr)
library(lubridate)
library(kableExtra)
library(gtsummary)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(kableExtra)
library(tidyverse)

# MCMC settings (ensure at most 12 cores)
ncores <- min(parallel::detectCores(logical = FALSE), 12)
nchains <- 4
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = nchains,
  cores = nchains,
  threads = ncores %/% nchains,
  iter = 2500,
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90,
  max_treedepth = 10
)

# Plotting theme & use this font if available
Font <- "Titillium Web"
theme_set(
  theme_linedraw(
    base_size = 12,
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
    )
)

# Format tables
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = Font,
    font_size = 13,
    lightable_options = "striped",
    position = "center",
    full_width = FALSE
  )
}

# Create directory for intermediate files
dir.create("models", FALSE)
```

### Gallup World Poll

We first prepare the Gallup data. Note that this data set is not publicly available, and therefore not included in our repository. We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.

```{r gallup-codebook}
#| echo: false
#| eval: false
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_101521.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) %>%
  generate_dictionary()
```

Here we import the relevant variables from Gallup's SPSS files and then

-   Clean the variable names
-   Set appropriate missing values (`NaN`, not e.g. `-99`)
-   Use appropriate coding schemes (e.g. 0: no; 1: yes)
-   Calculate scale scores (means over items)
-   Rescale outcomes to proportions (0 - 1)
-   Subset the data to 15 to 24 year olds
-   Create age-categories in line with GBD data
-   Drop one 13 year old as this data should only have people 15 and older

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- "data-raw/Gallup/gwp-processed.rds"
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    "data-raw/Gallup/The_Gallup_101521.sav",
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

  # Get rid of SPSS attributes
  gwp <- gwp %>%
    zap_labels() %>%
    zap_label() %>%
    zap_widths() %>%
    zap_formats()

  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}

gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

# Scale scores note rescaling
gwp <- gwp %>%
  mutate(
    Life_satisfaction = Life_satisfaction / 10,
    Negative_experiences =
      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
    Positive_experiences =
      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
  ) %>%
  select(-c(wp60:wp74))

# Categorize ages
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 105, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Focus on young people
gwp <- gwp %>%
  filter(age %in% c("15 to 19", "20 to 24"))
```

Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex). Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    se = sd(val, na.rm = TRUE) / sqrt(n()),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

We have three data sets with information on countries. Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. We do that here for the GWP data, and check that all countries receive a unique name.

```{r gwp-harmonise-countries}
#| results: hold
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GWP harmonised country names") %>%
  kable_custom()

# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising

# Harmonise old names and replace only if harmonised name found
gwp <- gwp %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) %>%
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### Global Burden of Disease

We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R. They are inside downloaded `.zip` files, of which there may be more than one.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/",
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>%
  read_csv()
```

We then clean the GBD data and

-   Clean the variable names
-   Remove the metric and measure variables; we focus on prevalence rate
    -   prevalence: Total number of cases
    -   rate: Total cases per 100,000 population
-   Convert outcome rates to proportions (0 - 1)
-   Clean cause names and rename to outcome to harmonise with GWP
-   Convert GBD estimated rate CI limits to an approximate standard error
-   Subset data to young people (10 - 24)

```{r gbd-data-clean}
# First step is to clean names
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>%
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>%
  rename(country = location, outcome = cause)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

# Focus on young people
gbd <- gbd %>%
  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
#| results: hold
#| label: tbl-gbd-countries
#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GBD harmonised country names") %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### International Telecommunication Union

After processing the outcome tables above, we move on to the internet adoption metrics from the ITU. We downloaded these data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.

After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1). Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "ITU countries"
#| layout-ncol: 1

# Download data sets from the ITU website if not yet downloaded
if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
  )
}

# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(fixed = as.numeric(value)) %>%
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(mobile = as.numeric(value)) %>%
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(internet = as.numeric(value)) %>%
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>%
  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "ITU harmonised country names") %>%
  kable_custom()

# Harmonise old names and replace only if harmonised name found
itu <- itu %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

# Drop countries that don't exist in outcomes
itu <- itu %>%
  filter(
    country %in% unique(gbd$country) | country %in% unique(gwp$country)
  )

# Drop countries that don't have any actual internet data
itu_zeros <- itu %>%
  group_by(country) %>%
  summarise(s = sum(internet, na.rm = TRUE)) %>%
  filter(s == 0)

itu <- itu %>%
  filter(!(country %in% itu_zeros$country))
rm(itu_zeros)
```

#### Missingness

We then impute missing intermediate values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.

```{r itu-impute}
#| results: hold
#| label: tbl-itu-impute
#| tbl-cap: "Summary of ITU data imputation"

# Reshape to easily impute all variables
itu_long <- itu %>%
  pivot_longer(c(internet, fixed, mobile))

# Impute by country and variable
itu_long <- itu_long %>%
  group_by(country, name) %>%
  # Find first and last year with this variable in each country
  # so as to prevent extrapolation
  mutate(
    min_year = year[min(which(!is.na(value)))],
    max_year = year[max(which(!is.na(value)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  mutate(
    across(
      value,
      .fns = list(
        i = possibly(
          function(x) na_interpolation(x, maxgap = Inf),
          otherwise = NaN
        )
      )
    )
  ) %>%
  # Take out projected (non-intermediate) imputed values
  mutate(
    value_i = if_else(
      between(year, unique(min_year), unique(max_year)),
      value_i,
      NaN
    )
  ) %>%
  ungroup() %>%
  select(-min_year, -max_year)

# Summary
itu_long %>%
  group_by(name) %>%
  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
  summarise(
    n_miss_orig = sum(is.na(value) & year >= min_year),
    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
    n_miss_imp = sum(is.na(value_i) & year >= min_year),
    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
    imputed = n_miss_orig - n_miss_imp
  ) %>%
  kbl(caption = "ITU data imputation summary") %>%
  kable_custom()

# We then replace the original values with the imputed ones
itu <- itu_long %>%
  # Pick non-missing value, from original and imputed
  mutate(value = coalesce(value, value_i)) %>%
  select(-value_i) %>%
  pivot_wider()
rm(itu_long)
```

### GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r globe-regions}
#| results: hold
#| label: tbl-globe
#| tbl-cap: "Countries with manually filled region"

regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>%
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>%
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>%
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in GBD not present in region data
no_region_gbd <- filter(
  distinct(gbd, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

# Then see what countries in GWP are without region
no_region_gwp <- filter(
  distinct(gwp, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

bind_rows(no_region_gbd, no_region_gwp) %>%
  arrange(country) %>%
  distinct() %>%
  write_csv("data-raw/Regions/countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/countries-without-region-filled.csv"
)

# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>%
  bind_rows(
    regions_filled %>%
      mutate(Note = "Filled")
  ) %>%
  arrange(region, country)

# Shorter name for plots
regions <- regions %>%
  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))

# Display table of regions and countries
regions %>%
  drop_na(Note) %>%
  select(-Note) %>%
  arrange(region, country) %>%
  kbl(caption = "Countries with a manually filled region") %>%
  kable_custom()

# Clean region labels
regions$region <- str_replace_all(regions$region, " ", "_")
regions$region <- factor(regions$region)

# Remove unnecessary items
regions <- select(regions, -Note)

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)
# Remove now unnecessary variables
rm(no_region_gbd, no_region_gwp, regions_filled, regions)
```

### ITU summary table

```{r itu-summary-table}
#| column: page
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

itu %>%
  select(region, country, year, internet) %>%
  mutate(internet = internet * 100) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(caption = "ITU summary") %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

## RQ1: Time courses

Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)? And, do changes in well-being correlate with changes in internet adoption (RQ1b)? To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.

### Modelling

We first prepare the variables for modelling:

-   Transform edge values of internet variable to fit beta
    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle)
-   Ensure that age and sex are treated with contrast codes

```{r model1-prepare-data}
# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet))

# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center and scale year
dat <- dat %>%
  mutate(year = (year - 2010) / 10)

# Identify values to use in mv models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1) %>%
  ungroup()

# Ensure that factors are contrast coded
dat <- dat %>%
  mutate(across(c(sex, age), factor))
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
dat <- dat %>%
  mutate(across(c(val, se), ~ . * 100))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(dat, outcome, region, country, year)

dat %>%
  group_by(outcome) %>%
  summarise(
    min = min(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    internet_min = min(internet, na.rm = TRUE),
    internet_max = max(internet, na.rm = TRUE)
  ) %>%
  kable(digits = 7) %>% 
  kable_custom()
```

#### Specification

We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b). Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g. Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries. We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)

We fit the model separately for each outcome. Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret). We therefore estimate six separate bivariate models

In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian. All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes. This latter specification is important to allow answering RQ1b.

The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate. For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age). The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data. Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.

We write the model as

$$
\begin{align*}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
\left[\begin{array}{c}
\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{r}
),
\left[\begin{array}{c}
\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{c}
)
\end{align*}
$$

Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.

We then define the model formulas in brms' formula syntax. First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table. To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model. The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).

```{r model1-itu-bf}
# Define a model of internet proportion over year
bf_itu <- bf(
  internet | resp_subset(itu) ~
  year +
    (year |c| country) +
    (year |r| region),
  family = Beta()
)
```

Here, we specify the outcome model. Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model. Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors. In addition, it leads to the residual variance to be estimated.

```{r model1-val-bf}
# Meta-regression model of outcomes
bf_1 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age +
    (year * sex + year * age | c | country) +
    (year * sex + year * age | r | region),
  family = gaussian()
)
```

Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged. We therefore effectively removed the SEs from self-harm by setting them to zero

```{r model1-selfharm-se}
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))
```

#### Fitting

We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.

```{r fit-model-1}

fits <- dat %>%
  # Could nest but need this to include group key in nested tibble
  group_by(outcome) %>%
  summarise(data = list(cur_data_all()))

fits <- fits %>%
  mutate(
    fit1 = map2(
      data, outcome,
      ~brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE),
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-1-internet")
      )
    )
  )
```

#### Summary

Here is a summary of the data modelled for each outcome

```{r model-1-data-summary}
#| column: body-outset
#| tbl-cap: "Summaries of data included in Model 1"
#| label: tbl-m1-data
msum <- function(x) {
  tibble(
    regions = ngrps(x)$region,
    countries = ngrps(x)$country,
    `year/country` = x$data %>%
      distinct(country, year) %>%
      count(country) %>%
      pull(n) %>%
      median(),
    nobs_internet = standata(x)$N_internet,
    nobs_outcome = standata(x)$N_val,
    outcome_range = str_glue(
      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
    )
  )
}
fits %>%
  mutate(summary = map(fit1, msum)) %>%
  select(outcome, summary) %>%
  unnest(summary) %>%
  kbl(caption = "Model 1 data summary") %>%
  kable_custom() %>% 
  row_spec(0, bold = TRUE)
```

#### Model checking

Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section

##### MCMC diagnostics

First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.

We can see that the models have converged nicely, apart from the self-harm outcome.

```{r model-1-diagnostics}
#| results: hold
#| label: tab-model1-diagnostic
#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
#| column: body-outset

diagnostic_table <- function(fit, rx, cp) {
  diag_1 <- fits %>%
    select(fit = {{ fit }}, outcome) %>% 
    mutate(
      out =
        map(
          fit,
          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
            summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>%
    select(outcome, out) %>%
    unnest(out)
  diag_1 %>%
    kbl(
      caption = cp,
      digits = c(0, 0, 0, 2, 0, 0)
    ) %>%
    column_spec(
      4,
      color = "white",
      background = spec_color(
        log(diag_1$rhat),
        direction = 1,
        option = "C",
        end = .6
      )
    ) %>%
    column_spec(
      c(5, 6),
      color = "white",
      background = spec_color(
        log(diag_1$ess_tail / diag_1$samples),
        direction = 1,
        option = "C",
        end = 0,
        begin = .6
      )
    ) %>%
    kable_custom()
}
diagnostic_table(
  fit1,
  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
  cp = "Model 1 MCMC diagnostics."
) %>% 
  scroll_box(height = "300px")
```

##### Posterior predictive check

We then take a coarse look at how well the models reproduce the input data.

```{r ppcheck-density}

#| column: page
#| fig-cap: "Graphical posterior predictive check by region (Model 1). Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g. Anglo Depression)."
#| label: fig-ppcheck-1
ppcheck_1 <- fits %>%
  group_by(outcome) %>%
  mutate(
    out = map(
      fit1,
      ~ pp_check(
        .x,
        ndraws = 10,
        type = "dens_overlay_grouped",
        group = "region",
        resp = "val",
        newdata = .x$data
      )[[1]]
    )
  ) %>%
  ungroup() %>% 
  select(outcome, out) %>%
  unnest(out)

ppcheck_1 %>%
  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
  scale_color_brewer(palette = "Set1") +
  scale_alpha_manual(values = c(.2, 1)) +
  stat_density(
    geom = "line",
    size = .75,
    position = position_identity()
  ) +
  labs(x = "Value", y = "Density") +
  facet_grid2(
    outcome ~ group,
    scales = "free", independent = "x",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

### Results

#### RQ1a: Temporal trends

Before presenting the time trends, we must calculate the required quantities from the posterior distribution. Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.

```{r calculate-simple-effects}

#' Posterior draws at average and region levels
#'
#' @param x brmsfit (model 1/2)
#' @param p name of parameter
#'
#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
pdraws <- function(x, p = "val_year") {
  bind_cols(
    tibble("Average" = fixef(x, summary = FALSE)[, p]),
    as_tibble(coef(x, summary = FALSE)$region[, , p])
  ) %>%
    pivot_longer(everything(), names_to = "region")
}

#' Posterior summaries at country- region- and average levels
#'
#' @param x brmsfit (model 1/2)
#' @param p name of parameter
#'
#' @return a long tibble with posterior summary of p at each level
psums <- function(x, p = "val_year") {
  psum_region <- bind_rows(
    fixef(x) %>%
      as.data.frame() %>%
      rownames_to_column("parameter") %>%
      filter(parameter == {{ p }}) %>%
      select(-parameter) %>%
      mutate(region = "Average"),
    coef(x)$region[, , p] %>%
      as.data.frame() %>%
      rownames_to_column("region")
  ) %>%
    as_tibble()

  psum_country <- ranef(x)$country[, , p] %>%
    as.data.frame() %>%
    rownames_to_column("country") %>%
    left_join(distinct(x$data, region, country)) %>%
    as_tibble() %>%
    left_join(select(psum_region, region, r_value = Estimate)) %>%
    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
    select(-r_value)

  bind_rows(
    psum_region,
    psum_country
  ) %>%
    mutate(region = fct_relevel(region, "Average"))
}

p_draws <- fits %>%
  mutate(pdraws = map(fit1, pdraws)) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums <- fits %>%
  mutate(psums = map(fit1, psums)) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
p_sums_internet <- fits %>%
  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
  select(outcome, psums) %>%
  unnest(psums) %>%
  mutate(region = fct_relevel(region, "Average"))
```

We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions. Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).

```{r forest-trends}
#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Forest plot of linear trends in outcomes"
#| label: fig-forest-trends
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction. This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade. The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.

Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data. This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes. Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.

We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region. However, the average change again is not credibly different from zero. Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety. Depression and self-harm, on the other hand, had decreased across the board.

In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.

Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.

```{r fitted-trend-country}

#' Get (grand mean) fitted values for countries
#'
#' @param x a brmsfit model 1
#'
#' @return a data frame of fitted values
fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country, region, outcome, year) %>%
    summarise(val = mean(val, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(sex = NA, age = NA, se = 0)
  newy <- bind_cols(
    newx,
    as.data.frame(fitted(x, newdata = newx, resp = "val"))
  ) %>%
    select(-outcome)
  newy
}

f_country <- fits %>%
  mutate(fc = map(fit1, fitted_country)) %>%
  select(outcome, fc)

#' Draw a panel plot of countries' fitted values and data
#'
#' @param x fitted country level data from fitted_country()
#' @param y outcome
#'
#' @return a ggplot for that outcome
plot_country <- function(x, y) {
  coefs <- p_sums %>%
    drop_na(country) %>%
    filter(outcome == y) %>%
    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
    mutate(country = fct_reorder(country, coef))
  x %>%
    left_join(coefs) %>%
    mutate(country = fct_reorder(country, coef)) %>%
    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
    scale_y_continuous(
      str_replace(y, "_", " "),
      breaks = pretty_breaks(),
      expand = expansion(.15),
      labels = function(x) {
        percent(x / 100, .01) %>%
          str_remove("\\.00")
      }
    ) +
    # Add parameters in text
    geom_richtext(
      data = coefs %>%
        mutate(across(where(is.numeric), ~ number(., .01))),
      aes(
        x = make_date(2000), y = Inf,
        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
      ),
      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
      family = Font,
      fill = alpha("white", .3), label.color = NA,
      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
    ) +
    geom_point(aes(y = val), shape = 1, alpha = .5) +
    geom_ribbon(
      aes(ymin = Q2.5, ymax = Q97.5),
      alpha = .3, col = NA, fill = "dodgerblue1"
    ) +
    geom_line(
      size = 0.5, col = "dodgerblue1"
    ) +
    facet_wrap(
      "country"
    ) +
    theme(panel.spacing = unit(2, "pt"))
}

# Create the plot for each outcome
f_country <- f_country %>%
  mutate(
    plot = map2(
      fc, outcome,
      ~ plot_country(.x, .y)
    )
  )
```

::: {.panel-tabset .column-screen-inset-shaded}
##### All outcomes

```{r trends-regions}
#| echo: false
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Trends in all variables across regions"
#| label: fig-trends-regions

# Stack data sets
# Assume all outcomes are proportions (0-1)
dat_all <- bind_rows(
  gwp,
  gbd,
  itu %>% mutate(outcome = "Internet", val = internet)
) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup()

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "5 years",
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title.y = element_blank()
  )
```

##### Life satisfaction

```{r trends-ls}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
#| label: fig-trends-ls
f_country$plot[[1]]
```

##### Negative experiences

```{r trends-ne}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Negative experiences trends, ordered by association magnitude"
#| label: fig-trends-ne
f_country$plot[[2]]
```

##### Positive experiences

```{r trends-pe}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Positive experiences trends, ordered by association magnitude"
#| label: fig-trends-pe
f_country$plot[[3]]
```

##### Anxiety

```{r trends-anx}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Anxiety trends, ordered by association magnitude"
#| label: fig-trends-anx
f_country$plot[[4]]
```

##### Depression

```{r trends-dep}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Depression trends, ordered by association magnitude"
#| label: fig-trends-dep
f_country$plot[[5]]
```

##### Self-harm

```{r trends-sel}
#| echo: false
#| fig-width: 16
#| fig-height: 12
#| fig-cap: "Self-harm trends, ordered by association magnitude"
#| label: fig-trends-sel
f_country$plot[[6]]
```
:::

#### RQ1b: Correlations

We then turned to research question 1b: To what extent were changes in well-being and internet adoption correlated across countries.

To investigate we examined the correlations between $\gamma^y_1$ and $\gamma^x_1$ ($\sigma_{\gamma^y_1,\gamma^x_1}$ in $\Sigma^{\text{c}}$). A positive correlation would indicate that countries with greater increases in internet adoption between 2000 and 2020 would tend to have greater increases in $y$ (e.g. Life satisfaction).

To answer, we display $\sigma_{\gamma^y_1,\gamma^x_1}$ from each outcome's model in the figure below. The figures are scatterplots of country-level trend coefficients, where each point's x-y coordinate indicate their trend magnitudes. The overlaid ellipses are the model's 95% predictive limits for $\gamma^y_1$ and $\gamma^x_1$.

```{r scatterplot-time-internet}
#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Scatterplots of country-level internet and outcome trends."
#| label: fig-trend-scatterplot

# Correlation parameters
cor_pars <- fits %>%
  mutate(
    out = map(
      fit1,
      ~ as_draws_df(
        .x,
        variable = "cor_country__internet_year__val_year"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

# Ellipses
ellipses <- fits %>%
  mutate(
    ellipse = map(
      fit1,
      ~ as_draws_df(
        .x,
        c(
          "b_val_year",
          "b_internet_year",
          "sd_country__val_year",
          "sd_country__internet_year",
          "cor_country__internet_year__val_year"
        )
      ) %>%
        slice_sample(n = 100) %>%
        rename(
          cor = cor_country__internet_year__val_year,
          sd_outcome = sd_country__val_year,
          sd_i = sd_country__internet_year,
          b_outcome = b_val_year,
          b_i = b_internet_year
        ) %>%
        mutate(
          e = pmap(
            list(cor, sd_outcome, sd_i, b_outcome, b_i),
            function(cor, sd_a, sd_i, b_a, b_i) {
              ellipse(
                cor,
                scale = c(sd_i, sd_outcome),
                centre = c(b_i, b_outcome),
                level = .95
              ) %>%
                as_tibble()
            }
          )
        ) %>%
        unnest(e)
    )
  )
ellipses <- ellipses %>%
  select(outcome, ellipse) %>%
  unnest(ellipse)

# Wide tibble of parameters
left_join(
  p_sums %>%
    drop_na(country) %>%
    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
  p_sums_internet %>%
    drop_na(country) %>%
    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
) %>%
  ggplot(aes(Internet_Estimate, Outcome_Estimate)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_path(
    data = ellipses,
    aes(x = x, y = y, group = .draw),
    alpha = .2, size = .1, col = "dodgerblue2"
  ) +
  geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
  scale_y_continuous(
    "Outcome trend",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  scale_x_continuous(
    "Internet trend",
    breaks = pretty_breaks()
  ) +
  geom_text(
    data = cor_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y",
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(aspect.ratio = 1)
```

#### Other results from Model 1

##### Shrinkage

It's important to note that at the level of countries and regions, the model parameters refer to country^\*^ and region^\*^, that is as they are in the sample of other countries and regions. This modelling strategy is important because it allows describing the parameters at each level while adjusting the values toward the group means (preventing "false alarms"). However it is then important to examine those values against their "fixed effect" counterparts, which we do here.

```{r shrinkage}

#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Scatterplots of multilevel and independent model coefficients"
#| label: fig-trend-shrinkage

lm_coefs <- fits %>%
  mutate(
    data = map(fit1, ~ as_tibble(.x$data))
  ) %>%
  mutate(
    fit_val = map(
      data,
      ~ tidy(
        lm(val ~ 0 + country + year:country, data = .x)
      )
    ),
    fit_internet = map(
      data,
      ~ tidy(
        gam(
          internet ~ 0 + country + year:country,
          family = betar, data = .x %>%
            filter(itu)
        ),
        parametric = TRUE
      )
    )
  )
lm_coefs <- lm_coefs %>%
  select(outcome, fit_val, fit_internet) %>%
  pivot_longer(c(fit_val, fit_internet)) %>%
  mutate(name = str_remove(name, "fit_")) %>%
  unnest(value) %>%
  select(outcome, name, term, estimate, std.error) %>%
  filter(str_detect(term, ":")) %>%
  mutate(term = str_remove(term, "country")) %>%
  mutate(term = str_remove(term, ":year")) %>%
  pivot_wider(names_from = name, values_from = c(estimate, std.error)) %>%
  rename(country = term)

# Plot
left_join(
  p_sums %>%
    drop_na(country) %>%
    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
  p_sums_internet %>%
    drop_na(country) %>%
    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
) %>%
  left_join(lm_coefs) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  ggplot(aes(Internet_Estimate, Outcome_Estimate, col = region)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_segment(
    aes(
      x = estimate_internet, xend = Internet_Estimate,
      y = estimate_val, yend = Outcome_Estimate
    ),
    arrow = arrow(type = "closed", length = unit(3, "pt")),
    size = .25, show.legend = FALSE
  ) +
  geom_point(size = 1.1, alpha = .4) +
  scale_y_continuous(
    "Outcome trend",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  scale_x_continuous(
    "Internet trend",
    breaks = pretty_breaks()
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  guides(
    color = guide_legend(override.aes = list(size = 2, alpha = 1))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "bottom"
  )
```

## RQ2: Associations

We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption? To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes. Before modelling, we calculated these quantities as shown in this code block.

```{r model2-data-prepare}
# Create lagged predictors
dat <- dat %>% 
  arrange(outcome, region, country, year) %>%
  group_by(outcome, region, country, sex, age) %>%
  mutate(
    across(
      c(internet, fixed, mobile),
      list(`1` = ~ lag(., 1)),
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  ) %>% 
  ungroup()

# Centering predictors within and between countries
dat <- dat %>%
  group_by(outcome, country) %>%
  mutate(
    i1_cb = mean(i1, na.rm = TRUE), # Country average
    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
    f1_cb = mean(f1, na.rm = TRUE),
    f1_cw = f1 - f1_cb,
    m1_cb = mean(m1, na.rm = TRUE),
    m1_cw = m1 - m1_cb,
  ) %>%
  group_by(outcome) %>% 
  # Grand-mean center the country averages
  mutate(
    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
  )
```

### Specification and fitting

Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions

$$\begin{align*}
y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\

\mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
\gamma_{0\text{country}[i]} + \\ &(\beta_{1} + \delta_{1\text{region}[i]} + \gamma_{1\text{country}[i]})\text{Time}_i + 
\\ &(\beta_{2} + \delta_{2\text{region}[i]} + \gamma_{2\text{country}[i]})\text{Sex}_i + 
\\ &(\beta_{3} + \delta_{3\text{region}[i]} + \gamma_{3\text{country}[i]})\text{Age}_i + 
\\ &(\beta_{4} + \delta_{4\text{region}[i]} + \gamma_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
\\ &(\beta_{5} + \delta_{5\text{region}[i]} + \gamma_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i +
\\ &(\beta_{6} + \delta_{6\text{region}[i]} + \gamma_{6\text{country}[i]})\text{Internet}^{\text{t-1}}_i + 
\\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\

\left[\begin{array}{c}
\delta_{0\text{region}} \\ \delta_{1\text{region}} \\ 
\delta_{2\text{region}} \\ \delta_{3\text{region}} \\ 
\delta_{4\text{region}} \\ \delta_{5\text{region}} \\ 
\delta_{6\text{region}} \\ \delta_{7\text{region}} \\ 
\delta_{8\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{r}
),
\left[\begin{array}{c}
\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\ 
\gamma_{4\text{country}} \\ \gamma_{5\text{country}} \\ 
\gamma_{6\text{country}} \\ \gamma_{7\text{country}} \\ 
\gamma_{8\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{c}
)
\end{align*}$$

```{r fit-model-2}

# Model formula is only a small update to Model 1
bf_2 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
  family = gaussian()
)

# As above with model 1
fits <- fits %>%
  mutate(
    fit2 = map2(
      data, outcome,
      ~brm(
        formula = bf_2,
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-2-internet")
      )
    )
  )
```

### Results

First, we compared the R2 values between Models 1 and 2. This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2). However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.

```{r model21-compare}

#| results: hold
#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
#| label: tbl-m12-r2
fits %>%
  select(outcome, fit1, fit2) %>% 
  pivot_longer(c(fit1, fit2)) %>% 
  mutate(
    r2 = map(
      value,
      ~ bayes_R2(., resp = "val") %>%
        as.data.frame() %>%
        mutate(across(everything(), ~ percent(., .1))) %>%
        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
    )
  ) %>%
  select(-value) %>%
  unnest(r2) %>% 
  pivot_wider(
    names_from = name,
    values_from = result,
    names_prefix = "Model "
  ) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  kbl(caption = "Model 1 and 2 R-squared values") %>%
  kable_custom()
```

Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.

```{r model2-calculate-coefficients}

p_draws <- fits %>%
  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws)

p_sums <- fits %>%
  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
  select(outcome, psums) %>%
  unnest(psums)

p_draws <- p_draws %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
p_sums <- p_sums %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
```

We then display summaries of the parameters' posterior distributions as forest plots, like above. Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).

```{r forest-internet}
#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Forest plot of internet associations"
#| label: fig-forest-internet
p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
```

This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small. First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`. However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%. Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region. However, none of the average associations were credibly different from zero. The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.

To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.

```{r model2-fitted-values}

#| column: screen-inset
#| fig-width: 14
#| fig-height: 9
#| fig-cap: "Counterfactual plot of internet associations"
#| label: fig-fitted-internet

fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country) %>%
    mutate(
      xmin = min(i1_cw, na.rm = TRUE),
      xmax = max(i1_cw, na.rm = TRUE)
    ) %>%
    filter(i1_cw %in% c(xmin, xmax)) %>%
    ungroup() %>%
    distinct(country, region, outcome, i1_cw, i1_cb) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)
  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
    select(-outcome)
  newy
}

fitted_region <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region) %>%
    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = ~ 
          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
        )
    )
  ) %>%
    select(-outcome)
  newy
}

f_country <- fits %>%
  mutate(fc = map(fit2, fitted_country)) %>%
  select(outcome, fc) %>%
  unnest(fc)

f_region <- fits %>%
  mutate(fr = map(fit2, fitted_region)) %>%
  select(outcome, fr) %>%
  unnest(fr)

f_country %>%
  ggplot(aes(i1_cw, Estimate)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = c(-.35, 0, .35),
    labels = function(x) percent(x, 1)
  ) +
  scale_y_continuous(
    "Estimate",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  geom_blank() +
  geom_ribbon(
    data = f_region,
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .15, fill = "dodgerblue4"
  ) +
  geom_line(
    data = f_region,
    col = "dodgerblue4", size = .6
  ) +
  geom_line(
    aes(group = country),
    size = .4, alpha = .35, col = "dodgerblue1"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    panel.spacing = unit(2, "pt"),
    axis.title.y = element_blank()
  )
```

### Other results from Model 2

We then focused on the between-country association between internet adoption and well-being. Recall that the model does not adjust for between-country differences so these associations are likely to reflect many other factors covarying with internet adoption (e.g. wealth and development factors).

```{r}
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Between-country associations"
#| label: fig-cb1

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region, country) %>%
    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NULL
        )
    )
  ) %>%
    select(-outcome)
  newy
}
tmp <- fits %>% 
  mutate(out = map(fit2, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

cb1_pars <- fits %>%
  mutate(
    out = map(
      fit2,
      ~ as_draws_df(
        .x,
        variable = "b_i1_cb"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(i1_cb, val)) +
  scale_x_continuous(
    "Between-country centered internet adoption",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75,
    aes(col = region)
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    fill = "dodgerblue2",
    alpha = .2
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

## RQ3: Demographics

We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents? To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations. In this section, we present results based on the moderated effects.

### Trends

```{r model1-demographics}

h_gwp <- c(
  `15 to 19` =
    "val_year + val_year:age1 * 1 = 0",
  `20 to 24` =
    "val_year + val_year:age1 * -1 = 0",
  `Female` =
    "val_year + val_year:sex1 * 1 = 0",
  `Male` =
    "val_year + val_year:sex1 * -1 = 0"
)
h_gbd <- c(
  `10 to 14` =
    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
  `15 to 19` =
    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
  `20 to 24` =
    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
  `Female` =
    "val_year + val_year:sex1 * 1 = 0",
  `Male` =
    "val_year + val_year:sex1 * -1 = 0"
)
#' Calculate posterior draws for simple effects (by sex and age) for regions and average
#'
#' @param x brmsfit model 2
#' @param h a brmshypothesis
#'
#' @return a long tibble of draws of posterior answers to hypothesis
simple_effects_samples <- function(x, h) {
  # Calculate hypotheses at average level
  average_h <- hypothesis(
    x, h
  )
  # Give hypotheses appropriate names
  average <- average_h$samples
  names(average) <- interaction(
    "Average", average_h$hypothesis$Hypothesis,
    sep = "+"
  )
  # Pivot to long format, note use of dtplyr
  average <- average %>%
    lazy_dt() %>%
    pivot_longer(everything()) %>%
    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
    as_tibble()

  # Regions as above
  region_h <- hypothesis(
    x, h,
    scope = "coef", group = "region"
  )
  region <- region_h$samples
  names(region) <- interaction(
    region_h$hypothesis$Group,
    region_h$hypothesis$Hypothesis,
    sep = "+"
  )
  region <- region %>%
    lazy_dt() %>%
    pivot_longer(everything()) %>%
    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
    as_tibble()

  bind_rows(average, region)
}

#' Posterior summaries of country- region- and average-level effects for the demographic groups
#'
#' @param x brmsfit model 2
#' @param h character vector of hypotheses
#'
#' @return
simple_effects_summary <- function(x, h) {

  # Calculate hypotheses at average level
  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
  average$region <- "Average"

  # Regions as above
  region <- hypothesis(
    x, h,
    scope = "coef", group = "region"
  )$hypothesis %>%
    as_tibble()
  region <- rename(region, region = Group)

  # Country hypotheses
  country <- hypothesis(
    x, h,
    scope = "ranef", group = "country"
  )
  country <- country$hypothesis %>% as_tibble()
  country <- rename(country, country = Group)

  # Add region coefs
  country <- left_join(country, distinct(x$data, region, country))
  region_coef <- region %>%
    select(region, Hypothesis, r_region = Estimate)
  country <- country %>%
    left_join(region_coef) %>%
    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
    select(-r_region)

  bind_rows(average, region, country)
}

sexage_draws <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    samples = map2(
      fit1, h,
      ~ simple_effects_samples(.x, .y)
    )
  ) %>%
  select(outcome, samples) %>%
  unnest(samples)
sexage_sums <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    sums = map2(
      fit1, h,
      ~ simple_effects_summary(.x, .y)
    )
  ) %>%
  select(outcome, sums) %>%
  unnest(sums)

sexage_draws <- sexage_draws %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(is_average = region == "Average") %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(
    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
  )

sexage_sums <- sexage_sums %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(region = fct_relevel(region, "Average"))

# Plot averages and regions
sexage_draws %>%
  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
  scale_color_brewer(
    "Group",
    palette = "Dark2",
    aesthetics = c("fill", "color")
  ) +
  scale_alpha_manual(values = c(.4, .8), guide = "none") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19), guide = "none") +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(3),
    labels = function(x) {
      percent(x / 100, .01) %>%
        str_remove("\\.00") %>%
        str_remove("(?<=[0-9])0")
    },
    expand = expansion(c(-.05, -.05))
  ) +
  stat_halfeye(
    point_interval = mean_qi, normalize = "xy",
    height = 1, alpha = .5, point_fill = "white",
    .width = .95, interval_alpha = 1, interval_size = .2,
    point_alpha = 1, point_size = 1.5, stroke = .5,
    aes(
      shape = after_stat(xmin > 0 | xmax < 0)
    ),
    position = position_dodge(.8),
    key_glyph = draw_key_point
  ) +
  guides(
    color = guide_legend(
      override.aes = list(size = 2, alpha = 1),
      nrow = 2, ncol = 3, byrow = TRUE
    ),
    fill = guide_legend(
      nrow = 2, ncol = 3, byrow = TRUE
    )
  ) +
  # Add country points
  # geom_point(
  #   data = sexage_sums %>%
  #     drop_na(country) %>%
  #     mutate(is_average = TRUE),
  #   aes(
  #     x = Estimate,
  #     shape = CI.Lower > 0 | CI.Upper < 0,
  #     group = interaction(country, Hypothesis),
  #     ),
  #   position = position_dodgev(.7),
  #   size = .5, alpha = .3
  # ) +
  facet_wrap(
    "outcome",
    scales = "free_x", nrow = 1,
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "bottom"
  )
```

### Associations

```{r model2-demographics}

h_gwp <- c(
  `15 to 19` =
    "i1_cw + age1:i1_cw * 1 = 0",
  `20 to 24` =
    "i1_cw + age1:i1_cw * -1 = 0",
  `Female` =
    "i1_cw + sex1:i1_cw * 1 = 0",
  `Male` =
    "i1_cw + sex1:i1_cw * -1 = 0"
)
h_gbd <- c(
  `10 to 14` =
    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
  `15 to 19` =
    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
  `20 to 24` =
    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
  `Female` =
    "i1_cw + sex1:i1_cw * 1 = 0",
  `Male` =
    "i1_cw + sex1:i1_cw * -1 = 0"
)

sexage_draws <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    samples = map2(
      fit2, h,
      ~ simple_effects_samples(.x, .y)
    )
  ) %>%
  select(outcome, samples) %>%
  unnest(samples)
sexage_sums <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    sums = map2(
      fit2, h,
      ~ simple_effects_summary(.x, .y)
    )
  ) %>%
  select(outcome, sums) %>%
  unnest(sums)

sexage_draws <- sexage_draws %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(is_average = region == "Average") %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(
    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
  )

sexage_sums <- sexage_sums %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(region = fct_relevel(region, "Average"))

# Plot averages and regions
sexage_draws %>%
  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
  scale_color_brewer(
    "Group",
    palette = "Dark2",
    aesthetics = c("fill", "color")
  ) +
  scale_alpha_manual(values = c(.4, .8), guide = "none") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19), guide = "none") +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome",
    breaks = pretty_breaks(3),
    labels = function(x) {
      percent(x / 100, .01) %>%
        str_remove("\\.00") %>%
        str_remove("(?<=[0-9])0")
    },
    expand = expansion(c(-.05, -.05))
  ) +
  stat_halfeye(
    point_interval = mean_qi, normalize = "xy",
    height = 1, alpha = .5, point_fill = "white",
    .width = .95, interval_alpha = 1, interval_size = .2,
    point_alpha = 1, point_size = 1.5, stroke = .5,
    aes(
      shape = after_stat(xmin > 0 | xmax < 0)
    ),
    position = position_dodge(.8),
    key_glyph = draw_key_point
  ) +
  guides(
    color = guide_legend(
      override.aes = list(size = 2, alpha = 1),
      nrow = 2, ncol = 3, byrow = TRUE
    ),
    fill = guide_legend(
      nrow = 2, ncol = 3, byrow = TRUE
    )
  ) +
  # Add country points
  # geom_point(
  #   data = sexage_sums %>%
  #     drop_na(country) %>%
  #     mutate(is_average = TRUE),
  #   aes(
  #     x = Estimate,
  #     shape = CI.Lower > 0 | CI.Upper < 0,
  #     group = interaction(country, Hypothesis),
  #     ),
  #   position = position_dodgev(.7),
  #   size = .5, alpha = .3
  # ) +
  facet_wrap(
    "outcome",
    scales = "free_x", nrow = 1,
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "bottom"
  )
```

## Other internet metrics

Fixed and mobile broadband subscription analyses

```{r fixed-mobile-formulas}
bf_2_f <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)

bf_2_m <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)
```

### 2021-12-17 _common.R

@@ -1,30 +1,0 @@
-# Set global options here
-
-# Global knitr options
-library(ragg)
-knitr::opts_chunk$set(
-  echo = TRUE,
-  warning = FALSE,
-  cache = TRUE,
-  error = FALSE,
-  message = FALSE,
-  fig.align = "center",
-  fig.width = 8,
-  dev = "ragg_png",
-  fig.retina = 2
-)
-
-# Plotting theme
-library(ggplot2)
-# Use better font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)

### 2021-12-17 index.qmd
more edits

@@
 author: "Matti Vuorre"
-date: "`r Sys.time()`"
 execute:
-  eval: true
-  error: true
+  enabled: true
   cache: true
@@
     font-size: 1.0em
-    linestretch: 1.4
     code-fold: true
-    code-summary: "Show code"
-    code-tools: true
-    code-link: true
 toc: true
 toc-depth: 4
-toc-title: Contents
-number-sections: false
 crossref:
@@
 
-# Format tables
+#' Custom kableExtra formatting
+#'
+#' @param a table from kbl()
+#'
+#' @return a table
 kable_custom <- function(x) {
@@
 ```{r fit-model-1}
-
 fits <- dat %>%
@@
 #| label: tbl-m1-data
+
+#' Model summary
+#'
+#' @param x a brmsfit
+#'
+#' @return A tibble with information on data in the model
 msum <- function(x) {
@@
 }
+
 fits %>%
@@
 ```{r ppcheck-density}
-
 #| column: page
@@
 #| label: fig-ppcheck-1
+
 ppcheck_1 <- fits %>%
@@
   )
+rm(ppcheck_1)
 ```
@@
 ```{r calculate-simple-effects}
-
 #' Posterior draws at average and region levels
@@
 ```{r shrinkage}
-
 #| column: screen-inset
@@
 ```{r model21-compare}
-
 #| results: hold
@@
 ```{r model2-calculate-coefficients}
-
 p_draws <- fits %>%
@@
 ```{r model2-fitted-values}
-
 #| column: screen-inset
@@
 ```{r}
-#| fig.width: 6
-#| fig.height: 4
+#| column: page
+#| fig.width: 8
+#| fig.height: 6
 #| fig-cap: "Between-country associations"
@@
         newdata = newx, 
-        re_formula = NULL
+        re_formula = NA
         )
@@
   geom_point(
-    shape = 1, size = 1, alpha = .75,
-    aes(col = region)
+    shape = 1, size = 1, alpha = .75
   ) +
@@
 ```{r model1-demographics}
-
+#| column: screen-inset
+#| fig-width: 14
+#| fig-height: 9
+#| fig-cap: "Forest plot of linear trends in outcomes by demographic group"
+#| label: fig-forest-trends-demo
 h_gwp <- c(
@@
 ```{r model2-demographics}
-
+#| column: screen-inset
+#| fig-width: 14
+#| fig-height: 9
+#| fig-cap: "Forest plot of associations by demographic group"
+#| label: fig-forest-association-demo
 h_gwp <- c(

### 2021-12-17 index.qmd
Colors

@@
   geom_point(
-    shape = 1, size = 1, alpha = .75
+    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
   ) +
@@
     aes(ymin = Q2.5, ymax = Q97.5),
-    fill = "dodgerblue2",
-    alpha = .2
+    alpha = .2, fill = "dodgerblue1"
     ) +

### 2022-01-10 00-clean.qmd
Split into sections

--- 2021-12-17 index.qmd
@@
----
-title: "Adolescent well-being in the digital age"
-author: "Matti Vuorre"
-date: "`r Sys.time()`"
-execute:
-  eval: true
-  error: true
-  cache: true
-  warning: false
-  message: false
-format: 
-  html:
-    monofont: Fira Code
-    font-size: 1.0em
-    linestretch: 1.4
-    code-fold: true
-    code-summary: "Show code"
-    code-tools: true
-    code-link: true
-toc: true
-toc-depth: 4
-toc-title: Contents
-number-sections: false
-crossref:
-  fig-prefix: Figure
-  tbl-prefix: Table
----
-
-```{r document-options, include = FALSE, cache = FALSE}
-# knitr options
-knitr::opts_chunk$set(
-  fig.align = "center",
-  cache.lazy = FALSE # Fix large knitr cache
-)
-```
-
-## Preface
-
-Welcome!
-This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation).
-It contains all the analyses reported in the manuscript along with supplemental analyses.
-The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).
-
-::: {.callout-note collapse="true"}
-### Reproducibility
-
-The analyses were conducted in R, and can be reproduced locally:
-
-1.  Clone the github repo
-
--   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
--   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
-
-2.  Prepare the R environment
-
--   Terminal: `Rscript -e "renv::restore()`
--   RStudio: Click renv -> Restore Library in the Packages panel
-
-3.  Render `index.qmd` to `index.html`
-
--   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
--   Terminal: `quarto render index.qmd`
--   RStudio: Open `index.qmd` and click Render
-
-The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.
-
-If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
-:::
-
-## Data preparation
-
-Our analyses draw on three sources of data.
-The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
-The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
-And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
-
-In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:
-
-```{r setup, cache = FALSE}
-
+# Data preparation {.unnumbered}
+
+```{r setup}
+#| cache: false
 # Packages
 library(readxl)
-library(knitr)
-library(ragg)
 library(imputeTS)
@@
 library(countrycode)
-library(ggtext)
-library(dtplyr)
 library(lubridate)
-library(kableExtra)
 library(gtsummary)
-library(ggstance)
-library(mgcv)
-library(brms)
-library(cmdstanr)
-library(ellipse)
-library(ggh4x)
-library(tidybayes)
-library(ggdist)
-library(posterior)
-library(parameters)
-library(emmeans)
-library(broom)
 library(kableExtra)
@@
 
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
-nchains <- 4
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = nchains,
-  cores = nchains,
-  threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1000,
-  refresh = 50,
-  adapt_delta = .90,
-  max_treedepth = 10
-)
-
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-# Format tables
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}
-
 # Create directory for intermediate files
-dir.create("models", FALSE)
-```
-
-### Gallup World Poll
-
-We first prepare the Gallup data.
+dir.create("data", FALSE)
+```
+
+In this first section, we load the raw data sets and prepare them for analyses.
+
+## Gallup World Poll
+
+We first prepare the Gallup data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
+
 Note that this data set is not publicly available, and therefore not included in our repository.
-We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.
+We provide a synthetic mock dataset for researchers who would like to reproduce our analyses but do not have access to the GWP dataset.
 
@@
 #| label: tbl-gwp-countries
-#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
+#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing and therefore the original name is retained."
 
@@
   filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GWP harmonised country names") %>%
+  kbl(caption = "GWP country names") %>%
   kable_custom()
@@
 
-### Global Burden of Disease
+We then load the synthetic GWP dataset if the real data was not found.
+This is just a list of the countries, years and demographics in the actual data, with gaussian noise for the outcomes' mean and SE values.
+
+```{r}
+# Create if doesn't exist
+gwp_mock_path <- "data-raw/gwp-MOCK.rds"
+if (!file.exists(gwp_mock_path)) {
+  distinct(gwp, outcome, country, year, sex, age) %>% 
+    mutate(
+      se = rnorm(
+        nrow(.), 
+        mean(gwp$se, na.rm = TRUE), 
+        sd(gwp$se, na.rm = TRUE)
+      ),
+      val = rnorm(
+        nrow(.), 
+        mean(gwp$val, na.rm = TRUE), 
+        sd(gwp$val, na.rm = TRUE)
+      )
+    ) %>% 
+    write_rds(gwp_mock_path, compress = "xz")
+}
+# Load if actual data doesn't exist
+if (!dir.exists("data-raw/Gallup")) {
+  cat("Using synthetic GWP data.")
+  gwp <- read_rds(gwp_mock_path)
+} else {
+  cat("Using actual GWP data.")
+}
+```
+
+## Global Burden of Disease
+
+The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
 
 We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
-We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R.
-They are inside downloaded `.zip` files, of which there may be more than one.
+We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/).
+They are inside downloaded `.zip` files, of which there may be more than one (depending on the download size).
+Here, we load those tables to R.
 
@@
   filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GBD harmonised country names") %>%
+  kbl(caption = "GBD country names") %>%
   kable_custom()
@@
 
-### International Telecommunication Union
+## International Telecommunication Union
 
 After processing the outcome tables above, we move on to the internet adoption metrics from the ITU.
-We downloaded these data files from the ITU website.
-New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
+The International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
+
+We downloaded the data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
 
@@
 #| label: tbl-itu-0
-#| tbl-cap: "ITU countries"
+#| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"
 #| layout-ncol: 1
@@
   filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "ITU harmonised country names") %>%
+  kbl(caption = "ITU country names") %>%
   kable_custom()
@@
 
-### GLOBE regions
+## GLOBE regions
 
@@
 
-### ITU summary table
+## ITU summary table
 
 ```{r itu-summary-table}
-#| column: page
+#| column: page-right
 #| tbl-cap: "Mean internet user percentages across regions and time."
@@
 
-## RQ1: Time courses
-
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
-To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.
-
-### Modelling
-
-We first prepare the variables for modelling:
-
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
--   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
-
-```{r model1-prepare-data}
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center and scale year
-dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in mv models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
-  ungroup()
-
-# Ensure that factors are contrast coded
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
-
-# Arrange on outcome
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-dat <- dat %>%
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(dat, outcome, region, country, year)
-
-dat %>%
-  group_by(outcome) %>%
-  summarise(
-    min = min(val, na.rm = TRUE),
-    max = max(val, na.rm = TRUE),
-    internet_min = min(internet, na.rm = TRUE),
-    internet_max = max(internet, na.rm = TRUE)
-  ) %>%
-  kable(digits = 7) %>% 
-  kable_custom()
-```
-
-#### Specification
-
-We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b).
-Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g.
-Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries.
-We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)
-
-We fit the model separately for each outcome.
-Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret).
-We therefore estimate six separate bivariate models
-
-In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.
-All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes.
-This latter specification is important to allow answering RQ1b.
-
-The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate.
-For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age).
-The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data.
-Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.
-
-We write the model as
-
-$$
-\begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
-\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
-\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
-x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
-\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
-\left[\begin{array}{c}
-\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
-\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
-\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
-\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
-\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
-\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
-\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}
-$$
-
-Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.
-
-We then define the model formulas in brms' formula syntax.
-First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
-To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model.
-The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).
-
-```{r model1-itu-bf}
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~
-  year +
-    (year |c| country) +
-    (year |r| region),
-  family = Beta()
-)
-```
-
-Here, we specify the outcome model.
-Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
-Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
-In addition, it leads to the residual variance to be estimated.
-
-```{r model1-val-bf}
-# Meta-regression model of outcomes
-bf_1 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
-  family = gaussian()
-)
-```
-
-Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged.
-We therefore effectively removed the SEs from self-harm by setting them to zero
-
-```{r model1-selfharm-se}
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
-
-#### Fitting
-
-We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.
-
-```{r fit-model-1}
-
-fits <- dat %>%
-  # Could nest but need this to include group key in nested tibble
-  group_by(outcome) %>%
-  summarise(data = list(cur_data_all()))
-
-fits <- fits %>%
-  mutate(
-    fit1 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE),
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-1-internet")
-      )
-    )
-  )
-```
-
-#### Summary
-
-Here is a summary of the data modelled for each outcome
-
-```{r model-1-data-summary}
-#| column: body-outset
-#| tbl-cap: "Summaries of data included in Model 1"
-#| label: tbl-m1-data
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
-fits %>%
-  mutate(summary = map(fit1, msum)) %>%
-  select(outcome, summary) %>%
-  unnest(summary) %>%
-  kbl(caption = "Model 1 data summary") %>%
-  kable_custom() %>% 
-  row_spec(0, bold = TRUE)
-```
-
-#### Model checking
-
-Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section
-
-##### MCMC diagnostics
-
-First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.
-
-We can see that the models have converged nicely, apart from the self-harm outcome.
-
-```{r model-1-diagnostics}
-#| results: hold
-#| label: tab-model1-diagnostic
-#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
-#| column: body-outset
-
-diagnostic_table <- function(fit, rx, cp) {
-  diag_1 <- fits %>%
-    select(fit = {{ fit }}, outcome) %>% 
-    mutate(
-      out =
-        map(
-          fit,
-          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
-            summarise_draws(samples = length, default_convergence_measures())
-        )
-    ) %>%
-    select(outcome, out) %>%
-    unnest(out)
-  diag_1 %>%
-    kbl(
-      caption = cp,
-      digits = c(0, 0, 0, 2, 0, 0)
-    ) %>%
-    column_spec(
-      4,
-      color = "white",
-      background = spec_color(
-        log(diag_1$rhat),
-        direction = 1,
-        option = "C",
-        end = .6
-      )
-    ) %>%
-    column_spec(
-      c(5, 6),
-      color = "white",
-      background = spec_color(
-        log(diag_1$ess_tail / diag_1$samples),
-        direction = 1,
-        option = "C",
-        end = 0,
-        begin = .6
-      )
-    ) %>%
-    kable_custom()
-}
-diagnostic_table(
-  fit1,
-  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
-  cp = "Model 1 MCMC diagnostics."
-) %>% 
-  scroll_box(height = "300px")
-```
-
-##### Posterior predictive check
-
-We then take a coarse look at how well the models reproduce the input data.
-
-```{r ppcheck-density}
-
-#| column: page
-#| fig-cap: "Graphical posterior predictive check by region (Model 1).
-Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g.
-Anglo Depression)."
-#| label: fig-ppcheck-1
-ppcheck_1 <- fits %>%
-  group_by(outcome) %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ pp_check(
-        .x,
-        ndraws = 10,
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val",
-        newdata = .x$data
-      )[[1]]
-    )
-  ) %>%
-  ungroup() %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-ppcheck_1 %>%
-  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
-  scale_color_brewer(palette = "Set1") +
-  scale_alpha_manual(values = c(.2, 1)) +
-  stat_density(
-    geom = "line",
-    size = .75,
-    position = position_identity()
-  ) +
-  labs(x = "Value", y = "Density") +
-  facet_grid2(
-    outcome ~ group,
-    scales = "free", independent = "x",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title = element_blank(),
-    axis.text = element_blank(),
-    axis.ticks = element_blank()
-  )
-```
-
-### Results
-
-#### RQ1a: Temporal trends
-
-Before presenting the time trends, we must calculate the required quantities from the posterior distribution.
-Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.
-
-```{r calculate-simple-effects}
-
-#' Posterior draws at average and region levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = "region")
-}
-
-#' Posterior summaries at country- region- and average levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
-    select(-r_value)
-
-  bind_rows(
-    psum_region,
-    psum_country
-  ) %>%
-    mutate(region = fct_relevel(region, "Average"))
-}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit1, pdraws)) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums <- fits %>%
-  mutate(psums = map(fit1, psums)) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums_internet <- fits %>%
-  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-```
-
-We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions.
-Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).
-
-```{r forest-trends}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes"
-#| label: fig-forest-trends
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-```
-
-@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction.
-This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade.
-The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.
-
-Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data.
-This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes.
-Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.
-
-We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region.
-However, the average change again is not credibly different from zero.
-Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety.
-Depression and self-harm, on the other hand, had decreased across the board.
-
-In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.
-
-Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.
-
-```{r fitted-trend-country}
-
-#' Get (grand mean) fitted values for countries
-#'
-#' @param x a brmsfit model 1
-#'
-#' @return a data frame of fitted values
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
-    summarise(val = mean(val, na.rm = TRUE)) %>%
-    ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
-  newy <- bind_cols(
-    newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit1, fitted_country)) %>%
-  select(outcome, fc)
-
-#' Draw a panel plot of countries' fitted values and data
-#'
-#' @param x fitted country level data from fitted_country()
-#' @param y outcome
-#'
-#' @return a ggplot for that outcome
-plot_country <- function(x, y) {
-  coefs <- p_sums %>%
-    drop_na(country) %>%
-    filter(outcome == y) %>%
-    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
-    mutate(country = fct_reorder(country, coef))
-  x %>%
-    left_join(coefs) %>%
-    mutate(country = fct_reorder(country, coef)) %>%
-    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
-    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
-    scale_y_continuous(
-      str_replace(y, "_", " "),
-      breaks = pretty_breaks(),
-      expand = expansion(.15),
-      labels = function(x) {
-        percent(x / 100, .01) %>%
-          str_remove("\\.00")
-      }
-    ) +
-    # Add parameters in text
-    geom_richtext(
-      data = coefs %>%
-        mutate(across(where(is.numeric), ~ number(., .01))),
-      aes(
-        x = make_date(2000), y = Inf,
-        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
-      ),
-      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
-      family = Font,
-      fill = alpha("white", .3), label.color = NA,
-      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
-    ) +
-    geom_point(aes(y = val), shape = 1, alpha = .5) +
-    geom_ribbon(
-      aes(ymin = Q2.5, ymax = Q97.5),
-      alpha = .3, col = NA, fill = "dodgerblue1"
-    ) +
-    geom_line(
-      size = 0.5, col = "dodgerblue1"
-    ) +
-    facet_wrap(
-      "country"
-    ) +
-    theme(panel.spacing = unit(2, "pt"))
-}
-
-# Create the plot for each outcome
-f_country <- f_country %>%
-  mutate(
-    plot = map2(
-      fc, outcome,
-      ~ plot_country(.x, .y)
-    )
-  )
-```
-
-::: {.panel-tabset .column-screen-inset-shaded}
-##### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-##### Life satisfaction
-
-```{r trends-ls}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
-#| label: fig-trends-ls
-f_country$plot[[1]]
-```
-
-##### Negative experiences
-
-```{r trends-ne}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Negative experiences trends, ordered by association magnitude"
-#| label: fig-trends-ne
-f_country$plot[[2]]
-```
-
-##### Positive experiences
-
-```{r trends-pe}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Positive experiences trends, ordered by association magnitude"
-#| label: fig-trends-pe
-f_country$plot[[3]]
-```
-
-##### Anxiety
-
-```{r trends-anx}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Anxiety trends, ordered by association magnitude"
-#| label: fig-trends-anx
-f_country$plot[[4]]
-```
-
-##### Depression
-
-```{r trends-dep}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Depression trends, ordered by association magnitude"
-#| label: fig-trends-dep
-f_country$plot[[5]]
-```
-
-##### Self-harm
-
-```{r trends-sel}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Self-harm trends, ordered by association magnitude"
-#| label: fig-trends-sel
-f_country$plot[[6]]
-```
-:::
-
-#### RQ1b: Correlations
-
-We then turned to research question 1b: To what extent were changes in well-being and internet adoption correlated across countries.
-
-To investigate we examined the correlations between $\gamma^y_1$ and $\gamma^x_1$ ($\sigma_{\gamma^y_1,\gamma^x_1}$ in $\Sigma^{\text{c}}$).
-A positive correlation would indicate that countries with greater increases in internet adoption between 2000 and 2020 would tend to have greater increases in $y$ (e.g.
-Life satisfaction).
-
-To answer, we display $\sigma_{\gamma^y_1,\gamma^x_1}$ from each outcome's model in the figure below.
-The figures are scatterplots of country-level trend coefficients, where each point's x-y coordinate indicate their trend magnitudes.
-The overlaid ellipses are the model's 95% predictive limits for $\gamma^y_1$ and $\gamma^x_1$.
-
-```{r scatterplot-time-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of country-level internet and outcome trends."
-#| label: fig-trend-scatterplot
-
-# Correlation parameters
-cor_pars <- fits %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        variable = "cor_country__internet_year__val_year"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-# Ellipses
-ellipses <- fits %>%
-  mutate(
-    ellipse = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        c(
-          "b_val_year",
-          "b_internet_year",
-          "sd_country__val_year",
-          "sd_country__internet_year",
-          "cor_country__internet_year__val_year"
-        )
-      ) %>%
-        slice_sample(n = 100) %>%
-        rename(
-          cor = cor_country__internet_year__val_year,
-          sd_outcome = sd_country__val_year,
-          sd_i = sd_country__internet_year,
-          b_outcome = b_val_year,
-          b_i = b_internet_year
-        ) %>%
-        mutate(
-          e = pmap(
-            list(cor, sd_outcome, sd_i, b_outcome, b_i),
-            function(cor, sd_a, sd_i, b_a, b_i) {
-              ellipse(
-                cor,
-                scale = c(sd_i, sd_outcome),
-                centre = c(b_i, b_outcome),
-                level = .95
-              ) %>%
-                as_tibble()
-            }
-          )
-        ) %>%
-        unnest(e)
-    )
-  )
-ellipses <- ellipses %>%
-  select(outcome, ellipse) %>%
-  unnest(ellipse)
-
-# Wide tibble of parameters
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_path(
-    data = ellipses,
-    aes(x = x, y = y, group = .draw),
-    alpha = .2, size = .1, col = "dodgerblue2"
-  ) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_text(
-    data = cor_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-#### Other results from Model 1
-
-##### Shrinkage
-
-It's important to note that at the level of countries and regions, the model parameters refer to country^\*^ and region^\*^, that is as they are in the sample of other countries and regions.
-This modelling strategy is important because it allows describing the parameters at each level while adjusting the values toward the group means (preventing "false alarms").
-However it is then important to examine those values against their "fixed effect" counterparts, which we do here.
-
-```{r shrinkage}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of multilevel and independent model coefficients"
-#| label: fig-trend-shrinkage
-
-lm_coefs <- fits %>%
-  mutate(
-    data = map(fit1, ~ as_tibble(.x$data))
-  ) %>%
-  mutate(
-    fit_val = map(
-      data,
-      ~ tidy(
-        lm(val ~ 0 + country + year:country, data = .x)
-      )
-    ),
-    fit_internet = map(
-      data,
-      ~ tidy(
-        gam(
-          internet ~ 0 + country + year:country,
-          family = betar, data = .x %>%
-            filter(itu)
-        ),
-        parametric = TRUE
-      )
-    )
-  )
-lm_coefs <- lm_coefs %>%
-  select(outcome, fit_val, fit_internet) %>%
-  pivot_longer(c(fit_val, fit_internet)) %>%
-  mutate(name = str_remove(name, "fit_")) %>%
-  unnest(value) %>%
-  select(outcome, name, term, estimate, std.error) %>%
-  filter(str_detect(term, ":")) %>%
-  mutate(term = str_remove(term, "country")) %>%
-  mutate(term = str_remove(term, ":year")) %>%
-  pivot_wider(names_from = name, values_from = c(estimate, std.error)) %>%
-  rename(country = term)
-
-# Plot
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  left_join(lm_coefs) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate, col = region)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_segment(
-    aes(
-      x = estimate_internet, xend = Internet_Estimate,
-      y = estimate_val, yend = Outcome_Estimate
-    ),
-    arrow = arrow(type = "closed", length = unit(3, "pt")),
-    size = .25, show.legend = FALSE
-  ) +
-  geom_point(size = 1.1, alpha = .4) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  guides(
-    color = guide_legend(override.aes = list(size = 2, alpha = 1))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "bottom"
-  )
-```
-
-## RQ2: Associations
-
-We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption?
-To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes.
-Before modelling, we calculated these quantities as shown in this code block.
-
-```{r model2-data-prepare}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(outcome, region, country, year) %>%
-  group_by(outcome, region, country, sex, age) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-dat <- dat %>%
-  group_by(outcome, country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  group_by(outcome) %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-```
-
-### Specification and fitting
-
-Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions
-
-$$\begin{align*}
-y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\
-
-\mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
-\gamma_{0\text{country}[i]} + \\ &(\beta_{1} + \delta_{1\text{region}[i]} + \gamma_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta_{2} + \delta_{2\text{region}[i]} + \gamma_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta_{3} + \delta_{3\text{region}[i]} + \gamma_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta_{4} + \delta_{4\text{region}[i]} + \gamma_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta_{5} + \delta_{5\text{region}[i]} + \gamma_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i +
-\\ &(\beta_{6} + \delta_{6\text{region}[i]} + \gamma_{6\text{country}[i]})\text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\
-
-\left[\begin{array}{c}
-\delta_{0\text{region}} \\ \delta_{1\text{region}} \\ 
-\delta_{2\text{region}} \\ \delta_{3\text{region}} \\ 
-\delta_{4\text{region}} \\ \delta_{5\text{region}} \\ 
-\delta_{6\text{region}} \\ \delta_{7\text{region}} \\ 
-\delta_{8\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\ 
-\gamma_{4\text{country}} \\ \gamma_{5\text{country}} \\ 
-\gamma_{6\text{country}} \\ \gamma_{7\text{country}} \\ 
-\gamma_{8\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}$$
-
-```{r fit-model-2}
-
-# Model formula is only a small update to Model 1
-bf_2 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-# As above with model 1
-fits <- fits %>%
-  mutate(
-    fit2 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-internet")
-      )
-    )
-  )
-```
-
-### Results
-
-First, we compared the R2 values between Models 1 and 2.
-This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2).
-However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.
-
-```{r model21-compare}
-
-#| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
-#| label: tbl-m12-r2
-fits %>%
-  select(outcome, fit1, fit2) %>% 
-  pivot_longer(c(fit1, fit2)) %>% 
-  mutate(
-    r2 = map(
-      value,
-      ~ bayes_R2(., resp = "val") %>%
-        as.data.frame() %>%
-        mutate(across(everything(), ~ percent(., .1))) %>%
-        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
-    )
-  ) %>%
-  select(-value) %>%
-  unnest(r2) %>% 
-  pivot_wider(
-    names_from = name,
-    values_from = result,
-    names_prefix = "Model "
-  ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  kbl(caption = "Model 1 and 2 R-squared values") %>%
-  kable_custom()
-```
-
-Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.
-
-```{r model2-calculate-coefficients}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws)
-
-p_sums <- fits %>%
-  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums)
-
-p_draws <- p_draws %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-p_sums <- p_sums %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-```
-
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
-
-```{r forest-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x"
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
-x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
-```
-
-This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
-However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
-Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region.
-However, none of the average associations were credibly different from zero.
-The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.
-
-To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
-
-```{r model2-fitted-values}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Counterfactual plot of internet associations"
-#| label: fig-fitted-internet
-
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country) %>%
-    mutate(
-      xmin = min(i1_cw, na.rm = TRUE),
-      xmax = max(i1_cw, na.rm = TRUE)
-    ) %>%
-    filter(i1_cw %in% c(xmin, xmax)) %>%
-    ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
-  newy
-}
-
-fitted_region <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region) %>%
-    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
-    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit2, fitted_country)) %>%
-  select(outcome, fc) %>%
-  unnest(fc)
-
-f_region <- fits %>%
-  mutate(fr = map(fit2, fitted_region)) %>%
-  select(outcome, fr) %>%
-  unnest(fr)
-
-f_country %>%
-  ggplot(aes(i1_cw, Estimate)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimate",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = f_region,
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = f_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country),
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    panel.spacing = unit(2, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-### Other results from Model 2
-
-We then focused on the between-country association between internet adoption and well-being.
-Recall that the model does not adjust for between-country differences so these associations are likely to reflect many other factors covarying with internet adoption (e.g.
-wealth and development factors).
+## Write data tables
+
+We have organised our code into separate files, and so save the processed data here for use in the other analysis scripts.
 
 ```{r}
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Between-country associations"
-#| label: fig-cb1
-
-fitted_cb1 <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region, country) %>%
-    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
-    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
-    ungroup()
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = NULL
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-tmp <- fits %>% 
-  mutate(out = map(fit2, fitted_cb1)) %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-cb1_pars <- fits %>%
-  mutate(
-    out = map(
-      fit2,
-      ~ as_draws_df(
-        .x,
-        variable = "b_i1_cb"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-tmp %>% 
-  ggplot(aes(i1_cb, val)) +
-  scale_x_continuous(
-    "Between-country centered internet adoption",
-    labels = ~percent(.)
-  ) +
-  scale_y_continuous(
-    "Value",
-    labels = ~percent(./100)
-  ) +
-  geom_point(
-    shape = 1, size = 1, alpha = .75,
-    aes(col = region)
-  ) +
-  geom_ribbon(
-    aes(ymin = Q2.5, ymax = Q97.5),
-    fill = "dodgerblue2",
-    alpha = .2
-    ) +
-  geom_line(aes(y = Estimate), col = "dodgerblue4") +
-  geom_text(
-    data = cb1_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    axis.title.y = element_blank()
-  )
-```
-
-## RQ3: Demographics
-
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
-
-### Trends
-
-```{r model1-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-#' Calculate posterior draws for simple effects (by sex and age) for regions and average
-#'
-#' @param x brmsfit model 2
-#' @param h a brmshypothesis
-#'
-#' @return a long tibble of draws of posterior answers to hypothesis
-simple_effects_samples <- function(x, h) {
-  # Calculate hypotheses at average level
-  average_h <- hypothesis(
-    x, h
-  )
-  # Give hypotheses appropriate names
-  average <- average_h$samples
-  names(average) <- interaction(
-    "Average", average_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  # Pivot to long format, note use of dtplyr
-  average <- average %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  # Regions as above
-  region_h <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )
-  region <- region_h$samples
-  names(region) <- interaction(
-    region_h$hypothesis$Group,
-    region_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  region <- region %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  bind_rows(average, region)
-}
-
-#' Posterior summaries of country- region- and average-level effects for the demographic groups
-#'
-#' @param x brmsfit model 2
-#' @param h character vector of hypotheses
-#'
-#' @return
-simple_effects_summary <- function(x, h) {
-
-  # Calculate hypotheses at average level
-  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
-  average$region <- "Average"
-
-  # Regions as above
-  region <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )$hypothesis %>%
-    as_tibble()
-  region <- rename(region, region = Group)
-
-  # Country hypotheses
-  country <- hypothesis(
-    x, h,
-    scope = "ranef", group = "country"
-  )
-  country <- country$hypothesis %>% as_tibble()
-  country <- rename(country, country = Group)
-
-  # Add region coefs
-  country <- left_join(country, distinct(x$data, region, country))
-  region_coef <- region %>%
-    select(region, Hypothesis, r_region = Estimate)
-  country <- country %>%
-    left_join(region_coef) %>%
-    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
-    select(-r_region)
-
-  bind_rows(average, region, country)
-}
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit1, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-### Associations
-
-```{r model2-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-## Other internet metrics
-
-Fixed and mobile broadband subscription analyses
-
-```{r fixed-mobile-formulas}
-bf_2_f <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-
-bf_2_m <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-```
+write_rds(itu, "data/itu.rds")
+write_rds(gwp, "data/gwp.rds")
+write_rds(gbd, "data/gbd.rds")
+```

### 2022-01-10 00-models.qmd
Split into sections

--- 2021-12-17 index.qmd
@@
----
-title: "Adolescent well-being in the digital age"
-author: "Matti Vuorre"
-execute:
-  enabled: true
-  cache: true
-  warning: false
-  message: false
-format: 
-  html:
-    monofont: Fira Code
-    font-size: 1.0em
-    code-fold: true
-toc: true
-toc-depth: 4
-crossref:
-  fig-prefix: Figure
-  tbl-prefix: Table
----
-
-```{r document-options, include = FALSE, cache = FALSE}
-# knitr options
-knitr::opts_chunk$set(
-  fig.align = "center",
-  cache.lazy = FALSE # Fix large knitr cache
-)
-```
-
-## Preface
-
-Welcome!
-This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation).
-It contains all the analyses reported in the manuscript along with supplemental analyses.
-The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).
-
-::: {.callout-note collapse="true"}
-### Reproducibility
-
-The analyses were conducted in R, and can be reproduced locally:
-
-1.  Clone the github repo
-
--   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
--   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
-
-2.  Prepare the R environment
-
--   Terminal: `Rscript -e "renv::restore()`
--   RStudio: Click renv -> Restore Library in the Packages panel
-
-3.  Render `index.qmd` to `index.html`
-
--   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
--   Terminal: `quarto render index.qmd`
--   RStudio: Open `index.qmd` and click Render
-
-The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.
-
-If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
-:::
-
-## Data preparation
-
-Our analyses draw on three sources of data.
-The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
-The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
-And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
-
-In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:
-
-```{r setup, cache = FALSE}
-
+# Model fitting {.unnumbered}
+
+```{r setup}
+#| cache: false
 # Packages
-library(readxl)
-library(knitr)
-library(ragg)
-library(imputeTS)
-library(naniar)
 library(scales)
-library(janitor)
-library(haven)
-library(labelled)
-library(countrycode)
 library(ggtext)
-library(dtplyr)
 library(lubridate)
 library(kableExtra)
-library(gtsummary)
 library(ggstance)
@@
 library(broom)
-library(kableExtra)
 library(tidyverse)
@@
 
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-#' Custom kableExtra formatting
-#'
-#' @param a table from kbl()
-#'
-#' @return a table
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}
-
 # Create directory for intermediate files
 dir.create("models", FALSE)
-```
-
-### Gallup World Poll
-
-We first prepare the Gallup data.
-Note that this data set is not publicly available, and therefore not included in our repository.
-We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.
-
-```{r gallup-codebook}
-#| echo: false
-#| eval: false
-# Understand variables & values
-# Codes NOTE 1: yes 2: no!
-read_spss(
-  "data-raw/Gallup/The_Gallup_101521.sav",
-  n_max = 1,
-  col_select = c(
-    WPID, WP1219,
-    WP16,
-    WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74
-  )
-) %>%
-  generate_dictionary()
-```
-
-Here we import the relevant variables from Gallup's SPSS files and then
-
--   Clean the variable names
--   Set appropriate missing values (`NaN`, not e.g. `-99`)
--   Use appropriate coding schemes (e.g. 0: no; 1: yes)
--   Calculate scale scores (means over items)
--   Rescale outcomes to proportions (0 - 1)
--   Subset the data to 15 to 24 year olds
--   Create age-categories in line with GBD data
--   Drop one 13 year old as this data should only have people 15 and older
-
-```{r gallup-clean}
-# First liberate the data from the slow SPSS file and save to disk
-gwp_path <- "data-raw/Gallup/gwp-processed.rds"
-if (!file.exists(gwp_path)) {
-  gwp <- read_spss(
-    "data-raw/Gallup/The_Gallup_101521.sav",
-    col_select = c(
-      YEAR_CALENDAR,
-      COUNTRYNEW,
-      WPID, WP1220, WP1219,
-      WP16,
-      WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
-    )
-  )
-
-  # Get rid of SPSS attributes
-  gwp <- gwp %>%
-    zap_labels() %>%
-    zap_label() %>%
-    zap_widths() %>%
-    zap_formats()
-
-  # Save into a good format
-  write_rds(gwp, gwp_path)
-} else {
-  gwp <- read_rds(gwp_path)
-}
-
-gwp <- gwp %>%
-  clean_names() %>%
-  transmute(
-    country = countrynew,
-    year = year_calendar,
-    id = wpid,
-    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
-    age = wp1220,
-    # Don't know, refused, and missing values
-    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
-    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
-    # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
-  )
-
-# Scale scores note rescaling
-gwp <- gwp %>%
-  mutate(
-    Life_satisfaction = Life_satisfaction / 10,
-    Negative_experiences =
-      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
-    Positive_experiences =
-      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
-  ) %>%
-  select(-c(wp60:wp74))
-
-# Categorize ages
-gwp <- gwp %>%
-  mutate(
-    age = cut(
-      age,
-      breaks = seq(15, 105, by = 5),
-      include.lowest = TRUE,
-      right = FALSE,
-      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
-    ) %>% as.character()
-  )
-
-# There is one 13 year old which resulted in a NA and we drop it
-gwp <- drop_na(gwp, age)
-
-# Focus on young people
-gwp <- gwp %>%
-  filter(age %in% c("15 to 19", "20 to 24"))
-```
-
-Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex).
-Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.
-
-```{r gallup-summarise}
-gwp <- gwp %>%
-  pivot_longer(
-    c(
-      Life_satisfaction,
-      Negative_experiences,
-      Positive_experiences
-    ),
-    names_to = "outcome", values_to = "val"
-  ) %>%
-  group_by(country, year, sex, age, outcome) %>%
-  summarise(
-    se = sd(val, na.rm = TRUE) / sqrt(n()),
-    val = mean(val, na.rm = TRUE)
-  ) %>%
-  ungroup()
-```
-
-We have three data sets with information on countries.
-Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values.
-We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
-We do that here for the GWP data, and check that all countries receive a unique name.
-
-```{r gwp-harmonise-countries}
-#| results: hold
-#| label: tbl-gwp-countries
-#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gwp %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GWP harmonised country names") %>%
-  kable_custom()
-
-# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
-
-# Harmonise old names and replace only if harmonised name found
-gwp <- gwp %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  # Prevent north cyprus from becoming cyprus
-  mutate(
-    country_harmonised = ifelse(
-      country == "Northern Cyprus",
-      "Northern Cyprus",
-      country_harmonised
-    )
-  ) %>%
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### Global Burden of Disease
-
-We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
-We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R.
-They are inside downloaded `.zip` files, of which there may be more than one.
-
-```{r gbd-data-load}
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/",
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>%
-  read_csv()
-```
-
-We then clean the GBD data and
-
--   Clean the variable names
--   Remove the metric and measure variables; we focus on prevalence rate
-    -   prevalence: Total number of cases
-    -   rate: Total cases per 100,000 population
--   Convert outcome rates to proportions (0 - 1)
--   Clean cause names and rename to outcome to harmonise with GWP
--   Convert GBD estimated rate CI limits to an approximate standard error
--   Subset data to young people (10 - 24)
-
-```{r gbd-data-clean}
-# First step is to clean names
-gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
-gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 100000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>%
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>%
-  rename(country = location, outcome = cause)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
-gbd <- gbd %>%
-  mutate(se = (upper - lower) / (1.96 * 2)) %>%
-  select(-c(upper, lower))
-
-# Focus on young people
-gbd <- gbd %>%
-  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
-```
-
-Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.
-
-```{r gbd-harmonise-countries}
-#| results: hold
-#| label: tbl-gbd-countries
-#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GBD harmonised country names") %>%
-  kable_custom()
-# Harmonise old names and replace only if harmonised name found
-gbd <- gbd %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### International Telecommunication Union
-
-After processing the outcome tables above, we move on to the internet adoption metrics from the ITU.
-We downloaded these data files from the ITU website.
-New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
-
-After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1).
-Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.
-
-```{r itu-process}
-#| results: hold
-#| label: tbl-itu-0
-#| tbl-cap: "ITU countries"
-#| layout-ncol: 1
-
-# Download data sets from the ITU website if not yet downloaded
-if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
-  dir.create("data-raw/ITU")
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
-    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
-    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
-    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
-  )
-}
-
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(fixed = as.numeric(value)) %>%
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(mobile = as.numeric(value)) %>%
-  select(country = Country, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(internet = as.numeric(value)) %>%
-  select(country = Country, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
-itu <- itu %>%
-  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-
-# Harmonise countries
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "ITU harmonised country names") %>%
-  kable_custom()
-
-# Harmonise old names and replace only if harmonised name found
-itu <- itu %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Drop countries that don't exist in outcomes
-itu <- itu %>%
-  filter(
-    country %in% unique(gbd$country) | country %in% unique(gwp$country)
-  )
-
-# Drop countries that don't have any actual internet data
-itu_zeros <- itu %>%
-  group_by(country) %>%
-  summarise(s = sum(internet, na.rm = TRUE)) %>%
-  filter(s == 0)
-
-itu <- itu %>%
-  filter(!(country %in% itu_zeros$country))
-rm(itu_zeros)
-```
-
-#### Missingness
-
-We then impute missing intermediate values to the internet adoption timeseries.
-We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.
-
-```{r itu-impute}
-#| results: hold
-#| label: tbl-itu-impute
-#| tbl-cap: "Summary of ITU data imputation"
-
-# Reshape to easily impute all variables
-itu_long <- itu %>%
-  pivot_longer(c(internet, fixed, mobile))
-
-# Impute by country and variable
-itu_long <- itu_long %>%
-  group_by(country, name) %>%
-  # Find first and last year with this variable in each country
-  # so as to prevent extrapolation
-  mutate(
-    min_year = year[min(which(!is.na(value)))],
-    max_year = year[max(which(!is.na(value)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  mutate(
-    across(
-      value,
-      .fns = list(
-        i = possibly(
-          function(x) na_interpolation(x, maxgap = Inf),
-          otherwise = NaN
-        )
-      )
-    )
-  ) %>%
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    value_i = if_else(
-      between(year, unique(min_year), unique(max_year)),
-      value_i,
-      NaN
-    )
-  ) %>%
-  ungroup() %>%
-  select(-min_year, -max_year)
-
-# Summary
-itu_long %>%
-  group_by(name) %>%
-  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
-  summarise(
-    n_miss_orig = sum(is.na(value) & year >= min_year),
-    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
-    n_miss_imp = sum(is.na(value_i) & year >= min_year),
-    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
-    imputed = n_miss_orig - n_miss_imp
-  ) %>%
-  kbl(caption = "ITU data imputation summary") %>%
-  kable_custom()
-
-# We then replace the original values with the imputed ones
-itu <- itu_long %>%
-  # Pick non-missing value, from original and imputed
-  mutate(value = coalesce(value, value_i)) %>%
-  select(-value_i) %>%
-  pivot_wider()
-rm(itu_long)
-```
-
-### GLOBE regions
-
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
-
-```{r globe-regions}
-#| results: hold
-#| label: tbl-globe
-#| tbl-cap: "Countries with manually filled region"
-
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
-) %>%
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>%
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>%
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in GBD not present in region data
-no_region_gbd <- filter(
-  distinct(gbd, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-# Then see what countries in GWP are without region
-no_region_gwp <- filter(
-  distinct(gwp, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-bind_rows(no_region_gbd, no_region_gwp) %>%
-  arrange(country) %>%
-  distinct() %>%
-  write_csv("data-raw/Regions/countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/countries-without-region-filled.csv"
-)
-
-# Combine Jebb et al GLOBE regions and our manually added ones
-regions <- regions %>%
-  bind_rows(
-    regions_filled %>%
-      mutate(Note = "Filled")
-  ) %>%
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>%
-  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))
-
-# Display table of regions and countries
-regions %>%
-  drop_na(Note) %>%
-  select(-Note) %>%
-  arrange(region, country) %>%
-  kbl(caption = "Countries with a manually filled region") %>%
-  kable_custom()
-
-# Clean region labels
-regions$region <- str_replace_all(regions$region, " ", "_")
-regions$region <- factor(regions$region)
-
-# Remove unnecessary items
-regions <- select(regions, -Note)
-
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-gwp <- left_join(gwp, regions)
-# Remove now unnecessary variables
-rm(no_region_gbd, no_region_gwp, regions_filled, regions)
-```
-
-### ITU summary table
-
-```{r itu-summary-table}
-#| column: page
-#| tbl-cap: "Mean internet user percentages across regions and time."
-#| label: tbl-itusummary
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-```
-
-## RQ1: Time courses
-
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
-To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.
-
-### Modelling
+
+# Load data sets
+itu <- read_rds("data/itu.rds")
+gwp <- read_rds("data/gwp.rds")
+gbd <- read_rds("data/gbd.rds")
+```
+
+## Model 1
 
@@
 
+-   Create lagged and centered predictors
 -   Transform edge values of internet variable to fit beta
@@
 ```{r model1-prepare-data}
+# Create lagged predictors
+itu <- itu %>% 
+  arrange(region, country, year) %>%
+  group_by(region, country) %>%
+  mutate(
+    across(
+      c(internet, fixed, mobile),
+      list(`1` = ~ lag(., 1)),
+      .names = "{str_sub(.col, 1, 1)}{.fn}"
+    )
+  ) %>% 
+  ungroup()
+
+# Centering predictors within and between countries
+itu <- itu %>%
+  group_by(country) %>%
+  mutate(
+    i1_cb = mean(i1, na.rm = TRUE), # Country average
+    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
+    f1_cb = mean(f1, na.rm = TRUE),
+    f1_cw = f1 - f1_cb,
+    m1_cb = mean(m1, na.rm = TRUE),
+    m1_cw = m1 - m1_cb,
+  ) %>%
+  # Grand-mean center the country averages
+  mutate(
+    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
+  )
+
 # Transform internet edge cases
@@
 
-#### Specification
+### Specification
 
@@
 \begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
+y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2}v_i) \\
 \mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
@@
 \\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
-x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
-\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
+x_i &\sim \text{Beta}(\mu^x_i, \phi) \\ 
+\text{logit}(\mu^x_i) &= \beta^{x}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
 \left[\begin{array}{c}
@@
 \end{align*}
-$$
+$$ {#eq-model1}
 
@@
 ```{r model1-itu-bf}
+#| echo: true
 # Define a model of internet proportion over year
@@
 ```{r model1-val-bf}
+#| echo: true
 # Meta-regression model of outcomes
@@
 ```{r model1-selfharm-se}
+#| echo: true
 dat <- dat %>% 
@@
 
-#### Fitting
+### Fitting
 
@@
 ```{r fit-model-1}
+#| cache: false
 fits <- dat %>%
@@
 
-#### Summary
+### Summary
 
@@
 #| label: tbl-m1-data
-
-#' Model summary
-#'
-#' @param x a brmsfit
-#'
-#' @return A tibble with information on data in the model
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
 
@@
 
-#### Model checking
+### Model checking
 
@@
 
-##### MCMC diagnostics
+#### MCMC diagnostics
 
@@
 ```{r model-1-diagnostics}
-#| results: hold
+#| column: body-outset-right
 #| label: tab-model1-diagnostic
 #| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
-#| column: body-outset
 
@@
 
-##### Posterior predictive check
+#### Posterior predictive check
 
@@
 ```{r ppcheck-density}
-#| column: page
+#| column: page-right
+#| fig-height: 6
+#| fig-width: 9
 #| fig-cap: "Graphical posterior predictive check by region (Model 1).
@@
     legend.position = "none",
+    panel.spacing = unit(3, "pt"),
     axis.title = element_blank(),
@@
 
-### Results
-
-#### RQ1a: Temporal trends
-
-Before presenting the time trends, we must calculate the required quantities from the posterior distribution.
-Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.
-
-```{r calculate-simple-effects}
-#' Posterior draws at average and region levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = "region")
-}
-
-#' Posterior summaries at country- region- and average levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
-    select(-r_value)
-
-  bind_rows(
-    psum_region,
-    psum_country
-  ) %>%
-    mutate(region = fct_relevel(region, "Average"))
-}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit1, pdraws)) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums <- fits %>%
-  mutate(psums = map(fit1, psums)) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums_internet <- fits %>%
-  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-```
-
-We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions.
-Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).
-
-```{r forest-trends}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes"
-#| label: fig-forest-trends
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-```
-
-@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction.
-This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade.
-The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.
-
-Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data.
-This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes.
-Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.
-
-We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region.
-However, the average change again is not credibly different from zero.
-Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety.
-Depression and self-harm, on the other hand, had decreased across the board.
-
-In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.
-
-Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.
-
-```{r fitted-trend-country}
-
-#' Get (grand mean) fitted values for countries
-#'
-#' @param x a brmsfit model 1
-#'
-#' @return a data frame of fitted values
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
-    summarise(val = mean(val, na.rm = TRUE)) %>%
-    ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
-  newy <- bind_cols(
-    newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit1, fitted_country)) %>%
-  select(outcome, fc)
-
-#' Draw a panel plot of countries' fitted values and data
-#'
-#' @param x fitted country level data from fitted_country()
-#' @param y outcome
-#'
-#' @return a ggplot for that outcome
-plot_country <- function(x, y) {
-  coefs <- p_sums %>%
-    drop_na(country) %>%
-    filter(outcome == y) %>%
-    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
-    mutate(country = fct_reorder(country, coef))
-  x %>%
-    left_join(coefs) %>%
-    mutate(country = fct_reorder(country, coef)) %>%
-    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
-    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
-    scale_y_continuous(
-      str_replace(y, "_", " "),
-      breaks = pretty_breaks(),
-      expand = expansion(.15),
-      labels = function(x) {
-        percent(x / 100, .01) %>%
-          str_remove("\\.00")
-      }
-    ) +
-    # Add parameters in text
-    geom_richtext(
-      data = coefs %>%
-        mutate(across(where(is.numeric), ~ number(., .01))),
-      aes(
-        x = make_date(2000), y = Inf,
-        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
-      ),
-      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
-      family = Font,
-      fill = alpha("white", .3), label.color = NA,
-      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
-    ) +
-    geom_point(aes(y = val), shape = 1, alpha = .5) +
-    geom_ribbon(
-      aes(ymin = Q2.5, ymax = Q97.5),
-      alpha = .3, col = NA, fill = "dodgerblue1"
-    ) +
-    geom_line(
-      size = 0.5, col = "dodgerblue1"
-    ) +
-    facet_wrap(
-      "country"
-    ) +
-    theme(panel.spacing = unit(2, "pt"))
-}
-
-# Create the plot for each outcome
-f_country <- f_country %>%
-  mutate(
-    plot = map2(
-      fc, outcome,
-      ~ plot_country(.x, .y)
-    )
-  )
-```
-
-::: {.panel-tabset .column-screen-inset-shaded}
-##### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-##### Life satisfaction
-
-```{r trends-ls}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
-#| label: fig-trends-ls
-f_country$plot[[1]]
-```
-
-##### Negative experiences
-
-```{r trends-ne}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Negative experiences trends, ordered by association magnitude"
-#| label: fig-trends-ne
-f_country$plot[[2]]
-```
-
-##### Positive experiences
-
-```{r trends-pe}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Positive experiences trends, ordered by association magnitude"
-#| label: fig-trends-pe
-f_country$plot[[3]]
-```
-
-##### Anxiety
-
-```{r trends-anx}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Anxiety trends, ordered by association magnitude"
-#| label: fig-trends-anx
-f_country$plot[[4]]
-```
-
-##### Depression
-
-```{r trends-dep}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Depression trends, ordered by association magnitude"
-#| label: fig-trends-dep
-f_country$plot[[5]]
-```
-
-##### Self-harm
-
-```{r trends-sel}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Self-harm trends, ordered by association magnitude"
-#| label: fig-trends-sel
-f_country$plot[[6]]
-```
-:::
-
-#### RQ1b: Correlations
-
-We then turned to research question 1b: To what extent were changes in well-being and internet adoption correlated across countries.
-
-To investigate we examined the correlations between $\gamma^y_1$ and $\gamma^x_1$ ($\sigma_{\gamma^y_1,\gamma^x_1}$ in $\Sigma^{\text{c}}$).
-A positive correlation would indicate that countries with greater increases in internet adoption between 2000 and 2020 would tend to have greater increases in $y$ (e.g.
-Life satisfaction).
-
-To answer, we display $\sigma_{\gamma^y_1,\gamma^x_1}$ from each outcome's model in the figure below.
-The figures are scatterplots of country-level trend coefficients, where each point's x-y coordinate indicate their trend magnitudes.
-The overlaid ellipses are the model's 95% predictive limits for $\gamma^y_1$ and $\gamma^x_1$.
-
-```{r scatterplot-time-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of country-level internet and outcome trends."
-#| label: fig-trend-scatterplot
-
-# Correlation parameters
-cor_pars <- fits %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        variable = "cor_country__internet_year__val_year"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-# Ellipses
-ellipses <- fits %>%
-  mutate(
-    ellipse = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        c(
-          "b_val_year",
-          "b_internet_year",
-          "sd_country__val_year",
-          "sd_country__internet_year",
-          "cor_country__internet_year__val_year"
-        )
-      ) %>%
-        slice_sample(n = 100) %>%
-        rename(
-          cor = cor_country__internet_year__val_year,
-          sd_outcome = sd_country__val_year,
-          sd_i = sd_country__internet_year,
-          b_outcome = b_val_year,
-          b_i = b_internet_year
-        ) %>%
-        mutate(
-          e = pmap(
-            list(cor, sd_outcome, sd_i, b_outcome, b_i),
-            function(cor, sd_a, sd_i, b_a, b_i) {
-              ellipse(
-                cor,
-                scale = c(sd_i, sd_outcome),
-                centre = c(b_i, b_outcome),
-                level = .95
-              ) %>%
-                as_tibble()
-            }
-          )
-        ) %>%
-        unnest(e)
-    )
-  )
-ellipses <- ellipses %>%
-  select(outcome, ellipse) %>%
-  unnest(ellipse)
-
-# Wide tibble of parameters
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_path(
-    data = ellipses,
-    aes(x = x, y = y, group = .draw),
-    alpha = .2, size = .1, col = "dodgerblue2"
-  ) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_text(
-    data = cor_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-#### Other results from Model 1
-
-##### Shrinkage
-
-It's important to note that at the level of countries and regions, the model parameters refer to country^\*^ and region^\*^, that is as they are in the sample of other countries and regions.
-This modelling strategy is important because it allows describing the parameters at each level while adjusting the values toward the group means (preventing "false alarms").
-However it is then important to examine those values against their "fixed effect" counterparts, which we do here.
-
-```{r shrinkage}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of multilevel and independent model coefficients"
-#| label: fig-trend-shrinkage
-
-lm_coefs <- fits %>%
-  mutate(
-    data = map(fit1, ~ as_tibble(.x$data))
-  ) %>%
-  mutate(
-    fit_val = map(
-      data,
-      ~ tidy(
-        lm(val ~ 0 + country + year:country, data = .x)
-      )
-    ),
-    fit_internet = map(
-      data,
-      ~ tidy(
-        gam(
-          internet ~ 0 + country + year:country,
-          family = betar, data = .x %>%
-            filter(itu)
-        ),
-        parametric = TRUE
-      )
-    )
-  )
-lm_coefs <- lm_coefs %>%
-  select(outcome, fit_val, fit_internet) %>%
-  pivot_longer(c(fit_val, fit_internet)) %>%
-  mutate(name = str_remove(name, "fit_")) %>%
-  unnest(value) %>%
-  select(outcome, name, term, estimate, std.error) %>%
-  filter(str_detect(term, ":")) %>%
-  mutate(term = str_remove(term, "country")) %>%
-  mutate(term = str_remove(term, ":year")) %>%
-  pivot_wider(names_from = name, values_from = c(estimate, std.error)) %>%
-  rename(country = term)
-
-# Plot
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  left_join(lm_coefs) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate, col = region)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_segment(
-    aes(
-      x = estimate_internet, xend = Internet_Estimate,
-      y = estimate_val, yend = Outcome_Estimate
-    ),
-    arrow = arrow(type = "closed", length = unit(3, "pt")),
-    size = .25, show.legend = FALSE
-  ) +
-  geom_point(size = 1.1, alpha = .4) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  guides(
-    color = guide_legend(override.aes = list(size = 2, alpha = 1))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "bottom"
-  )
-```
-
-## RQ2: Associations
-
-We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption?
-To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes.
-Before modelling, we calculated these quantities as shown in this code block.
-
-```{r model2-data-prepare}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(outcome, region, country, year) %>%
-  group_by(outcome, region, country, sex, age) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-dat <- dat %>%
-  group_by(outcome, country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  group_by(outcome) %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-```
-
-### Specification and fitting
+## Model 2
 
@@
 
-$$\begin{align*}
+$$
+\begin{align*}
 y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\
-
 \mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
@@
 \\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\
-
+\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
+\\ &\beta_9\text{Internet}^{\text{between}}_i\\ \\
 \left[\begin{array}{c}
@@
 )
-\end{align*}$$
+\end{align*}
+$$ {#eq-model2}
+
+Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion, and $\text{Internet}^{\text{between}}_i$ is the between-country-centered internet adoption proportion.
 
 ```{r fit-model-2}
-
+#| cache: false
+#| results: hide
 # Model formula is only a small update to Model 1
@@
 # As above with model 1
-fits <- fits %>%
+# Note we don't need to save these in the R environment, just files
+fits %>%
   mutate(
@@
 
-### Results
-
-First, we compared the R2 values between Models 1 and 2.
-This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2).
-However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.
-
-```{r model21-compare}
-#| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
-#| label: tbl-m12-r2
-fits %>%
-  select(outcome, fit1, fit2) %>% 
-  pivot_longer(c(fit1, fit2)) %>% 
-  mutate(
-    r2 = map(
-      value,
-      ~ bayes_R2(., resp = "val") %>%
-        as.data.frame() %>%
-        mutate(across(everything(), ~ percent(., .1))) %>%
-        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
-    )
-  ) %>%
-  select(-value) %>%
-  unnest(r2) %>% 
-  pivot_wider(
-    names_from = name,
-    values_from = result,
-    names_prefix = "Model "
-  ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  kbl(caption = "Model 1 and 2 R-squared values") %>%
-  kable_custom()
-```
-
-Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.
-
-```{r model2-calculate-coefficients}
-p_draws <- fits %>%
-  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws)
-
-p_sums <- fits %>%
-  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums)
-
-p_draws <- p_draws %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-p_sums <- p_sums %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-```
-
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
-
-```{r forest-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x"
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
-x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
-```
-
-This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
-However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
-Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region.
-However, none of the average associations were credibly different from zero.
-The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.
-
-To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
-
-```{r model2-fitted-values}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Counterfactual plot of internet associations"
-#| label: fig-fitted-internet
-
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country) %>%
-    mutate(
-      xmin = min(i1_cw, na.rm = TRUE),
-      xmax = max(i1_cw, na.rm = TRUE)
-    ) %>%
-    filter(i1_cw %in% c(xmin, xmax)) %>%
-    ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
-  newy
-}
-
-fitted_region <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region) %>%
-    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
-    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit2, fitted_country)) %>%
-  select(outcome, fc) %>%
-  unnest(fc)
-
-f_region <- fits %>%
-  mutate(fr = map(fit2, fitted_region)) %>%
-  select(outcome, fr) %>%
-  unnest(fr)
-
-f_country %>%
-  ggplot(aes(i1_cw, Estimate)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimate",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = f_region,
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = f_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country),
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    panel.spacing = unit(2, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-### Other results from Model 2
-
-We then focused on the between-country association between internet adoption and well-being.
-Recall that the model does not adjust for between-country differences so these associations are likely to reflect many other factors covarying with internet adoption (e.g.
-wealth and development factors).
-
-```{r}
-#| column: page
-#| fig.width: 8
-#| fig.height: 6
-#| fig-cap: "Between-country associations"
-#| label: fig-cb1
-
-fitted_cb1 <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region, country) %>%
-    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
-    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
-    ungroup()
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = NA
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-tmp <- fits %>% 
-  mutate(out = map(fit2, fitted_cb1)) %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-cb1_pars <- fits %>%
-  mutate(
-    out = map(
-      fit2,
-      ~ as_draws_df(
-        .x,
-        variable = "b_i1_cb"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-tmp %>% 
-  ggplot(aes(i1_cb, val)) +
-  scale_x_continuous(
-    "Between-country centered internet adoption",
-    labels = ~percent(.)
-  ) +
-  scale_y_continuous(
-    "Value",
-    labels = ~percent(./100)
-  ) +
-  geom_point(
-    shape = 1, size = 1, alpha = .75
-  ) +
-  geom_ribbon(
-    aes(ymin = Q2.5, ymax = Q97.5),
-    fill = "dodgerblue2",
-    alpha = .2
-    ) +
-  geom_line(aes(y = Estimate), col = "dodgerblue4") +
-  geom_text(
-    data = cb1_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    axis.title.y = element_blank()
-  )
-```
-
-## RQ3: Demographics
-
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
-
-### Trends
-
-```{r model1-demographics}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes by demographic group"
-#| label: fig-forest-trends-demo
-h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-#' Calculate posterior draws for simple effects (by sex and age) for regions and average
-#'
-#' @param x brmsfit model 2
-#' @param h a brmshypothesis
-#'
-#' @return a long tibble of draws of posterior answers to hypothesis
-simple_effects_samples <- function(x, h) {
-  # Calculate hypotheses at average level
-  average_h <- hypothesis(
-    x, h
-  )
-  # Give hypotheses appropriate names
-  average <- average_h$samples
-  names(average) <- interaction(
-    "Average", average_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  # Pivot to long format, note use of dtplyr
-  average <- average %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  # Regions as above
-  region_h <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )
-  region <- region_h$samples
-  names(region) <- interaction(
-    region_h$hypothesis$Group,
-    region_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  region <- region %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  bind_rows(average, region)
-}
-
-#' Posterior summaries of country- region- and average-level effects for the demographic groups
-#'
-#' @param x brmsfit model 2
-#' @param h character vector of hypotheses
-#'
-#' @return
-simple_effects_summary <- function(x, h) {
-
-  # Calculate hypotheses at average level
-  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
-  average$region <- "Average"
-
-  # Regions as above
-  region <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )$hypothesis %>%
-    as_tibble()
-  region <- rename(region, region = Group)
-
-  # Country hypotheses
-  country <- hypothesis(
-    x, h,
-    scope = "ranef", group = "country"
-  )
-  country <- country$hypothesis %>% as_tibble()
-  country <- rename(country, country = Group)
-
-  # Add region coefs
-  country <- left_join(country, distinct(x$data, region, country))
-  region_coef <- region %>%
-    select(region, Hypothesis, r_region = Estimate)
-  country <- country %>%
-    left_join(region_coef) %>%
-    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
-    select(-r_region)
-
-  bind_rows(average, region, country)
-}
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit1, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-### Associations
-
-```{r model2-demographics}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of associations by demographic group"
-#| label: fig-forest-association-demo
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-## Other internet metrics
-
-Fixed and mobile broadband subscription analyses
-
-```{r fixed-mobile-formulas}
+## Other predictors
+
+Here we further fit model 2 using the different internet predictors
+
+```{r fixed-mobile}
+#| cache: false
+#| results: hide
 bf_2_f <- bf(
@@
 )
-```
+
+fits %>%
+  mutate(
+    fit2_f = map2(
+      data, outcome,
+      ~brm(
+        formula = bf_2_f,
+        data = .x,
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("models/brm-{.y}-2-fixed")
+      )
+    )
+  )
+
+fits %>%
+  mutate(
+    fit2_m = map2(
+      data, outcome,
+      ~brm(
+        formula = bf_2_m,
+        data = .x,
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("models/brm-{.y}-2-mobile")
+      )
+    )
+  )
+```

### 2022-01-10 01-timecourses.qmd
Split into sections

--- 2021-12-17 index.qmd
@@
----
-title: "Adolescent well-being in the digital age"
-author: "Matti Vuorre"
-date: "`r Sys.time()`"
-execute:
-  eval: true
-  error: true
-  cache: true
-  warning: false
-  message: false
-format: 
-  html:
-    monofont: Fira Code
-    font-size: 1.0em
-    linestretch: 1.4
-    code-fold: true
-    code-summary: "Show code"
-    code-tools: true
-    code-link: true
-toc: true
-toc-depth: 4
-toc-title: Contents
-number-sections: false
-crossref:
-  fig-prefix: Figure
-  tbl-prefix: Table
----
-
-```{r document-options, include = FALSE, cache = FALSE}
-# knitr options
-knitr::opts_chunk$set(
-  fig.align = "center",
-  cache.lazy = FALSE # Fix large knitr cache
-)
-```
-
-## Preface
-
-Welcome!
-This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation).
-It contains all the analyses reported in the manuscript along with supplemental analyses.
-The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).
-
-::: {.callout-note collapse="true"}
-### Reproducibility
-
-The analyses were conducted in R, and can be reproduced locally:
-
-1.  Clone the github repo
-
--   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
--   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
-
-2.  Prepare the R environment
-
--   Terminal: `Rscript -e "renv::restore()`
--   RStudio: Click renv -> Restore Library in the Packages panel
-
-3.  Render `index.qmd` to `index.html`
-
--   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
--   Terminal: `quarto render index.qmd`
--   RStudio: Open `index.qmd` and click Render
-
-The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.
-
-If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
-:::
-
-## Data preparation
-
-Our analyses draw on three sources of data.
-The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
-The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
-And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
-
-In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:
-
-```{r setup, cache = FALSE}
-
+# Time courses
+
+```{r setup}
+#| cache: false
 # Packages
-library(readxl)
-library(knitr)
-library(ragg)
-library(imputeTS)
-library(naniar)
 library(scales)
-library(janitor)
-library(haven)
-library(labelled)
-library(countrycode)
 library(ggtext)
-library(dtplyr)
 library(lubridate)
 library(kableExtra)
-library(gtsummary)
 library(ggstance)
@@
 library(broom)
-library(kableExtra)
 library(tidyverse)
-
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
-nchains <- 4
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = nchains,
-  cores = nchains,
-  threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1000,
-  refresh = 50,
-  adapt_delta = .90,
-  max_treedepth = 10
-)
-
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-# Format tables
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}
-
-# Create directory for intermediate files
-dir.create("models", FALSE)
-```
-
-### Gallup World Poll
-
-We first prepare the Gallup data.
-Note that this data set is not publicly available, and therefore not included in our repository.
-We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.
-
-```{r gallup-codebook}
-#| echo: false
-#| eval: false
-# Understand variables & values
-# Codes NOTE 1: yes 2: no!
-read_spss(
-  "data-raw/Gallup/The_Gallup_101521.sav",
-  n_max = 1,
-  col_select = c(
-    WPID, WP1219,
-    WP16,
-    WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74
-  )
-) %>%
-  generate_dictionary()
-```
-
-Here we import the relevant variables from Gallup's SPSS files and then
-
--   Clean the variable names
--   Set appropriate missing values (`NaN`, not e.g. `-99`)
--   Use appropriate coding schemes (e.g. 0: no; 1: yes)
--   Calculate scale scores (means over items)
--   Rescale outcomes to proportions (0 - 1)
--   Subset the data to 15 to 24 year olds
--   Create age-categories in line with GBD data
--   Drop one 13 year old as this data should only have people 15 and older
-
-```{r gallup-clean}
-# First liberate the data from the slow SPSS file and save to disk
-gwp_path <- "data-raw/Gallup/gwp-processed.rds"
-if (!file.exists(gwp_path)) {
-  gwp <- read_spss(
-    "data-raw/Gallup/The_Gallup_101521.sav",
-    col_select = c(
-      YEAR_CALENDAR,
-      COUNTRYNEW,
-      WPID, WP1220, WP1219,
-      WP16,
-      WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
-    )
-  )
-
-  # Get rid of SPSS attributes
-  gwp <- gwp %>%
-    zap_labels() %>%
-    zap_label() %>%
-    zap_widths() %>%
-    zap_formats()
-
-  # Save into a good format
-  write_rds(gwp, gwp_path)
-} else {
-  gwp <- read_rds(gwp_path)
-}
-
-gwp <- gwp %>%
-  clean_names() %>%
-  transmute(
-    country = countrynew,
-    year = year_calendar,
-    id = wpid,
-    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
-    age = wp1220,
-    # Don't know, refused, and missing values
-    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
-    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
-    # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
-  )
-
-# Scale scores note rescaling
-gwp <- gwp %>%
-  mutate(
-    Life_satisfaction = Life_satisfaction / 10,
-    Negative_experiences =
-      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
-    Positive_experiences =
-      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
-  ) %>%
-  select(-c(wp60:wp74))
-
-# Categorize ages
-gwp <- gwp %>%
-  mutate(
-    age = cut(
-      age,
-      breaks = seq(15, 105, by = 5),
-      include.lowest = TRUE,
-      right = FALSE,
-      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
-    ) %>% as.character()
-  )
-
-# There is one 13 year old which resulted in a NA and we drop it
-gwp <- drop_na(gwp, age)
-
-# Focus on young people
-gwp <- gwp %>%
-  filter(age %in% c("15 to 19", "20 to 24"))
-```
-
-Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex).
-Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.
-
-```{r gallup-summarise}
-gwp <- gwp %>%
-  pivot_longer(
-    c(
-      Life_satisfaction,
-      Negative_experiences,
-      Positive_experiences
-    ),
-    names_to = "outcome", values_to = "val"
-  ) %>%
-  group_by(country, year, sex, age, outcome) %>%
-  summarise(
-    se = sd(val, na.rm = TRUE) / sqrt(n()),
-    val = mean(val, na.rm = TRUE)
-  ) %>%
-  ungroup()
-```
-
-We have three data sets with information on countries.
-Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values.
-We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
-We do that here for the GWP data, and check that all countries receive a unique name.
-
-```{r gwp-harmonise-countries}
-#| results: hold
-#| label: tbl-gwp-countries
-#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gwp %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GWP harmonised country names") %>%
-  kable_custom()
-
-# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
-
-# Harmonise old names and replace only if harmonised name found
-gwp <- gwp %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  # Prevent north cyprus from becoming cyprus
-  mutate(
-    country_harmonised = ifelse(
-      country == "Northern Cyprus",
-      "Northern Cyprus",
-      country_harmonised
-    )
-  ) %>%
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### Global Burden of Disease
-
-We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
-We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R.
-They are inside downloaded `.zip` files, of which there may be more than one.
-
-```{r gbd-data-load}
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/",
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>%
-  read_csv()
-```
-
-We then clean the GBD data and
-
--   Clean the variable names
--   Remove the metric and measure variables; we focus on prevalence rate
-    -   prevalence: Total number of cases
-    -   rate: Total cases per 100,000 population
--   Convert outcome rates to proportions (0 - 1)
--   Clean cause names and rename to outcome to harmonise with GWP
--   Convert GBD estimated rate CI limits to an approximate standard error
--   Subset data to young people (10 - 24)
-
-```{r gbd-data-clean}
-# First step is to clean names
-gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
-gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 100000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>%
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>%
-  rename(country = location, outcome = cause)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
-gbd <- gbd %>%
-  mutate(se = (upper - lower) / (1.96 * 2)) %>%
-  select(-c(upper, lower))
-
-# Focus on young people
-gbd <- gbd %>%
-  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
-```
-
-Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.
-
-```{r gbd-harmonise-countries}
-#| results: hold
-#| label: tbl-gbd-countries
-#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GBD harmonised country names") %>%
-  kable_custom()
-# Harmonise old names and replace only if harmonised name found
-gbd <- gbd %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### International Telecommunication Union
-
-After processing the outcome tables above, we move on to the internet adoption metrics from the ITU.
-We downloaded these data files from the ITU website.
-New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
-
-After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1).
-Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.
-
-```{r itu-process}
-#| results: hold
-#| label: tbl-itu-0
-#| tbl-cap: "ITU countries"
-#| layout-ncol: 1
-
-# Download data sets from the ITU website if not yet downloaded
-if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
-  dir.create("data-raw/ITU")
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
-    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
-    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
-    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
-  )
-}
-
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(fixed = as.numeric(value)) %>%
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(mobile = as.numeric(value)) %>%
-  select(country = Country, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(internet = as.numeric(value)) %>%
-  select(country = Country, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
-itu <- itu %>%
-  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-
-# Harmonise countries
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "ITU harmonised country names") %>%
-  kable_custom()
-
-# Harmonise old names and replace only if harmonised name found
-itu <- itu %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Drop countries that don't exist in outcomes
-itu <- itu %>%
-  filter(
-    country %in% unique(gbd$country) | country %in% unique(gwp$country)
-  )
-
-# Drop countries that don't have any actual internet data
-itu_zeros <- itu %>%
-  group_by(country) %>%
-  summarise(s = sum(internet, na.rm = TRUE)) %>%
-  filter(s == 0)
-
-itu <- itu %>%
-  filter(!(country %in% itu_zeros$country))
-rm(itu_zeros)
-```
-
-#### Missingness
-
-We then impute missing intermediate values to the internet adoption timeseries.
-We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.
-
-```{r itu-impute}
-#| results: hold
-#| label: tbl-itu-impute
-#| tbl-cap: "Summary of ITU data imputation"
-
-# Reshape to easily impute all variables
-itu_long <- itu %>%
-  pivot_longer(c(internet, fixed, mobile))
-
-# Impute by country and variable
-itu_long <- itu_long %>%
-  group_by(country, name) %>%
-  # Find first and last year with this variable in each country
-  # so as to prevent extrapolation
-  mutate(
-    min_year = year[min(which(!is.na(value)))],
-    max_year = year[max(which(!is.na(value)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  mutate(
-    across(
-      value,
-      .fns = list(
-        i = possibly(
-          function(x) na_interpolation(x, maxgap = Inf),
-          otherwise = NaN
-        )
-      )
-    )
-  ) %>%
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    value_i = if_else(
-      between(year, unique(min_year), unique(max_year)),
-      value_i,
-      NaN
-    )
-  ) %>%
-  ungroup() %>%
-  select(-min_year, -max_year)
-
-# Summary
-itu_long %>%
-  group_by(name) %>%
-  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
-  summarise(
-    n_miss_orig = sum(is.na(value) & year >= min_year),
-    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
-    n_miss_imp = sum(is.na(value_i) & year >= min_year),
-    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
-    imputed = n_miss_orig - n_miss_imp
-  ) %>%
-  kbl(caption = "ITU data imputation summary") %>%
-  kable_custom()
-
-# We then replace the original values with the imputed ones
-itu <- itu_long %>%
-  # Pick non-missing value, from original and imputed
-  mutate(value = coalesce(value, value_i)) %>%
-  select(-value_i) %>%
-  pivot_wider()
-rm(itu_long)
-```
-
-### GLOBE regions
-
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
-
-```{r globe-regions}
-#| results: hold
-#| label: tbl-globe
-#| tbl-cap: "Countries with manually filled region"
-
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
-) %>%
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>%
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>%
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in GBD not present in region data
-no_region_gbd <- filter(
-  distinct(gbd, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-# Then see what countries in GWP are without region
-no_region_gwp <- filter(
-  distinct(gwp, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-bind_rows(no_region_gbd, no_region_gwp) %>%
-  arrange(country) %>%
-  distinct() %>%
-  write_csv("data-raw/Regions/countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/countries-without-region-filled.csv"
-)
-
-# Combine Jebb et al GLOBE regions and our manually added ones
-regions <- regions %>%
-  bind_rows(
-    regions_filled %>%
-      mutate(Note = "Filled")
-  ) %>%
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>%
-  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))
-
-# Display table of regions and countries
-regions %>%
-  drop_na(Note) %>%
-  select(-Note) %>%
-  arrange(region, country) %>%
-  kbl(caption = "Countries with a manually filled region") %>%
-  kable_custom()
-
-# Clean region labels
-regions$region <- str_replace_all(regions$region, " ", "_")
-regions$region <- factor(regions$region)
-
-# Remove unnecessary items
-regions <- select(regions, -Note)
-
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-gwp <- left_join(gwp, regions)
-# Remove now unnecessary variables
-rm(no_region_gbd, no_region_gwp, regions_filled, regions)
-```
-
-### ITU summary table
-
-```{r itu-summary-table}
-#| column: page
-#| tbl-cap: "Mean internet user percentages across regions and time."
-#| label: tbl-itusummary
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-```
-
-## RQ1: Time courses
-
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
-To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.
-
-### Modelling
-
-We first prepare the variables for modelling:
-
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
--   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
-
-```{r model1-prepare-data}
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center and scale year
-dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in mv models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
-  ungroup()
-
-# Ensure that factors are contrast coded
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
-
-# Arrange on outcome
+```
+
+```{r load}
+#| cache: false
+# Load data sets
+itu <- read_rds("data/itu.rds")
+gwp <- read_rds("data/gwp.rds")
+gbd <- read_rds("data/gbd.rds")
+
+# Load models
 oo <- c(
@@
 )
-dat <- dat %>%
+fits <- tibble(outcome = oo) %>% 
   mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(dat, outcome, region, country, year)
-
-dat %>%
-  group_by(outcome) %>%
-  summarise(
-    min = min(val, na.rm = TRUE),
-    max = max(val, na.rm = TRUE),
-    internet_min = min(internet, na.rm = TRUE),
-    internet_max = max(internet, na.rm = TRUE)
-  ) %>%
-  kable(digits = 7) %>% 
-  kable_custom()
-```
-
-#### Specification
-
-We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b).
-Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g.
-Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries.
-We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)
-
-We fit the model separately for each outcome.
-Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret).
-We therefore estimate six separate bivariate models
-
-In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.
-All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes.
-This latter specification is important to allow answering RQ1b.
-
-The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate.
-For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age).
-The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data.
-Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.
-
-We write the model as
-
-$$
-\begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
-\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
-\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
-x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
-\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
-\left[\begin{array}{c}
-\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
-\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
-\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
-\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
-\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
-\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
-\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}
-$$
-
-Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.
-
-We then define the model formulas in brms' formula syntax.
-First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
-To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model.
-The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).
-
-```{r model1-itu-bf}
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~
-  year +
-    (year |c| country) +
-    (year |r| region),
-  family = Beta()
-)
-```
-
-Here, we specify the outcome model.
-Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
-Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
-In addition, it leads to the residual variance to be estimated.
-
-```{r model1-val-bf}
-# Meta-regression model of outcomes
-bf_1 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
-  family = gaussian()
-)
-```
-
-Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged.
-We therefore effectively removed the SEs from self-harm by setting them to zero
-
-```{r model1-selfharm-se}
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
-
-#### Fitting
-
-We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.
-
-```{r fit-model-1}
-
-fits <- dat %>%
-  # Could nest but need this to include group key in nested tibble
-  group_by(outcome) %>%
-  summarise(data = list(cur_data_all()))
-
-fits <- fits %>%
-  mutate(
-    fit1 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE),
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-1-internet")
-      )
-    )
-  )
-```
-
-#### Summary
-
-Here is a summary of the data modelled for each outcome
-
-```{r model-1-data-summary}
-#| column: body-outset
-#| tbl-cap: "Summaries of data included in Model 1"
-#| label: tbl-m1-data
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
-fits %>%
-  mutate(summary = map(fit1, msum)) %>%
-  select(outcome, summary) %>%
-  unnest(summary) %>%
-  kbl(caption = "Model 1 data summary") %>%
-  kable_custom() %>% 
-  row_spec(0, bold = TRUE)
-```
-
-#### Model checking
-
-Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section
-
-##### MCMC diagnostics
-
-First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.
-
-We can see that the models have converged nicely, apart from the self-harm outcome.
-
-```{r model-1-diagnostics}
-#| results: hold
-#| label: tab-model1-diagnostic
-#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
-#| column: body-outset
-
-diagnostic_table <- function(fit, rx, cp) {
-  diag_1 <- fits %>%
-    select(fit = {{ fit }}, outcome) %>% 
-    mutate(
-      out =
-        map(
-          fit,
-          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
-            summarise_draws(samples = length, default_convergence_measures())
-        )
-    ) %>%
-    select(outcome, out) %>%
-    unnest(out)
-  diag_1 %>%
-    kbl(
-      caption = cp,
-      digits = c(0, 0, 0, 2, 0, 0)
-    ) %>%
-    column_spec(
-      4,
-      color = "white",
-      background = spec_color(
-        log(diag_1$rhat),
-        direction = 1,
-        option = "C",
-        end = .6
-      )
-    ) %>%
-    column_spec(
-      c(5, 6),
-      color = "white",
-      background = spec_color(
-        log(diag_1$ess_tail / diag_1$samples),
-        direction = 1,
-        option = "C",
-        end = 0,
-        begin = .6
-      )
-    ) %>%
-    kable_custom()
-}
-diagnostic_table(
-  fit1,
-  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
-  cp = "Model 1 MCMC diagnostics."
-) %>% 
-  scroll_box(height = "300px")
-```
-
-##### Posterior predictive check
-
-We then take a coarse look at how well the models reproduce the input data.
-
-```{r ppcheck-density}
-
-#| column: page
-#| fig-cap: "Graphical posterior predictive check by region (Model 1).
-Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g.
-Anglo Depression)."
-#| label: fig-ppcheck-1
-ppcheck_1 <- fits %>%
-  group_by(outcome) %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ pp_check(
-        .x,
-        ndraws = 10,
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val",
-        newdata = .x$data
-      )[[1]]
-    )
-  ) %>%
-  ungroup() %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-ppcheck_1 %>%
-  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
-  scale_color_brewer(palette = "Set1") +
-  scale_alpha_manual(values = c(.2, 1)) +
-  stat_density(
-    geom = "line",
-    size = .75,
-    position = position_identity()
-  ) +
-  labs(x = "Value", y = "Density") +
-  facet_grid2(
-    outcome ~ group,
-    scales = "free", independent = "x",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title = element_blank(),
-    axis.text = element_blank(),
-    axis.ticks = element_blank()
-  )
-```
-
-### Results
-
-#### RQ1a: Temporal trends
+  mutate(
+    fit1 = map(
+      outcome, 
+      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
+    )
+  )
+```
+
+Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
+And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
+To answer, we examine Model 1's results.
+
+## Results
+
+### RQ1a: Temporal trends
 
@@
 ```{r calculate-simple-effects}
-
-#' Posterior draws at average and region levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = "region")
-}
-
-#' Posterior summaries at country- region- and average levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
-    select(-r_value)
-
-  bind_rows(
-    psum_region,
-    psum_country
-  ) %>%
-    mutate(region = fct_relevel(region, "Average"))
-}
-
 p_draws <- fits %>%
@@
 
-We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions.
+We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$ in @eq-model1) time trend parameters' posterior distributions.
 Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).
@@
 ```{r forest-trends}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
+#| column: screen-inset-right
+#| fig-width: 13
+#| fig-height: 8
 #| fig-cap: "Forest plot of linear trends in outcomes"
@@
     family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
+    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
     fill = NA, label.color = NA,
@@
 
-@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction.
+Starting from the top left panel, the average (across countries and regions) change in life satisfaction.
 This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade.
@@
 ```{r fitted-trend-country}
-
-#' Get (grand mean) fitted values for countries
-#'
-#' @param x a brmsfit model 1
-#'
-#' @return a data frame of fitted values
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
-    summarise(val = mean(val, na.rm = TRUE)) %>%
-    ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
-  newy <- bind_cols(
-    newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
-  newy
-}
-
 f_country <- fits %>%
@@
     ) +
-    theme(panel.spacing = unit(2, "pt"))
+    theme(
+      panel.spacing = unit(2, "pt")
+    )
 }
@@
 
-::: {.panel-tabset .column-screen-inset-shaded}
-##### All outcomes
+::: {.panel-tabset .column-screen-inset-right}
+#### All outcomes
 
@@
 #| echo: false
-#| fig-width: 14
-#| fig-height: 9
+#| fig-width: 12
+#| fig-height: 8
 #| fig-cap: "Trends in all variables across regions"
@@
 
-##### Life satisfaction
+#### Life satisfaction
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Life satisfaction trends, ordered by association magnitude"
@@
 
-##### Negative experiences
+#### Negative experiences
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Negative experiences trends, ordered by association magnitude"
@@
 
-##### Positive experiences
+#### Positive experiences
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Positive experiences trends, ordered by association magnitude"
@@
 
-##### Anxiety
+#### Anxiety
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Anxiety trends, ordered by association magnitude"
@@
 
-##### Depression
+#### Depression
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Depression trends, ordered by association magnitude"
@@
 
-##### Self-harm
+#### Self-harm
 
@@
 #| echo: false
-#| fig-width: 16
-#| fig-height: 12
+#| fig-width: 12
+#| fig-height: 10
 #| fig-cap: "Self-harm trends, ordered by association magnitude"
@@
 
-#### RQ1b: Correlations
+### RQ1b: Correlations
 
@@
 ```{r scatterplot-time-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
+#| column: screen-inset-right
+#| fig-width: 12
+#| fig-height: 8
 #| fig-cap: "Scatterplots of country-level internet and outcome trends."
@@
 
-#### Other results from Model 1
-
-##### Shrinkage
+### Other results from Model 1
+
+#### Shrinkage
 
@@
 ```{r shrinkage}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
+#| column: screen-inset-right
+#| fig-width: 12
+#| fig-height: 8
 #| fig-cap: "Scatterplots of multilevel and independent model coefficients"
@@
   ) +
+  scale_color_discrete("Region") +
   facet_wrap(
@@
     scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+    labeller = as_labeller(function(x) str_replace(x, "_", " "))
   ) +
@@
 
-## RQ2: Associations
-
-We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption?
-To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes.
-Before modelling, we calculated these quantities as shown in this code block.
-
-```{r model2-data-prepare}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(outcome, region, country, year) %>%
-  group_by(outcome, region, country, sex, age) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-dat <- dat %>%
-  group_by(outcome, country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  group_by(outcome) %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-```
-
-### Specification and fitting
-
-Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions
-
-$$\begin{align*}
-y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\
-
-\mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
-\gamma_{0\text{country}[i]} + \\ &(\beta_{1} + \delta_{1\text{region}[i]} + \gamma_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta_{2} + \delta_{2\text{region}[i]} + \gamma_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta_{3} + \delta_{3\text{region}[i]} + \gamma_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta_{4} + \delta_{4\text{region}[i]} + \gamma_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta_{5} + \delta_{5\text{region}[i]} + \gamma_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i +
-\\ &(\beta_{6} + \delta_{6\text{region}[i]} + \gamma_{6\text{country}[i]})\text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\
-
-\left[\begin{array}{c}
-\delta_{0\text{region}} \\ \delta_{1\text{region}} \\ 
-\delta_{2\text{region}} \\ \delta_{3\text{region}} \\ 
-\delta_{4\text{region}} \\ \delta_{5\text{region}} \\ 
-\delta_{6\text{region}} \\ \delta_{7\text{region}} \\ 
-\delta_{8\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\ 
-\gamma_{4\text{country}} \\ \gamma_{5\text{country}} \\ 
-\gamma_{6\text{country}} \\ \gamma_{7\text{country}} \\ 
-\gamma_{8\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}$$
-
-```{r fit-model-2}
-
-# Model formula is only a small update to Model 1
-bf_2 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-# As above with model 1
-fits <- fits %>%
-  mutate(
-    fit2 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-internet")
-      )
-    )
-  )
-```
-
-### Results
-
-First, we compared the R2 values between Models 1 and 2.
-This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2).
-However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.
-
-```{r model21-compare}
-
-#| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
-#| label: tbl-m12-r2
-fits %>%
-  select(outcome, fit1, fit2) %>% 
-  pivot_longer(c(fit1, fit2)) %>% 
-  mutate(
-    r2 = map(
-      value,
-      ~ bayes_R2(., resp = "val") %>%
-        as.data.frame() %>%
-        mutate(across(everything(), ~ percent(., .1))) %>%
-        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
-    )
-  ) %>%
-  select(-value) %>%
-  unnest(r2) %>% 
-  pivot_wider(
-    names_from = name,
-    values_from = result,
-    names_prefix = "Model "
-  ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  kbl(caption = "Model 1 and 2 R-squared values") %>%
-  kable_custom()
-```
-
-Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.
-
-```{r model2-calculate-coefficients}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws)
-
-p_sums <- fits %>%
-  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums)
-
-p_draws <- p_draws %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-p_sums <- p_sums %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-```
-
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
-
-```{r forest-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x"
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
-x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
-```
-
-This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
-However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
-Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region.
-However, none of the average associations were credibly different from zero.
-The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.
-
-To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
-
-```{r model2-fitted-values}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Counterfactual plot of internet associations"
-#| label: fig-fitted-internet
-
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country) %>%
-    mutate(
-      xmin = min(i1_cw, na.rm = TRUE),
-      xmax = max(i1_cw, na.rm = TRUE)
-    ) %>%
-    filter(i1_cw %in% c(xmin, xmax)) %>%
-    ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
-  newy
-}
-
-fitted_region <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region) %>%
-    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
-    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit2, fitted_country)) %>%
-  select(outcome, fc) %>%
-  unnest(fc)
-
-f_region <- fits %>%
-  mutate(fr = map(fit2, fitted_region)) %>%
-  select(outcome, fr) %>%
-  unnest(fr)
-
-f_country %>%
-  ggplot(aes(i1_cw, Estimate)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimate",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = f_region,
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = f_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country),
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    panel.spacing = unit(2, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-### Other results from Model 2
-
-We then focused on the between-country association between internet adoption and well-being.
-Recall that the model does not adjust for between-country differences so these associations are likely to reflect many other factors covarying with internet adoption (e.g.
-wealth and development factors).
-
-```{r}
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Between-country associations"
-#| label: fig-cb1
-
-fitted_cb1 <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region, country) %>%
-    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
-    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
-    ungroup()
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = NULL
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-tmp <- fits %>% 
-  mutate(out = map(fit2, fitted_cb1)) %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-cb1_pars <- fits %>%
-  mutate(
-    out = map(
-      fit2,
-      ~ as_draws_df(
-        .x,
-        variable = "b_i1_cb"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-tmp %>% 
-  ggplot(aes(i1_cb, val)) +
-  scale_x_continuous(
-    "Between-country centered internet adoption",
-    labels = ~percent(.)
-  ) +
-  scale_y_continuous(
-    "Value",
-    labels = ~percent(./100)
-  ) +
-  geom_point(
-    shape = 1, size = 1, alpha = .75,
-    aes(col = region)
-  ) +
-  geom_ribbon(
-    aes(ymin = Q2.5, ymax = Q97.5),
-    fill = "dodgerblue2",
-    alpha = .2
-    ) +
-  geom_line(aes(y = Estimate), col = "dodgerblue4") +
-  geom_text(
-    data = cb1_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    axis.title.y = element_blank()
-  )
-```
-
-## RQ3: Demographics
-
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
-
-### Trends
-
-```{r model1-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-#' Calculate posterior draws for simple effects (by sex and age) for regions and average
-#'
-#' @param x brmsfit model 2
-#' @param h a brmshypothesis
-#'
-#' @return a long tibble of draws of posterior answers to hypothesis
-simple_effects_samples <- function(x, h) {
-  # Calculate hypotheses at average level
-  average_h <- hypothesis(
-    x, h
-  )
-  # Give hypotheses appropriate names
-  average <- average_h$samples
-  names(average) <- interaction(
-    "Average", average_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  # Pivot to long format, note use of dtplyr
-  average <- average %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  # Regions as above
-  region_h <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )
-  region <- region_h$samples
-  names(region) <- interaction(
-    region_h$hypothesis$Group,
-    region_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  region <- region %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  bind_rows(average, region)
-}
-
-#' Posterior summaries of country- region- and average-level effects for the demographic groups
-#'
-#' @param x brmsfit model 2
-#' @param h character vector of hypotheses
-#'
-#' @return
-simple_effects_summary <- function(x, h) {
-
-  # Calculate hypotheses at average level
-  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
-  average$region <- "Average"
-
-  # Regions as above
-  region <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )$hypothesis %>%
-    as_tibble()
-  region <- rename(region, region = Group)
-
-  # Country hypotheses
-  country <- hypothesis(
-    x, h,
-    scope = "ranef", group = "country"
-  )
-  country <- country$hypothesis %>% as_tibble()
-  country <- rename(country, country = Group)
-
-  # Add region coefs
-  country <- left_join(country, distinct(x$data, region, country))
-  region_coef <- region %>%
-    select(region, Hypothesis, r_region = Estimate)
-  country <- country %>%
-    left_join(region_coef) %>%
-    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
-    select(-r_region)
-
-  bind_rows(average, region, country)
-}
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit1, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-### Associations
-
-```{r model2-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-## Other internet metrics
-
-Fixed and mobile broadband subscription analyses
-
-```{r fixed-mobile-formulas}
-bf_2_f <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-
-bf_2_m <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-```
+This figure indicates, for each country's internet trend and outcome trend parameters, the degree of shrinkage.
+That is, the start of each arrow indicates the magnitudes from a simple linear regression for that country.
+The end of the arrow indicates the magnitudes from the multilevel regression model.
+We can then see that especially for countries further away from the overall mean effects, there was considerable shrinkage.
+It is important to keep this in mind when interpreting the country-level parameters.

### 2022-01-10 02-associations.qmd
Split into sections

--- 2021-12-17 index.qmd
@@
----
-title: "Adolescent well-being in the digital age"
-author: "Matti Vuorre"
-execute:
-  enabled: true
-  cache: true
-  warning: false
-  message: false
-format: 
-  html:
-    monofont: Fira Code
-    font-size: 1.0em
-    code-fold: true
-toc: true
-toc-depth: 4
-crossref:
-  fig-prefix: Figure
-  tbl-prefix: Table
----
+# Associations {#sec-associations}
 
-```{r document-options, include = FALSE, cache = FALSE}
-# knitr options
-knitr::opts_chunk$set(
-  fig.align = "center",
-  cache.lazy = FALSE # Fix large knitr cache
-)
-```
-
-## Preface
-
-Welcome!
-This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation).
-It contains all the analyses reported in the manuscript along with supplemental analyses.
-The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).
-
-::: {.callout-note collapse="true"}
-### Reproducibility
-
-The analyses were conducted in R, and can be reproduced locally:
-
-1.  Clone the github repo
-
--   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
--   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
-
-2.  Prepare the R environment
-
--   Terminal: `Rscript -e "renv::restore()`
--   RStudio: Click renv -> Restore Library in the Packages panel
-
-3.  Render `index.qmd` to `index.html`
-
--   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
--   Terminal: `quarto render index.qmd`
--   RStudio: Open `index.qmd` and click Render
-
-The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.
-
-If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
-:::
-
-## Data preparation
-
-Our analyses draw on three sources of data.
-The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
-The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
-And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
-
-In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:
-
-```{r setup, cache = FALSE}
-
+```{r setup}
+#| cache: false
 # Packages
-library(readxl)
-library(knitr)
-library(ragg)
-library(imputeTS)
-library(naniar)
 library(scales)
-library(janitor)
-library(haven)
-library(labelled)
-library(countrycode)
 library(ggtext)
-library(dtplyr)
 library(lubridate)
 library(kableExtra)
-library(gtsummary)
 library(ggstance)
@@
 library(broom)
-library(kableExtra)
 library(tidyverse)
-
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
-nchains <- 4
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = nchains,
-  cores = nchains,
-  threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1000,
-  refresh = 50,
-  adapt_delta = .90,
-  max_treedepth = 10
-)
-
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-#' Custom kableExtra formatting
-#'
-#' @param a table from kbl()
-#'
-#' @return a table
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}
-
-# Create directory for intermediate files
-dir.create("models", FALSE)
 ```
 
-### Gallup World Poll
+```{r load}
+#| cache: false
+# Load data sets
+itu <- read_rds("data/itu.rds")
+gwp <- read_rds("data/gwp.rds")
+gbd <- read_rds("data/gbd.rds")
 
-We first prepare the Gallup data.
-Note that this data set is not publicly available, and therefore not included in our repository.
-We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.
-
-```{r gallup-codebook}
-#| echo: false
-#| eval: false
-# Understand variables & values
-# Codes NOTE 1: yes 2: no!
-read_spss(
-  "data-raw/Gallup/The_Gallup_101521.sav",
-  n_max = 1,
-  col_select = c(
-    WPID, WP1219,
-    WP16,
-    WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74
-  )
-) %>%
-  generate_dictionary()
-```
-
-Here we import the relevant variables from Gallup's SPSS files and then
-
--   Clean the variable names
--   Set appropriate missing values (`NaN`, not e.g. `-99`)
--   Use appropriate coding schemes (e.g. 0: no; 1: yes)
--   Calculate scale scores (means over items)
--   Rescale outcomes to proportions (0 - 1)
--   Subset the data to 15 to 24 year olds
--   Create age-categories in line with GBD data
--   Drop one 13 year old as this data should only have people 15 and older
-
-```{r gallup-clean}
-# First liberate the data from the slow SPSS file and save to disk
-gwp_path <- "data-raw/Gallup/gwp-processed.rds"
-if (!file.exists(gwp_path)) {
-  gwp <- read_spss(
-    "data-raw/Gallup/The_Gallup_101521.sav",
-    col_select = c(
-      YEAR_CALENDAR,
-      COUNTRYNEW,
-      WPID, WP1220, WP1219,
-      WP16,
-      WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
-    )
-  )
-
-  # Get rid of SPSS attributes
-  gwp <- gwp %>%
-    zap_labels() %>%
-    zap_label() %>%
-    zap_widths() %>%
-    zap_formats()
-
-  # Save into a good format
-  write_rds(gwp, gwp_path)
-} else {
-  gwp <- read_rds(gwp_path)
-}
-
-gwp <- gwp %>%
-  clean_names() %>%
-  transmute(
-    country = countrynew,
-    year = year_calendar,
-    id = wpid,
-    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
-    age = wp1220,
-    # Don't know, refused, and missing values
-    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
-    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
-    # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
-  )
-
-# Scale scores note rescaling
-gwp <- gwp %>%
-  mutate(
-    Life_satisfaction = Life_satisfaction / 10,
-    Negative_experiences =
-      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
-    Positive_experiences =
-      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
-  ) %>%
-  select(-c(wp60:wp74))
-
-# Categorize ages
-gwp <- gwp %>%
-  mutate(
-    age = cut(
-      age,
-      breaks = seq(15, 105, by = 5),
-      include.lowest = TRUE,
-      right = FALSE,
-      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
-    ) %>% as.character()
-  )
-
-# There is one 13 year old which resulted in a NA and we drop it
-gwp <- drop_na(gwp, age)
-
-# Focus on young people
-gwp <- gwp %>%
-  filter(age %in% c("15 to 19", "20 to 24"))
-```
-
-Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex).
-Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.
-
-```{r gallup-summarise}
-gwp <- gwp %>%
-  pivot_longer(
-    c(
-      Life_satisfaction,
-      Negative_experiences,
-      Positive_experiences
-    ),
-    names_to = "outcome", values_to = "val"
-  ) %>%
-  group_by(country, year, sex, age, outcome) %>%
-  summarise(
-    se = sd(val, na.rm = TRUE) / sqrt(n()),
-    val = mean(val, na.rm = TRUE)
-  ) %>%
-  ungroup()
-```
-
-We have three data sets with information on countries.
-Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values.
-We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
-We do that here for the GWP data, and check that all countries receive a unique name.
-
-```{r gwp-harmonise-countries}
-#| results: hold
-#| label: tbl-gwp-countries
-#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gwp %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GWP harmonised country names") %>%
-  kable_custom()
-
-# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
-
-# Harmonise old names and replace only if harmonised name found
-gwp <- gwp %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  # Prevent north cyprus from becoming cyprus
-  mutate(
-    country_harmonised = ifelse(
-      country == "Northern Cyprus",
-      "Northern Cyprus",
-      country_harmonised
-    )
-  ) %>%
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### Global Burden of Disease
-
-We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
-We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R.
-They are inside downloaded `.zip` files, of which there may be more than one.
-
-```{r gbd-data-load}
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/",
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>%
-  read_csv()
-```
-
-We then clean the GBD data and
-
--   Clean the variable names
--   Remove the metric and measure variables; we focus on prevalence rate
-    -   prevalence: Total number of cases
-    -   rate: Total cases per 100,000 population
--   Convert outcome rates to proportions (0 - 1)
--   Clean cause names and rename to outcome to harmonise with GWP
--   Convert GBD estimated rate CI limits to an approximate standard error
--   Subset data to young people (10 - 24)
-
-```{r gbd-data-clean}
-# First step is to clean names
-gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
-gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 100000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>%
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>%
-  rename(country = location, outcome = cause)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
-gbd <- gbd %>%
-  mutate(se = (upper - lower) / (1.96 * 2)) %>%
-  select(-c(upper, lower))
-
-# Focus on young people
-gbd <- gbd %>%
-  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
-```
-
-Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.
-
-```{r gbd-harmonise-countries}
-#| results: hold
-#| label: tbl-gbd-countries
-#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GBD harmonised country names") %>%
-  kable_custom()
-# Harmonise old names and replace only if harmonised name found
-gbd <- gbd %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### International Telecommunication Union
-
-After processing the outcome tables above, we move on to the internet adoption metrics from the ITU.
-We downloaded these data files from the ITU website.
-New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
-
-After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1).
-Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.
-
-```{r itu-process}
-#| results: hold
-#| label: tbl-itu-0
-#| tbl-cap: "ITU countries"
-#| layout-ncol: 1
-
-# Download data sets from the ITU website if not yet downloaded
-if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
-  dir.create("data-raw/ITU")
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
-    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
-    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
-    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
-  )
-}
-
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(fixed = as.numeric(value)) %>%
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(mobile = as.numeric(value)) %>%
-  select(country = Country, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(internet = as.numeric(value)) %>%
-  select(country = Country, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
-itu <- itu %>%
-  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-
-# Harmonise countries
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "ITU harmonised country names") %>%
-  kable_custom()
-
-# Harmonise old names and replace only if harmonised name found
-itu <- itu %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Drop countries that don't exist in outcomes
-itu <- itu %>%
-  filter(
-    country %in% unique(gbd$country) | country %in% unique(gwp$country)
-  )
-
-# Drop countries that don't have any actual internet data
-itu_zeros <- itu %>%
-  group_by(country) %>%
-  summarise(s = sum(internet, na.rm = TRUE)) %>%
-  filter(s == 0)
-
-itu <- itu %>%
-  filter(!(country %in% itu_zeros$country))
-rm(itu_zeros)
-```
-
-#### Missingness
-
-We then impute missing intermediate values to the internet adoption timeseries.
-We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.
-
-```{r itu-impute}
-#| results: hold
-#| label: tbl-itu-impute
-#| tbl-cap: "Summary of ITU data imputation"
-
-# Reshape to easily impute all variables
-itu_long <- itu %>%
-  pivot_longer(c(internet, fixed, mobile))
-
-# Impute by country and variable
-itu_long <- itu_long %>%
-  group_by(country, name) %>%
-  # Find first and last year with this variable in each country
-  # so as to prevent extrapolation
-  mutate(
-    min_year = year[min(which(!is.na(value)))],
-    max_year = year[max(which(!is.na(value)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  mutate(
-    across(
-      value,
-      .fns = list(
-        i = possibly(
-          function(x) na_interpolation(x, maxgap = Inf),
-          otherwise = NaN
-        )
-      )
-    )
-  ) %>%
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    value_i = if_else(
-      between(year, unique(min_year), unique(max_year)),
-      value_i,
-      NaN
-    )
-  ) %>%
-  ungroup() %>%
-  select(-min_year, -max_year)
-
-# Summary
-itu_long %>%
-  group_by(name) %>%
-  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
-  summarise(
-    n_miss_orig = sum(is.na(value) & year >= min_year),
-    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
-    n_miss_imp = sum(is.na(value_i) & year >= min_year),
-    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
-    imputed = n_miss_orig - n_miss_imp
-  ) %>%
-  kbl(caption = "ITU data imputation summary") %>%
-  kable_custom()
-
-# We then replace the original values with the imputed ones
-itu <- itu_long %>%
-  # Pick non-missing value, from original and imputed
-  mutate(value = coalesce(value, value_i)) %>%
-  select(-value_i) %>%
-  pivot_wider()
-rm(itu_long)
-```
-
-### GLOBE regions
-
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
-
-```{r globe-regions}
-#| results: hold
-#| label: tbl-globe
-#| tbl-cap: "Countries with manually filled region"
-
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
-) %>%
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>%
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>%
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in GBD not present in region data
-no_region_gbd <- filter(
-  distinct(gbd, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-# Then see what countries in GWP are without region
-no_region_gwp <- filter(
-  distinct(gwp, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-bind_rows(no_region_gbd, no_region_gwp) %>%
-  arrange(country) %>%
-  distinct() %>%
-  write_csv("data-raw/Regions/countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/countries-without-region-filled.csv"
-)
-
-# Combine Jebb et al GLOBE regions and our manually added ones
-regions <- regions %>%
-  bind_rows(
-    regions_filled %>%
-      mutate(Note = "Filled")
-  ) %>%
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>%
-  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))
-
-# Display table of regions and countries
-regions %>%
-  drop_na(Note) %>%
-  select(-Note) %>%
-  arrange(region, country) %>%
-  kbl(caption = "Countries with a manually filled region") %>%
-  kable_custom()
-
-# Clean region labels
-regions$region <- str_replace_all(regions$region, " ", "_")
-regions$region <- factor(regions$region)
-
-# Remove unnecessary items
-regions <- select(regions, -Note)
-
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-gwp <- left_join(gwp, regions)
-# Remove now unnecessary variables
-rm(no_region_gbd, no_region_gwp, regions_filled, regions)
-```
-
-### ITU summary table
-
-```{r itu-summary-table}
-#| column: page
-#| tbl-cap: "Mean internet user percentages across regions and time."
-#| label: tbl-itusummary
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-```
-
-## RQ1: Time courses
-
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
-To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.
-
-### Modelling
-
-We first prepare the variables for modelling:
-
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
--   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
-
-```{r model1-prepare-data}
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center and scale year
-dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in mv models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
-  ungroup()
-
-# Ensure that factors are contrast coded
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
-
-# Arrange on outcome
+# Load models
 oo <- c(
@@
 )
-dat <- dat %>%
+fits <- tibble(outcome = oo) %>% 
   mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(dat, outcome, region, country, year)
-
-dat %>%
-  group_by(outcome) %>%
-  summarise(
-    min = min(val, na.rm = TRUE),
-    max = max(val, na.rm = TRUE),
-    internet_min = min(internet, na.rm = TRUE),
-    internet_max = max(internet, na.rm = TRUE)
-  ) %>%
-  kable(digits = 7) %>% 
-  kable_custom()
-```
-
-#### Specification
-
-We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b).
-Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g.
-Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries.
-We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)
-
-We fit the model separately for each outcome.
-Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret).
-We therefore estimate six separate bivariate models
-
-In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.
-All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes.
-This latter specification is important to allow answering RQ1b.
-
-The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate.
-For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age).
-The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data.
-Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.
-
-We write the model as
-
-$$
-\begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
-\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
-\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
-x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
-\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
-\left[\begin{array}{c}
-\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
-\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
-\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
-\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
+  mutate(
+    fit1 = map(
+      outcome, 
+      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
     ),
-\left[\begin{array}{c}
-\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
-\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
-\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
-\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}
-$$
-
-Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.
-
-We then define the model formulas in brms' formula syntax.
-First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
-To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model.
-The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).
-
-```{r model1-itu-bf}
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~
-  year +
-    (year |c| country) +
-    (year |r| region),
-  family = Beta()
-)
-```
-
-Here, we specify the outcome model.
-Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
-Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
-In addition, it leads to the residual variance to be estimated.
-
-```{r model1-val-bf}
-# Meta-regression model of outcomes
-bf_1 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
-  family = gaussian()
-)
-```
-
-Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged.
-We therefore effectively removed the SEs from self-harm by setting them to zero
-
-```{r model1-selfharm-se}
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
-
-#### Fitting
-
-We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.
-
-```{r fit-model-1}
-fits <- dat %>%
-  # Could nest but need this to include group key in nested tibble
-  group_by(outcome) %>%
-  summarise(data = list(cur_data_all()))
-
-fits <- fits %>%
-  mutate(
-    fit1 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE),
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-1-internet")
-      )
+    fit2 = map(
+      outcome, 
+      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
     )
@@
 
-#### Summary
+We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption? To answer, we investigate the results of Model 2.
 
-Here is a summary of the data modelled for each outcome
-
-```{r model-1-data-summary}
-#| column: body-outset
-#| tbl-cap: "Summaries of data included in Model 1"
-#| label: tbl-m1-data
-
-#' Model summary
-#'
-#' @param x a brmsfit
-#'
-#' @return A tibble with information on data in the model
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
-
-fits %>%
-  mutate(summary = map(fit1, msum)) %>%
-  select(outcome, summary) %>%
-  unnest(summary) %>%
-  kbl(caption = "Model 1 data summary") %>%
-  kable_custom() %>% 
-  row_spec(0, bold = TRUE)
-```
-
-#### Model checking
-
-Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section
-
-##### MCMC diagnostics
-
-First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.
-
-We can see that the models have converged nicely, apart from the self-harm outcome.
-
-```{r model-1-diagnostics}
-#| results: hold
-#| label: tab-model1-diagnostic
-#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
-#| column: body-outset
-
-diagnostic_table <- function(fit, rx, cp) {
-  diag_1 <- fits %>%
-    select(fit = {{ fit }}, outcome) %>% 
-    mutate(
-      out =
-        map(
-          fit,
-          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
-            summarise_draws(samples = length, default_convergence_measures())
-        )
-    ) %>%
-    select(outcome, out) %>%
-    unnest(out)
-  diag_1 %>%
-    kbl(
-      caption = cp,
-      digits = c(0, 0, 0, 2, 0, 0)
-    ) %>%
-    column_spec(
-      4,
-      color = "white",
-      background = spec_color(
-        log(diag_1$rhat),
-        direction = 1,
-        option = "C",
-        end = .6
-      )
-    ) %>%
-    column_spec(
-      c(5, 6),
-      color = "white",
-      background = spec_color(
-        log(diag_1$ess_tail / diag_1$samples),
-        direction = 1,
-        option = "C",
-        end = 0,
-        begin = .6
-      )
-    ) %>%
-    kable_custom()
-}
-diagnostic_table(
-  fit1,
-  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
-  cp = "Model 1 MCMC diagnostics."
-) %>% 
-  scroll_box(height = "300px")
-```
-
-##### Posterior predictive check
-
-We then take a coarse look at how well the models reproduce the input data.
-
-```{r ppcheck-density}
-#| column: page
-#| fig-cap: "Graphical posterior predictive check by region (Model 1).
-Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g.
-Anglo Depression)."
-#| label: fig-ppcheck-1
-
-ppcheck_1 <- fits %>%
-  group_by(outcome) %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ pp_check(
-        .x,
-        ndraws = 10,
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val",
-        newdata = .x$data
-      )[[1]]
-    )
-  ) %>%
-  ungroup() %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-ppcheck_1 %>%
-  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
-  scale_color_brewer(palette = "Set1") +
-  scale_alpha_manual(values = c(.2, 1)) +
-  stat_density(
-    geom = "line",
-    size = .75,
-    position = position_identity()
-  ) +
-  labs(x = "Value", y = "Density") +
-  facet_grid2(
-    outcome ~ group,
-    scales = "free", independent = "x",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title = element_blank(),
-    axis.text = element_blank(),
-    axis.ticks = element_blank()
-  )
-rm(ppcheck_1)
-```
-
-### Results
-
-#### RQ1a: Temporal trends
-
-Before presenting the time trends, we must calculate the required quantities from the posterior distribution.
-Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.
-
-```{r calculate-simple-effects}
-#' Posterior draws at average and region levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = "region")
-}
-
-#' Posterior summaries at country- region- and average levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
-    select(-r_value)
-
-  bind_rows(
-    psum_region,
-    psum_country
-  ) %>%
-    mutate(region = fct_relevel(region, "Average"))
-}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit1, pdraws)) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums <- fits %>%
-  mutate(psums = map(fit1, psums)) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums_internet <- fits %>%
-  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-```
-
-We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions.
-Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).
-
-```{r forest-trends}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes"
-#| label: fig-forest-trends
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-```
-
-@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction.
-This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade.
-The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.
-
-Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data.
-This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes.
-Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.
-
-We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region.
-However, the average change again is not credibly different from zero.
-Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety.
-Depression and self-harm, on the other hand, had decreased across the board.
-
-In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.
-
-Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.
-
-```{r fitted-trend-country}
-
-#' Get (grand mean) fitted values for countries
-#'
-#' @param x a brmsfit model 1
-#'
-#' @return a data frame of fitted values
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
-    summarise(val = mean(val, na.rm = TRUE)) %>%
-    ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
-  newy <- bind_cols(
-    newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit1, fitted_country)) %>%
-  select(outcome, fc)
-
-#' Draw a panel plot of countries' fitted values and data
-#'
-#' @param x fitted country level data from fitted_country()
-#' @param y outcome
-#'
-#' @return a ggplot for that outcome
-plot_country <- function(x, y) {
-  coefs <- p_sums %>%
-    drop_na(country) %>%
-    filter(outcome == y) %>%
-    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
-    mutate(country = fct_reorder(country, coef))
-  x %>%
-    left_join(coefs) %>%
-    mutate(country = fct_reorder(country, coef)) %>%
-    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
-    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
-    scale_y_continuous(
-      str_replace(y, "_", " "),
-      breaks = pretty_breaks(),
-      expand = expansion(.15),
-      labels = function(x) {
-        percent(x / 100, .01) %>%
-          str_remove("\\.00")
-      }
-    ) +
-    # Add parameters in text
-    geom_richtext(
-      data = coefs %>%
-        mutate(across(where(is.numeric), ~ number(., .01))),
-      aes(
-        x = make_date(2000), y = Inf,
-        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
-      ),
-      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
-      family = Font,
-      fill = alpha("white", .3), label.color = NA,
-      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
-    ) +
-    geom_point(aes(y = val), shape = 1, alpha = .5) +
-    geom_ribbon(
-      aes(ymin = Q2.5, ymax = Q97.5),
-      alpha = .3, col = NA, fill = "dodgerblue1"
-    ) +
-    geom_line(
-      size = 0.5, col = "dodgerblue1"
-    ) +
-    facet_wrap(
-      "country"
-    ) +
-    theme(panel.spacing = unit(2, "pt"))
-}
-
-# Create the plot for each outcome
-f_country <- f_country %>%
-  mutate(
-    plot = map2(
-      fc, outcome,
-      ~ plot_country(.x, .y)
-    )
-  )
-```
-
-::: {.panel-tabset .column-screen-inset-shaded}
-##### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-##### Life satisfaction
-
-```{r trends-ls}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
-#| label: fig-trends-ls
-f_country$plot[[1]]
-```
-
-##### Negative experiences
-
-```{r trends-ne}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Negative experiences trends, ordered by association magnitude"
-#| label: fig-trends-ne
-f_country$plot[[2]]
-```
-
-##### Positive experiences
-
-```{r trends-pe}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Positive experiences trends, ordered by association magnitude"
-#| label: fig-trends-pe
-f_country$plot[[3]]
-```
-
-##### Anxiety
-
-```{r trends-anx}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Anxiety trends, ordered by association magnitude"
-#| label: fig-trends-anx
-f_country$plot[[4]]
-```
-
-##### Depression
-
-```{r trends-dep}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Depression trends, ordered by association magnitude"
-#| label: fig-trends-dep
-f_country$plot[[5]]
-```
-
-##### Self-harm
-
-```{r trends-sel}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Self-harm trends, ordered by association magnitude"
-#| label: fig-trends-sel
-f_country$plot[[6]]
-```
-:::
-
-#### RQ1b: Correlations
-
-We then turned to research question 1b: To what extent were changes in well-being and internet adoption correlated across countries.
-
-To investigate we examined the correlations between $\gamma^y_1$ and $\gamma^x_1$ ($\sigma_{\gamma^y_1,\gamma^x_1}$ in $\Sigma^{\text{c}}$).
-A positive correlation would indicate that countries with greater increases in internet adoption between 2000 and 2020 would tend to have greater increases in $y$ (e.g.
-Life satisfaction).
-
-To answer, we display $\sigma_{\gamma^y_1,\gamma^x_1}$ from each outcome's model in the figure below.
-The figures are scatterplots of country-level trend coefficients, where each point's x-y coordinate indicate their trend magnitudes.
-The overlaid ellipses are the model's 95% predictive limits for $\gamma^y_1$ and $\gamma^x_1$.
-
-```{r scatterplot-time-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of country-level internet and outcome trends."
-#| label: fig-trend-scatterplot
-
-# Correlation parameters
-cor_pars <- fits %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        variable = "cor_country__internet_year__val_year"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-# Ellipses
-ellipses <- fits %>%
-  mutate(
-    ellipse = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        c(
-          "b_val_year",
-          "b_internet_year",
-          "sd_country__val_year",
-          "sd_country__internet_year",
-          "cor_country__internet_year__val_year"
-        )
-      ) %>%
-        slice_sample(n = 100) %>%
-        rename(
-          cor = cor_country__internet_year__val_year,
-          sd_outcome = sd_country__val_year,
-          sd_i = sd_country__internet_year,
-          b_outcome = b_val_year,
-          b_i = b_internet_year
-        ) %>%
-        mutate(
-          e = pmap(
-            list(cor, sd_outcome, sd_i, b_outcome, b_i),
-            function(cor, sd_a, sd_i, b_a, b_i) {
-              ellipse(
-                cor,
-                scale = c(sd_i, sd_outcome),
-                centre = c(b_i, b_outcome),
-                level = .95
-              ) %>%
-                as_tibble()
-            }
-          )
-        ) %>%
-        unnest(e)
-    )
-  )
-ellipses <- ellipses %>%
-  select(outcome, ellipse) %>%
-  unnest(ellipse)
-
-# Wide tibble of parameters
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_path(
-    data = ellipses,
-    aes(x = x, y = y, group = .draw),
-    alpha = .2, size = .1, col = "dodgerblue2"
-  ) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_text(
-    data = cor_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-#### Other results from Model 1
-
-##### Shrinkage
-
-It's important to note that at the level of countries and regions, the model parameters refer to country^\*^ and region^\*^, that is as they are in the sample of other countries and regions.
-This modelling strategy is important because it allows describing the parameters at each level while adjusting the values toward the group means (preventing "false alarms").
-However it is then important to examine those values against their "fixed effect" counterparts, which we do here.
-
-```{r shrinkage}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of multilevel and independent model coefficients"
-#| label: fig-trend-shrinkage
-
-lm_coefs <- fits %>%
-  mutate(
-    data = map(fit1, ~ as_tibble(.x$data))
-  ) %>%
-  mutate(
-    fit_val = map(
-      data,
-      ~ tidy(
-        lm(val ~ 0 + country + year:country, data = .x)
-      )
-    ),
-    fit_internet = map(
-      data,
-      ~ tidy(
-        gam(
-          internet ~ 0 + country + year:country,
-          family = betar, data = .x %>%
-            filter(itu)
-        ),
-        parametric = TRUE
-      )
-    )
-  )
-lm_coefs <- lm_coefs %>%
-  select(outcome, fit_val, fit_internet) %>%
-  pivot_longer(c(fit_val, fit_internet)) %>%
-  mutate(name = str_remove(name, "fit_")) %>%
-  unnest(value) %>%
-  select(outcome, name, term, estimate, std.error) %>%
-  filter(str_detect(term, ":")) %>%
-  mutate(term = str_remove(term, "country")) %>%
-  mutate(term = str_remove(term, ":year")) %>%
-  pivot_wider(names_from = name, values_from = c(estimate, std.error)) %>%
-  rename(country = term)
-
-# Plot
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  left_join(lm_coefs) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate, col = region)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_segment(
-    aes(
-      x = estimate_internet, xend = Internet_Estimate,
-      y = estimate_val, yend = Outcome_Estimate
-    ),
-    arrow = arrow(type = "closed", length = unit(3, "pt")),
-    size = .25, show.legend = FALSE
-  ) +
-  geom_point(size = 1.1, alpha = .4) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  guides(
-    color = guide_legend(override.aes = list(size = 2, alpha = 1))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "bottom"
-  )
-```
-
-## RQ2: Associations
-
-We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption?
-To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes.
-Before modelling, we calculated these quantities as shown in this code block.
-
-```{r model2-data-prepare}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(outcome, region, country, year) %>%
-  group_by(outcome, region, country, sex, age) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-dat <- dat %>%
-  group_by(outcome, country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  group_by(outcome) %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-```
-
-### Specification and fitting
-
-Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions
-
-$$\begin{align*}
-y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\
-
-\mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
-\gamma_{0\text{country}[i]} + \\ &(\beta_{1} + \delta_{1\text{region}[i]} + \gamma_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta_{2} + \delta_{2\text{region}[i]} + \gamma_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta_{3} + \delta_{3\text{region}[i]} + \gamma_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta_{4} + \delta_{4\text{region}[i]} + \gamma_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta_{5} + \delta_{5\text{region}[i]} + \gamma_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i +
-\\ &(\beta_{6} + \delta_{6\text{region}[i]} + \gamma_{6\text{country}[i]})\text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\
-
-\left[\begin{array}{c}
-\delta_{0\text{region}} \\ \delta_{1\text{region}} \\ 
-\delta_{2\text{region}} \\ \delta_{3\text{region}} \\ 
-\delta_{4\text{region}} \\ \delta_{5\text{region}} \\ 
-\delta_{6\text{region}} \\ \delta_{7\text{region}} \\ 
-\delta_{8\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\ 
-\gamma_{4\text{country}} \\ \gamma_{5\text{country}} \\ 
-\gamma_{6\text{country}} \\ \gamma_{7\text{country}} \\ 
-\gamma_{8\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}$$
-
-```{r fit-model-2}
-
-# Model formula is only a small update to Model 1
-bf_2 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-# As above with model 1
-fits <- fits %>%
-  mutate(
-    fit2 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-internet")
-      )
-    )
-  )
-```
-
-### Results
+## Model comparison
 
@@
 #| label: tbl-m12-r2
+
 fits %>%
@@
   kable_custom()
+fits <- select(fits, -fit1)
 ```
 
-Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.
+## Forest plot
 
-```{r model2-calculate-coefficients}
+We then display summaries of the parameters' posterior distributions as forest plots, like above.
+Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
+
+```{r forest-internet}
+#| column: screen-inset-right
+#| fig-width: 13
+#| fig-height: 8
+#| fig-cap: "Forest plot of internet associations"
+#| label: fig-forest-internet
+
+# Calculate parameters at all levels of analysis
 p_draws <- fits %>%
@@
   unnest(pdraws)
-
 p_sums <- fits %>%
@@
   unnest(psums)
-
 p_draws <- p_draws %>%
@@
   mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-```
 
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
-
-```{r forest-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
 p_draws %>%
@@
 
+## Counterfactual plot
+
 To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
@@
 ```{r model2-fitted-values}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
+#| column: screen-inset-right
+#| fig-width: 13
+#| fig-height: 8
 #| fig-cap: "Counterfactual plot of internet associations"
@@
 
-### Other results from Model 2
+## Between-country associations
 
@@
 ```{r}
-#| column: page
+#| column: page-right
 #| fig.width: 8
@@
 ```
-
-## RQ3: Demographics
-
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
-
-### Trends
-
-```{r model1-demographics}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes by demographic group"
-#| label: fig-forest-trends-demo
-h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-#' Calculate posterior draws for simple effects (by sex and age) for regions and average
-#'
-#' @param x brmsfit model 2
-#' @param h a brmshypothesis
-#'
-#' @return a long tibble of draws of posterior answers to hypothesis
-simple_effects_samples <- function(x, h) {
-  # Calculate hypotheses at average level
-  average_h <- hypothesis(
-    x, h
-  )
-  # Give hypotheses appropriate names
-  average <- average_h$samples
-  names(average) <- interaction(
-    "Average", average_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  # Pivot to long format, note use of dtplyr
-  average <- average %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  # Regions as above
-  region_h <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )
-  region <- region_h$samples
-  names(region) <- interaction(
-    region_h$hypothesis$Group,
-    region_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  region <- region %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  bind_rows(average, region)
-}
-
-#' Posterior summaries of country- region- and average-level effects for the demographic groups
-#'
-#' @param x brmsfit model 2
-#' @param h character vector of hypotheses
-#'
-#' @return
-simple_effects_summary <- function(x, h) {
-
-  # Calculate hypotheses at average level
-  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
-  average$region <- "Average"
-
-  # Regions as above
-  region <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )$hypothesis %>%
-    as_tibble()
-  region <- rename(region, region = Group)
-
-  # Country hypotheses
-  country <- hypothesis(
-    x, h,
-    scope = "ranef", group = "country"
-  )
-  country <- country$hypothesis %>% as_tibble()
-  country <- rename(country, country = Group)
-
-  # Add region coefs
-  country <- left_join(country, distinct(x$data, region, country))
-  region_coef <- region %>%
-    select(region, Hypothesis, r_region = Estimate)
-  country <- country %>%
-    left_join(region_coef) %>%
-    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
-    select(-r_region)
-
-  bind_rows(average, region, country)
-}
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit1, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-### Associations
-
-```{r model2-demographics}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of associations by demographic group"
-#| label: fig-forest-association-demo
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-## Other internet metrics
-
-Fixed and mobile broadband subscription analyses
-
-```{r fixed-mobile-formulas}
-bf_2_f <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-
-bf_2_m <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-```

### 2022-01-10 03-demographics.qmd
Split into sections

## Demographics

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(dtplyr)
library(tidyverse)
```

```{r}
# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit1 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
    ),
    fit2 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
    )
  )
```

We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents? To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations. In this section, we present results based on the moderated effects.

### Trends

```{r model1-demographics}
#| column: screen-inset-right
#| fig-width: 12
#| fig-height: 8
#| fig-cap: "Forest plot of linear trends in outcomes by demographic group"
#| label: fig-forest-trends-demo
h_gwp <- c(
  `15 to 19` =
    "val_year + val_year:age1 * 1 = 0",
  `20 to 24` =
    "val_year + val_year:age1 * -1 = 0",
  `Female` =
    "val_year + val_year:sex1 * 1 = 0",
  `Male` =
    "val_year + val_year:sex1 * -1 = 0"
)
h_gbd <- c(
  `10 to 14` =
    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
  `15 to 19` =
    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
  `20 to 24` =
    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
  `Female` =
    "val_year + val_year:sex1 * 1 = 0",
  `Male` =
    "val_year + val_year:sex1 * -1 = 0"
)

sexage_draws <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    samples = map2(
      fit1, h,
      ~ simple_effects_samples(.x, .y)
    )
  ) %>%
  select(outcome, samples) %>%
  unnest(samples)
sexage_sums <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    sums = map2(
      fit1, h,
      ~ simple_effects_summary(.x, .y)
    )
  ) %>%
  select(outcome, sums) %>%
  unnest(sums)

sexage_draws <- sexage_draws %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(is_average = region == "Average") %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(
    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
  )

sexage_sums <- sexage_sums %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(region = fct_relevel(region, "Average"))

# Plot averages and regions
sexage_draws %>%
  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
  scale_color_brewer(
    "Group",
    palette = "Dark2",
    aesthetics = c("fill", "color")
  ) +
  scale_alpha_manual(values = c(.4, .8), guide = "none") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19), guide = "none") +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Estimated linear change per decade",
    breaks = pretty_breaks(3),
    labels = function(x) {
      percent(x / 100, .01) %>%
        str_remove("\\.00") %>%
        str_remove("(?<=[0-9])0")
    },
    expand = expansion(c(-.05, -.05))
  ) +
  stat_halfeye(
    point_interval = mean_qi, normalize = "xy",
    height = 1, alpha = .5, point_fill = "white",
    .width = .95, interval_alpha = 1, interval_size = .2,
    point_alpha = 1, point_size = 1.5, stroke = .5,
    aes(
      shape = after_stat(xmin > 0 | xmax < 0)
    ),
    position = position_dodge(.8),
    key_glyph = draw_key_point
  ) +
  guides(
    color = guide_legend(
      override.aes = list(size = 3, alpha = 1),
      nrow = 2, ncol = 3, byrow = TRUE
    ),
    fill = guide_legend(
      nrow = 2, ncol = 3, byrow = TRUE
    )
  ) +
  # Add country points
  # geom_point(
  #   data = sexage_sums %>%
  #     drop_na(country) %>%
  #     mutate(is_average = TRUE),
  #   aes(
  #     x = Estimate,
  #     shape = CI.Lower > 0 | CI.Upper < 0,
  #     group = interaction(country, Hypothesis),
  #     ),
  #   position = position_dodgev(.7),
  #   size = .5, alpha = .3
  # ) +
  facet_wrap(
    "outcome",
    scales = "free_x", nrow = 1,
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "bottom"
  )
```

### Associations

```{r model2-demographics}
#| column: screen-inset-right
#| fig-width: 12
#| fig-height: 8
#| fig-cap: "Forest plot of associations by demographic group"
#| label: fig-forest-association-demo
h_gwp <- c(
  `15 to 19` =
    "i1_cw + age1:i1_cw * 1 = 0",
  `20 to 24` =
    "i1_cw + age1:i1_cw * -1 = 0",
  `Female` =
    "i1_cw + sex1:i1_cw * 1 = 0",
  `Male` =
    "i1_cw + sex1:i1_cw * -1 = 0"
)
h_gbd <- c(
  `10 to 14` =
    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
  `15 to 19` =
    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
  `20 to 24` =
    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
  `Female` =
    "i1_cw + sex1:i1_cw * 1 = 0",
  `Male` =
    "i1_cw + sex1:i1_cw * -1 = 0"
)

sexage_draws <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    samples = map2(
      fit2, h,
      ~ simple_effects_samples(.x, .y)
    )
  ) %>%
  select(outcome, samples) %>%
  unnest(samples)
sexage_sums <- fits %>%
  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
  mutate(
    sums = map2(
      fit2, h,
      ~ simple_effects_summary(.x, .y)
    )
  ) %>%
  select(outcome, sums) %>%
  unnest(sums)

sexage_draws <- sexage_draws %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(is_average = region == "Average") %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(
    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
  )

sexage_sums <- sexage_sums %>%
  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
  mutate(region = fct_relevel(region, "Average"))

# Plot averages and regions
sexage_draws %>%
  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
  scale_color_brewer(
    "Group",
    palette = "Dark2",
    aesthetics = c("fill", "color")
  ) +
  scale_alpha_manual(values = c(.4, .8), guide = "none") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19), guide = "none") +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome",
    breaks = pretty_breaks(3),
    labels = function(x) {
      percent(x / 100, .01) %>%
        str_remove("\\.00") %>%
        str_remove("(?<=[0-9])0")
    },
    expand = expansion(c(-.05, -.05))
  ) +
  stat_halfeye(
    point_interval = mean_qi, normalize = "xy",
    height = 1, alpha = .5, point_fill = "white",
    .width = .95, interval_alpha = 1, interval_size = .2,
    point_alpha = 1, point_size = 1.5, stroke = .5,
    aes(
      shape = after_stat(xmin > 0 | xmax < 0)
    ),
    position = position_dodge(.8),
    key_glyph = draw_key_point
  ) +
  guides(
    color = guide_legend(
      override.aes = list(size = 3, alpha = 1),
      nrow = 2, ncol = 3, byrow = TRUE
    ),
    fill = guide_legend(
      nrow = 2, ncol = 3, byrow = TRUE
    )
  ) +
  # Add country points
  # geom_point(
  #   data = sexage_sums %>%
  #     drop_na(country) %>%
  #     mutate(is_average = TRUE),
  #   aes(
  #     x = Estimate,
  #     shape = CI.Lower > 0 | CI.Upper < 0,
  #     group = interaction(country, Hypothesis),
  #     ),
  #   position = position_dodgev(.7),
  #   size = .5, alpha = .3
  # ) +
  facet_wrap(
    "outcome",
    scales = "free_x", nrow = 1,
    labeller = as_labeller(~ str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "bottom"
  )
```

### 2022-01-10 04-fixed-mobile.qmd
Split into sections

# Other internet metrics

In this section we reproduce Model 2 results from @sec-associations but instead of using the ITU internet user proportions, we look at fixed and mobile broadband subscription percentages as predictors.

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(tidyverse)
```

```{r}
# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fitf = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-fixed.rds"))
    ),
    fitm = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-mobile.rds"))
    )
  )
```

## Data figures

```{r}
itu %>% 
  select(-internet) %>% 
  rename(Fixed = fixed, Mobile = mobile) %>% 
  pivot_longer(c(Fixed, Mobile)) %>% 
  # filter(value < 2) %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, value)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "5 years",
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = country),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(
    name ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title.y = element_blank()
  )
```

## Fixed broadband

### Forest plot

```{r}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of internet associations"
#| label: fig-forest-fixed

# Calculate parameters at all levels of analysis
p_draws <- fits %>%
  mutate(pdraws = map(fitf, ~pdraws(.x, "f1_cw"))) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws)
p_sums <- fits %>%
  mutate(psums = map(fitf, ~psums(.x, "f1_cw"))) %>%
  select(outcome, psums) %>%
  unnest(psums)
p_draws <- p_draws %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
p_sums <- p_sums %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))

p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in fixed broadband subscriptions",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

### Between-country associations

```{r}
#| column: page-right
#| fig.width: 8
#| fig.height: 6
#| fig-cap: "Between-country associations"
#| label: fig-cb1-fixed

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region, country) %>%
    summarise(f1_cb = unique(f1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(f1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NA
        )
    )
  ) %>%
    select(-outcome)
  newy
}
tmp <- fits %>% 
  mutate(out = map(fitf, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

cb1_pars <- fits %>%
  mutate(
    out = map(
      fitf,
      ~ as_draws_df(
        .x,
        variable = "b_f1_cb"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(f1_cb, val)) +
  scale_x_continuous(
    "Between-country centered fixed broadband subscriptions",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

## Mobile broadband

### Forest plot

```{r}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of internet associations"
#| label: fig-forest-mobile

# Calculate parameters at all levels of analysis
p_draws <- fits %>%
  mutate(pdraws = map(fitm, ~pdraws(.x, "m1_cw"))) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws)
p_sums <- fits %>%
  mutate(psums = map(fitm, ~psums(.x, "m1_cw"))) %>%
  select(outcome, psums) %>%
  unnest(psums)
p_draws <- p_draws %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
p_sums <- p_sums %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))

p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in mobile broadband subscriptions",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
```

### Between-country associations

```{r}
#| column: page-right
#| fig.width: 8
#| fig.height: 6
#| fig-cap: "Between-country associations"
#| label: fig-cb1-mobile

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region, country) %>%
    summarise(m1_cb = unique(m1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(m1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NA
        )
    )
  ) %>%
    select(-outcome)
  newy
}
tmp <- fits %>% 
  mutate(out = map(fitm, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

cb1_pars <- fits %>%
  mutate(
    out = map(
      fitm,
      ~ as_draws_df(
        .x,
        variable = "b_m1_cb"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(m1_cb, val)) +
  scale_x_continuous(
    "Between-country centered mobile broadband subscriptions",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

### 2022-01-10 index.qmd
Split into sections

--- 2021-12-17 index.qmd
@@
----
-title: "Adolescent well-being in the digital age"
-author: "Matti Vuorre"
-date: "`r Sys.time()`"
-execute:
-  eval: true
-  error: true
-  cache: true
-  warning: false
-  message: false
-format: 
-  html:
-    monofont: Fira Code
-    font-size: 1.0em
-    linestretch: 1.4
-    code-fold: true
-    code-summary: "Show code"
-    code-tools: true
-    code-link: true
-toc: true
-toc-depth: 4
-toc-title: Contents
-number-sections: false
-crossref:
-  fig-prefix: Figure
-  tbl-prefix: Table
----
-
-```{r document-options, include = FALSE, cache = FALSE}
-# knitr options
-knitr::opts_chunk$set(
-  fig.align = "center",
-  cache.lazy = FALSE # Fix large knitr cache
-)
-```
-
-## Preface
+# Preface {.unnumbered}
 
@@
 It contains all the analyses reported in the manuscript along with supplemental analyses.
-The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).
+The data and source code repository, along with the datasets, are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
 
-::: {.callout-note collapse="true"}
-### Reproducibility
+::: {.callout-note}
+### How to reproduce our results
 
@@
 1. Clone the github repo
-
   - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
+      OR
   - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
@@
 2. Prepare the R environment
-
--   Terminal: `Rscript -e "renv::restore()`
+  - Terminal: `Rscript -e "renv::restore()"`  
+      OR
   - RStudio: Click renv -> Restore Library in the Packages panel
 
-3.  Render `index.qmd` to `index.html`
+3. Render the source files to a Quarto book
+ - Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
+  - Terminal: `quarto render`  
+      OR
+  - RStudio: Open the project (`global-wbmh.Rproj`) and click Render in the Build panel
 
--   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
--   Terminal: `quarto render index.qmd`
--   RStudio: Open `index.qmd` and click Render
-
-The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.
-
-If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
+::: {.callout-important}
+The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
+**The models take several hours each to run**---depending on your local computing resources---and therefore the rendering process can take several days.
+For this reason it might be easier to run the individual `.qmd` files interactively in RStudio.
 :::
 
-## Data preparation
-
-Our analyses draw on three sources of data.
-The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.
-The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.
-And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.
-
-In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:
-
-```{r setup, cache = FALSE}
-
-# Packages
-library(readxl)
-library(knitr)
-library(ragg)
-library(imputeTS)
-library(naniar)
-library(scales)
-library(janitor)
-library(haven)
-library(labelled)
-library(countrycode)
-library(ggtext)
-library(dtplyr)
-library(lubridate)
-library(kableExtra)
-library(gtsummary)
-library(ggstance)
-library(mgcv)
-library(brms)
-library(cmdstanr)
-library(ellipse)
-library(ggh4x)
-library(tidybayes)
-library(ggdist)
-library(posterior)
-library(parameters)
-library(emmeans)
-library(broom)
-library(kableExtra)
-library(tidyverse)
-
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
-nchains <- 4
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = nchains,
-  cores = nchains,
-  threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1000,
-  refresh = 50,
-  adapt_delta = .90,
-  max_treedepth = 10
-)
-
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
-theme_set(
-  theme_linedraw(
-    base_size = 12,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
-    )
-)
-
-# Format tables
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}
-
-# Create directory for intermediate files
-dir.create("models", FALSE)
-```
-
-### Gallup World Poll
-
-We first prepare the Gallup data.
-Note that this data set is not publicly available, and therefore not included in our repository.
-We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.
-
-```{r gallup-codebook}
-#| echo: false
-#| eval: false
-# Understand variables & values
-# Codes NOTE 1: yes 2: no!
-read_spss(
-  "data-raw/Gallup/The_Gallup_101521.sav",
-  n_max = 1,
-  col_select = c(
-    WPID, WP1219,
-    WP16,
-    WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74
-  )
-) %>%
-  generate_dictionary()
-```
-
-Here we import the relevant variables from Gallup's SPSS files and then
-
--   Clean the variable names
--   Set appropriate missing values (`NaN`, not e.g. `-99`)
--   Use appropriate coding schemes (e.g. 0: no; 1: yes)
--   Calculate scale scores (means over items)
--   Rescale outcomes to proportions (0 - 1)
--   Subset the data to 15 to 24 year olds
--   Create age-categories in line with GBD data
--   Drop one 13 year old as this data should only have people 15 and older
-
-```{r gallup-clean}
-# First liberate the data from the slow SPSS file and save to disk
-gwp_path <- "data-raw/Gallup/gwp-processed.rds"
-if (!file.exists(gwp_path)) {
-  gwp <- read_spss(
-    "data-raw/Gallup/The_Gallup_101521.sav",
-    col_select = c(
-      YEAR_CALENDAR,
-      COUNTRYNEW,
-      WPID, WP1220, WP1219,
-      WP16,
-      WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
-    )
-  )
-
-  # Get rid of SPSS attributes
-  gwp <- gwp %>%
-    zap_labels() %>%
-    zap_label() %>%
-    zap_widths() %>%
-    zap_formats()
-
-  # Save into a good format
-  write_rds(gwp, gwp_path)
-} else {
-  gwp <- read_rds(gwp_path)
-}
-
-gwp <- gwp %>%
-  clean_names() %>%
-  transmute(
-    country = countrynew,
-    year = year_calendar,
-    id = wpid,
-    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
-    age = wp1220,
-    # Don't know, refused, and missing values
-    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
-    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
-    # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
-  )
-
-# Scale scores note rescaling
-gwp <- gwp %>%
-  mutate(
-    Life_satisfaction = Life_satisfaction / 10,
-    Negative_experiences =
-      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
-    Positive_experiences =
-      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
-  ) %>%
-  select(-c(wp60:wp74))
-
-# Categorize ages
-gwp <- gwp %>%
-  mutate(
-    age = cut(
-      age,
-      breaks = seq(15, 105, by = 5),
-      include.lowest = TRUE,
-      right = FALSE,
-      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
-    ) %>% as.character()
-  )
-
-# There is one 13 year old which resulted in a NA and we drop it
-gwp <- drop_na(gwp, age)
-
-# Focus on young people
-gwp <- gwp %>%
-  filter(age %in% c("15 to 19", "20 to 24"))
-```
-
-Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex).
-Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.
-
-```{r gallup-summarise}
-gwp <- gwp %>%
-  pivot_longer(
-    c(
-      Life_satisfaction,
-      Negative_experiences,
-      Positive_experiences
-    ),
-    names_to = "outcome", values_to = "val"
-  ) %>%
-  group_by(country, year, sex, age, outcome) %>%
-  summarise(
-    se = sd(val, na.rm = TRUE) / sqrt(n()),
-    val = mean(val, na.rm = TRUE)
-  ) %>%
-  ungroup()
-```
-
-We have three data sets with information on countries.
-Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values.
-We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`.
-We do that here for the GWP data, and check that all countries receive a unique name.
-
-```{r gwp-harmonise-countries}
-#| results: hold
-#| label: tbl-gwp-countries
-#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gwp %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GWP harmonised country names") %>%
-  kable_custom()
-
-# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
-
-# Harmonise old names and replace only if harmonised name found
-gwp <- gwp %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  # Prevent north cyprus from becoming cyprus
-  mutate(
-    country_harmonised = ifelse(
-      country == "Northern Cyprus",
-      "Northern Cyprus",
-      country_harmonised
-    )
-  ) %>%
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### Global Burden of Disease
-
-We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`.
-We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R.
-They are inside downloaded `.zip` files, of which there may be more than one.
-
-```{r gbd-data-load}
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/",
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>%
-  read_csv()
-```
-
-We then clean the GBD data and
-
--   Clean the variable names
--   Remove the metric and measure variables; we focus on prevalence rate
-    -   prevalence: Total number of cases
-    -   rate: Total cases per 100,000 population
--   Convert outcome rates to proportions (0 - 1)
--   Clean cause names and rename to outcome to harmonise with GWP
--   Convert GBD estimated rate CI limits to an approximate standard error
--   Subset data to young people (10 - 24)
-
-```{r gbd-data-clean}
-# First step is to clean names
-gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
-gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 100000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>%
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>%
-  rename(country = location, outcome = cause)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
-gbd <- gbd %>%
-  mutate(se = (upper - lower) / (1.96 * 2)) %>%
-  select(-c(upper, lower))
-
-# Focus on young people
-gbd <- gbd %>%
-  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
-```
-
-Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.
-
-```{r gbd-harmonise-countries}
-#| results: hold
-#| label: tbl-gbd-countries
-#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
-
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "GBD harmonised country names") %>%
-  kable_custom()
-# Harmonise old names and replace only if harmonised name found
-gbd <- gbd %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-```
-
-### International Telecommunication Union
-
-After processing the outcome tables above, we move on to the internet adoption metrics from the ITU.
-We downloaded these data files from the ITU website.
-New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.
-
-After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1).
-Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.
-
-```{r itu-process}
-#| results: hold
-#| label: tbl-itu-0
-#| tbl-cap: "ITU countries"
-#| layout-ncol: 1
-
-# Download data sets from the ITU website if not yet downloaded
-if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
-  dir.create("data-raw/ITU")
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
-    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
-    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
-    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
-  )
-}
-
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(fixed = as.numeric(value)) %>%
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(mobile = as.numeric(value)) %>%
-  select(country = Country, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(internet = as.numeric(value)) %>%
-  select(country = Country, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
-itu <- itu %>%
-  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-
-# Harmonise countries
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl(caption = "ITU harmonised country names") %>%
-  kable_custom()
-
-# Harmonise old names and replace only if harmonised name found
-itu <- itu %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Drop countries that don't exist in outcomes
-itu <- itu %>%
-  filter(
-    country %in% unique(gbd$country) | country %in% unique(gwp$country)
-  )
-
-# Drop countries that don't have any actual internet data
-itu_zeros <- itu %>%
-  group_by(country) %>%
-  summarise(s = sum(internet, na.rm = TRUE)) %>%
-  filter(s == 0)
-
-itu <- itu %>%
-  filter(!(country %in% itu_zeros$country))
-rm(itu_zeros)
-```
-
-#### Missingness
-
-We then impute missing intermediate values to the internet adoption timeseries.
-We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.
-
-```{r itu-impute}
-#| results: hold
-#| label: tbl-itu-impute
-#| tbl-cap: "Summary of ITU data imputation"
-
-# Reshape to easily impute all variables
-itu_long <- itu %>%
-  pivot_longer(c(internet, fixed, mobile))
-
-# Impute by country and variable
-itu_long <- itu_long %>%
-  group_by(country, name) %>%
-  # Find first and last year with this variable in each country
-  # so as to prevent extrapolation
-  mutate(
-    min_year = year[min(which(!is.na(value)))],
-    max_year = year[max(which(!is.na(value)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  mutate(
-    across(
-      value,
-      .fns = list(
-        i = possibly(
-          function(x) na_interpolation(x, maxgap = Inf),
-          otherwise = NaN
-        )
-      )
-    )
-  ) %>%
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    value_i = if_else(
-      between(year, unique(min_year), unique(max_year)),
-      value_i,
-      NaN
-    )
-  ) %>%
-  ungroup() %>%
-  select(-min_year, -max_year)
-
-# Summary
-itu_long %>%
-  group_by(name) %>%
-  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
-  summarise(
-    n_miss_orig = sum(is.na(value) & year >= min_year),
-    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
-    n_miss_imp = sum(is.na(value_i) & year >= min_year),
-    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
-    imputed = n_miss_orig - n_miss_imp
-  ) %>%
-  kbl(caption = "ITU data imputation summary") %>%
-  kable_custom()
-
-# We then replace the original values with the imputed ones
-itu <- itu_long %>%
-  # Pick non-missing value, from original and imputed
-  mutate(value = coalesce(value, value_i)) %>%
-  select(-value_i) %>%
-  pivot_wider()
-rm(itu_long)
-```
-
-### GLOBE regions
-
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
-
-```{r globe-regions}
-#| results: hold
-#| label: tbl-globe
-#| tbl-cap: "Countries with manually filled region"
-
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
-) %>%
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>%
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>%
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in GBD not present in region data
-no_region_gbd <- filter(
-  distinct(gbd, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-# Then see what countries in GWP are without region
-no_region_gwp <- filter(
-  distinct(gwp, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-bind_rows(no_region_gbd, no_region_gwp) %>%
-  arrange(country) %>%
-  distinct() %>%
-  write_csv("data-raw/Regions/countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/countries-without-region-filled.csv"
-)
-
-# Combine Jebb et al GLOBE regions and our manually added ones
-regions <- regions %>%
-  bind_rows(
-    regions_filled %>%
-      mutate(Note = "Filled")
-  ) %>%
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>%
-  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))
-
-# Display table of regions and countries
-regions %>%
-  drop_na(Note) %>%
-  select(-Note) %>%
-  arrange(region, country) %>%
-  kbl(caption = "Countries with a manually filled region") %>%
-  kable_custom()
-
-# Clean region labels
-regions$region <- str_replace_all(regions$region, " ", "_")
-regions$region <- factor(regions$region)
-
-# Remove unnecessary items
-regions <- select(regions, -Note)
-
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-gwp <- left_join(gwp, regions)
-# Remove now unnecessary variables
-rm(no_region_gbd, no_region_gwp, regions_filled, regions)
-```
-
-### ITU summary table
-
-```{r itu-summary-table}
-#| column: page
-#| tbl-cap: "Mean internet user percentages across regions and time."
-#| label: tbl-itusummary
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-```
-
-## RQ1: Time courses
-
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
-To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.
-
-### Modelling
-
-We first prepare the variables for modelling:
-
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
--   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
-
-```{r model1-prepare-data}
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center and scale year
-dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in mv models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
-  ungroup()
-
-# Ensure that factors are contrast coded
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
-
-# Arrange on outcome
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-dat <- dat %>%
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(dat, outcome, region, country, year)
-
-dat %>%
-  group_by(outcome) %>%
-  summarise(
-    min = min(val, na.rm = TRUE),
-    max = max(val, na.rm = TRUE),
-    internet_min = min(internet, na.rm = TRUE),
-    internet_max = max(internet, na.rm = TRUE)
-  ) %>%
-  kable(digits = 7) %>% 
-  kable_custom()
-```
-
-#### Specification
-
-We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b).
-Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g.
-Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries.
-We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)
-
-We fit the model separately for each outcome.
-Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret).
-We therefore estimate six separate bivariate models
-
-In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.
-All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes.
-This latter specification is important to allow answering RQ1b.
-
-The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate.
-For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age).
-The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data.
-Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.
-
-We write the model as
-
-$$
-\begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
-\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
-\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
-x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
-\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
-\left[\begin{array}{c}
-\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
-\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
-\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
-\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
-\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
-\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
-\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}
-$$
-
-Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.
-
-We then define the model formulas in brms' formula syntax.
-First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table.
-To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model.
-The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).
-
-```{r model1-itu-bf}
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~
-  year +
-    (year |c| country) +
-    (year |r| region),
-  family = Beta()
-)
-```
-
-Here, we specify the outcome model.
-Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model.
-Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors.
-In addition, it leads to the residual variance to be estimated.
-
-```{r model1-val-bf}
-# Meta-regression model of outcomes
-bf_1 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
-  family = gaussian()
-)
-```
-
-Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged.
-We therefore effectively removed the SEs from self-harm by setting them to zero
-
-```{r model1-selfharm-se}
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
-
-#### Fitting
-
-We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.
-
-```{r fit-model-1}
-
-fits <- dat %>%
-  # Could nest but need this to include group key in nested tibble
-  group_by(outcome) %>%
-  summarise(data = list(cur_data_all()))
-
-fits <- fits %>%
-  mutate(
-    fit1 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE),
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-1-internet")
-      )
-    )
-  )
-```
-
-#### Summary
-
-Here is a summary of the data modelled for each outcome
-
-```{r model-1-data-summary}
-#| column: body-outset
-#| tbl-cap: "Summaries of data included in Model 1"
-#| label: tbl-m1-data
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
-fits %>%
-  mutate(summary = map(fit1, msum)) %>%
-  select(outcome, summary) %>%
-  unnest(summary) %>%
-  kbl(caption = "Model 1 data summary") %>%
-  kable_custom() %>% 
-  row_spec(0, bold = TRUE)
-```
-
-#### Model checking
-
-Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section
-
-##### MCMC diagnostics
-
-First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.
-
-We can see that the models have converged nicely, apart from the self-harm outcome.
-
-```{r model-1-diagnostics}
-#| results: hold
-#| label: tab-model1-diagnostic
-#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
-#| column: body-outset
-
-diagnostic_table <- function(fit, rx, cp) {
-  diag_1 <- fits %>%
-    select(fit = {{ fit }}, outcome) %>% 
-    mutate(
-      out =
-        map(
-          fit,
-          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
-            summarise_draws(samples = length, default_convergence_measures())
-        )
-    ) %>%
-    select(outcome, out) %>%
-    unnest(out)
-  diag_1 %>%
-    kbl(
-      caption = cp,
-      digits = c(0, 0, 0, 2, 0, 0)
-    ) %>%
-    column_spec(
-      4,
-      color = "white",
-      background = spec_color(
-        log(diag_1$rhat),
-        direction = 1,
-        option = "C",
-        end = .6
-      )
-    ) %>%
-    column_spec(
-      c(5, 6),
-      color = "white",
-      background = spec_color(
-        log(diag_1$ess_tail / diag_1$samples),
-        direction = 1,
-        option = "C",
-        end = 0,
-        begin = .6
-      )
-    ) %>%
-    kable_custom()
-}
-diagnostic_table(
-  fit1,
-  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
-  cp = "Model 1 MCMC diagnostics."
-) %>% 
-  scroll_box(height = "300px")
-```
-
-##### Posterior predictive check
-
-We then take a coarse look at how well the models reproduce the input data.
-
-```{r ppcheck-density}
-
-#| column: page
-#| fig-cap: "Graphical posterior predictive check by region (Model 1).
-Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g.
-Anglo Depression)."
-#| label: fig-ppcheck-1
-ppcheck_1 <- fits %>%
-  group_by(outcome) %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ pp_check(
-        .x,
-        ndraws = 10,
-        type = "dens_overlay_grouped",
-        group = "region",
-        resp = "val",
-        newdata = .x$data
-      )[[1]]
-    )
-  ) %>%
-  ungroup() %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-ppcheck_1 %>%
-  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
-  scale_color_brewer(palette = "Set1") +
-  scale_alpha_manual(values = c(.2, 1)) +
-  stat_density(
-    geom = "line",
-    size = .75,
-    position = position_identity()
-  ) +
-  labs(x = "Value", y = "Density") +
-  facet_grid2(
-    outcome ~ group,
-    scales = "free", independent = "x",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title = element_blank(),
-    axis.text = element_blank(),
-    axis.ticks = element_blank()
-  )
-```
-
-### Results
-
-#### RQ1a: Temporal trends
-
-Before presenting the time trends, we must calculate the required quantities from the posterior distribution.
-Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.
-
-```{r calculate-simple-effects}
-
-#' Posterior draws at average and region levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = "region")
-}
-
-#' Posterior summaries at country- region- and average levels
-#'
-#' @param x brmsfit (model 1/2)
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
-    select(-r_value)
-
-  bind_rows(
-    psum_region,
-    psum_country
-  ) %>%
-    mutate(region = fct_relevel(region, "Average"))
-}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit1, pdraws)) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums <- fits %>%
-  mutate(psums = map(fit1, psums)) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-p_sums_internet <- fits %>%
-  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums) %>%
-  mutate(region = fct_relevel(region, "Average"))
-```
-
-We then display the average ($\beta^y_1$), region- ($\delta^y_1$), and country-level ($\gamma^y_1$) time trend parameters' posterior distributions.
-Recall the scales of the variables when interpreting the magnitudes: Year is in decades and outcomes are percentages (0-100).
-
-```{r forest-trends}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of linear trends in outcomes"
-#| label: fig-forest-trends
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-```
-
-@fig-forest-trends shows, starting from the top left panel, the average (across countries and regions) change in life satisfaction.
-This change is not credibly different from zero, at the 95% credibility level, and the posterior mean value of change was a 1% increase in life satisfaction per decade.
-The region-specific changes were likewise not credibly different from zero, apart from the Eastern Europe region that indicated a modest increase in life satisfaction.
-
-Because we modelled regions (and countries) as draws from a multivariate normal prior distribution, the region-specific estimates are shrunk toward the overall mean and therefore less likely to overfit any individual region's data.
-This means that the model is less likely to report "false alarms", or estimates at the region- and country-levels that indicate false certainty in nonzero changes.
-Therefore, although there are a large number of change parameters for each individual outcome, we can be fairly certain that the observed change in Eastern Europe is not due to sampling error but represents a real trend in that population.
-
-We observe credible increases in negative experiences in more regions, with notably a \~10% increase per decade in the African region.
-However, the average change again is not credibly different from zero.
-Positive experiences had increased, both on average and across 7/10 regions, with very similar changes in Anxiety.
-Depression and self-harm, on the other hand, had decreased across the board.
-
-In sum these results were somewhat mixed, where some regions showing both increases (e.g. decreased depression) and decreases (increased anxiety) in well-being.
-
-Then to help illustrate the parameters, we draw figures of the fitted lines conditional on the predictors, or so called counterfactual plots.
-
-```{r fitted-trend-country}
-
-#' Get (grand mean) fitted values for countries
-#'
-#' @param x a brmsfit model 1
-#'
-#' @return a data frame of fitted values
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
-    summarise(val = mean(val, na.rm = TRUE)) %>%
-    ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
-  newy <- bind_cols(
-    newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit1, fitted_country)) %>%
-  select(outcome, fc)
-
-#' Draw a panel plot of countries' fitted values and data
-#'
-#' @param x fitted country level data from fitted_country()
-#' @param y outcome
-#'
-#' @return a ggplot for that outcome
-plot_country <- function(x, y) {
-  coefs <- p_sums %>%
-    drop_na(country) %>%
-    filter(outcome == y) %>%
-    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
-    mutate(country = fct_reorder(country, coef))
-  x %>%
-    left_join(coefs) %>%
-    mutate(country = fct_reorder(country, coef)) %>%
-    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
-    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
-    scale_y_continuous(
-      str_replace(y, "_", " "),
-      breaks = pretty_breaks(),
-      expand = expansion(.15),
-      labels = function(x) {
-        percent(x / 100, .01) %>%
-          str_remove("\\.00")
-      }
-    ) +
-    # Add parameters in text
-    geom_richtext(
-      data = coefs %>%
-        mutate(across(where(is.numeric), ~ number(., .01))),
-      aes(
-        x = make_date(2000), y = Inf,
-        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
-      ),
-      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
-      family = Font,
-      fill = alpha("white", .3), label.color = NA,
-      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
-    ) +
-    geom_point(aes(y = val), shape = 1, alpha = .5) +
-    geom_ribbon(
-      aes(ymin = Q2.5, ymax = Q97.5),
-      alpha = .3, col = NA, fill = "dodgerblue1"
-    ) +
-    geom_line(
-      size = 0.5, col = "dodgerblue1"
-    ) +
-    facet_wrap(
-      "country"
-    ) +
-    theme(panel.spacing = unit(2, "pt"))
-}
-
-# Create the plot for each outcome
-f_country <- f_country %>%
-  mutate(
-    plot = map2(
-      fc, outcome,
-      ~ plot_country(.x, .y)
-    )
-  )
-```
-
-::: {.panel-tabset .column-screen-inset-shaded}
-##### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-##### Life satisfaction
-
-```{r trends-ls}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
-#| label: fig-trends-ls
-f_country$plot[[1]]
-```
-
-##### Negative experiences
-
-```{r trends-ne}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Negative experiences trends, ordered by association magnitude"
-#| label: fig-trends-ne
-f_country$plot[[2]]
-```
-
-##### Positive experiences
-
-```{r trends-pe}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Positive experiences trends, ordered by association magnitude"
-#| label: fig-trends-pe
-f_country$plot[[3]]
-```
-
-##### Anxiety
-
-```{r trends-anx}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Anxiety trends, ordered by association magnitude"
-#| label: fig-trends-anx
-f_country$plot[[4]]
-```
-
-##### Depression
-
-```{r trends-dep}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Depression trends, ordered by association magnitude"
-#| label: fig-trends-dep
-f_country$plot[[5]]
-```
-
-##### Self-harm
-
-```{r trends-sel}
-#| echo: false
-#| fig-width: 16
-#| fig-height: 12
-#| fig-cap: "Self-harm trends, ordered by association magnitude"
-#| label: fig-trends-sel
-f_country$plot[[6]]
-```
+If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
 :::
-
-#### RQ1b: Correlations
-
-We then turned to research question 1b: To what extent were changes in well-being and internet adoption correlated across countries.
-
-To investigate we examined the correlations between $\gamma^y_1$ and $\gamma^x_1$ ($\sigma_{\gamma^y_1,\gamma^x_1}$ in $\Sigma^{\text{c}}$).
-A positive correlation would indicate that countries with greater increases in internet adoption between 2000 and 2020 would tend to have greater increases in $y$ (e.g.
-Life satisfaction).
-
-To answer, we display $\sigma_{\gamma^y_1,\gamma^x_1}$ from each outcome's model in the figure below.
-The figures are scatterplots of country-level trend coefficients, where each point's x-y coordinate indicate their trend magnitudes.
-The overlaid ellipses are the model's 95% predictive limits for $\gamma^y_1$ and $\gamma^x_1$.
-
-```{r scatterplot-time-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of country-level internet and outcome trends."
-#| label: fig-trend-scatterplot
-
-# Correlation parameters
-cor_pars <- fits %>%
-  mutate(
-    out = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        variable = "cor_country__internet_year__val_year"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-# Ellipses
-ellipses <- fits %>%
-  mutate(
-    ellipse = map(
-      fit1,
-      ~ as_draws_df(
-        .x,
-        c(
-          "b_val_year",
-          "b_internet_year",
-          "sd_country__val_year",
-          "sd_country__internet_year",
-          "cor_country__internet_year__val_year"
-        )
-      ) %>%
-        slice_sample(n = 100) %>%
-        rename(
-          cor = cor_country__internet_year__val_year,
-          sd_outcome = sd_country__val_year,
-          sd_i = sd_country__internet_year,
-          b_outcome = b_val_year,
-          b_i = b_internet_year
-        ) %>%
-        mutate(
-          e = pmap(
-            list(cor, sd_outcome, sd_i, b_outcome, b_i),
-            function(cor, sd_a, sd_i, b_a, b_i) {
-              ellipse(
-                cor,
-                scale = c(sd_i, sd_outcome),
-                centre = c(b_i, b_outcome),
-                level = .95
-              ) %>%
-                as_tibble()
-            }
-          )
-        ) %>%
-        unnest(e)
-    )
-  )
-ellipses <- ellipses %>%
-  select(outcome, ellipse) %>%
-  unnest(ellipse)
-
-# Wide tibble of parameters
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_path(
-    data = ellipses,
-    aes(x = x, y = y, group = .draw),
-    alpha = .2, size = .1, col = "dodgerblue2"
-  ) +
-  geom_point(col = "dodgerblue1", size = 1, alpha = .5) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  geom_text(
-    data = cor_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(aspect.ratio = 1)
-```
-
-#### Other results from Model 1
-
-##### Shrinkage
-
-It's important to note that at the level of countries and regions, the model parameters refer to country^\*^ and region^\*^, that is as they are in the sample of other countries and regions.
-This modelling strategy is important because it allows describing the parameters at each level while adjusting the values toward the group means (preventing "false alarms").
-However it is then important to examine those values against their "fixed effect" counterparts, which we do here.
-
-```{r shrinkage}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Scatterplots of multilevel and independent model coefficients"
-#| label: fig-trend-shrinkage
-
-lm_coefs <- fits %>%
-  mutate(
-    data = map(fit1, ~ as_tibble(.x$data))
-  ) %>%
-  mutate(
-    fit_val = map(
-      data,
-      ~ tidy(
-        lm(val ~ 0 + country + year:country, data = .x)
-      )
-    ),
-    fit_internet = map(
-      data,
-      ~ tidy(
-        gam(
-          internet ~ 0 + country + year:country,
-          family = betar, data = .x %>%
-            filter(itu)
-        ),
-        parametric = TRUE
-      )
-    )
-  )
-lm_coefs <- lm_coefs %>%
-  select(outcome, fit_val, fit_internet) %>%
-  pivot_longer(c(fit_val, fit_internet)) %>%
-  mutate(name = str_remove(name, "fit_")) %>%
-  unnest(value) %>%
-  select(outcome, name, term, estimate, std.error) %>%
-  filter(str_detect(term, ":")) %>%
-  mutate(term = str_remove(term, "country")) %>%
-  mutate(term = str_remove(term, ":year")) %>%
-  pivot_wider(names_from = name, values_from = c(estimate, std.error)) %>%
-  rename(country = term)
-
-# Plot
-left_join(
-  p_sums %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Outcome_{.}"), .cols = c(Estimate:Q97.5)),
-  p_sums_internet %>%
-    drop_na(country) %>%
-    rename_with(~ str_glue("Internet_{.}"), .cols = c(Estimate:Q97.5))
-) %>%
-  left_join(lm_coefs) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  ggplot(aes(Internet_Estimate, Outcome_Estimate, col = region)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_segment(
-    aes(
-      x = estimate_internet, xend = Internet_Estimate,
-      y = estimate_val, yend = Outcome_Estimate
-    ),
-    arrow = arrow(type = "closed", length = unit(3, "pt")),
-    size = .25, show.legend = FALSE
-  ) +
-  geom_point(size = 1.1, alpha = .4) +
-  scale_y_continuous(
-    "Outcome trend",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  scale_x_continuous(
-    "Internet trend",
-    breaks = pretty_breaks()
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  guides(
-    color = guide_legend(override.aes = list(size = 2, alpha = 1))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "bottom"
-  )
-```
-
-## RQ2: Associations
-
-We then turned to the second research question: To what extent are changes in well-being predicted by internet adoption?
-To answer, we expand Model 1 to include the country-specific 1-year-lagged internet adoption values (both within- and between country centred) as predictors of the outcomes.
-Before modelling, we calculated these quantities as shown in this code block.
-
-```{r model2-data-prepare}
-# Create lagged predictors
-dat <- dat %>% 
-  arrange(outcome, region, country, year) %>%
-  group_by(outcome, region, country, sex, age) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-dat <- dat %>%
-  group_by(outcome, country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  group_by(outcome) %>% 
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-```
-
-### Specification and fitting
-
-Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions
-
-$$\begin{align*}
-y_i &\sim \text{Normal}(\mu_i, \sigma^2v_i) \\
-
-\mu_i &= \beta_{0} + \delta_{0\text{region}[i]} + 
-\gamma_{0\text{country}[i]} + \\ &(\beta_{1} + \delta_{1\text{region}[i]} + \gamma_{1\text{country}[i]})\text{Time}_i + 
-\\ &(\beta_{2} + \delta_{2\text{region}[i]} + \gamma_{2\text{country}[i]})\text{Sex}_i + 
-\\ &(\beta_{3} + \delta_{3\text{region}[i]} + \gamma_{3\text{country}[i]})\text{Age}_i + 
-\\ &(\beta_{4} + \delta_{4\text{region}[i]} + \gamma_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
-\\ &(\beta_{5} + \delta_{5\text{region}[i]} + \gamma_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i +
-\\ &(\beta_{6} + \delta_{6\text{region}[i]} + \gamma_{6\text{country}[i]})\text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{7} + \delta_{7\text{region}[i]} + \gamma_{7\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + 
-\\ &(\beta_{8} + \delta_{8\text{region}[i]} + \gamma_{8\text{country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i\\ \\
-
-\left[\begin{array}{c}
-\delta_{0\text{region}} \\ \delta_{1\text{region}} \\ 
-\delta_{2\text{region}} \\ \delta_{3\text{region}} \\ 
-\delta_{4\text{region}} \\ \delta_{5\text{region}} \\ 
-\delta_{6\text{region}} \\ \delta_{7\text{region}} \\ 
-\delta_{8\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{r}
-),
-\left[\begin{array}{c}
-\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\ 
-\gamma_{4\text{country}} \\ \gamma_{5\text{country}} \\ 
-\gamma_{6\text{country}} \\ \gamma_{7\text{country}} \\ 
-\gamma_{8\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{c}
-)
-\end{align*}$$
-
-```{r fit-model-2}
-
-# Model formula is only a small update to Model 1
-bf_2 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
-
-# As above with model 1
-fits <- fits %>%
-  mutate(
-    fit2 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-internet")
-      )
-    )
-  )
-```
-
-### Results
-
-First, we compared the R2 values between Models 1 and 2.
-This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2).
-However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.
-
-```{r model21-compare}
-
-#| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
-#| label: tbl-m12-r2
-fits %>%
-  select(outcome, fit1, fit2) %>% 
-  pivot_longer(c(fit1, fit2)) %>% 
-  mutate(
-    r2 = map(
-      value,
-      ~ bayes_R2(., resp = "val") %>%
-        as.data.frame() %>%
-        mutate(across(everything(), ~ percent(., .1))) %>%
-        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
-    )
-  ) %>%
-  select(-value) %>%
-  unnest(r2) %>% 
-  pivot_wider(
-    names_from = name,
-    values_from = result,
-    names_prefix = "Model "
-  ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  kbl(caption = "Model 1 and 2 R-squared values") %>%
-  kable_custom()
-```
-
-Before we can present the results, we calculate the "internet effect" at each of three levels of analysis; the average, region, and country-level.
-
-```{r model2-calculate-coefficients}
-
-p_draws <- fits %>%
-  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws)
-
-p_sums <- fits %>%
-  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums)
-
-p_draws <- p_draws %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-p_sums <- p_sums %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-```
-
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
-
-```{r forest-internet}
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
-  ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
-  ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
-  ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
-  ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 2.8, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
-  facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x"
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "none"
-  )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
-x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
-```
-
-This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
-However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
-Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region.
-However, none of the average associations were credibly different from zero.
-The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.
-
-To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
-
-```{r model2-fitted-values}
-
-#| column: screen-inset
-#| fig-width: 14
-#| fig-height: 9
-#| fig-cap: "Counterfactual plot of internet associations"
-#| label: fig-fitted-internet
-
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country) %>%
-    mutate(
-      xmin = min(i1_cw, na.rm = TRUE),
-      xmax = max(i1_cw, na.rm = TRUE)
-    ) %>%
-    filter(i1_cw %in% c(xmin, xmax)) %>%
-    ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
-  newy
-}
-
-fitted_region <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region) %>%
-    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
-    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit2, fitted_country)) %>%
-  select(outcome, fc) %>%
-  unnest(fc)
-
-f_region <- fits %>%
-  mutate(fr = map(fit2, fitted_region)) %>%
-  select(outcome, fr) %>%
-  unnest(fr)
-
-f_country %>%
-  ggplot(aes(i1_cw, Estimate)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimate",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = f_region,
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = f_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country),
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    panel.spacing = unit(2, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-### Other results from Model 2
-
-We then focused on the between-country association between internet adoption and well-being.
-Recall that the model does not adjust for between-country differences so these associations are likely to reflect many other factors covarying with internet adoption (e.g.
-wealth and development factors).
-
-```{r}
-#| fig.width: 6
-#| fig.height: 4
-#| fig-cap: "Between-country associations"
-#| label: fig-cb1
-
-fitted_cb1 <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region, country) %>%
-    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
-    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
-    ungroup()
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = NULL
-        )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-tmp <- fits %>% 
-  mutate(out = map(fit2, fitted_cb1)) %>% 
-  select(outcome, out) %>%
-  unnest(out)
-
-cb1_pars <- fits %>%
-  mutate(
-    out = map(
-      fit2,
-      ~ as_draws_df(
-        .x,
-        variable = "b_i1_cb"
-      ) %>%
-        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
-  ) %>%
-  select(outcome, out) %>%
-  unnest(out) %>%
-  mutate(across(where(is.numeric), ~ number(., .01)))
-
-tmp %>% 
-  ggplot(aes(i1_cb, val)) +
-  scale_x_continuous(
-    "Between-country centered internet adoption",
-    labels = ~percent(.)
-  ) +
-  scale_y_continuous(
-    "Value",
-    labels = ~percent(./100)
-  ) +
-  geom_point(
-    shape = 1, size = 1, alpha = .75,
-    aes(col = region)
-  ) +
-  geom_ribbon(
-    aes(ymin = Q2.5, ymax = Q97.5),
-    fill = "dodgerblue2",
-    alpha = .2
-    ) +
-  geom_line(aes(y = Estimate), col = "dodgerblue4") +
-  geom_text(
-    data = cb1_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
-  ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    axis.title.y = element_blank()
-  )
-```
-
-## RQ3: Demographics
-
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
-
-### Trends
-
-```{r model1-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
-)
-#' Calculate posterior draws for simple effects (by sex and age) for regions and average
-#'
-#' @param x brmsfit model 2
-#' @param h a brmshypothesis
-#'
-#' @return a long tibble of draws of posterior answers to hypothesis
-simple_effects_samples <- function(x, h) {
-  # Calculate hypotheses at average level
-  average_h <- hypothesis(
-    x, h
-  )
-  # Give hypotheses appropriate names
-  average <- average_h$samples
-  names(average) <- interaction(
-    "Average", average_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  # Pivot to long format, note use of dtplyr
-  average <- average %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  # Regions as above
-  region_h <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )
-  region <- region_h$samples
-  names(region) <- interaction(
-    region_h$hypothesis$Group,
-    region_h$hypothesis$Hypothesis,
-    sep = "+"
-  )
-  region <- region %>%
-    lazy_dt() %>%
-    pivot_longer(everything()) %>%
-    separate(name, into = c("region", "Hypothesis"), sep = "\\+") %>%
-    as_tibble()
-
-  bind_rows(average, region)
-}
-
-#' Posterior summaries of country- region- and average-level effects for the demographic groups
-#'
-#' @param x brmsfit model 2
-#' @param h character vector of hypotheses
-#'
-#' @return
-simple_effects_summary <- function(x, h) {
-
-  # Calculate hypotheses at average level
-  average <- hypothesis(x, h)$hypothesis %>% as_tibble()
-  average$region <- "Average"
-
-  # Regions as above
-  region <- hypothesis(
-    x, h,
-    scope = "coef", group = "region"
-  )$hypothesis %>%
-    as_tibble()
-  region <- rename(region, region = Group)
-
-  # Country hypotheses
-  country <- hypothesis(
-    x, h,
-    scope = "ranef", group = "country"
-  )
-  country <- country$hypothesis %>% as_tibble()
-  country <- rename(country, country = Group)
-
-  # Add region coefs
-  country <- left_join(country, distinct(x$data, region, country))
-  region_coef <- region %>%
-    select(region, Hypothesis, r_region = Estimate)
-  country <- country %>%
-    left_join(region_coef) %>%
-    mutate(across(c(Estimate, CI.Lower, CI.Upper), ~ . + r_region)) %>%
-    select(-r_region)
-
-  bind_rows(average, region, country)
-}
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit1, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-### Associations
-
-```{r model2-demographics}
-
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
-)
-
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
-    )
-  ) %>%
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
-
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
-  ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
-  scale_shape_manual(values = c(21, 19), guide = "none") +
-  scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
-  ) +
-  scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
-  ) +
-  stat_halfeye(
-    point_interval = mean_qi, normalize = "xy",
-    height = 1, alpha = .5, point_fill = "white",
-    .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
-    aes(
-      shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
-  ) +
-  guides(
-    color = guide_legend(
-      override.aes = list(size = 2, alpha = 1),
-      nrow = 2, ncol = 3, byrow = TRUE
-    ),
-    fill = guide_legend(
-      nrow = 2, ncol = 3, byrow = TRUE
-    )
-  ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
-  facet_wrap(
-    "outcome",
-    scales = "free_x", nrow = 1,
-    labeller = as_labeller(~ str_replace(., "_", " "))
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    axis.text.y = element_markdown(),
-    legend.position = "bottom"
-  )
-```
-
-## Other internet metrics
-
-Fixed and mobile broadband subscription analyses
-
-```{r fixed-mobile-formulas}
-bf_2_f <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-
-bf_2_m <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-```

### 2022-01-10 R/functions.R

@@ -1,0 +1,190 @@
+#' Custom kableExtra formatting
+#'
+#' @param a table from kbl()
+#'
+#' @return a table
+kable_custom <- function(x) {
+  kable_classic(
+    kable_input = x,
+    html_font = Font,
+    font_size = 13,
+    lightable_options = "striped",
+    position = "center",
+    full_width = FALSE
+  )
+}
+
+#' Model summary
+#'
+#' @param x a brmsfit
+#'
+#' @return A tibble with information on data in the model
+msum <- function(x) {
+  tibble(
+    regions = ngrps(x)$region,
+    countries = ngrps(x)$country,
+    `year/country` = x$data %>%
+      distinct(country, year) %>%
+      count(country) %>%
+      pull(n) %>%
+      median(),
+    nobs_internet = standata(x)$N_internet,
+    nobs_outcome = standata(x)$N_val,
+    outcome_range = str_glue(
+      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
+    )
+  )
+}
+
+#' Posterior draws at average and region levels
+#'
+#' @param x brmsfit (model 1/2)
+#' @param p name of parameter
+#'
+#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
+pdraws <- function(x, p = "val_year") {
+  bind_cols(
+    tibble("Average" = fixef(x, summary = FALSE)[, p]),
+    as_tibble(coef(x, summary = FALSE)$region[, , p])
+  ) %>%
+    pivot_longer(everything(), names_to = "region")
+}
+
+#' Posterior summaries at country- region- and average levels
+#'
+#' @param x brmsfit (model 1/2)
+#' @param p name of parameter
+#'
+#' @return a long tibble with posterior summary of p at each level
+psums <- function(x, p = "val_year") {
+  psum_region <- bind_rows(
+    fixef(x) %>%
+      as.data.frame() %>%
+      rownames_to_column("parameter") %>%
+      filter(parameter == {{ p }}) %>%
+      select(-parameter) %>%
+      mutate(region = "Average"),
+    coef(x)$region[, , p] %>%
+      as.data.frame() %>%
+      rownames_to_column("region")
+  ) %>%
+    as_tibble()
+
+  psum_country <- ranef(x)$country[, , p] %>%
+    as.data.frame() %>%
+    rownames_to_column("country") %>%
[…]

### 2022-01-10 _common.R

@@ -1,0 +1,19 @@
+library(ggplot2)
+# Plotting theme & use this font if available
+Font <- "Titillium Web"
+theme_set(
+  theme_linedraw(
+    base_size = 12,
+    base_family = Font
+  ) +
+    theme(
+      panel.grid = element_blank(),
+      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
+    )
+)
+
+library(knitr)
+opts_chunk$set(
+  cache = TRUE,
+  cache.lazy = FALSE
+)

### 2022-01-10 00-clean.qmd
Add mock gwp data

@@
 if (!file.exists(gwp_mock_path)) {
+  set.seed(101010)
   distinct(gwp, outcome, country, year, sex, age) %>% 

### 2022-01-20 00-clean.qmd
Quarto book

--- 2022-01-10 00-clean.qmd
@@
 #| cache: false
+#| results: hide
+#| message: false
 # Packages
@@
     WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74
+    WP68, WP69, WP70, WP71, WP74,
+    WP16056
   )
@@
       WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
+      WP68, WP69, WP70, WP71, WP74,
+      WP16056
     )
@@
     # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
+    across(wp60:wp74, ~ 3 - .),
+    # Internet (fix NAs and reverse 1:yes 2:no coding to 1:no 2:yes)
+    gwpi = 2 - if_else(between(wp16056, 1, 2), wp16056, NaN)
   )
@@
 gwp <- gwp %>%
+  # Aggregate internet
+  group_by(country, year, sex, age) %>% 
+  mutate(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
   pivot_longer(
@@
   ) %>%
-  group_by(country, year, sex, age, outcome) %>%
+  group_by(country, year, sex, age, outcome, gwpi) %>%
   summarise(
@@
 ```{r gwp-harmonise-countries}
-#| results: hold
 #| label: tbl-gwp-countries
@@
 if (!file.exists(gwp_mock_path)) {
-  distinct(gwp, outcome, country, year, sex, age) %>% 
+  set.seed(101010)
+  distinct(gwp, outcome, country, year, sex, age, gwpi) %>% 
     mutate(
@@
 ```{r gbd-harmonise-countries}
-#| results: hold
 #| label: tbl-gbd-countries
 #| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
 
@@
 #| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"
-#| layout-ncol: 1
 
@@
 
+## GWP summary table
+
+```{r gwp-summary-table}
+#| column: page-right
+#| tbl-cap: "Mean internet user percentages across regions and time from the GWP data."
+#| label: tbl-gwpsummary
+
+gwp %>%
+  select(region, country, year, gwpi) %>%
+  mutate(internet = internet * 100) %>%
+  mutate(region = str_replace(region, "_", " ")) %>%
+  pivot_wider(names_from = year, values_from = internet) %>%
+  select(-country) %>%
+  tbl_summary(
+    by = region,
+    missing = "no",
+    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
+  ) %>%
+  add_overall(col_label = "Total") %>%
+  as_kable_extra(caption = "ITU summary") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_custom()
+```
+
 ## Write data tables

### 2022-01-20 00-models.qmd
Quarto book

@@
   # Grand-mean center the country averages
+  ungroup() %>% 
   mutate(
@@
   kable_custom()
+```
+
+We then create the lagged and centered GWP internet predictor. Note that this is at the level of demographics, not just a country average like in ITU.
+
+```{r}
+# Take only relevant variables to make this easier
+gwpi <- dat %>% 
+  filter(outcome == "Life_satisfaction") %>% 
+  filter(year >= .5) %>% 
+  select(region, country, year, sex, age, year, gwpi)
+
+# Create lagged GWP internet
+gwpi <- gwpi %>% 
+  arrange(region, country, sex, age, year) %>% 
+  group_by(region, country, sex, age) %>% 
+  mutate(g1 = lag(gwpi, 1))
+
+# Center GWP internet
+gwpi <- gwpi %>%
+  group_by(country) %>%
+  mutate(
+    g1_cb = mean(g1, na.rm = TRUE), # Country average
+    g1_cw = g1 - g1_cb, # Year-specific deviation from country average
+  ) %>%
+  # Grand-mean center the country averages
+  ungroup() %>% 
+  mutate(
+    g1_cb = g1_cb - mean(g1_cb, na.rm = TRUE)
+  )
+
+# Join to data (all outcomes)
+dat <- left_join(dat, select(gwpi, -gwpi))
 ```
@@
 
+bf_2_g <- bf(
+  val | resp_se(se, sigma = TRUE) ~
+  year * sex + year * age + g1_cw * sex + g1_cw * age + g1_cb +
+    (year * sex + year * age + g1_cw * sex + g1_cw * age | country) +
+    (year * sex + year * age + g1_cw * sex + g1_cw * age | region),
+  family = gaussian(),
+  unused = ~outcome
+)
+
 fits %>%
@@
   )
+
+fits %>%
+  mutate(
+    fit2_g = map2(
+      data, outcome,
+      ~brm(
+        formula = bf_2_g,
+        data = .x,
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        file = str_glue("models/brm-{.y}-2-gwpinternet")
+      )
+    )
+  )
 ```
+
+```{r}
+fits$data[[1]] %>% select(country, year, g1_cb) %>% drop_na(g1_cb)
+```

### 2022-01-20 01-timecourses.qmd
Quarto book

@@
 #| fig-height: 8
-#| fig-cap: "Forest plot of linear trends in outcomes"
+#| fig-cap: "Forest plot of linear trends in outcomes.
+Shaded areas indicate approximate posterior densities of average and region-specific trends.
+Blue points are country-specific posterior means.
+Black points and lines are 95%CIs; open points indicate estimates where zero is within the 95% most credible values."
 #| label: fig-forest-trends

### 2022-01-20 04-fixed-mobile.qmd
Quarto book

@@
   )
+```
+
+Correspondence between different internet metrics. Note that
+
+- ITU internet metrics are for everyone (all ages, genders, etc)
+- GWP metrics are per demographic, aggregated to the country-year mean here (for 15 to 24 year olds!)
+
+This helps to explain why, across the board, the ITU internet metric (`internet`, below) is lower than the GWP internet metric (`gwpi`) as younger people tend to have access to the internet more often (see e.g.
+[this ITU spreadsheet](https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_Oct_2021.xlsx) showing that the percentage of individuals using the internet is ~15% greater for youth (15-24) than the rest of the population.)
+
+```{r}
+#| column: screen-inset-right
+#| fig-width: 13
+#| fig-height: 8
+#| fig-cap: "GWP and ITU internet metrics for all countries."
+#| label: fig-internet-metrics
+gwp %>% 
+  group_by(region, country, year) %>% 
+  summarise(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
+  left_join(select(itu, country, year, internet)) %>% 
+  filter(year >= 2015) %>% 
+  pivot_longer(gwpi:internet) %>% 
+  ggplot(aes(year, value, color = name)) +
+  scale_color_brewer("Metric", palette = "Set1") +
+  geom_line() +
+  facet_wrap("country")
 ```

### 2022-01-20 index.qmd
Quarto book

@@
 Welcome!
-This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation).
+This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [preprint]() in preparation).
 It contains all the analyses reported in the manuscript along with supplemental analyses.
-The data and source code repository, along with the datasets, are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
+The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
 

### 2022-01-20 _common.R

@@ -14,6 +14,7 @@ theme_set(
 
 library(knitr)
 opts_chunk$set(
-  cache = TRUE,
   cache.lazy = FALSE
 )
+
+source("R/functions.R")

### 2022-01-20 00-models.qmd
Fit three-way interactions

@@
   val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
+  year * sex * age +
+    (year * sex * age | c | country) +
+    (year * sex * age | r | region),
   family = gaussian()
@@
   val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
+  year * sex * age + i1_cw * sex * age + i1_cb +
+    (year * sex * age + i1_cw * sex * age | country) +
+    (year * sex * age + i1_cw * sex * age | region),
   family = gaussian()
@@
   val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
+  year * sex * age + i1_cw * sex * age + f1_cb +
+    (year * sex * age + i1_cw * sex * age | country) +
+    (year * sex * age + i1_cw * sex * age | region),
   family = gaussian(),
@@
   val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
+  year * sex * age + i1_cw * sex * age + m1_cb +
+    (year * sex * age + i1_cw * sex * age | country) +
+    (year * sex * age + i1_cw * sex * age | region),
   family = gaussian(),
@@
   val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + g1_cw * sex + g1_cw * age + g1_cb +
-    (year * sex + year * age + g1_cw * sex + g1_cw * age | country) +
-    (year * sex + year * age + g1_cw * sex + g1_cw * age | region),
+  year * sex * age + i1_cw * sex * age + g1_cb +
+    (year * sex * age + i1_cw * sex * age | country) +
+    (year * sex * age + i1_cw * sex * age | region),
   family = gaussian(),

### 2022-01-27 00-clean.qmd
Fix GWP internet summary table

@@
 gwp %>%
-  select(region, country, year, gwpi) %>%
-  mutate(internet = internet * 100) %>%
+  filter(year >= 2015) %>% 
+  group_by(region, country, year) %>%
+  summarise(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  mutate(gwpi = gwpi * 100) %>%
   mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
+  arrange(year, region, country) %>% 
+  pivot_wider(names_from = year, values_from = gwpi) %>%
   select(-country) %>%
@@
   add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
+  as_kable_extra(
+    caption = "GWP Internet use summary (mean over demographics)"
+  ) %>%
   row_spec(0, bold = TRUE) %>%

### 2022-01-27 01-timecourses.qmd
Save correlation parameter docx table

@@
 library(mgcv)
-library(brms)
 library(cmdstanr)
+library(officer)
 library(ellipse)
@@
 library(broom)
+library(brms)
 library(tidyverse)
@@
 
-```{r fitted-trend-country}
+::: {.panel-tabset .column-screen-inset-right}
+#### All outcomes
+
+```{r trends-regions}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 8
+#| fig-cap: "Trends in all variables across regions"
+#| label: fig-trends-regions
+
+# Stack data sets
+# Assume all outcomes are proportions (0-1)
+dat_all <- bind_rows(
+  gwp,
+  gbd,
+  itu %>% mutate(outcome = "Internet", val = internet)
+) %>%
+  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
+  group_by(region, country, year, outcome) %>%
+  summarise(mean = mean(val, na.rm = TRUE)) %>%
+  ungroup()
+
+# Draw small multiples figure, outcomes x regions
+dat_all %>% 
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(year, mean)) +
+  scale_y_continuous(
+    "Value",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    date_breaks = "5 years",
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country, outcome)),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line",
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_grid(
+    outcome ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
+    aspect.ratio = 1,
+    legend.position = "none",
+    panel.spacing = unit(3, "pt"),
+    axis.title.y = element_blank()
+  )
+```
+
+#### Life satisfaction
+
+```{r trends-ls}
 f_country <- fits %>%
@@
   )
-```
-
-::: {.panel-tabset .column-screen-inset-right}
-#### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 8
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-#### Life satisfaction
-
-```{r trends-ls}
 #| echo: false
@@
 
+```{r}
+# Display table and print in word document
+cor_tab <- cor_pars %>% 
+  transmute(
+    outcome = str_replace(outcome, "_", " "), 
+    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
+  )
+cor_tab %>%   
+  kbl(caption = "Between-country trend correlation parameters") %>% 
+  kable_custom()
+
+read_docx() %>% 
+  body_add_table(
+    cor_tab,
+    first_column = TRUE
+  ) %>% 
+  print("Table-correlations.docx")
+```
+
 ### Other results from Model 1

### 2022-01-27 R/functions.R
Fixety fix

@@ -93,15 +93,14 @@ psums <- function(x, p = "val_year") {
 #' @return a data frame of fitted values
 fitted_country <- function(x) {
   newx <- x$data %>%
-    group_by(country, region, outcome, year) %>%
+    group_by(country, region, year) %>%
     summarise(val = mean(val, na.rm = TRUE)) %>%
     ungroup() %>%
-    mutate(sex = NA, age = NA, se = 0)
+    mutate(sex = NA, age = NA, se = 0, itu = TRUE)
   newy <- bind_cols(
     newx,
     as.data.frame(fitted(x, newdata = newx, resp = "val"))
-  ) %>%
-    select(-outcome)
+  )
   newy
 }
 

### 2022-01-28 03-demographics.qmd

@@
 library(dtplyr)
+library(patchwork)
 library(tidyverse)
@@
 
-# Load models
 oo <- c(
@@
   "Anxiety", "Depression", "Selfharm"
-)
-fits <- tibble(outcome = oo) %>% 
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  mutate(
-    fit1 = map(
-      outcome, 
-      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
-    ),
-    fit2 = map(
-      outcome, 
-      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
-    )
 )
@@
 #| label: fig-forest-trends-demo
+
+fits <- tibble(outcome = oo) %>% 
+  mutate(outcome = factor(outcome, levels = oo)) %>% 
+  mutate(
+    fit1 = map(
+      outcome, 
+      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
+    )
+  )
+
 h_gwp <- c(
-  `15 to 19` =
-    "val_year + val_year:age1 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
+  `Female_15 to 19` =
+    "val_year + val_year:sex1 * 1 + val_year:age1 * 1 + val_year:sex1:age1 * 1 = 0",
+  `Female_20 to 24` =
+    "val_year + val_year:sex1 * 1 + val_year:age1 * -1 + val_year:sex1:age1 * -1 = 0",
+  `Male_15 to 19` =
+    "val_year + val_year:sex1 * -1 + val_year:age1 * 1 + val_year:sex1:age1 * -1 = 0",
+  `Male_20 to 24` =
+    "val_year + val_year:sex1 * -1 + val_year:age1 * -1 + val_year:sex1:age1 * 1 = 0"
 )
+
 h_gbd <- c(
-  `10 to 14` =
-    "val_year + val_year:age1 * 1 + val_year:age2 * 0 = 0",
-  `15 to 19` =
-    "val_year + val_year:age1 * 0 + val_year:age2 * 1 = 0",
-  `20 to 24` =
-    "val_year + val_year:age1 * -1 + val_year:age2 * -1 = 0",
-  `Female` =
-    "val_year + val_year:sex1 * 1 = 0",
-  `Male` =
-    "val_year + val_year:sex1 * -1 = 0"
+  `Female_10 to 14` =
+    "val_year + val_year:sex1 * 1 + val_year:age1 * 1 + val_year:age2 * 0 + val_year:sex1:age1 * 1 + val_year:sex1:age2 * 0 = 0",
+  `Female_15 to 19` =
+    "val_year + val_year:sex1 * 1 + val_year:age1 * 0 + val_year:age2 * 1 + val_year:sex1:age1 * 0 + val_year:sex1:age2 * 1 = 0",
+  `Female_20 to 24` =
+    "val_year + val_year:sex1 * 1 + val_year:age1 * -1 + val_year:age2 * -1 + val_year:sex1:age1 * -1 + val_year:sex1:age2 * -1 = 0",
+  `Male_10 to 14` =
+    "val_year + val_year:sex1 * -1 + val_year:age1 * 1 + val_year:age2 * 0 + val_year:sex1:age1 * -1 + val_year:sex1:age2 * 0 = 0",
+  `Male_15 to 19` =
+    "val_year + val_year:sex1 * -1 + val_year:age1 * 0 + val_year:age2 * 1 + val_year:sex1:age1 * 0 + val_year:sex1:age2 * -1 = 0",
+  `Male_20 to 24` =
+    "val_year + val_year:sex1 * -1 + val_year:age1 * -1 + val_year:age2 * -1 + val_year:sex1:age1 * 1 + val_year:sex1:age2 * 1 = 0"
 )
@@
   unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit1, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
 
 sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
+  filter(region == "Average")
 
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
+trends_demo <- sexage_draws %>%
+  mutate(Hypothesis = str_replace(Hypothesis, "_", " ")) %>% 
+  ggplot(
+    aes(value, Hypothesis)
   ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
   geom_vline(xintercept = 0, lty = 2, size = .2) +
@@
   scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
+    expand = expansion(c(0.1, .1))
   ) +
@@
     "Estimated linear change per decade",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
+    breaks = extended_breaks(5),
+    labels = ~percent(. / 100, .001) %>% 
+      # Remove trailing zeroes
+      str_remove("[\\.000](?=%)") %>% 
+      str_remove("[\\.00](?=%)"),
+    expand = expansion(c(.05, .05))
   ) +
@@
     .width = .95, interval_alpha = 1, interval_size = .2,
-    point_alpha = 1, point_size = 1.5, stroke = .5,
+    point_alpha = 1, point_size = 1.75, stroke = .75,
+    fill = "dodgerblue1", adjust = 0.8,
     aes(
       shape = after_stat(xmin > 0 | xmax < 0)
-    ),
-    position = position_dodge(.8),
-    key_glyph = draw_key_point
+    )
   ) +
@@
   ) +
-  # Add country points
-  # geom_point(
-  #   data = sexage_sums %>%
-  #     drop_na(country) %>%
-  #     mutate(is_average = TRUE),
-  #   aes(
-  #     x = Estimate,
-  #     shape = CI.Lower > 0 | CI.Upper < 0,
-  #     group = interaction(country, Hypothesis),
-  #     ),
-  #   position = position_dodgev(.7),
-  #   size = .5, alpha = .3
-  # ) +
   facet_wrap(
@@
   )
+trends_demo
+```
+
+```{r}
+fits %>% 
+  mutate(
+    out = map(
+      fit1,
+      ~fixef(.x) %>% as.data.frame() %>% rownames_to_column("term")
+    )
+  ) %>% 
+  select(outcome, out) %>% 
+  unnest(out) %>% 
+  filter(str_detect(term, "year:")) %>% 
+  mutate(across(where(is.numeric), ~number(., .001))) %>% 
+  kbl(caption = "Model 1 interaction parameters") %>% 
+  kable_custom()
+# contrasts(fits$fit1[[4]]$data$age)
+# fixef(fits$fit1[[3]])
 ```
@@
 ### Associations
+
+```{r}
+fits <- tibble(outcome = oo) %>% 
+  mutate(outcome = factor(outcome, levels = oo)) %>% 
+  mutate(
+    fit2 = map(
+      outcome, 
+      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
+    )
+  )
+```
 
@@
 #| label: fig-forest-association-demo
-h_gwp <- c(
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
+
+tmp <- fits %>% 
+  mutate(
+    out = map(
+      fit2,
+      ~emtrends(.x, specs = c("sex", "age"), var = "year")
     )
-h_gbd <- c(
-  `10 to 14` =
-    "i1_cw + age1:i1_cw * 1 + age2:i1_cw * 0 = 0",
-  `15 to 19` =
-    "i1_cw + age1:i1_cw * 0 + age2:i1_cw * 1 = 0",
-  `20 to 24` =
-    "i1_cw + age1:i1_cw * -1 + age2:i1_cw * -1 = 0",
-  `Female` =
-    "i1_cw + sex1:i1_cw * 1 = 0",
-  `Male` =
-    "i1_cw + sex1:i1_cw * -1 = 0"
   )
 
-sexage_draws <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
+tmp <- tmp %>% 
   mutate(
-    samples = map2(
-      fit2, h,
-      ~ simple_effects_samples(.x, .y)
+    out2 = map(
+      out,
+      ~gather_emmeans_draws(.x)
     )
   ) %>% 
-  select(outcome, samples) %>%
-  unnest(samples)
-sexage_sums <- fits %>%
-  mutate(h = list(h_gwp, h_gwp, h_gwp, h_gbd, h_gbd, h_gbd)) %>%
-  mutate(
-    sums = map2(
-      fit2, h,
-      ~ simple_effects_summary(.x, .y)
-    )
-  ) %>%
-  select(outcome, sums) %>%
-  unnest(sums)
+  select(outcome, out2)
 
-sexage_draws <- sexage_draws %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(is_average = region == "Average") %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(
-    side = if_else(Hypothesis %in% c("15 to 19", "Female"), "top", "bottom")
-  )
-
-sexage_sums <- sexage_sums %>%
-  mutate(f = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>%
-  mutate(region = fct_relevel(region, "Average"))
-
-# Plot averages and regions
-sexage_draws %>%
-  ggplot(aes(value, region, fill = Hypothesis, col = Hypothesis)) +
-  scale_color_brewer(
-    "Group",
-    palette = "Dark2",
-    aesthetics = c("fill", "color")
+associations_demo <- tmp %>% 
+  unnest(out2) %>% 
+  mutate(Hypothesis = paste(sex, age, sep = " ")) %>% 
+  ggplot(
+    aes(.value, Hypothesis)
   ) +
-  scale_alpha_manual(values = c(.4, .8), guide = "none") +
   geom_vline(xintercept = 0, lty = 2, size = .2) +
@@
   scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
+    expand = expansion(c(0.1, .1))
   ) +
   scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(3),
-    labels = function(x) {
-      percent(x / 100, .01) %>%
-        str_remove("\\.00") %>%
-        str_remove("(?<=[0-9])0")
-    },
-    expand = expansion(c(-.05, -.05))
+    "Conditional lagged effect of 10% increase in internet adoption",
+    breaks = extended_breaks(5),
+    labels = ~percent(. / 1000, .001) %>% 
+      # Remove trailing zeroes
+      str_remove("[\\.000](?=%)") %>% 
+      str_remove("[\\.00](?=%)"),
+    expand = expansion(c(.05, .05))
   ) +
@@
   )
+associations_demo
 ```
+
+```{r}
+trends_demo /
+  associations_demo
+```
+
+```{r}
+fits %>% 
+  mutate(
+    out = map(
+      fit2,
+      ~fixef(.x) %>% as.data.frame() %>% rownames_to_column("term")
+    )
+  ) %>% 
+  select(outcome, out) %>% 
+  unnest(out) %>% 
+  filter(str_detect(term, ":i1_cw")) %>% 
+  mutate(across(where(is.numeric), ~number(., .001))) %>% 
+  kbl(caption = "Model 2 interaction parameters") %>% 
+  kable_custom()
+```

### 2022-01-28 00-clean.qmd
Update GBD data with older ages

@@
 # Confirm that correct measures were downloaded:
-# distinct(gbd, measure, metric)
+distinct(gbd, measure, metric)
 gbd <- select(gbd, -metric, -measure)
@@
   select(-c(upper, lower))
-
-# Focus on young people
-gbd <- gbd %>%
-  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
 ```

### 2022-01-28 00-clean.qmd
USe more GWP age groups

@@
 # Categorize ages
+gwp <- filter(gwp, age <= 89)
 gwp <- gwp %>%
@@
       age,
-      breaks = seq(15, 105, by = 5),
+      breaks = seq(15, 90, by = 5),
       include.lowest = TRUE,
       right = FALSE,
-      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
+      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
     ) %>% as.character()
@@
 gwp <- drop_na(gwp, age)
-
-# Focus on young people
-gwp <- gwp %>%
-  filter(age %in% c("15 to 19", "20 to 24"))
 ```
@@
   summarise(
-    se = sd(val, na.rm = TRUE) / sqrt(n()),
+    n = n(),
+    se = sd(val, na.rm = TRUE) / sqrt(n),
     val = mean(val, na.rm = TRUE)

### 2022-01-31 associations.Rmd
Use .Rmd

--- 2022-01-10 02-associations.qmd
@@
   mutate(
-    fit1 = map(
-      outcome, 
-      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
-    ),
     fit2 = map(
@@
 #| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
+#| tbl-cap: "Model 1 and 2 proportions variance explained"
 #| label: tbl-m12-r2
 
-fits %>%
+# Takes a while so save to file
+r2_file_path <- "models/m12r2.rds"
+if (!file.exists(r2_file_path)) {
+  fits <- fits %>% 
+    mutate(
+      fit1 = map(
+        outcome, 
+        ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
+      )
+    )
+
+  r2_tab <- fits %>%
     select(outcome, fit1, fit2) %>% 
@@
     ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
+    mutate(outcome = str_replace(outcome, "_", " "))
+  write_rds(r2_tab, r2_file_path)
+  fits <- select(fits, -fit1)
+} else {r2_tab <- read_rds(r2_file_path)}
+
+r2_tab %>% 
   kbl(caption = "Model 1 and 2 R-squared values") %>%
   kable_custom()
-fits <- select(fits, -fit1)
+
+read_docx() %>% 
+  body_add_table(
+    r2_tab,
+    first_column = TRUE
+  ) %>% 
+  print("Table-R2.docx")
 ```
@@
   scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
+    "Conditional lagged effect of 10% increase in internet adoption",
     breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
+    labels = function(x) percent(x / 1000, .001) %>% 
+      str_remove("\\.000") %>% 
+      # Remove trailing zero (twice)
+      str_remove("(?<=[:digit:])0(?=%)") %>% 
+      str_remove("(?<=[:digit:])0(?=%)"),
+    expand = expansion(c(.15, .15))
   ) +
@@
       drop_na(country) %>%
+      filter(!(outcome=="Selfharm" & abs(Estimate) > .05)) %>% 
       mutate(is_average = TRUE),
@@
             outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
+            percent(. / 1000, .0001),
+            percent(. / 1000, .01)
           )
@@
       ),
-    family = Font,
+    family = Font, lineheight = 1,
     alpha = 1, size = 3, hjust = 1, vjust = 0.2,
@@
     axis.text.y = element_markdown(),
+    panel.spacing.x = unit(10, "pt"), 
+    plot.margin = unit(rep(10, 4), "pt"),
     legend.position = "none"
   )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
+x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/1000)
 x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
+
+# How many selfharm countries not shown on plot for clarity?
+p_sums %>%
+  filter(outcome=="Selfharm") %>% 
+  drop_na(country) %>% 
+  mutate(extreme = abs(Estimate) > .05) %>% 
+  janitor::tabyl(extreme)
+
+# Numbers
+p_sums %>% 
+  filter(region=="Average") %>% 
+  mutate(across(where(is.numeric), ~percent(./1000, .0001))) %>% 
+  transmute(
+    outcome,
+    result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]")
+  )
 ```
@@
 This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
+First, on average across regions and countries, a 10% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
 However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
@@
     ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
+    distinct(country, region, i1_cw, i1_cb) %>%
     mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
+  newy <- bind_cols(
+    newx, 
+    as.data.frame(fitted(x, newdata = newx))
+  )
   newy
@@
   newx <- x$data %>%
-    group_by(outcome, region) %>%
+    group_by(region) %>%
     summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
@@
         re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
+          (year * sex * age + i1_cw * sex * age | region)
         )
     )
-  ) %>%
-    select(-outcome)
+  )
   newy
@@
     panel.spacing = unit(2, "pt"),
+    aspect.ratio = 1,
     axis.title.y = element_blank()
@@
   newx <- x$data %>%
-    group_by(outcome, region, country) %>%
+    group_by(region, country) %>%
     summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
@@
     )
-  ) %>%
-    select(-outcome)
+  )
   newy

### 2022-02-01 clean.Rmd
Take out gwpi

--- 2022-01-28 00-clean.qmd
@@
-# Data preparation {.unnumbered}
+# Data preparation
 
@@
     WP60, WP61, WP63, WP65, WP67,
-    WP68, WP69, WP70, WP71, WP74,
-    WP16056
+    WP68, WP69, WP70, WP71, WP74
   )
@@
       WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74,
-      WP16056
+      WP68, WP69, WP70, WP71, WP74
     )
@@
     # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .),
-    # Internet (fix NAs and reverse 1:yes 2:no coding to 1:no 2:yes)
-    gwpi = 2 - if_else(between(wp16056, 1, 2), wp16056, NaN)
+    across(wp60:wp74, ~ 3 - .)
   )
@@
 gwp <- gwp %>%
-  # Aggregate internet
-  group_by(country, year, sex, age) %>% 
-  mutate(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
   pivot_longer(
@@
   ) %>%
-  group_by(country, year, sex, age, outcome, gwpi) %>%
+  group_by(country, year, sex, age, outcome) %>%
   summarise(
@@
   set.seed(101010)
-  distinct(gwp, outcome, country, year, sex, age, gwpi) %>% 
-    mutate(
-      se = rnorm(
-        nrow(.), 
-        mean(gwp$se, na.rm = TRUE), 
-        sd(gwp$se, na.rm = TRUE)
-      ),
-      val = rnorm(
-        nrow(.), 
-        mean(gwp$val, na.rm = TRUE), 
-        sd(gwp$val, na.rm = TRUE)
-      )
-    ) %>% 
-    write_rds(gwp_mock_path, compress = "xz")
+  # TODO
 }
@@
 itu_long <- itu %>%
-  pivot_longer(c(internet, fixed, mobile))
+  pivot_longer(c(internet, mobile))
 
@@
 
-## GWP summary table
+## Prepare model data
 
-```{r gwp-summary-table}
-#| column: page-right
-#| tbl-cap: "Mean internet user percentages across regions and time from the GWP data."
-#| label: tbl-gwpsummary
+-   Create lagged and centered predictors
+-   Transform edge values of internet variable to fit beta
+    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
+-   Join outcome and predictor tables
+-   Center year on 2010 (roughly in the middle)
+-   Ensure that age and sex are treated with contrast codes
 
-gwp %>%
-  filter(year >= 2015) %>% 
-  group_by(region, country, year) %>%
-  summarise(gwpi = mean(gwpi, na.rm = TRUE)) %>% 
+```{r model-prepare-data}
+# Create lagged predictors
+itu <- itu %>% 
+  arrange(region, country, year) %>%
+  group_by(region, country) %>%
+  mutate(
+    across(
+      c(internet, mobile),
+      list(`1` = ~ lag(., 1)),
+      .names = "{str_sub(.col, 1, 1)}{.fn}"
+    )
+  ) %>% 
+  ungroup()
+
+# Centering predictors within and between countries
+itu <- itu %>%
+  group_by(country) %>%
+  mutate(
+    i1_cb = mean(i1, na.rm = TRUE), # Country average
+    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
+    m1_cb = mean(m1, na.rm = TRUE),
+    m1_cw = m1 - m1_cb,
+  ) %>%
+  # Grand-mean center the country averages
   ungroup() %>% 
-  mutate(gwpi = gwpi * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  arrange(year, region, country) %>% 
-  pivot_wider(names_from = year, values_from = gwpi) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(
-    caption = "GWP Internet use summary (mean over demographics)"
-  ) %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
+  mutate(
+    across(c(i1_cb, m1_cb), ~ . - mean(., na.rm = T))
+  )
+
+# Transform internet edge cases
+itu <- itu %>%
+  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
+  mutate(internet = if_else(internet == 1, .9999999, internet))
+
+# Stack outcome data
+dat <- bind_rows(gwp, gbd)
+
+# Merge predictors to outcomes
+dat <- left_join(dat, itu)
+
+# Center and scale year
+dat <- dat %>%
+  mutate(year = (year - 2010) / 10)
+
+# Identify values to use in mv models
+# Indicate unique ITU values for MV model
+dat <- dat %>%
+  # Unique values exist for each country-year, but must be given for each
+  # outcome
+  group_by(region, country, year, outcome) %>%
+  mutate(itu = 1:n() == 1) %>%
+  ungroup()
+
+# Ensure that categorical variables are factors
+dat <- dat %>%
+  mutate(across(c(sex, age), factor))
+
+# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
+dat <- dat %>%
+  mutate(across(c(val, se), ~ . * 100))
+
+# Arrange on outcome
+oo <- c(
+  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
+  "Anxiety", "Depression", "Selfharm"
+)
+dat <- dat %>%
+  mutate(outcome = factor(outcome, levels = oo)) %>% 
+  arrange(outcome, region, country, year)
+
+# Selfharm models don't converge with SEs
+dat <- dat %>% 
+  mutate(se = if_else(outcome == "Selfharm", 0, se))
 ```
@@
 ```{r}
+write_rds(dat, "data/data-all.rds")
 write_rds(itu, "data/itu.rds")

### 2022-02-01 models.Rmd
Use .Rmd
Estimate models in script

--- 2022-01-10 00-models.qmd
@@
-# Model fitting {.unnumbered}
+# Models
 
@@
 library(mgcv)
-library(brms)
 library(cmdstanr)
@@
 library(broom)
+library(brms)
 library(tidyverse)
-
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
-nchains <- 4
-options(brms.backend = "cmdstanr")
-hmc <- list(
-  chains = nchains,
-  cores = nchains,
-  threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1000,
-  refresh = 50,
-  adapt_delta = .90,
-  max_treedepth = 10
-)
-
-# Create directory for intermediate files
-dir.create("models", FALSE)
-
-# Load data sets
-itu <- read_rds("data/itu.rds")
-gwp <- read_rds("data/gwp.rds")
-gbd <- read_rds("data/gbd.rds")
 ```
@@
 ## Model 1
-
-We first prepare the variables for modelling:
-
--   Create lagged and centered predictors
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
--   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
-
-```{r model1-prepare-data}
-# Create lagged predictors
-itu <- itu %>% 
-  arrange(region, country, year) %>%
-  group_by(region, country) %>%
-  mutate(
-    across(
-      c(internet, fixed, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-itu <- itu %>%
-  group_by(country) %>%
-  mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    f1_cb = mean(f1, na.rm = TRUE),
-    f1_cw = f1 - f1_cb,
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
-  ) %>%
-  # Grand-mean center the country averages
-  mutate(
-    across(c(i1_cb, f1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
-
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center and scale year
-dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in mv models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
-  ungroup()
-
-# Ensure that factors are contrast coded
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
-
-# Arrange on outcome
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-dat <- dat %>%
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(dat, outcome, region, country, year)
-
-dat %>%
-  group_by(outcome) %>%
-  summarise(
-    min = min(val, na.rm = TRUE),
-    max = max(val, na.rm = TRUE),
-    internet_min = min(internet, na.rm = TRUE),
-    internet_max = max(internet, na.rm = TRUE)
-  ) %>%
-  kable(digits = 7) %>% 
-  kable_custom()
-```
 
@@
 #| echo: true
-# Define a model of internet proportion over year
-bf_itu <- bf(
-  internet | resp_subset(itu) ~
-  year +
-    (year |c| country) +
-    (year |r| region),
-  family = Beta()
-)
 ```
@@
 #| echo: true
-# Meta-regression model of outcomes
-bf_1 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age +
-    (year * sex + year * age | c | country) +
-    (year * sex + year * age | r | region),
-  family = gaussian()
-)
 ```
@@
 
-```{r model1-selfharm-se}
-#| echo: true
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
-
 ### Fitting
-
-We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.
 
@@
 #| cache: false
-fits <- dat %>%
-  # Could nest but need this to include group key in nested tibble
-  group_by(outcome) %>%
-  summarise(data = list(cur_data_all()))
 
-fits <- fits %>%
-  mutate(
-    fit1 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_itu + bf_1 + set_rescor(FALSE),
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-1-internet")
-      )
-    )
-  )
 ```
@@
 #| results: hide
-# Model formula is only a small update to Model 1
-bf_2 <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
-    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
-  family = gaussian()
-)
 
-# As above with model 1
-# Note we don't need to save these in the R environment, just files
-fits %>%
-  mutate(
-    fit2 = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-internet")
-      )
-    )
-  )
 ```
@@
 #| results: hide
-bf_2_f <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
-    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
 
-bf_2_m <- bf(
-  val | resp_se(se, sigma = TRUE) ~
-  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
-    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
-  family = gaussian(),
-  unused = ~outcome
-)
-
-fits %>%
-  mutate(
-    fit2_f = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2_f,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-fixed")
-      )
-    )
-  )
-
-fits %>%
-  mutate(
-    fit2_m = map2(
-      data, outcome,
-      ~brm(
-        formula = bf_2_m,
-        data = .x,
-        chains = hmc$chains,
-        cores = hmc$cores,
-        threads = hmc$threads,
-        iter = hmc$iter,
-        warmup = hmc$warmup,
-        refresh = hmc$refresh,
-        control = list(
-          adapt_delta = hmc$adapt_delta,
-          max_treedepth = hmc$max_treedepth
-        ),
-        file = str_glue("models/brm-{.y}-2-mobile")
-      )
-    )
-  )
 ```

### 2022-02-01 models.R

@@ -1,0 +1,155 @@
+# Independent script to fit models
+
+# Setup -------------------------------------------------------------------
+
+library(cmdstanr)
+library(brms)
+library(tidyverse)
+
+# MCMC settings (ensure at most 12 cores)
+ncores <- min(parallel::detectCores(logical = FALSE), 12)
+nchains <- 4
+options(brms.backend = "cmdstanr")
+hmc <- list(
+  chains = nchains,
+  cores = nchains,
+  threads = ncores %/% nchains,
+  iter = 2500,
+  warmup = 1250,
+  refresh = 100,
+  adapt_delta = .90,
+  max_treedepth = 10
+)
+
+# Create directory for intermediate files
+dir.create("models", FALSE)
+
+# Load data
+dat <- readRDS("data/data-all.rds")
+
+# Set global contrasts
+options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
+
+# Nest data frames to fit models programmatically
+fits <- dat %>%
+  group_by(outcome) %>%
+  nest() %>%
+  ungroup()
+
+# Model 1 formulas --------------------------------------------------------
+
+
+bf_itu <- bf(
+  internet | subset(itu) ~
+    year +
+    (year |c| country) +
+    (year |r| region),
+  family = Beta()
+)
+
+bf_1 <- bf(
+  val | se(se, sigma = TRUE) ~
+    year * sex +
+    (year * sex | c | country) +
+    (year * sex | r | region) +
+    (year * sex || age) +
+    (year * sex || age:country) +
+    (year * sex || age:region),
+  family = gaussian()
+)
+
+# Model 1 fit -------------------------------------------------------------
+
+
+fits %>%
+  mutate(
+    fit1 = walk2(
+      data, outcome,
+      ~brm(
+        formula = bf_itu + bf_1 + set_rescor(FALSE),
+        data = .x,
+        chains = hmc$chains,
+        cores = hmc$cores,
+        threads = hmc$threads,
+        iter = hmc$iter,
+        warmup = hmc$warmup,
+        refresh = hmc$refresh,
+        control = list(
+          adapt_delta = hmc$adapt_delta,
+          max_treedepth = hmc$max_treedepth
+        ),
+        save_pars = save_pars(group = c("country", "region", "age")),
+        file = str_glue("models/brm-{.y}-1-internet")
+      )
+    )
+  )
+
[…]

### 2022-02-01 submit.sh
slurm script

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+# Runs the R script serially
+# It requests 12 cores per model
+
+#SBATCH --nodes=1
+#SBATCH --ntasks-per-node=1
+#SBATCH --cpus-per-task=12
+#SBATCH --mem-per-cpu=2G
+#SBATCH --time=48:00:00
+#SBATCH --job-name=Global-WBMH
+#SBATCH --output=global-wbmh-slurm.out
+
+module purge
+module load R/4.1.2-foss-2021b-ARC
+
+Rscript models.R

### 2022-02-02 models.R
Edit slurm settings

@@ -1,21 +1,26 @@
 # Independent script to fit models
 
-# Setup -------------------------------------------------------------------
+# Accept outcome names as command line arguments
+cmdargs <- commandArgs(trailingOnly = TRUE)
+cat("Estimating model for outcome(s)", paste(cmdargs, collapse = ", "), "\n")
+
+
+# ---- setup ---------------------------------------------------------------
 
 library(cmdstanr)
 library(brms)
 library(tidyverse)
 
-# MCMC settings (ensure at most 12 cores)
-ncores <- min(parallel::detectCores(logical = FALSE), 12)
+# MCMC settings (max 12 cores)
+(ncores <- min(parallel::detectCores(logical = FALSE), 12))
 nchains <- 4
 options(brms.backend = "cmdstanr")
 hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = ncores %/% nchains,
-  iter = 2500,
-  warmup = 1250,
+  iter = 3000,
+  warmup = 1500,
   refresh = 100,
   adapt_delta = .90,
   max_treedepth = 10
@@ -31,12 +36,16 @@ dat <- readRDS("data/data-all.rds")
 options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
 
 # Nest data frames to fit models programmatically
+# Fit models only to outcome(s) specified in command line arguments
 fits <- dat %>%
   group_by(outcome) %>%
   nest() %>%
   ungroup()
 
-# Model 1 formulas --------------------------------------------------------
+# Use command line arguments
+fits <- fits[cmdargs, ]
+
+# model-1 -----------------------------------------------------------------
 
 
 bf_itu <- bf(
@@ -58,9 +67,6 @@ bf_1 <- bf(
   family = gaussian()
 )
 
-# Model 1 fit -------------------------------------------------------------
-
-
 fits %>%
   mutate(
     fit1 = walk2(
@@ -78,21 +84,23 @@ fits %>%
           adapt_delta = hmc$adapt_delta,
           max_treedepth = hmc$max_treedepth
         ),
-        save_pars = save_pars(group = c("country", "region", "age")),
         file = str_glue("models/brm-{.y}-1-internet")
       )
     )
   )
 
-# Model 2 -----------------------------------------------------------------
+# model-2 -----------------------------------------------------------------
 
 
[…]

### 2022-02-02 submit.sh

@@ -1,17 +1,16 @@
 #!/bin/bash
 
-# Runs the R script serially
+# Runs the R script models.R with arguments from --array
 # It requests 12 cores per model
+# Use sbatch --array=1-6 to use a job array to submit 6 tasks
 
-#SBATCH --nodes=1
-#SBATCH --ntasks-per-node=1
+#SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=12
 #SBATCH --mem-per-cpu=2G
-#SBATCH --time=48:00:00
-#SBATCH --job-name=Global-WBMH
-#SBATCH --output=global-wbmh-slurm.out
+#SBATCH --time=00:02:00
+#SBATCH --job-name=DWG-Global
 
 module purge
 module load R/4.1.2-foss-2021b-ARC
 
-Rscript models.R
+Rscript models.R $SLURM_ARRAY_TASK_ID

### 2022-02-02 submit.sh
Need filename duh

@@ -2,7 +2,7 @@
 
 # Runs the R script models.R with arguments from --array
 # It requests 12 cores per model
-# Use sbatch --array=1-6 to use a job array to submit 6 tasks
+# Use sbatch submit.sh --array=1-6 to use a job array to submit 6 tasks
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=12

### 2022-02-02 models.R
Prepare for takeoff

@@ -2,7 +2,7 @@
 
 # Accept outcome names as command line arguments
 cmdargs <- commandArgs(trailingOnly = TRUE)
-cat("Estimating model for outcome(s)", paste(cmdargs, collapse = ", "), "\n")
+cat("\n***\nEstimating model for outcome(s)", paste(cmdargs, collapse = ", "), "\n***\n")
 
 
 # ---- setup ---------------------------------------------------------------

### 2022-02-02 submit.sh

@@ -2,12 +2,12 @@
 
 # Runs the R script models.R with arguments from --array
 # It requests 12 cores per model
-# Use sbatch submit.sh --array=1-6 to use a job array to submit 6 tasks
+# Use sbatch --array=1-6 submit.sh to use a job array to submit 6 tasks
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=12
 #SBATCH --mem-per-cpu=2G
-#SBATCH --time=00:02:00
+#SBATCH --time=24:00:00
 #SBATCH --job-name=DWG-Global
 
 module purge

### 2022-02-02 timecourses.Rmd
Revise for new RE structure

--- 2022-01-27 01-timecourses.qmd
@@
 library(ggstance)
-library(mgcv)
-library(cmdstanr)
 library(officer)
+library(bayestestR)
 library(ellipse)
 library(ggh4x)
+library(mgcv)
 library(tidybayes)
@@
 library(tidyverse)
-```
 
-```{r load}
-#| cache: false
 # Load data sets
@@
 fits <- tibble(outcome = oo) %>% 
+  slice(1:3) %>% 
   mutate(outcome = factor(outcome, levels = oo)) %>% 
@@
 
-Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)?
-And, do changes in well-being correlate with changes in internet adoption (RQ1b)?
+Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time?
+And, do changes in well-being correlate with changes in internet adoption?
 To answer, we examine Model 1's results.
 
-## Results
+## Data figure
 
-### RQ1a: Temporal trends
+```{r trends-regions}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 8
+#| fig-cap: "Trends in all variables across regions"
+#| label: fig-trends-regions
+
+# Stack data sets
+# Assume all outcomes are proportions (0-1)
+# Draw small multiples figure, outcomes x regions
+bind_rows(
+  gwp,
+  gbd,
+  itu %>% mutate(outcome = "Internet", val = internet)
+) %>%
+  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
+  group_by(region, country, year, outcome) %>%
+  summarise(mean = mean(val, na.rm = TRUE)) %>%
+  ungroup() %>% 
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(year, mean)) +
+  scale_y_continuous(
+    "Value",
+    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
+    breaks = pretty_breaks()
+  ) +
+  scale_x_date(
+    "Year",
+    date_breaks = "5 years",
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country, outcome)),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  stat_summary(
+    fun = mean, geom = "line",
+    size = .6, color = "dodgerblue4"
+  ) +
+  facet_grid(
+    outcome ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
+    aspect.ratio = 1,
+    legend.position = "none",
+    panel.spacing = unit(4, "pt"),
+    axis.title.y = element_blank()
+  )
+```
+
+```{r}
+tmp <- itu %>% 
+  arrange(country, year) %>% 
+  group_by(country) %>% 
+  mutate(i = internet - lag(internet)) %>% 
+  summarise(i = mean(i, na.rm = TRUE))
+internet_yoy <- percent(mean(tmp$i, na.rm = TRUE), .1)
+```
+
+Average year-on-year increase in internet adoption was `r internet_yoy`.
+
+## Main result: Trends
+
+```{r}
+get_tab <- function(pattern, label, sort = outcome) {
+  fits %>% 
+    mutate(
+      out = map(
+        fit1,
+        ~as_draws_df(
+          .x, 
+          variable = pattern, 
+          regex = TRUE
+        ) %>% 
+          summarise_draws(
+            mean, 
+            ~quantile2(., probs = c(.025, .975)),
+            pd = ~pd(as.numeric(.)), 
+            rhat
+            )
+      )
+    ) %>% 
+    select(outcome, out) %>% 
+    unnest(out) %>% 
+    mutate(pd = percent(pd, .1)) %>% 
+    arrange({{sort}}) %>% 
+    kbl(digits = 2, caption = label) %>% 
+    kable_custom()
+}
+
+get_tab(
+  "b_val_(Intercept|year)$", 
+  "Model 1: Population level effects",
+  variable
+)
+```
+
+This table shows the population-level (average across region, country, age) intercepts and time-courses.
+Negative experiences had increased.
+We then summarise the region- and country-level trends in a table.
+
+```{r}
+get_coeftab <- function(x, group) {
+  coef(x, summary = FALSE)[[group]][,,"val_year"] %>% 
+    summarise_draws(
+      mean, 
+      ~quantile2(., probs = c(.025, .975)),
+      pd = ~pd(as.numeric(.)), 
+      rhat
+    ) %>% 
+    mutate(pd = percent(pd, .1))
+}
+
+val_year_region <- fits %>% 
+  mutate(out = map(fit1, ~get_coeftab(.x, "region"))) %>% 
+  select(outcome, out)
+val_year_country <- fits %>% 
+  mutate(out = map(fit1, ~get_coeftab(.x, "country"))) %>% 
+  select(outcome, out)
+
+bind_rows(
+  "region" = val_year_region,
+  "country" = val_year_country,
+  .id = "Grouping"
+) %>% 
+  unnest(out) %>% 
+  rename(Group = variable) %>% 
+  kbl(digits = 2, caption = "Country-specific timecourses") %>% 
+  kable_custom() %>% 
+  scroll_box("500px")
+```
 
 Before presenting the time trends, we must calculate the required quantities from the posterior distribution.
-Here we calculate posterior *samples* of region and average-level trends over time, and posterior *summaries* of trends at all levels.
+Here we calculate posterior samples of region and average-level trends over time, and posterior summaries of trends at all levels.
 
@@
 p_sums_internet <- fits %>%
-  mutate(psums = map(fit1, ~ psums(.x, "internet_year"))) %>%
+  mutate(psums = map(fit1, ~psums(.x, "internet_year"))) %>%
   select(outcome, psums) %>%
@@
     "outcome",
-    nrow = 2, scales = "free_x",
+    nrow = 1, scales = "free_x",
     labeller = as_labeller(~ str_replace(., "_", " "))
@@
 
-::: {.panel-tabset .column-screen-inset-right}
-#### All outcomes
-
-```{r trends-regions}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 8
-#| fig-cap: "Trends in all variables across regions"
-#| label: fig-trends-regions
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-dat_all <- bind_rows(
-  gwp,
-  gbd,
-  itu %>% mutate(outcome = "Internet", val = internet)
-) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup()
-
-# Draw small multiples figure, outcomes x regions
-dat_all %>% 
-  mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
-  scale_y_continuous(
-    "Value",
-    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
-    breaks = pretty_breaks()
-  ) +
-  scale_x_date(
-    "Year",
-    date_breaks = "5 years",
-    date_labels = "'%y",
-    expand = expansion(.02)
-  ) +
-  geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
-  ) +
-  stat_summary(
-    fun = mean, geom = "line",
-    size = .6, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    aspect.ratio = 1,
-    legend.position = "none",
-    panel.spacing = unit(3, "pt"),
-    axis.title.y = element_blank()
-  )
-```
-
-#### Life satisfaction
-
-```{r trends-ls}
-f_country <- fits %>%
-  mutate(fc = map(fit1, fitted_country)) %>%
-  select(outcome, fc)
-
-#' Draw a panel plot of countries' fitted values and data
-#'
-#' @param x fitted country level data from fitted_country()
-#' @param y outcome
-#'
-#' @return a ggplot for that outcome
-plot_country <- function(x, y) {
-  coefs <- p_sums %>%
-    drop_na(country) %>%
-    filter(outcome == y) %>%
-    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
-    mutate(country = fct_reorder(country, coef))
-  x %>%
-    left_join(coefs) %>%
-    mutate(country = fct_reorder(country, coef)) %>%
-    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
-    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
-    scale_y_continuous(
-      str_replace(y, "_", " "),
-      breaks = pretty_breaks(),
-      expand = expansion(.15),
-      labels = function(x) {
-        percent(x / 100, .01) %>%
-          str_remove("\\.00")
-      }
-    ) +
-    # Add parameters in text
-    geom_richtext(
-      data = coefs %>%
-        mutate(across(where(is.numeric), ~ number(., .01))),
-      aes(
-        x = make_date(2000), y = Inf,
-        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
-      ),
-      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
-      family = Font,
-      fill = alpha("white", .3), label.color = NA,
-      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
-    ) +
-    geom_point(aes(y = val), shape = 1, alpha = .5) +
-    geom_ribbon(
-      aes(ymin = Q2.5, ymax = Q97.5),
-      alpha = .3, col = NA, fill = "dodgerblue1"
-    ) +
-    geom_line(
-      size = 0.5, col = "dodgerblue1"
-    ) +
-    facet_wrap(
-      "country"
-    ) +
-    theme(
-      panel.spacing = unit(2, "pt")
-    )
-}
-
-# Create the plot for each outcome
-f_country <- f_country %>%
-  mutate(
-    plot = map2(
-      fc, outcome,
-      ~ plot_country(.x, .y)
-    )
-  )
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
-#| label: fig-trends-ls
-f_country$plot[[1]]
-```
-
-#### Negative experiences
-
-```{r trends-ne}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Negative experiences trends, ordered by association magnitude"
-#| label: fig-trends-ne
-f_country$plot[[2]]
-```
-
-#### Positive experiences
-
-```{r trends-pe}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Positive experiences trends, ordered by association magnitude"
-#| label: fig-trends-pe
-f_country$plot[[3]]
-```
-
-#### Anxiety
-
-```{r trends-anx}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Anxiety trends, ordered by association magnitude"
-#| label: fig-trends-anx
-f_country$plot[[4]]
-```
-
-#### Depression
-
-```{r trends-dep}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Depression trends, ordered by association magnitude"
-#| label: fig-trends-dep
-f_country$plot[[5]]
-```
-
-#### Self-harm
-
-```{r trends-sel}
-#| echo: false
-#| fig-width: 12
-#| fig-height: 10
-#| fig-cap: "Self-harm trends, ordered by association magnitude"
-#| label: fig-trends-sel
-f_country$plot[[6]]
-```
-:::
-
-### RQ1b: Correlations
+## Main result: Correlations
 
@@
   mutate(across(where(is.numeric), ~ number(., .01)))
+
+# Display table and print in word document
+cor_tab <- cor_pars %>% 
+  transmute(
+    outcome = str_replace(outcome, "_", " "), 
+    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
+  )
+cor_tab %>%   
+  kbl(caption = "Between-country trend correlation parameters") %>% 
+  kable_custom()
+
+read_docx() %>% 
+  body_add_table(
+    cor_tab,
+    first_column = TRUE
+  ) %>% 
+  print("Table-correlations.docx")
 
@@
 
-```{r}
-# Display table and print in word document
-cor_tab <- cor_pars %>% 
-  transmute(
-    outcome = str_replace(outcome, "_", " "), 
-    correlation = str_glue("{mean} [{q2.5}, {q97.5}]")
+## Country-specific lines
+
+::: {.panel-tabset .column-screen-inset-right}
+
+### Life satisfaction
+
+```{r trends-ls}
+f_country <- fits %>%
+  mutate(fc = map(fit1, fitted_country)) %>%
+  select(outcome, fc)
+
+#' Draw a panel plot of countries' fitted values and data
+#'
+#' @param x fitted country level data from fitted_country()
+#' @param y outcome
+#'
+#' @return a ggplot for that outcome
+plot_country <- function(x, y) {
+  coefs <- p_sums %>%
+    drop_na(country) %>%
+    filter(outcome == y) %>%
+    select(country, coef = Estimate, coef.l = Q2.5, coef.u = Q97.5) %>%
+    mutate(country = fct_reorder(country, coef))
+  x %>%
+    left_join(coefs) %>%
+    mutate(country = fct_reorder(country, coef)) %>%
+    ggplot(aes(make_date(year * 10 + 2010), Estimate)) +
+    scale_x_date("Year", date_breaks = "5 years", date_labels = "'%y") +
+    scale_y_continuous(
+      str_replace(y, "_", " "),
+      breaks = pretty_breaks(),
+      expand = expansion(.15),
+      labels = function(x) {
+        percent(x / 100, .01) %>%
+          str_remove("\\.00")
+      }
+    ) +
+    # Add parameters in text
+    geom_richtext(
+      data = coefs %>%
+        mutate(across(where(is.numeric), ~ number(., .01))),
+      aes(
+        x = make_date(2000), y = Inf,
+        label = str_glue("{coef}<br>[{coef.l}, {coef.u}]")
+      ),
+      size = 2.4, vjust = 1, hjust = 0.05, color = "black",
+      family = Font,
+      fill = alpha("white", .3), label.color = NA,
+      label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")
+    ) +
+    geom_point(aes(y = val), shape = 1, alpha = .5) +
+    geom_ribbon(
+      aes(ymin = Q2.5, ymax = Q97.5),
+      alpha = .3, col = NA, fill = "dodgerblue1"
+    ) +
+    geom_line(
+      size = 0.5, col = "dodgerblue1"
+    ) +
+    facet_wrap(
+      "country"
+    ) +
+    theme(
+      panel.spacing = unit(2, "pt")
     )
-cor_tab %>%   
-  kbl(caption = "Between-country trend correlation parameters") %>% 
-  kable_custom()
+}
 
-read_docx() %>% 
-  body_add_table(
-    cor_tab,
-    first_column = TRUE
-  ) %>% 
-  print("Table-correlations.docx")
+# Create the plot for each outcome
+f_country <- f_country %>%
+  mutate(
+    plot = map2(
+      fc, outcome,
+      ~ plot_country(.x, .y)
+    )
+  )
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Life satisfaction trends, ordered by association magnitude"
+#| label: fig-trends-ls
+f_country$plot[[1]]
 ```
 
-### Other results from Model 1
+### Negative experiences
 
-#### Shrinkage
+```{r trends-ne}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Negative experiences trends, ordered by association magnitude"
+#| label: fig-trends-ne
+f_country$plot[[2]]
+```
+
+### Positive experiences
+
+```{r trends-pe}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Positive experiences trends, ordered by association magnitude"
+#| label: fig-trends-pe
+f_country$plot[[3]]
+```
+
+### Anxiety
+
+```{r trends-anx}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Anxiety trends, ordered by association magnitude"
+#| label: fig-trends-anx
+f_country$plot[[4]]
+```
+
+### Depression
+
+```{r trends-dep}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Depression trends, ordered by association magnitude"
+#| label: fig-trends-dep
+f_country$plot[[5]]
+```
+
+### Self-harm
+
+```{r trends-sel}
+#| echo: false
+#| fig-width: 12
+#| fig-height: 10
+#| fig-cap: "Self-harm trends, ordered by association magnitude"
+#| label: fig-trends-sel
+f_country$plot[[6]]
+```
+:::
+
+## Other results
+
+### Shrinkage
 

### 2022-02-02 R/functions.R

@@ -36,23 +36,24 @@ msum <- function(x) {
   )
 }
 
-#' Posterior draws at average and region levels
+#' Posterior draws at average and grouping levels
 #'
-#' @param x brmsfit (model 1/2)
+#' @param x brmsfit model 1/2
 #' @param p name of parameter
+#' @param grouping the grouping factor (e.g. region)
 #'
-#' @return a long tibble posterior draws of p for every region (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year") {
+#' @return a long tibble of posterior draws of p for every group in grouping (including the average, so useful for e.g. forest plots)
+pdraws <- function(x, p = "val_year", grouping = "region") {
   bind_cols(
     tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)$region[, , p])
+    as_tibble(coef(x, summary = FALSE)[[grouping]][, , p])
   ) %>%
-    pivot_longer(everything(), names_to = "region")
+    pivot_longer(everything(), names_to = grouping)
 }
 
-#' Posterior summaries at country- region- and average levels
+#' Country-specific posterior summaries
 #'
-#' @param x brmsfit (model 1/2)
+#' @param x brmsfit model 1/2
 #' @param p name of parameter
 #'
 #' @return a long tibble with posterior summary of p at each level
@@ -99,7 +100,14 @@ fitted_country <- function(x) {
     mutate(sex = NA, age = NA, se = 0, itu = TRUE)
   newy <- bind_cols(
     newx,
-    as.data.frame(fitted(x, newdata = newx, resp = "val"))
+    as.data.frame(
+      fitted(
+        x,
+        newdata = newx,
+        resp = "val",
+        re_formula = ~ (year * sex | country) + (year * sex | region)
+        )
+      )
   )
   newy
 }

### 2022-02-03 models.R
Adjust model run options

@@ -7,6 +7,7 @@ cat("\n***\nEstimating model for outcome(s)", paste(cmdargs, collapse = ", "), "
 
 # ---- setup ---------------------------------------------------------------
 
+options(tidyverse.quiet = TRUE)
 library(cmdstanr)
 library(brms)
 library(tidyverse)
@@ -19,8 +20,8 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = ncores %/% nchains,
-  iter = 3000,
-  warmup = 1500,
+  iter = 2500,
+  warmup = 1250,
   refresh = 100,
   adapt_delta = .90,
   max_treedepth = 10
@@ -42,7 +43,7 @@ fits <- dat %>%
   nest() %>%
   ungroup()
 
-# Use command line arguments
+# Pick Nth row given by command line argument N (1-6)
 fits <- fits[cmdargs, ]
 
 # model-1 -----------------------------------------------------------------

### 2022-02-03 models.R
Adjust run parameters

@@ -89,6 +89,7 @@ fits %>%
       )
     )
   )
+message("\nModel 1 done\n")
 
 # model-2 -----------------------------------------------------------------
 
@@ -128,6 +129,7 @@ fits %>%
       )
     )
   )
+message("\nModel 2 done\n")
 
 # model-2-m ---------------------------------------------------------------
 
@@ -165,3 +167,4 @@ fits %>%
       )
     )
   )
+message("\nModel 2M done\n")

### 2022-02-03 submit.sh

@@ -7,7 +7,7 @@
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=12
 #SBATCH --mem-per-cpu=2G
-#SBATCH --time=24:00:00
+#SBATCH --time=4-00:00:00
 #SBATCH --job-name=DWG-Global
 
 module purge

### 2022-02-04 models.R
Fix formula

@@ -142,8 +142,7 @@ bf_2_m <- bf(
     ((year + m1_cw) * sex || age) +
     ((year + m1_cw) * sex || age:country) +
     ((year + m1_cw) * sex || age:region),
-  family = gaussian(),
-  unused = ~outcome
+  family = gaussian()
 )
 
 fits %>%

### 2022-03-17 models.R
Adjust HMC settings

@@ -4,7 +4,7 @@
 # of outcomes (6) and models (3)
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cmdargs <- as.numeric(cmdargs)
-cat("Fitting row", cmdargs)
+cat("\nFitting row\n", cmdargs)
 
 # ---- setup ---------------------------------------------------------------
 
@@ -21,11 +21,11 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = min(ncores %/% nchains, 2),
-  iter = 2500,
-  warmup = 1300,
+  iter = 2200,
+  warmup = 1100,
   refresh = 100,
-  adapt_delta = .90,
-  max_treedepth = 10
+  adapt_delta = .99,
+  max_treedepth = 15
 )
 
 # Create directory for intermediate files

### 2022-03-17 clean.Rmd
Also estimate model 1 for mobile

@@
   group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1) %>%
+  mutate(itu = 1:n() == 1, itum = 1:n() == 1) %>%
   ungroup()

### 2022-03-17 models.R

@@ -122,8 +122,19 @@ bf_3.s <- bf(
   family = gaussian()
 )
 
+bf_mobile <- bf(
+  mobile | subset(itum) ~
+    year +
+    (year |c| country) +
+    (year |r| region),
+  family = Beta()
+)
+
+bf_4 <- bf_mobile + bf_val + set_rescor(FALSE)
+bf_4.s <- bf_mobile + bf_val.s + set_rescor(FALSE)
+
 fits <- fits %>%
-  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3), model = 1:3))
+  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
 
 fits <- fits %>%
   mutate(
@@ -131,9 +142,11 @@ fits <- fits %>%
       outcome == "Selfharm" & model == 1 ~ list(bf_1.s),
       outcome == "Selfharm" & model == 2 ~ list(bf_2.s),
       outcome == "Selfharm" & model == 3 ~ list(bf_3.s),
+      outcome == "Selfharm" & model == 4 ~ list(bf_4.s),
       TRUE ~ bfrm
     )
-  )
+  ) %>%
+  arrange(model, outcome)
 
 
 

### 2022-03-17 submit.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 # Runs the R script models.R with arguments from --array
-# Use sbatch --array=1-18 submit.sh to use a job array to submit 6 tasks
+# Use sbatch --array=1-24 submit.sh to submit
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=8

### 2022-03-17 clean.Rmd
Also transform mobile edge values

@@
   mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
+  mutate(internet = if_else(internet == 1, .9999999, internet)) %>% 
+  mutate(mobile = if_else(mobile == 0, .0000001, mobile)) %>%
+  mutate(mobile = if_else(mobile == 1, .9999999, mobile))
 

### 2022-03-17 models.R
Linear model for mobile

@@ -126,8 +126,7 @@ bf_mobile <- bf(
   mobile | subset(itum) ~
     year +
     (year |c| country) +
-    (year |r| region),
-  family = Beta()
+    (year |r| region)
 )
 
 bf_4 <- bf_mobile + bf_val + set_rescor(FALSE)

### 2022-03-18 models.R
Adjust hmc

@@ -1,7 +1,7 @@
 # Independent script to fit models
 
-# command line argument must be 1-18 to pick a model from the combinations
-# of outcomes (6) and models (3)
+# command line argument must be 1-24 to pick a model from the combinations
+# of outcomes (6) and models (4)
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cmdargs <- as.numeric(cmdargs)
 cat("\nFitting row\n", cmdargs)
@@ -24,8 +24,8 @@ hmc <- list(
   iter = 2200,
   warmup = 1100,
   refresh = 100,
-  adapt_delta = .99,
-  max_treedepth = 15
+  adapt_delta = .95,
+  max_treedepth = 12
 )
 
 # Create directory for intermediate files

### 2022-03-21 associations.Rmd
bump

--- 2022-01-10 02-associations.qmd
@@
 library(kableExtra)
+library(memoise)
+library(cachem)
 library(ggstance)
+library(ggbeeswarm)
 library(mgcv)
 library(brms)
-library(cmdstanr)
-library(ellipse)
 library(ggh4x)
@@
 library(parameters)
+library(bayestestR)
 library(emmeans)
@@
 library(tidyverse)
+
+cd <- cache_disk("memoise_cache", max_size = Inf)
 ```
@@
 # Load data sets
-itu <- read_rds("data/itu.rds")
-gwp <- read_rds("data/gwp.rds")
-gbd <- read_rds("data/gbd.rds")
+dat <- read_rds("data/data-all.rds")
+
+# Countries and regions
+countries <- dat %>% 
+  distinct(region, country)
 
@@
 fits <- tibble(outcome = oo) %>% 
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  mutate(
-    fit1 = map(
-      outcome, 
-      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
-    ),
-    fit2 = map(
-      outcome, 
-      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
-    )
-  )
+  mutate(outcome = factor(outcome, levels = oo))
 ```
@@
 
-## Model comparison
+## Main result: Association
 
-First, we compared the R2 values between Models 1 and 2.
-This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2).
-However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.
+```{r}
+get_fixef <- function(outcome, var = "i1_cw"){
+  path <- str_glue("models/brm-{outcome}-2-internet.rds")
+  fixef(
+    readRDS(path), 
+    summary = FALSE
+  )[,var, drop = FALSE] %>% 
+    summarise_draws(
+      mean, sd,
+      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
+      pd = ~pd(as.numeric(.)), 
+      rhat
+    ) %>% 
+    mutate(pd = percent(pd, .1))
+}
+get_fixef <- memoise(get_fixef, cache = cd)
 
-```{r model21-compare}
-#| results: hold
-#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
-#| label: tbl-m12-r2
+fits_fixef <- fits %>% 
+  mutate(out = map(outcome, ~get_fixef(.x))) %>% 
+  select(outcome, out) %>% 
+  unnest(out)
 
-fits %>%
-  select(outcome, fit1, fit2) %>% 
-  pivot_longer(c(fit1, fit2)) %>% 
-  mutate(
-    r2 = map(
-      value,
-      ~ bayes_R2(., resp = "val") %>%
-        as.data.frame() %>%
-        mutate(across(everything(), ~ percent(., .1))) %>%
-        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
-    )
-  ) %>%
-  select(-value) %>%
-  unnest(r2) %>% 
-  pivot_wider(
-    names_from = name,
-    values_from = result,
-    names_prefix = "Model "
-  ) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  kbl(caption = "Model 1 and 2 R-squared values") %>%
+fits_fixef %>%
+  mutate(across(mean:q97.5, ~./10)) %>% 
+  kbl(digits = 2, caption = "Model 2 population level associations (% increase per 10% increase in internet adoption)") %>% 
   kable_custom()
-fits <- select(fits, -fit1)
 ```
 
-## Forest plot
+This table shows the population-level (average across region, country, age) associations. We then summarise the region- and country-level trends in a table.
 
-We then display summaries of the parameters' posterior distributions as forest plots, like above.
-Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).
+```{r}
+# Region coefficients
+get_region_coef <- function(outcome) {
+  path <- str_glue("models/brm-{outcome}-2-internet.rds")
+  coef(readRDS(path), summary = FALSE)$region[,,"i1_cw"] %>% 
+    summarise_draws(
+      mean, sd,
+      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
+      pd = ~pd(as.numeric(.)), 
+      rhat
+    ) %>% 
+    mutate(pd = percent(pd, .1))
+}
+get_region_coef <- memoise(get_region_coef, cache = cd)
 
-```{r forest-internet}
-#| column: screen-inset-right
-#| fig-width: 13
-#| fig-height: 8
-#| fig-cap: "Forest plot of internet associations"
-#| label: fig-forest-internet
+i1_cw_region <- fits %>% 
+  mutate(out = map(outcome, ~get_region_coef(.x))) %>% 
+  select(outcome, out) %>% 
+  unnest(out)
+i1_cw_region <- rename(i1_cw_region, region = variable)
 
-# Calculate parameters at all levels of analysis
-p_draws <- fits %>%
-  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
-  select(outcome, pdraws) %>%
-  unnest(pdraws)
-p_sums <- fits %>%
-  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
-  select(outcome, psums) %>%
-  unnest(psums)
-p_draws <- p_draws %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
-p_sums <- p_sums %>%
-  mutate(region = fct_relevel(region, "Average")) %>%
-  mutate(outcome = str_replace(outcome, "_", " ")) %>%
-  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
+# Country random deviations + region coefficients
+get_country_ranef <- function(outcome) {
+  path <- str_glue("models/brm-{outcome}-2-internet.rds")
+  ranef(readRDS(path), summary = FALSE)$country[,,"i1_cw"] %>% 
+    summarise_draws(
+      mean, sd,
+      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
+      pd = ~pd(as.numeric(.)), 
+      rhat
+    ) %>% 
+    mutate(pd = percent(pd, .1))
+}
+get_country_ranef <- memoise(get_country_ranef, cache = cd)
 
-p_draws %>%
-  mutate(is_average = region == "Average") %>%
-  ggplot(aes(value, region, fill = is_average)) +
-  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
-  scale_alpha_manual(values = c(.4, .8)) +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
+i1_cw_country <- fits %>% 
+  mutate(out = map(outcome, ~get_country_ranef(.x))) %>% 
+  select(outcome, out) %>% 
+  unnest(out)
+
+# Add region coefs
+i1_cw_country <- i1_cw_country %>% 
+  rename(country = variable) %>% 
+  left_join(countries) %>% 
+  left_join(
+    select(i1_cw_region, outcome, region, mean_region = mean)
+  ) %>% 
+  mutate(across(mean:q97.5, ~. + mean_region)) %>% 
+  # pd doesn't work without the region coefs
+  select(-mean_region, -pd)
+
+i1_cw_region %>% 
+  mutate(across(mean:q97.5, ~./10)) %>% 
+  arrange(outcome, mean) %>% 
+  kbl(
+    digits = 2, 
+    caption = "Region-specific associations, arranged by outcome and magnitude"
+  ) %>% 
+  kable_custom() %>% 
+  scroll_box("500px")
+
+i1_cw_country %>% 
+  mutate(across(mean:q97.5, ~./10)) %>% 
+  select(outcome, country, everything()) %>% 
+  arrange(outcome, mean) %>% 
+  kbl(
+    digits = 2, 
+    caption = "Country-specific associations, ordered by outcome and magnitude"
+  ) %>% 
+  kable_custom() %>% 
+  scroll_box("500px")
+```
+
+### Coefficient plot
+
+Putting these together into a plot
+
+```{r}
+tmp <- i1_cw_country %>%
+  mutate(Level = "Country") %>% 
+  mutate(s = sign(q2.5) == sign(q97.5))
+
+bind_rows(
+  "Average" = fits_fixef %>% mutate(region = "**Average**"),
+  "Region" = i1_cw_region,
+  .id = "Level"
+) %>% 
+  mutate(region = fct_relevel(region, "**Average**")) %>% 
+  mutate(s = sign(q2.5) == sign(q97.5)) %>% 
+  ggplot(aes(mean, region, col = Level, shape = s)) +
+  scale_color_manual(
+    values = c("dodgerblue4", "dodgerblue3", "dodgerblue3")
+  ) +
   scale_shape_manual(values = c(21, 19)) +
   scale_y_discrete(
-    expand = expansion(c(0.01, .1)),
-    labels = function(x) {
-      if_else(x == "Average", "**Average**", x) %>%
-        str_replace("_", " ")
-    }
+    labels = ~str_replace(., "_", " "),
+    expand = expansion(c(0.05, 0.05))
   ) +
   scale_x_continuous(
-    "Conditional effect of 100% increase in internet adoption on outcome",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
-    expand = expansion(c(.1, .1))
+    "Conditional lagged effect of 10% increase in internet adoption",
+    breaks = pretty_breaks(5),
+    # Effect of 10% increase
+    labels = function(x) percent(x / 1000, .001) %>% 
+      str_remove("\\.000") %>% 
+      str_remove("(?<=[0-9])0(?=%)"),
+    expand = expansion(c(0.025, .025))
   ) +
-  stat_halfeye(
-    point_interval = NULL, normalize = "panels",
-    height = .75, adjust = 1,
-    aes(alpha = is_average)
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_point(
+    data = tmp,
+    size = 1, col = "dodgerblue1", stroke = .3, alpha = .8,
+    position = position_quasirandom(width = .2, groupOnX = F)
   ) +
-  # Add country points
-  geom_point(
-    data = p_sums %>%
-      drop_na(country) %>%
-      mutate(is_average = TRUE),
-    aes(x = Estimate), size = 1, col = "dodgerblue1",
-    position = position_nudge(0, -0.075), alpha = .4
+  geom_linerange(
+    aes(xmin = q10, xmax = q90), size = 1, col = "dodgerblue4"
   ) +
-  stat_pointinterval(
-    alpha = 1, .width = c(.95),
-    interval_size = 1,
-    point_size = 1.75,
-    fill = "white",
-    aes(shape = after_stat(xmin > 0 | xmax < 0)),
-    position = position_nudge(0, 0)
+  geom_pointrangeh(
+    aes(xmin = q2.5, xmax = q97.5), col = "dodgerblue4",
+    fatten = 4, fill = "white", stroke = .8
   ) +
-  geom_richtext(
-    data = p_sums %>%
-      filter(is.na(country)) %>%
-      mutate(is_average = region == "Average") %>%
-      mutate(
-        across(
-          where(is.numeric),
-          ~ if_else(
-            outcome == "Selfharm",
-            percent(. / 100, .001),
-            percent(. / 100, .01)
-          )
-        )
-      ),
-    family = Font,
-    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
-    fill = NA, label.color = NA,
-    aes(
-      x = Inf,
-      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
-    )
-  ) +
+  # geom_richtext(
+  #   aes(x = Inf, label = str_glue("{percent(mean/100, .01)}<br>[{percent(q2.5/100, .01)} {percent(q97.5/100, .01)}]")), 
+  #   hjust = 1, vjust = 0.15, size = 2.7, lineheight = .9,
+  #   col = "black", fill = NA, label.color = NA
+  # ) +
   facet_wrap(
-    "outcome",
-    nrow = 2, scales = "free_x"
-  ) +
+    "outcome", scales = "free_x", ncol = 3,
+    labeller = as_labeller(~str_replace(., "_", " "))) +
   theme(
@@
   )
-x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
-x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
-```
-
-This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small.
-First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`.
-However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%.
-Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region.
-However, none of the average associations were credibly different from zero.
-The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.
-
-## Counterfactual plot
-
-To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.
-
-```{r model2-fitted-values}
-#| column: screen-inset-right
-#| fig-width: 13
-#| fig-height: 8
-#| fig-cap: "Counterfactual plot of internet associations"
-#| label: fig-fitted-internet
-
-fitted_country <- function(x) {
-  newx <- x$data %>%
-    group_by(country) %>%
-    mutate(
-      xmin = min(i1_cw, na.rm = TRUE),
-      xmax = max(i1_cw, na.rm = TRUE)
-    ) %>%
-    filter(i1_cw %in% c(xmin, xmax)) %>%
-    ungroup() %>%
-    distinct(country, region, outcome, i1_cw, i1_cb) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
-    select(-outcome)
-  newy
-}
-
-fitted_region <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region) %>%
-    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
-    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
-    mutate(year = 0, sex = NA, age = NA, se = 0)
-
-  newy <- bind_cols(
-    newx,
-    as.data.frame(
-      fitted(
-        x, 
-        newdata = newx, 
-        re_formula = ~ 
-          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
+agg_png(
+  "Fig-assc-coef.png", 
+  width = W, height = W*0.6, units = "in", res = 400
 )
-    )
-  ) %>%
-    select(-outcome)
-  newy
-}
-
-f_country <- fits %>%
-  mutate(fc = map(fit2, fitted_country)) %>%
-  select(outcome, fc) %>%
-  unnest(fc)
-
-f_region <- fits %>%
-  mutate(fr = map(fit2, fitted_region)) %>%
-  select(outcome, fr) %>%
-  unnest(fr)
-
-f_country %>%
-  ggplot(aes(i1_cw, Estimate)) +
-  scale_x_continuous(
-    "Previous year's internet adoption relative to country average in 2000-2020",
-    breaks = c(-.35, 0, .35),
-    labels = function(x) percent(x, 1)
-  ) +
-  scale_y_continuous(
-    "Estimate",
-    breaks = pretty_breaks(),
-    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
-  ) +
-  geom_blank() +
-  geom_ribbon(
-    data = f_region,
-    aes(ymin = Q2.5, ymax = Q97.5),
-    alpha = .15, fill = "dodgerblue4"
-  ) +
-  geom_line(
-    data = f_region,
-    col = "dodgerblue4", size = .6
-  ) +
-  geom_line(
-    aes(group = country),
-    size = .4, alpha = .35, col = "dodgerblue1"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
-    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
-  ) +
-  theme(
-    panel.spacing = unit(2, "pt"),
-    axis.title.y = element_blank()
-  )
+last_plot()
+dev.off()
 ```
@@
 
-fitted_cb1 <- function(x) {
-  newx <- x$data %>%
-    group_by(outcome, region, country) %>%
+fitted_cb1 <- function(outcome) {
+  fit <- readRDS(str_glue("models/brm-{outcome}-2-internet.rds"))
+  newx <- fit$data %>%
+    group_by(region, country) %>%
     summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
@@
       fitted(
-        x, 
+        fit, 
         newdata = newx, 
@@
     )
-  ) %>%
-    select(-outcome)
+  )
   newy
 }
+fitted_cb1 <- memoise(fitted_cb1, cache = cd)
+
 tmp <- fits %>% 
-  mutate(out = map(fit2, fitted_cb1)) %>% 
+  mutate(out = map(outcome, fitted_cb1)) %>% 
   select(outcome, out) %>%
@@
 
-cb1_pars <- fits %>%
-  mutate(
-    out = map(
-      fit2,
-      ~ as_draws_df(
-        .x,
+get_cor_par <- function(outcome) {
+  as_draws_df(
+    readRDS(str_glue("models/brm-{outcome}-2-internet.rds")),
     variable = "b_i1_cb"
@@
     summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
-    )
+}
+get_cor_par <- memoise(get_cor_par, cache = cd)
+
+cb1_pars <- fits %>%
+  mutate(
+    out = map(outcome, ~get_cor_par(.x))
   ) %>%
@@
     "Value",
-    labels = ~percent(./100)
+    labels = ~percent(./100),
+    breaks = extended_breaks()
   ) +
@@
   ) +
-  geom_line(aes(y = Estimate), col = "dodgerblue4") +
-  geom_text(
-    data = cb1_pars,
-    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
-    vjust = 1.3, hjust = -0.025, family = Font
+  geom_line(
+    aes(y = Estimate), 
+    col = "dodgerblue4", size = 1
   ) +
+  geom_smooth(
+    method = "lm", se = F, 
+    size = .5, col = "black", lty = 2
+  ) +
+  # geom_text(
+  #   data = cb1_pars,
+  #   aes(
+  #     x = -Inf, 
+  #     y = Inf, 
+  #     label = str_glue("{mean} [{q2.5}, {q97.5}]")
+  #   ),
+  #   vjust = 1.3, hjust = -0.025, size = 2.8, family = Font
+  # ) +
   facet_wrap(
     "outcome",
-    scales = "free_y", nrow = 2,
+    scales = "free_y", nrow = 1,
     labeller = as_labeller(~str_replace(., "_", " "))
@@
   )
+
+agg_png(
+  "Fig-assc-cor.png", 
+  width = W, height = W*0.2, units = "in", res = 400
+)
+last_plot()
+dev.off()
 ```
+
+Here are these correlations calculated from data
+
+```{r}
+# From data
+tmp <- dat %>% 
+  mutate(outcome = factor(outcome, levels = oo)) %>% 
+  group_by(outcome, country) %>% 
+  summarise(
+    val = mean(val, na.rm = TRUE),
+    internet = mean(i1_cb, na.rm = TRUE)
+  )
+tmp_tab <- tmp %>% 
+  summarise(
+    tidy(lm(scale(val) ~ scale(internet), data = cur_data()), conf.int = TRUE)
+  ) %>% 
+  ungroup() %>%
+  filter(term != "(Intercept)") %>% 
+  mutate(across(where(is.numeric), ~number(., .01))) %>% 
+  transmute(
+    Outcome = str_replace(outcome, "_", " "),
+    r_CI = str_glue("{estimate}, [{conf.low}, {conf.high}]")
+  )
+tmp_tab
+tmp_tab %>% 
+  flextable::flextable(cwidth = 2) %>% 
+  flextable::save_as_docx(path = "tmp.docx")
+```

### 2022-03-21 mobile.Rmd
bump

# Other internet metrics

In this section we reproduce Model 2 results from @sec-associations but instead of using the ITU internet user proportions, we look at mobile broadband subscription percentages as the predictor.

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(memoise)
library(cachem)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(bayestestR)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(tidyverse)

cd <- cache_disk("memoise_cache", max_size = Inf)
```

```{r}
# Load data sets
dat <- read_rds("data/data-all.rds")
itu <- read_rds("data/itu.rds")

# Countries and regions
countries <- dat %>% 
  distinct(region, country)

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo))
```

## Data figures

```{r}
itu %>% 
  filter(year > 2007) %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mobile)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    date_breaks = "3 years",
    date_labels = "'%y",
    expand = expansion(.01)
  ) +
  geom_line(
    aes(group = country),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line",
    size = .6, color = "dodgerblue4"
  ) +
  facet_wrap(
    ~region,
    labeller = as_labeller(function(x) str_replace(x, "_", "\n")),
    nrow = 1
  ) +
  theme(
    aspect.ratio = 2,
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title.y = element_blank()
  )
```

## Main result: Association

```{r}
get_fixef <- function(outcome, var = "m1_cw"){
  fixef(
    readRDS(str_glue("models/brm-{outcome}-2-mobile.rds")), 
    summary = FALSE
  )[,var , drop = FALSE] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_fixef <- memoise(get_fixef, cache = cd)

fits_fixef <- fits %>% 
  mutate(out = map(outcome, ~get_fixef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)

fits_fixef %>%   
  mutate(across(mean:q97.5, ~./10)) %>% 
  kbl(
    digits = 2, 
    caption = "Model 2 population level associations (% increase per 10% increase in mobile broadband subscriptions)"
  ) %>% 
  kable_custom()
```

This table shows the population-level (average across region, country, age) associations. We then summarise the region- and country-level trends in a table.

```{r}
# Region coefficients
get_region_coef <- function(outcome) {
  coef(
    readRDS(str_glue("models/brm-{outcome}-2-mobile.rds")), 
    summary = FALSE
  )$region[,,"m1_cw"] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_region_coef <- memoise(get_region_coef, cache = cd)

cw_region <- fits %>% 
  mutate(out = map(outcome, ~get_region_coef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)
cw_region <- rename(cw_region, region = variable)

# Country random deviations + region coefficients
get_country_ranef <- function(outcome) {
  ranef(
    readRDS(str_glue("models/brm-{outcome}-2-mobile.rds")), 
    summary = FALSE
  )$country[,,"m1_cw"] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_country_ranef <- memoise(get_country_ranef, cache = cd)

cw_country <- fits %>% 
  mutate(out = map(outcome, ~get_country_ranef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)

# Add region coefs
cw_country <- cw_country %>% 
  rename(country = variable) %>% 
  left_join(countries) %>% 
  left_join(
    select(cw_region, outcome, region, mean_region = mean)
  ) %>% 
  mutate(across(mean:q97.5, ~. + mean_region)) %>% 
  # pd doesn't work without the region coefs
  select(-mean_region, -pd)

cw_region %>% 
  mutate(across(mean:q97.5, ~./10)) %>% 
  arrange(outcome, mean) %>% 
  kbl(
    digits = 2, 
    caption = "Region-specific associations, arranged by outcome and magnitude"
  ) %>% 
  kable_custom() %>% 
  scroll_box("500px")

cw_country %>% 
  mutate(across(mean:q97.5, ~./10)) %>% 
  select(outcome, country, everything()) %>% 
  arrange(outcome, mean) %>% 
  kbl(
    digits = 2, 
    caption = "Country-specific associations, ordered by outcome and magnitude"
  ) %>% 
  kable_custom() %>% 
  scroll_box("500px")
```

### Coefficient plot

Putting these together into a plot

```{r}
tmp <- cw_country %>%
  mutate(Level = "Country") %>% 
  mutate(s = sign(q2.5) == sign(q97.5))

bind_rows(
  "Average" = fits_fixef %>% mutate(region = "**Average**"),
  "Region" = cw_region,
  .id = "Level"
) %>% 
  mutate(region = fct_relevel(region, "**Average**")) %>% 
  mutate(s = sign(q2.5) == sign(q97.5)) %>% 
  # Effect of 10% increase
  # mutate(across(c(mean:q97.5), ~./10)) %>% 
  ggplot(aes(mean, region, shape = s)) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    labels = ~str_replace(., "_", " "),
    expand = expansion(c(0.05, 0.125))
  ) +
  scale_x_continuous(
    "Conditional lagged effect of 10% increase in mobile broadband subscriptions",
    breaks = pretty_breaks(5),
    # Effect of 10% increase
    # X is 0-1, y is 0-100, so x/1000
    labels = function(x) percent(x / 1000, .001) %>% 
      str_remove("\\.000") %>% 
      str_remove("!^0(?=%)"),
    expand = expansion(c(0.05, .05))
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_point(
    data = tmp %>%
      mutate(across(c(mean:q97.5))),
    size = .5, col = "dodgerblue1",
    position = ggbeeswarm::position_quasirandom(width = .25, groupOnX = F)
  ) +
  geom_linerange(
    aes(xmin = q10, xmax = q90), size = 1, col = "dodgerblue4"
  ) +
  geom_pointrangeh(
    aes(xmin = q2.5, xmax = q97.5), col = "dodgerblue4",
    fatten = 4, fill = "white", stroke = .75
  ) +
  # geom_richtext(
  #   aes(x = Inf, label = str_glue("{percent(mean/100, .01)}<br>[{percent(q2.5/100, .01)} {percent(q97.5/100, .01)}]")), 
  #   hjust = 1, vjust = 0.15, size = 2.7, lineheight = .9,
  #   col = "black", fill = NA, label.color = NA
  # ) +
  facet_wrap(
    "outcome", scales = "free_x", ncol = 3,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(), 
    panel.spacing.x = unit(12, "pt"),
    legend.position = "none"
  )
```

## Between-country correlation

```{r}
#| column: page-right
#| fig.width: 8
#| fig.height: 6
#| fig-cap: "Between-country associations"
#| label: fig-cb1

fitted_cb1 <- function(outcome) {
  fit <- readRDS(str_glue("models/brm-{outcome}-2-mobile.rds"))
  newx <- fit$data %>%
    group_by(region, country) %>%
    summarise(m1_cb = unique(m1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(m1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        fit, 
        newdata = newx, 
        re_formula = NA
      )
    )
  )
  newy
}
fitted_cb1 <- memoise(fitted_cb1, cache = cd)

tmp <- fits %>% 
  mutate(out = map(outcome, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

cb1_pars <- fits %>%
  mutate(
    out = map(
      outcome,
      ~ as_draws_df(
        readRDS(str_glue("models/brm-{.x}-2-mobile.rds")),
        variable = "b_m1_cb"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(m1_cb, val)) +
  scale_x_continuous(
    "Between-country centered mobile broadband subscription rate",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100),
    breaks = extended_breaks()
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
  ) +
  geom_line(
    aes(y = Estimate), 
    col = "dodgerblue4", size = 1
  ) +
  geom_smooth(
    method = "lm", se = F, 
    size = .5, col = "black", lty = 2
  ) +
  geom_text(
    data = cb1_pars,
    aes(
      x = -Inf, 
      y = Inf, 
      label = str_glue("{mean} [{q2.5}, {q97.5}]")
    ),
    vjust = 1.3, hjust = -0.025, size = 2.8, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

Here are these correlations calculated from data

```{r}
# From data
tmp <- dat %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  group_by(outcome, region, country) %>% 
  summarise(
    val = mean(val, na.rm = TRUE),
    internet = mean(m1_cb, na.rm = TRUE)
  )
tmp_tab <- tmp %>% 
  summarise(
    tidy(
      lm(
        scale(val) ~ scale(internet), 
        data = cur_data()
      ), 
      conf.int = TRUE
    )
  ) %>% 
  ungroup() %>%
  filter(term != "(Intercept)") %>% 
  mutate(across(where(is.numeric), ~number(., .01))) %>% 
  transmute(
    outcome = outcome,
    r_CI = str_glue("{estimate}, [{conf.low}, {conf.high}]")
  )

tmp %>% 
  group_by(region) %>% 
  # mutate(r = mean(val, na.rm = TRUE), val = val - r) %>%  
  ggplot(aes(internet, val)) +
  scale_x_continuous(
    "Between-country centered mobile subscription rate",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_smooth(method = "lm") +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

## Demographics

Associations

```{r}
h <- c(
  # Intercept_Male = "Intercept + sex1 * -1 = 0",
  # Intercept_Female = "Intercept + sex1 * 1 = 0",
  Slope_Male = "m1_cw + m1_cw:sex1 * -1 = 0",
  Slope_Female = "m1_cw + m1_cw:sex1 * 1 = 0"
)

get_hyp <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
}
get_hyp <- memoise(get_hyp, cache = cd)

tmp <- fits %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp(.x, h = h, model = "2-mobile")
    )
  )

p_tmp <- tmp %>%
  unnest(out) %>% 
  mutate(Group = fct_relevel(Group, "10 to 14")) %>% 
  select(outcome:CI.Upper) %>% 
  separate(Hypothesis, c("Parameter", "Sex")) %>% 
  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
  ggplot(aes(Group, Estimate, col = Sex, shape = s)) +
  scale_color_brewer(
    "", palette = "Set1", direction = -1
  ) +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_y_continuous(
    breaks = extended_breaks(),
    labels = ~percent(./1000), 
    expand = expansion(.4)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_pointrange(
    aes(ymin = CI.Lower, ymax = CI.Upper),
    position = position_dodge(.5),
    size = .5, fatten = 2.5, fill = "white", stroke = .75,
  ) +
  facet_wrap(
    ~outcome, scales = "free_y", ncol = 3,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.text.x = element_text(angle = 90),
    axis.title.x = element_blank()
  )
p_tmp %+% 
  filter(p_tmp$data, Parameter == "Slope") +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  labs(y = "Conditional lagged effect of\n10% increase in internet adoption")
```

And for all regions too

```{r}
get_region_association_demo <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2-mobile.rds"))
  tmp <- x$data %>% 
    group_by(region, age, sex) %>% 
    summarise(m1_cb = mean(m1_cb, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | age) + 
        (m1_cw*sex | region) + (m1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_association_demo <- memoise(
  get_region_association_demo, cache = cd
)

tmp <- fits %>% 
  mutate(out = map(outcome, get_region_association_demo))

x <- sort(unique(dat$age))
tmp %>% 
  unnest(out) %>% 
  mutate(star = sign(.lower) == sign(.upper)) %>% 
  mutate(age = fct_relevel(age, "10 to 14")) %>% 
  ggplot(aes(age, delta, col = sex, group = sex)) +
  geom_hline(yintercept = 0, lty = 2, size = .25) +
  scale_color_brewer(
    "", palette = "Set1", direction = -1, 
    aesthetics = c("color", "fill")
  ) +
  scale_x_discrete(
    "Age",
    breaks = x[seq(1, length(x), 2)],
  ) +
  scale_y_continuous(
    "Conditional lagged effect of\n10% increase in mobile broadband subscriptions",
    labels = ~percent(./1000, .01) %>% 
      str_remove("\\.00(?=%)") %>% 
      str_remove("\\.0(?=%)")
  ) +
  # geom_linerange(
  #   aes(ymin = .lower, ymax = .upper), 
  #   size = .2,
  #   position = position_dodge2(.1)
  # ) +
  geom_ribbon(
    aes(ymin = .lower, ymax = .upper, fill = sex), 
    alpha = .2, col = NA
    ) +
  geom_line(size = .6) +
  # geom_point(
  #   size = .8, fill = "white"
  # ) +
  facet_grid(
    outcome~region, scales = "free_y",
    labeller = as_labeller(~str_replace(., "_", "\n"))
  ) +
  theme(
    text = element_text(size = 10),
    axis.text.x = element_text(angle = 90)
  )
```

Post hoc?

```{r}
yvo_association <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2-internet.rds"))
  y <- coef(x, summary = FALSE)$age[,,"i1_cw"]
  delta <- mean_qi(
    rowMeans(y[,c("15 to 19", "20 to 24")]) - 
      rowMeans(y[,c("25 to 29", "30 to 34")])
    )
  delta
}

yvo_association <- memoise(
  yvo_association, cache = cd
)

tmp <- fits %>% 
  mutate(out = map(outcome, yvo_association))

tmp %>% 
  unnest(out) %>% 
  select(-.point, -.interval) %>% 
  mutate(across(y:ymax, ~percent(./1000)))
```

### 2022-03-21 submit.sh
Adjust slurm options

@@ -5,7 +5,7 @@
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=8
-#SBATCH --mem-per-cpu=2G
+#SBATCH --mem-per-cpu=3G
 #SBATCH --time=4-00:00:00
 #SBATCH --job-name=DWG-Global
 

### 2022-03-21 models.R
Simplify models for mental health outcomes

@@ -135,13 +135,14 @@ bf_4.s <- bf_mobile + bf_val.s + set_rescor(FALSE)
 fits <- fits %>%
   crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
 
+# Simplify models for mental health outcomes
 fits <- fits %>%
   mutate(
     bfrm = case_when(
-      outcome == "Selfharm" & model == 1 ~ list(bf_1.s),
-      outcome == "Selfharm" & model == 2 ~ list(bf_2.s),
-      outcome == "Selfharm" & model == 3 ~ list(bf_3.s),
-      outcome == "Selfharm" & model == 4 ~ list(bf_4.s),
+      !str_detect(outcome, "_") & model == 1 ~ list(bf_1.s),
+      !str_detect(outcome, "_") & model == 2 ~ list(bf_2.s),
+      !str_detect(outcome, "_") & model == 3 ~ list(bf_3.s),
+      !str_detect(outcome, "_") & model == 4 ~ list(bf_4.s),
       TRUE ~ bfrm
     )
   ) %>%

### 2022-03-21 models.R
fix

@@ -139,10 +139,10 @@ fits <- fits %>%
 fits <- fits %>%
   mutate(
     bfrm = case_when(
-      !str_detect(outcome, "_") & model == 1 ~ list(bf_1.s),
-      !str_detect(outcome, "_") & model == 2 ~ list(bf_2.s),
-      !str_detect(outcome, "_") & model == 3 ~ list(bf_3.s),
-      !str_detect(outcome, "_") & model == 4 ~ list(bf_4.s),
+      outcome == "Selfharm" & model == 1 ~ list(bf_1.s),
+      outcome == "Selfharm" & model == 2 ~ list(bf_2.s),
+      outcome == "Selfharm" & model == 3 ~ list(bf_3.s),
+      outcome == "Selfharm" & model == 4 ~ list(bf_4.s),
       TRUE ~ bfrm
     )
   ) %>%

### 2022-03-22 submit.sh
Adjust hmc

@@ -4,9 +4,9 @@
 # Use sbatch --array=1-24 submit.sh to submit
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
-#SBATCH --cpus-per-task=8
+#SBATCH --cpus-per-task=12
 #SBATCH --mem-per-cpu=3G
-#SBATCH --time=4-00:00:00
+#SBATCH --time=7-00:00:00
 #SBATCH --job-name=DWG-Global
 
 module purge

### 2022-03-24 00-clean.Rmd
Use synthpop for mock data

--- 2022-03-17 clean.Rmd
@@
 -   Rescale outcomes to proportions (0 - 1)
--   Subset the data to 15 to 24 year olds
--   Create age-categories in line with GBD data
+-   Create age categories in line with GBD data
 -   Drop one 13 year old as this data should only have people 15 and older
+-   Exclude people older than 89
 
@@
 
+# Rename and recode variables
 gwp <- gwp %>%
@@
 
-We then load the synthetic GWP dataset if the real data was not found.
-This is just a list of the countries, years and demographics in the actual data, with gaussian noise for the outcomes' mean and SE values.
+### Synthetic GWP data
+
+If the real GWP data was not available above, here we load the synthetic dataset (having first created it).
+
+```{r create-mock-gwp-data}
+#| eval: false
+gwp_mock_path <- "data-raw/gwp-MOCK.rds"
+library(synthpop)
+gwp_syn <- gwp %>% 
+  drop_na()
+gwp_syn <- syn(
+  gwp_syn %>% filter(outcome == "Life_satisfaction"), 
+  method = c("", "", "", "", "", "normrank", "normrank"),
+  # visit.sequence = c(1:6, 8, 7),
+  maxfaclevels = 168
+  )
+saveRDS(gwp_syn, gwp_mock_path)
+```
 
 ```{r}
-# Create if doesn't exist
 gwp_mock_path <- "data-raw/gwp-MOCK.rds"
-if (!file.exists(gwp_mock_path)) {
-  set.seed(101010)
-  # TODO
-}
 # Load if actual data doesn't exist

### 2022-03-24 models.R
Fix data subsetting & drop country:age from MH RE

@@ -21,10 +21,10 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = min(ncores %/% nchains, 3),
-  iter = 2000,
-  warmup = 1000,
+  iter = 2300,
+  warmup = 1150,
   refresh = 100,
-  adapt_delta = .925,
+  adapt_delta = .93,
   max_treedepth = 10
 )
 
@@ -55,7 +55,7 @@ bf_itu <- bf(
 )
 
 bf_val <- bf(
-  val | se(se, sigma = TRUE) ~
+  val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
     year * sex +
     (year * sex | c | country) +
     (year * sex | r | region) +
@@ -69,7 +69,7 @@ bf_1 <- bf_itu + bf_val + set_rescor(FALSE)
 
 # Simplified model for self-harm
 bf_val.s <- bf(
-  val | se(se, sigma = TRUE) ~
+  val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
     year * sex +
     (year * sex | c | country) +
     (year * sex | r | region) +
@@ -136,13 +136,14 @@ fits <- fits %>%
   crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
 
 # Simplify models for mental health outcomes
+MH <- c("Anxiety", "Depression", "Selfharm")
 fits <- fits %>%
   mutate(
     bfrm = case_when(
-      outcome == "Selfharm" & model == 1 ~ list(bf_1.s),
-      outcome == "Selfharm" & model == 2 ~ list(bf_2.s),
-      outcome == "Selfharm" & model == 3 ~ list(bf_3.s),
-      outcome == "Selfharm" & model == 4 ~ list(bf_4.s),
+      outcome %in% MH & model == 1 ~ list(bf_1.s),
+      outcome %in% MH & model == 2 ~ list(bf_2.s),
+      outcome %in% MH & model == 3 ~ list(bf_3.s),
+      outcome %in% MH & model == 4 ~ list(bf_4.s),
       TRUE ~ bfrm
     )
   ) %>%

### 2022-03-24 00-clean.Rmd
Drop missing sex rows
Fix missing SEs

@@
 gwp <- drop_na(gwp, age)
+
+# Some sex values are missing, drop those
+gwp <- drop_na(gwp, sex)
 ```
@@
   ungroup()
+
+# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
+gwp <- gwp %>% 
+  mutate(
+    se = if_else(is.na(se) | se == 0, 0.5, se)
+  )
 ```

### 2022-03-24 00-clean.Rmd
Fix synthetic data gen

@@
 
-```{r create-mock-gwp-data}
-#| eval: false
+```{r mock-gwp-data}
 gwp_mock_path <- "data-raw/gwp-MOCK.rds"
+if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
   library(synthpop)
@@
   gwp_syn <- syn(
-  gwp_syn %>% filter(outcome == "Life_satisfaction"), 
-  method = c("", "", "", "", "", "normrank", "normrank"),
-  # visit.sequence = c(1:6, 8, 7),
+    gwp_syn, 
+    method = c("", "", "", "", "", "", "normrank", "normrank"),
     maxfaclevels = 168
@@
   saveRDS(gwp_syn, gwp_mock_path)
-```
+}
 
-```{r}
-gwp_mock_path <- "data-raw/gwp-MOCK.rds"
 # Load if actual data doesn't exist

### 2022-03-24 00-clean.Rmd
Fix a bug that dropped 209 outcome rows

@@
 
-# Identify values to use in mv models
+# Identify values to use in MV models
 # Indicate unique ITU values for MV model
@@
   ungroup()
+
+# This prevents a glitch where rows where ITU==TRUE but internet is missing would not be included in model of val
+dat <- dat %>% 
+  mutate(
+    itu = if_else(itu & is.na(internet), FALSE, itu),
+    itum = if_else(itum & is.na(mobile), FALSE, itum)
+    )
 

### 2022-03-24 models.R
Adjust hmc

@@ -9,9 +9,9 @@ cat("\nFitting row\n", cmdargs)
 # ---- setup ---------------------------------------------------------------
 
 options(tidyverse.quiet = TRUE)
+library(tidyverse)
 library(cmdstanr)
 library(brms)
-library(tidyverse)
 
 # MCMC settings
 (ncores <- min(parallel::detectCores(logical = FALSE), 12))
@@ -21,10 +21,10 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = min(ncores %/% nchains, 3),
-  iter = 2300,
-  warmup = 1150,
+  iter = 2200,
+  warmup = 1100,
   refresh = 100,
-  adapt_delta = .93,
+  adapt_delta = .94,
   max_treedepth = 10
 )
 

### 2022-03-24 00-describe.Rmd
Refactor

# Describe

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(ggh4x)
library(mgcv)
library(tidyverse)

# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")
d <- read_rds("data/data-all.rds")

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
```

Number of countries/years/people per outcome

```{r}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl(caption = "Dataset summary") %>% 
  kable_custom()
gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n)))
```

Number of data points per outcome

```{r}
unique(gwp$age)
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome)
itu %>% 
  drop_na(internet)

```

## Data figure

```{r trends-regions}
#| echo: false
#| fig-width: 12
#| fig-height: 8
#| fig-cap: "Trends in all variables across regions"
#| label: fig-trends-regions

# Stack data sets
# Assume all outcomes are proportions (0-1)
# Draw small multiples figure, outcomes x regions
d <- bind_rows(
  read_rds("data/gwp.rds"),
  read_rds("data/gbd.rds")
)

itu <- read_rds("data/itu.rds") %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

tmp_country <- bind_rows(itu, d) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo)))

tmp_region <- tmp_country %>%
  group_by(region, outcome) %>%
  group_modify(~broom::augment(gam(mean ~ s(year, bs = "cs", k = 5), data = .))) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo)))

tmp_world <- tmp_country %>%
  group_by(outcome) %>%
  group_modify(~broom::augment(gam(mean ~ s(year, bs = "cs", k = 5), data = .))) %>%
  ungroup() %>%
  mutate(region = "World") %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo)))

tmp_country %>%
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = ~percent(., .1),
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, outcome)),
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  geom_line(
    data = tmp_region %>% mutate(year = make_date(year)),
    aes(y = .fitted, group = interaction(region, outcome)),
    alpha = 1, size = .6, color = "dodgerblue4"
  ) +
  geom_line(
    data = tmp_world %>% mutate(year = make_date(year)),
    aes(y = .fitted, group = interaction(region, outcome)),
    alpha = 1, size = .8, color = "dodgerblue4"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt"),
    axis.title.y = element_blank()
  )
agg_png(
  "figures/Fig-trends-data.png",
  width = W, height = W*0.8, units = "in", res = 400
)
last_plot()
dev.off()
```

### 2022-03-24 01-models.Rmd
Refactor

# Models

```{r setup}
#| cache: false
# Packages
library(tidyverse)
library(knitr)
library(posterior)
library(ragg)
library(here)
library(scales)
library(bayestestR)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(brms)
library(multidplyr)

cluster <- new_cluster(3)

cd <- cache_disk("memoise_cache", max_size = Inf)
```

Here we discuss the models. The models are fitted in `models.R`. We submit that to our local SLURM cluster with `submit.sh`.

## Model 1

Model 1 is a three-level bayesian multivariate meta-regression model that simultaneously estimates trends over time for the outcome (e.g. Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries. It also includes sex and the sex by time interaction predictors for the outcomes. The parameters are also treated as random across the age groups, and the age by country, and age by region interactions. We fit the model separately for each outcome. In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.

The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate. For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age). The one downside of this modelling strategy is that it does not converge for self-harm. Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero. In addition, for self-harm, we remove the $age:country$ random effects.

We write the model as

$$
\begin{align}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2}v_i) \\

\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{region}[i]} + \gamma^{y}_{0\text{country}[i]} + \delta^{y}_{0\text{age}[i]} + \zeta^{y}_{0\text{age:region}[i]} + \eta^{y}_{0\text{age:country}[i]} \\ &(\alpha^{y}_{1} + \beta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]} + \delta^{y}_{1\text{age}[i]} + \zeta^{y}_{1\text{age:region}[i]} + \eta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha^{y}_{2} + \beta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]} + \delta^{y}_{2\text{age}[i]} + \zeta^{y}_{2\text{age:region}[i]} + \eta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha^{y}_{3} + \beta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]} + \delta^{y}_{3\text{age}[i]} + \zeta^{y}_{3\text{age:region}[i]} + \eta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\ \\

x_i &\sim \text{Beta}(\mu^x_i, \phi) \\ 
\text{logit}(\mu^x_i) &= \alpha^{x}_{0} + \beta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
\end{align}
$$

$$
\begin{align}

\left[\begin{array}{c}
\beta^y_{0\text{region}} \\ \beta^y_{1\text{region}}\\ 
\beta^y_{2\text{region}} \\ \beta^y_{3\text{region}} \\
\beta^x_{0\text{region}} \\ \beta^x_{1\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{region}),

\left[\begin{array}{c}
\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\
\gamma^x_{2\text{country}} \\ \gamma^x_{3\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{country}),

\left[\begin{array}{c}
\delta^y_{0\text{age}} \\ \delta^y_{1\text{age}} \\ 
\delta^y_{2\text{age}} \\ \delta^y_{3\text{age}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age}), \\

\left[\begin{array}{c}
\zeta^y_{0\text{age:region}} \\ \zeta^y_{1\text{age:region}} \\ 
\zeta^y_{2\text{age:region}} \\ \zeta^y_{3\text{age:region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{age:region}),

\left[\begin{array}{c}
\eta^y_{0\text{age:country}} \\ \eta^y_{1\text{age:country}} \\ 
\eta^y_{2\text{age:country}} \\ \eta^y_{3\text{age:country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age:country})

\end{align}
$$ {#eq-model1}

Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances. We also fit this same model but using the mobile broadband subscriptions as $x$ ("Model 4").

## Model 2

Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions

$$
\begin{align*}
y_i &\sim \text{Normal}(\mu_i, \sigma^{2}v_i) \\

\mu_i &= \alpha_{0} + \beta_{0\text{region}[i]} + \gamma_{0\text{country}[i]} + \delta_{0\text{age}[i]} + \zeta_{0\text{age:region}[i]} + \eta_{0\text{age:country}[i]} \\ &(\alpha_{1} + \beta_{1\text{region}[i]} + \gamma_{1\text{country}[i]} + \delta_{1\text{age}[i]} + \zeta_{1\text{age:region}[i]} + \eta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{region}[i]} + \gamma_{2\text{country}[i]} + \delta_{2\text{age}[i]} + \zeta_{2\text{age:region}[i]} + \eta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{region}[i]} + \gamma_{3\text{country}[i]} + \delta_{3\text{age}[i]} + \zeta_{3\text{age:region}[i]} + \eta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&(\alpha_{4} + \beta_{4\text{region}[i]} + \gamma_{4\text{country}[i]} + \delta_{4\text{age}[i]} + \zeta_{4\text{age:region}[i]} + \eta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
&(\alpha_{5} + \beta_{5\text{region}[i]} + \gamma_{5\text{country}[i]} + \delta_{5\text{age}[i]} + \zeta_{5\text{age:region}[i]} + \eta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\ \\

\left[\begin{array}{c}
\beta_{0\text{region}} \\ \beta_{1\text{region}} \\ 
\beta_{2\text{region}} \\ \beta_{3\text{region}} \\
\beta_{4\text{region}} \\ \beta_{5\text{region}} 
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{region}),

\left[\begin{array}{c}
\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\
\gamma_{2\text{country}} \\ \gamma_{3\text{country}} 
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{country}),

\left[\begin{array}{c}
\delta_{0\text{age}} \\ \delta_{1\text{age}} \\ 
\delta_{2\text{age}} \\ \delta_{3\text{age}} \\
\delta_{4\text{age}} \\ \delta_{5\text{age}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age}), \\

\left[\begin{array}{c}
\zeta_{0\text{age:region}} \\ \zeta_{1\text{age:region}} \\ 
\zeta_{2\text{age:region}} \\ \zeta_{3\text{age:region}} \\
\zeta_{4\text{age:region}} \\ \zeta_{5\text{age:region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{age:region}),

\left[\begin{array}{c}
\eta_{0\text{age:country}} \\ \eta_{1\text{age:country}} \\ 
\eta_{2\text{age:country}} \\ \eta_{3\text{age:country}} \\
\eta_{4\text{age:country}} \\ \eta_{5\text{age:country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{age:country})
\end{align*}
$$ {#eq-model1}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion. We then also fit this model but using the mobile broadband subscription numbers instead of the internet user proportions ("Model 3").

## Model checking and parameters

Next, we display the population-level parameters of each model, along with their numberical HMC diagnostics (ESS and Rhat values).

```{r}
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = fct_inorder(outcome))
```

### Parameters and diagnostics

Rhats should approach 1, and the latter should approach the number of hmc iterations (about 4000). We first calculate these posterior summaries for each population level parameter for each outcome and model.

```{r model-diagnostics}
parameter_summary <- function(outcome, model) {
  path <- str_glue("models/brm-{outcome}-{model}.rds")
  as_draws_df(
    readRDS(path), 
    variable = c("^b_", "^sd_", "^cor_"), 
    regex = TRUE
  ) %>%
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .5, .975)),
      pd = ~pd(as.numeric(.)), 
      samples = length, 
      default_convergence_measures()
    )
}
parameter_summary <- memoise(parameter_summary, cache = cd)

fits_parameters <- tibble(
  path = list.files("models/", full.names = TRUE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
  unnest(parameters)
```

Then display them for each model

```{r model-1-diagnostics}
#| column: body-outset-right
#| label: tab-model1-diagnostic
#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."

parameter_table <- function(model) {
  x <- fits_parameters %>% 
    filter(model == {{model}}) %>% 
    select(-model)
  x %>% 
    kbl(
      caption = str_glue("Model {model}"),
      digits = c(0,0,2,2,2,2,2,2,0,2,0,0)
    ) %>%
    column_spec(
      10,
      color = "white",
      background = spec_color(
        log(x$rhat),
        direction = 1,
        option = "C",
        end = .6
      )
    ) %>%
    row_spec(0, bold = TRUE) %>% 
    kable_custom() %>% 
    scroll_box(height = "800px", width = "900px")
}
```

::: {.panel-tabset}

#### Model 1

```{r}
#| echo: false
parameter_table(1)
```

#### Model 2

```{r}
#| echo: false
parameter_table(2)
```

#### Model 3

```{r}
#| echo: false
parameter_table(3)
```

#### Model 4

```{r}
#| echo: false
parameter_table(4)
```

:::

### Rhats

Take a look at distributions with worst rhats

```{r}
#| eval: false
x <- readRDS("models/brm-Depression-3.rds")
rhat(x, pars = variables(x)[1:10])
bads <- fits_parameters %>% 
  group_by(outcome, model) %>% 
  arrange(outcome, model, desc(rhat)) %>% 
  slice(1:4)
bads

foo <- function(outcome, model) {
  bads <- filter(bads, outcome == {{outcome}}, model == {{model}})
  x <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  agg_png(
    str_glue("diagnostics/bads-{outcome}-{model}.png"),
    width = W, height = W, units = "in", res = 200
  )
  pairs(x$fit, pars = pull(bads, variable))
  title(sub = str_glue("bads-{outcome}-{model}"))
  dev.off()
}
foo <- memoise(foo, cache = cd)
fits %>% 
  crossing(model = 1:4) %>% 
  mutate(walk2(outcome, model, foo))
```

### Scatterplots

Browse these figures at `diagnostics/`

```{r}
#| eval: false
pairsplot <- function(path) {
  x <- readRDS(str_glue(here(path)))
  agg_png(
    str_glue("diagnostics/{path}.png"),
    width = W*1.5, height = W*1.5, units = "in", res = 200
  )
  pairs(x$fit, pars = variables(x)[1:22])
  title(sub = path)
  dev.off()
}
pairsplot <- memoise(pairsplot, cache = cd)
list.files("models", full.names = TRUE) %>% 
  walk(pairsplot)
```

### Posterior predictive checks

```{r ppcheck-density}
#| eval: false
#| column: page-right
#| fig-height: 6
#| fig-width: 9
#| fig-cap: "Graphical posterior predictive check by region (Model 1). Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g. Anglo Depression)."
#| label: fig-ppcheck-1

pp_check_fun <- function(outcome, model) {
  path <- str_glue("models/brm-{outcome}-{model}.rds")
  fit <- readRDS(path)
  pp_check(
    fit,
    ndraws = 10,
    type = "dens_overlay_grouped",
    group = "region",
    resp = "val",
    newdata = fit$data
  )[[1]]
}
pp_check_fun <- memoise(pp_check_fun, cache = cd)

cluster_copy(cluster, "pp_check_fun")
cluster_library(cluster, c("tidyverse", "bayesplot", "brms"))
pp_checks <- tibble(
  path = list.files("models/", full.names = TRUE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(pp_check = map2(outcome, model, ~pp_check_fun(.x, .y))) %>% 
  unnest(pp_check)

pp_checks %>%
  filter(model == 1) %>% 
  ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
  scale_color_brewer(palette = "Set1") +
  scale_alpha_manual(values = c(.2, 1)) +
  stat_density(
    geom = "line",
    size = .75,
    position = position_identity()
  ) +
  labs(x = "Value", y = "Density") +
  facet_grid2(
    outcome ~ group,
    scales = "free", independent = "x",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt"),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

### 2022-03-24 02-correlations.Rmd
Refactor

# Between-country correlations

```{r}
# Between-country correlations

library(scales)
library(memoise)
library(tidyverse)
library(kableExtra)
library(ggtext)
library(cachem)
library(bayestestR)
library(multidplyr)
library(broom)
library(brms)
library(posterior)
library(ggstance)
library(ellipse)
library(ggh4x)
library(patchwork)

cd <- cache_disk("memoise_cache", max_size = Inf)
cluster <- new_cluster(3)

dat <- readRDS("data/data-all.rds")
itu <- readRDS("data/itu.rds")

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))
```

## OLS

```{r}
# Parameters for delta scatterplots
delta_ols_i <- itu %>%
  mutate(year = year - 2010) %>%
  group_by(region, country) %>%
  group_modify(~tidy(lm(internet ~ year, data = .))) %>%
  filter(term == "year") %>%
  select(country, estimate_internet = estimate)
delta_ols_m <- itu %>%
  drop_na(mobile) %>%
  mutate(year = year - 2010) %>%
  group_by(region, country) %>%
  group_modify(~tidy(lm(mobile ~ year, data = .))) %>%
  filter(term == "year") %>%
  select(country, estimate_mobile = estimate)
delta_ols_v <- dat %>%
  drop_na(val) %>%
  mutate(year = year - 2010) %>%
  group_by(region, outcome, country, year) %>%
  summarise(val = mean(val, na.rm = TRUE)) %>%
  group_modify(~tidy(lm(val ~ year, data = .))) %>%
  filter(term == "year") %>%
  select(country, estimate_val = estimate)
delta_ols <- left_join(
  delta_ols_v,
  delta_ols_i
) %>%
  left_join(delta_ols_m) %>%
  ungroup()

p_delta_ols_internet <- delta_ols %>%
  ggplot(aes(estimate_internet, estimate_val, col = region)) +
  scale_color_discreterainbow(
    name = "Region",
    labels = ~str_replace(., "_", " ")
  ) +
  scale_y_continuous(
    labels = ~percent(./100, .1)
  ) +
  scale_x_continuous(
    labels = ~percent(., .1)
  ) +
  geom_point(
    shape = 1, size = 1.0, alpha = .75
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y",
    nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1
  ) +
  guides(
    color = guide_legend(
      override.aes = list(alpha = 1, shape = 16, size = 1.5)
    )
  ) +
  labs(
    y = expression(Delta~"Outcome"),
    x = expression(Delta~"Internet users per capita")
  )

p_delta_ols_mobile <- p_delta_ols_internet +
  aes(x = estimate_mobile) +
  labs(
    x = expression(Delta~"Mobile users per capita")
  )

# Data for average levels scatterplots
dat_avg <- dat %>%
  group_by(outcome, region, country) %>%
  summarise(
    internet = mean(internet, na.rm = TRUE),
    mobile = mean(mobile, na.rm = TRUE),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

p_means_ols_internet <- dat_avg %>%
  ggplot(aes(y = val, col = region)) +
  scale_color_discreterainbow(
    name = "Region",
    labels = ~str_replace(., "_", " ")
  ) +
  scale_y_continuous(
    "Mean outcome",
    labels = ~percent(./100, .1),
    breaks = extended_breaks()
  ) +
  geom_point(
    shape = 1, size = 1.0, alpha = .75
  ) +
  facet_wrap(
    ~outcome,
    scales = "free", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " ") %>% str_to_title(.))
  ) +
  guides(
    color = guide_legend(
      override.aes = list(alpha = 1, shape = 16, size = 1.5)
    )
  ) +
  theme(
    aspect.ratio = 1
  )

p_means_ols_internet <- p_means_ols_internet +
  aes(x = internet) +
  scale_x_continuous(
    "Mean internet users per capita",
    breaks = seq(0, 1, by = .25),
    labels = ~percent(.),
    limits = 0:1
  )
p_means_ols_mobile <- p_means_ols_internet +
  aes(x = mobile) +
  scale_x_continuous(
    "Mean mobile internet subscriptions per capita",
    breaks = seq(0, 1.5, by = .5),
    labels = ~percent(.),
    limits = c(0, 1.5)
  )

(p_means_ols_internet | 
    p_delta_ols_internet | 
    p_means_ols_mobile | 
    p_delta_ols_mobile
) +
  plot_layout(nrow = 4, guides = "collect")

agg_png(
  "figures/Fig-country-correlations-OLS.png",
  width = W, height = W*0.8, units = "in", res = 400
)
last_plot()
dev.off()

# Coefficient plot
means_ols_cors <- dat_avg %>%
  group_by(outcome) %>%
  group_modify(
    ~tidy(lm(scale(val) ~ scale(internet), data = .), conf.int = TRUE)
  ) %>%
  filter(term != "(Intercept)")
delta_ols_cors <- delta_ols %>%
  group_by(outcome) %>%
  group_modify(
    ~tidy(lm(scale(estimate_val) ~ scale(estimate_internet), data = .), conf.int = TRUE)
  ) %>%
  filter(term != "(Intercept)")
cor_pars_ols <- bind_rows(
  "Means" = means_ols_cors,
  "Deltas" = delta_ols_cors,
  .id = "type"
)
cor_pars_ols %>%
  mutate(type = fct_rev(type)) %>%
  mutate(outcome = fct_rev(factor(outcome, levels = oo))) %>%
  ggplot(aes(estimate, outcome)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrangeh(aes(xmin = conf.low, xmax = conf.high)) +
  facet_wrap("type") +
  labs(x = "Correlation") +
  theme(axis.title.y = element_blank())
```

## Model based

### Correlation parameters

```{r}
get_cor_pars <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  as_draws_df(
    x,
    variable = c(
      str_glue("b_{predictor}_Intercept"),
      "b_val_Intercept",
      str_glue("b_{predictor}_year"),
      "b_val_year",
      str_glue("sd_country__{predictor}_Intercept"),
      "sd_country__val_Intercept",
      str_glue("sd_country__{predictor}_year"),
      "sd_country__val_year",
      str_glue("cor_country__{predictor}_year__val_year"),
      str_glue("cor_country__{predictor}_Intercept__val_Intercept")
    )
  )
}
get_cor_pars <- memoise(get_cor_pars, cache = cd)

cor_pars_brm_internet <- fits %>%
  mutate(out = map(outcome, ~get_cor_pars(.x, "internet", "1")))
cor_pars_brm_mobile <- fits %>%
  mutate(out = map(outcome, ~get_cor_pars(.x, "mobile", "4")))

cor_pars_brm <- bind_rows(
  "internet" = cor_pars_brm_internet,
  "mobile" = cor_pars_brm_mobile,
  .id = "type"
) %>% 
  mutate(
    out = map(
      out,
      ~summarize_draws(., mean, ~quantile2(., probs = c(.025, .975))))
  ) %>%
  unnest(out) %>% 
  filter(str_detect(variable, "cor_country")) %>% 
  mutate(variable = if_else(str_detect(variable, "Intercept"), "Intercepts", "Slopes")) %>% 
  mutate(outcome = factor(outcome, levels = oo))
cor_pars_brm %>%   
  ggplot(aes(mean, outcome, col = type)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrangeh(
    aes(xmin = q2.5, xmax = q97.5),
    position = position_dodge2v(.25)
  ) +
  facet_wrap("variable") +
  labs(x = "Correlation") +
  theme(axis.title.y = element_blank())
cor_pars_brm %>% 
  mutate(across(where(is.numeric), ~number(., .01))) %>% 
  transmute(
    type, outcome, variable,
    r = str_glue("{mean} [{q2.5}, {q97.5}]")
  ) %>% 
  pivot_wider(names_from = variable, values_from = r) %>% 
  arrange(outcome, type) %>% 
  kbl() %>% 
  kable_custom()
```

### Internet

#### Draw scatterplots

```{r}
get_country_coefs <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  x_country <- coef(x)$country[
    ,,c(
      str_glue("{predictor}_Intercept"), 
      "val_Intercept", 
      str_glue("{predictor}_year"), 
      "val_year"
      )
    ] %>%
    as.data.frame() %>% 
    rownames_to_column("country") %>% 
    tibble() %>% 
    select(country, contains("Estimate"))
  # Below adds region ranefs to country coefs to produce predictions
  x_region <- ranef(x)$region[
    ,,c(
      str_glue("{predictor}_Intercept"), 
      "val_Intercept", 
      str_glue("{predictor}_year"), 
      "val_year"
      )
    ] %>%
    as.data.frame() %>%
    rownames_to_column("region") %>%
    tibble() %>%
    select(region, contains("Estimate"))
  x_country %>%
    left_join(distinct(dat, region, country)) %>%
    left_join(x_region, by = c("region")) %>%
    # Rename X for function
    rename_with(~str_replace(., "internet|mobile", "x")) %>% 
    transmute(
      country, region,
      Estimate.x_Intercept = Estimate.x_Intercept.x + Estimate.x_Intercept.y,
      Estimate.x_year = Estimate.x_year.x + Estimate.x_year.y,
      Estimate.val_Intercept = Estimate.val_Intercept.x + Estimate.val_Intercept.y,
      Estimate.val_year = Estimate.val_year.x + Estimate.val_year.y,
    )
}
get_country_coefs <- memoise(get_country_coefs, cache = cd)
brm_country_coefs_internet <- fits %>%
  mutate(out = map(outcome, ~get_country_coefs(.x, "internet", "1"))) %>% 
  unnest(out)

p_means_brm_internet <- brm_country_coefs_internet %>%
  ggplot(aes(Estimate.x_Intercept, Estimate.val_Intercept, col = region)) +
  scale_color_discreterainbow(
    name = "Region",
    labels = ~str_replace(., "_", " ")
  ) +
  geom_point(
    shape = 1, size = 1.0, alpha = .75
  ) +
  scale_y_continuous(
    labels = ~percent(./100, .1)
  ) +
  facet_wrap(
    ~outcome,
    scales = "free", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1
  ) +
  guides(
    color = guide_legend(
      override.aes = list(alpha = 1, shape = 16, size = 1.5)
    )
  ) +
  labs(x = "Internet users per capita (logits)", y = "Outcome")

p_delta_brm_internet <- p_means_brm_internet +
  aes(Estimate.x_year, Estimate.val_year) +
  labs(
    y = "Change in outcome",
    x = "Change in internet users per capita (logits)"
  )
```

### Mobile

#### Draw scatterplots

```{r}
brm_country_coefs_mobile <- fits %>%
  mutate(out = map(outcome, ~get_country_coefs(.x, "mobile", "4"))) %>% 
  unnest(out)

p_means_brm_mobile <- brm_country_coefs_mobile %>%
  ggplot(aes(Estimate.x_Intercept, Estimate.val_Intercept, col = region)) +
  scale_color_discreterainbow(
    name = "Region",
    labels = ~str_replace(., "_", " ")
  ) +
  scale_x_continuous(
    labels = ~percent(., 1),
    breaks = c(-.25, 0, .25, .5, .75, 1)
  ) +
  geom_point(
    shape = 1, size = 1.0, alpha = .75
  ) +
  scale_y_continuous(
    labels = ~percent(./100, .1)
  ) +
  facet_wrap(
    ~outcome,
    scales = "free", nrow = 1, drop = FALSE,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1
  ) +
  guides(
    color = guide_legend(
      override.aes = list(alpha = 1, shape = 16, size = 1.5)
    )
  ) +
  labs(x = "Mobile broadband subscriptions per capita", y = "Outcome")

p_delta_brm_mobile <- p_means_brm_mobile +
  scale_x_continuous(
    labels = ~percent(., 1),
    breaks = extended_breaks(5)
  ) +
  aes(Estimate.x_year, Estimate.val_year) +
  labs(
    y = "Change in outcome",
    x = "Change in mobile broadband subscriptions per capita"
  )
```

```{r}
(
  p_means_ols_internet + ggtitle("A") +
    p_delta_brm_internet + ggtitle("B") +
  p_means_ols_mobile + ggtitle("C") +
    p_delta_brm_mobile + coord_cartesian(xlim = c(0, 2)) + ggtitle("D")
  ) +
  plot_layout(nrow = 4, guides = "collect") & 
  theme(legend.position = "bottom")

agg_png(
  "figures/Fig-country-correlations.png",
  width = W, height = W*0.9, units = "in", res = 400
)
last_plot()
dev.off()
```

### 2022-03-24 02-results.Rmd
Refactor

# Main results

```{r setup}
#| cache: false
# Packages
library(tidyverse)
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(memoise)
library(cachem)
library(posterior)
library(ggh4x)
library(parameters)
library(emmeans)
library(patchwork)
library(multidplyr)

cluster <- new_cluster(3)

cd <- cache_disk("memoise_cache", max_size = Inf)

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)

fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

dat <- readRDS("data/data-all.rds")
```

We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents? To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations. In this section, we present results based on the moderated effects.

## Time courses

This figure shows the time courses of each of the six outcome variables. Panels by outcome (rows) and region (columns; including World). Each panel shows the time course by all ages and sex, and on average across ages. So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.

Calculate contrast by sex at the world level.

```{r}
#' Get contrast at average level (no random effects)
#'
#' @param outcome Life_satisfaction etc.
#' @param h Strings representing hypotheses (brm::hypothesis())
#' @param model 1, 2, 3, or 4
get_hyp_avg <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h)$hypothesis
}
get_hyp_avg <- memoise(get_hyp_avg, cache = cd)

h_timecourses <- c(
  Slope_Male = "val_year + val_year:sex1 * -1 = 0",
  Slope_Female = "val_year + val_year:sex1 * 1 = 0"
)

cluster_library(cluster, c("brms", "purrr", "stringr"))
cluster_copy(cluster, c("get_hyp_avg", "h_timecourses"))

timecourses_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()

timecourses_world_average %>% 
  unnest(out)
```

And then for each sex*age at the world level.

```{r}
#' Get contrast for each age
#'
#' @param outcome Life_satisfaction etc
#' @param h brms hypothesis
#' @param model 1,2,3, or 4
get_hyp_age <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
}
get_hyp_age <- memoise(get_hyp_age, cache = cd)
cluster_copy(cluster, "get_hyp_age")

timecourses_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()
```

Combine these to one and plot

```{r}
bind_rows(
  timecourses_world_age %>% 
    unnest(out),
  timecourses_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  mutate(Group = fct_relevel(Group, "Average", "10 to 14")) %>% 
  select(outcome:CI.Upper) %>% 
  separate(Hypothesis, c("Parameter", "Sex")) %>% 
  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
  ggplot(aes(Group, Estimate, ymin = CI.Lower, ymax = CI.Upper, fill = Sex, col = Sex, group = Sex)) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_y_continuous(
    breaks = extended_breaks(),
    # Effect of 10%
    labels = ~percent(./1000), 
    expand = expansion(.4)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(Group != "Average"),
    aes(), 
    alpha = .2, col = NA
  ) +
  geom_line(
    data = . %>% filter(Group != "Average"),
    aes(group = Sex),
    size = .6
  ) +
  geom_pointrange(
    data = . %>% filter(Group == "Average"),
    position = position_dodge(.75),
    size = .4, fatten = 2.5
  ) +
  facet_wrap(
    "outcome", scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "none",
    axis.title.x = element_blank()
  )
```

And for all regions too.

First we calculate the contrast by sex for each region.

```{r}
get_region_timecourse_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note 1 for 10 year change
    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_timecourse_avg <- memoise(
  get_region_timecourse_avg, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_avg")
cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
timecourses_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_avg)) %>% 
  collect()
timecourses_region_average %>% 
  unnest(out)
```

Then we calculate the contrasts for each sex*age for each region.

```{r}
get_region_timecourse_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note 1 for decade change
    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | age) + 
        (year*sex | region) + (year*sex | age:region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_timecourse_age <- memoise(
  get_region_timecourse_age, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_age")
timecourses_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_age)) %>% 
  collect()
```

Combine these with world level estimates and plot

```{r}
timecourses_world <- bind_rows(
  timecourses_world_age %>% 
    unnest(out),
  timecourses_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  separate(Hypothesis, c("Parameter", "sex")) %>% 
  select(
    outcome,
    age = Group,
    sex,
    delta = Estimate,
    .lower = CI.Lower,
    .upper = CI.Upper,
  ) %>% 
  mutate(region = "World")

x <- sort(unique(timecourses_world$age))
x2 <- as.character(x)
x2[str_detect(x2, "5 ")] <- ""

bind_rows(
  timecourses_region_age %>% 
    unnest(out),
  timecourses_region_average %>% 
    unnest(out) %>% 
    mutate(age = "Average")
) %>% 
  ungroup() %>% 
  bind_rows(timecourses_world) %>% 
  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
  arrange(sex) %>% 
  select(outcome:.upper) %>% 
  mutate(s = sign(.lower) == sign(.upper)) %>% 
  ggplot(
    aes(
      age, delta, 
      ymin = .lower, ymax = .upper, 
      fill = sex, col = sex, group = sex
    )
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_x_discrete(
    breaks = x,
    labels = x2,
    expand = expansion(c(0.02, 0.05))
  ) +
  scale_y_continuous(
    "Estimated linear change per decade",
    breaks = extended_breaks(),
    labels = ~percent(./100),
    expand = expansion(.1)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(age != "Average"),
    aes(), 
    alpha = .15, col = NA
  ) +
  geom_line(
    data = . %>% filter(age != "Average"),
    aes(group = sex),
    size = .4
  ) +
  geom_pointrange(
    data = . %>% filter(age == "Average"),
    position = position_dodge(.9),
    size = .3, fatten = 0.1
  ) +
  facet_grid(
    outcome~region, scales = "free_y", 
    labeller = as_labeller(~str_replace(., "_", "\n"))) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "none",
    axis.title.x = element_blank()
  )
agg_png(
  "figures/Fig-timecourses-demographics.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

## Associations

### Internet

Calculate contrast by sex at the world level.

```{r}
h_internet_associations <- c(
  Slope_Male = "i1_cw + i1_cw:sex1 * -1 = 0",
  Slope_Female = "i1_cw + i1_cw:sex1 * 1 = 0"
)
cluster_copy(cluster, "h_internet_associations")

internet_associations_world_average <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()

internet_associations_world_average %>% 
  unnest(out)
```

And then for each sex*age at the world level.

```{r}
internet_associations_world_age <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
internet_associations_world_age %>% 
  unnest(out)
```

And for all regions too.

First we calculate the contrast by sex for each region.

```{r}
get_internet_region_association_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note .1 for 10% change
    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (i1_cw*sex | region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_internet_region_association_avg <- memoise(
  get_internet_region_association_avg, cache = cd
)

cluster_copy(cluster, "get_internet_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
internet_associations_region_average <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_avg)) %>% 
  collect()
internet_associations_region_average %>% 
  unnest(out)
```

#### Demographics

Then we calculate the contrasts for each sex*age for each region.

```{r}
get_internet_region_association_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note .1 for 10% change
    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (i1_cw*sex | age) + 
        (i1_cw*sex | region) + (i1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_internet_region_association_age <- memoise(
  get_internet_region_association_age, cache = cd
)

cluster_copy(cluster, "get_internet_region_association_age")
internet_associations_region_age <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_age)) %>% 
  collect()
```

Combine these with world level estimates and plot

```{r}
internet_associations_world <- bind_rows(
  internet_associations_world_age %>% 
    unnest(out),
  internet_associations_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  separate(Hypothesis, c("Parameter", "sex")) %>% 
  mutate(
    # Convert to effect of 10% change in internet/mobile
    delta = Estimate/10,
    .lower = CI.Lower/10,
    .upper = CI.Upper/10
  ) %>% 
  select(
    outcome,
    age = Group,
    sex,
    delta,
    .lower,
    .upper,
  ) %>% 
  mutate(region = "World")

internet_associations <- bind_rows(
  internet_associations_region_age %>% 
    unnest(out),
  internet_associations_region_average %>% 
    unnest(out) %>% 
    mutate(age = "Average")
) %>% 
  ungroup() %>% 
  bind_rows(internet_associations_world) %>% 
  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
  arrange(sex) %>% 
  select(outcome:.upper) %>% 
  mutate(s = sign(.lower) == sign(.upper))
internet_associations %>%   
  ggplot(aes(
    age, delta, 
    ymin = .lower, ymax = .upper, 
    fill = sex, col = sex, group = sex)
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_x_discrete(
    breaks = x,
    labels = x2,
    expand = expansion(c(0.02, 0.06))
  ) +
  scale_y_continuous(
    "Conditional effect of 10% increase\nin per capita internet users",
    breaks = extended_breaks(),
    labels = ~percent(./100),
    expand = expansion(c(.25, .25))
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(age != "Average"),
    aes(), 
    alpha = .15, col = NA
  ) +
  geom_line(
    data = . %>% filter(age != "Average"),
    aes(group = sex),
    size = .4
  ) +
  geom_pointrange(
    data = . %>% filter(age == "Average"),
    position = position_dodge(.9),
    size = .2, fatten = 1.25
  ) +
  facet_grid(
    outcome~region, scales = "free_y", drop = FALSE,
    labeller = as_labeller(~str_replace(., "_", "\n"))) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "none",
    axis.title.x = element_blank()
  )
agg_png(
  "figures/Fig-associations-internet-demographics.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

#### Compare ages

We then compared, for selfharm, the youngest age group's association to all other age group's associations.

```{r}
fit_selfharm <- readRDS("models/brm-Selfharm-3.rds")
h <- hypothesis(fit_selfharm, "m1_cw = 0", scope = "coef", group = "age")
s <- tibble(h$samples)
hypothesis(s, paste0("H1 > H", 2:9))$hypothesis %>% 
  as.data.frame() %>% 
  kbl(digits = 4) %>% 
  kable_custom()
```

#### Forest plot

```{r}
library(ggstance)
internet_associations %>% 
  filter(age == "Average") %>% 
  ggplot(aes(delta, region, col = sex)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.3)
  ) +
  facet_wrap("outcome", scales = "free_x", ncol = 3)
```

### Mobile

This figure shows mobile --> outcome associations. Panels by outcome (rows) and region (columns; including World). Each panel shows the association by all ages and sex, and on average across ages. So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.

Calculate contrast by sex at the world level.

```{r}
get_hyp_avg <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h)$hypothesis
}
get_hyp_avg <- memoise(get_hyp_avg, cache = cd)

h_mobile_associations <- c(
  # Intercept_Male = "Intercept + sex1 * -1 = 0",
  # Intercept_Female = "Intercept + sex1 * 1 = 0",
  Slope_Male = "m1_cw + m1_cw:sex1 * -1 = 0",
  Slope_Female = "m1_cw + m1_cw:sex1 * 1 = 0"
)

cluster_library(cluster, c("brms", "purrr", "stringr"))
cluster_copy(cluster, c("get_hyp_avg", "h_mobile_associations"))

mobile_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()

mobile_associations_world_average %>% 
  unnest(out)
```

And then for each sex*age at the world level.

```{r}
get_hyp_age <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
}
get_hyp_age <- memoise(get_hyp_age, cache = cd)
cluster_copy(cluster, "get_hyp_age")

mobile_associations_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()
```

Combine these to one and plot

```{r}
bind_rows(
  mobile_associations_world_age %>% 
    unnest(out),
  mobile_associations_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  mutate(Group = fct_relevel(Group, "Average", "10 to 14")) %>% 
  select(outcome:CI.Upper) %>% 
  separate(Hypothesis, c("Parameter", "Sex")) %>% 
  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
  ggplot(aes(Group, Estimate, ymin = CI.Lower, ymax = CI.Upper, fill = Sex, col = Sex, group = Sex)) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_y_continuous(
    breaks = extended_breaks(),
    # Effect of 10%
    labels = ~percent(./1000), 
    expand = expansion(.4)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(Group != "Average"),
    aes(), 
    alpha = .2, col = NA
  ) +
  geom_line(
    data = . %>% filter(Group != "Average"),
    aes(group = Sex),
    size = .6
  ) +
  geom_pointrange(
    data = . %>% filter(Group == "Average"),
    position = position_dodge(.75),
    size = .4, fatten = 2.5
  ) +
  facet_wrap(
    "outcome", scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "none",
    axis.title.x = element_blank()
  )
```

And for all regions too.

First we calculate the contrast by sex for each region.

```{r}
get_region_association_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_association_avg <- memoise(
  get_region_association_avg, cache = cd
)

cluster_copy(cluster, "get_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
mobile_associations_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_avg)) %>% 
  collect()
mobile_associations_region_average %>% 
  unnest(out)
```

Then we calculate the contrasts for each sex*age for each region.

```{r}
get_region_association_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | age) + 
        (m1_cw*sex | region) + (m1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_association_age <- memoise(
  get_region_association_age, cache = cd
)

cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
cluster_copy(cluster, "get_region_association_age")
mobile_associations_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_age)) %>% 
  collect()
```

Combine these with world level estimates and plot

```{r}
mobile_associations_world <- bind_rows(
  mobile_associations_world_age %>% 
    unnest(out),
  mobile_associations_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  separate(Hypothesis, c("Parameter", "sex")) %>% 
  mutate(
    # Convert to effect of 10% change in internet/mobile
    delta = Estimate/10,
    .lower = CI.Lower/10,
    .upper = CI.Upper/10
  ) %>% 
  select(
    outcome,
    age = Group,
    sex,
    delta,
    .lower,
    .upper,
  ) %>% 
  mutate(region = "World")

mobile_associations <- bind_rows(
  mobile_associations_region_age %>% 
    unnest(out),
  mobile_associations_region_average %>% 
    unnest(out) %>% 
    mutate(age = "Average")
) %>% 
  ungroup() %>% 
  bind_rows(mobile_associations_world) %>% 
  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
  arrange(sex) %>% 
  select(outcome:.upper) %>% 
  mutate(s = sign(.lower) == sign(.upper))
mobile_associations %>%   
  ggplot(
    aes(
      age, delta, 
      ymin = .lower, ymax = .upper, 
      fill = sex, col = sex, group = sex
    )
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_x_discrete(
    breaks = x,
    labels = x2,
    expand = expansion(c(0.02, 0.06))
  ) +
  scale_y_continuous(
    "Conditional effect of 10% increase\nin per capita mobile broadband subscriptions",
    breaks = extended_breaks(),
    labels = ~percent(./100),
    expand = expansion(.4)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(age != "Average"),
    aes(), 
    alpha = .15, col = NA
  ) +
  geom_line(
    data = . %>% filter(age != "Average"),
    aes(group = sex),
    size = .4
  ) +
  geom_pointrange(
    data = . %>% filter(age == "Average"),
    position = position_dodge(.9),
    size = .2, fatten = 1.25
  ) +
  facet_grid(
    outcome~region, scales = "free_y", 
    labeller = as_labeller(~str_replace(., "_", "\n"))) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "none",
    axis.title.x = element_blank()
  )
agg_png(
  "figures/Fig-associations-mobile-demographics.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

#### Forest plot

```{r}
mobile_associations %>% 
  filter(age == "Average") %>% 
  ggplot(aes(delta, region, col = sex)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.3)
  ) +
  facet_wrap("outcome", scales = "free_x", ncol = 3)
```

### 2022-03-24 index.Rmd
Refactor

@@
----
-title: Global study of well-being and internet adoption | Online analysis supplement
-description: |
-  Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
-author: Matti Vuorre & Andy Przybylski
-date: "`r Sys.Date()`"
-site: bookdown::bookdown_site
-output: bookdown::bs4_book
-url: https://digital-wellbeing.github.io/global-wbmh
-biblio-style: apalike
----
+# Preface {.unnumbered}
 
-# Preface
+Welcome!
+This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [preprint]() in preparation).
+It contains all the analyses reported in the manuscript along with supplemental analyses.
+The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
 
-This repository ([GitHub](https://github.com/digital-wellbeing/global-wbmh) / [OSF](https://osf.io/ys7m9/)) contains the code and synthetic datasets required to reproduce all analyses reported in our manuscript, *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, in preparation).
-These analyses are presented in the [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh).
+::: {.callout-note}
+### How to reproduce our results
 
-## Materials
+The analyses were conducted in R, and can be reproduced locally:
 
-- [Preprint]()  
-  - A publicly available version of our manuscript in advance of peer-review and formal publication
-- [GitHub repository](https://github.com/digital-wellbeing/global-wbmh)  
-  - A version controlled repository containing all the raw data and code in this project
-- [OSF repository](https://osf.io/ys7m9/)  
-  - An archived permanent copy of the GitHub repository
-- [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)
-  - The output document of our analyses
+1. Clone the github repo
+  - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
+      OR
+  - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above
 
-## Reproducibility
+2. Prepare the R environment
+  - Terminal: `Rscript -e "renv::restore()"`  
+      OR
+  - RStudio: Click renv -> Restore Library in the Packages panel
 
-The code that we used to clean and analyse the data are organised in R Markdown (`.Rmd`) files in this directory, which are meant to be run in the sequence indicated by their numeric prefixes.
-To run all the cleaning and analyses, and compile the resulting document ([the online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)), run `bookdown::render_book()` in R or click "Build Book" in the RStudio IDE.
+3. Render the source files to a Quarto book
+ - Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
+  - Terminal: `quarto render`  
+      OR
+  - RStudio: Open the project (`global-wbmh.Rproj`) and click Render in the Build panel
 
-### Docker
+::: {.callout-important}
+The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
+**The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days.
+For this reason it might be easier to run the individual `.Rmd` files interactively in RStudio.
+:::
 
-To ensure the reproducibility of our analyses, you can use Docker:
-
-Build the Docker image
-```
-docker build \
-    --build-arg R_VERSION=4.1.1 \
-    --build-arg RENV_VERSION=0.14.0 \
-    -t global-wbmh .
-```
-
-Run the container and render output
-```
-docker run \
-    --rm \
-    -v "$(pwd):/home/" \
-    -v "/home/renv/library" \
-    -e MAX_CORES=1 \
-    global-wbmh \
-    R -e 'renv::restore(prompt = FALSE); rmarkdown::render("index.Rmd")'
-```
+If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
+:::

### 2022-03-24 R/functions.R

@@ -13,185 +13,3 @@ kable_custom <- function(x) {
     full_width = FALSE
   )
 }
-
-#' Model summary
-#'
-#' @param x a brmsfit
-#'
-#' @return A tibble with information on data in the model
-msum <- function(x) {
-  tibble(
-    regions = ngrps(x)$region,
-    countries = ngrps(x)$country,
-    `year/country` = x$data %>%
-      distinct(country, year) %>%
-      count(country) %>%
-      pull(n) %>%
-      median(),
-    nobs_internet = standata(x)$N_internet,
-    nobs_outcome = standata(x)$N_val,
-    outcome_range = str_glue(
-      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
-    )
-  )
-}
-
-#' Posterior draws at average and grouping levels
-#'
-#' @param x brmsfit model 1/2
-#' @param p name of parameter
-#' @param grouping the grouping factor (e.g. region)
-#'
-#' @return a long tibble of posterior draws of p for every group in grouping (including the average, so useful for e.g. forest plots)
-pdraws <- function(x, p = "val_year", grouping = "region") {
-  bind_cols(
-    tibble("Average" = fixef(x, summary = FALSE)[, p]),
-    as_tibble(coef(x, summary = FALSE)[[grouping]][, , p])
-  ) %>%
-    pivot_longer(everything(), names_to = grouping)
-}
-
-#' Country-specific posterior summaries
-#'
-#' @param x brmsfit model 1/2
-#' @param p name of parameter
-#'
-#' @return a long tibble with posterior summary of p at each level
-psums <- function(x, p = "val_year") {
-  psum_region <- bind_rows(
-    fixef(x) %>%
-      as.data.frame() %>%
-      rownames_to_column("parameter") %>%
-      filter(parameter == {{ p }}) %>%
-      select(-parameter) %>%
-      mutate(region = "Average"),
-    coef(x)$region[, , p] %>%
-      as.data.frame() %>%
-      rownames_to_column("region")
-  ) %>%
-    as_tibble()
-
-  psum_country <- ranef(x)$country[, , p] %>%
-    as.data.frame() %>%
-    rownames_to_column("country") %>%
-    left_join(distinct(x$data, region, country)) %>%
-    as_tibble() %>%
-    left_join(select(psum_region, region, r_value = Estimate)) %>%
-    mutate(across(Estimate:Q97.5, ~ . + r_value)) %>%
[…]

### 2022-03-24 _common.R

@@ -1,16 +1,23 @@
 library(ggplot2)
-# Plotting theme & use this font if available
-Font <- "Titillium Web"
+library(ragg)
+library(khroma)
+
+# Plotting options
+# If you've defined a custom font, we will use it in outputs
+Font <- Sys.getenv("FONT")
 theme_set(
   theme_linedraw(
-    base_size = 12,
+    base_size = 9,
     base_family = Font
   ) +
     theme(
       panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
+      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
+      axis.text = element_text(size = rel(0.75))
     )
 )
+# Width of figures
+W <- 9
 
 library(knitr)
 opts_chunk$set(

### 2022-03-24 00-clean.Rmd
New synthetic GWP data

@@
   )
+  gwp_syn <- tibble(gwp_syn$syn)
   saveRDS(gwp_syn, gwp_mock_path)

### 2022-03-30 00-clean.Rmd
Small fixes

@@
 # Confirm that correct measures were downloaded:
-distinct(gbd, measure, metric)
+# distinct(gbd, measure, metric)
 gbd <- select(gbd, -metric, -measure)

### 2022-03-30 02-results.Rmd
Small fixes

@@
 # Packages
-library(tidyverse)
 library(scales)
@@
 library(multidplyr)
+library(tidyverse)
 
@@
   collect()
-
-timecourses_world_average %>% 
-  unnest(out)
 ```
@@
     # Note 1 for 10 year change
-    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
+    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
     add_epred_draws(
@@
   tmp %>% 
-    select(-.row, -se, -.chain, -.iteration) %>% 
+    select(-.row, -se, -.chain, -.iteration, -val) %>% 
     pivot_wider(names_from = year, values_from = .epred) %>% 
@@
   collect()
-timecourses_region_average %>% 
-  unnest(out)
 ```
@@
     # Note 1 for decade change
-    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
+    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
     add_epred_draws(
@@
 internet_associations_world_average <- fits %>% 
-  slice(1:3) %>% 
   group_by(outcome) %>% 
@@
   collect()
-
-internet_associations_world_average %>% 
-  unnest(out)
 ```
@@
 internet_associations_world_age <- fits %>% 
-  slice(1:3) %>% 
   group_by(outcome) %>% 
@@
   collect()
-internet_associations_world_age %>% 
-  unnest(out)
 ```
@@
 internet_associations_region_average <- fits %>% 
-  slice(1:3) %>% 
   group_by(outcome) %>% 
@@
   collect()
-internet_associations_region_average %>% 
-  unnest(out)
 ```
@@
 internet_associations_region_age <- fits %>% 
-  slice(1:3) %>% 
   group_by(outcome) %>% 
@@
   collect()
-
-mobile_associations_world_average %>% 
-  unnest(out)
 ```
@@
     # Note .1 for 10% change
-    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
+    crossing(m1_cw = c(0, .1), se = 0, year = 0, val = 1) %>% 
     add_epred_draws(
@@
   tmp %>% 
-    select(-.row, -se, -.chain, -.iteration) %>% 
+    select(-.row, -se, -.chain, -.iteration, -val) %>% 
     pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
@@
   collect()
-mobile_associations_region_average %>% 
-  unnest(out)
 ```
@@
 
-cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
+cluster_library(cluster, c("dplyr", "tidyr", "tidybayes", "purrr"))
 cluster_copy(cluster, "get_region_association_age")

### 2022-04-08 00-describe.Rmd

@@
   kable_custom()
-gwp %>% 
+tmp <- gwp %>% 
   group_by(outcome) %>% 
   summarise(n=sum(n)) %>% 
-  summarise(N=comma(median(n)))
+  summarise(N=comma(median(n))) %>% 
+  pull(N)
 ```
+
+The median number of respondents per (well-being) outcome was `r tmp`, and the unique age bins in the GWP data were `r unique(gwp$age)`.
 
@@
 ```{r}
-unique(gwp$age)
 bind_rows(
@@
   mutate(Dataset = fct_inorder(Dataset)) %>% 
-  count(Dataset, outcome)
-itu %>% 
-  drop_na(internet)
+  count(Dataset, outcome) %>% 
+  kbl(caption = "Observations per outcome") %>% 
+  kable_custom()
 
+```
+
+Number of ITU observations
+
+```{r}
+tmp <- itu %>% 
+  select(region, country, year, internet, mobile)
+tmp %>% 
+  drop_na(mobile)
 ```

### 2022-04-08 00-clean.Rmd
Add HDI cleaning

@@
 gwp <- left_join(gwp, regions)
+hdi <- left_join(hdi, regions) %>% 
+  drop_na(region)
+
 # Remove now unnecessary variables
@@
 write_rds(gbd, "data/gbd.rds")
+write_rds(hdi, "data/hdi.rds")
 ```

### 2022-04-08 02-controls.Rmd
Init control analyses

# Control analyses

```{r setup}
#| cache: false
# Packages
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(memoise)
library(cachem)
library(lubridate)
library(posterior)
library(ggh4x)
library(parameters)
library(janitor)
library(countrycode)
library(emmeans)
library(patchwork)
library(multidplyr)
library(tidyverse)

cluster <- new_cluster(3)

cd <- cache_disk("memoise_cache", max_size = Inf)

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)

fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

dat <- readRDS("data/data-all.rds")
```

Here, we analyse associations between other country-level indicators and well-being and mental health.

### 2022-04-08 02-controls.Rmd
visualize hdi

@@
 Here, we analyse associations between other country-level indicators and well-being and mental health.
+
+```{r}
+hdi <- read_rds("data/hdi.rds")
+hdi %>%
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(year, hdi)) +
+  scale_y_continuous(
+    "Value",
+    labels = ~percent(., .1),
+    breaks = pretty_breaks(),
+    expand = expansion(.05)
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015, 2020)),
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country)),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  facet_grid(
+    ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
+    aspect.ratio = 1,
+    legend.position = "none",
+    panel.spacing.x = unit(4, "pt"),
+    panel.spacing.y = unit(6, "pt"),
+    axis.title.y = element_blank()
+  )
+```
+
+```{r}
+# Merge to country-aggregated outcomes
+tmp <- dat %>% 
+  mutate(year = (year * 10 + 2010)) %>% 
+  group_by(country, year, outcome) %>% 
+  summarise(val = mean(val, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  right_join(hdi) %>% 
+  mutate(year = (year - 2010) / 10) %>% 
+  drop_na(val)
+```

### 2022-04-08 00-clean.Rmd
Combine predictors to one table

@@
 
+-   Combine all predictors into one table (primary ITU and controls HDI)
 -   Create lagged and centered predictors
@@
 ```{r model-prepare-data}
+# Merge different predictors to itu
+itu <- left_join(itu, hdi)
+
 # Create lagged predictors
@@
     across(
-      c(internet, mobile),
+      c(internet, mobile, hdi),
       list(`1` = ~ lag(., 1)),
@@
   mutate(
-    i1_cb = mean(i1, na.rm = TRUE), # Country average
-    i1_cw = i1 - i1_cb, # Year-specific deviation from country average
-    m1_cb = mean(m1, na.rm = TRUE),
-    m1_cw = m1 - m1_cb,
+    # Year-specific deviations from country average
+    i1_cw = i1 - mean(i1, na.rm = TRUE), 
+    m1_cw = m1 - mean(m1, na.rm = TRUE),
+    h1_cw = h1 - mean(h1, na.rm = TRUE)
   ) %>% 
-  # Grand-mean center the country averages
-  ungroup() %>% 
-  mutate(
-    across(c(i1_cb, m1_cb), ~ . - mean(., na.rm = T))
-  )
+  ungroup()
 
@@
 write_rds(gbd, "data/gbd.rds")
-write_rds(hdi, "data/hdi.rds")
 ```

### 2022-05-04 00-clean.Rmd
Wip controls

@@
 
+## HDI
+
 This data set was downloaded from <http://hdr.undp.org/en/indicators/137506#> in November 2021, and shared here under the terms of use <http://hdr.undp.org/en/content/copyright-and-terms-use>.
@@
     # Year-specific deviations from country average
+    i_cw = internet - mean(internet, na.rm = TRUE), 
+    m_cw = internet - mean(mobile, na.rm = TRUE),
+    h_cw = internet - mean(hdi, na.rm = TRUE),
     i1_cw = i1 - mean(i1, na.rm = TRUE), 

### 2022-05-04 02-controls.Rmd
Wip controls

--- 2022-04-08 02-controls.Rmd
@@
 library(scales)
-library(kableExtra)
 library(ggstance)
-library(brms)
-library(tidybayes)
-library(ggdist)
 library(memoise)
 library(cachem)
+library(lme4)
+library(broom.mixed)
 library(lubridate)
-library(posterior)
-library(ggh4x)
-library(parameters)
 library(janitor)
-library(countrycode)
-library(emmeans)
 library(patchwork)
-library(multidplyr)
 library(tidyverse)
-
-cluster <- new_cluster(3)
 
@@
 Here, we analyse associations between other country-level indicators and well-being and mental health.
+
+## Human development index
+
+```{r}
+itu <- read_rds("data/itu.rds")
+itu %>%
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(year, hdi)) +
+  scale_y_continuous(
+    "Value",
+    labels = ~percent(., .1),
+    breaks = pretty_breaks(),
+    expand = expansion(.05)
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015, 2020)),
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(group = interaction(country)),
+    alpha = .25, size = .4, color = "dodgerblue1"
+  ) +
+  facet_grid(
+    ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
+    aspect.ratio = 1,
+    legend.position = "none",
+    panel.spacing.x = unit(4, "pt"),
+    panel.spacing.y = unit(6, "pt"),
+    axis.title.y = element_blank()
+  )
+```
+
+```{r}
+# Merge to country-aggregated outcomes
+tmp <- dat %>% 
+  mutate(year = (year * 10 + 2010)) %>% 
+  # Aggregate to country-year means (across age & sex)
+  group_by(region, country, year, outcome) %>% 
+  summarise(
+    val = mean(val, na.rm = TRUE), 
+  ) %>% 
+  ungroup() %>% 
+  # Join to country-year predictors
+  left_join(itu) %>% 
+  mutate(year = (year - 2010) / 10) %>% 
+  drop_na(val)
+```
+
+### Between-country associations
+
+```{r}
+# Correlate country-level intercepts of outcomes and predictors
+coef2 <- possibly(coef, NA)
+tmp %>% 
+  mutate(hdi = hdi - mean(hdi, na.rm = TRUE)) %>% 
+  group_by(outcome, region, country) %>% 
+  group_modify(
+    ~tibble(
+      mean = coef(lm(val ~ 1, data = .))[1],
+      adjusted = coef2(lm(val ~ 1 + hdi, data = .))[1]
+      )
+  )
+
+# Data for average levels scatterplots
+dat_avg <- tmp %>%
+  group_by(outcome, region, country) %>%
+  summarise(
+    internet = mean(internet, na.rm = TRUE),
+    mobile = mean(mobile, na.rm = TRUE),
+    hdi = mean(hdi, na.rm = TRUE),
+    val = mean(val, na.rm = TRUE)
+  ) %>%
+  ungroup()
+
+dat_avg
+
+p_means_ols_internet <- dat_avg %>%
+  ggplot(aes(y = val, col = region)) +
+  scale_color_discreterainbow(
+    name = "Region",
+    labels = ~str_replace(., "_", " ")
+  ) +
+  scale_y_continuous(
+    "Mean outcome",
+    labels = ~percent(./100, .1),
+    breaks = extended_breaks()
+  ) +
+  geom_point(
+    shape = 1, size = 1.0, alpha = .75
+  ) +
+  facet_wrap(
+    ~outcome,
+    scales = "free", nrow = 1,
+    labeller = as_labeller(~str_replace(., "_", " ") %>% str_to_title(.))
+  ) +
+  guides(
+    color = guide_legend(
+      override.aes = list(alpha = 1, shape = 16, size = 1.5)
+    )
+  ) +
+  theme(
+    aspect.ratio = 1
+  )
+
+p_means_ols_internet <- p_means_ols_internet +
+  aes(x = internet) +
+  scale_x_continuous(
+    "Mean internet users per capita",
+    breaks = seq(0, 1, by = .25),
+    labels = ~percent(.),
+    limits = 0:1
+  )
+p_means_ols_mobile <- p_means_ols_internet +
+  aes(x = mobile) +
+  scale_x_continuous(
+    "Mean mobile internet subscriptions per capita",
+    breaks = seq(0, 1.5, by = .5),
+    labels = ~percent(.),
+    limits = c(0, 1.5)
+  )
+
+(p_means_ols_internet | 
+    p_delta_ols_internet | 
+    p_means_ols_mobile | 
+    p_delta_ols_mobile
+) +
+  plot_layout(nrow = 4, guides = "collect")
+
+agg_png(
+  "figures/Fig-country-correlations-OLS.png",
+  width = W, height = W*0.8, units = "in", res = 400
+)
+last_plot()
+dev.off()
+
+# Coefficient plot
+means_ols_cors <- dat_avg %>%
+  group_by(outcome) %>%
+  group_modify(
+    ~tidy(lm(scale(val) ~ scale(internet), data = .), conf.int = TRUE)
+  ) %>%
+  filter(term != "(Intercept)")
+delta_ols_cors <- delta_ols %>%
+  group_by(outcome) %>%
+  group_modify(
+    ~tidy(lm(scale(estimate_val) ~ scale(estimate_internet), data = .), conf.int = TRUE)
+  ) %>%
+  filter(term != "(Intercept)")
+cor_pars_ols <- bind_rows(
+  "Means" = means_ols_cors,
+  "Deltas" = delta_ols_cors,
+  .id = "type"
+)
+cor_pars_ols %>%
+  mutate(type = fct_rev(type)) %>%
+  mutate(outcome = fct_rev(factor(outcome, levels = oo))) %>%
+  ggplot(aes(estimate, outcome)) +
+  geom_vline(xintercept = 0, lty = 2, size = .25) +
+  geom_pointrangeh(aes(xmin = conf.low, xmax = conf.high)) +
+  facet_wrap("type") +
+  labs(x = "Correlation") +
+  theme(axis.title.y = element_blank())
+```
+
+### Within-country associations
+
+```{r}
+predictors <- c("internet", "i_cw", "i1", "i1_cw", "hdi", "h_cw", "h1", "h1_cw")
+lmer2 <- memoise(lmer, cache = cd)
+out <- fits %>% 
+  crossing(
+    x = predictors
+  ) %>% 
+  mutate(
+    frm = str_glue(
+      "val ~ {x} + year + ({x} + year | country) + ({x} + year | region)"
+    )
+  ) %>% 
+  mutate(
+    fit = map2(
+      frm, outcome, 
+      ~lmer2(.x, data = tmp %>% filter(outcome == .y))
+    )
+  )
+
+pars <- out %>% 
+  mutate(
+    fixef = map(
+      fit,
+      ~tidy(.x, effects = "fixed", conf.int = TRUE)
+    ),
+    coef_region = map(
+      fit,
+      ~coef(.x)$region %>% 
+        rownames_to_column("region") %>% 
+        pivot_longer(-region, names_to = "term", values_to = "estimate")
+    )
+  ) %>% 
+  mutate(
+    x = factor(
+      x,
+      levels = predictors
+    )
+  ) %>% 
+  select(-fit)
+
+pars %>%
+  select(-coef_region) %>% 
+  unnest(fixef) %>% 
+  filter(!(term %in% c("(Intercept)", "year"))) %>% 
+  ggplot(aes(estimate, x)) +
+  scale_y_discrete("Predictor", limits = rev) +
+  scale_x_continuous(
+    "Conditional effect of 10% change in predictor",
+    breaks = extended_breaks(),
+    # Visualize conditional effect of 10% change on x
+    # Modelled (0-100), change to proportion so percentage is correct
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .25) +
+  geom_point(
+    data = pars %>% 
+      select(-fixef) %>% 
+      unnest(coef_region) %>% 
+      filter(!(term %in% c("(Intercept)", "year"))),
+    size = .75, shape = 1,
+    position = position_nudge(y = -.2)
+  ) +
+  geom_pointrangeh(
+    aes(xmin = conf.low, xmax = conf.high),
+    position = position_dodge2v(.25),
+    fatten = 3
+  ) +
+  facet_wrap("outcome", scales = "free_x", nrow = 2)
+```
+
+```{r}
+library(mgcv)
+tmp2 <- tmp %>% 
+  filter(outcome == "Life_satisfaction") %>% 
+  mutate(country = factor(country))
+
+fit <- gamm(
+  val ~ s(year, by = region) + s(internet, by = region), 
+  random = list(
+    # region = ~1,
+    country = ~1
+  ),
+  data = tmp2,
+  method = "REML"
+  )
+summary(fit$gam)
+summary(fit$lme)
+library(gratia)
+library(ggh4x)
+draw(fit, nrow = 2)
+# Draw only for values in data for each region
+
+smooth_year <- smooth_estimates(
+    fit, 
+    smooth = "s(year)", 
+    partial_match = TRUE
+  ) %>%
+  rename(X = year)
+smooth_internet <- smooth_estimates(
+    fit, 
+    smooth = "s(internet)", 
+    partial_match = TRUE
+) %>% 
+  left_join(
+    tmp2 %>% 
+      group_by(region) %>% 
+      summarise(min = min(internet, na.rm = TRUE))
+  ) %>% 
+  filter(internet >= min | is.na(internet)) %>% 
+  rename(X = internet)
+bind_rows(
+  "Time" = smooth_year,
+  "Internet" = smooth_internet,
+  .id = "Predictor"
+) %>% 
+  ggplot(aes(X, est)) +
+  scale_x_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(.)
+  ) +
+  scale_y_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(./100)
+  ) +
+  geom_ribbon(aes(ymin = est-se, ymax = est+se), alpha = .2) +
+  geom_line() +
+  facet_grid2(Predictor~region, scales = "free", independent = "x")
+
+library(emmeans)
+emtrends(fit, var = "internet", data = fit$lme$data, )
+emmeans(
+  fit, 
+  "internet", 
+  at = group_by(tmp2, region) %>% 
+    summarise(internet = min(internet, na.rm = TRUE)), 
+  data = fit$lme$data,
+  by = "region"
+)
+```

### 2022-05-04 00-clean.Rmd
Switch from GLOBE to WB regions

@@
 
-## GLOBE regions
+## Regions
 
-We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised.
-This allows us to eg.
-present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models.
-We use the extended GLOBE regions following Jebb et al.
-(2020), and had to manually add labels to some countries that were not grouped in those studies.
+>continent: "Continent as defined in the World Bank Development Indicators"
 
-```{r globe-regions}
-#| results: hold
-#| label: tbl-globe
-#| tbl-cap: "Countries with manually filled region"
-
-regions <- read_csv(
-  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
+```{r}
+regions <- bind_rows(
+  distinct(itu, country),
+  distinct(gbd, country),
+  distinct(gwp, country)
 ) %>% 
-  # Jebb et al used * to indicate deviance from GLOBE, remove
-  mutate(country = str_remove_all(country, "\\*")) %>%
-  # Standardize country names
-  # This drops Nagorno-Karabakh Republic
-  mutate(country = countryname(country)) %>%
-  drop_na(country)
-
-# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
-regions <- distinct(regions, region, country)
-
-# Countries in GBD not present in region data
-no_region_gbd <- filter(
-  distinct(gbd, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-# Then see what countries in GWP are without region
-no_region_gwp <- filter(
-  distinct(gwp, country),
-  !(country %in% unique(regions$country))
-) %>%
-  arrange(country)
-
-bind_rows(no_region_gbd, no_region_gwp) %>%
-  arrange(country) %>%
   distinct() %>% 
-  write_csv("data-raw/Regions/countries-without-region.csv")
-
-# I then filled missing regions in Jebb et al and extended GLOBE referenced therein
-
-# Load our manually filled region data
-regions_filled <- read_csv(
-  "data-raw/Regions/countries-without-region-filled.csv"
+  mutate(
+    region = countrycode(
+      country, 
+      origin = "country.name", 
+      destination = "continent"
+    )
   )
 
-# Combine Jebb et al GLOBE regions and our manually added ones
+# Manually fix two countries
 regions <- regions %>% 
-  bind_rows(
-    regions_filled %>%
-      mutate(Note = "Filled")
-  ) %>%
-  arrange(region, country)
-
-# Shorter name for plots
-regions <- regions %>%
-  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))
-
-# Display table of regions and countries
-regions %>%
-  drop_na(Note) %>%
-  select(-Note) %>%
-  arrange(region, country) %>%
-  kbl(caption = "Countries with a manually filled region") %>%
-  kable_custom()
-
-# Clean region labels
-regions$region <- str_replace_all(regions$region, " ", "_")
-regions$region <- factor(regions$region)
-
-# Remove unnecessary items
-regions <- select(regions, -Note)
+  mutate(
+    region = if_else(country == "Kosovo", "Europe", region),
+    region = if_else(country == "Nagorno Karabakh", "Asia", region)
+    )
 
@@
 
-# Remove now unnecessary variables
-rm(no_region_gbd, no_region_gwp, regions_filled, regions)
+regions %>% 
+  group_by(region) %>%
+  summarise(
+    N = n(),
+    Countries = str_c(country, collapse = ", ")
+  ) %>% 
+  kbl(caption = "Regions") %>% 
+  kable_custom()
 ```

### 2022-05-04 00-describe.Rmd
More informative ITU summary

@@
   kable_custom()
-
 ```
@@
 ```{r}
-tmp <- itu %>% 
-  select(region, country, year, internet, mobile)
-tmp %>% 
-  drop_na(mobile)
+itu %>% 
+  summarise(
+    internet = sum(!is.na(internet)),
+    mobile = sum(!is.na(mobile))
+  )
 ```

### 2022-05-04 models.R
Update models to 2level

@@ -4,6 +4,7 @@
 # of outcomes (6) and models (4)
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cmdargs <- as.numeric(cmdargs)
+if (length(cmdargs) == 0) cmdargs <- menu(c(1:24, "Abort"), "Choose model")
 cat("\nFitting row\n", cmdargs)
 
 # ---- setup ---------------------------------------------------------------
@@ -46,110 +47,54 @@ fits <- dat %>%
 
 # models ------------------------------------------------------------------
 
+# Bivariate internet & outcome on time
 bf_itu <- bf(
   internet | subset(itu) ~
     year +
-    (year |c| country) +
-    (year |r| region),
+    (year |c| country),
   family = Beta()
 )
-
 bf_val <- bf(
   val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
     year * sex +
     (year * sex | c | country) +
-    (year * sex | r | region) +
     (year * sex || age) +
-    (year * sex || age:country) +
-    (year * sex || age:region),
+    (year * sex || age:country),
   family = gaussian()
 )
-
 bf_1 <- bf_itu + bf_val + set_rescor(FALSE)
 
-# Simplified model for self-harm
-bf_val.s <- bf(
-  val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
-    year * sex +
-    (year * sex | c | country) +
-    (year * sex | r | region) +
-    (year * sex || age) +
-    (year * sex || age:region),
-  family = gaussian()
-)
-
-bf_1.s <- bf_itu + bf_val.s + set_rescor(FALSE)
-
-bf_2 <- bf(
-  val | se(se, sigma = TRUE) ~
-    (year + i1_cw) * sex +
-    ((year + i1_cw) * sex | country) +
-    ((year + i1_cw) * sex | region) +
-    ((year + i1_cw) * sex || age) +
-    ((year + i1_cw) * sex || age:country) +
-    ((year + i1_cw) * sex || age:region),
-  family = gaussian()
-)
-
-bf_2.s <- bf(
-  val | se(se, sigma = TRUE) ~
-    (year + i1_cw) * sex +
-    ((year + i1_cw) * sex | country) +
-    ((year + i1_cw) * sex | region) +
-    ((year + i1_cw) * sex || age) +
[…]

### 2022-05-06 models.R
Indicate which model is being fitted

@@ -5,7 +5,6 @@
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cmdargs <- as.numeric(cmdargs)
 if (length(cmdargs) == 0) cmdargs <- menu(c(1:24, "Abort"), "Choose model")
-cat("\nFitting row\n", cmdargs)
 
 # ---- setup ---------------------------------------------------------------
 
@@ -101,5 +100,7 @@ fits <- fits %>%
 hmc$data <- fits$data[[cmdargs]]
 hmc$formula <- fits$bfrm[[cmdargs]]
 hmc$file <- str_glue("models/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
+
+cat("Now fitting", hmc$file)
 
 do.call(brm, hmc)

### 2022-05-06 submit.sh
Get notified when job ends

@@ -8,6 +8,8 @@
 #SBATCH --mem-per-cpu=3G
 #SBATCH --time=7-00:00:00
 #SBATCH --job-name=DWG-Global
+#SBATCH --mail-type=END
+#SBATCH --mail-user=matti.vuorre@oii.ox.ac.uk
 
 module purge
 module load R/4.1.2-foss-2021b-ARC

### 2022-05-06 models.R
Adjust models & priors for nonconvergence

@@ -21,10 +21,10 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = min(ncores %/% nchains, 3),
-  iter = 2200,
-  warmup = 1100,
+  iter = 2500,
+  warmup = 1250,
   refresh = 100,
-  adapt_delta = .94,
+  adapt_delta = .95,
   max_treedepth = 10
 )
 
@@ -51,14 +51,14 @@ bf_itu <- bf(
   internet | subset(itu) ~
     year +
     (year |c| country),
-  family = Beta()
+  family = gaussian()
 )
 bf_val <- bf(
   val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
     year * sex +
     (year * sex | c | country) +
-    (year * sex || age) +
-    (year * sex || age:country),
+    (year * sex | age) +
+    (year * sex | age:country),
   family = gaussian()
 )
 bf_1 <- bf_itu + bf_val + set_rescor(FALSE)
@@ -76,8 +76,8 @@ bf_3 <- bf(
   val | se(se, sigma = TRUE) ~
     (year + i1_cw) * sex +
     ((year + i1_cw) * sex | country) +
-    ((year + i1_cw) * sex || age) +
-    ((year + i1_cw) * sex || age:country),
+    ((year + i1_cw) * sex | age) +
+    ((year + i1_cw) * sex | age:country),
   family = gaussian()
 )
 
@@ -86,8 +86,8 @@ bf_4 <- bf(
   val | se(se, sigma = TRUE) ~
     (year + m1_cw) * sex +
     ((year + m1_cw) * sex | country) +
-    ((year + m1_cw) * sex || age) +
-    ((year + m1_cw) * sex || age:country),
+    ((year + m1_cw) * sex | age) +
+    ((year + m1_cw) * sex | age:country),
   family = gaussian()
 )
 
@@ -100,6 +100,32 @@ fits <- fits %>%
 hmc$data <- fits$data[[cmdargs]]
 hmc$formula <- fits$bfrm[[cmdargs]]
 hmc$file <- str_glue("models/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
+hmc$prior <- NULL
+
+# Assign prior for mental health outcomes
+if (fits$outcome[[cmdargs]] %in% c("Anxiety", "Depression", "Selfharm"))
+  hmc$prior <- prior(
+    lkj(6), class = cor, group = age
+  ) +
+  prior(
[…]

### 2022-05-06 00-clean.Rmd
Missed one!
Update ITU data and fix typo

@@
 library(tidyverse)
+
+# Common options
+source("_common.R")
 
@@
   download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/PercentIndividualsUsingInternet.xlsx",
     "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
@@
   download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/FixedBroadbandSubscriptions_2000-2020.xlsx",
     "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
@@
   download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/MobileBroadbandSubscriptions_2007-2020.xlsx",
     "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
@@
 itu <- itu %>%
+  # Grand mean centering so both components are zero-centered
+  mutate(across(c(i1, m1, h1), ~. - mean(., na.rm = TRUE))) %>% 
   group_by(country) %>%
   mutate(
-    # Year-specific deviations from country average
-    i_cw = internet - mean(internet, na.rm = TRUE), 
-    m_cw = internet - mean(mobile, na.rm = TRUE),
-    h_cw = internet - mean(hdi, na.rm = TRUE),
-    i1_cw = i1 - mean(i1, na.rm = TRUE), 
-    m1_cw = m1 - mean(m1, na.rm = TRUE),
-    h1_cw = h1 - mean(h1, na.rm = TRUE)
+    # Between
+    i1_cb = mean(i1, na.rm = TRUE),
+    m1_cb = mean(m1, na.rm = TRUE),
+    h1_cb = mean(h1, na.rm = TRUE),
+    # Within
+    i1_cw = i1 - i1_cb, 
+    m1_cw = m1 - m1_cb,
+    h1_cw = h1 - h1_cb
   ) %>% 
@@
   mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(outcome, region, country, year)
+  arrange(outcome, country, region, year)
 

### 2022-05-06 models.R

@@ -95,37 +95,52 @@ bf_4 <- bf(
 fits <- fits %>%
   crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
 
+# Assign priors to mental health outcomes
+# Defaults to all
+fits <- fits %>%
+  mutate(
+    prior = map2(bfrm, data, ~get_prior(.x, .y))
+  )
+# Informative ones to mental health
+ip <- c(
+  prior(
+    lkj(6), class = cor, group = age
+  ),
+  prior(
+    lkj(6), class = cor, group = age:country
+  ),
+  prior(
+    student_t(7, 0, .2), class = sd, group = age:country, resp = val,
+    coef = "Intercept"
+  ),
+  prior(
+    student_t(7, 0, .02), class = sd, group = age:country, resp = val,
+    coef = "sex1"
+  ),
+  prior(
+    student_t(7, 0, .05), class = sd, group = age:country, resp = val,
+    coef = "year"
+  ),
+  prior(
+    student_t(7, 0, .02), class = sd, group = age:country, resp = val,
+    coef = "year:sex1"
+  )
+)
+fits <- fits %>%
+  mutate(
+    prior = if_else(
+      outcome %in% c("Anxiety", "Depression", "Selfharm"),
+      list(ip),
+      prior
+    )
+  )
+
+
 # fit model ---------------------------------------------------------------
 
 hmc$data <- fits$data[[cmdargs]]
 hmc$formula <- fits$bfrm[[cmdargs]]
 hmc$file <- str_glue("models/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
-hmc$prior <- NULL
-
-# Assign prior for mental health outcomes
-if (fits$outcome[[cmdargs]] %in% c("Anxiety", "Depression", "Selfharm"))
-  hmc$prior <- prior(
-    lkj(6), class = cor, group = age
-  ) +
-  prior(
-    lkj(6), class = cor, group = age:country
-  ) +
-  prior(
-    student_t(7, 0, .2), class = sd, group = age:country, resp = val,
-    coef = "Intercept"
-  ) +
-  prior(
-    student_t(7, 0, .02), class = sd, group = age:country, resp = val,
-    coef = "sex1"
-  ) +
-  prior(
-    student_t(7, 0, .05), class = sd, group = age:country, resp = val,
-    coef = "year"
-  ) +
-  prior(
[…]

### 2022-05-09 models.R
Include country means

@@ -74,7 +74,7 @@ bf_2 <- bf_mobile + bf_val + set_rescor(FALSE)
 # Univariate outcome on time and internet
 bf_3 <- bf(
   val | se(se, sigma = TRUE) ~
-    (year + i1_cw) * sex +
+    (year + i1_cw) * sex + i1_cb +
     ((year + i1_cw) * sex | country) +
     ((year + i1_cw) * sex | age) +
     ((year + i1_cw) * sex | age:country),
@@ -84,7 +84,7 @@ bf_3 <- bf(
 # Univariate outcome on time and mobile
 bf_4 <- bf(
   val | se(se, sigma = TRUE) ~
-    (year + m1_cw) * sex +
+    (year + m1_cw) * sex + m1_cb +
     ((year + m1_cw) * sex | country) +
     ((year + m1_cw) * sex | age) +
     ((year + m1_cw) * sex | age:country),

### 2022-05-09 submit.sh

@@ -8,8 +8,6 @@
 #SBATCH --mem-per-cpu=3G
 #SBATCH --time=7-00:00:00
 #SBATCH --job-name=DWG-Global
-#SBATCH --mail-type=END
-#SBATCH --mail-user=matti.vuorre@oii.ox.ac.uk
 
 module purge
 module load R/4.1.2-foss-2021b-ARC

### 2022-05-09 models.R
br

@@ -142,6 +142,6 @@ hmc$data <- fits$data[[cmdargs]]
 hmc$formula <- fits$bfrm[[cmdargs]]
 hmc$file <- str_glue("models/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
 
-cat("Now fitting", hmc$file)
+cat("\n\nNow fitting", hmc$file, "\n\n")
 
 do.call(brm, hmc)

### 2022-05-13 models.R
Fit more models

@@ -105,8 +105,19 @@ bf_4 <- bf(
 )
 bf_4.s <- update(bf_4, ~ . -((year + m1_cw) * sex | age:country))
 
+# Univariate outcome on time and hdi
+bf_5 <- bf(
+  val | se(se, sigma = TRUE) ~
+    (year + h1_cw) * sex + h1_cb +
+    ((year + h1_cw) * sex | country) +
+    ((year + h1_cw) * sex | age) +
+    ((year + h1_cw) * sex | age:country),
+  family = gaussian()
+)
+bf_5.s <- update(bf_5, ~ . -((year + h1_cw) * sex | age:country))
+
 fits <- fits %>%
-  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
+  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4, bf_5), model = 1:5))
 
 # Simplify models for mental health outcomes
 MH <- c("Anxiety", "Depression", "Selfharm")
@@ -117,6 +128,7 @@ fits <- fits %>%
       outcome %in% MH & model == 2 ~ list(bf_2.s),
       outcome %in% MH & model == 3 ~ list(bf_3.s),
       outcome %in% MH & model == 4 ~ list(bf_4.s),
+      outcome %in% MH & model == 5 ~ list(bf_5.s),
       TRUE ~ bfrm
     )
   ) %>%

### 2022-05-16 index.Rmd
Cleaning

@@
 Welcome!
-This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [preprint]() in preparation).
-It contains all the analyses reported in the manuscript along with supplemental analyses.
+This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [submitted]()).
+It contains all the analyses reported in the manuscript along with supplemental figures and data.
 The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
 
-::: {.callout-note}
 ### How to reproduce our results
@@
 
+If you encounter problems, please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
+
 ::: {.callout-important}
-The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
+The project repo includes the GBD and ITU datasets, and a synthetic mock version of the GWP dataset to enable reproducing all our computations.
 **The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days.
-For this reason it might be easier to run the individual `.Rmd` files interactively in RStudio.
+For this reason, the build will fail after having cleaned the data.
+Then, run `models.R` with settings specific to your environment/cluster.
+Once that is done you can build again and it should work.
 :::
-
-If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
-:::

### 2022-05-16 00-clean.Rmd
More explanation

@@
 
-```{r setup}
+```{r setup, include = FALSE}
 #| cache: false
@@
 -   Create age categories in line with GBD data
+-   Aggregate data to means and SEs at each country * year * age * sex group
 -   Drop one 13 year old as this data should only have people 15 and older
@@
 
-We have three data sets with information on countries.
+We have multiple data sets with information on countries.
 Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values.
@@
 -   Convert GBD estimated rate CI limits to an approximate standard error
--   Subset data to young people (10 - 24)
 
@@
 
-# Replace broken string
-hdi$country[46]
-hdi$country[46] <- "Côte d’Ivoire"
-
 # Harmonise names
@@
 
->continent: "Continent as defined in the World Bank Development Indicators"
+We also include a `region` variable in the data ("Continent as defined in the World Bank Development Indicators") to allow grouping countries in figures and outputs.
 
@@
 
-## ITU summary table
-
-```{r itu-summary-table}
-#| column: page-right
-#| tbl-cap: "Mean internet user percentages across regions and time."
-#| label: tbl-itusummary
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  mutate(region = str_replace(region, "_", " ")) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra(caption = "ITU summary") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-```
-
 ## Prepare model data
 
--   Combine all predictors into one table (primary ITU and controls HDI)
+We then further wrangle this data in preparation for the models:
+
+-   Combine all predictors into one table
 -   Create lagged and centered predictors
--   Transform edge values of internet variable to fit beta
-    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
 -   Join outcome and predictor tables
--   Center year on 2010 (roughly in the middle)
--   Ensure that age and sex are treated with contrast codes
+-   Center year on 2010 (roughly in the middle) and divide by ten ("effect" of decades)
 
@@
   ungroup()
-
-# Transform internet edge cases
-itu <- itu %>%
-  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
-  mutate(internet = if_else(internet == 1, .9999999, internet))
 

### 2022-05-16 _common.R
Don't echo code in outputs

@@ -21,7 +21,8 @@ W <- 9
 
 library(knitr)
 opts_chunk$set(
-  cache.lazy = FALSE
+  cache.lazy = FALSE,
+  echo = FALSE
 )
 
 source("R/functions.R")

### 2022-06-30 00-clean.Rmd
wip 2022-06-30

@@
 library(lubridate)
-library(gtsummary)
 library(kableExtra)

### 2022-06-30 00-describe.Rmd
Don't load anything in .Rprofile
wip 2022-06-30

--- 2022-03-24 00-describe.Rmd
@@
 library(ggh4x)
+library(gtsummary)
 library(mgcv)
+library(plotly)
 library(tidyverse)
+
+# Common options
+source("_common.R")
 
@@
 ```
+
+Here are some descriptives of the datasets.
+
+## Sample summaries
 
@@
   ) %>%
-  kbl(caption = "Dataset summary") %>% 
+  kbl(caption = "Number of respondents and years by outcome and region") %>% 
   kable_custom()
-gwp %>% 
+tmp <- gwp %>% 
   group_by(outcome) %>% 
   summarise(n=sum(n)) %>% 
-  summarise(N=comma(median(n)))
+  summarise(N=comma(median(n))) %>% 
+  pull(N)
 ```
 
-Number of data points per outcome
+The median number of respondents per Gallup well-being outcome was `r tmp`, and the unique age bins in the GWP data were `r unique(gwp$age)`.
+
+We then examined the total number of observations (cell means and SEs) per outcome
 
 ```{r}
-unique(gwp$age)
 bind_rows(
@@
   mutate(Dataset = fct_inorder(Dataset)) %>% 
-  count(Dataset, outcome)
+  count(Dataset, outcome) %>% 
+  bind_rows(
     itu %>% 
-  drop_na(internet)
+      select(internet, mobile) %>% 
+      pivot_longer(everything(), names_to = "outcome") %>% 
+      drop_na(value) %>% 
+      count(outcome) %>% 
+      mutate(Dataset = "ITU")
+  ) %>% 
+  kbl(caption = "Observations per outcome") %>% 
+  kable_custom()
+```
 
+And noted that the number of Gallup respondents decreases with age:
+
+```{r}
+gwp %>% 
+  # filter(age %in% c("15 to 19", "50 to 54", "85 to 89")) %>% 
+  group_by(age) %>% 
+  summarise(
+    n = quantile(n, probs = c(.1, .5, .9)),
+    quantile = c("10%", "50%", "90%")
+  ) %>% 
+  pivot_wider(names_from = quantile, values_from = n) %>% 
+  kbl(caption = "Quantiles of numbers of observations per age group") %>% 
+  kable_custom()
+```
+
+## ITU summary table
+
+Here is a table summarising the ITU internet predictor over time to region average percentage and number of coutries.
+
+```{r itu-summary-table}
+#| column: page-right
+#| tbl-cap: "Mean internet user percentages across regions and time."
+#| label: tbl-itusummary
+
+itu %>%
+  select(region, country, year, internet) %>%
+  mutate(internet = internet * 100) %>%
+  pivot_wider(names_from = year, values_from = internet) %>%
+  select(-country) %>%
+  tbl_summary(
+    by = region,
+    missing = "no",
+    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
+  ) %>%
+  add_overall(col_label = "Total") %>%
+  as_kable_extra(caption = "ITU summary") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_custom()
 ```
@@
 
-```{r trends-regions}
-#| echo: false
-#| fig-width: 12
+:::{.panel-tabset .column-body-outset-right}
+
+### Static
+
+```{r trends-regions, message = FALSE}
+#| fig-width: 10
 #| fig-height: 8
@@
     Internet = internet,
-    Mobile = mobile
+    Mobile = mobile,
   ) %>%
@@
 
-tmp_country %>%
+p1 <- tmp_country %>%
   mutate(year = make_date(year)) %>%
   ggplot(aes(year, mean)) +
+  scale_y_continuous(
+    "Value (%)",
+    # Display percentages
+    labels = ~. * 100,
+    breaks = pretty_breaks(),
+    expand = expansion(.05)
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2005, 2010, 2015, 2020)),
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(
+      group = interaction(country, outcome), 
+      text = str_glue("{country} {year(year)} ({percent(mean)})")
+    ),
+    alpha = .45, size = .3, color = "dodgerblue1"
+  ) +
+  # geom_line(
+  #   data = tmp_region %>% mutate(year = make_date(year)),
+  #   aes(
+  #     y = .fitted, 
+  #     group = interaction(region, outcome),
+  #     text = str_glue("{region} {year(year)} ({percent(.fitted)})")
+  #   ),
+  #   alpha = 1, size = .6, color = "dodgerblue4"
+  # ) +
+  # geom_line(
+  #   data = tmp_world %>% mutate(year = make_date(year)),
+  #   aes(
+  #     y = .fitted, 
+  #     group = interaction(region, outcome),
+  #     text = str_glue("{region} {year(year)} ({percent(.fitted)})")
+  #   ),
+  #   alpha = 1, size = .8, color = "dodgerblue4"
+  # ) +
+  facet_grid(
+    outcome ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
+    # aspect.ratio = 1,
+    legend.position = "none",
+    panel.spacing.x = unit(4, "pt"),
+    panel.spacing.y = unit(6, "pt")
+  )
+p1
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/Trends-data.png",
+  width = W, height = W*0.85, units = "in", res = 300
+)
+p1
+dev.off()
+```
+
+### Interactive
+
+```{r out.height = 860}
+#| fig-cap: "Trends in all variables across regions. Hover over years to show the country's name."
+#| label: fig-trends-regions-i
+gp <- ggplotly(p1, tooltip = "text")
+gp %>% 
+  layout(
+    margin = list(t = 30, r = 20, b = 40, l = 30),
+    width = 840, height = 840
+    )
+```
+
+### HDI
+
+```{r fig.height = 1.8}
+read_rds("data/itu.rds") %>% 
+  mutate(year = make_date(year)) %>%
+  ggplot(aes(year, hdi)) +
   scale_y_continuous(
@@
   geom_line(
-    aes(group = interaction(country, outcome)),
-    alpha = .25, size = .4, color = "dodgerblue1"
+    aes(
+      group = country, 
+      text = str_glue("{country} {year(year)} ({hdi})")
+    ),
+    alpha = .45, size = .3, color = "dodgerblue1"
   ) +
-  geom_line(
-    data = tmp_region %>% mutate(year = make_date(year)),
-    aes(y = .fitted, group = interaction(region, outcome)),
-    alpha = 1, size = .6, color = "dodgerblue4"
-  ) +
-  geom_line(
-    data = tmp_world %>% mutate(year = make_date(year)),
-    aes(y = .fitted, group = interaction(region, outcome)),
-    alpha = 1, size = .8, color = "dodgerblue4"
-  ) +
-  facet_grid(
-    outcome ~ region,
+  facet_wrap(
+    ~ region,
     scales = "free_y",
+    nrow = 1,
     labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
@@
   theme(
-    aspect.ratio = 1,
+    # aspect.ratio = 1,
     legend.position = "none",
@@
   )
-agg_png(
-  "figures/Fig-trends-data.png",
-  width = W, height = W*0.8, units = "in", res = 400
-)
-last_plot()
-dev.off()
 ```
+
+:::

### 2022-06-30 01-models.Rmd
Small fixes
Don't load anything in .Rprofile
wip 2022-06-30

@@
 library(brms)
-library(multidplyr)
 
-cluster <- new_cluster(3)
-
+# Common options
+source("_common.R")
 cd <- cache_disk("memoise_cache", max_size = Inf)
@@
 
-Here we discuss the models. The models are fitted in `models.R`. We submit that to our local SLURM cluster with `submit.sh`.
+Here we discuss the models. The code for estimating these models is in `models.R`. We submit that to our local HPC with SLURM scheduler with `submit.sh`.
 
@@
 
-Model 1 is a three-level bayesian multivariate meta-regression model that simultaneously estimates trends over time for the outcome (e.g.
-Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries.
-It also includes sex and the sex by time interaction predictors for the outcomes.
-The parameters are also treated as random across the age groups, and the age by country, and age by region interactions.
-We fit the model separately for each outcome.
-In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian.
+Model 1 is a two-level probabilistic multivariate meta-regression model that simultaneously predicts the health (e.g.
+Life satisfaction) and internet variables (e.g.
+internet adoption) from time, sex, and time by sex interactions.
+These regression coefficients are modelled as multivariate normal distributed over countries, age groups, and the country by age groups.
+The latter clustering was dropped from the mental health variables because of nonconvergence due to lack of variance in data ($\Sigma^\text{age:country} = 0$).
+The country-level covariance matrices are shared across the two outcomes so we can assess correlations between countries' intercepts and slopes over the two outcomes.
 
-The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate.
-For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age).
-The one downside of this modelling strategy is that it does not converge for self-harm.
-Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero.
-In addition, for self-harm, we remove the $age:country$ random effects.
-
-We write the model as
+Because we are modelling meta-analytic estimates (GBD) and aggregated scores (GWP), we also incorporate the aggregates' standard errors in the model to weight the observations on their corresponding uncertainties.
+Due to nonconvergence, we set the SEs to zero for self-harm ($v = 0$).
 
@@
 \begin{align}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2}v_i) \\
-
-\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{region}[i]} + \gamma^{y}_{0\text{country}[i]} + \delta^{y}_{0\text{age}[i]} + \zeta^{y}_{0\text{age:region}[i]} + \eta^{y}_{0\text{age:country}[i]} \\ &(\alpha^{y}_{1} + \beta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]} + \delta^{y}_{1\text{age}[i]} + \zeta^{y}_{1\text{age:region}[i]} + \eta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
-&(\alpha^{y}_{2} + \beta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]} + \delta^{y}_{2\text{age}[i]} + \zeta^{y}_{2\text{age:region}[i]} + \eta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
-&(\alpha^{y}_{3} + \beta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]} + \delta^{y}_{3\text{age}[i]} + \zeta^{y}_{3\text{age:region}[i]} + \eta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\ \\
-
-x_i &\sim \text{Beta}(\mu^x_i, \phi) \\ 
-\text{logit}(\mu^x_i) &= \alpha^{x}_{0} + \beta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
-\end{align}
-$$
-
-$$
-\begin{align}
-
-\left[\begin{array}{c}
-\beta^y_{0\text{region}} \\ \beta^y_{1\text{region}}\\ 
-\beta^y_{2\text{region}} \\ \beta^y_{3\text{region}} \\
-\beta^x_{0\text{region}} \\ \beta^x_{1\text{region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{region}),
-
-\left[\begin{array}{c}
-\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
-\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\
-\gamma^x_{2\text{country}} \\ \gamma^x_{3\text{country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{country}),
-
-\left[\begin{array}{c}
-\delta^y_{0\text{age}} \\ \delta^y_{1\text{age}} \\ 
-\delta^y_{2\text{age}} \\ \delta^y_{3\text{age}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{age}), \\
-
-\left[\begin{array}{c}
-\zeta^y_{0\text{age:region}} \\ \zeta^y_{1\text{age:region}} \\ 
-\zeta^y_{2\text{age:region}} \\ \zeta^y_{3\text{age:region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{age:region}),
-
-\left[\begin{array}{c}
-\eta^y_{0\text{age:country}} \\ \eta^y_{1\text{age:country}} \\ 
-\eta^y_{2\text{age:country}} \\ \eta^y_{3\text{age:country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{age:country})
-
+y_i &\sim \text{Normal}(\mu^y_i, \sigma^{y2}v_i) \\
+x_i &\sim \text{Normal}(\mu^x_i, \sigma^{x2}) \\ 
+\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{country}[i]} + \gamma^{y}_{0\text{age}[i]} + \delta^{y}_{0\text{age:country}[i]} + \\ 
+&(\alpha^{y}_{1} + \beta^{y}_{1\text{country}[i]} + \gamma^{y}_{1\text{age}[i]} + \delta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
+&(\alpha^{y}_{2} + \beta^{y}_{2\text{country}[i]} + \gamma^{y}_{2\text{age}[i]} + \delta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
+&(\alpha^{y}_{3} + \beta^{y}_{3\text{country}[i]} + \gamma^{y}_{3\text{age}[i]} + \delta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
+\mu^x_i &= \alpha^{x}_{0} + \beta^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{country}[i]})\text{Time}_i \\
+\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
+\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
+\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
 \end{align}
 $$ {#eq-model1}
-
-Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.
-We also fit this same model but using the mobile broadband subscriptions as $x$ ("Model 4").
 
@@
 $$
-\begin{align*}
-y_i &\sim \text{Normal}(\mu_i, \sigma^{2}v_i) \\
+\begin{align}
+y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
+\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\ 
+&(\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
+&(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
+&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
+&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i \\
+&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\
+\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
+\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
+\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
+\end{align}
+$$ {#eq-model2}
 
-\mu_i &= \alpha_{0} + \beta_{0\text{region}[i]} + \gamma_{0\text{country}[i]} + \delta_{0\text{age}[i]} + \zeta_{0\text{age:region}[i]} + \eta_{0\text{age:country}[i]} \\ &(\alpha_{1} + \beta_{1\text{region}[i]} + \gamma_{1\text{country}[i]} + \delta_{1\text{age}[i]} + \zeta_{1\text{age:region}[i]} + \eta_{1\text{age:country}[i]})\text{Time}_i + \\
-&(\alpha_{2} + \beta_{2\text{region}[i]} + \gamma_{2\text{country}[i]} + \delta_{2\text{age}[i]} + \zeta_{2\text{age:region}[i]} + \eta_{2\text{age:country}[i]})\text{Sex}_i + \\
-&(\alpha_{3} + \beta_{3\text{region}[i]} + \gamma_{3\text{country}[i]} + \delta_{3\text{age}[i]} + \zeta_{3\text{age:region}[i]} + \eta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
-&(\alpha_{4} + \beta_{4\text{region}[i]} + \gamma_{4\text{country}[i]} + \delta_{4\text{age}[i]} + \zeta_{4\text{age:region}[i]} + \eta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
-&(\alpha_{5} + \beta_{5\text{region}[i]} + \gamma_{5\text{country}[i]} + \delta_{5\text{age}[i]} + \zeta_{5\text{age:region}[i]} + \eta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\ \\
-
-\left[\begin{array}{c}
-\beta_{0\text{region}} \\ \beta_{1\text{region}} \\ 
-\beta_{2\text{region}} \\ \beta_{3\text{region}} \\
-\beta_{4\text{region}} \\ \beta_{5\text{region}} 
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{region}),
-
-\left[\begin{array}{c}
-\gamma_{0\text{country}} \\ \gamma_{1\text{country}} \\ 
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} \\
-\gamma_{2\text{country}} \\ \gamma_{3\text{country}} 
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{country}),
-
-\left[\begin{array}{c}
-\delta_{0\text{age}} \\ \delta_{1\text{age}} \\ 
-\delta_{2\text{age}} \\ \delta_{3\text{age}} \\
-\delta_{4\text{age}} \\ \delta_{5\text{age}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{age}), \\
-
-\left[\begin{array}{c}
-\zeta_{0\text{age:region}} \\ \zeta_{1\text{age:region}} \\ 
-\zeta_{2\text{age:region}} \\ \zeta_{3\text{age:region}} \\
-\zeta_{4\text{age:region}} \\ \zeta_{5\text{age:region}}
-\end{array}\right] 
-&\sim MVN(
-\mathbf{0},
-\Sigma^\text{age:region}),
-
-\left[\begin{array}{c}
-\eta_{0\text{age:country}} \\ \eta_{1\text{age:country}} \\ 
-\eta_{2\text{age:country}} \\ \eta_{3\text{age:country}} \\
-\eta_{4\text{age:country}} \\ \eta_{5\text{age:country}}
-\end{array}\right] 
-\sim MVN(
-\mathbf{0},
-\Sigma^\text{age:country})
-\end{align*}
-$$ {#eq-model1}
-
-Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion.
-We then also fit this model but using the mobile broadband subscription numbers instead of the internet user proportions ("Model 3").
+Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions).
 
@@
 
-Next, we display the population-level parameters of each model, along with their numberical HMC diagnostics (ESS and Rhat values).
+Next, we display the population-level parameters of each model, along with their numerical HMC diagnostics (ESS and Rhat values).
 
@@
   mutate(outcome = fct_inorder(outcome))
+
+# The files are huge and unwieldy to work with. We create smaller files for each by dropping samples of the age:country interaction random effects. It is then easier to post-process the models.
+dir.create("models-small", FALSE)
+
+replace_chain <- function(x) {
+  x %>%
+    select(
+      -starts_with("r_1"),
+      -starts_with("r_2"),
+      -starts_with("r_3"),
+      -starts_with("z_1"),
+      -starts_with("z_2"),
+      -starts_with("z_3"),
+      -starts_with("r_age:country"),
+      -starts_with("L_")
+    )
+}
+
+replace_chain_all <- function(x) {
+  if (!file.exists(str_glue("models-small/{x}"))) {
+    message(x)
+    out <- readRDS(str_glue("models/{x}"))
+    out$fit@sim$samples <- map(1:4, ~replace_chain(out$fit@sim$samples[[.]]))
+    saveRDS(out, str_glue("models-small/{x}"), compress = FALSE)
+  }
+}
+
+walk(
+  list.files("models"),
+  ~replace_chain_all(.x)
+)
 ```
@@
 
-Rhats should approach 1, and the latter should approach the number of hmc iterations (about 4000).
-We first calculate these posterior summaries for each population level parameter for each outcome and model.
+Rhats should approach 1, and the latter should approach the number of hmc iterations. We first calculate these posterior summaries for each population level parameter for each outcome and model.
 
@@
 parameter_summary <- function(outcome, model) {
-  path <- str_glue("models/brm-{outcome}-{model}.rds")
+  path <- str_glue("models-small/brm-{outcome}-{model}.rds")
   as_draws_df(
@@
 fits_parameters <- tibble(
-  path = list.files("models/", full.names = TRUE)
+  path = list.files("models-small/", pattern = ".rds$", full.names = FALSE)
 ) %>% 
@@
   select(-brm) %>% 
+  mutate(outcome = factor(outcome, levels = oo)) %>% 
+  arrange(outcome) %>% 
   mutate(model = str_extract(model, "[0-9]")) %>% 
@@
 
-### Rhats
+### Scatterplots
 
-Take a look at distributions with worst rhats
+Have the chains converged? Are there divergences?
+
+For each model, we draw a scatterplot matrix of parameters with worst rhats. Browse these figures at `diagnostics/`
 
 ```{r}
-#| eval: false
-x <- readRDS("models/brm-Depression-3.rds")
-rhat(x, pars = variables(x)[1:10])
-bads <- fits_parameters %>% 
-  group_by(outcome, model) %>% 
-  arrange(outcome, model, desc(rhat)) %>% 
-  slice(1:4)
-bads
-
-foo <- function(outcome, model) {
-  bads <- filter(bads, outcome == {{outcome}}, model == {{model}})
-  x <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
+# Function to draw a pairsplot of variables `v` of model in `path` 
+pairsplot <- function(path, v) {
+  if (!file.exists(str_glue("diagnostics/{basename(path)}.png"))) {
+    x <- readRDS(here(path))
     agg_png(
-    str_glue("diagnostics/bads-{outcome}-{model}.png"),
-    width = W, height = W, units = "in", res = 200
+      str_glue("diagnostics/{basename(path)}.png"),
+      width = W*1.2, height = W*1.2, units = "in", res = 160
     )
-  pairs(x$fit, pars = pull(bads, variable))
-  title(sub = str_glue("bads-{outcome}-{model}"))
-  dev.off()
-}
-foo <- memoise(foo, cache = cd)
-fits %>% 
-  crossing(model = 1:4) %>% 
-  mutate(walk2(outcome, model, foo))
-```
-
-### Scatterplots
-
-Browse these figures at `diagnostics/`
-
-```{r}
-#| eval: false
-pairsplot <- function(path) {
-  x <- readRDS(str_glue(here(path)))
-  agg_png(
-    str_glue("diagnostics/{path}.png"),
-    width = W*1.5, height = W*1.5, units = "in", res = 200
-  )
-  pairs(x$fit, pars = variables(x)[1:22])
+    pairs(x$fit, pars = v)
     title(sub = path)
@@
   }
-pairsplot <- memoise(pairsplot, cache = cd)
-list.files("models", full.names = TRUE) %>% 
-  walk(pairsplot)
+}
+
+# Draw pairsplot for 10 worst rhats per model
+fits_parameters %>% 
+  group_by(outcome, model) %>% 
+  arrange(outcome, model, desc(rhat)) %>% 
+  slice(1:10) %>% 
+  ungroup() %>% 
+  group_by(outcome, model) %>% 
+  summarise(v = list(variable)) %>% 
+  mutate(path = str_glue("models-small/brm-{outcome}-{model}.rds")) %>% 
+  ungroup() %>% 
+  {walk2(.$path, .$v, ~pairsplot(.x, .y))}
 ```
@@
 
+Do the models reproduce the observed data?
+
 ```{r ppcheck-density}
-#| eval: false
-#| column: page-right
 #| fig-height: 6
 #| fig-width: 9
-#| fig-cap: "Graphical posterior predictive check by region (Model 1).
-Thin red lines indicate model replicates, whereas the blue lines indicate data; the model is mostly in smooth agreement with data, but has greater discrepancies in some regions (e.g.
-Anglo Depression)."
+#| fig-cap: "Graphical posterior predictive check by region. Thin red lines indicate model replicates, whereas the blue lines indicate data."
 #| label: fig-ppcheck-1
@@
     ndraws = 10,
-    type = "dens_overlay_grouped",
-    group = "region",
+    type = "dens_overlay",
     resp = "val",
@@
 
-cluster_copy(cluster, "pp_check_fun")
-cluster_library(cluster, c("tidyverse", "bayesplot", "brms"))
 pp_checks <- tibble(
@@
 pp_checks %>%
-  filter(model == 1) %>% 
+  slice_sample(prop = .1) %>% 
   ggplot(aes(value, col = is_y, alpha = is_y, group = rep_id)) +
@@
   facet_grid2(
-    outcome ~ group,
-    scales = "free", independent = "x",
+    model~outcome,
+    scales = "free", independent = "y",
     labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
@@
     axis.title = element_blank(),
-    axis.text = element_blank(),
+    axis.text.y = element_blank(),
     axis.ticks = element_blank()

### 2022-06-30 02-results.Rmd
Don't load anything in .Rprofile
wip 2022-06-30

@@
-# Main results
-
-```{r setup}
+# Results
+
+```{r setup, include = FALSE}
 #| cache: false
@@
 library(ggdist)
+library(lme4)
+library(broom.mixed)
 library(memoise)
 library(cachem)
+library(flextable)
 library(posterior)
@@
 library(patchwork)
-library(multidplyr)
+library(bayestestR)
+library(plotly)
 library(tidyverse)
 
-cluster <- new_cluster(3)
-
+# Common options
+source("_common.R")
 cd <- cache_disk("memoise_cache", max_size = Inf)
@@
 )
-
 fits <- tibble(outcome = oo) %>%
@@
 
-We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents?
-To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations.
-In this section, we present results based on the moderated effects.
+Here, we examine the models to answer
+
+1. To what extent have the well-being and mental health outcomes changed over time
+2. To what extent do lagged internet/mobile adoption values predict changes in the outcomes above and beyond the temporal trends
+2b. Variance across country, sex, and age in the above
+3. Correlations between country-level parameters
+
+```{r}
+# Before drawing any plots, we need to extract/compute the relevant parameters from the models.
+We do that here: For each outcome, we get the countries' average changes over time (in the outcome, internet, and mobile) and associations with internet and mobile
+country_post_fun <- function(outcome) {
+
+  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
+  fit2 <- readRDS(str_glue("models-small/brm-{outcome}-2.rds"))
+  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
+  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))
+
+  out_outcome_year <- spread_draws(
+    fit1,
+    b_val_year, r_country__val[country, x] | country
+  ) %>% 
+    filter(x == "year") %>% 
+    ungroup() %>% 
+    rename(World = b_val_year) %>% 
+    mutate(y = "outcome")
+
+  out_internet_year <- spread_draws(
+    fit1,
+    b_internet_year, r_country__internet[country, x] | country
+  ) %>% 
+    filter(x == "year") %>% 
+    ungroup() %>% 
+    rename(World = b_internet_year) %>% 
+    mutate(y = "Internet")
+
+  out_mobile_year <- spread_draws(
+    fit2,
+    b_mobile_year, r_country__mobile[country, x] | country
+  ) %>% 
+    filter(x == "year") %>% 
+    ungroup() %>% 
+    rename(World = b_mobile_year) %>% 
+    mutate(y = "Mobile")
+
+  out_outcome_internet <- spread_draws(
+    fit3,
+    b_i1_cw, r_country[country, x] | country
+  ) %>% 
+    filter(x == "i1_cw") %>% 
+    ungroup() %>% 
+    rename(World = b_i1_cw) %>% 
+    mutate(y = "outcome")
+
+  out_outcome_mobile <- spread_draws(
+    fit4,
+    b_m1_cw, r_country[country, x] | country
+  ) %>% 
+    filter(x == "m1_cw") %>% 
+    ungroup() %>% 
+    rename(World = b_m1_cw) %>% 
+    mutate(y = "outcome")
+
+  out <- bind_rows(
+    out_outcome_year, 
+    out_internet_year,
+    out_mobile_year,
+    out_outcome_internet,
+    out_outcome_mobile
+  ) %>%  
+    select(x, y, everything(), -c(.chain, .iteration, .draw)) %>% 
+    mutate(across(-c(x, y, World), ~. + World)) %>% 
+    rename_with(~str_replace_all(., "\\.(?!\\.)", " ")) %>% 
+    mutate(
+      x = factor(
+        x, 
+        levels = c("year", "i1_cw", "m1_cw"),
+        labels = c("Time", "Internet", "Mobile")
+        )
+    )
+
+  out 
+}
+country_post_fun <- memoise(country_post_fun, cache = cd)
+country_post <- fits %>% 
+  mutate(
+    samples = map(outcome, country_post_fun),
+    summary = map(
+      samples, 
+      ~.x %>% 
+        group_by(x, y) %>% 
+        summarise_draws(
+          mean, 
+          ~quantile2(., probs = c(.025, .975)),
+          pd = ~pd(as.numeric(.))
+        ) %>% 
+        rename(country = variable)
+    )
+  )
+```
 
@@
 
-This figure shows the time courses of each of the six outcome variables.
-Panels by outcome (rows) and region (columns; including World).
-Each panel shows the time course by all ages and sex, and on average across ages.
-So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.
-
-Calculate contrast by sex at the world level.
-
-```{r}
-#' Get contrast at average level (no random effects)
-#'
-#' @param outcome Life_satisfaction etc.
-#' @param h Strings representing hypotheses (brm::hypothesis())
-#' @param model 1, 2, 3, or 4
-get_hyp_avg <- function(outcome, h, model) {
-  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
-  hypothesis(fit, h)$hypothesis
+::: {.panel-tabset .column-body-outset-right}
+
+### Countries
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+country_year_plot <- country_coefs %>% 
+  filter(x == "Time", y == "outcome") %>% 
+  # Arrange each panel
+  group_by(outcome) %>% 
+  arrange(outcome, mean) %>% 
+  mutate(n = 1:n(), y = factor(n)) %>% 
+  ungroup() %>% 
+  mutate(
+    level = country != "World", 
+    mh = outcome %in% oo[4:6],
+    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
+  ) %>% 
+  ggplot(aes(mean, y, color = level)) +
+  scale_size_manual(values = c(1.25, 0.25)) +
+  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
+  scale_y_discrete(expand = expansion(.01)) +
+  scale_x_continuous(
+    "Estimated change per decade",
+    breaks = extended_breaks(),
+    expand = expansion(.01),
+    labels = ~percent(./100)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_segment(
+    aes(
+      x = q2.5, xend = q97.5, yend = y, 
+      text = text
+    ),
+    size = .15
+  ) +
+  # Put world in top layer
+  geom_point(
+    data = . %>% filter(country == "World"), 
+    aes(text = text, size = level)
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  labs(y = "Country") +
+  theme(
+    legend.position = "none",
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  )
+
+country_year_plot
+```
+
+### Countries interactive
+
+```{r out.height = 860}
+gp <- ggplotly(country_year_plot, tooltip = "text")
+gp %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30),
+    width = 970,
+    height = 830
+  )
+```
+
+### Age and sex
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+sex_year_sum <- function(fit) {
+  spread_draws(
+    fit, 
+    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
+  ) %>% 
+    transmute(
+      female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
+      male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
+    ) %>% 
+    pivot_longer(-age) %>% 
+    group_by(age, name) %>% 
+    mean_qi()
 }
-get_hyp_avg <- memoise(get_hyp_avg, cache = cd)
-
-h_timecourses <- c(
-  Slope_Male = "val_year + val_year:sex1 * -1 = 0",
-  Slope_Female = "val_year + val_year:sex1 * 1 = 0"
-)
-
-cluster_library(cluster, c("brms", "purrr", "stringr"))
-cluster_copy(cluster, c("get_hyp_avg", "h_timecourses"))
-
-timecourses_world_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_avg(.x, h = h_timecourses, model = "1")
-    )
-  ) %>% 
-  collect()
-```
-
-And then for each sex*age at the world level.
-
-```{r}
-#' Get contrast for each age
-#'
-#' @param outcome Life_satisfaction etc
-#' @param h brms hypothesis
-#' @param model 1,2,3, or 4
-get_hyp_age <- function(outcome, h, model) {
-  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
-  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
-}
-get_hyp_age <- memoise(get_hyp_age, cache = cd)
-cluster_copy(cluster, "get_hyp_age")
-
-timecourses_world_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_age(.x, h = h_timecourses, model = "1")
-    )
-  ) %>% 
-  collect()
-```
-
-Combine these to one and plot
-
-```{r}
-bind_rows(
-  timecourses_world_age %>% 
-    unnest(out),
-  timecourses_world_average %>% 
-    unnest(out) %>% 
-    mutate(Group = "Average")
-) %>% 
-  ungroup() %>% 
-  mutate(Group = fct_relevel(Group, "Average", "10 to 14")) %>% 
-  select(outcome:CI.Upper) %>% 
-  separate(Hypothesis, c("Parameter", "Sex")) %>% 
-  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
-  ggplot(aes(Group, Estimate, ymin = CI.Lower, ymax = CI.Upper, fill = Sex, col = Sex, group = Sex)) +
-  scale_color_bright() +
-  scale_fill_bright() +
-  scale_shape_manual(values = c(21, 19), guide = NULL) +
-  scale_y_continuous(
+sex_year_sum <- memoise(sex_year_sum, cache = cd)
+
+sex_year_coefs <- fits %>% 
+  mutate(
+    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-1.rds"))),
+    sex_year = map(fit, sex_year_sum)
+  ) %>% 
+  select(-fit) %>% 
+  unnest(sex_year)
+
+sex_year_plot <- sex_year_coefs %>% 
+  mutate(Sex = str_to_title(name)) %>% 
+  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
+  ggplot(aes(value, age, col = Sex)) +
+  scale_color_vibrant() +
+  scale_x_continuous(
+    "Estimated change per decade",
     breaks = extended_breaks(),
-    # Effect of 10%
-    labels = ~percent(./1000), 
-    expand = expansion(.4)
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_ribbon(
-    data = . %>% filter(Group != "Average"),
-    aes(), 
-    alpha = .2, col = NA
-  ) +
-  geom_line(
-    data = . %>% filter(Group != "Average"),
-    aes(group = Sex),
-    size = .6
-  ) +
-  geom_pointrange(
-    data = . %>% filter(Group == "Average"),
-    position = position_dodge(.75),
-    size = .4, fatten = 2.5
-  ) +
-  facet_wrap(
-    "outcome", scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))) +
-  theme(
-    axis.text.x = element_text(angle = 90),
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-```
-
-And for all regions too.
-
-First we calculate the contrast by sex for each region.
-
-```{r}
-get_region_timecourse_avg <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex) %>% 
-    # Note 1 for 10 year change
-    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (year*sex | region),
-      resp = "val",
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration, -val) %>% 
-    pivot_wider(names_from = year, values_from = .epred) %>% 
-    mutate(delta = `1` - `0`) %>% 
-    select(region, sex, .draw, delta) %>% 
-    group_by(region, sex) %>% 
-    mean_qi(delta)
-}
-get_region_timecourse_avg <- memoise(
-  get_region_timecourse_avg, cache = cd
-)
-
-cluster_copy(cluster, "get_region_timecourse_avg")
-cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
-timecourses_region_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_region_timecourse_avg)) %>% 
-  collect()
-```
-
-Then we calculate the contrasts for each sex*age for each region.
-
-```{r}
-get_region_timecourse_age <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex, age) %>% 
-    # Note 1 for decade change
-    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (year*sex | age) + 
-        (year*sex | region) + (year*sex | age:region),
-      resp = "val",
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration, -val) %>% 
-    pivot_wider(names_from = year, values_from = .epred) %>% 
-    mutate(delta = `1` - `0`) %>% 
-    select(region, sex, age, .draw, delta) %>% 
-    group_by(region, sex, age) %>% 
-    mean_qi(delta)
-}
-get_region_timecourse_age <- memoise(
-  get_region_timecourse_age, cache = cd
-)
-
-cluster_copy(cluster, "get_region_timecourse_age")
-timecourses_region_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_region_timecourse_age)) %>% 
-  collect()
-```
-
-Combine these with world level estimates and plot
-
-```{r}
-timecourses_world <- bind_rows(
-  timecourses_world_age %>% 
-    unnest(out),
-  timecourses_world_average %>% 
-    unnest(out) %>% 
-    mutate(Group = "Average")
-) %>% 
-  ungroup() %>% 
-  separate(Hypothesis, c("Parameter", "sex")) %>% 
-  select(
-    outcome,
-    age = Group,
-    sex,
-    delta = Estimate,
-    .lower = CI.Lower,
-    .upper = CI.Upper,
-  ) %>% 
-  mutate(region = "World")
-
-x <- sort(unique(timecourses_world$age))
-x2 <- as.character(x)
-x2[str_detect(x2, "5 ")] <- ""
-
-bind_rows(
-  timecourses_region_age %>% 
-    unnest(out),
-  timecourses_region_average %>% 
-    unnest(out) %>% 
-    mutate(age = "Average")
-) %>% 
-  ungroup() %>% 
-  bind_rows(timecourses_world) %>% 
-  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
-  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
-  arrange(sex) %>% 
-  select(outcome:.upper) %>% 
-  mutate(s = sign(.lower) == sign(.upper)) %>% 
-  ggplot(
-    aes(
-      age, delta, 
-      ymin = .lower, ymax = .upper, 
-      fill = sex, col = sex, group = sex
-    )
-  ) +
-  scale_color_bright() +
-  scale_fill_bright() +
-  scale_shape_manual(values = c(21, 19), guide = NULL) +
-  scale_x_discrete(
-    breaks = x,
-    labels = x2,
-    expand = expansion(c(0.02, 0.05))
-  ) +
-  scale_y_continuous(
-    "Estimated linear change per decade",
-    breaks = extended_breaks(),
-    labels = ~percent(./100),
-    expand = expansion(.1)
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_ribbon(
-    data = . %>% filter(age != "Average"),
-    aes(), 
-    alpha = .15, col = NA
-  ) +
-  geom_line(
-    data = . %>% filter(age != "Average"),
-    aes(group = sex),
-    size = .4
-  ) +
-  geom_pointrange(
-    data = . %>% filter(age == "Average"),
-    position = position_dodge(.9),
-    size = .3, fatten = 0.1
-  ) +
-  facet_grid(
-    outcome~region, scales = "free_y", 
-    labeller = as_labeller(~str_replace(., "_", "\n"))) +
-  theme(
-    axis.text.x = element_text(angle = 90, vjust = 0.5),
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-agg_png(
-  "figures/Fig-timecourses-demographics.png", 
-  width = W, height = W*0.6, units = "in", res = 400
-)
-last_plot()
-dev.off()
-```
-
-## Associations
-
-### Internet
-
-Calculate contrast by sex at the world level.
-
-```{r}
-h_internet_associations <- c(
-  Slope_Male = "i1_cw + i1_cw:sex1 * -1 = 0",
-  Slope_Female = "i1_cw + i1_cw:sex1 * 1 = 0"
-)
-cluster_copy(cluster, "h_internet_associations")
-
-internet_associations_world_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_avg(.x, h = h_internet_associations, model = "2")
-    )
-  ) %>% 
-  collect()
-```
-
-And then for each sex*age at the world level.
-
-```{r}
-internet_associations_world_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_age(.x, h = h_internet_associations, model = "2")
-    )
-  ) %>% 
-  collect()
-```
-
-And for all regions too.
-
-First we calculate the contrast by sex for each region.
-
-```{r}
-get_internet_region_association_avg <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex) %>% 
-    # Note .1 for 10% change
-    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (i1_cw*sex | region),
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration) %>% 
-    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
-    mutate(delta = `0.1` - `0`) %>% 
-    select(region, sex, .draw, delta) %>% 
-    group_by(region, sex) %>% 
-    mean_qi(delta)
-}
-get_internet_region_association_avg <- memoise(
-  get_internet_region_association_avg, cache = cd
-)
-
-cluster_copy(cluster, "get_internet_region_association_avg")
-cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
-internet_associations_region_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_internet_region_association_avg)) %>% 
-  collect()
-```
-
-#### Demographics
-
-Then we calculate the contrasts for each sex*age for each region.
-
-```{r}
- get_internet_region_association_age <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex, age) %>% 
-    # Note .1 for 10% change
-    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (i1_cw*sex | age) + 
-        (i1_cw*sex | region) + (i1_cw*sex | age:region),
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration) %>% 
-    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
-    mutate(delta = `0.1` - `0`) %>% 
-    select(region, sex, age, .draw, delta) %>% 
-    group_by(region, sex, age) %>% 
-    mean_qi(delta)
-}
-get_internet_region_association_age <- memoise(
-  get_internet_region_association_age, cache = cd
-)
-
-cluster_copy(cluster, "get_internet_region_association_age")
-internet_associations_region_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_internet_region_association_age)) %>% 
-  collect()
-```
-
-Combine these with world level estimates and plot
-
-```{r}
-internet_associations_world <- bind_rows(
-  internet_associations_world_age %>% 
-    unnest(out),
-  internet_associations_world_average %>% 
-    unnest(out) %>% 
-    mutate(Group = "Average")
-) %>% 
-  ungroup() %>% 
-  separate(Hypothesis, c("Parameter", "sex")) %>% 
-  mutate(
-    # Convert to effect of 10% change in internet/mobile
-    delta = Estimate/10,
-    .lower = CI.Lower/10,
-    .upper = CI.Upper/10
-  ) %>% 
-  select(
-    outcome,
-    age = Group,
-    sex,
-    delta,
-    .lower,
-    .upper,
-  ) %>% 
-  mutate(region = "World")
-
-internet_associations <- bind_rows(
-  internet_associations_region_age %>% 
-    unnest(out),
-  internet_associations_region_average %>% 
-    unnest(out) %>% 
-    mutate(age = "Average")
-) %>% 
-  ungroup() %>% 
-  bind_rows(internet_associations_world) %>% 
-  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
-  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
-  arrange(sex) %>% 
-  select(outcome:.upper) %>% 
-  mutate(s = sign(.lower) == sign(.upper))
-internet_associations %>%   
-  ggplot(aes(
-    age, delta, 
-    ymin = .lower, ymax = .upper, 
-    fill = sex, col = sex, group = sex)
-  ) +
-  scale_color_bright() +
-  scale_fill_bright() +
-  scale_shape_manual(values = c(21, 19), guide = NULL) +
-  scale_x_discrete(
-    breaks = x,
-    labels = x2,
-    expand = expansion(c(0.02, 0.06))
-  ) +
-  scale_y_continuous(
-    "Conditional effect of 10% increase\nin per capita internet users",
-    breaks = extended_breaks(),
-    labels = ~percent(./100),
-    expand = expansion(c(.25, .25))
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_ribbon(
-    data = . %>% filter(age != "Average"),
-    aes(), 
-    alpha = .15, col = NA
-  ) +
-  geom_line(
-    data = . %>% filter(age != "Average"),
-    aes(group = sex),
-    size = .4
-  ) +
-  geom_pointrange(
-    data = . %>% filter(age == "Average"),
-    position = position_dodge(.9),
-    size = .2, fatten = 1.25
-  ) +
-  facet_grid(
-    outcome~region, scales = "free_y", drop = FALSE,
-    labeller = as_labeller(~str_replace(., "_", "\n"))) +
-  theme(
-    axis.text.x = element_text(angle = 90, vjust = 0.5),
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-agg_png(
-  "figures/Fig-associations-internet-demographics.png", 
-  width = W, height = W*0.6, units = "in", res = 400
-)
-last_plot()
-dev.off()
-```
-
-#### Compare ages
-
-We then compared, for selfharm, the youngest age group's association to all other age group's associations.
-
-```{r}
-fit_selfharm <- readRDS("models/brm-Selfharm-3.rds")
-h <- hypothesis(fit_selfharm, "m1_cw = 0", scope = "coef", group = "age")
-s <- tibble(h$samples)
-hypothesis(s, paste0("H1 > H", 2:9))$hypothesis %>% 
-  as.data.frame() %>% 
-  kbl(digits = 4) %>% 
-  kable_custom()
-```
-
-#### Forest plot
-
-```{r}
-library(ggstance)
-internet_associations %>% 
-  filter(age == "Average") %>% 
-  ggplot(aes(delta, region, col = sex)) +
+    expand = expansion(.1),
+    labels = ~percent(./100)
+  ) +
   geom_vline(xintercept = 0, lty = 2, size = .2) +
@@
     aes(xmin = .lower, xmax = .upper),
-    position = position_dodge2v(.3)
-  ) +
-  facet_wrap("outcome", scales = "free_x", ncol = 3)
-```
-
-### Mobile
-
-This figure shows mobile --> outcome associations.
-Panels by outcome (rows) and region (columns; including World).
-Each panel shows the association by all ages and sex, and on average across ages.
-So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.
-
-Calculate contrast by sex at the world level.
-
-```{r}
-get_hyp_avg <- function(outcome, h, model) {
-  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
-  hypothesis(fit, h)$hypothesis
+    position = position_dodge2v(.35),
+    size = .25, fatten = 1.5
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(
+    axis.title.y = element_blank()
+  )
+sex_year_plot
+```
+
+#### Table
+
+```{r}
+country_year_coefs %>% 
+  filter(country == "World") %>% 
+  mutate(
+    across(
+      c(mean, q2.5, q97.5), ~percent(./100, .01)
+    ),
+    pd = percent(pd, .1)
+  ) %>% 
+  kbl(caption = "Average changes per decade") %>% 
+  kable_custom()
+```
+
+:::
+
+### Average trends
+
+```{r}
+country_year_coefs %>% 
+  filter(country == "World") %>% 
+  transmute(
+    Outcome = str_replace(outcome, "_", " "),
+    Trend = str_glue("{number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}]")
+  ) %>% 
+  kbl(caption = "Estimated world average changes per decade") %>% 
+  kable_custom()
+```
+
+## Associations
+
+### Internet
+
+::: {.panel-tabset}
+
+#### Countries
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+country_internet_plot <- country_coefs %>% 
+  filter(x == "Internet", y == "outcome") %>% 
+  # Arrange each panel
+  group_by(outcome) %>% 
+  arrange(outcome, mean) %>% 
+  mutate(n = 1:n(), y = factor(n)) %>% 
+  ungroup() %>% 
+  mutate(
+    level = country != "World", 
+    mh = outcome %in% oo[4:6],
+    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
+  ) %>% 
+  # mutate(star = sign(.lower) == sign(.upper)) %>% 
+  ggplot(aes(mean, y, color = level)) +
+  scale_size_manual(values = c(1.25, 0.25)) +
+  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
+  scale_y_discrete(expand = expansion(.01)) +
+  # Association with 10% change
+  scale_x_continuous(
+    "Estimated association with 10% increase in\nper capita internet users",
+    breaks = extended_breaks(),
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_segment(
+    aes(
+      x = q2.5, xend = q97.5, yend = y, 
+      text = text
+    ),
+    size = .15
+  ) +
+  geom_point(aes(text = text, size = level)) +
+  # Put world in top layer
+  geom_point(
+    data = . %>% filter(country == "World"), 
+    aes(text = text, size = level)
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  labs(y = "Country") +
+  theme(
+    legend.position = "none",
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  )
+country_internet_plot
+```
+
+#### Countries interactive
+
+```{r out.height = 860}
+gp <- ggplotly(country_internet_plot, tooltip = "text")
+gp %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30),
+    width = 970,
+    height = 830
+  )
+```
+
+#### Age and sex
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+sex_internet_sum <- function(fit) {
+  spread_draws(
+    fit, 
+    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
+  ) %>% 
+    transmute(
+      female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
+      male = b_i1_cw + year + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
+    ) %>% 
+    pivot_longer(-age) %>% 
+    group_by(age, name) %>% 
+    mean_qi()
 }
-get_hyp_avg <- memoise(get_hyp_avg, cache = cd)
-
-h_mobile_associations <- c(
-  # Intercept_Male = "Intercept + sex1 * -1 = 0",
-  # Intercept_Female = "Intercept + sex1 * 1 = 0",
-  Slope_Male = "m1_cw + m1_cw:sex1 * -1 = 0",
-  Slope_Female = "m1_cw + m1_cw:sex1 * 1 = 0"
-)
-
-cluster_library(cluster, c("brms", "purrr", "stringr"))
-cluster_copy(cluster, c("get_hyp_avg", "h_mobile_associations"))
-
-mobile_associations_world_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_avg(.x, h = h_mobile_associations, model = "3")
-    )
-  ) %>% 
-  collect()
-```
-
-And then for each sex*age at the world level.
-
-```{r}
-get_hyp_age <- function(outcome, h, model) {
-  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
-  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
-}
-get_hyp_age <- memoise(get_hyp_age, cache = cd)
-cluster_copy(cluster, "get_hyp_age")
-
-mobile_associations_world_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~get_hyp_age(.x, h = h_mobile_associations, model = "3")
-    )
-  ) %>% 
-  collect()
-```
-
-Combine these to one and plot
-
-```{r}
-bind_rows(
-  mobile_associations_world_age %>% 
-    unnest(out),
-  mobile_associations_world_average %>% 
-    unnest(out) %>% 
-    mutate(Group = "Average")
-) %>% 
-  ungroup() %>% 
-  mutate(Group = fct_relevel(Group, "Average", "10 to 14")) %>% 
-  select(outcome:CI.Upper) %>% 
-  separate(Hypothesis, c("Parameter", "Sex")) %>% 
-  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
-  ggplot(aes(Group, Estimate, ymin = CI.Lower, ymax = CI.Upper, fill = Sex, col = Sex, group = Sex)) +
-  scale_color_bright() +
-  scale_fill_bright() +
-  scale_shape_manual(values = c(21, 19), guide = NULL) +
-  scale_y_continuous(
+sex_internet_sum <- memoise(sex_internet_sum, cache = cd)
+
+sex_internet_coefs <- fits %>% 
+  mutate(
+    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-3.rds"))),
+    sex_internet = map(fit, sex_internet_sum)
+  ) %>% 
+  select(-fit) %>% 
+  unnest(sex_internet)
+
+sex_internet_plot <- sex_internet_coefs %>% 
+  mutate(Sex = str_to_title(name)) %>% 
+  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
+  ggplot(aes(value, age, col = Sex)) +
+  scale_color_vibrant() +
+  scale_x_continuous(
+    "Estimated association with 10% increase in\nper capita internet users",
     breaks = extended_breaks(),
-    # Effect of 10%
-    labels = ~percent(./1000), 
-    expand = expansion(.4)
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_ribbon(
-    data = . %>% filter(Group != "Average"),
-    aes(), 
-    alpha = .2, col = NA
-  ) +
-  geom_line(
-    data = . %>% filter(Group != "Average"),
-    aes(group = Sex),
-    size = .6
-  ) +
-  geom_pointrange(
-    data = . %>% filter(Group == "Average"),
-    position = position_dodge(.75),
-    size = .4, fatten = 2.5
-  ) +
-  facet_wrap(
-    "outcome", scales = "free_y", nrow = 2,
-    labeller = as_labeller(~str_replace(., "_", " "))) +
-  theme(
-    axis.text.x = element_text(angle = 90),
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-```
-
-And for all regions too.
-
-First we calculate the contrast by sex for each region.
-
-```{r}
-get_region_association_avg <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex) %>% 
-    # Note .1 for 10% change
-    crossing(m1_cw = c(0, .1), se = 0, year = 0, val = 1) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (m1_cw*sex | region),
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration, -val) %>% 
-    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
-    mutate(delta = `0.1` - `0`) %>% 
-    select(region, sex, .draw, delta) %>% 
-    group_by(region, sex) %>% 
-    mean_qi(delta)
-}
-get_region_association_avg <- memoise(
-  get_region_association_avg, cache = cd
-)
-
-cluster_copy(cluster, "get_region_association_avg")
-cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
-mobile_associations_region_average <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_region_association_avg)) %>% 
-  collect()
-```
-
-Then we calculate the contrasts for each sex*age for each region.
-
-```{r}
-get_region_association_age <- function(outcome) {
-  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
-  tmp <- x$data %>% 
-    distinct(region, sex, age) %>% 
-    # Note .1 for 10% change
-    crossing(m1_cw = c(0, .1), se = 0, year = 0, val = 1) %>% 
-    add_epred_draws(
-      x,
-      re_formula = ~ (m1_cw*sex | age) + 
-        (m1_cw*sex | region) + (m1_cw*sex | age:region),
-      ndraws = 1000
-    ) %>% 
-    ungroup()
-  tmp %>% 
-    select(-.row, -se, -.chain, -.iteration, -val) %>% 
-    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
-    mutate(delta = `0.1` - `0`) %>% 
-    select(region, sex, age, .draw, delta) %>% 
-    group_by(region, sex, age) %>% 
-    mean_qi(delta)
-}
-get_region_association_age <- memoise(
-  get_region_association_age, cache = cd
-)
-
-cluster_library(cluster, c("dplyr", "tidyr", "tidybayes", "purrr"))
-cluster_copy(cluster, "get_region_association_age")
-mobile_associations_region_age <- fits %>% 
-  group_by(outcome) %>% 
-  partition(cluster) %>% 
-  mutate(out = map(outcome, get_region_association_age)) %>% 
-  collect()
-```
-
-Combine these with world level estimates and plot
-
-```{r}
-mobile_associations_world <- bind_rows(
-  mobile_associations_world_age %>% 
-    unnest(out),
-  mobile_associations_world_average %>% 
-    unnest(out) %>% 
-    mutate(Group = "Average")
-) %>% 
-  ungroup() %>% 
-  separate(Hypothesis, c("Parameter", "sex")) %>% 
-  mutate(
-    # Convert to effect of 10% change in internet/mobile
-    delta = Estimate/10,
-    .lower = CI.Lower/10,
-    .upper = CI.Upper/10
-  ) %>% 
-  select(
-    outcome,
-    age = Group,
-    sex,
-    delta,
-    .lower,
-    .upper,
-  ) %>% 
-  mutate(region = "World")
-
-mobile_associations <- bind_rows(
-  mobile_associations_region_age %>% 
-    unnest(out),
-  mobile_associations_region_average %>% 
-    unnest(out) %>% 
-    mutate(age = "Average")
-) %>% 
-  ungroup() %>% 
-  bind_rows(mobile_associations_world) %>% 
-  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
-  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
-  arrange(sex) %>% 
-  select(outcome:.upper) %>% 
-  mutate(s = sign(.lower) == sign(.upper))
-mobile_associations %>%   
-  ggplot(
-    aes(
-      age, delta, 
-      ymin = .lower, ymax = .upper, 
-      fill = sex, col = sex, group = sex
-    )
-  ) +
-  scale_color_bright() +
-  scale_fill_bright() +
-  scale_shape_manual(values = c(21, 19), guide = NULL) +
-  scale_x_discrete(
-    breaks = x,
-    labels = x2,
-    expand = expansion(c(0.02, 0.06))
-  ) +
-  scale_y_continuous(
-    "Conditional effect of 10% increase\nin per capita mobile broadband subscriptions",
-    breaks = extended_breaks(),
-    labels = ~percent(./100),
-    expand = expansion(.4)
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_ribbon(
-    data = . %>% filter(age != "Average"),
-    aes(), 
-    alpha = .15, col = NA
-  ) +
-  geom_line(
-    data = . %>% filter(age != "Average"),
-    aes(group = sex),
-    size = .4
-  ) +
-  geom_pointrange(
-    data = . %>% filter(age == "Average"),
-    position = position_dodge(.9),
-    size = .2, fatten = 1.25
-  ) +
-  facet_grid(
-    outcome~region, scales = "free_y", 
-    labeller = as_labeller(~str_replace(., "_", "\n"))) +
-  theme(
-    axis.text.x = element_text(angle = 90, vjust = 0.5),
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-agg_png(
-  "figures/Fig-associations-mobile-demographics.png", 
-  width = W, height = W*0.6, units = "in", res = 400
-)
-last_plot()
-dev.off()
-```
-
-#### Forest plot
-
-```{r}
-mobile_associations %>% 
-  filter(age == "Average") %>% 
-  ggplot(aes(delta, region, col = sex)) +
+    labels = ~percent(./1000)
+  ) +
   geom_vline(xintercept = 0, lty = 2, size = .2) +
@@
     aes(xmin = .lower, xmax = .upper),
-    position = position_dodge2v(.3)
-  ) +
-  facet_wrap("outcome", scales = "free_x", ncol = 3)
-```
+    position = position_dodge2v(.35),
+    size = .25, fatten = 1.5
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(
+    axis.title.y = element_blank()
+  )
+sex_internet_plot
+```
+
+#### Table
+
+```{r}
+country_internet_coefs %>% 
+  filter(country == "World") %>% 
+  mutate(
+    across(
+      c(mean, q2.5, q97.5), ~percent(./1000, .001)
+    )
+  ) %>% 
+  kbl(caption = "Estimated world associations with 10% increase in internet adoption") %>% 
+  kable_custom()
+```
+
+:::
+
+### Mobile
+
+::: {.panel-tabset}
+
+#### Countries
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+country_mobile_plot <- country_coefs %>% 
+  filter(x == "Mobile", y == "outcome") %>% 
+  # Arrange each panel
+  group_by(outcome) %>% 
+  arrange(outcome, mean) %>% 
+  mutate(n = 1:n(), y = factor(n)) %>% 
+  ungroup() %>% 
+  mutate(
+    level = country != "World", 
+    mh = outcome %in% oo[4:6],
+    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
+  ) %>% 
+  # mutate(star = sign(.lower) == sign(.upper)) %>% 
+  ggplot(aes(mean, y, color = level)) +
+  scale_size_manual(values = c(1.25, 0.25)) +
+  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
+  scale_y_discrete(expand = expansion(.01)) +
+  # Association with 10% change
+  scale_x_continuous(
+    "Estimated association with 10% increase in\nper capita mobile broadband subscriptions",
+    breaks = extended_breaks(),
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_segment(
+    aes(
+      x = q2.5, xend = q97.5, yend = y, 
+      text = text
+    ),
+    size = .15
+  ) +
+  geom_point(aes(text = text, size = level)) +
+  # Put world in top layer
+  geom_point(
+    data = . %>% filter(country == "World"), 
+    aes(text = text, size = level)
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  labs(y = "Country") +
+  theme(
+    legend.position = "none",
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  )
+country_mobile_plot
+```
+
+#### Countries interactive
+
+```{r out.height = 860}
+gp <- ggplotly(country_mobile_plot, tooltip = "text")
+gp %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30),
+    width = 970,
+    height = 830
+  )
+```
+
+#### Age and sex
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+sex_mobile_sum <- function(fit) {
+  spread_draws(
+    fit, 
+    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
+  ) %>% 
+    transmute(
+      female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
+      male = b_m1_cw + year + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
+    ) %>% 
+    pivot_longer(-age) %>% 
+    group_by(age, name) %>% 
+    mean_qi()
+}
+sex_mobile_sum <- memoise(sex_mobile_sum, cache = cd)
+
+sex_mobile_coefs <- fits %>% 
+  mutate(
+    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-4.rds"))),
+    sex_mobile = map(fit, sex_mobile_sum)
+  ) %>% 
+  select(-fit) %>% 
+  unnest(sex_mobile)
+
+sex_mobile_plot <- sex_mobile_coefs %>% 
+  mutate(Sex = str_to_title(name)) %>% 
+  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
+  ggplot(aes(value, age, col = Sex)) +
+  scale_color_vibrant() +
+  scale_x_continuous(
+    "Estimated association with 10% increase in\nper capita mobile broadband subscriptions",
+    breaks = extended_breaks(),
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_pointrangeh(
+    aes(xmin = .lower, xmax = .upper),
+    position = position_dodge2v(.35),
+    size = .25, fatten = 1.5
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(
+    axis.title.y = element_blank()
+  )
+sex_mobile_plot
+```
+
+#### Table
+
+```{r}
+country_mobile_coefs %>% 
+  filter(country == "World") %>% 
+  mutate(
+    across(
+      c(mean, q2.5, q97.5), ~percent(./100, .01)
+    )
+  ) %>% 
+  kbl(caption = "Estimated world associations with 10% increase in mobile internet subscriptions") %>% 
+  kable_custom()
+```
+
+:::
+
+## Figure 2
+
+For this one, we rescale the outcome~internet and outcome~mobile associations to be in units of decade-equivalent changes of internet and mobile.
+
+```{r}
+# There is a different scaling factor for each outcome,
+# even though they used the same internet/mobile values. That's because 
+# different countries were included by outcome, and its then most faithful
+# to the data to keep these separate by outcome.
+scaling_factors <- country_post %>% 
+  select(-samples) %>% 
+  unnest(summary) %>% 
+  filter(x == "Time", y != "outcome") %>% 
+  select(outcome, y, country, scaling = mean)
+
+country_coefs_scaled <- country_post %>% 
+  select(-samples) %>% 
+  unnest(summary) %>%
+  filter(y == "outcome") %>% 
+  select(-y) %>% 
+  # Get internet-decade changes
+  left_join(scaling_factors, by = c("x" = "y", "outcome", "country")) %>%
+  mutate(scaling = if_else(x == "Time", 1, scaling)) %>% 
+  # Scale associations
+  mutate(across(c(mean, q2.5, q97.5), ~ . * scaling)) %>% 
+  # Arrange panels
+  mutate(x = factor(x, levels = c("Time", "Internet", "Mobile")))
+
+# Arrange points within panels such that the order of countries is same in the rows of each column, running from smallest time change to greatest time change.
+This is a rudimentary way to show correlation between the two.
+tmp <- country_coefs_scaled %>% 
+  filter(x == "Time", country != "World") %>% 
+  arrange(mean) %>% 
+  group_by(outcome) %>% 
+  mutate(x_order = 1:n()) %>% 
+  select(outcome, country, x_order) %>% 
+  ungroup()
+
+p_country <- country_coefs_scaled %>% 
+  left_join(tmp) %>% 
+  mutate(
+    sig = sign(q2.5) == sign(q97.5),
+    color = case_when(
+      !sig ~ "c",
+      sig & sign(mean) == -1 ~ "b",
+      sig & sign(mean) == 1 ~ "a"
+    )
+  ) %>%
+  drop_na(mean) %>% 
+  ggplot(aes(x_order, mean, col = color)) +
+  scale_color_brewer(palette = "Dark2") +
+  scale_x_continuous("Country") +
+  scale_y_continuous(
+    "Estimated linear association (%)"
+  ) +
+  geom_hline(yintercept = 0, lty = 2, size = .2) +
+  geom_linerange(
+    data = . %>% filter(country != "World"),
+    size = .15,
+    aes(ymin = q2.5, ymax = q97.5)
+  ) +
+  geom_linerange(
+    data = . %>% filter(country == "World") %>% mutate(x_order = -10L),
+    size = .3, 
+    aes(ymin = q2.5, ymax = q97.5)
+  ) +
+  geom_point(
+    data = . %>% filter(country != "World"),
+    size = .2
+  ) +
+  geom_point(
+    data = . %>% filter(country == "World") %>% mutate(x_order = -10L),
+    size = .75
+  ) +
+  facet_grid2(
+    x~outcome, 
+    scales = "free",
+    independent = "all",
+    labeller = labeller(
+      .cols = as_labeller(~str_replace(., "_", " "))
+    )
+  ) +
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "none"
+  )
+p_country
+agg_png(
+  "figures/SCA-countries.png",
+  width = W, height = W*0.5, units = "in", res = 300
+)
+p_country
+dev.off()
+```
+
+```{r}
+country_coefs_scaled %>% 
+  filter(country != "World") %>% 
+  drop_na(mean) %>% 
+  transmute(
+    Outcome = fct_inorder(str_replace(outcome, "_", " ")),
+    Predictor = x,
+    country, mean
+  ) %>% 
+  arrange(Outcome, Predictor, desc(mean)) %>% 
+  group_by(Predictor, Outcome) %>% 
+  do(rbind(head(., n = 3), tail(., n = 3))) %>% 
+  transmute(
+    country = str_glue("{country} ({number(mean, .1)})")
+  ) %>% 
+  mutate(position = c(str_c("Top ", 1:3), str_c("Bottom ", rev(1:3)))) %>% 
+  pivot_wider(names_from = position, values_from = country) %>% 
+  flextable() %>% 
+  flextable::set_caption("Top and bottom 3 countries for each parameter")
+```
+
+```{r}
+country_coefs_scaled %>% 
+  filter(country != "World") %>% 
+  drop_na(mean) %>% 
+  mutate(
+    case = case_when(
+      sign(q2.5) == sign(q97.5) & sign(mean) == -1 ~ "Negative",
+      sign(q2.5) == sign(q97.5) & sign(mean) == 1 ~ "Positive",
+      TRUE ~ "Inconclusive"
+    )
+  ) %>% 
+  mutate(
+    case = factor(case, levels = c("Negative", "Inconclusive", "Positive"))
+  ) %>% 
+  count(x, outcome, case) %>% 
+  group_by(x, outcome) %>% 
+  mutate(p = percent(n / sum(n), .1)) %>% 
+  ungroup() %>% 
+  transmute(
+    Outcome = fct_inorder(str_replace(outcome, "_", " ")),
+    Predictor = x,
+    case,
+    count = as.character(str_glue("{n} ({p})"))
+  ) %>%
+  complete(Outcome, Predictor, case, fill = list(count = "0")) %>%
+  pivot_wider(names_from = case, values_from = count) %>% 
+  flextable() %>% 
+  set_caption(
+    "Counts of countries with negative, positive, and inconclusive results"
+  )
+```
+
+This table shows
+- Coefficients: change per decade and 10% shift in internet/mobile
+- Coefficients: change per decade-equivalent shift in internet/mobile
+- Posterior probability of latter being smaller than change per decade
+
+```{r}
+# Changes per decade per outcome
+change_factors <- country_post %>% 
+  select(outcome, summary) %>% 
+  unnest(summary) %>% 
+  filter(x == "Time", y == "outcome") %>% 
+  select(outcome, country, change_per_decade = mean)
+
+# Posterior samples of all effects on outcomes
+tab <- country_post %>% 
+  select(outcome, samples) %>% 
+  unnest(samples) %>% 
+  filter(y == "outcome") %>%
+  select(-y) %>%
+  pivot_longer(-c(outcome, x), names_to = "country") %>% 
+  # Drop NAs because some country-outcome combinations don't exist
+  drop_na(value)
+
+# Scale internet and mobile to decade-equivalents
+scaling_factors %>% 
+  filter(country == "World") %>% 
+  group_by(y, country) %>% 
+  summarise(scaling = mean(scaling))
+tab <- tab %>% 
+  left_join(
+    scaling_factors %>% 
+      rename(x = y)
+  ) %>% 
+  mutate(scaling = if_else(x == "Time", 1, scaling)) %>% 
+  mutate(scaled = value * scaling) %>% 
+  select(-scaling)
+
+# Change associations with internet and mobile to units of 10% not 100%
+tab <- tab %>% 
+  mutate(
+    value = if_else(x == "Time", value, value / 10)
+  )
+
+# Add ROPE limits (change in outcome per decade) and
+# compute posterior summaries
+
+# Function to replace extreme percentages
+percent2 <- function(x, accuracy = .1) {
+  x <- percent(x, accuracy = accuracy)
+  x <- if_else(x == "100.0%", ">99.9%", x)
+  x <- if_else(x == "0.0%", "<0.1%", x)
+  x
+}
+
+path <- "models/pub-table.rds"
+if (!file.exists(path)) {
+  tab <- tab %>% 
+    nest(data = c(value, scaled)) %>% 
+    left_join(change_factors) %>% 
+    mutate(change_per_decade = if_else(x == "Time", 1, change_per_decade)) %>% 
+    mutate(
+      out = map2(
+        data, change_per_decade,
+        ~describe_posterior(
+          .x, 
+          centrality = "mean", 
+          ci_method = "eti",
+          rope_range = c(-.y, .y), 
+          rope_ci = 1
+        )
+      )
+    ) %>% 
+    mutate(
+      Predictor = fct_inorder(x), 
+      Outcome = fct_inorder(str_replace(outcome, "_", " "))
+    ) %>% 
+    select(Predictor, Outcome, country, out) %>% 
+    arrange(Predictor, Outcome) %>% 
+    unnest(out) %>% 
+    mutate(
+      across(c(Mean, CI_low, CI_high), ~number(., .001, trim = TRUE))
+    ) %>% 
+    mutate(
+      pd = percent2(pd, .1),
+      ROPE_Percentage = percent2(ROPE_Percentage, .1)
+    ) %>% 
+    mutate(
+      Result = case_when(
+        Parameter == "value" ~ 
+          str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})"),
+        Predictor == "Time" & Parameter == "scaled" ~ "",
+        Predictor != "Time" & Parameter != "value" ~ 
+          str_glue("{Mean} [{CI_low}, {CI_high}] ({ROPE_Percentage})"),
+      )
+    ) %>% 
+    transmute(
+      Predictor,
+      Outcome,
+      Country = country,
+      Parameter,
+      Result
+    ) %>% 
+    select(Predictor, Outcome, Country, Result, Parameter) %>% 
+    pivot_wider(names_from = Parameter, values_from = Result) %>% 
+    rename(`Raw association` = value, `Scaled association` = scaled)
+  saveRDS(tab, path)
+} else {tab <- readRDS(path)}
+
+tab %>% 
+  filter(Country == "World") %>% 
+  select(-Country) %>% 
+  flextable(cwidth = c(.8,1.4,2.3,2.3)) %>% 
+  autofit() %>% 
+  # footnote(
+  #   i = 1, 
+  #   j = c(3, 4), 
+  #   part = "header",
+  #   value = as_paragraph(
+  #     c(
+  #       "Posterior mean, [95%CI], and (posterior probability of direction).
+Associations are in units of decades (change in outcome (%) as a function of a decade) or 10% (change in outcome as a function of 10% increase in Internet or Mobile).",
+  #       "Decade-equivalent posterior mean associations, [95%CI], and (posterior probability outside the region of practical equivalence).
+Decade-equivalent associations indicate contrasts in the outcome as a function of the extent to which the predictor changed in a decade."
+  #     )
+  #   ), 
+  # ) %>% 
+  save_as_docx(path = "figures/parameter-table.docx")
+```
+
+## Correlations
+
+Next, we examine how the average levels, and changes in, countries internet adoption and mental health / well-being parameters correlate. That is, we ask whether
+
+- Countries with greater levels of internet adoption on average tend to be those with greater/lesser mental health and well-being?
+- Countries where internet adoption increased most tend to be those where mental health / well-being increased/decreased the most?
+
+### OLS
+
+We begin by a look at the ordinary least squares (OLS) estimates, recognizing that this approach is limited by ignoring the noise in the parameters used as data in the analysis.
+
+:::{.panel-tabset}
+
+#### Scatterplot
+
+```{r}
+dat <- readRDS("data/data-all.rds")
+itu <- readRDS("data/itu.rds")
+
+# Some countries don't have mobile data, enable computation still
+pcoef <- possibly(coef, NA)
+
+# Get all regression parameters
+ols_itu <- itu %>%
+  mutate(year = (year-2010)/10) %>% 
+  group_by(country) %>%
+  summarise(
+    internet_mean = mean(internet, na.rm = TRUE),
+    internet_slope = coef(lm(internet ~ year, data = cur_data()))[2],
+    mobile_mean = mean(mobile, na.rm = TRUE),
+    mobile_slope = pcoef(lm(mobile ~ year, data = cur_data()))[2],
+    hdi_mean = mean(hdi, na.rm = TRUE),
+    hdi_slope = pcoef(lm(hdi ~ year, data = cur_data()))[2]
+  )
+ols_val <- dat %>%
+  drop_na(val) %>%
+  group_by(outcome, country) %>%
+  summarise(
+    val_mean = mean(val, na.rm = TRUE),
+    val_slope = coef(lm(val ~ year, data = cur_data()))[2]
+  )
+
+ols <- left_join(ols_itu, ols_val)
+ols_internet_mean_plot <- ols %>% 
+  ggplot(aes(internet_mean, val_mean)) +
+  scale_x_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(., 01)
+  ) +
+  scale_y_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(./100, .01)
+  ) +
+  geom_point(aes(text = country), size = .75, shape = 1) +
+  geom_smooth(method = "lm", size = .5) +
+  labs(
+    x = "Mean internet users per capita",
+    y = "Mean outcome"
+  ) +
+  facet_wrap(
+    "outcome", 
+    scales = "free", 
+    nrow = 1, 
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(aspect.ratio = 1)
+
+ols_mobile_mean_plot <- ols_internet_mean_plot +
+  aes(mobile_mean, val_mean) +
+  labs(
+    x = "Mean mobile broadband subscriptions per capita",
+    y = "Mean outcome"
+  )
+
+ols_internet_slope_plot <- ols_internet_mean_plot + 
+  aes(internet_slope, val_slope) +
+  labs(
+    x = "Change per decade in internet users per capita",
+    y = "Change in outcome"
+  )
+
+ols_mobile_slope_plot <- ols_internet_mean_plot + 
+  aes(mobile_slope, val_slope) +
+  labs(
+    x = "Change per decade in mobile broadband subscriptions per capita",
+    y = "Change in outcome"
+  )
+
+ols_internet_mean_plot /
+  ols_internet_slope_plot /
+  ols_mobile_mean_plot /
+  ols_mobile_slope_plot
+
+# (ols_internet_mean_plot /
+#   ols_internet_slope_plot /
+#   ols_mobile_mean_plot /
+#   ols_mobile_slope_plot) & stat_ellipse()
+```
+
+#### Interactive scatterplot
+
+```{r}
+p1 <- ggplotly(ols_internet_mean_plot, tooltip = "text") %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30)
+  )
+p2 <- ggplotly(ols_internet_slope_plot) %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30)
+  )
+p3 <- ggplotly(ols_mobile_mean_plot) %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30)
+  )
+p4 <- ggplotly(ols_mobile_slope_plot) %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30)
+  )
+subplot(
+  p1, p2, p3, p4, 
+  nrows = 4, 
+  shareX = FALSE, 
+  shareY = FALSE, 
+  titleX = TRUE,
+  margin = 0.05
+)
+```
+
+:::
+
+### Model based
+
+#### Correlation parameters
+
+```{r}
+get_cor_pars <- function(outcome, predictor, model) {
+  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
+  as_draws_df(
+    x,
+    variable = c(
+      str_glue("b_{predictor}_Intercept"),
+      "b_val_Intercept",
+      str_glue("b_{predictor}_year"),
+      "b_val_year",
+      str_glue("sd_country__{predictor}_Intercept"),
+      "sd_country__val_Intercept",
+      str_glue("sd_country__{predictor}_year"),
+      "sd_country__val_year",
+      str_glue("cor_country__{predictor}_year__val_year"),
+      str_glue("cor_country__{predictor}_Intercept__val_Intercept")
+    )
+  )
+}
+get_cor_pars <- memoise(get_cor_pars, cache = cd)
+
+cor_pars_brm <- fits %>%
+  mutate(
+    internet = map(outcome, ~get_cor_pars(.x, "internet", "1")),
+    mobile = map(outcome, ~get_cor_pars(.x, "mobile", "2"))
+  )
+
+cor_sum <- cor_pars_brm %>% 
+  mutate(
+    across(
+      internet:mobile, 
+      ~map(., ~summarise_draws(., mean, ~quantile2(., probs = c(.025, .975))))
+    )
+  )
+cor_sum %>% 
+  pivot_longer(-outcome, names_to = "predictor") %>% 
+  unnest(value) %>% 
+  filter(str_detect(variable, "cor_")) %>% 
+  mutate(
+    across(mean:q97.5, ~number(., .01))
+  ) %>% 
+  transmute(
+    Outcome = str_replace(outcome, "_", " "),
+    Predictor = str_to_title(predictor),
+    Correlation = if_else(str_detect(variable, "Intercept"), "Averages", "Slopes"),
+    Summary = str_glue("{mean} [{q2.5}, {q97.5}]")
+  ) %>% 
+  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
+  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
+  arrange(Correlation, Outcome) %>% 
+  kbl(caption = "Correlation parameters") %>% 
+  kable_custom()
+```
+
+::: {.panel-tabset .column-body-outset-right}
+
+#### Scatterplot
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+mcoef <- memoise(brms:::coef.brmsfit, cache = cd)
+country_pars <- fits %>% 
+  mutate(
+    internet = map(
+      outcome,
+      ~mcoef(readRDS(str_glue("models/brm-{.x}-1.rds")))$country %>% 
+        as.data.frame.array() %>% 
+        rownames_to_column("country")
+    ),
+    mobile = map(
+      outcome,
+      ~mcoef(readRDS(str_glue("models/brm-{.x}-2.rds")))$country %>% 
+        as.data.frame.array() %>% 
+        rownames_to_column("country")
+    )
+  )
+
+c1 <- country_pars %>% 
+  select(outcome, internet) %>% 
+  unnest(internet) %>% 
+  transmute(
+    outcome, country,
+    internet_intercept = Estimate.internet_Intercept,
+    internet_slope = Estimate.internet_year,
+    val_intercept = Estimate.val_Intercept,
+    val_slope = Estimate.val_year
+  )
+c2 <- country_pars %>% 
+  select(outcome, mobile) %>% 
+  unnest(mobile) %>% 
+  transmute(
+    outcome, country,
+    mobile_intercept = Estimate.mobile_Intercept,
+    mobile_slope = Estimate.mobile_year,
+    val2_intercept = Estimate.val_Intercept,
+    val2_slope = Estimate.val_year
+  )
+
+brm_internet_intercept_plot <- left_join(c1, c2) %>% 
+  ggplot(aes(internet_intercept, val_intercept)) +
+  scale_x_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(., 01)
+  ) +
+  scale_y_continuous(
+    breaks = extended_breaks(),
+    labels = ~percent(./100, .1)
+  ) +
+  geom_point(
+    aes(text = country), 
+    col = "dodgerblue1", size = .75, shape = 1) +
+  labs(
+    x = "Average internet users per capita",
+    y = "Average outcome"
+  ) +
+  facet_wrap(
+    "outcome", 
+    scales = "free", 
+    nrow = 1, 
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(aspect.ratio = 1)
+
+brm_mobile_intercept_plot <- brm_internet_intercept_plot +
+  aes(mobile_intercept, val2_intercept) +
+  labs(
+    x = "Average mobile broadband subscriptions per capita",
+    y = "Average outcome"
+  )
+
+brm_internet_slope_plot <- brm_internet_intercept_plot + 
+  aes(internet_slope, val_slope) +
+  labs(
+    x = "Change in internet users per capita",
+    y = "Change in outcome"
+  )
+
+brm_mobile_slope_plot <- brm_internet_intercept_plot + 
+  aes(mobile_slope, val_slope) +
+  labs(
+    x = "Change in mobile broadband subscriptions per capita",
+    y = "Change in outcome"
+  )
+
+brm_internet_intercept_plot /
+  brm_internet_slope_plot /
+  brm_mobile_intercept_plot /
+  brm_mobile_slope_plot
+```
+
+## Publication figures
+
+Here we combine and further edit the figures from above to a format for publication.
+
+:::{.panel-tabset}
+
+### Timecourses
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+pa <- country_year_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(axis.title.x = element_blank())
+pb <- sex_year_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  )
+pc <- pa / pb +
+  plot_annotation(tag_levels = "A") +
+  plot_layout(heights = c(5.5, 4.5)) &
+  theme(
+    legend.position = "none",
+    axis.text.x = element_text(angle = 90)
+  )
+pc
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/Parameters-timecourses.png",
+  width = W, height = W*0.55, units = "in", res = 300
+)
+pc
+dev.off()
+```
+
+### Internet associations
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+pa <- country_internet_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(axis.title.x = element_blank())
+pb <- sex_internet_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(legend.position = "none")
+pc <- pa / pb +
+  plot_annotation(tag_levels = "A") +
+  plot_layout(heights = c(5.5, 4.5)) &
+  theme(
+    legend.position = "none",
+    axis.text.x = element_text(angle = 90)
+  )
+pc
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/Parameters-associations-internet.png",
+  width = W, height = W*0.55, units = "in", res = 300
+)
+pc
+dev.off()
+```
+
+### Mobile associations
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+pa <- country_mobile_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(axis.title.x = element_blank())
+pb <- sex_mobile_plot +
+  facet_wrap(
+    "outcome", 
+    nrow = 1, 
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(legend.position = "none")
+pc <- pa / pb +
+  plot_annotation(tag_levels = "A") +
+  plot_layout(heights = c(5.5, 4.5)) &
+  theme(
+    legend.position = "none",
+    axis.text.x = element_text(angle = 90)
+  )
+pc
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/Parameters-associations-mobile.png",
+  width = W, height = W*0.55, units = "in", res = 300
+)
+pc
+dev.off()
+```
+
+### Correlations
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+library(ellipse)
+# This is hairy because of two different internet metrics
+ellipses <- cor_pars_brm %>% 
+  pivot_longer(-outcome) %>% 
+  unnest(value) %>% 
+  group_by(outcome, name) %>% 
+  slice_sample(n = 30) %>% 
+  select(
+    # Intercept parameters
+    i_int_mu = b_internet_Intercept,
+    i_int_sd = sd_country__internet_Intercept,
+    i_val_mu = b_val_Intercept,
+    i_val_sd = sd_country__val_Intercept,
+    i_pxy = cor_country__internet_Intercept__val_Intercept,
+    i_mob_mu = b_mobile_Intercept,
+    i_mob_sd = sd_country__mobile_Intercept,
+    i_pxy2 = cor_country__mobile_Intercept__val_Intercept,
+    # Slope parameters
+    s_int_mu = b_internet_year,
+    s_int_sd = sd_country__internet_year,
+    s_val_mu = b_val_year,
+    s_val_sd = sd_country__val_year,
+    s_pxy = cor_country__internet_year__val_year,
+    s_mob_mu = b_mobile_year,
+    s_mob_sd = sd_country__mobile_year,
+    s_pxy2 = cor_country__mobile_year__val_year,
+    .draw
+  ) %>%
+  mutate(
+    i_int_mu = coalesce(i_int_mu, i_mob_mu),
+    i_int_sd = coalesce(i_int_sd, i_mob_sd),
+    i_pxy = coalesce(i_pxy, i_pxy2),
+    s_int_mu = coalesce(s_int_mu, s_mob_mu),
+    s_int_sd = coalesce(s_int_sd, s_mob_sd),
+    s_pxy = coalesce(s_pxy, s_pxy2)
+  ) %>% 
+  mutate(
+    ellipse_intercept = pmap(
+      list(i_pxy, i_int_sd, i_val_sd, i_int_mu, i_val_mu),
+      ~ellipse(..1, scale = c(..2, ..3), centre = c(..4, ..5)) %>% 
+        as_tibble()
+    ),
+    ellipse_slope = pmap(
+      list(s_pxy, s_int_sd, s_val_sd, s_int_mu, s_val_mu),
+      ~ellipse(..1, scale = c(..2, ..3), centre = c(..4, ..5)) %>% 
+        as_tibble()
+    )
+  )
+
+p1 <- brm_internet_intercept_plot +
+  geom_path(
+    data = filter(ellipses, name == "internet") %>% unnest(ellipse_intercept),
+    aes(x, y, group = .draw), color = "dodgerblue1", alpha = .05
+  )
+p2 <- brm_internet_slope_plot +
+  geom_path(
+    data = filter(ellipses, name == "internet") %>% unnest(ellipse_slope),
+    aes(x, y, group = .draw), color = "dodgerblue1", alpha = .05
+  )
+p3 <- brm_mobile_intercept_plot +
+  geom_path(
+    data = filter(ellipses, name == "mobile") %>% unnest(ellipse_intercept),
+    aes(x, y, group = .draw), color = "dodgerblue1", alpha = .05
+  )
+p4 <- brm_mobile_slope_plot +
+  geom_path(
+    data = filter(ellipses, name == "mobile") %>% unnest(ellipse_slope),
+    aes(x, y, group = .draw), color = "dodgerblue1", alpha = .05
+  ) +
+  coord_cartesian(xlim = c(-.2, 1.8))
+pc <- p1 / p2 / p3 / p4 +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/Correlations.png",
+  width = W, height = W*0.8, units = "in", res = 300
+)
+pc
+dev.off()
+```
+
+:::
+
+## SCA
+
+### OLS {.panel-tabset}
+
+First we draw figures from OLS regressions of `outcome ~ time + predictor`.
+We draw parameter estimates `b_time` and `b_predictor` for every combination of country, year, and sex, for each outcome and predictor (internet/mobile).
+
+#### Well-being
+
+```{r}
+if (!file.exists("tmp.rds")) {
+  library(multidplyr)
+  library(tictoc)
+  pfilter <- possibly(dplyr::filter, NA)
+  cluster <- new_cluster(8)
+  cluster_library(cluster, c("tidyverse", "broom"))
+  cluster_copy(cluster, "pfilter")
+  tic()
+  out <- dat %>% 
+    # Limit to aggregates with 10 or more people (or MH model estimates)
+    filter(n > 9 | is.na(n)) %>% 
+    select(outcome, country, sex, age, val, year, i1_cw, m1_cw) %>% 
+    pivot_longer(i1_cw:m1_cw, names_to = "predictor", values_to = "x") %>% 
+    group_by(outcome, predictor, country, sex, age) %>% 
+    mutate(z = cur_group_id()) %>% 
+    nest(data = c(val, x, year)) %>% 
+    mutate(n = map_dbl(data, nrow)) %>% 
+    arrange(n) %>% 
+    # Limit to specs for which 5 or more years existed
+    filter(n > 4) %>%
+    partition(cluster) %>%
+    mutate(
+      out = map(
+        data,
+        ~pfilter(
+          tidy(
+            lm(val ~ x + year, data = .x), 
+            conf.int = TRUE
+          ), 
+          term %in% c("x", "year")
+        )
+      )
+    ) %>% 
+    collect()
+  toc()
+  saveRDS(out, "tmp.rds")
+} else {out <- readRDS("tmp.rds")}
+
+# Wrangle
+tmp <- out %>% 
+  select(-data, -n) %>% 
+  unnest(out) %>% 
+  # Create three predictors: year, internet, mobile
+  ungroup() %>% 
+  filter(!(predictor == "m1_cw" & term == "year")) %>% 
+  mutate(
+    predictor = case_when(
+      predictor == "i1_cw" & term == "x" ~ "Internet",
+      predictor == "m1_cw" & term == "x" ~ "Mobile",
+      predictor == "i1_cw" & term == "year" ~ "Time"
+    )
+  ) %>% 
+  group_by(predictor, outcome) %>% 
+  arrange(predictor, outcome, estimate) %>% 
+  mutate(n = 1:n()) %>% 
+  mutate(
+    sig = p.value < .05,
+    color = case_when(
+      !sig ~ "a",
+      sig & sign(estimate) == -1 ~ "b",
+      sig & sign(estimate) == 1 ~ "c"
+    )
+  )
+
+tmp <- tmp %>% 
+  rename(X = predictor, Sex = sex, Age = age)
+
+tmp <- drop_na(tmp, X)
+
+# Rescale to "decade-equivalent dose"
+tmp <- tmp %>% 
+  left_join(select(ols_itu, country, internet_slope, mobile_slope)) %>% 
+  mutate(
+    across(
+      c(estimate, std.error, conf.low, conf.high), 
+      ~case_when(
+        X == "Time" ~ .,
+        X == "Internet" ~ . * abs(internet_slope),
+        X == "Mobile" ~ . * abs(mobile_slope)
+      )
+    )
+  )
+
+# Arrange data for X axis
+tmp <- tmp %>% 
+  ungroup() %>% 
+  select(-c(z, term, std.error, statistic, ends_with("slope"))) %>% 
+  group_by(outcome, X) %>% 
+  arrange(outcome, X, estimate) %>% 
+  mutate(n = 1:n())
+
+sca_plot <- function(outcome, ylim = 50) {
+  data <- filter(tmp, outcome == {{outcome}})
+
+  p0 <- data %>%   
+    ggplot(
+      aes(
+        x = n, y = estimate, col = color,
+        text = str_glue("{country}, {Sex}, {Age}")
+      )
+    ) +
+    scale_color_manual(
+      values = c("grey75", "#CC3311", "#009988")
+    ) +
+    theme(
+      legend.position = "none"
+    )
+
+  p1 <- p0 +  
+    scale_y_continuous(
+      "Estimate",
+      breaks = extended_breaks(),
+      labels = ~percent(./100)
+    ) +
+    geom_hline(yintercept = 0, lty = 2, size = .1) +
+    # geom_linerange(
+    #   aes(ymin = conf.low, ymax = conf.high),
+    #   size = .025
+    # ) +
+    geom_point(
+      data = filter(p0$data, color == "a"), 
+      size = .275, alpha = .75
+    ) +
+    geom_point(
+      data = filter(p0$data, color == "b"), 
+      size = .275, alpha = .75
+    ) +
+    geom_point(
+      data = filter(p0$data, color == "c"), 
+      size = .275, alpha = .75
+    ) +
+    coord_cartesian(ylim = c(-ylim, ylim)) +
+    facet_grid(
+      rows = vars(X), 
+      cols = vars(outcome), 
+      labeller = as_labeller(~str_replace(., "_", " "))
+    ) +
+    theme(
+      plot.margin = unit(c(4,4,2,4), "pt"),
+      axis.title.x = element_blank()
+    )
+
+  p2 <- p0 + 
+    scale_y_discrete() +
+    aes(n, X, col = color) +
+    geom_point(shape = "|") +
+    # facet_grid(rows = "1", labeller = as_labeller(~"Sex")) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      plot.margin = unit(c(0,0,0,0), "pt"),
+      strip.background = element_blank()
+    )
+
+  p3 <- p0 + 
+    scale_y_discrete() +
+    aes(n, Sex, col = color) +
+    geom_point(
+      size = .1,
+      position = position_jitter(0, .3)
+    ) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      plot.margin = unit(c(0,0,0,0), "pt"),
+      strip.background = element_blank()
+    )
+
+  p4 <- p0 + 
+    aes(n, Age, col = color) +
+    geom_point(
+      size = .15, shape = 20,
+      position = position_jitter(0, .3)
+    ) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank()
+    ) + 
+    scale_y_discrete(limits = rev) +
+    labs(x = "Specification") +
+    theme(plot.margin = unit(c(0,0,6,0), "pt"))
+  (p1 / p3 / p4) +
+    plot_layout(heights = c(6.5, 0.4, 2.5))
+}
+p1 <- oo[1:3] %>% 
+  map(~sca_plot(.))
+wrap_plots(p1[[1]], p1[[2]], p1[[3]])
+```
+
+#### Well-being interactive
+
+```{r}
+subplot(
+  ggplotly(p1[[1]][[1]], tooltip = "text"),
+  ggplotly(p1[[2]][[1]], tooltip = "text"),
+  ggplotly(p1[[3]][[1]], tooltip = "text"),
+  ggplotly(p1[[1]][[2]], tooltip = "text"), 
+  ggplotly(p1[[2]][[2]], tooltip = "text"), 
+  ggplotly(p1[[3]][[2]], tooltip = "text"), 
+  ggplotly(p1[[1]][[3]], tooltip = "text"), 
+  ggplotly(p1[[2]][[3]], tooltip = "text"), 
+  ggplotly(p1[[3]][[3]], tooltip = "text"), 
+  nrows = 3, 
+  heights = c(0.6, 0.1, 0.3), 
+  titleX = TRUE, shareX = TRUE
+) %>% 
+  layout(
+    margin = list(t = 30, r = 30, b = 30, l = 30)
+  )
+```
+
+#### Mental health
+
+```{r}
+p2 <- oo[4:5] %>% 
+  map(~sca_plot(., 1))
+p2[[3]] <- sca_plot(oo[6], .1)
+wrap_plots(p2[[1]], p2[[2]], p2[[3]])
+```
+
+#### Mental health interactive
+
+```{r}
+subplot(
+  ggplotly(p2[[1]][[1]], tooltip = "text"),
+  ggplotly(p2[[2]][[1]], tooltip = "text"),
+  ggplotly(p2[[3]][[1]], tooltip = "text"),
+  ggplotly(p2[[1]][[2]], tooltip = "text"), 
+  ggplotly(p2[[2]][[2]], tooltip = "text"), 
+  ggplotly(p2[[3]][[2]], tooltip = "text"), 
+  ggplotly(p2[[1]][[3]], tooltip = "text"), 
+  ggplotly(p2[[2]][[3]], tooltip = "text"), 
+  ggplotly(p2[[3]][[3]], tooltip = "text"), 
+  nrows = 3, 
+  heights = c(0.6, 0.1, 0.3), 
+  titleX = TRUE, shareX = TRUE
+) %>% 
+  layout(
+    margin = list(t = 30, r = 30, b = 30, l = 30)
+  )
+```
+
+:::
+
+### Model based
+
+OLS estimates are very noisy and lead to implausibly large values and issues with multiple comparisons.
+Therefore a more accurate image is drawn from the models' estimates of country-, age-, and sex-specific estimates.
+Calculating these takes up to 20 minutes,
+
+```{r}
+# Function to get country-sex-age estimates of time, internet and mobile effects for each outcome
+
+get_coefs <- function(outcome) {
+  if (!file.exists(str_glue("memoise_cache/{outcome}-sca-coefs.rds"))) {
+    # Load three fits for outcome
+    fit_1 <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
+    fit_3 <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
+    fit_4 <- readRDS(str_glue("models/brm-{outcome}-4.rds"))
+
+    # Calculate time, internet, and mobile effects
+    # for each country, sex, and age
+    y_time <- tibble(fit_1$data) %>% 
+      distinct(country, sex, age) %>% 
+      mutate(se = 0, val = 0) %>% 
+      mutate(min = -0.5, max = 0.5) %>% 
+      pivot_longer(c(min, max), values_to = "year") %>% 
+      add_epred_draws(fit_1, ndraws = 200, resp = "val") %>% 
+      ungroup() %>% 
+      select(country, sex, age, name, .epred) %>% 
+      group_by(country, sex, age) %>%
+      summarise(.epred = .epred[name=="max"] - .epred[name=="min"]) %>% 
+      mean_qi()
+
+    # Internet slopes ("decade-equivalent") from model 3
+    y_internet <- tibble(fit_3$data) %>% 
+      distinct(country, sex, age) %>% 
+      left_join(distinct(itu, country, i1_cb)) %>% 
+      left_join(distinct(ols_itu, country, internet_slope)) %>% 
+      mutate(year = 0, se = 0) %>% 
+      mutate(min = -internet_slope/2, max = internet_slope/2) %>% 
+      pivot_longer(c(min, max), values_to = "i1_cw") %>% 
+      add_epred_draws(fit_3, ndraws = 200, resp = "val") %>% 
+      ungroup() %>% 
+      select(country, sex, age, name, .epred) %>% 
+      group_by(country, sex, age) %>%
+      summarise(.epred = .epred[name=="max"] - .epred[name=="min"]) %>% 
+      mean_qi()
+
+    y_mobile <- tibble(fit_4$data) %>% 
+      distinct(country, sex, age) %>% 
+      left_join(distinct(itu, country, m1_cb)) %>% 
+      left_join(distinct(ols_itu, country, mobile_slope)) %>% 
+      mutate(year = 0, se = 0) %>% 
+      mutate(min = -mobile_slope/2, max = mobile_slope/2) %>% 
+      pivot_longer(c(min, max), values_to = "m1_cw") %>% 
+      add_epred_draws(fit_4, ndraws = 200, resp = "val") %>% 
+      ungroup() %>% 
+      select(country, sex, age, name, .epred) %>% 
+      group_by(country, sex, age) %>%
+      summarise(.epred = .epred[name=="max"] - .epred[name=="min"]) %>% 
+      mean_qi()
+
+    y_all <- bind_rows(
+      "Time" = y_time,
+      "Internet" = y_internet,
+      "Mobile" = y_mobile,
+      .id = "predictor"
+    )
+    saveRDS(y_all, str_glue("memoise_cache/{outcome}-sca-coefs.rds"))
+  } else {y_all <- readRDS(str_glue("memoise_cache/{outcome}-sca-coefs.rds"))}
+  y_all
+}
+
+coefs <- tibble(
+  outcome = factor(oo, levels = oo)
+) %>% 
+  group_by(outcome) %>% 
+  mutate(out = map(outcome, get_coefs))
+```
+
+```{r}
+# Wrangle
+tmp <- coefs %>% 
+  unnest(out) %>% 
+  mutate(
+    sig = sign(.lower) == sign(.upper),
+    color = case_when(
+      !sig ~ "a",
+      sig & sign(.epred) == -1 ~ "b",
+      sig & sign(.epred) == 1 ~ "c"
+    )
+  ) %>% 
+  rename(X = predictor, Sex = sex, Age = age) %>% 
+  # Rescale to "decade-equivalent dose"
+  left_join(select(ols_itu, country, internet_slope, mobile_slope)) %>% 
+  mutate(
+    across(
+      c(.epred, .lower, .upper), 
+      ~case_when(
+        X == "Time" ~ .,
+        X == "Internet" ~ . * abs(internet_slope),
+        X == "Mobile" ~ . * abs(mobile_slope)
+      )
+    )
+  ) %>% 
+  # Arrange data for X axis
+  ungroup() %>% 
+  select(-c(.width, .point, .interval, ends_with("slope"))) %>% 
+  group_by(outcome, X) %>% 
+  arrange(outcome, X, .epred) %>% 
+  mutate(n = 1:n()) %>% 
+  mutate(X = factor(X, levels = c("Time", "Internet", "Mobile")))
+
+# We also display the world averages
+tmp_world_scaling <- select(ols_itu, country, internet_slope, mobile_slope) %>% 
+  summarise(
+    internet_slope = mean(internet_slope, na.rm = TRUE),
+    mobile_slope = mean(mobile_slope, na.rm = TRUE)
+  )
+tmp_world <- bind_rows(
+  "Time" = country_year_coefs,
+  "Internet" = country_internet_coefs,
+  "Mobile" = country_mobile_coefs,
+  .id = "X"
+) %>% 
+  filter(country == "World") %>% 
+  transmute(
+    X, outcome, .epred = mean, .lower = q2.5, .upper = q97.5
+  ) %>% 
+  mutate(
+    sig = sign(.lower) == sign(.upper),
+    color = case_when(
+      !sig ~ "a",
+      sig & sign(.epred) == -1 ~ "b",
+      sig & sign(.epred) == 1 ~ "c"
+    )
+  ) %>% 
+  # Rescale to "decade-equivalent dose"
+  bind_cols(tmp_world_scaling) %>% 
+  mutate(
+    across(
+      c(.epred, .lower, .upper), 
+      ~case_when(
+        X == "Time" ~ .,
+        X == "Internet" ~ . * abs(internet_slope),
+        X == "Mobile" ~ . * abs(mobile_slope)
+      )
+    )
+  ) %>% 
+  mutate(X = factor(X, levels = c("Time", "Internet", "Mobile")))
+```
+
+```{r}
+sca_plot <- function(outcome, ylim = 25) {
+  data <- filter(tmp, outcome == {{outcome}})
+
+  avg_n <- data %>% 
+    group_by(X) %>% 
+    summarise(n = median(n))
+
+  avg <- filter(tmp_world, outcome == {{outcome}}) %>% 
+    mutate(n = -50)
+
+  p0 <- data %>%   
+    ggplot(
+      aes(
+        x = n, y = .epred, col = color, group = interaction(X, color),
+        text = str_glue("{country}, {Sex}, {Age}")
+      )
+    ) +
+    scale_color_manual(
+      values = c("grey80", "#CC3311", "#009988")
+    ) +
+    theme(
+      legend.position = "none"
+    )
+
+  p1 <- p0 +  
+    scale_y_continuous(
+      "Estimate",
+      breaks = extended_breaks(7),
+      labels = ~percent(./100)
+    ) +
+    geom_hline(yintercept = 0, lty = 2, size = .1) +
+    geom_linerange(
+      aes(ymin = .lower, ymax = .upper),
+      size = .025
+    ) +
+    geom_point(
+      data = filter(p0$data, color == "a"), 
+      size = .001, alpha = .5
+    ) +
+    geom_point(
+      data = filter(p0$data, color == "b"), 
+      size = .001, alpha = .5
+    ) +
+    geom_point(
+      data = filter(p0$data, color == "c"), 
+      size = .001, alpha = .5
+    ) +
+    coord_cartesian(ylim = c(-ylim, ylim)) +
+    facet_grid(
+      rows = vars(X),
+      cols = vars(outcome),
+      labeller = as_labeller(~str_replace(., "_", " "))
+    ) +
+    theme(
+      panel.grid.major.y = element_line(size = .1, color = "grey90"),
+      plot.margin = unit(c(4,4,2,4), "pt"),
+      axis.title.x = element_blank()
+    ) +
+    geom_pointrange(
+      data = avg,
+      aes(
+        ymin = .lower, 
+        ymax = .upper,
+        text = str_glue("World: {number(.epred, .1)} [{number(.lower, .1)}, {number(.upper, .1)}]")
+      ),
+      fatten = 0.75, size = .2, 
+    )
+
+  p2 <- p0 + 
+    scale_y_discrete() +
+    aes(n, X, col = color) +
+    geom_point(
+      size = .01, alpha = .25,
+      position = position_jitter(0, .35)
+    ) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.title.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      plot.margin = unit(c(0,0,0,0), "pt"),
+      strip.background = element_blank(),
+      axis.text.y = element_text(size = rel(0.75))
+    )
+
+  p3 <- p0 + 
+    scale_y_discrete() +
+    aes(n, Sex, col = color) +
+    geom_point(
+      size = .01, alpha = .25,
+      position = position_jitter(0, .35)
+    ) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.title.x = element_blank(),
+      axis.ticks.x = element_blank(),
+      plot.margin = unit(c(0,0,0,0), "pt"),
+      strip.background = element_blank(),
+      axis.text.y = element_text(size = rel(0.75))
+    )
+
+  p4 <- p0 + 
+    aes(n, Age, col = color) +
+    geom_point(
+      size = .01, alpha = .25,
+      position = position_jitter(0, .35)
+    ) +
+    theme(
+      axis.text.x = element_blank(),
+      axis.ticks.x = element_blank()
+    ) + 
+    scale_y_discrete(limits = rev) +
+    labs(x = "Specification") +
+    theme(
+      plot.margin = unit(c(0,0,6,0), "pt"),
+      axis.text.y = element_text(size = rel(0.75))
+    )
+  (p1 / p2 / p3 / p4) +
+    plot_layout(heights = c(7.4, 0.5, 0.3, 1.8))
+}
+```
+
+#### Well-being
+
+```{r}
+p1 <- oo[1:3] %>% 
+  map(~sca_plot(.))
+p1p <- wrap_plots(
+  (p1[[1]] & theme(axis.title.x = element_blank())), 
+  (p1[[2]] & theme(axis.title.y = element_blank())), 
+  (p1[[3]] & theme(axis.title = element_blank()))
+  )
+p1p
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/SCA-wellbeing-(model).png",
+  width = W, height = W*0.6, units = "in", res = 300
+)
+p1p
+dev.off()
+```
+
+#### Well-being interactive
+
+```{r}
+subplot(
+  ggplotly(p1p[[1]][[1]], tooltip = "text"),
+  ggplotly(p1p[[2]][[1]], tooltip = "text"),
+  ggplotly(p1p[[3]][[1]], tooltip = "text"),
+  ggplotly(p1p[[1]][[2]], tooltip = "text"), 
+  ggplotly(p1p[[2]][[2]], tooltip = "text"), 
+  ggplotly(p1p[[3]][[2]], tooltip = "text"), 
+  ggplotly(p1p[[1]][[3]], tooltip = "text"), 
+  ggplotly(p1p[[2]][[3]], tooltip = "text"), 
+  ggplotly(p1p[[3]][[3]], tooltip = "text"), 
+  ggplotly(p1p[[1]][[4]], tooltip = "text"), 
+  ggplotly(p1p[[2]][[4]], tooltip = "text"), 
+  ggplotly(p1p[[3]][[4]], tooltip = "text"), 
+  nrows = 4, 
+  heights = c(0.65, 0.06, 0.04, 0.25), 
+  titleX = TRUE, shareX = TRUE
+) %>% 
+  layout(
+    margin = list(t = 30, r = 30, b = 30, l = 30)
+  )
+```
+
+#### Mental health
+
+```{r}
+p2 <- oo[4:5] %>% 
+  map(~sca_plot(., .5))
+p2[[3]] <- sca_plot(oo[6], .08)
+p2p <- wrap_plots(p2[[1]], p2[[2]], p2[[3]])
+p2p
+```
+
+```{r include = FALSE}
+agg_png(
+  "figures/SCA-mentalhealth-(model).png",
+  width = W, height = W*0.7, units = "in", res = 300
+)
+p2p
+dev.off()
+```
+
+```{r}
+# Compare magnitudes of internet & mobile & time
+# It is critical that internet & mobile are appropriately scaled
+# That's why we use the "decade-equivalent" values
+# To do this properly we should do it one the samples not just means
+coefs %>% 
+  unnest(out) %>% 
+  select(-c(.width, .point, .interval)) %>% 
+  pivot_wider(
+    names_from = predictor,
+    values_from = starts_with(".")
+  ) %>% 
+  transmute(
+    outcome, country, sex, age,
+    internet = .epred_Internet / .epred_Time
+  ) %>% 
+  ggplot(aes(internet)) +
+  geom_histogram() +
+  scale_x_continuous(limits = c(-10, 10)) +
+  facet_wrap("outcome")
+```
+
+```{r}
+out <- z %>% 
+  ungroup() %>% 
+  select(country, sex, age, name, .epred) %>% 
+  group_by(country, sex, age) %>%
+  summarise(.epred = .epred[name=="max"] - .epred[name=="min"]) %>% 
+  mean_qi()
+# install.packages("specr")
+# library(specr)
+out <- out %>% 
+  arrange(.epred) %>% 
+  mutate(n = 1:n()) %>% 
+  mutate(
+    sig = sign(.lower) == sign(.upper),
+    x = case_when(
+      sig & sign(.epred) == -1 ~ "a",
+      !sig ~ "b",
+      sig & sign(.epred) == 1 ~ "c"
+    )
+  ) 
+p_t <- out %>%   
+  ggplot(aes(x = n, y = .epred, col = x)) +
+  scale_color_manual(
+    values = c("tomato2", "grey50", "dodgerblue2")
+  ) +
+  theme(
+    axis.title.x = element_blank(),
+    legend.position = "none"
+  )
+p1 <- p_t +  
+  scale_y_continuous(
+    "Estimate",
+    breaks = extended_breaks(),
+    labels = ~percent(./100)
+  ) +
+  scale_x_continuous(position = "top") +
+  geom_hline(yintercept = 0, lty = 2, size = .1) +
+  geom_linerange(
+    aes(ymin = .lower, ymax = .upper),
+    size = .025
+  ) +
+  geom_point(size = .025) +
+  theme(plot.margin = unit(c(4,4,2,4), "pt"))
+
+p2 <- p_t + 
+  aes(n, sex, col = x) +
+  geom_point(shape = "|") +
+  facet_grid(rows = "1", labeller = as_labeller(~"Sex")) +
+  theme(
+    axis.title = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+    plot.margin = unit(c(0,0,0,0), "pt")
+  )
+
+p3 <- p_t + 
+  aes(n, age, col = x) +
+  geom_point(shape = "|") +
+  facet_grid(rows = "1", labeller = as_labeller(~"Age")) +
+  theme(
+    axis.title = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank()
+  ) + 
+  scale_y_discrete(limits = rev) +
+  theme(plot.margin = unit(c(0,0,0,0), "pt"))
+(p1 / p2 / p3) +
+  plot_layout(heights = c(6.3, 0.4, 3.3))
+```
+
+## New figure 3
+
+```{r}
+this_name <- function(outcome) {
+
+  fit_time <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
+  fit_internet <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
+  fit_mobile <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))
+
+  y_time <- spread_draws(
+    fit_time, 
+    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
+  ) %>% 
+    ungroup() %>% 
+    mutate(
+      World_Female = b_val_year + `b_val_year:sex1`*1,
+      World_Male = b_val_year + `b_val_year:sex1`*-1,
+      Age_Female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
+      Age_Male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
+    ) %>% 
+    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
+    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
+    pivot_longer(-.draw, names_to = "Variable") %>% 
+    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
+    mutate(Age = str_replace_all(Age, "\\.", " "))
+
+  y_internet <- spread_draws(
+    fit_internet, 
+    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
+  ) %>% 
+    ungroup() %>% 
+    mutate(
+      World_Female = b_i1_cw + `b_i1_cw:sex1`*1,
+      World_Male = b_i1_cw + `b_i1_cw:sex1`*-1,
+      Age_Female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
+      Age_Male = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
+    ) %>% 
+    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
+    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
+    pivot_longer(-.draw, names_to = "Variable") %>% 
+    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
+    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
+    # Rescale effect to "decade-equivalent"
+    bind_cols(
+      scaling_factors %>% 
+        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
+        select(scaling)
+    ) %>% 
+    mutate(value = value * scaling) %>% 
+    select(-scaling)
+
+  y_mobile <- spread_draws(
+    fit_mobile, 
+    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
+  ) %>% 
+    ungroup() %>% 
+    mutate(
+      World_Female = b_m1_cw + `b_m1_cw:sex1`*1,
+      World_Male = b_m1_cw + `b_m1_cw:sex1`*-1,
+      Age_Female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
+      Age_Male = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
+    ) %>% 
+    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
+    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
+    pivot_longer(-.draw, names_to = "Variable") %>% 
+    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
+    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
+    # Rescale effect to "decade-equivalent"
+    bind_cols(
+      scaling_factors %>% 
+        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
+        select(scaling)
+    ) %>% 
+    mutate(value = value * scaling) %>% 
+    select(-scaling)
+
+  bind_rows(
+    "Time" = y_time,
+    "Internet" = y_internet,
+    "Mobile" = y_mobile,
+    .id = "X"
+  ) %>% 
+    mutate(X = factor(X, levels = c("Time", "Internet", "Mobile"))) %>% 
+    group_by(X, Level, Sex, Age) %>% 
+    mean_qi(value)
+}
+this_name <- memoise(this_name, cache = cd)
+
+out <- fits %>% 
+  mutate(
+    out = map(
+      outcome,
+      ~this_name(.x)
+    )
+  )
+
+p_tmp <- out %>% 
+  unnest(out) %>% 
+  mutate(
+    sig = sign(.lower) == sign(.upper),
+    color = case_when(
+      !sig ~ "c",
+      sig & sign(value) == -1 ~ "b",
+      sig & sign(value) == 1 ~ "a"
+    )
+  ) %>% 
+  mutate(Age = if_else(is.na(Age), Sex, Age)) %>% 
+  mutate(
+    Age = factor(
+      Age,
+      levels = c(
+        sort(levels(dat$age), decreasing = TRUE),
+        "Male", "Female"
+        )
+    )
+  ) %>%
+  ggplot(aes(value, Age, col = color, shape = Sex)) +
+  scale_color_brewer(palette = "Dark2") +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  scale_x_continuous(
+    "Estimated linear association (%)",
+    breaks = extended_breaks(5),
+    # labels = ~percent(./100, .01),
+    expand = expansion(.1)
+  ) +
+  geom_pointinterval(
+    aes(xmin = .lower, xmax = .upper),
+    interval_size_range = c(.1, .3),
+    fatten_point = 3,
+    position = position_dodgev(.5)
+  ) +
+  facet_grid(
+    rows = vars(X),
+    cols = vars(outcome),
+    scales = "free_x",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "none"
+  )
+p_tmp
+
+agg_png(
+  "figures/Parameters-all-sex.png",
+  width = W, height = W*0.6, units = "in", res = 300
+)
+p_tmp
+dev.off()
+```
+
+## Controls
+
+We then compare and contrast our results re internet adoption metrics to those with using Human Development Index as the predictor.
+We ask how different are associations with well being and mental health to internet adoption and HDI.
+
+```{r}
+# How do these things correlate
+correlations <- itu %>% 
+  group_by(country) %>% 
+  select(year, internet, hdi) %>% 
+  correlation::correlation()
+correlations %>%
+  tibble() %>% 
+  mutate(Group = fct_rev(Group)) %>% 
+  mutate(Correlation = str_glue("correlation({Parameter1}, {Parameter2})")) %>% 
+  ggplot(aes(r, Group)) +
+  scale_x_continuous(
+    "Pearson correlation"
+  ) +
+  geom_pointrangeh(
+    size = .15, fatten = 1.25,
+    aes(xmin = CI_low, xmax = CI_high)
+  ) +
+  facet_wrap("Correlation") +
+  theme(
+    text = element_text(size = 11),
+    axis.title.y = element_blank(),
+    panel.grid.major.x = element_line(linetype = 2, size = .1)
+  )
+```
+
+### Between-country correlations
+
+```{r}
+ols_hdi_mean_plot <- ols_internet_mean_plot +
+  aes(hdi_mean, val_mean) +
+  labs(
+    x = "Mean Human Development Index",
+    y = "Mean outcome"
+  )
+
+ols_hdi_slope_plot <- ols_internet_mean_plot + 
+  aes(hdi_slope, val_slope) +
+  labs(
+    x = "Change per decade in Human Development Index",
+    y = "Change in outcome"
+  )
+
+ols_internet_mean_plot /
+  ols_hdi_mean_plot /
+  ols_internet_slope_plot /
+  ols_hdi_slope_plot
+```
+
+We can then correlate internet and well-being, adjusting for hdi.
+
+```{r fig.height = 1.2}
+ols %>% 
+  group_by(outcome) %>% 
+  nest() %>% 
+  # mutate(data = map(data, ~mutate(., across(ends_with("mean"), scale)))) %>% 
+  mutate(
+    Raw_Internet = map(
+      data, 
+      ~tidy(lm(val_mean ~ internet_mean, data = .x), conf.int = TRUE)
+    ),
+    Adjusted_Internet = map(
+      data, 
+      ~tidy(lm(val_mean ~ internet_mean + hdi_mean, data = .x), conf.int = TRUE)
+    ),
+    Raw_Mobile = map(
+      data, 
+      ~tidy(lm(val_mean ~ mobile_mean, data = .x), conf.int = TRUE)
+    ),
+    Adjusted_Mobile = map(
+      data, 
+      ~tidy(lm(val_mean ~ mobile_mean + hdi_mean, data = .x), conf.int = TRUE)
+    )
+  ) %>% 
+  select(-data) %>% 
+  pivot_longer(
+    c(starts_with("Raw"), starts_with("Adjusted")), 
+    names_to = "Model"
+  ) %>% 
+  separate(Model, into = c("Model", "Predictor")) %>% 
+  unnest(value) %>% 
+  filter(term %in% c("internet_mean", "mobile_mean")) %>% 
+  ggplot(aes(estimate, Predictor, col = Model)) +
+  geom_vline(xintercept = 0, lty = 2, size = .25) +
+  scale_x_continuous(
+    "Association with 10% increase in internet adoption",
+    expand = expansion(.1),
+    breaks = extended_breaks(),
+    labels = ~percent(./1000, .1)
+  ) +
+  geom_pointrangeh(
+    aes(xmin = conf.low, xmax = conf.high),
+    position = position_dodge2v(.35)
+  ) +
+  facet_wrap("outcome", nrow = 1, scales = "free_x") +
+  theme(axis.text.x = element_text(angle = 90))
+```
+
+### HDI within-country associations
+
+::: {.panel-tabset}
+
+#### Countries
+
+```{r}
+#| fig.width: 10
+#| fig.height: 8
+country_hdi_sum <- function(fit) {
+  as_draws_df(
+    fit, 
+    variable = c("b_h1_cw", "^r_country"), 
+    regex = TRUE
+  ) %>% 
+    select(b_h1_cw, ends_with("h1_cw]")) %>% 
+    rename_with(
+      ~str_remove(., "r_country\\[") %>% str_remove(., ",h1_cw\\]")
+    ) %>% 
+    mutate(across(-b_h1_cw, ~.+b_h1_cw)) %>% 
+    rename(World = b_h1_cw) %>% 
+    summarise_draws(mean, ~quantile2(., probs = c(.025, .975))) %>% 
+    mutate(country = factor(variable))
+}
+country_hdi_sum <- memoise(country_hdi_sum, cache = cd)
+
+country_hdi_coefs <- fits %>% 
+  mutate(
+    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-5.rds"))),
+    country_hdi = map(fit, country_hdi_sum)
+  ) %>% 
+  select(-fit) %>% 
+  unnest(country_hdi)
+
+country_hdi_plot <- country_hdi_coefs %>% 
+  # Clean all country names
+  mutate(country = str_replace_all(country, "\\.(?!\\.)", " ")) %>% 
+  left_join(distinct(dat, region, country)) %>% 
+  # Arrange each panel
+  group_by(outcome) %>% 
+  arrange(outcome, mean) %>% 
+  mutate(n = 1:n(), y = factor(n)) %>% 
+  ungroup() %>% 
+  mutate(
+    level = country != "World", 
+    mh = outcome %in% oo[4:6],
+    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
+  ) %>% 
+  # mutate(star = sign(.lower) == sign(.upper)) %>% 
+  ggplot(aes(mean, y, color = level)) +
+  scale_size_manual(values = c(1.25, 0.25)) +
+  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
+  scale_y_discrete(expand = expansion(.01)) +
+  # Association with 10% change
+  scale_x_continuous(
+    "Estimated association with .1\nincrease Human Development Index",
+    breaks = extended_breaks(),
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  geom_segment(
+    aes(
+      x = q2.5, xend = q97.5, yend = y, 
+      text = text
+    ),
+    size = .15
+  ) +
+  geom_point(aes(text = text, size = level)) +
+  # Put world in top layer
+  geom_point(
+    data = . %>% filter(country == "World"), 
+    aes(text = text, size = level)
+  ) +
+  facet_wrap(
+    "outcome", 
+    nrow = 2, 
+    scales = "free",
+    labeller = as_labeller(~str_replace(., "_", " "))
+  ) +
+  labs(y = "Country") +
+  theme(
+    legend.position = "none",
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank()
+  )
+country_hdi_plot
+```
+
+#### Countries interactive
+
+```{r out.height = 860}
+gp <- ggplotly(country_hdi_plot, tooltip = "text")
+gp %>% 
+  layout(
+    margin = list(t = 40, r = 20, b = 60, l = 30),
+    width = 970,
+    height = 830
+  )
+```
+
+#### Table
+
+```{r}
+country_hdi_coefs %>% 
+  filter(country == "World") %>% 
+  mutate(
+    across(
+      c(mean, q2.5, q97.5), ~percent(./1000, .001)
+    )
+  ) %>% 
+  kbl(caption = "Estimated world associations with .1 increase in HDI") %>% 
+  kable_custom()
+```
+
+:::
+
+```{r some-quick-lme-models, eval = FALSE}
+itu_tmp <- itu %>% 
+  group_by(country) %>% 
+  mutate(
+    i_cw = internet - mean(internet, na.rm = TRUE),
+    m_cw = mobile - mean(mobile, na.rm = TRUE),
+    h_cw = hdi - mean(hdi, na.rm = TRUE)
+  ) %>% 
+  mutate(year = (year-2010)/10)
+
+tmp <- dat %>% 
+  group_by(country, year, outcome) %>% 
+  summarise(val = mean(val, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  left_join(itu_tmp)
+
+predictors <- c(
+  "internet", "mobile", "hdi",
+  "i_cw", "m_cw", "h_cw",
+  "i1_cw", "m1_cw", "h1_cw"
+)
+
+lmer2 <- memoise(lmer, cache = cd)
+out <- fits %>% 
+  crossing(
+    x = predictors
+  ) %>% 
+  mutate(
+    frm = str_glue(
+      "val ~ {x} + year + ({x} + year | country)"
+    )
+  ) %>% 
+  mutate(
+    fit = map2(
+      frm, outcome, 
+      ~lmer2(.x, data = tmp %>% filter(outcome == .y))
+    )
+  )
+
+lme_pars <- out %>% 
+  mutate(
+    fixef = map(
+      fit,
+      ~tidy(.x, effects = "fixed", conf.int = TRUE)
+    ),
+    coef_country = map(
+      fit,
+      ~coef(.x)$country %>% 
+        rownames_to_column("country") %>% 
+        pivot_longer(-country, names_to = "term", values_to = "estimate")
+    )
+  ) %>% 
+  mutate(
+    x = factor(
+      x,
+      levels = predictors
+    )
+  ) %>% 
+  select(-fit)
+
+lme_pars %>%
+  select(-coef_country) %>% 
+  unnest(fixef) %>% 
+  filter(!(term %in% c("(Intercept)", "year"))) %>% 
+  ggplot(aes(estimate, x)) +
+  scale_y_discrete("Predictor", limits = rev) +
+  scale_x_continuous(
+    "Conditional effect of 10% change in predictor",
+    breaks = extended_breaks(),
+    # Visualize conditional effect of 10% change on x
+    # Modelled (0-100), change to proportion so percentage is correct
+    labels = ~percent(./1000)
+  ) +
+  geom_vline(xintercept = 0, lty = 2, size = .25) +
+  geom_pointrangeh(
+    aes(xmin = conf.low, xmax = conf.high),
+    # position = position_dodge2v(.25),
+    fatten = 3
+  ) +
+  facet_wrap("outcome", scales = "free_x", nrow = 2)
+
+last_plot() +
+  geom_point(
+    data = lme_pars %>% 
+      select(-fixef) %>% 
+      unnest(coef_country) %>% 
+      filter(!(term %in% c("(Intercept)", "year"))),
+    size = .5, alpha = .5, shape = 1, col = "grey60",
+    position = position_jitter(height = .15)
+  )
+```
+
+```{r }
+benchmarks <- lme_pars %>% 
+  select(outcome, fixef) %>% 
+  unnest(fixef) %>% 
+  filter(term == "h1_cw") %>% 
+  transmute(
+    outcome,
+    benchmark = estimate/10  # Association with .1 change in HDI
+  )
+
+x <- readRDS("models-small/brm-Positive_experiences-3.rds")
+fits
+as_draws_df(x, variable = "^b_[i|m]1_cw$", regex = TRUE)
+tmp <- benchmarks %>% 
+  mutate(
+    est = map(
+      outcome, 
+      ~as_draws_df(
+        readRDS(str_glue("models-small/brm-{.x}-3.rds")),
+        variable = "^b_i1_cw$", regex = TRUE
+      ) %>% tibble()
+    )
+  ) %>% 
+  unnest(est)
+ggplot(aes(b_i1_cw, outcome)) +
+  geom_vline(xintercept = 0, lty = 2, size = .25) +
+  geom_vline(aes(xintercept = benchmark)) +
+  stat_halfeye(
+    normalize = "xy"
+  ) +
+  facet_wrap("outcome", scales = "free", nrow = 1)
+
+library(bayestestR)
+bayestestR::p_significance()
+
+tmp %>% 
+  group_by(outcome) %>% 
+  mutate(
+    m = map_dbl(
+      est,
+      ~mean(pull(.x, 1))
+    ),
+    p_rope = map2_dbl(
+      benchmark, est,
+      ~p_rope(
+        as.numeric(pull(.y, 1)), 
+        range = c(-abs(.x), abs(.x))
+      )$p_ROPE
+    )
+  )
+```

### 2022-06-30 05-supp.Rmd
wip 2022-06-30

--- 2022-05-04 02-controls.Rmd
@@
-# Control analyses
+# Supplemental analyses
+
+```{r setup, include = FALSE}
+library(lubridate)
+library(scales)
+library(broom)
+library(patchwork)
+library(spData)
+library(tmap)
+library(countrycode)
+library(ggtext)
+library(janitor)
+library(kableExtra)
+library(ggstance)
+library(ggh4x)
+library(mgcv)
+library(tidyverse)
+
+source("_common.R")
+
+dat <- readRDS("data/data-all.rds")
+itu <- read_rds("data/itu.rds")
+```
+
+## Control analyses
 
@@
 
+# Common options
+source("_common.R")
+
 cd <- cache_disk("memoise_cache", max_size = Inf)
@@
 
-dat <- readRDS("data/data-all.rds")
 ```
@@
 
-## Human development index
+### Human development index
 
 ```{r}
-itu <- read_rds("data/itu.rds")
 itu %>%
@@
   scale_y_continuous(
-    "Value",
+    "Human Development Index",
     labels = ~percent(., .1),
@@
     panel.spacing.x = unit(4, "pt"),
-    panel.spacing.y = unit(6, "pt"),
-    axis.title.y = element_blank()
+    panel.spacing.y = unit(6, "pt")
   )
@@
 
-### Between-country associations
+#### Between-country associations
 
@@
 
-### Within-country associations
+#### Within-country associations
 
@@
 ```
+
+## Maps
+
+```{r}
+itu <- read_rds("data/itu.rds") %>%
+  select(
+    region, country, year,
+    Internet = internet,
+    Mobile = mobile
+  ) %>%
+  pivot_longer(
+    c(Internet, Mobile),
+    names_to = "outcome", values_to = "val"
+  )
+
+d <- bind_rows(
+  read_rds("data/gwp.rds"),
+  read_rds("data/gbd.rds"),
+  itu
+)
+```
+
+Average well being and internet in each country
+
+```{r}
+x <- d %>% 
+  mutate(outcome = if_else(str_detect(outcome, "_"), "Well-being", outcome)) %>% 
+  filter(outcome %in% c("Well-being", "Internet")) %>% 
+  group_by(outcome, country) %>% 
+  summarise(val = mean(val, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = outcome, values_from = val)
+
+map_internet <- world %>% 
+  mutate(country = countryname(name_long)) %>% 
+  inner_join(x) %>% 
+  tm_shape() +
+  tm_borders(lwd = .15)
+
+tmap_mode(mode = "view")
+pa <- map_internet +
+  tm_fill(
+    col = "Internet", 
+    palette = "viridis", 
+    style = "cont", 
+    legend.reverse = TRUE
+    )
+pb <- map_internet +
+  tm_fill(
+    col = "Well-being", 
+    palette = "viridis", 
+    style = "cont", 
+    legend.reverse = TRUE
+    )
+tmap_arrange(pa, pb, sync = TRUE)
+```
+
+## GBD metrics
+
+While the Gallup data are (intended to be) representative of each country & year, there is more uncertainty in the GBD data.
+The latter are meta-analytic estimates produced by the IHME and as such can be inaccurate in some locations and or/years.
+Here, we compare the GBD self-harm indicator to CDC's self-injury data from <https://wisqars.cdc.gov>.
+
+```{r}
+# Load data sets
+gbd <- read_rds("data/gbd.rds") %>% 
+  filter(country == "US", outcome == "Selfharm") %>% 
+  group_by(year, age) %>% 
+  summarise(val = mean(val), se = mean(se)) %>% 
+  filter(year > 2001)
+
+cdc <- read_csv("data-raw/CDC/wisqars.csv") %>% 
+  clean_names()
+cdc <- cdc %>% 
+  mutate(
+    val = as.numeric(injuries) / as.numeric(population),
+    se = as.numeric(standard_error) / as.numeric(population)
+  ) %>% 
+  select(
+    year, 
+    age = age_group,
+    val, se
+  ) %>% 
+  mutate(
+    age = str_replace(age, "-", " to ")
+  )
+```
+
+```{r}
+bind_rows(
+  "IHME" = gbd,
+  "CDC" = cdc,
+  .id = "Source"
+) %>% 
+  drop_na(val) %>% 
+  ggplot(aes(year, val, col = Source, fill = Source, group = Source)) +
+  scale_y_continuous(
+    "Rate",
+    labels = ~percent(., .01),
+    breaks = extended_breaks(5)
+  ) +
+  geom_ribbon(aes(ymin = val - se, ymax = val + se), col = NA, alpha = .2) +
+  geom_line() +
+  facet_wrap("age", ncol = 8) +
+  theme(
+    legend.position = "bottom",
+    axis.title.x = element_blank()
+  )
+```

### 2022-07-05 01-models.Rmd
Fix model equations

@@
 &(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
-&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
-&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i \\
-&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i \\
+&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
+&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
+&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + \\
+&\alpha_6 \text{Internet}^{\text{t-1[CB]}}_i
+\\
 \pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
@@
 Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions).
+$\text{Internet}^{\text{t-1[CB]}}_i$ are the between-country centered values.
 

### 2022-07-05 models.R
Use $DATA on HPC

@@ -31,6 +31,14 @@ hmc <- list(
 # Create directory for intermediate files
 dir.create("models", FALSE)
 
+# Save models to $DATA on HPC
+path <- Sys.getenv("DATA")
+path <- ifelse(
+  path == "",
+  "models",
+  Sys.getenv("DATA")
+)
+
 # Load data
 dat <- readRDS("data/data-all.rds")
 

### 2022-07-05 models.R
Use $DATA on HPC

@@ -31,6 +31,14 @@ hmc <- list(
 # Create directory for intermediate files
 dir.create("models", FALSE)
 
+# Save models to $DATA on HPC
+path <- Sys.getenv("DATA")
+path <- ifelse(
+  path == "",
+  "models",
+  Sys.getenv("DATA")
+)
+
 # Load data
 dat <- readRDS("data/data-all.rds")
 
@@ -139,7 +147,7 @@ fits <- fits %>%
 
 hmc$data <- fits$data[[cmdargs]]
 hmc$formula <- fits$bfrm[[cmdargs]]
-hmc$file <- str_glue("models/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
+hmc$file <- str_glue("{path}/brm-{fits$outcome[[cmdargs]]}-{fits$model[[cmdargs]]}")
 
 cat("\n\nNow fitting", hmc$file, "\n\n")
 

### 2022-07-05 models.R
More hmc iterations

@@ -21,8 +21,8 @@ hmc <- list(
   chains = nchains,
   cores = nchains,
   threads = min(ncores %/% nchains, 3),
-  iter = 2500,
-  warmup = 1250,
+  iter = 4000,
+  warmup = 2000,
   refresh = 100,
   adapt_delta = .95,
   max_treedepth = 10

### 2022-07-07 models.R
Take out dumb model

@@ -113,19 +113,8 @@ bf_4 <- bf(
 )
 bf_4.s <- update(bf_4, ~ . -((year + m1_cw) * sex | age:country))
 
-# Univariate outcome on time and hdi
-bf_5 <- bf(
-  val | se(se, sigma = TRUE) ~
-    (year + h1_cw) * sex + h1_cb +
-    ((year + h1_cw) * sex | country) +
-    ((year + h1_cw) * sex | age) +
-    ((year + h1_cw) * sex | age:country),
-  family = gaussian()
-)
-bf_5.s <- update(bf_5, ~ . -((year + h1_cw) * sex | age:country))
-
 fits <- fits %>%
-  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4, bf_5), model = 1:5))
+  crossing(nesting(bfrm = list(bf_1, bf_2, bf_3, bf_4), model = 1:4))
 
 # Simplify models for mental health outcomes
 MH <- c("Anxiety", "Depression", "Selfharm")
@@ -136,7 +125,6 @@ fits <- fits %>%
       outcome %in% MH & model == 2 ~ list(bf_2.s),
       outcome %in% MH & model == 3 ~ list(bf_3.s),
       outcome %in% MH & model == 4 ~ list(bf_4.s),
-      outcome %in% MH & model == 5 ~ list(bf_5.s),
       TRUE ~ bfrm
     )
   ) %>%

### 2022-07-12 Analysis.qmd
Move everything to 1 file

---
title: Global mental health and well-being in the internet age
description: | 
  Online analysis supplement to "Global mental health and well-being in the internet age (Vuorre & Przybylski, 2022)"
author:
  - name: Matti Vuorre
    affiliation: University of Oxford
    affiliation-url: https://www.oii.ox.ac.uk/people/matti-vuorre/
    orcid_id: 0000-0001-5052-066X
citation:
  url: https://github.com/digital-wellbeing/global-wbmh/
date: 2022-07-06
toc: true
toc-depth: 2
toc-location: left
number-sections: true
format:
  html:
    code-fold: true
    code-summary: "Show the code"
    html-math-method: katex
    theme: pulse
    anchor-sections: true
    self-contained: true
    self-contained-math: false
editor_options: 
  chunk_output_type: inline
---

# Preface

Welcome! This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [submitted]()). It contains all the analyses reported in the manuscript along with supplemental figures and data. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

## How to reproduce our results

The analyses were conducted in R, and can be reproduced locally:

1. Clone the [github repo](https://github.com/digital-wellbeing/global-wbmh)
  - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
      OR
  - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2. Prepare the R environment
  - Terminal: `Rscript -e "renv::restore()"`  
      OR
  - RStudio: Click renv -> Restore Library in the Packages panel

3. Render the Quarto source file `Analysis.qmd`
 - Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
  - Terminal: `quarto render Analysis.qmd`  
      OR
  - RStudio: Open the file and click Render

If you encounter problems, please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).

::: {.callout-important}
The project repo includes the GBD dataset, code to download the ITU dataset, and a synthetic mock version of the GWP dataset to enable reproducing all our computations.
**The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason, the build will fail after having cleaned the data. Then, run `models.R` with settings specific to your environment/cluster. Once that is done you can render the document again and it should work.
:::

# Data preparation

```{r setup, include = FALSE}
#| cache: false
#| results: hide
#| message: false
# Packages
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(ragg)
library(khroma)
library(labelled)
library(countrycode)
library(plotly)
library(lubridate)
library(kableExtra)
library(brms)
library(knitr)
library(here)
library(posterior)
library(bayestestR)
library(gtsummary)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(ggstance)
library(tidybayes)
library(ggdist)
library(DT)
library(tidyverse)

# For tables: Show NAs as blanks
options(knitr.kable.NA = '')

# Data frame for computing over models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

# Create directory for intermediate files
dir.create(here("data"), FALSE)

# Cache for memoised functions
cd <- cache_disk("cache", max_size = Inf)

# Plotting options
# If you've defined a custom font, we will use it in outputs
Font <- Sys.getenv("FONT")
theme_set(
  theme_linedraw(
    base_size = 9,
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.75))
    )
)

# Width of figures
W <- 9

# Output chunk options
opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE, 
  dpi = 300
)

#' Custom kableExtra formatting
#'
#' @param a table from kbl()
#'
#' @return a table
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = Font,
    font_size = 13,
    position = "center",
    full_width = FALSE
  )
}
```

In this first section, we load the raw data sets and prepare them for analyses.

## Gallup World Poll

We first prepare the Gallup data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021.

Note that this data set is not publicly available, and therefore not included in our repository. We provide a synthetic mock dataset for researchers who would like to reproduce our analyses but do not have access to the GWP dataset. That mock dataset is automatically loaded with a confirmation message below if this analysis is run without access to the actual GWP data.

```{r gallup-codebook}
#| echo: false
#| eval: false
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_101521.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) %>%
  generate_dictionary()
```

Here we import the relevant variables from Gallup's SPSS files and then

-   Clean the variable names
-   Set appropriate missing values (`NaN`, not e.g. `-99`)
-   Use appropriate coding schemes (e.g. 0: no; 1: yes)
-   Calculate scale scores (means over items)
-   Rescale outcomes to proportions (0 - 1)
-   Create age categories in line with GBD data
-   Aggregate data to means and SEs at each country * year * age * sex group
-   Drop one 13 year old as this data should only have people 15 and older
-   Exclude people older than 89

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- here("data-raw/Gallup/gwp-processed.rds")
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    here("data-raw/Gallup/The_Gallup_101521.sav"),
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

  # Get rid of SPSS attributes
  gwp <- gwp %>%
    zap_labels() %>%
    zap_label() %>%
    zap_widths() %>%
    zap_formats()

  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}

# Rename and recode variables
gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

# Scale scores note rescaling
gwp <- gwp %>%
  mutate(
    Life_satisfaction = Life_satisfaction / 10,
    Negative_experiences =
      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
    Positive_experiences =
      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
  ) %>%
  select(-c(wp60:wp74))

# Categorize ages
gwp <- filter(gwp, age <= 89)
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 90, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Some sex values are missing, drop those
gwp <- drop_na(gwp, sex)
```

Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex). Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
gwp <- gwp %>% 
  mutate(
    se = if_else(is.na(se) | se == 0, 0.5, se)
  )
```

We have multiple data sets with information on countries. Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. We do that here for the GWP data, and check that all countries receive a unique name.

```{r gwp-harmonise-countries}
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing and therefore the original name is retained."

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()

# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising

# Harmonise old names and replace only if harmonised name found
gwp <- gwp %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) %>%
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### Synthetic GWP data

If the real GWP data was not available above, here we load the synthetic dataset (having first created it).

```{r mock-gwp-data}
gwp_mock_path <- here("data-raw/gwp-MOCK.rds")
if (dir.exists(here("data-raw/Gallup")) & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp %>% 
    drop_na()
  gwp_syn <- syn(
    gwp_syn, 
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  gwp_syn <- tibble(gwp_syn$syn)
  saveRDS(gwp_syn, gwp_mock_path)
}

# Load if actual data doesn't exist
if (!dir.exists(here("data-raw/Gallup"))) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

## Global Burden of Disease

The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019.

We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/). They are inside downloaded `.zip` files, of which there may be more than one (depending on the download size). Here, we load those tables to R.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  here("data-raw/GBD/"),
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>%
  read_csv()
```

We then clean the GBD data and

-   Clean the variable names
-   Remove the metric and measure variables; we focus on prevalence rate
    -   prevalence: Total number of cases
    -   rate: Total cases per 100,000 population
-   Convert outcome rates to proportions (0 - 1)
-   Clean cause names and rename to outcome to harmonise with GWP
-   Convert GBD estimated rate CI limits to an approximate standard error

```{r gbd-data-clean}
# First step is to clean names
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>%
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>%
  rename(country = location, outcome = cause)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
#| label: tbl-gbd-countries
#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

## International Telecommunication Union

After processing the outcome tables above, we move on to the internet adoption metrics from the ITU. The International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.

We downloaded the data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.

After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1). Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "Countries whose original ITU name is different to the harmonised one, or whose harmonised name is missing"

# Download data sets from the ITU website if not yet downloaded
if (!file.exists(here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"))) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/PercentIndividualsUsingInternet.xlsx",
    here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/FixedBroadbandSubscriptions_2000-2020.xlsx",
    here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx")
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/MobileBroadbandSubscriptions_2007-2020.xlsx",
    here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx")
  )
}

# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"),
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(fixed = as.numeric(value)) %>%
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"),
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(mobile = as.numeric(value)) %>%
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"),
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(internet = as.numeric(value)) %>%
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>%
  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()

# Harmonise old names and replace only if harmonised name found
itu <- itu %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

# Drop countries that don't exist in outcomes
itu <- itu %>%
  filter(
    country %in% unique(gbd$country) | country %in% unique(gwp$country)
  )

# Drop countries that don't have any actual internet data
itu_zeros <- itu %>%
  group_by(country) %>%
  summarise(s = sum(internet, na.rm = TRUE)) %>%
  filter(s == 0)

itu <- itu %>%
  filter(!(country %in% itu_zeros$country))
rm(itu_zeros)
```

### Missingness

We then impute missing intermediate values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.

```{r itu-impute}
#| results: hold
#| label: tbl-itu-impute
#| tbl-cap: "Summary of ITU data imputation"

# Reshape to easily impute all variables
itu_long <- itu %>%
  pivot_longer(c(internet, mobile))

# Impute by country and variable
itu_long <- itu_long %>%
  group_by(country, name) %>%
  # Find first and last year with this variable in each country
  # so as to prevent extrapolation
  mutate(
    min_year = year[min(which(!is.na(value)))],
    max_year = year[max(which(!is.na(value)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  mutate(
    across(
      value,
      .fns = list(
        i = possibly(
          function(x) na_interpolation(x, maxgap = Inf),
          otherwise = NaN
        )
      )
    )
  ) %>%
  # Take out projected (non-intermediate) imputed values
  mutate(
    value_i = if_else(
      between(year, unique(min_year), unique(max_year)),
      value_i,
      NaN
    )
  ) %>%
  ungroup() %>%
  select(-min_year, -max_year)

# Summary
itu_long %>%
  group_by(name) %>%
  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
  summarise(
    n_miss_orig = sum(is.na(value) & year >= min_year),
    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
    n_miss_imp = sum(is.na(value_i) & year >= min_year),
    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
    imputed = n_miss_orig - n_miss_imp
  ) %>%
  kbl() %>%
  kable_custom()

# We then replace the original values with the imputed ones
itu <- itu_long %>%
  # Pick non-missing value, from original and imputed
  mutate(value = coalesce(value, value_i)) %>%
  select(-value_i) %>%
  pivot_wider()
rm(itu_long)
```

## Regions

We also include a `region` variable in the data ("Continent as defined in the World Bank Development Indicators") to allow grouping countries in figures and outputs.

```{r}
#| label: tbl-regions
#| tbl-cap: "Countries in each region."

regions <- bind_rows(
  distinct(itu, country),
  distinct(gbd, country),
  distinct(gwp, country)
) %>% 
  distinct() %>% 
  mutate(
    region = countrycode(
      country, 
      origin = "country.name", 
      destination = "continent"
    )
  )

# Manually fix two countries
regions <- regions %>% 
  mutate(
    region = if_else(country == "Kosovo", "Europe", region),
    region = if_else(country == "Nagorno Karabakh", "Asia", region)
    )

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)

regions %>% 
  group_by(region) %>%
  summarise(
    N = n(),
    Countries = str_c(country, collapse = ", ")
  ) %>% 
  kbl() %>% 
  kable_custom()
```

## Prepare model data

We then further wrangle this data in preparation for the models:

-   Combine all predictors into one table
-   Create lagged and centered predictors
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle) and divide by ten ("effect" of decades)

```{r model-prepare-data}
# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>%
  group_by(region, country) %>%
  mutate(
    across(
      c(internet, mobile),
      list(`1` = ~ lag(., 1)),
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  ) %>% 
  ungroup()

# Centering predictors within and between countries
itu <- itu %>%
  # Grand mean centering so both components are zero-centered
  mutate(across(c(i1, m1), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    i1_cb = mean(i1, na.rm = TRUE),
    m1_cb = mean(m1, na.rm = TRUE),
    # Within
    i1_cw = i1 - i1_cb, 
    m1_cw = m1 - m1_cb
  ) %>% 
  ungroup()

# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center and scale year
dat <- dat %>%
  mutate(year = (year - 2010) / 10)

# Identify values to use in MV models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1, itum = 1:n() == 1) %>%
  ungroup()

# This prevents a glitch where rows where ITU==TRUE but internet is missing would not be included in model of val
dat <- dat %>% 
  mutate(
    itu = if_else(itu & is.na(internet), FALSE, itu),
    itum = if_else(itum & is.na(mobile), FALSE, itum)
    )

# Ensure that categorical variables are factors
dat <- dat %>%
  mutate(across(c(sex, age), factor))

# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
dat <- dat %>%
  mutate(across(c(val, se), ~ . * 100))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome, country, region, year)

# Selfharm models don't converge with SEs
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))
```

# Data description

Here are some descriptives of the datasets.

## Sample summaries

Number of countries/years/people per outcome

```{r}
#| label: tbl-data-n
#| tbl-cap: "Numbers of respondents and years per outcome and region."

bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl() %>% 
  kable_custom()
tmp <- gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n))) %>% 
  pull(N)
```

The median number of respondents per Gallup well-being outcome was `r tmp`, and the unique age bins in the GWP data were `r unique(gwp$age)`.

We then examined the total number of observations (cell means and SEs) per outcome

```{r}
#| label: tbl-obs-per-outcome
#| tbl-cap: "Numbers of observations per outcome."
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  bind_rows(
    itu %>% 
      select(internet, mobile) %>% 
      pivot_longer(everything(), names_to = "outcome") %>% 
      drop_na(value) %>% 
      count(outcome) %>% 
      mutate(Dataset = "ITU")
  ) %>% 
  kbl() %>% 
  kable_custom()
```

And noted that the number of Gallup respondents decreases with age:

```{r}
#| label: tbl-gallup-age
#| tbl-cap: "Quantiles of numbers of observations per age group"

gwp %>% 
  # filter(age %in% c("15 to 19", "50 to 54", "85 to 89")) %>% 
  group_by(age) %>% 
  summarise(
    n = quantile(n, probs = c(.1, .5, .9)),
    quantile = c("10%", "50%", "90%")
  ) %>% 
  pivot_wider(names_from = quantile, values_from = n) %>% 
  kbl() %>% 
  kable_custom()
```

## ITU summary table

Here is a table summarising the ITU internet predictor over time to region average percentage and number of coutries.

```{r itu-summary-table}
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

itu %>%
  select(region, country, year, internet) %>%
  mutate(internet = internet * 100) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra() %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

## Figure 1

This figure shows the timeseries of each country's key variables (aggregated over sex and age for outcomes).

:::{.panel-tabset .column-body-outset-right}

### Static

```{r figure-1, message = FALSE}
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Trends in all variables across regions"
#| label: fig-1

# Stack data sets
# Assume all outcomes are proportions (0-1)
# Draw small multiples figure, outcomes x regions
d <- bind_rows(
  gwp,
  gbd
)

itu <- itu %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile,
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

p1 <- bind_rows(itu, d) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value (%)",
    # Display percentages
    labels = ~. * 100,
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = interaction(country, outcome), 
      text = str_glue("{country} {year(year)} ({percent(mean)})")
    ),
    size = .25, col = "gray20"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    # aspect.ratio = 1,
    legend.position = "none",
    panel.spacing.x = unit(4, "pt"),
    panel.spacing.y = unit(6, "pt")
  )
p1
```

### Interactive

```{r}
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Trends in all variables across regions (interactive)"
#| label: fig-trends-regions-interactive

gp <- ggplotly(p1, tooltip = "text")
gp %>% 
  layout(
    margin = list(t = 30, r = 20, b = 40, l = 30)
    )
```

:::

# Models

Here we discuss the models. The code for estimating these models is in `models.R`. We submit that to our local HPC with SLURM scheduler with `submit.sh`.

## Model 1

Model 1 is a two-level probabilistic multivariate meta-regression model that simultaneously predicts the health (e.g. Life satisfaction) and internet variables (e.g. internet adoption) from time, sex, and time by sex interactions. These regression coefficients are modelled as multivariate normal distributed over countries, age groups, and the country by age groups. The latter clustering was dropped from the mental health variables because of nonconvergence due to lack of variance in data ($\Sigma^\text{age:country} = 0$). The country-level covariance matrices are shared across the two outcomes so we can assess correlations between countries' intercepts and slopes over the two outcomes.

Because we are modelling meta-analytic estimates (GBD) and aggregated scores (GWP), we also incorporate the aggregates' standard errors in the model to weight the observations on their corresponding uncertainties. Due to nonconvergence, we set the SEs to zero for self-harm ($v = 0$).

$$
\begin{align}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{y2}v_i) \\
x_i &\sim \text{Normal}(\mu^x_i, \sigma^{x2}) \\ 
\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{country}[i]} + \gamma^{y}_{0\text{age}[i]} + \delta^{y}_{0\text{age:country}[i]} + \\ 
&(\alpha^{y}_{1} + \beta^{y}_{1\text{country}[i]} + \gamma^{y}_{1\text{age}[i]} + \delta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha^{y}_{2} + \beta^{y}_{2\text{country}[i]} + \gamma^{y}_{2\text{age}[i]} + \delta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha^{y}_{3} + \beta^{y}_{3\text{country}[i]} + \gamma^{y}_{3\text{age}[i]} + \delta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
\mu^x_i &= \alpha^{x}_{0} + \beta^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{country}[i]})\text{Time}_i \\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model1}

## Model 2

Model 2 was similar to Model 1, but the internet outcome was dropped, and the regression equation for outcomes expanded to include the lagged internet predictor and its two-way interactions

$$
\begin{align}
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\ 
&(\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&(\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&(\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&(\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
&(\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + \\
&\alpha_6 \text{Internet}^{\text{t-1[CB]}}_i
\\
\pmb{\beta} &\sim MVN(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim MVN(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim MVN(\pmb{0}, \Sigma^\text{age:country})
\end{align}
$$ {#eq-model2}

Where $\text{Internet}^{\text{t-1}}_i$ is the within-country centered 1-year-lagged internet user proportion (or mobile subscriptions). $\text{Internet}^{\text{t-1[CB]}}_i$ are the between-country centered values.

## Model checking and parameters

Next, we display the population-level parameters of each model, along with their numerical HMC diagnostics (ESS and Rhat values).

```{r}
# Create a table of outcomes in appropriate order, so can map functions over this
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = fct_inorder(outcome))

# The files are huge and unwieldy to work with. We create smaller files for each by dropping samples of the age:country interaction random effects. It is then easier to post-process the models.
dir.create("models-small", FALSE)

replace_chain <- function(x) {
  x %>%
    select(
      -starts_with("r_1"),
      -starts_with("r_2"),
      -starts_with("r_3"),
      -starts_with("z_1"),
      -starts_with("z_2"),
      -starts_with("z_3"),
      -starts_with("r_age:country"),
      -starts_with("L_")
    )
}

replace_chain_all <- function(x) {
  if (!file.exists(str_glue("models-small/{x}"))) {
    message(x)
    out <- readRDS(str_glue("models/{x}"))
    out$fit@sim$samples <- map(1:4, ~replace_chain(out$fit@sim$samples[[.]]))
    saveRDS(out, str_glue("models-small/{x}"), compress = FALSE)
  }
}

walk(
  list.files("models"),
  ~replace_chain_all(.x)
)
```

### Diagnostics

Here we take a look at model convergence using numerical summaries (rhat) and scatterplot matrices of posterior draws.

```{r model-diagnostics}
#| label: tbl-rhats
#| tbl-cap: "Numerical convergence diagnostics for parameters with suspicious rhats."

parameter_summary <- function(outcome, model) {
  path <- str_glue("models-small/brm-{outcome}-{model}.rds")
  as_draws_df(
    readRDS(path), 
    variable = c("^b_", "^sd_", "^cor_"), 
    regex = TRUE
  ) %>%
    summarise_draws(
      mean, sd,
      samples = length, 
      default_convergence_measures()
    )
}
parameter_summary <- memoise(parameter_summary, cache = cd)

convergence_summary <- tibble(
  path = list.files("models-small/", pattern = ".rds$", full.names = FALSE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
  unnest(parameters)

convergence_summary %>% 
  filter(abs(rhat) > 1.03) %>% 
  arrange(outcome, model, variable) %>% 
  kbl(digits = c(rep(2, 7), 0, 0)) %>% 
  kable_custom()
```

For each model, we then draw a scatterplot matrix of parameters with worst rhats. Browse these figures at `figures/diagnostics/`.

```{r ppcheck-scatter}
#| eval: !expr file.exists("figures/diagnostics/brm-Anxiety-1.png")*-1

# Function to draw a pairsplot of variables `v` of model in `path` 
dir.create(here("figures/diagnostics"), FALSE)
pairsplot <- function(filename, v) {
  out_path <- here(str_glue("figures/diagnostics/{basename(filename)}.png"))
  if (!file.exists(out_path)) {
    x <- readRDS(here(filename))
    agg_png(
      out_path,
      width = W*1.2, height = W*1.2, units = "in", res = 160
    )
    pairs(x$fit, pars = v)
    title(sub = out_path)
    dev.off()
  }
}

# Draw pairsplot for 10 worst rhats per model
convergence_summary %>% 
  group_by(outcome, model) %>% 
  arrange(outcome, model, desc(rhat)) %>% 
  slice(1:10) %>% 
  ungroup() %>% 
  group_by(outcome, model) %>% 
  summarise(v = list(variable)) %>% 
  mutate(path = str_glue("models-small/brm-{outcome}-{model}.rds")) %>% 
  ungroup() %>% 
  {walk2(.$path, .$v, ~pairsplot(.x, .y))}
```

We determined that, although a handful of parameters had slightly suspicious rhats, the chains had converged well and the HMC outputs are reliable, because the scatterplots checked out well.

# Results

The main results of the study are calculated and presented here.

```{r}
# Before drawing any plots, we need to extract/compute the relevant parameters from the models. We do that here: For each outcome, we get the countries' average changes over time (in the outcome, internet, and mobile) and associations with internet and mobile
country_post_fun <- function(outcome) {

  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
  fit2 <- readRDS(str_glue("models-small/brm-{outcome}-2.rds"))
  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))

  out_outcome_year <- spread_draws(
    fit1,
    b_val_year, r_country__val[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_val_year) %>% 
    mutate(y = "outcome")

  out_internet_year <- spread_draws(
    fit1,
    b_internet_year, r_country__internet[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_internet_year) %>% 
    mutate(y = "Internet")

  out_mobile_year <- spread_draws(
    fit2,
    b_mobile_year, r_country__mobile[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_mobile_year) %>% 
    mutate(y = "Mobile")

  out_outcome_internet <- spread_draws(
    fit3,
    b_i1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "i1_cw") %>% 
    ungroup() %>% 
    rename(World = b_i1_cw) %>% 
    mutate(y = "outcome")

  out_outcome_mobile <- spread_draws(
    fit4,
    b_m1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "m1_cw") %>% 
    ungroup() %>% 
    rename(World = b_m1_cw) %>% 
    mutate(y = "outcome")

  out <- bind_rows(
    out_outcome_year, 
    out_internet_year,
    out_mobile_year,
    out_outcome_internet,
    out_outcome_mobile
  ) %>%  
    select(x, y, everything(), -c(.chain, .iteration, .draw)) %>% 
    # Add average to all but itself
    mutate(across(-c(x, y, World), ~. + World)) %>% 
    rename_with(~str_replace_all(., "\\.(?!\\.)", " ")) %>% 
    mutate(
      x = factor(
        x, 
        levels = c("year", "i1_cw", "m1_cw"),
        labels = c("Time", "Internet", "Mobile")
      )
    )

  out 
}
country_post_fun <- memoise(country_post_fun, cache = cd)
country_post <- fits %>% 
  mutate(
    samples = map(outcome, country_post_fun),
    summary = map(
      samples, 
      ~.x %>% 
        group_by(x, y) %>% 
        summarise_draws(
          mean, 
          ~quantile2(., probs = c(.025, .975)),
          pd = ~pd(as.numeric(.))
        ) %>% 
        rename(country = variable)
    )
  )

# Create scaling factors for decade-equivalent associations
# There is a different scaling factor for each outcome,
# even though they used the same internet/mobile values. That's because 
# different countries were included by outcome, and its then most faithful
# to the data to keep these separate by outcome.
# Get each country's Time -> Predictor parameters
scaling_factors <- country_post %>% 
  select(outcome, summary) %>% 
  unnest(summary) %>% 
  filter(x == "Time", y != "outcome") %>% 
  select(outcome, y, country, scaling = mean)

# Find changes per decade per outcome for ROPE limits
change_factors <- country_post %>% 
  select(outcome, summary) %>% 
  unnest(summary) %>% 
  filter(x == "Time", y == "outcome") %>% 
  select(outcome, country, change = mean)

# Calculate sign and ROPE tests for time/internet/mobile -> outcomes
summarise_all <- function(
    posterior = country_post,
    scaling_factors = scaling_factors,
    change_factors = change_factors
) {

  # Posterior samples of all effects on outcomes
  tab <- posterior %>% 
    select(outcome, samples) %>% 
    unnest(samples) %>% 
    filter(y == "outcome") %>%
    select(-y) %>%
    pivot_longer(-c(outcome, x), names_to = "country") %>% 
    # Drop NAs because some country-outcome combinations don't exist
    drop_na(value) %>% 
    # We will have raw and scaled results
    rename(raw = value)

  # Scale internet and mobile to decade-equivalents
  tab <- tab %>% 
    left_join(
      scaling_factors %>% 
        rename(x = y)
    ) %>% 
    mutate(scaling = if_else(x == "Time", 1, scaling)) %>% 
    mutate(scaled = raw * scaling) %>% 
    select(-scaling)

  # Change associations with internet and mobile to units of 10% not 100%
  tab <- tab %>% 
    mutate(
      raw = if_else(x == "Time", raw, raw / 10)
    )

  # Calculate the raw and scaled results for each outcome and predictor
  tab <- tab %>% 
    nest(data = c(raw, scaled)) %>% 
    left_join(change_factors) %>% 
    mutate(
      out = map2(
        data, change,
        ~describe_posterior(
          .x, 
          centrality = "mean", 
          ci_method = "eti",
          rope_range = c(-.y, .y), 
          rope_ci = 1
        )
      )
    ) %>% 
    transmute(
      Predictor = fct_inorder(x), 
      Outcome = fct_inorder(str_replace(outcome, "_", " ")),
      country, 
      out
    ) %>% 
    arrange(Predictor, Outcome) %>% 
    unnest(out) %>% 
    # Clean the names a bit
    rename(
      rope = ROPE_Percentage,
      mean = Mean,
      low = CI_low,
      high = CI_high
    ) %>% 
    # Put raw and scaled results on one row
    pivot_wider(
      names_from = Parameter,
      values_from = c(mean, low, high, pd, rope),
      names_glue = "{Parameter}_{.value}"
    ) %>% 
    # Leave symmetric ROPE limit in table
    mutate(rope_limit = abs(ROPE_low)) %>% 
    select(
      Predictor, 
      Outcome, 
      Country = country, 
      starts_with("raw_"), 
      starts_with("scaled_"),
      # pd is common to raw and scaled values, rope only applies to scaled values
      pd = raw_pd,
      rope = scaled_rope,
      rope_limit,
      -raw_rope, 
      -scaled_pd
    )

  # Calculate decision based on pd and rope
  tab <- tab %>% 
    mutate(
      d_nhst = case_when(
        pd < 0.975 ~ "Null",
        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
      ),
      d_rope = case_when(
        scaled_high < rope_limit*-1 ~ "Negative",
        scaled_low > rope_limit ~ "Positive",
        rope > 0.95 ~ "Null",
        TRUE ~ "Inconclusive"
      )
    )

  # Return object
  tab
}
summarise_all <- memoise(summarise_all, cache = cd)
tab <- summarise_all(country_post, scaling_factors, change_factors)
```

## Average parameters

### Table 1

This table shows the raw coefficients of the outcome variables' associations with Time (change over time), Internet, and Mobile. These are for the average country. For those associations, it displays the posterior probability of direction of the association.

It also shows the decade-equivalent associations between Internet and Mobile and each outcome. For those, it displays the posterior probability that the association is smaller than the simple association with time.

```{r}
#| label: tbl-average
#| tbl-cap: "Average parameter estimates"

# Function to replace extreme percentages
percent2 <- function(x, accuracy = .1) {
  x <- percent(x, accuracy = accuracy)
  x <- if_else(x == "100.0%", ">99.9%", x)
  x <- if_else(x == "0.0%", "<0.1%", x)
  x
}

# Then display the table
tab %>% 
  filter(Country == "World") %>% 
  # Create a result string for table
  mutate(
    raw_result = str_glue(
      "{number(raw_mean, .001)}
      [{number(raw_low, .001)}, 
      {number(raw_high, .001)}] 
      ({percent2(pd, .1)})"
    ),
    scaled_result = str_glue(
      "{number(scaled_mean, .001)} 
      [{number(scaled_low, .001)}, 
      {number(scaled_high, .001)}] 
      ({percent2(rope, .1)})"
    ),
    # ROPE doesn't make sense for change over time (it is ROPE)
    scaled_result = if_else(Predictor == "Time", "", as.character(scaled_result))
  ) %>% 
  select(
    Predictor, 
    Outcome, 
    `Raw association` = raw_result, 
    `Scaled association` = scaled_result
  ) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  kbl() %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    number = c(
      "Raw associations are percentage changes in outcomes associated with a decade (Time) or 10% (Internet & Mobile) increase in the predictor. Numbers indicate posterior means, [95%CI], and (posterior probability of direction).", 
      "Scaled associations are percentage changes in outcomes associated with per-decade change in the predictor (“decade-equivalent” association). Numbers indicate posterior means, [95%CI], and (posterior probability inside the region of practical equivalence; i.e. probability that the association is smaller than the per-decade change in the respective outcome)."
    )
  )
```

```{r include = FALSE}
# Are the sign tests and rope tests consistent?
tab %>% 
  count(d_nhst, d_rope)
tab %>% 
  filter(d_nhst == "Positive", d_rope == "Null")
country_post %>% 
  select(outcome, summary) %>% 
  unnest(summary) %>% 
  filter(country == "Bahrain", outcome == "Life_satisfaction")
```

## Heterogeneity

Next we look at the heterogeneity (deviations and correlations) of the parameters across countries, age groups, and their interactions.

### Variability

This table shows the standard deviations of the lower level parameters.

```{r}
#| label: tbl-variability
#| tbl-cap: "Heterogeneity in associations across countries, age groups, and their interaction."

get_het_pars <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
  draws <- as_draws_df(
    x,
    variable = c(
      str_glue("^b_{predictor}$"),
      str_glue("^sd_age__{predictor}$"),
      str_glue("^sd_country__{predictor}$"),
      str_glue("^sd_age:country__{predictor}$")
    ),
    regex = TRUE
  ) %>% 
    select(-c(.chain, .iteration, .draw)) %>% 
    # From 100% to 10% units for associations
    mutate(across(-contains("val_year"), ~ ./10)) %>% 
    rename_with(~str_remove(., str_glue("{predictor}")))
  draws
}

get_het_pars <- memoise(get_het_pars, cache = cd)

het_pars <- fits %>% 
  crossing(
    nesting(predictor = c("val_year", "i1_cw", "m1_cw"), model = c(1, 3, 4))
  ) %>%
  mutate(
    out = pmap(
      list(outcome, predictor, model), 
      ~get_het_pars(..1, ..2, ..3))
  )
het_tab <- het_pars %>% 
  unnest(out) %>%
  select(-model) %>% 
  rename(
    Association = b_,
    `SD (age)` = sd_age__,
    `SD (country)` = sd_country__,
    `SD (age * country)` = `sd_age:country__`,
  ) %>%
  group_by(outcome, predictor) %>% 
  summarise_draws(mean, ~quantile2(., probs = c(.025, .975))) %>% 
  ungroup() %>% 
  mutate(
    across(c(mean, q2.5, q97.5), ~number(., .001)),
    res = as.character(str_glue("{mean} [{q2.5}, {q97.5}]")),
    Outcome = str_replace(outcome, "_", " "),
    Predictor = case_when(
      predictor == "val_year" ~ "Time",
      predictor == "i1_cw" ~ "Internet",
      predictor == "m1_cw" ~ "Mobile"
    ) %>% factor(levels = c("Time", "Internet", "Mobile"))
  ) %>% 
  select(
    Predictor, Outcome, variable, res
  ) %>% 
  mutate(res = if_else(res == "NA [NA, NA]", "", res)) %>% 
  pivot_wider(names_from = variable, values_from = res) %>% 
  mutate(Outcome = fct_inorder(Outcome)) %>% 
  select(Predictor, Outcome, Association, `SD (country)`, everything()) %>% 
  arrange(Predictor, Outcome)

het_tab %>% 
  select(-Association) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  kbl() %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    general = "Numbers indicate the standard deviations [95%CI] of the distributions of associations in the population of all countries.",
    general_title = "Note. ",
    footnote_as_chunk = TRUE
  )
```

### Correlations

These are the cross-country correlations of the well-being / mental health and internet / mobile broadband adoption intercepts and slopes.

```{r}
#| label: tbl-correlations
#| tbl-cap: "Correlations between country-level parameters"

get_cor_pars <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
  as_draws_df(
    x,
    variable = c(
      str_glue("b_{predictor}_Intercept"),
      "b_val_Intercept",
      str_glue("b_{predictor}_year"),
      "b_val_year",
      str_glue("sd_country__{predictor}_Intercept"),
      "sd_country__val_Intercept",
      str_glue("sd_country__{predictor}_year"),
      "sd_country__val_year",
      str_glue("cor_country__{predictor}_year__val_year"),
      str_glue("cor_country__{predictor}_Intercept__val_Intercept")
    )
  )
}
get_cor_pars <- memoise(get_cor_pars, cache = cd)

cor_pars_brm <- fits %>%
  mutate(
    internet = map(outcome, ~get_cor_pars(.x, "internet", "1")),
    mobile = map(outcome, ~get_cor_pars(.x, "mobile", "2"))
  )

cor_sum <- cor_pars_brm %>% 
  mutate(
    across(
      internet:mobile, 
      ~map(., ~describe_posterior(., centrality = "mean", test = "pd"))
    )
  )
cor_sum %>% 
  pivot_longer(-outcome, names_to = "Predictor") %>% 
  unnest(value) %>% 
  filter(str_detect(Parameter, "cor_")) %>% 
  mutate(
    across(Mean:CI_high, ~number(., .01)), pd = percent2(pd, .1)
  ) %>% 
  transmute(
    Predictor = str_to_title(Predictor),
    Correlation = if_else(
      str_detect(Parameter, "Intercept"), "Intercepts", "Slopes"
    ),
    Outcome = str_replace(outcome, "_", " "),
    Summary = str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})")
  ) %>% 
  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
  arrange(Correlation, Outcome) %>% 
  mutate(
    Correlation = if_else(Outcome == "Life satisfaction", Correlation, "")
  ) %>% 
  kbl() %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    general = "Numbers indicate the correlations [95%CI] between the intercepts and slopes of time of the corresponding outcome and internet / mobile broadband adoption.",
    general_title = "Note. ",
    footnote_as_chunk = TRUE
  )
```

## Countries

We then look at the country-level parameters.

### Tables

This table shows the percentages of countries with credibly positive, null, and positive countries.

```{r}
#| label: tbl-countries-sign
#| tbl-cap: "Country-level association classifications."

t1 <- tab %>% 
  filter(Country != "World") %>% 
  count(Predictor, Outcome, d_nhst) %>% 
  group_by(Outcome, Predictor) %>% 
  mutate(sum = sum(n), p = n / sum) %>% 
  transmute(
    Predictor,
    Outcome,
    Decision = d_nhst,
    p = percent(p, 1)
  ) %>% 
  pivot_wider(names_from = Decision, values_from = p) %>% 
  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))

t2 <- tab %>% 
  filter(Country != "World", Predictor != "Time") %>% 
  count(Predictor, Outcome, d_rope) %>% 
  group_by(Outcome, Predictor) %>% 
  mutate(sum = sum(n), p = n / sum) %>% 
  transmute(
    Predictor,
    Outcome,
    Decision = d_rope,
    p = percent(p, 1)
  ) %>% 
  pivot_wider(names_from = Decision, values_from = p) %>% 
  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))

left_join(t1, t2, by = c("Predictor", "Outcome"), suffix = c("", " ")) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  kbl() %>% 
  add_header_above(c(" " = 2, "Sign test" = 3, "ROPE test" = 4), align = "c") %>% 
  kable_custom() %>% 
  column_spec(1, bold = TRUE) %>% 
  footnote(
    general = "Numbers may not add up to 100% because of rounding.",
    general_title = "Note. ",
    footnote_as_chunk = TRUE
  )
```

All country-specific parameters are shown in [this table](country-table.html). There, `raw_` associations indicate associations in terms of decades (Time) or 10% change in predictor (Internet & Mobile). `scaled_` associations are decade-equivalent associations (association with how many % per decade the predictor changed). `pd` is probability of direction, and `rope` is posterior probability in ROPE as defined by the outcome's per-decade change over time. `d_` indicate decisions based on direction and ROPE.

```{r}
# Save interactive table to country-table.html
tab %>% 
  mutate(
    Country = relevel(factor(Country), ref = "World"),
    d_nhst = factor(d_nhst),
    d_rope = factor(d_rope)
  ) %>% 
  datatable(filter = "top", rownames = FALSE) %>% 
  formatRound(4:12, 3) %>% 
  saveWidget("country-table.html", title = "Country-specific parameters")
```

### Figure 2

For this one, we rescale the outcome~internet and outcome~mobile associations to be in units of decade-equivalent changes of internet and mobile.

```{r figure-2}
#| label: fig-2
#| fig-cap: "Country-level estimates"

# Arrange points within panels such that the order of countries is same in the rows of each column, running from smallest time change to greatest time change. This is a rudimentary way to show correlation between the two.
tmp <- tab %>% 
  filter(Predictor == "Time", Country != "World") %>% 
  arrange(raw_mean) %>% 
  group_by(Outcome) %>% 
  mutate(x_order = 1:n()) %>% 
  select(Outcome, Country, x_order) %>% 
  ungroup()

tab %>% 
  filter(Country != "World") %>% 
  left_join(tmp) %>% 
  # Factor order for colors
  mutate(
    color_nhst = recode(d_nhst, Null = "c", Negative = "b", Positive = "b")
  ) %>% 
  ggplot(aes(x_order, scaled_mean, col = color_nhst)) +
  scale_color_brewer(palette = "Paired", direction = -1) +
  # scale_color_manual(values = c("dodgerblue3", "dodgerblue1", "dodgerblue1")) +
  scale_x_continuous("Country") +
  scale_y_continuous(
    "Estimated linear association (%)"
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_linerange(
    size = .15,
    aes(ymin = scaled_low, ymax = scaled_high)
  ) +
  geom_point(
    size = .2
  ) +
  facet_grid2(
    Predictor~Outcome, 
    scales = "free",
    independent = "all",
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    )
  ) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none"
  )
```

## Demographics

### Figure 3

```{r figure-3}
#| label: fig-3
#| fig-cap: "Demography-specific estimates"

summarise_demographics <- function(outcome) {

  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))

  out_outcome_year <- spread_draws(
    fit1, 
    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_val_year + `b_val_year:sex1`*1,
      World_Male = b_val_year + `b_val_year:sex1`*-1,
      Age_Female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
      Age_Male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    # Throws a warning for Age cells in World rows (value doesn't exist)
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " "))

  out_outcome_internet <- spread_draws(
    fit3, 
    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_i1_cw + `b_i1_cw:sex1`*1,
      World_Male = b_i1_cw + `b_i1_cw:sex1`*-1,
      Age_Female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
      Age_Male = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
    # Rescale effect to "decade-equivalent"
    bind_cols(
      scaling_factors %>% 
        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
        select(scaling)
    ) %>% 
    mutate(value = value * scaling) %>% 
    select(-scaling)

  out_outcome_mobile <- spread_draws(
    fit4, 
    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_m1_cw + `b_m1_cw:sex1`*1,
      World_Male = b_m1_cw + `b_m1_cw:sex1`*-1,
      Age_Female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
      Age_Male = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
    # Rescale effect to "decade-equivalent"
    bind_cols(
      scaling_factors %>% 
        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
        select(scaling)
    ) %>% 
    mutate(value = value * scaling) %>% 
    select(-scaling)

  out <- bind_rows(
    "Time" = out_outcome_year,
    "Internet" = out_outcome_internet,
    "Mobile" = out_outcome_mobile,
    .id = "Predictor"
  ) %>% 
    mutate(Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")))

  # Scaling factors are invariant to demography
  out <- scaling_factors %>% 
    filter(country == "World") %>% 
    filter(outcome == {{outcome}}) %>% 
    select(Predictor = y, scaling) %>% 
    right_join(out) %>% 
    mutate(scaling = if_else(Predictor == "Time", 1, scaling)) %>% 
    rename(raw = value) %>% 
    mutate(scaled = raw * scaling) %>% 
    select(-scaling)

  # Calculate demography-specific change-factors (how much outcome changed)
  change_factors <- out %>% 
    filter(Predictor == "Time") %>% 
    group_by(Level, Sex, Age) %>% 
    mean_qi(change = raw) %>% 
    select(Level, Sex, Age, change)

  # Then calculate pd and rope

  # Change associations with internet and mobile to units of 10% not 100%
  out <- out %>% 
    mutate(
      raw = if_else(Predictor == "Time", raw, raw / 10)
    )

  # Calculate the raw and scaled results for each outcome and predictor
  out <- out %>% 
    select(-.draw) %>% 
    nest(data = c(raw, scaled)) %>% 
    left_join(change_factors) %>% 
    mutate(
      out = map2(
        data, change,
        ~describe_posterior(
          .x, 
          centrality = "mean", 
          ci_method = "eti",
          rope_range = c(-.y, .y), 
          rope_ci = 1
        )
      )
    ) %>% 
    transmute(
      Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")), 
      Level, Sex, Age, out
    ) %>% 
    arrange(Predictor) %>% 
    unnest(out) %>% 
    # Clean the names a bit
    rename(
      rope = ROPE_Percentage,
      mean = Mean,
      low = CI_low,
      high = CI_high
    ) %>% 
    # Put raw and scaled results on one row
    pivot_wider(
      names_from = Parameter,
      values_from = c(mean, low, high, pd, rope),
      names_glue = "{Parameter}_{.value}"
    ) %>% 
    # Leave symmetric ROPE limit in table
    mutate(rope_limit = abs(ROPE_low)) %>% 
    select(
      Predictor, 
      Level, Sex, Age,
      starts_with("raw_"), 
      starts_with("scaled_"),
      # pd is common to raw and scaled values, rope only applies to scaled values
      pd = raw_pd,
      rope = scaled_rope,
      rope_limit,
      -raw_rope, 
      -scaled_pd
    )

  # Calculate decision based on pd and rope
  out %>% 
    mutate(
      d_nhst = case_when(
        pd < 0.975 ~ "Null",
        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
      ),
      d_rope = case_when(
        scaled_high < rope_limit*-1 ~ "Negative",
        scaled_low > rope_limit ~ "Positive",
        rope > 0.95 ~ "Null",
        TRUE ~ "Inconclusive"
      )
    )
}
summarise_demographics <- memoise(summarise_demographics, cache = cd)

out <- fits %>% 
  mutate(
    out = map(
      outcome,
      ~summarise_demographics(.x)
    )
  )

out %>% 
  unnest(out) %>% 
  # We'll use Age on the y axis, but also want to show the sex averages
  mutate(Age = if_else(is.na(Age), Sex, Age)) %>% 
  mutate(
    Age = factor(
      Age,
      levels = c(
        sort(levels(dat$age), decreasing = TRUE),
        "Male", "Female"
      )
    )
  ) %>%
  mutate(
    color_nhst = recode(d_nhst, Null = "a", Negative = "b", Positive = "b")
  ) %>% 
  ggplot(aes(scaled_mean, Age, col = color_nhst, shape = Sex)) +
  scale_color_brewer(palette = "Paired") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous(
    "Estimated linear association (%)",
    breaks = extended_breaks(5),
    expand = expansion(.2)
  ) +
  geom_linerange(
    aes(xmin = scaled_low, xmax = scaled_high),
    size = .3,
    position = position_dodge2v(
      height = .7,
      padding = 1,
      reverse = TRUE
    )
  ) +
  geom_point(
    size = .9,
    position = position_dodge2v(
      height = .7,
      padding = 1,
      reverse = TRUE
    )
  ) +
  facet_grid(
    rows = vars(Predictor),
    cols = vars(outcome),
    scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "none"
  )
```

### 2022-07-12 R/functions.R

@@ -1,15 +1,0 @@
-#' Custom kableExtra formatting
-#'
-#' @param a table from kbl()
-#'
-#' @return a table
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    html_font = Font,
-    font_size = 13,
-    lightable_options = "striped",
-    position = "center",
-    full_width = FALSE
-  )
-}

### 2022-07-12 _common.R

@@ -1,28 +1,0 @@
-library(ggplot2)
-library(ragg)
-library(khroma)
-
-# Plotting options
-# If you've defined a custom font, we will use it in outputs
-Font <- Sys.getenv("FONT")
-theme_set(
-  theme_linedraw(
-    base_size = 9,
-    base_family = Font
-  ) +
-    theme(
-      panel.grid = element_blank(),
-      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
-      axis.text = element_text(size = rel(0.75))
-    )
-)
-# Width of figures
-W <- 9
-
-library(knitr)
-opts_chunk$set(
-  cache.lazy = FALSE,
-  echo = FALSE
-)
-
-source("R/functions.R")

### 2022-07-14 Analysis.qmd
Update meta

@@
 ---
-title: Global mental health and well-being in the internet age
+title: Global well-being and mental health in the internet age
 description: | 
-  Online analysis supplement to "Global mental health and well-being in the internet age (Vuorre & Przybylski, 2022)"
+  Online analysis supplement to [*Global well-being and mental health in the internet age*](preprint url) (Vuorre & Przybylski, 2022)
 author:
@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
 ---
@@
 
-Welcome!
-This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [submitted]()).
-It contains all the analyses reported in the manuscript along with supplemental figures and data.
-The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).
+This document is the online analysis supplement to *Global well-being and mental health in the internet age* (Vuorre & Przybylski, [submitted]()).
+It contains all the analyses reported in the manuscript along with supplemental analyses.
+The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [Zenodo]().
 

### 2022-07-14 Analysis.qmd
Improve tables

@@
     kable_input = x,
-    html_font = Font,
+    html_font = "Arial",
     font_size = 13,
@@
 
+# Function to align positive and negative values
+number2 <- function(x, accuracy = .001, pad = FALSE) {
+  out <- number(
+    x,
+    accuracy = accuracy,
+    style_negative = "minus"
+    )
+
+  # Justify on decimal point
+  if (pad) {
+    # Add white space to start of non-negative numbers
+    out[str_starts(out, "[0-9]")] <- str_c(
+      "<code style='background:white'> </code>", 
+      out[str_starts(out, "[0-9]")]
+    )
+  }
+  out
+
+}
+
 # Then display the table
@@
     raw_result = str_glue(
-      "{number(raw_mean, .001)}
-      [{number(raw_low, .001)}, 
-      {number(raw_high, .001)}] 
-      ({percent2(pd, .1)})"
+      "{number2(raw_mean, pad = TRUE)}
+      [{number2(raw_low)}, 
+      {number2(raw_high)}] 
+      ({percent2(pd)})"
     ),
     scaled_result = str_glue(
-      "{number(scaled_mean, .001)} 
-      [{number(scaled_low, .001)}, 
-      {number(scaled_high, .001)}] 
-      ({percent2(rope, .1)})"
+      "{number2(scaled_mean, pad = TRUE)} 
+      [{number2(scaled_low)}, 
+      {number2(scaled_high)}] 
+      ({percent2(rope)})"
     ),
@@
   ) %>% 
-  kbl() %>% 
+  kable(escape = FALSE) %>% 
   kable_custom() %>% 
@@
   mutate(
-    across(Mean:CI_high, ~number(., .01)), pd = percent2(pd, .1)
+    Mean = number2(Mean, .01, pad = TRUE),
+    across(CI_low:CI_high, ~number(., .01)), 
+    pd = percent2(pd, .1)
   ) %>% 
@@
   ) %>% 
-  kbl() %>% 
+  kbl(escape = FALSE) %>% 
   kable_custom() %>% 

### 2022-07-14 Analysis.qmd
Table of ITU aggregates

@@
   row_spec(0, bold = TRUE) %>%
+  kable_custom()
+```
+
+```{r itu-aggregates}
+#| tbl-cap: "ITU's reported percentages of World's individuals using the internet"
+#| label: tbl-ituworld
+
+if (!file.exists(here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))) {
+  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))
+}
+# Individuals using the internet per 100 inhabitants | World
+tmp <- read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
+tmp %>% 
+  kbl() %>% 
   kable_custom()

### 2022-08-17 ms.Rmd
Create reproducible manuscript

---
title: Global well-being and mental health in the internet age
shorttitle: Global well-being
leftheader: Global well-being
author: 
  - name: Matti Vuorre
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project Administration
      - Software
      - Validation
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Andrew K. Przybylski
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Conceptualization
      - Data curation
      - Funding acquisition
      - Investigation
      - Methodology
      - Project Administration
      - Resources
      - Supervision
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford

authornote: |
  \noindent \textbf{This pre-print is not yet peer-reviewed.}

  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1. All code supporting this manuscript is available at <https://github.com/digital-wellbeing/global-wbmh>. This draft is available at psyarxiv.

abstract: | 
  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has had a harmful effect on mental health and psychological well-being. However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown. We show that the past two decades have seen only small and inconsistent changes in global well-being and mental health. We demonstrate that the broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband has been psychologically harmful on a global level. Moreover, little or no negative associations were observed for adolescents—a group thought particularly vulnerable. Further investigation of this topic requires transparent study of online behaviours where they occur: on online communication, media, social media, and video game platforms. We place an urgent call to increase the collaborative efforts between independent scientists and the internet technology sector.
keywords: well-being, mental health, internet technology, technology effects
# wordcount: 
bibliography: "references.bib"
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
header-includes:
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(ragg)
library(khroma)
library(labelled)
library(countrycode)
library(plotly)
library(lubridate)
library(kableExtra)
library(brms)
library(knitr)
library(here)
library(posterior)
library(bayestestR)
library(gtsummary)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(ggstance)
library(tidybayes)
library(ggdist)
library(DT)
library(tidyverse)

opts_chunk$set(
  eval = TRUE,
  cache = TRUE,
  include = FALSE,
  warning = FALSE,
  dpi = 300,
  fig.align = "center"
)
# For tables: Show NAs as blanks
options(knitr.kable.NA = '')

# Data frame for computing over models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

# Create directory for intermediate files
dir.create(here("data"), FALSE)

# Cache for memoised functions
cd <- cache_disk("cache", max_size = Inf)

# Plotting options
# If you've defined a custom font, we will use it in outputs
theme_set(
  theme_linedraw(
    base_size = 8
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.6)),
      axis.ticks = element_line(size = rel(0.3))
    )
)
```

```{r functions}
#' Custom kableExtra formatting
#'
#' @param a table from kbl()
#'
#' @return a table
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    # html_font = "Arial",
    font_size = 11,
    position = "center",
    full_width = FALSE
  )
}

# Function to replace extreme percentages
percent2 <- function(x, accuracy = .1) {
  x <- percent(x, accuracy = accuracy)
  x <- if_else(x == "100.0%", ">99.9%", x)
  x <- if_else(x == "0.0%", "<0.1%", x)
  x
}

# Function to align positive and negative values
number2 <- function(x, accuracy = .001, pad = FALSE) {
  out <- number(
    x,
    accuracy = accuracy,
    style_negative = "hyphen"
    )

  # Justify on decimal point
  if (pad) {
    # Add white space to start of non-negative numbers
    out[str_starts(out, "[0-9]")] <- str_c(
      " ", 
      out[str_starts(out, "[0-9]")]
    )
  }
  out

}
```

```{r data-clean}
## # Understand variables & values
## # Codes NOTE 1: yes 2: no!
## read_spss(
##   "data-raw/Gallup/The_Gallup_101521.sav",
##   n_max = 1,
##   col_select = c(
##     WPID, WP1219,
##     WP16,
##     WP60, WP61, WP63, WP65, WP67,
##     WP68, WP69, WP70, WP71, WP74
##   )
## ) %>%
##   generate_dictionary()

# First liberate the data from the slow SPSS file and save to disk
gwp_path <- here("data-raw/Gallup/gwp-processed.rds")
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    here("data-raw/Gallup/The_Gallup_101521.sav"),
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

  # Get rid of SPSS attributes
  gwp <- gwp %>%
    zap_labels() %>%
    zap_label() %>%
    zap_widths() %>%
    zap_formats()

  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}

# Rename and recode variables
gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

# Scale scores note rescaling
gwp <- gwp %>%
  mutate(
    Life_satisfaction = Life_satisfaction / 10,
    Negative_experiences =
      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
    Positive_experiences =
      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
  ) %>%
  select(-c(wp60:wp74))

# Categorize ages
gwp <- filter(gwp, age <= 89)
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 90, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Some sex values are missing, drop those
gwp <- drop_na(gwp, sex)

gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
gwp <- gwp %>% 
  mutate(
    se = if_else(is.na(se) | se == 0, 0.5, se)
  )

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()

# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising

# Harmonise old names and replace only if harmonised name found
gwp <- gwp %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) %>%
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

gwp_mock_path <- here("data-raw/gwp-MOCK.rds")
if (dir.exists(here("data-raw/Gallup")) & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp %>% 
    drop_na()
  gwp_syn <- syn(
    gwp_syn, 
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  gwp_syn <- tibble(gwp_syn$syn)
  saveRDS(gwp_syn, gwp_mock_path)
}

# Load if actual data doesn't exist
if (!dir.exists(here("data-raw/Gallup"))) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}

# Load data files and merge to one table
gbd <- list.files(
  here("data-raw/GBD/"),
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>%
  read_csv()

# First step is to clean names
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>%
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>%
  rename(country = location, outcome = cause)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

# Download data sets from the ITU website if not yet downloaded
if (!file.exists(here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"))) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/PercentIndividualsUsingInternet.xlsx",
    here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/FixedBroadbandSubscriptions_2000-2020.xlsx",
    here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx")
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/MobileBroadbandSubscriptions_2007-2020.xlsx",
    here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx")
  )
}

# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"),
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(fixed = as.numeric(value)) %>%
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"),
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(mobile = as.numeric(value)) %>%
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"),
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(internet = as.numeric(value)) %>%
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>%
  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl() %>%
  kable_custom()

# Harmonise old names and replace only if harmonised name found
itu <- itu %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

# Drop countries that don't exist in outcomes
itu <- itu %>%
  filter(
    country %in% unique(gbd$country) | country %in% unique(gwp$country)
  )

# Drop countries that don't have any actual internet data
itu_zeros <- itu %>%
  group_by(country) %>%
  summarise(s = sum(internet, na.rm = TRUE)) %>%
  filter(s == 0)

itu <- itu %>%
  filter(!(country %in% itu_zeros$country))
rm(itu_zeros)

# Reshape to easily impute all variables
itu_long <- itu %>%
  pivot_longer(c(internet, mobile))

# Impute by country and variable
itu_long <- itu_long %>%
  group_by(country, name) %>%
  # Find first and last year with this variable in each country
  # so as to prevent extrapolation
  mutate(
    min_year = year[min(which(!is.na(value)))],
    max_year = year[max(which(!is.na(value)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  mutate(
    across(
      value,
      .fns = list(
        i = possibly(
          function(x) na_interpolation(x, maxgap = Inf),
          otherwise = NaN
        )
      )
    )
  ) %>%
  # Take out projected (non-intermediate) imputed values
  mutate(
    value_i = if_else(
      between(year, unique(min_year), unique(max_year)),
      value_i,
      NaN
    )
  ) %>%
  ungroup() %>%
  select(-min_year, -max_year)

# Summary
itu_long %>%
  group_by(name) %>%
  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
  summarise(
    n_miss_orig = sum(is.na(value) & year >= min_year),
    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
    n_miss_imp = sum(is.na(value_i) & year >= min_year),
    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
    imputed = n_miss_orig - n_miss_imp
  ) %>%
  kbl() %>%
  kable_custom()

# We then replace the original values with the imputed ones
itu <- itu_long %>%
  # Pick non-missing value, from original and imputed
  mutate(value = coalesce(value, value_i)) %>%
  select(-value_i) %>%
  pivot_wider()
rm(itu_long)

regions <- bind_rows(
  distinct(itu, country),
  distinct(gbd, country),
  distinct(gwp, country)
) %>% 
  distinct() %>% 
  mutate(
    region = countrycode(
      country, 
      origin = "country.name", 
      destination = "continent"
    )
  )

# Manually fix two countries
regions <- regions %>% 
  mutate(
    region = if_else(country == "Kosovo", "Europe", region),
    region = if_else(country == "Nagorno Karabakh", "Asia", region)
    )

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)

regions %>% 
  group_by(region) %>%
  summarise(
    N = n(),
    Countries = str_c(country, collapse = ", ")
  ) %>% 
  kbl() %>% 
  kable_custom()

# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>%
  group_by(region, country) %>%
  mutate(
    across(
      c(internet, mobile),
      list(`1` = ~ lag(., 1)),
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  ) %>% 
  ungroup()

# Centering predictors within and between countries
itu <- itu %>%
  # Grand mean centering so both components are zero-centered
  mutate(across(c(i1, m1), ~. - mean(., na.rm = TRUE))) %>% 
  group_by(country) %>%
  mutate(
    # Between
    i1_cb = mean(i1, na.rm = TRUE),
    m1_cb = mean(m1, na.rm = TRUE),
    # Within
    i1_cw = i1 - i1_cb, 
    m1_cw = m1 - m1_cb
  ) %>% 
  ungroup()

# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center and scale year
dat <- dat %>%
  mutate(year = (year - 2010) / 10)

# Identify values to use in MV models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1, itum = 1:n() == 1) %>%
  ungroup()

# This prevents a glitch where rows where ITU==TRUE but internet is missing would not be included in model of val
dat <- dat %>% 
  mutate(
    itu = if_else(itu & is.na(internet), FALSE, itu),
    itum = if_else(itum & is.na(mobile), FALSE, itum)
    )

# Ensure that categorical variables are factors
dat <- dat %>%
  mutate(across(c(sex, age), factor))

# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
dat <- dat %>%
  mutate(across(c(val, se), ~ . * 100))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome, country, region, year)

# Selfharm models don't converge with SEs
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))
```

```{r data-describe}
bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  group_by(Dataset, region, outcome, country) %>% 
  summarise(
    n_n = sum(n),
    n_year = length(unique(year))
  ) %>% 
  summarise(
    N = sum(n_n), 
    Years = mean(n_year)
  ) %>%
  summarise(
    N_sum = round(mean(N)), 
    Years_mean = round(mean(Years))
  ) %>%
  kbl() %>% 
  kable_custom()
tmp <- gwp %>% 
  group_by(outcome) %>% 
  summarise(n=sum(n)) %>% 
  summarise(N=comma(median(n))) %>% 
  pull(N)

bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) %>% 
  mutate(Dataset = fct_inorder(Dataset)) %>% 
  count(Dataset, outcome) %>% 
  bind_rows(
    itu %>% 
      select(internet, mobile) %>% 
      pivot_longer(everything(), names_to = "outcome") %>% 
      drop_na(value) %>% 
      count(outcome) %>% 
      mutate(Dataset = "ITU")
  ) %>% 
  kbl() %>% 
  kable_custom()

gwp %>% 
  # filter(age %in% c("15 to 19", "50 to 54", "85 to 89")) %>% 
  group_by(age) %>% 
  summarise(
    n = quantile(n, probs = c(.1, .5, .9)),
    quantile = c("10%", "50%", "90%")
  ) %>% 
  pivot_wider(names_from = quantile, values_from = n) %>% 
  kbl() %>% 
  kable_custom()

itu %>%
  select(region, country, year, internet) %>%
  mutate(internet = internet * 100) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra() %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()

if (!file.exists(here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))) {
  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))
}
# Individuals using the internet per 100 inhabitants | World
tmp <- read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
tmp %>% 
  kbl() %>% 
  kable_custom()
```

```{r models-process}
# Create a table of outcomes in appropriate order, so can map functions over this
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = fct_inorder(outcome))

# The files are huge and unwieldy to work with. We create smaller files for each by dropping samples of the age:country interaction random effects. It is then easier to post-process the models.
dir.create("models-small", FALSE)

replace_chain <- function(x) {
  x %>%
    select(
      -starts_with("r_1"),
      -starts_with("r_2"),
      -starts_with("r_3"),
      -starts_with("z_1"),
      -starts_with("z_2"),
      -starts_with("z_3"),
      -starts_with("r_age:country"),
      -starts_with("L_")
    )
}

replace_chain_all <- function(x) {
  if (!file.exists(str_glue("models-small/{x}"))) {
    message(x)
    out <- readRDS(str_glue("models/{x}"))
    out$fit@sim$samples <- map(1:4, ~replace_chain(out$fit@sim$samples[[.]]))
    saveRDS(out, str_glue("models-small/{x}"), compress = FALSE)
  }
}

walk(
  list.files("models"),
  ~replace_chain_all(.x)
)

parameter_summary <- function(outcome, model) {
  path <- str_glue("models-small/brm-{outcome}-{model}.rds")
  as_draws_df(
    readRDS(path), 
    variable = c("^b_", "^sd_", "^cor_"), 
    regex = TRUE
  ) %>%
    summarise_draws(
      mean, sd,
      samples = length, 
      default_convergence_measures()
    )
}
parameter_summary <- memoise(parameter_summary, cache = cd)

convergence_summary <- tibble(
  path = list.files("models-small/", pattern = ".rds$", full.names = FALSE)
) %>% 
  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
  select(-brm) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(outcome) %>% 
  mutate(model = str_extract(model, "[0-9]")) %>% 
  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
  unnest(parameters)

convergence_summary %>% 
  filter(abs(rhat) > 1.03) %>% 
  arrange(outcome, model, variable) %>% 
  kbl(digits = c(rep(2, 7), 0, 0)) %>% 
  kable_custom()

# Function to draw a pairsplot of variables `v` of model in `path` 
dir.create(here("figures/diagnostics"), FALSE)
pairsplot <- function(filename, v) {
  out_path <- here(str_glue("figures/diagnostics/{basename(filename)}.png"))
  if (!file.exists(out_path)) {
    x <- readRDS(here(filename))
    agg_png(
      out_path,
      width = W*1.2, height = W*1.2, units = "in", res = 160
    )
    pairs(x$fit, pars = v)
    title(sub = out_path)
    dev.off()
  }
}

# Draw pairsplot for 10 worst rhats per model
convergence_summary %>% 
  group_by(outcome, model) %>% 
  arrange(outcome, model, desc(rhat)) %>% 
  slice(1:10) %>% 
  ungroup() %>% 
  group_by(outcome, model) %>% 
  summarise(v = list(variable)) %>% 
  mutate(path = str_glue("models-small/brm-{outcome}-{model}.rds")) %>% 
  ungroup() %>% 
  {walk2(.$path, .$v, ~pairsplot(.x, .y))}
```

```{r results}
# Before drawing any plots, we need to extract/compute the relevant parameters from the models. We do that here: For each outcome, we get the countries' average changes over time (in the outcome, internet, and mobile) and associations with internet and mobile
country_post_fun <- function(outcome) {

  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
  fit2 <- readRDS(str_glue("models-small/brm-{outcome}-2.rds"))
  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))

  out_outcome_year <- spread_draws(
    fit1,
    b_val_year, r_country__val[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_val_year) %>% 
    mutate(y = "outcome")

  out_internet_year <- spread_draws(
    fit1,
    b_internet_year, r_country__internet[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_internet_year) %>% 
    mutate(y = "Internet")

  out_mobile_year <- spread_draws(
    fit2,
    b_mobile_year, r_country__mobile[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_mobile_year) %>% 
    mutate(y = "Mobile")

  out_outcome_internet <- spread_draws(
    fit3,
    b_i1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "i1_cw") %>% 
    ungroup() %>% 
    rename(World = b_i1_cw) %>% 
    mutate(y = "outcome")

  out_outcome_mobile <- spread_draws(
    fit4,
    b_m1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "m1_cw") %>% 
    ungroup() %>% 
    rename(World = b_m1_cw) %>% 
    mutate(y = "outcome")

  out <- bind_rows(
    out_outcome_year, 
    out_internet_year,
    out_mobile_year,
    out_outcome_internet,
    out_outcome_mobile
  ) %>%  
    select(x, y, everything(), -c(.chain, .iteration, .draw)) %>% 
    # Add average to all but itself
    mutate(across(-c(x, y, World), ~. + World)) %>% 
    rename_with(~str_replace_all(., "\\.(?!\\.)", " ")) %>% 
    mutate(
      x = factor(
        x, 
        levels = c("year", "i1_cw", "m1_cw"),
        labels = c("Time", "Internet", "Mobile")
      )
    )

  out 
}
country_post_fun <- memoise(country_post_fun, cache = cd)
country_post <- fits %>% 
  mutate(
    samples = map(outcome, country_post_fun),
    summary = map(
      samples, 
      ~.x %>% 
        group_by(x, y) %>% 
        summarise_draws(
          mean, 
          ~quantile2(., probs = c(.025, .975)),
          pd = ~pd(as.numeric(.))
        ) %>% 
        rename(country = variable)
    )
  )

# Create scaling factors for decade-equivalent associations
# There is a different scaling factor for each outcome,
# even though they used the same internet/mobile values. That's because 
# different countries were included by outcome, and its then most faithful
# to the data to keep these separate by outcome.
# Get each country's Time -> Predictor parameters
scaling_factors <- country_post %>% 
  select(outcome, summary) %>% 
  unnest(summary) %>% 
  filter(x == "Time", y != "outcome") %>% 
  select(outcome, y, country, scaling = mean)

# Find changes per decade per outcome for ROPE limits
change_factors <- country_post %>% 
  select(outcome, summary) %>% 
  unnest(summary) %>% 
  filter(x == "Time", y == "outcome") %>% 
  select(outcome, country, change = mean)

# Calculate sign and ROPE tests for time/internet/mobile -> outcomes
summarise_all <- function(
    posterior = country_post,
    scaling_factors = scaling_factors,
    change_factors = change_factors
) {

  # Posterior samples of all effects on outcomes
  tab <- posterior %>% 
    select(outcome, samples) %>% 
    unnest(samples) %>% 
    filter(y == "outcome") %>%
    select(-y) %>%
    pivot_longer(-c(outcome, x), names_to = "country") %>% 
    # Drop NAs because some country-outcome combinations don't exist
    drop_na(value) %>% 
    # We will have raw and scaled results
    rename(raw = value)

  # Scale internet and mobile to decade-equivalents
  tab <- tab %>% 
    left_join(
      scaling_factors %>% 
        rename(x = y)
    ) %>% 
    mutate(scaling = if_else(x == "Time", 1, scaling)) %>% 
    mutate(scaled = raw * scaling) %>% 
    select(-scaling)

  # Change associations with internet and mobile to units of 10% not 100%
  tab <- tab %>% 
    mutate(
      raw = if_else(x == "Time", raw, raw / 10)
    )

  # Calculate the raw and scaled results for each outcome and predictor
  tab <- tab %>% 
    nest(data = c(raw, scaled)) %>% 
    left_join(change_factors) %>% 
    mutate(
      out = map2(
        data, change,
        ~describe_posterior(
          .x, 
          centrality = "mean", 
          ci_method = "eti",
          rope_range = c(-.y, .y), 
          rope_ci = 1
        )
      )
    ) %>% 
    transmute(
      Predictor = fct_inorder(x), 
      Outcome = fct_inorder(str_replace(outcome, "_", " ")),
      country, 
      out
    ) %>% 
    arrange(Predictor, Outcome) %>% 
    unnest(out) %>% 
    # Clean the names a bit
    rename(
      rope = ROPE_Percentage,
      mean = Mean,
      low = CI_low,
      high = CI_high
    ) %>% 
    # Put raw and scaled results on one row
    pivot_wider(
      names_from = Parameter,
      values_from = c(mean, low, high, pd, rope),
      names_glue = "{Parameter}_{.value}"
    ) %>% 
    # Leave symmetric ROPE limit in table
    mutate(rope_limit = abs(ROPE_low)) %>% 
    select(
      Predictor, 
      Outcome, 
      Country = country, 
      starts_with("raw_"), 
      starts_with("scaled_"),
      # pd is common to raw and scaled values, rope only applies to scaled values
      pd = raw_pd,
      rope = scaled_rope,
      rope_limit,
      -raw_rope, 
      -scaled_pd
    )

  # Calculate decision based on pd and rope
  tab <- tab %>% 
    mutate(
      d_nhst = case_when(
        pd < 0.975 ~ "Null",
        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
      ),
      d_rope = case_when(
        scaled_high < rope_limit*-1 ~ "Negative",
        scaled_low > rope_limit ~ "Positive",
        rope > 0.95 ~ "Null",
        TRUE ~ "Inconclusive"
      )
    )

  # Return object
  tab
}
summarise_all <- memoise(summarise_all, cache = cd)
tab <- summarise_all(country_post, scaling_factors, change_factors)
```

In 2005, an estimated 17% of the global population used the internet, but by 2020 this number was already 59% [@ituITUICTStatistics2021]. Accompanying the rapid spread of the internet, worries have proliferated that its broad adoption—and technologies enabled by it such as online games, smartphones, and social media—is actively harming its users, particularly adolescents [@carrShallowsHowInternet2010; @turkleAloneTogetherWhy2011]. As a response, users and a growing number of national governments have acted in limiting access to online technologies.

However, evidence for widespread harms of online technologies is limited. Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020]. Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2021], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006]. A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted. As a consequence, much of the evidence purporting to show that internet technology adoption causes negative outcomes remains anecdotal [@dickson2018screen; @hawkesCMOReportUnable2019].

We examined six aspects of global psychological well-being [@gallupGallupWorldPoll2020] and mental health [@vosGlobalBurden3692020]: measures of life satisfaction, positive and negative psychological experiences, and rates of anxiety, depression, and self-harm from 2000 to 2021, using data from 2,359,264 individuals aged 15 to 89 from 164 countries and meta-analytic model estimates from 202 countries (Methods). We contrasted those observations with timeseries of countries’ per capita internet users and mobile broadband subscriptions [@ituITUICTStatistics2021] to examine if and how internet and mobile broadband adoption predicted fluctuations in global psychological well-being and mental health over the past two decades.

```{r figure-1}
#| include: true
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.height: 5.4
#| fig.cap: Time courses of per capita internet users (row one), mobile broadband subscriptions (row two), and six psychological well-being and mental health outcomes (rows three to eight). Lines indicate countries’ yearly means of the respective variable, aggregated across sex and age. An interactive version of this figure is available in the SOM.

# Stack data sets
# Assume all outcomes are proportions (0-1)
# Draw small multiples figure, outcomes x regions
d <- bind_rows(
  gwp,
  gbd
)

itu <- itu %>%
  select(
    region, country, year,
    Internet = internet,
    Mobile = mobile,
  ) %>%
  # Truncate mobile percentages for figure
  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
  pivot_longer(
    c(Internet, Mobile),
    names_to = "outcome", values_to = "val"
  )

p1 <- bind_rows(itu, d) %>%
  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
  group_by(region, country, year, outcome) %>%
  summarise(mean = mean(val, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
  mutate(year = make_date(year)) %>%
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value (%)",
    # Display percentages
    labels = ~. * 100,
    breaks = pretty_breaks(),
    expand = expansion(.05)
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2005, 2010, 2015, 2020)),
    date_labels = "'%y",
    expand = expansion(.02)
  ) +
  geom_line(
    aes(
      group = interaction(country, outcome), 
      text = str_glue("{country} {year(year)} ({percent(mean)})")
    ),
    size = .15
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    legend.position = "none"
  )
p1

ggplotly(p1, tooltip = "text") %>% 
  layout(
    margin = list(t = 100, r = 100, b = 100, l = 100)
  ) %>% 
  htmlwidgets::saveWidget("Figure-1-interactive.html")
```

Figure \@ref(fig:figure-1) describes these data: Countries’ yearly rates of per capita internet users and mobile broadband subscriptions, and six indicators of psychological well-being and mental health (the latter two averaged over sex and age). Figure \@ref(fig:figure-1) shows the universal global penetration of internet technologies in the past two decades, and suggests that in contrast, changes in well-being and mental health are likely to be small or mixed across countries.

```{r table-1}
#| include: true

tmp <- tab %>% 
  filter(Country == "World") %>% 
  # Create a result string for table
  mutate(
    raw_result = str_glue(
      "{number2(raw_mean, pad = TRUE)} [{number2(raw_low)}, {number2(raw_high)}] ({percent2(pd)})"
    ),
    scaled_result = str_glue(
      "{number2(scaled_mean, pad = TRUE)} [{number2(scaled_low)}, {number2(scaled_high)}] ({percent2(rope)})"
    ),
    # ROPE doesn't make sense for change over time (it is ROPE)
    scaled_result = if_else(
      Predictor == "Time", "", as.character(scaled_result)
    )
  ) %>% 
  select(
    Predictor, 
    Outcome, 
    `Raw association` = raw_result, 
    `Scaled association` = scaled_result
  ) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) 
tmp %>%   
  apa_table(
    font_size = "small",
    span_text_columns = TRUE,
    note = "Raw associations are percentage changes in outcomes associated with a decade (Time) or 10% (Internet & Mobile) increase in the predictor. Numbers indicate posterior means, [95%CI], and (posterior probability of direction). Scaled associations are percentage changes in outcomes associated with per-decade change in the predictor ('decade-equivalent' association). Numbers indicate posterior means, [95%CI], and (posterior probability inside the region of practical equivalence; i.e. probability that the association is smaller than the per-decade change in the respective outcome)."
  )
```

Parameter estimates from hierarchical models (Methods, Model 1; Table \@ref(tab:table-1), Time) did not convincingly show that global well-being or mental health had decreased during this period of global internet adoption, as would be expected if internet technologies had broad negative consequences. While life satisfaction overall had remained relatively stable, both negative and positive experiences had increased—although the former more so (6.8% [5.4, 8.2] per decade). Meta-analytic estimates of rates of anxiety [@vosGlobalBurden3692020] had increased by 0.07% [0.05, 0.08] globally, but depression and self-harm rates had decreased (by 0.09% [0.05, 0.11] and 0.02% [0.01, 0.03], respectively).

We then predicted each outcome from time-lagged and within-country centred per capita internet users and mobile broadband subscriptions (Methods, Model 2; Table \@ref(tab:table-1), Internet & Mobile Raw associations). This association is our key estimate of interest and describes the extent to which an increase in a country’s per capita internet users and mobile broadband subscriptions predict that country’s well-being and mental health in the following year. Internet adoption did not predict any outcome at the 95% credibility level, but a 10% increase in per capita internet users predicted a 1.1% [-0.09, 2.24] increase in negative experiences for the average country with 96.4% posterior probability of direction. Mobile broadband, on the other hand, positively predicted life satisfaction (0.84% [0.20, 1.49]), with greater evidence for direction (99.6%).

We then put the associations in context with simple temporal changes and created "decade-equivalent" associations by dividing the internet and mobile associations by their per-decade changes (Table \@ref(tab:table-1), Scaled associations). We then tested whether those associations were practically null at the 95% credibility level, practically meaningful (credibly greater), or inconclusive (not credibly smaller or greater) by comparing them to a region of practical equivalence to zero (ROPE) defined by the estimated (absolute) linear by-decade change in the outcome [@kruschkeBayesianNewStatistics2017]. This allowed us to quantify evidence toward the null hypothesis of smaller than practically meaningful association. While internet adoption did predict increases in negative experiences with a 96.4% certainty of direction, the decade-equivalent association was smaller than a simple change per decade in negative experiences with 98.3% confidence. In other words, the magnitude of the predictive association between per capita internet users and negative psychological experiences was smaller than the decade-by-decade change in negative experiences (by about a half). This suggested that while internet adoption did predict increases in negative experiences, that magnitude is not practically meaningful when compared to overall temporal trends.

On the other hand, the same reasoning regarding mobile broadband adoption and life satisfaction indicated 99.6% confidence of a global positive predictive association, and a 99.9% certainty that the association was (about 60 times) greater than the simple per-decade change in life satisfaction. This indicated that per capita mobile broadband subscriptions were a meaningfully large positive predictor of country-level life satisfaction (5.60% [1.31, 9.94]). In sum, the global predictive associations between internet and mobile broadband adoption and well-being and mental health were mixed and, in most cases, supported the null hypothesis of smaller than meaningful association (percentages in rightmost column of Table \@ref(tab:table-1)).

```{r figure-2}
#| include: true
#| fig.height: 4
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.cap: Country-specific changes per decade (top row), and decade-equivalent associations with per capita internet users (middle; see text) and mobile broadband subscriptions (bottom). Points and lines indicate posterior means and 95\% CIs. Darker blue indicates that the parameter is credibly different from zero (with 95\% confidence). Countries are sorted from the greatest decrease to the greatest increase for that outcome.
# Arrange points within panels such that the order of countries is same in the rows of each column, running from smallest time change to greatest time change. This is a rudimentary way to show correlation between the two.
tmp <- tab %>% 
  filter(Predictor == "Time", Country != "World") %>% 
  arrange(raw_mean) %>% 
  group_by(Outcome) %>% 
  mutate(x_order = 1:n()) %>% 
  select(Outcome, Country, x_order) %>% 
  ungroup()

tab %>% 
  filter(Country != "World") %>% 
  left_join(tmp) %>% 
  # Factor order for colors
  mutate(
    color_nhst = recode(d_nhst, Null = "c", Negative = "b", Positive = "b")
  ) %>% 
  ggplot(aes(x_order, scaled_mean, col = color_nhst)) +
  scale_color_brewer(palette = "Paired", direction = -1) +
  # scale_color_manual(values = c("dodgerblue3", "dodgerblue1", "dodgerblue1")) +
  scale_x_continuous("Country") +
  scale_y_continuous(
    "Estimated linear association (%)"
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_linerange(
    size = .15,
    aes(ymin = scaled_low, ymax = scaled_high)
  ) +
  geom_point(
    size = .2
  ) +
  facet_grid2(
    Predictor~Outcome, 
    scales = "free",
    independent = "all",
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    )
  ) +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none"
  )
```

These global trends and associations are meaningful summaries, but do not represent any specific country. Indeed, variability across countries dwarfed the average global trends and associations (Figure \@ref(fig:figure-2) and Table \@ref(tab:table-s1)). The first row of Figure \@ref(fig:figure-2) displays country-level trends over time for each of the six outcomes. There appear to be no universal trends that apply to all countries. The next two rows indicate decade-equivalent associations between well-being and mental health outcomes and per capita internet users and mobile broadband subscriptions, respectively.

To summarize these country-specific associations, we calculated proportions of countries with credibly positive, negative, and null associations (Table \@ref(tab:table-s2)). Above we identified that internet adoption predicted modest increases in negative experiences for the average country with 96.4% confidence. Table \@ref(tab:table-s2) shows that this association was credibly positive (negative) for 31% (22%) of countries, and practically meaningfully so for 15% (12%). The null hypothesis was supported for 13% of countries. We observed similar percentages for the other well-being outcomes. For mental health outcomes, 92%-100% (across outcomes) of countries’ associations were not credibly negative or positive, and indeed supported the null hypothesis of non-meaningfully large association for 18-54% countries. This lack of consistent associations across countries, and support for the null hypothesis for many countries, should qualify any inferences concerning global associations and is evidence against the idea that the adoption of internet or mobile broadband have uniform global negative effects on well-being and mental health.

These global and country-specific analyses are informative but shed no light on how internet and mobile broadband adoption might have different effects for different demographic groups. So we then examined variation across age and sex (for the average country) in the relations linking internet and mobile broadband adoption to psychological well-being and mental health. Table \@ref(tab:table-s1) shows that there was modest variation in the associations across age groups, and the variation was always smaller than the variation across countries. Age- and sex-specific estimates, for the average country, are shown in Figure \@ref(fig:figure-3). Notable cases where demography-specific trends emerged were life satisfaction, whose association with mobile broadband adoption was credibly positive for all but the youngest group of individuals (although variation in the age groups was modest; Table \@ref(tab:table-s1)); negative experiences, which had increased more for older age groups, and whose association with internet adoption was credibly positive for most age groups between 20 to 59; and positive experiences, which had increased more for females and the youngest and oldest age groups.

```{r figure-3}
#| include: true
#| fig.height: 5
#| out.width: "\\textwidth"
#| fig.env: "figure*"
#| fig.cap: Age- and sex-specific changes in well-being and mental health outcomes (top row), and their decade-equivalent (see text) associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row). Circles indicate females and triangles males. Darker blue indicates that the parameter is credibly different from zero (with 95\% confidence).
summarise_demographics <- function(outcome) {

  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))

  out_outcome_year <- spread_draws(
    fit1, 
    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_val_year + `b_val_year:sex1`*1,
      World_Male = b_val_year + `b_val_year:sex1`*-1,
      Age_Female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
      Age_Male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    # Throws a warning for Age cells in World rows (value doesn't exist)
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " "))

  out_outcome_internet <- spread_draws(
    fit3, 
    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_i1_cw + `b_i1_cw:sex1`*1,
      World_Male = b_i1_cw + `b_i1_cw:sex1`*-1,
      Age_Female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
      Age_Male = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
    # Rescale effect to "decade-equivalent"
    bind_cols(
      scaling_factors %>% 
        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
        select(scaling)
    ) %>% 
    mutate(value = value * scaling) %>% 
    select(-scaling)

  out_outcome_mobile <- spread_draws(
    fit4, 
    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    ungroup() %>% 
    mutate(
      World_Female = b_m1_cw + `b_m1_cw:sex1`*1,
      World_Male = b_m1_cw + `b_m1_cw:sex1`*-1,
      Age_Female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
      Age_Male = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
    ) %>% 
    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
    pivot_longer(-.draw, names_to = "Variable") %>% 
    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
    # Rescale effect to "decade-equivalent"
    bind_cols(
      scaling_factors %>% 
        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
        select(scaling)
    ) %>% 
    mutate(value = value * scaling) %>% 
    select(-scaling)

  out <- bind_rows(
    "Time" = out_outcome_year,
    "Internet" = out_outcome_internet,
    "Mobile" = out_outcome_mobile,
    .id = "Predictor"
  ) %>% 
    mutate(Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")))

  # Scaling factors are invariant to demography
  out <- scaling_factors %>% 
    filter(country == "World") %>% 
    filter(outcome == {{outcome}}) %>% 
    select(Predictor = y, scaling) %>% 
    right_join(out) %>% 
    mutate(scaling = if_else(Predictor == "Time", 1, scaling)) %>% 
    rename(raw = value) %>% 
    mutate(scaled = raw * scaling) %>% 
    select(-scaling)

  # Calculate demography-specific change-factors (how much outcome changed)
  change_factors <- out %>% 
    filter(Predictor == "Time") %>% 
    group_by(Level, Sex, Age) %>% 
    mean_qi(change = raw) %>% 
    select(Level, Sex, Age, change)

  # Then calculate pd and rope

  # Change associations with internet and mobile to units of 10% not 100%
  out <- out %>% 
    mutate(
      raw = if_else(Predictor == "Time", raw, raw / 10)
    )

  # Calculate the raw and scaled results for each outcome and predictor
  out <- out %>% 
    select(-.draw) %>% 
    nest(data = c(raw, scaled)) %>% 
    left_join(change_factors) %>% 
    mutate(
      out = map2(
        data, change,
        ~describe_posterior(
          .x, 
          centrality = "mean", 
          ci_method = "eti",
          rope_range = c(-.y, .y), 
          rope_ci = 1
        )
      )
    ) %>% 
    transmute(
      Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")), 
      Level, Sex, Age, out
    ) %>% 
    arrange(Predictor) %>% 
    unnest(out) %>% 
    # Clean the names a bit
    rename(
      rope = ROPE_Percentage,
      mean = Mean,
      low = CI_low,
      high = CI_high
    ) %>% 
    # Put raw and scaled results on one row
    pivot_wider(
      names_from = Parameter,
      values_from = c(mean, low, high, pd, rope),
      names_glue = "{Parameter}_{.value}"
    ) %>% 
    # Leave symmetric ROPE limit in table
    mutate(rope_limit = abs(ROPE_low)) %>% 
    select(
      Predictor, 
      Level, Sex, Age,
      starts_with("raw_"), 
      starts_with("scaled_"),
      # pd is common to raw and scaled values, rope only applies to scaled values
      pd = raw_pd,
      rope = scaled_rope,
      rope_limit,
      -raw_rope, 
      -scaled_pd
    )

  # Calculate decision based on pd and rope
  out %>% 
    mutate(
      d_nhst = case_when(
        pd < 0.975 ~ "Null",
        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
      ),
      d_rope = case_when(
        scaled_high < rope_limit*-1 ~ "Negative",
        scaled_low > rope_limit ~ "Positive",
        rope > 0.95 ~ "Null",
        TRUE ~ "Inconclusive"
      )
    )
}
summarise_demographics <- memoise(summarise_demographics, cache = cd)

out <- fits %>% 
  mutate(
    out = map(
      outcome,
      ~summarise_demographics(.x)
    )
  )

out %>% 
  unnest(out) %>% 
  # We'll use Age on the y axis, but also want to show the sex averages
  mutate(Age = if_else(is.na(Age), Sex, Age)) %>% 
  mutate(
    Age = factor(
      Age,
      levels = c(
        sort(levels(dat$age), decreasing = TRUE),
        "Male", "Female"
      )
    )
  ) %>%
  mutate(
    color_nhst = recode(d_nhst, Null = "a", Negative = "b", Positive = "b")
  ) %>% 
  ggplot(aes(scaled_mean, Age, col = color_nhst, shape = Sex)) +
  scale_color_brewer(palette = "Paired") +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous(
    "Estimated linear association (%)",
    breaks = extended_breaks(5),
    expand = expansion(.2)
  ) +
  geom_linerange(
    aes(xmin = scaled_low, xmax = scaled_high),
    size = .3,
    position = position_dodge2v(
      height = .8,
      padding = 1,
      reverse = TRUE
    )
  ) +
  geom_point(
    size = .9,
    position = position_dodge2v(
      height = .8,
      padding = 1,
      reverse = TRUE
    )
  ) +
  facet_grid(
    rows = vars(Predictor),
    cols = vars(outcome),
    scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "none"
  )
```

Rates of anxiety were negatively associated with per capita mobile broadband subscriptions for the youngest and oldest males and no other group. Both depression and self-harm had decreased overall, but those decreases were smallest for the youngest age groups. Self-harm was most positively associated with internet adoption and mobile broadband subscriptions for the youngest age groups, particularly for males in the latter case, a finding that runs contrary to the prevailing narrative of young females being most at risk. (In fact we observed no particularly negative associations for this group; Figure \@ref(fig:figure-3).)

Up to this point we have examined associations linking internet and mobile broadband adoption to well-being and mental health within countries. It is also possible that countries with greater levels of internet technology adoption show lower levels of well-being and mental health if the former are adversely affecting the latter. Our models indexed these between-country associations with separate parameters (Methods), summarised in Table \@ref(tab:table-s3). We found that, across countries, greater average levels of per capita internet users and mobile broadband subscriptions were associated with greater levels of life satisfaction, positive experiences, anxiety, and self-harm, and lower levels of negative experiences and depression. Furthermore, countries with greatest increases in per capita internet users were not countries where well-being and mental health declined the most. To the contrary, increases in internet technology adoption were negatively correlated with increases in negative experiences, and positively correlated with increases in life satisfaction and positive experiences. That is, countries where internet and mobile broadband penetration was most rapid in this period were also those where well-being increased the most. Complementary to our patterns of findings regarding predictive associations within-countries, the cross-country associations between internet technology adoption and well-being and mental health did not lend support to the idea that the former has had worldwide (negative) impacts on the latter.

The idea that the rapid and global penetration of the internet, and technologies enabled by it, is affecting well-being and mental health is compelling but not adequately tested. We tested the extent to which countries’ per-capita internet users and mobile broadband subscriptions predict levels of well-being and mental health, and found that, overall, there were few if any meaningfully large associations. In all cases but one—mobile broadband adoption predicted life satisfaction positively—these associations were smaller than the corresponding total changes in the outcomes over time (Table \@ref(tab:table-1)). The small observed associations were also qualified by substantive variability across countries (Figure \@ref(fig:figure-2)) and demographics (Figure \@ref(fig:figure-3)). Furthermore, countries where internet technologies were more widely or rapidly adopted were not those with lowest levels of, or fastest declines in, well-being and mental health.

Our results do not support the view that the internet, and technologies enabled by it such as smartphones with internet access, are actively harming well-being or mental health globally, nor that adolescents, and females in particular, are vulnerable to a greater degree. Nevertheless, data and theory required to address this question at the causal level are absent. Consequently, our analyses cannot account for potential time-varying confounders. Our descriptions, therefore, are suggestive but do not provide strong evidence for, or against, causal relations. In addition, our results regarding mental health, while comprehensive, are necessarily and considerably less certain than those on well-being, due to the lack of diverse global data and our own reliance on GBD estimates of mental health.

Research on the effects of internet technologies is stalled because the data most urgently needed are collected and held behind closed doors by technology companies and online platforms. It is crucial to study, in more detail and with more transparency from all stakeholders, data on individual adoption of and engagement with internet-based technologies. These data exist and are continuously analysed by global technology firms for marketing and product improvement, but unfortunately are not accessible for independent research. It remains a fundamental challenge to this field of inquiry to ensure that this information is accessible to independent scholars. Until these data can be transparently analysed for the public good, the potential harmful effects of the internet and other digital environments will remain unknown.

# References

::: {#refs}
:::

# Methods

## Internet adoption

We identified the International Telecommunication Union’s (ITU) database of information and communications technology (ICT) as the most comprehensive country-level source of time-series data on internet adoption [@ituITUICTStatistics2021]. The ITU has collated, from 222 countries’ statistical and telecommunications agencies, the yearly percentages of population using the internet from 2000 to 2020, and yearly per capita broadband subscriptions from 2007 to 2020. Our analyses used 3,857 yearly internet percentages and 2,260 broadband subscription rates; we imputed 95 (70 mobile) intermediate missing values to this dataset using linear interpolation without extrapolation. Our online analysis supplement contains a complete list of years, countries, and sources of data underlying the ITU ICT data. The ITU ICT data are freely available at <https://www.itu.int/en/ITU-D/Statistics/Pages/stat/default.aspx>.

## Subjective well-being

We examined subjective well-being indicators from the Gallup World Poll (GWP), a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from 164 countries from 2005 to 2021. The surveys are conducted face-to-face or via telephone, in the respondents’ native language and by local interviewers. For details on the GWP sampling and survey methodology, see [@gallupGallupWorldPoll2020; @gallupHowDoesGallup2014]. GWP measures subjective well-being with the Positive (PE) and Negative Experience (NE) indices. The PE and NE indices measure respondents’ experienced well-being on the day before the survey with five items each. For PE, these items are:

- Did you feel well-rested yesterday?
- Were you treated with respect all day yesterday?
- Did you smile or laugh a lot yesterday?
- Did you learn or do something interesting yesterday?
- (Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?

And for NE, the items are responses to "Did you experience the following feelings during a lot of the day yesterday?":

- How about physical pain?
- How about worry?
- How about sadness?
- How about stress?
- How about anger?

We aggregated both scales for each respondent by taking a mean of the five items. Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top. The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you. On which step of the ladder would you say you personally feel you stand at this time?", similar to the Cantril self-anchoring scale [@cantril1965pattern; @kapteynDimensionsSubjectiveWellbeing2015]. For analyses, we converted these variables to percentages, and aggregated the 2,359,264 individuals’ data to means and standard errors for each country, year, sex, and age (5-year age groups from 15 to 89 years) combination (58,379 cells). The GWP data are available to subscribing institutions through Gallup.

## Mental health

We studied prevalence rates (per 100 population; hereafter percentages) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0) in 204 countries from 2000 to 2019 as estimated by the Institute for Health Metrics and Evaluation’s (IHME) Global Burden of Disease 2019 study (GBD; [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020]). The GBD collates heterogeneous data from all WHO member states’ censuses, household surveys, civil registration and vital statistics, disease registries, health service use, disease notifications, and other sources. It then aggregates data from these sources with Bayesian meta-regression to produce country-specific yearly prevalence estimates.

The GBD 2019 prevalence rate estimates are based on 19,773 data sources with varying coverage for individual countries; for details of the GBD 2019 methodology, see [@vosGlobalBurden3692020] and especially Appendix 1 therein. The prevalence rates are estimated for females and males in 5-year age groups, and are provided as the IHME meta-regression model’s predicted means and 95% credibility intervals; we converted the latter to approximate standard errors for our meta-analytic modelling strategy (see below).

We emphasize that the GBD estimates are not observed data, and therefore are accurate only to the extent that the GBD’s data collection methods and modelling strategies are valid. We have compared the GBD estimates to the CDC’s estimates of self-harm in the United States[@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources. We nevertheless argue that because the GBD provides the most comprehensive dataset of global mental health, studying these estimates is informative, but emphasize this caveat. The sample size for our analyses (combinations of country, year, sex, and age) was 130,560. The GBD data are freely available at <http://ghdx.healthdata.org/gbd-results-tool>.

## Material availability and ethics

The supplementary online materials (SOM) of this manuscript contain all the data-analytic code, GBD and ITU data, and a synthetic GWP dataset to facilitate the verification, extension, and critique of our procedures (<https://digital-wellbeing.github.io/global-wbmh/>). 
This study and methods therein were approved by the University of Oxford Central University Research Ethics Committee (SSH_OII_CIA_21_084).

## Data analysis

We analysed the data with meta-analytic bayesian hierarchical regression models [@burknerBrmsPackageBayesian2017; @gelmanDataAnalysisUsing2007; @standevelopmentteamStanModelingLanguage2021]. Our first research question focused on changes over time in the mental health and well-being outcomes and internet adoption metrics. For each well-being and mental health outcome $y$ (e.g. life satisfaction) and internet adoption metric $x$ (e.g. per capita mobile broadband subscriptions), we specified a multivariate model of $y$ and $x$ on population level intercepts ($\alpha_0$; we centred time on the year 2010), contrasts of time (in decades, $\alpha_1$), sex (-1: Female; 1: Male; $\alpha_2$), and their interaction ($\alpha_3$). We allowed all coefficients to vary across countries, age groups, and the age by country interactions for models of the well-being outcomes. We did not include the age by country interaction for the GBD mental health outcomes because the models did not converge due to invariance in the data.

The multivariate normal distributions of the country-level deviations were shared across models of $y$ and $x$, allowing examining the extent to which country-level deviations from the average in levels (intercepts) and changes (slopes) of well-being and mental health correlated with the corresponding levels and changes in internet and mobile broadband adoption. Because we modelled aggregated data (GWP) and model estimates (GBD), we incorporated the observed standard errors in the model. We set this standard error to zero for models of self-harm due to convergence problems. We treated all outcomes as normally distributed. We specified Model 1 as

\begin{align*}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{y2}v_i) \\
x_i &\sim \text{Normal}(\mu^x_i, \sigma^{x2}) \\ 
\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{country}[i]} + \gamma^{y}_{0\text{age}[i]} + \delta^{y}_{0\text{age:country}[i]} + \\ 
&\quad\ (\alpha^{y}_{1} + \beta^{y}_{1\text{country}[i]} + \gamma^{y}_{1\text{age}[i]} + \delta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
&\quad\ (\alpha^{y}_{2} + \beta^{y}_{2\text{country}[i]} + \gamma^{y}_{2\text{age}[i]} + \delta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
&\quad\ (\alpha^{y}_{3} + \beta^{y}_{3\text{country}[i]} + \gamma^{y}_{3\text{age}[i]} + \delta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
\mu^x_i &= \alpha^{x}_{0} + \beta^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{country}[i]})\text{Time}_i \\
\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country})
\end{align*}

where $i$ indexes rows in the data and $v_i$ are the known sampling variances. Because we incorporated deviations from the average parameters (intercept, linear change (Time), sex, and the change by sex interaction) for each country, age, and age by country interactions, we obtained shrinkage estimates specific to countries, age groups, and age groups within countries that are robust to multiple comparisons [@gelmanWhyWeUsually2012]. Of particular interest are the $\rho_{\beta_0^y\beta_0^x}$ and $\rho_{\beta_1^y\beta_1^x}$) correlations in $\Sigma^\text{country}$, indicating the correlations between country-level deviations in the levels and changes in internet and mobile broadband adoption, and well-being and mental health.

Aggregating the well-being outcomes to means ($y_i$) and sampling variances ($v_i$) for each country-year-sex-age group facilitated the Hamiltonian Monte Carlo [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021] computations on otherwise large data and enabled applying the same models to the well-being and mental health outcomes, the latter of which are meta-analytic estimates for these groupings. Allowing the coefficients to vary randomly across age groups (and their interactions with countries) allowed inferences to and contrasts between age groups that were robust to multiple comparisons [@gelmanAnalysisVarianceWhy2005; @gelmanWhyWeUsually2012]. Specifying the country-level deviations across parameters on $y$ and $x$ in the same distributions allowed assessing their correlations that accounted for uncertainty in the country-level estimates.

Importantly, we note that because we model unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g. population size. This means that our inferences pertain to (demographics within) countries, and not to individual people.

Our second research question asked whether changes in internet adoption predicted changes in well-being within countries. To answer, we expanded Model 1 to include the 1-year-lagged value of internet or mobile broadband adoption, within-country-centred, and its interaction with sex as predictors of the well-being outcome. We specified Model 2 as

\begin{align*} 
y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + \\
&\quad\ \alpha_6 \text{Internet}^{\text{t-1[CB]}}_i
\\
\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}) \\
\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}) \\
\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country})
\end{align*}

where $\text{Internet}^{\text{t-1[CB]}}_i$ is the country-specific grand-mean centred mean of the lagged internet / mobile broadband adoption value for the country on row $i$.

We chose to use a lagged predictor to take a first step in moving this inquiry toward examining causal associations. Because our hypothesized treatment, per capita internet users and mobile broadband subscriptions, is at the country-level, it is likely that any possible effect mediated by the group rather than the individuals themselves would manifest only over time and not immediately. Therefore, a lagged association would capture potential causal effects better than a contemporary association, but we highlight that this is only an initial step toward examining causality: We do not make the necessary strong assumptions required for identifying causal effects. For instance, we don’t adjust for either time-invariant (Model 1) or time-varying (Model 2) confounders, which could bias observed between-country and within-country associations, respectively. Nevertheless, including time as a predictor gives some preliminary adjustment for simple temporal trends. In addition, we within-country centred the lagged internet adoption so that we could isolate within-country associations from between-country associations. We believe the latter are much more likely to be confounded, and the former to better approximate causal associations (keeping in mind the above caveats.)

Our third research question asked whether any trends in well-being and mental health or their associations with internet or mobile broadband adoption were specific to adolescents. To answer, the models above allowed all parameters to vary randomly across the age groups and the age by country interaction. Therefore, each age group, on average and within each country, received their own partially pooled estimates [@gelmanDataAnalysisUsing2007]. This bayesian approach to estimating age-specific associations is beneficial, given that the large number of age groups, especially within countries, would otherwise present difficulties with uncertain estimates and multiple comparisons. Instead, partial pooling allowed us to do any desired comparison, such as comparing younger age groups to older age groups, with confidence and without additional post-hoc adjustment procedures [@gelmanWhyWeUsually2012].

We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021]. We used default noninformative priors, 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.

# Acknowledgements

We thank Niklas Johannes for feedback on this work. The authors would like to acknowledge the use of the University of Oxford Advanced Research Computing (ARC) facility in carrying out this work http://dx.doi.org/10.5281/zenodo.22558.

# Author Contributions

A.K.P.: Conceptualization, Data curation, Funding acquisition, Investigation, Methodology, Project administration, Resources, Supervision, Visualization, Writing - original draft, and Writing - review & editing. M.V.: Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Software, Validation, Visualization, Writing - original draft, and Writing - review & editing.

# Competing Interests Declaration

The authors declare no competing interests. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

# Supplementary analyses

<!-- Prepend table numbers with S and reset counter -->
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}

```{r table-s1}
#| include: true
get_het_pars <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
  draws <- as_draws_df(
    x,
    variable = c(
      str_glue("^b_{predictor}$"),
      str_glue("^sd_age__{predictor}$"),
      str_glue("^sd_country__{predictor}$"),
      str_glue("^sd_age:country__{predictor}$")
    ),
    regex = TRUE
  ) %>% 
    select(-c(.chain, .iteration, .draw)) %>% 
    # From 100% to 10% units for associations
    mutate(across(-contains("val_year"), ~ ./10)) %>% 
    rename_with(~str_remove(., str_glue("{predictor}")))
  draws
}

get_het_pars <- memoise(get_het_pars, cache = cd)

het_pars <- fits %>% 
  crossing(
    nesting(predictor = c("val_year", "i1_cw", "m1_cw"), model = c(1, 3, 4))
  ) %>%
  mutate(
    out = pmap(
      list(outcome, predictor, model), 
      ~get_het_pars(..1, ..2, ..3))
  )
het_tab <- het_pars %>% 
  unnest(out) %>%
  select(-model) %>% 
  rename(
    Association = b_,
    `SD (age)` = sd_age__,
    `SD (country)` = sd_country__,
    `SD (age * country)` = `sd_age:country__`,
  ) %>%
  group_by(outcome, predictor) %>% 
  summarise_draws(mean, ~quantile2(., probs = c(.025, .975))) %>% 
  ungroup() %>% 
  mutate(
    across(c(mean, q2.5, q97.5), ~number(., .001)),
    res = as.character(str_glue("{mean} [{q2.5}, {q97.5}]")),
    Outcome = str_replace(outcome, "_", " "),
    Predictor = case_when(
      predictor == "val_year" ~ "Time",
      predictor == "i1_cw" ~ "Internet",
      predictor == "m1_cw" ~ "Mobile"
    ) %>% factor(levels = c("Time", "Internet", "Mobile"))
  ) %>% 
  select(
    Predictor, Outcome, variable, res
  ) %>% 
  mutate(res = if_else(res == "NA [NA, NA]", "", res)) %>% 
  pivot_wider(names_from = variable, values_from = res) %>% 
  mutate(Outcome = fct_inorder(Outcome)) %>% 
  select(Predictor, Outcome, Association, `SD (country)`, everything()) %>% 
  arrange(Predictor, Outcome)

het_tab %>% 
  select(-Association) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  apa_table(
    font_size = "small",
    placement = "htb",
    span_text_columns = TRUE,
    note = "Numbers indicate the standard deviations [95%CI] of the distributions of associations in the population of all countries."
  )
```

In the main manuscript, we focus on within-country associations between per capita internet users and mobile broadband subscriptions, and well-being and mental health outcomes. Critically, in addition to averages—which describe the within-country associations for the average country—our models describe variabilities in the trends and associations across countries, age groups, and their interaction (variability of age groups within countries). To put the average global estimates (Table \@ref(tab:table-1)) in context, we present their standard deviations in Table \@ref(tab:table-s1). This table shows that for all outcomes, i) the associations varied most across countries, compared to age groups and the age by country interaction; and ii) the average associations reported in Table \@ref(tab:table-1) should be qualified by the substantial variability across countries. These variabilities speak against a universal negative impact of internet technologies on well-being and mental health, to the extent that it is accurately represented in our models, which assume no time-varying confounders.

```{r table-s2}
#| include: true
t1 <- tab %>% 
  filter(Country != "World") %>% 
  count(Predictor, Outcome, d_nhst) %>% 
  group_by(Outcome, Predictor) %>% 
  mutate(sum = sum(n), p = n / sum) %>% 
  transmute(
    Predictor,
    Outcome,
    Decision = d_nhst,
    p = percent(p, 1)
  ) %>% 
  pivot_wider(names_from = Decision, values_from = p) %>% 
  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))

t2 <- tab %>% 
  filter(Country != "World", Predictor != "Time") %>% 
  count(Predictor, Outcome, d_rope) %>% 
  group_by(Outcome, Predictor) %>% 
  mutate(sum = sum(n), p = n / sum) %>% 
  transmute(
    Predictor,
    Outcome,
    Decision = d_rope,
    p = percent(p, 1)
  ) %>% 
  pivot_wider(names_from = Decision, values_from = p) %>% 
  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))

left_join(t1, t2, by = c("Predictor", "Outcome"), suffix = c("", " ")) %>% 
  mutate(
    Predictor = as.character(Predictor),
    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
  ) %>% 
  replace_na(
    list(Inconclusive = "", `Negative ` = "", `Null ` = "", `Positive ` = "")
  ) %>% 
  apa_table(
    font_size = "small",
    placement = "htb",
    span_text_columns = TRUE,
    note = "Numbers may not add up to 100% because of rounding.",
    col_spanners = list("Sign test" = c(3, 5), "ROPE test" = c(6, 9))
  )

# Save interactive table to country-table.html
tab %>% 
  mutate(
    Country = relevel(factor(Country), ref = "World"),
    d_nhst = factor(d_nhst),
    d_rope = factor(d_rope)
  ) %>% 
  datatable(filter = "top", rownames = FALSE) %>% 
  formatRound(4:12, 3) %>% 
  saveWidget("country-table.html", title = "Country-specific parameters")
```

Another way in which this variability can be summarised is to calculate proportions of countries where the association between internet adoption / mobile broadband adoption and well-being / mental health was credible negative, positive, or neither (null), or whether it was credibly outside the region of practical equivalence (ROPE) to zero as defined by the simple linear change in the outcome. The latter test allows quantifying evidence for four distinct propositions: Support for a credibly negative association, support for a credibly positive association, support for the null hypothesis (of smaller than meaningful association), and not enough support for either of the three alternatives (inconclusive) [@kruschkeBayesianNewStatistics2017]. We present these numbers in Table \@ref(tab:table-s2), which further highlights substantive between-country differences in well-being associations, and the fact that most associations were not credibly positive or negative at the country level—especially for mental health outcomes. Indeed, quantified in this manner, we find the null hypothesis in excess of 95% credibility for 8-15% of countries for the well-being outcomes, and 18-54% of countries for the mental health outcomes.

```{r table-s3}
#| include: true
get_cor_pars <- function(outcome, predictor, model) {
  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
  as_draws_df(
    x,
    variable = c(
      str_glue("b_{predictor}_Intercept"),
      "b_val_Intercept",
      str_glue("b_{predictor}_year"),
      "b_val_year",
      str_glue("sd_country__{predictor}_Intercept"),
      "sd_country__val_Intercept",
      str_glue("sd_country__{predictor}_year"),
      "sd_country__val_year",
      str_glue("cor_country__{predictor}_year__val_year"),
      str_glue("cor_country__{predictor}_Intercept__val_Intercept")
    )
  )
}
get_cor_pars <- memoise(get_cor_pars, cache = cd)

cor_pars_brm <- fits %>%
  mutate(
    internet = map(outcome, ~get_cor_pars(.x, "internet", "1")),
    mobile = map(outcome, ~get_cor_pars(.x, "mobile", "2"))
  )

cor_sum <- cor_pars_brm %>% 
  mutate(
    across(
      internet:mobile, 
      ~map(., ~describe_posterior(., centrality = "mean", test = "pd"))
    )
  )
cor_sum %>% 
  pivot_longer(-outcome, names_to = "Predictor") %>% 
  unnest(value) %>% 
  filter(str_detect(Parameter, "cor_")) %>% 
  mutate(
    Mean = number2(Mean, .01, pad = TRUE),
    across(CI_low:CI_high, ~number(., .01)), 
    pd = percent2(pd, .1)
  ) %>% 
  transmute(
    Predictor = str_to_title(Predictor),
    Correlation = if_else(
      str_detect(Parameter, "Intercept"), "Intercepts", "Slopes"
    ),
    Outcome = str_replace(outcome, "_", " "),
    Summary = str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})")
  ) %>% 
  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
  arrange(Correlation, Outcome) %>% 
  mutate(
    Correlation = if_else(Outcome == "Life satisfaction", Correlation, "")
  ) %>% 
  apa_table(
    font_size = "small",
    placement = "htb",
    span_text_columns = TRUE,
    note = "Numbers indicate the correlations [95%CI] between the intercepts and slopes of time of the corresponding outcome and internet / mobile broadband adoption."
  )
```

Our main analyses concerned within-country associations between internet / mobile broadband adoption and well-being / mental health. To test this association from another perspective, we also examined correlations in countries’ average levels of well-being and mental health on the one hand, and average levels of internet / mobile broadband adoption on the other. The first six rows of Table \@ref(tab:table-s3) ("Averages") shows that, between countries, internet and mobile broadband adoption positively predict life satisfaction, positive experiences, anxiety, and self-harm, and negatively predict negative experiences and depression.

An arguably stronger test of the idea that changes in internet / mobile broadband adoption predict changes in well-being and mental health is to correlate the country-specific rates of changes in the variables: Are countries with more rapid internet adoption also those countries where well-being declined faster? The answer in these data is in the negative (Table \@ref(tab:table-s3) ("Slopes")). Countries' slopes of internet adoption were negatively correlated with slopes of negative experiences, indicating that countries where internet penetration was fastest were also those where negative experiences decreased the most. In addition, slopes of mobile broadband adoption were positively correlated with slopes of life satisfaction and positive experiences, and negatively correlated with slopes of negative experiences, indicating that countries where mobile broadband penetration was most rapid were those where life satisfaction and positive experiences increased the most, and negative experiences increased the least.

### 2022-08-17 ms.Rmd
Improve outputs

@@
   chunk_output_type: console
+always_allow_html: true
 ---
@@
 library(DT)
+library(htmlwidgets)
 library(tidyverse)
@@
 
-# Create directory for intermediate files
+# Create directory for intermediate and output files
 dir.create(here("data"), FALSE)
+dir.create(here("Output"), FALSE)
 
@@
   ) %>% 
-  htmlwidgets::saveWidget("Figure-1-interactive.html")
+  saveWidget("Output/Figure-1.html")
 ```
@@
 
-# Save interactive table to country-table.html
+# Save interactive table
 tab %>% 
@@
   formatRound(4:12, 3) %>% 
-  saveWidget("country-table.html", title = "Country-specific parameters")
+  saveWidget("Output/Table-S2.html", title = "Country-specific parameters")
 ```

### 2022-09-26 models.R
Revise models

@@ -1,10 +1,10 @@
 # Independent script to fit models
 
-# command line argument must be 1-24 to pick a model from the combinations
+# command line argument must be 1-18 to pick a model from the combinations
 # of outcomes (6) and models (4)
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cmdargs <- as.numeric(cmdargs)
-if (length(cmdargs) == 0) cmdargs <- menu(c(1:24, "Abort"), "Choose model")
+if (length(cmdargs) == 0) cmdargs <- menu(c(1:18, "Abort"), "Choose model")
 
 # ---- setup ---------------------------------------------------------------
 
@@ -16,16 +16,16 @@ library(brms)
 # MCMC settings
 (ncores <- min(parallel::detectCores(logical = FALSE), 12))
 nchains <- 4
-options(brms.backend = "cmdstanr")
+options(brms.backend = "rstan")
 hmc <- list(
+  save_pars = save_pars(c("age", "country")),
   chains = nchains,
   cores = nchains,
-  threads = min(ncores %/% nchains, 3),
+  # threads = min(ncores %/% nchains, 3),
   iter = 4000,
   warmup = 2000,
   refresh = 100,
-  adapt_delta = .95,
-  max_treedepth = 10
+  control = list(adapt_delta = .95, max_treedepth = 10)
 )
 
 # Create directory for intermediate files
@@ -54,88 +54,65 @@ fits <- dat %>%
 
 # models ------------------------------------------------------------------
 
-# Bivariate internet & outcome on time
-bf_itu <- bf(
-  internet | subset(itu) ~
-    year +
-    (year |c| country),
-  family = gaussian()
-)
-bf_val <- bf(
+# Time only
+bf_t <- bf(
   val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
     year * sex +
-    (year * sex | c | country) +
+    (year * sex | country) +
     (year * sex | age) +
     (year * sex | age:country),
   family = gaussian()
 )
-# Model for well-being outcomes
-bf_1 <- bf_itu +
-  bf_val +
-  set_rescor(FALSE)
 # Simplified model for mental health outcomes
-bf_1.s <- bf_itu +
[…]

### 2022-09-26 submit.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 # Runs the R script models.R with arguments from --array
-# Use sbatch --array=1-24 submit.sh to submit
+# Submit on cluster with: sbatch --array=1-18 submit.sh
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=12

### 2022-09-27 models.R
Remove cmdstanr dep and update pkgs

@@ -10,7 +10,6 @@ if (length(cmdargs) == 0) cmdargs <- menu(c(1:18, "Abort"), "Choose model")
 
 options(tidyverse.quiet = TRUE)
 library(tidyverse)
-library(cmdstanr)
 library(brms)
 
 # MCMC settings

### 2022-09-28 ms.Rmd
Update links
Prune pkgs

@@
   This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.
-All code supporting this manuscript is available at <https://github.com/digital-wellbeing/global-wbmh>.
-This draft is available at psyarxiv.
+All code supporting this manuscript is available at <https://doi.org/10.5281/zenodo.7004053>.
+This draft is available at <https://doi.org/10.31234/osf.io/9tbjy>.
 
 abstract: |
-  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has had a harmful effect on mental health and psychological well-being.
+
+  \textbf{Abstract.} In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has had a harmful effect on mental health and psychological well-being.
 However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown.
@@
 We place an urgent call to increase the collaborative efforts between independent scientists and the internet technology sector.
+
+  \textbf{Statement of Relevance} tbd
+
 keywords: well-being, mental health, internet technology, technology effects
@@
 footnotelist: no
-header-includes:
-  - |
-    \makeatletter
-    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-1em}%
-      {\normalfont\normalsize\bfseries\typesectitle}}
-
-    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-      {-\z@\relax}%
-      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-    \makeatother
+# header-includes:
 
@@
     number_sections: false
+  bookdown::html_document2:
+    toc: true
+    toc_float:
+      collapsed: true
+      smooth_scroll: true
+    code_folding: hide
 editor_options: 
@@
 library(imputeTS)
-library(naniar)
 library(scales)
@@
 library(haven)
-library(ragg)
-library(khroma)
 library(labelled)
@@
 library(here)
-library(posterior)
 library(bayestestR)
-library(gtsummary)
-library(kableExtra)
-library(memoise)
-library(cachem)
 library(ggh4x)
-library(cmdstanr)
-library(ggstance)
 library(tidybayes)
@@
 library(DT)
-library(htmlwidgets)
 library(tidyverse)
@@
   cache = TRUE,
-  include = FALSE,
+  include = knitr::is_html_output(),  # Show code only in HTML
   warning = FALSE,
@@
 
-# Data frame for computing over models
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-fits <- tibble(outcome = oo) %>%
-  mutate(outcome = factor(outcome, levels = oo))
-
-# Create directory for intermediate and output files
+# Create directory for intermediate files
 dir.create(here("data"), FALSE)
-dir.create(here("Output"), FALSE)
-
-# Cache for memoised functions
-cd <- cache_disk("cache", max_size = Inf)
 
 # Plotting options
-# If you've defined a custom font, we will use it in outputs
 theme_set(
   theme_linedraw(
-    base_size = 8
+    base_size = 10
   ) +

### 2022-09-28 models.R

@@ -8,8 +8,8 @@ if (length(cmdargs) == 0) cmdargs <- menu(c(1:18, "Abort"), "Choose model")
 
 # ---- setup ---------------------------------------------------------------
 
-options(tidyverse.quiet = TRUE)
-library(tidyverse)
+library(dplyr)
+library(tidyr)
 library(brms)
 
 # MCMC settings
@@ -111,7 +111,7 @@ fits <- fits %>%
 
 hmc$data <- fits$data[[1]]
 hmc$formula <- fits$bfrm[[1]]
-hmc$file <- str_glue("{path}/brm-{fits$outcome[[1]]}-{fits$model[[1]]}")
+hmc$file <- paste0(path, "/brm-", fits$outcome[[1]], "-", fits$model[[1]])
 
 cat("\n\nNow fitting", hmc$file, "\n\n")
 

### 2022-10-26 ms.Rmd
Major revision

@@
     email: matti.vuorre@oii.ox.ac.uk
-    role:
-      - Conceptualization
-      - Data curation
-      - Formal analysis
-      - Investigation
-      - Methodology
-      - Project Administration
-      - Software
-      - Validation
-      - Visualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
   - name: Andrew K. Przybylski
@@
     email: andy.przybylski@oii.ox.ac.uk
-    role:
-      - Conceptualization
-      - Data curation
-      - Funding acquisition
-      - Investigation
-      - Methodology
-      - Project Administration
-      - Resources
-      - Supervision
-      - Visualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-
 affiliation:
@@
     institution: Oxford Internet Institute, University of Oxford
-
 authornote: |
   \noindent \textbf{This pre-print is not yet peer-reviewed.}
-
-  This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.
-All code supporting this manuscript is available at <https://doi.org/10.5281/zenodo.7004053>.
-This draft is available at <https://doi.org/10.31234/osf.io/9tbjy>.
-
 abstract: | 
-
-  \textbf{Abstract.} In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has had a harmful effect on mental health and psychological well-being.
+  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has impacted mental health and psychological well-being.
 However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown.
-We show that the past two decades have seen only small and inconsistent changes in global well-being and mental health.
-We demonstrate that the broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband has been psychologically harmful on a global level.
-Moreover, little or no negative associations were observed for adolescents—a group thought particularly vulnerable.
-Further investigation of this topic requires transparent study of online behaviours where they occur: on online communication, media, social media, and video game platforms.
-We place an urgent call to increase the collaborative efforts between independent scientists and the internet technology sector.
-
-  \textbf{Statement of Relevance} tbd
+We show that the past two decades have seen small and inconsistent changes in global well-being and mental health.
+The broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes.
+However, associations between internet technology adoption and depression and self-harm were strongest for individuals aged between 10 and 34.
+Further investigation of this topic requires transparent study of online behaviours where they occur, namely on online platforms.
+We call for increased collaborative efforts between independent scientists and the internet technology sector.
 
 keywords: well-being, mental health, internet technology, technology effects
-# wordcount: 
+wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
 bibliography: "references.bib"
@@
 # header-includes:
-
 csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
@@
     number_sections: false
-  bookdown::html_document2:
-    toc: true
-    toc_float:
-      collapsed: true
-      smooth_scroll: true
-    code_folding: hide
 editor_options: 
@@
 library(labelled)
+library(tidybayes)
+library(ggdist)
 library(countrycode)
-library(plotly)
 library(lubridate)
-library(kableExtra)
 library(brms)
+library(patchwork)
 library(knitr)
-library(here)
+library(ggstance)
 library(bayestestR)
 library(ggh4x)
-library(tidybayes)
-library(ggdist)
-library(DT)
 library(tidyverse)
@@
   cache = TRUE,
-  include = knitr::is_html_output(),  # Show code only in HTML
+  include = FALSE,
+  message = FALSE,
   warning = FALSE,
@@
 # Create directory for intermediate files
-dir.create(here("data"), FALSE)
+dir.create("data", FALSE)
 
@@
   theme_linedraw(
-    base_size = 10
+    base_size = if_else(knitr::is_latex_output(), 9, 8)
   ) +
@@
       strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
-      axis.text = element_text(size = rel(0.6)),
+      axis.text = element_text(size = rel(0.75)),
       axis.ticks = element_line(size = rel(0.3))
@@
 ```{r functions}
-#' Custom kableExtra formatting
-#'
-#' @param a table from kbl()
-#'
-#' @return a table
-kable_custom <- function(x) {
-  kable_classic(
-    kable_input = x,
-    # html_font = "Arial",
-    font_size = 11,
-    position = "center",
-    full_width = FALSE
-  )
-}
-
 # Function to replace extreme percentages
@@
   x
-}
-
-# Function to align positive and negative values
-number2 <- function(x, accuracy = .001, pad = FALSE) {
-  out <- number(
-    x,
-    accuracy = accuracy,
-    style_negative = "hyphen"
-    )
-
-  # Justify on decimal point
-  if (pad) {
-    # Add white space to start of non-negative numbers
-    out[str_starts(out, "[0-9]")] <- str_c(
-      " ", 
-      out[str_starts(out, "[0-9]")]
-    )
-  }
-  out
-
 }
@@
 # First liberate the data from the slow SPSS file and save to disk
-gwp_path <- here("data-raw/Gallup/gwp-processed.rds")
+gwp_path <- "data-raw/Gallup/gwp-processed.rds"
 if (!file.exists(gwp_path)) {
   gwp <- read_spss(
-    here("data-raw/Gallup/The_Gallup_101521.sav"),
+    "data-raw/Gallup/The_Gallup_101521.sav",
     col_select = c(
@@
   )
-
   # Get rid of SPSS attributes
@@
     zap_formats()
-
   # Save into a good format
@@
 
-# Scale scores note rescaling
+# Scale scores note rescaling to percentages
 gwp <- gwp %>%
   mutate(
-    Life_satisfaction = Life_satisfaction / 10,
+    Life_satisfaction = Life_satisfaction * 10,
     Negative_experiences =
-      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
+      (rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1) * 100,
     Positive_experiences =
-      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
+      (rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1) * 100
   ) %>%
@@
 
-# Check what names were changed and if any don't have harmonised counterpart
-gwp %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl() %>%
-  kable_custom()
-
 # We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
@@
 
-gwp_mock_path <- here("data-raw/gwp-MOCK.rds")
-if (dir.exists(here("data-raw/Gallup")) & !file.exists(gwp_mock_path)) {
+gwp_mock_path <- "data-raw/gwp-MOCK.rds"
+if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
   library(synthpop)
@@
 # Load if actual data doesn't exist
-if (!dir.exists(here("data-raw/Gallup"))) {
+if (!dir.exists("data-raw/Gallup")) {
   cat("Using synthetic GWP data.")
@@
 gbd <- list.files(
-  here("data-raw/GBD/"),
+  "data-raw/GBD/",
   pattern = ".zip", full.names = TRUE, recursive = TRUE
@@
 
-# First step is to clean names
+# First step is to clean names and remove unnecessary variables
 gbd <- clean_names(gbd)
-
-# Confirm that correct measures were downloaded:
 # distinct(gbd, measure, metric)
-gbd <- select(gbd, -metric, -measure)
+gbd <- select(gbd, -measure, -metric)
+
+# Rates to percentages
 gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 100000))
+  mutate(across(c(val, upper, lower), ~ .x / 1000))
 
@@
 
-# Check what names were changed and if any don't have harmonised counterpart
-gbd %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl() %>%
-  kable_custom()
 # Harmonise old names and replace only if harmonised name found
@@
 # Download data sets from the ITU website if not yet downloaded
-if (!file.exists(here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"))) {
+if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
   dir.create("data-raw/ITU")
   download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/PercentIndividualsUsingInternet.xlsx",
-    here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/July/PercentIndividualsUsingInternet.xlsx",
+    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
   )
   download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/FixedBroadbandSubscriptions_2000-2020.xlsx",
-    here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx")
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/December/MobileBroadbandSubscriptions_2007-2020.xlsx",
-    here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx")
+    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/July/MobileBroadbandSubscriptions_2007-2021.xlsx",
+    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
   )
@@
 
-# Read and reshape fixed broadband data
-itu_fixed <- read_xlsx(
-  here("data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"),
+# Read and reshape mobile broadband data
+itu_mobile <- read_xlsx(
+  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
   sheet = 2,
@@
 ) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(fixed = as.numeric(value)) %>%
-  select(country = Country, year, fixed)
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  here("data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"),
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
+  pivot_longer(-c(Indicator, Economy)) %>%
   separate(name, into = c("year", "variable")) %>%
@@
   mutate(mobile = as.numeric(value)) %>%
-  select(country = Country, year, mobile)
+  select(country = Economy, year, mobile)
 
@@
 itu_percent <- read_xlsx(
-  here("data-raw/ITU/PercentIndividualsUsingInternet.xlsx"),
+  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
   col_types = "text"
 ) %>%
-  pivot_longer(-c(Indicator, Country)) %>%
+  pivot_longer(-c(Indicator, Economy)) %>%
   separate(name, into = c("year", "variable")) %>%
@@
   mutate(internet = as.numeric(value)) %>%
-  select(country = Country, year, internet)
+  select(country = Economy, year, internet)
 
 # Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)
-
-# values (1-100) to proportions (0-1) and years to numbers
+itu <- reduce(list(itu_percent, itu_mobile), left_join)
+
+# years to numbers
 itu <- itu %>%
-  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
   mutate(year = as.numeric(year))
@@
 # Drop tables
-rm(itu_fixed, itu_mobile, itu_percent)
-
-# Harmonise countries
-# Check what names were changed and if any don't have harmonised counterpart
-itu %>%
-  distinct(country) %>%
-  arrange(country) %>%
-  mutate(
-    country_harmonised = countryname(country, destination = "cldr.short.en")
-  ) %>%
-  filter(country != country_harmonised | is.na(country_harmonised)) %>%
-  kbl() %>%
-  kable_custom()
+rm(itu_mobile, itu_percent)
 
@@
 # Summary
-itu_long %>%
-  group_by(name) %>%
-  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
+itu_sum <- itu_long %>%
+  filter(!(name=="mobile" & year < 2007)) %>% 
+  group_by(Metric = name) %>%
   summarise(
-    n_miss_orig = sum(is.na(value) & year >= min_year),
-    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
-    n_miss_imp = sum(is.na(value_i) & year >= min_year),
-    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
-    imputed = n_miss_orig - n_miss_imp
-  ) %>%
-  kbl() %>%
-  kable_custom()
+    total = n(), 
+    total_not_missing = sum(!is.na(value)),
+    missing = sum(is.na(value)),
+    imputed = sum(is.na(value) & !is.na(value_i))
+  )
 
@@
 
-regions %>% 
-  group_by(region) %>%
-  summarise(
-    N = n(),
-    Countries = str_c(country, collapse = ", ")
-  ) %>% 
-  kbl() %>% 
-  kable_custom()
-
-# Create lagged predictors
-itu <- itu %>% 
-  arrange(region, country, year) %>%
-  group_by(region, country) %>%
-  mutate(
-    across(
-      c(internet, mobile),
-      list(`1` = ~ lag(., 1)),
-      .names = "{str_sub(.col, 1, 1)}{.fn}"
-    )
-  ) %>% 
-  ungroup()
-
-# Centering predictors within and between countries
-itu <- itu %>%
-  # Grand mean centering so both components are zero-centered
-  mutate(across(c(i1, m1), ~. - mean(., na.rm = TRUE))) %>% 
-  group_by(country) %>%
-  mutate(
-    # Between
-    i1_cb = mean(i1, na.rm = TRUE),
-    m1_cb = mean(m1, na.rm = TRUE),
-    # Within
-    i1_cw = i1 - i1_cb, 
-    m1_cw = m1 - m1_cb
-  ) %>% 
-  ungroup()
-
 # Stack outcome data
@@
 
-# Center and scale year
+# Center year
 dat <- dat %>%
-  mutate(year = (year - 2010) / 10)
-
-# Identify values to use in MV models
-# Indicate unique ITU values for MV model
-dat <- dat %>%
-  # Unique values exist for each country-year, but must be given for each
-  # outcome
-  group_by(region, country, year, outcome) %>%
-  mutate(itu = 1:n() == 1, itum = 1:n() == 1) %>%
-  ungroup()
-
-# This prevents a glitch where rows where ITU==TRUE but internet is missing would not be included in model of val
-dat <- dat %>% 
-  mutate(
-    itu = if_else(itu & is.na(internet), FALSE, itu),
-    itum = if_else(itum & is.na(mobile), FALSE, itum)
-    )
+  mutate(year = (year - 2010))
 
@@
   mutate(across(c(sex, age), factor))
-
-# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
-dat <- dat %>%
-  mutate(across(c(val, se), ~ . * 100))
 
@@
   mutate(se = if_else(outcome == "Selfharm", 0, se))
-```
+
+# Save data for models
+saveRDS(dat, "data/data-all.rds")
+```
+
+In 2005, an estimated 17% of the global population used the internet, but by 2020 this number was already 59% [@ituITUICTStatistics2021].
+Accompanying the rapid spread of the internet, worries have proliferated that its broad adoption—and technologies enabled by it such as online games, smartphones, and social media—is actively harming its users, particularly adolescents [@carrShallowsHowInternet2010; @turkleAloneTogetherWhy2011].
+As a response, users and a growing number of national governments have acted in limiting access to online technologies [@buckleyChinaTightensLimits2021; @departmentfordigitalculturemedia&sportDraftOnlineSafety2021; @kattulaGamePoliciesContexts2021].
+
+However, evidence for widespread harms of online technologies is limited.
+Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020].
+Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2021], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
+A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted.
+As a consequence, much of the evidence purporting to show that internet technology adoption is associated with broad changes in well-being and mental health, or even causes negative outcomes, remains equivocal [@dickson2018screen; @hawkesCMOReportUnable2019].
+
+In this research we present two studies of global well-being and mental health in the internet age.
+In the first, we focus on three aspects of psychological well-being, and contrast them with yearly per-capita internet users and mobile broadband subscriptions, across 168 countries and 16 years.
+In the second we examine three mental health outcomes across 202 countries and 19 years.
+Our aim is to better understand: 1) How well-being and mental health have changed, on a global scale, during the past two decades of dramatic proliferation of internet technologies and connectivity; 2) How per-capita internet users and mobile broadband subscriptions predict country-level well-being and mental health within a given country and across countries; and 3) Assess the extent to which associations between internet technology adoption and well-being and mental health differ across age and sex and if they are specific to previously suggested vulnerable populations, such as young women.
+
+# Study 1: Well-being
+
+```{r gwp-data-summaries}
+gwp_sum <- gwp %>% 
+  group_by(outcome) %>% 
+  summarise(n = sum(n), cells = n()) %>% 
+  mutate(across(n:cells, ~number(., big.mark = ",")))
+```
+
+In Study 1, we focused on psychological well-being, as reflected in self-reports of life satisfaction, positive experiences, and negative experiences from `r gwp_sum$n[1]` individuals aged 15 to 89 across `r length(unique(gwp$country))` countries from `r paste0(range(gwp$year), collapse = " to ")`.
+We contrasted those observations with time series data of the countries' per capita internet users and mobile broadband subscriptions [@ituITUICTStatistics2021] to examine if and how internet and mobile broadband adoption predicted psychological well-being over the past two decades.
+
+## Transparency and Openness
+
+This study was not preregistered.
+All code used in this project, along with the GBD data, link to the ITU data, and a synthetic version of the GWP data are available at <https://doi.org/10.5281/zenodo.7004053>.
+Our sample size was determined by the number of available years, countries, and demographics in each respective dataset.
+
+## Methods
+
+### Internet adoption
+
+We identified the International Telecommunication Union's (ITU) database of information and communications technology (ICT) as the most comprehensive country-level source of time-series data on internet adoption [@ituITUICTStatistics2021].
+The ITU has collated, from 222 countries' statistical and telecommunications agencies, the yearly percentages of population using the internet from 2000 to `r max(itu$year)`, and yearly per capita broadband subscriptions from 2007 to `r max(itu$year)`.
+Our analyses used `r number(itu_sum[1, 3, drop = TRUE], big.mark = ",")` yearly internet percentages and `r number(itu_sum[2, 3, drop = TRUE], big.mark = ",")` broadband subscription rates; we imputed `r number(itu_sum[1, 5, drop = TRUE], big.mark = ",")` (`r number(itu_sum[2, 5, drop = TRUE], big.mark = ",")` mobile) intermediate missing values to this dataset using linear interpolation without extrapolation.
+
+### Subjective well-being
+
+We examined subjective well-being indicators from the Gallup World Poll (GWP), a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from `r length(unique(gwp$country))` countries from 2005 to 2021.
+The surveys are conducted face-to-face or via telephone, in the respondents' native language and by local interviewers.
+For details on the GWP sampling and survey methodology, see [@gallupGallupWorldPoll2020; @gallupHowDoesGallup2014].
+
+GWP measures subjective well-being with the positive and negative experience indices, which measure respondents' experienced well-being on the day before the survey with five items each.
+For positive experiences, these items are "Did you feel well-rested yesterday?"; "Were you treated with respect all day yesterday?"; "Did you smile or laugh a lot yesterday?"; "Did you learn or do something interesting yesterday?"; and "(Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?" And for negative experiences, the items are responses to "Did you experience the following feelings during a lot of the day yesterday?" with prompts "How about physical pain?"; "How about worry?"; "How about sadness?"; "How about stress?"; and "How about anger?" We aggregated both scales for each respondent by taking a mean of the five items.
+
+Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
+The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you.
+On which step of the ladder would you say you personally feel you stand at this time?", similar to the Cantril self-anchoring scale [@cantril1965pattern; @kapteynDimensionsSubjectiveWellbeing2015].
+For analyses, we converted these variables to percentages, and aggregated the `r gwp_sum[1, 2]` individuals' data to means and standard errors for each outcome, country, year, sex, and age (5-year age groups from 15 to 89 years) combination (`r gwp_sum[1, 3]` cells).
+
+### Data analysis
+
+We analysed the data with meta-analytic bayesian hierarchical regression models [@burknerBrmsPackageBayesian2017; @gelmanDataAnalysisUsing2007; @standevelopmentteamStanModelingLanguage2021].
+We first asked how the well-being outcomes had changed over time.
+To answer, we modelled each outcome (e.g.
+life satisfaction) on population level intercepts (we centred time on 2010), contrasts of time (in continuous years), sex (Female: 1, Male: -1), and their interaction.
+We allowed all coefficients to vary across countries, age groups, and the age by country interactions, and treated all outcomes as normally distributed.
+
+Before modelling the data, we aggregated the individual-level well-being values to means and standard errors for each country-year-age-sex combination, in order to facilitate the Hamiltonian Monte Carlo computations on large data, and to harmonise the analyses and inferences between Studies 1 and 2.
+Importantly, we note that because we modelled unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g.
+countries' population sizes.
+
+Our second research question asked how changes in internet technology adoption predicted well-being.
+To answer, we expanded the above model to include within-country centred per capita internet users (or mobile broadband subscriptions in a separate model) and its interaction with sex as predictors of the well-being outcome, and all their associated varying effects.
+We also included the between-country centered variable as a predictor to examine between-country associations between internet technology adoption and well-being.
+
+Importantly, we did not make the necessary strong assumptions required for identifying causal effects, and therefore highlight the descriptive nature of the resulting associations.
+For instance, we did not adjust for either time-invariant or -varying confounders, which could bias observed between-country and within-country associations, respectively.
+Nevertheless, we included time as a predictor to adjust for simple temporal trends.
+In addition, we within-country centred the internet technology adoption variables in order to isolate within-country associations from between-country associations.
+
+We specified the model as
+
+\begin{align*} 
+y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{se}^2_i}), \\
+\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
+&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
+&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
+&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
+&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{X}^{\text{CW}}_i + \\
+&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{X}^{\text{CW}}_i + \\
+&\quad\ \alpha_6 \text{X}^{\text{CB}}_i,
+\\
+\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}), \\
+\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}), \\
+\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country}),
+\end{align*}
+
+where $i$ indexes rows in the data and $\text{se}_i$ are the known standard errors.
+$\text{X}^{\text{CW}}_i$ and $\text{X}^{\text{CB}}_i$ are the within- and between-country centred internet technology adoption predictor (per capita internet users or mobile broadband subscriptions, in separate models), respectively.
+We used default noninformative priors on all parameters except the following population-level coefficients, that were modelled as
+
+\begin{align*}
+\alpha_{1,3-6} &\sim \text{Normal}(0, 1), \\
+\alpha_{2} &\sim \text{Normal}(0, 3), \\
+\sigma_{\gamma_4} &\sim \text{Normal}^+(0, 0.5).
+\end{align*}
+
+We used these priors to help model convergence, and on the assumption that differences in well-being between males and females are likely greater than differences associated with years, one-percent increases in technology adoption predictors, or the interaction terms.
+
+Our third research question asked whether any trends in well-being or its associations with internet or mobile broadband adoption were specific to adolescents or other demographic groups.
+To answer, the model allowed all parameters to vary randomly across the age groups and the age by country interaction.
+Therefore, each age group, on average and within each country, received their own partially pooled estimates [@gelmanDataAnalysisUsing2007].
+This bayesian approach to estimating age-specific associations is beneficial, given that the large number of age groups, especially within countries, would otherwise present difficulties with uncertain estimates and multiple comparisons.
+Therefore, we could compare younger age groups to older age groups, and investigate other contrasts, with confidence and without additional post-hoc adjustment procedures [@gelmanWhyWeUsually2012].
+
+We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
+We ran 4 HMC chains with 3,000 iterations and first 1,500 as warmup for 6,000 total iterations.
+We ensured that all population-level parameters' had converged using numeric diagnostics (all Rhats were within 0.01 of 1) and visual inspection of parameters' scatterplot matrices.
+
+## Results
 
 ```{r data-describe}
-bind_rows(
-  "GWP" = gwp,
-  "GBD" = gbd,
-  .id = "Dataset"
-) %>% 
-  mutate(Dataset = fct_inorder(Dataset)) %>% 
-  group_by(Dataset, region, outcome, country) %>% 
-  summarise(
-    n_n = sum(n),
-    n_year = length(unique(year))
-  ) %>% 
-  summarise(
-    N = sum(n_n), 
-    Years = mean(n_year)
-  ) %>%
-  summarise(
-    N_sum = round(mean(N)), 
-    Years_mean = round(mean(Years))
-  ) %>%
-  kbl() %>% 
-  kable_custom()
-tmp <- gwp %>% 
+gwp %>% 
   group_by(outcome) %>% 
@@
       mutate(Dataset = "ITU")
-  ) %>% 
-  kbl() %>% 
-  kable_custom()
-
-gwp %>% 
-  # filter(age %in% c("15 to 19", "50 to 54", "85 to 89")) %>% 
-  group_by(age) %>% 
-  summarise(
-    n = quantile(n, probs = c(.1, .5, .9)),
-    quantile = c("10%", "50%", "90%")
-  ) %>% 
-  pivot_wider(names_from = quantile, values_from = n) %>% 
-  kbl() %>% 
-  kable_custom()
-
-itu %>%
-  select(region, country, year, internet) %>%
-  mutate(internet = internet * 100) %>%
-  pivot_wider(names_from = year, values_from = internet) %>%
-  select(-country) %>%
-  tbl_summary(
-    by = region,
-    missing = "no",
-    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
-  ) %>%
-  add_overall(col_label = "Total") %>%
-  as_kable_extra() %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_custom()
-
-if (!file.exists(here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))) {
-  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", here("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx"))
+  )
+
+# Individuals using the internet per 100 inhabitants | World
+if (!file.exists(
+  "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")) {
+  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")
 }
-# Individuals using the internet per 100 inhabitants | World
-tmp <- read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
-tmp %>% 
-  kbl() %>% 
-  kable_custom()
-```
-
-```{r models-process}
+read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
+```
+
+```{r models-load}
 # Create a table of outcomes in appropriate order, so can map functions over this
@@
 )
-fits <- tibble(outcome = oo) %>% 
-  mutate(outcome = fct_inorder(outcome))
-
-# The files are huge and unwieldy to work with. We create smaller files for each by dropping samples of the age:country interaction random effects. It is then easier to post-process the models.
-dir.create("models-small", FALSE)
-
-replace_chain <- function(x) {
-  x %>%
-    select(
-      -starts_with("r_1"),
-      -starts_with("r_2"),
-      -starts_with("r_3"),
-      -starts_with("z_1"),
-      -starts_with("z_2"),
-      -starts_with("z_3"),
-      -starts_with("r_age:country"),
-      -starts_with("L_")
-    )
-}
-
-replace_chain_all <- function(x) {
-  if (!file.exists(str_glue("models-small/{x}"))) {
-    message(x)
-    out <- readRDS(str_glue("models/{x}"))
-    out$fit@sim$samples <- map(1:4, ~replace_chain(out$fit@sim$samples[[.]]))
-    saveRDS(out, str_glue("models-small/{x}"), compress = FALSE)
+
+fits <- tibble(
+  path = list.files("models", pattern = "brm-", full.names = TRUE),
+  outcome = basename(path)
+) %>%
+  separate(outcome, c("discard", "outcome", "model"), sep = "-") %>% 
+  mutate(model = str_extract(model, "[0-9]")) %>% 
+  filter(outcome %in% oo) %>% 
+  mutate(fit = map(path, readRDS)) %>% 
+  select(-c(path, discard)) %>% 
+  mutate(outcome = factor(outcome, levels = oo))
+fits_wb <- fits %>% 
+  filter(outcome %in% oo[1:3])
+fits_mh <- fits %>% 
+  filter(outcome %in% oo[4:6])
+rm(fits)
+```
+
+```{r gwp-model-diagnostics}
+if (length(list.files("diagnostics/wb")) == 0) {
+  rhats <- fits_wb %>% 
+    mutate(
+      out = map(
+        fit, 
+        ~describe_posterior(
+          .x, 
+          ci_method = "eti", 
+          test = NULL, 
+          effects = "all",
+          parameters = "^cor_|^sd_|^b_"
+        ) %>% 
+          as_tibble() %>% 
+          select(Parameter, Rhat, ESS)
+      )
+    ) %>% 
+    select(-fit) %>% 
+    unnest(out)
+
+  # Show a table of bad rhats
+  rhats %>%
+    filter(!near(Rhat, 1, tol = .01))
+
+  # Draw a scatterplot of parameters with 9 worst rhats
+  # Create a tabset of this in HTML output
+  rhats_sum <- rhats %>% 
+    group_by(outcome, model) %>% 
+    arrange(outcome, model, desc(abs(Rhat))) %>% 
+    slice(1:9) %>% 
+    summarise(v = list(str_c(Parameter))) %>% 
+    ungroup() %>% 
+    right_join(fits_wb)
+
+  dir.create("diagnostics/wb", FALSE, recursive = TRUE)
+  for (i in 1:nrow(rhats_sum)) {
+    x <- slice(rhats_sum, i)
+    path <- str_glue("diagnostics/wb/{x$outcome}-{x$model}.png")
+    png(path, width = 1200, height = 1200, res = 120)
+    pairs(x$fit[[1]]$fit, pars = x$v[[1]])
+    dev.off()
+
   }
 }
-
-walk(
-  list.files("models"),
-  ~replace_chain_all(.x)
-)
-
-parameter_summary <- function(outcome, model) {
-  path <- str_glue("models-small/brm-{outcome}-{model}.rds")
-  as_draws_df(
-    readRDS(path), 
-    variable = c("^b_", "^sd_", "^cor_"), 
-    regex = TRUE
-  ) %>%
-    summarise_draws(
-      mean, sd,
-      samples = length, 
-      default_convergence_measures()
-    )
-}
-parameter_summary <- memoise(parameter_summary, cache = cd)
-
-convergence_summary <- tibble(
-  path = list.files("models-small/", pattern = ".rds$", full.names = FALSE)
-) %>% 
-  separate(path, c("brm", "outcome", "model"), sep = "-") %>% 
-  select(-brm) %>% 
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(outcome) %>% 
-  mutate(model = str_extract(model, "[0-9]")) %>% 
-  mutate(parameters = map2(outcome, model, ~parameter_summary(.x, .y))) %>% 
-  unnest(parameters)
-
-convergence_summary %>% 
-  filter(abs(rhat) > 1.03) %>% 
-  arrange(outcome, model, variable) %>% 
-  kbl(digits = c(rep(2, 7), 0, 0)) %>% 
-  kable_custom()
-
-# Function to draw a pairsplot of variables `v` of model in `path` 
-dir.create(here("figures/diagnostics"), FALSE)
-pairsplot <- function(filename, v) {
-  out_path <- here(str_glue("figures/diagnostics/{basename(filename)}.png"))
-  if (!file.exists(out_path)) {
-    x <- readRDS(here(filename))
-    agg_png(
-      out_path,
-      width = W*1.2, height = W*1.2, units = "in", res = 160
-    )
-    pairs(x$fit, pars = v)
-    title(sub = out_path)
-    dev.off()
-  }
-}
-
-# Draw pairsplot for 10 worst rhats per model
-convergence_summary %>% 
-  group_by(outcome, model) %>% 
-  arrange(outcome, model, desc(rhat)) %>% 
-  slice(1:10) %>% 
-  ungroup() %>% 
-  group_by(outcome, model) %>% 
-  summarise(v = list(variable)) %>% 
-  mutate(path = str_glue("models-small/brm-{outcome}-{model}.rds")) %>% 
-  ungroup() %>% 
-  {walk2(.$path, .$v, ~pairsplot(.x, .y))}
-```
-
-```{r results}
-# Before drawing any plots, we need to extract/compute the relevant parameters from the models.
-We do that here: For each outcome, we get the countries' average changes over time (in the outcome, internet, and mobile) and associations with internet and mobile
-country_post_fun <- function(outcome) {
-
-  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
-  fit2 <- readRDS(str_glue("models-small/brm-{outcome}-2.rds"))
-  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
-  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))
-
-  out_outcome_year <- spread_draws(
-    fit1,
-    b_val_year, r_country__val[country, x] | country
-  ) %>% 
-    filter(x == "year") %>% 
-    ungroup() %>% 
-    rename(World = b_val_year) %>% 
-    mutate(y = "outcome")
-
-  out_internet_year <- spread_draws(
-    fit1,
-    b_internet_year, r_country__internet[country, x] | country
-  ) %>% 
-    filter(x == "year") %>% 
-    ungroup() %>% 
-    rename(World = b_internet_year) %>% 
-    mutate(y = "Internet")
-
-  out_mobile_year <- spread_draws(
-    fit2,
-    b_mobile_year, r_country__mobile[country, x] | country
-  ) %>% 
-    filter(x == "year") %>% 
-    ungroup() %>% 
-    rename(World = b_mobile_year) %>% 
-    mutate(y = "Mobile")
-
-  out_outcome_internet <- spread_draws(
-    fit3,
-    b_i1_cw, r_country[country, x] | country
-  ) %>% 
-    filter(x == "i1_cw") %>% 
-    ungroup() %>% 
-    rename(World = b_i1_cw) %>% 
-    mutate(y = "outcome")
-
-  out_outcome_mobile <- spread_draws(
-    fit4,
-    b_m1_cw, r_country[country, x] | country
-  ) %>% 
-    filter(x == "m1_cw") %>% 
-    ungroup() %>% 
-    rename(World = b_m1_cw) %>% 
-    mutate(y = "outcome")
-
-  out <- bind_rows(
-    out_outcome_year, 
-    out_internet_year,
-    out_mobile_year,
-    out_outcome_internet,
-    out_outcome_mobile
-  ) %>%  
-    select(x, y, everything(), -c(.chain, .iteration, .draw)) %>% 
-    # Add average to all but itself
-    mutate(across(-c(x, y, World), ~. + World)) %>% 
-    rename_with(~str_replace_all(., "\\.(?!\\.)", " ")) %>% 
-    mutate(
-      x = factor(
-        x, 
-        levels = c("year", "i1_cw", "m1_cw"),
-        labels = c("Time", "Internet", "Mobile")
-      )
-    )
-
-  out 
-}
-country_post_fun <- memoise(country_post_fun, cache = cd)
-country_post <- fits %>% 
-  mutate(
-    samples = map(outcome, country_post_fun),
-    summary = map(
-      samples, 
-      ~.x %>% 
-        group_by(x, y) %>% 
-        summarise_draws(
-          mean, 
-          ~quantile2(., probs = c(.025, .975)),
-          pd = ~pd(as.numeric(.))
-        ) %>% 
-        rename(country = variable)
-    )
-  )
-
-# Create scaling factors for decade-equivalent associations
-# There is a different scaling factor for each outcome,
-# even though they used the same internet/mobile values. That's because 
-# different countries were included by outcome, and its then most faithful
-# to the data to keep these separate by outcome.
-# Get each country's Time -> Predictor parameters
-scaling_factors <- country_post %>% 
-  select(outcome, summary) %>% 
-  unnest(summary) %>% 
-  filter(x == "Time", y != "outcome") %>% 
-  select(outcome, y, country, scaling = mean)
-
-# Find changes per decade per outcome for ROPE limits
-change_factors <- country_post %>% 
-  select(outcome, summary) %>% 
-  unnest(summary) %>% 
-  filter(x == "Time", y == "outcome") %>% 
-  select(outcome, country, change = mean)
-
-# Calculate sign and ROPE tests for time/internet/mobile -> outcomes
-summarise_all <- function(
-    posterior = country_post,
-    scaling_factors = scaling_factors,
-    change_factors = change_factors
-) {
-
-  # Posterior samples of all effects on outcomes
-  tab <- posterior %>% 
-    select(outcome, samples) %>% 
-    unnest(samples) %>% 
-    filter(y == "outcome") %>%
-    select(-y) %>%
-    pivot_longer(-c(outcome, x), names_to = "country") %>% 
-    # Drop NAs because some country-outcome combinations don't exist
-    drop_na(value) %>% 
-    # We will have raw and scaled results
-    rename(raw = value)
-
-  # Scale internet and mobile to decade-equivalents
-  tab <- tab %>% 
-    left_join(
-      scaling_factors %>% 
-        rename(x = y)
-    ) %>% 
-    mutate(scaling = if_else(x == "Time", 1, scaling)) %>% 
-    mutate(scaled = raw * scaling) %>% 
-    select(-scaling)
-
-  # Change associations with internet and mobile to units of 10% not 100%
-  tab <- tab %>% 
-    mutate(
-      raw = if_else(x == "Time", raw, raw / 10)
-    )
-
-  # Calculate the raw and scaled results for each outcome and predictor
-  tab <- tab %>% 
-    nest(data = c(raw, scaled)) %>% 
-    left_join(change_factors) %>% 
-    mutate(
-      out = map2(
-        data, change,
+```
+
+```{r gwp-model-process}
+# Extract the relevant parameters' summaries from the models
+tab_wb <- fits_wb %>% 
+  mutate(
+    out = map(
+      fit,
       ~describe_posterior(
         .x, 
+        effects = "all", 
         centrality = "mean", 
-          ci_method = "eti",
-          rope_range = c(-.y, .y), 
-          rope_ci = 1
-        )
-      )
-    ) %>% 
-    transmute(
-      Predictor = fct_inorder(x), 
-      Outcome = fct_inorder(str_replace(outcome, "_", " ")),
-      country, 
-      out
-    ) %>% 
-    arrange(Predictor, Outcome) %>% 
+        ci = 0.95, 
+        ci_method = "ETI", 
+        test = "pd",
+        diagnostic = NULL
+      )
+    )
+  ) %>% 
+  select(-fit) %>% 
   unnest(out) %>% 
-    # Clean the names a bit
-    rename(
-      rope = ROPE_Percentage,
-      mean = Mean,
-      low = CI_low,
-      high = CI_high
-    ) %>% 
-    # Put raw and scaled results on one row
-    pivot_wider(
-      names_from = Parameter,
-      values_from = c(mean, low, high, pd, rope),
-      names_glue = "{Parameter}_{.value}"
-    ) %>% 
-    # Leave symmetric ROPE limit in table
-    mutate(rope_limit = abs(ROPE_low)) %>% 
+  select(-CI)
+tab_wb <- tab_wb %>% 
+  # Clean parameter names
+  separate(
+    Parameter, 
+    into = c("factor", "country", "parameter"), 
+    sep = "\\[|\\]|,"
+  ) %>%
+  mutate(
+    parameter = if_else(
+      Effects == "fixed",
+      str_remove(factor, "^b_"),
+      parameter
+    ),
+    # Clean predictor name
+    Predictor = case_when(
+      parameter == "year" & model == "1" ~ "Time",
+      parameter == "i_cw" ~ "Internet",
+      parameter == "m_cw" ~ "Mobile"
+    ) %>% factor(., levels = c("Time", "Internet", "Mobile"))
+  ) %>% 
+  mutate(
+    cred = pd > .975
+  )
+
+```
+
+Figure \@ref(fig:fig-gwp-data)A describes the levels of internet and mobile broadband adoption, and the three well-being variables over time averaged over sex and age.
+Figure \@ref(fig:fig-gwp-data)A shows the universal global penetration of internet technologies in the past two decades, and suggests that in contrast, changes in well-being are likely to be small.
+
+```{r tab-gwp-estimates}
+avg_wb <- tab_wb %>% 
+  filter(Effects == "fixed") %>%
+  mutate(
+    Predictor = case_when(
+      factor == "b_year" & model == "1" ~ "Time Within country",
+      factor == "b_i_cw" ~ "Internet Within country",
+      factor == "b_m_cw" ~ "Mobile Within country",
+      factor == "b_i_cb" ~ "Internet Between countries",
+      factor == "b_m_cb" ~ "Mobile Between countries"
+    )
+  ) %>% 
+  drop_na(Predictor) %>% 
+  # Create a result string for table
+  mutate(
+    Estimate = str_glue(
+      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
+    ),
+    pd = percent2(pd)
+  ) %>% 
   select(
     Predictor, 
-      Outcome, 
-      Country = country, 
-      starts_with("raw_"), 
-      starts_with("scaled_"),
-      # pd is common to raw and scaled values, rope only applies to scaled values
-      pd = raw_pd,
-      rope = scaled_rope,
-      rope_limit,
-      -raw_rope, 
-      -scaled_pd
-    )
-
-  # Calculate decision based on pd and rope
-  tab <- tab %>% 
-    mutate(
-      d_nhst = case_when(
-        pd < 0.975 ~ "Null",
-        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
-        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
-      ),
-      d_rope = case_when(
-        scaled_high < rope_limit*-1 ~ "Negative",
-        scaled_low > rope_limit ~ "Positive",
-        rope > 0.95 ~ "Null",
-        TRUE ~ "Inconclusive"
-      )
-    )
-
-  # Return object
-  tab
-}
-summarise_all <- memoise(summarise_all, cache = cd)
-tab <- summarise_all(country_post, scaling_factors, change_factors)
-```
-
-In 2005, an estimated 17% of the global population used the internet, but by 2020 this number was already 59% [@ituITUICTStatistics2021].
-Accompanying the rapid spread of the internet, worries have proliferated that its broad adoption—and technologies enabled by it such as online games, smartphones, and social media—is actively harming its users, particularly adolescents [@carrShallowsHowInternet2010; @turkleAloneTogetherWhy2011].
-As a response, users and a growing number of national governments have acted in limiting access to online technologies.
-
-However, evidence for widespread harms of online technologies is limited.
-Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020].
-Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2021], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
-A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted.
-As a consequence, much of the evidence purporting to show that internet technology adoption causes negative outcomes remains anecdotal [@dickson2018screen; @hawkesCMOReportUnable2019].
-
-We examined six aspects of global psychological well-being [@gallupGallupWorldPoll2020] and mental health [@vosGlobalBurden3692020]: measures of life satisfaction, positive and negative psychological experiences, and rates of anxiety, depression, and self-harm from 2000 to 2021, using data from 2,359,264 individuals aged 15 to 89 from 164 countries and meta-analytic model estimates from 202 countries (Methods).
-We contrasted those observations with timeseries of countries’ per capita internet users and mobile broadband subscriptions [@ituITUICTStatistics2021] to examine if and how internet and mobile broadband adoption predicted fluctuations in global psychological well-being and mental health over the past two decades.
-
-```{r figure-1}
+    Outcome = outcome, 
+    Estimate,
+    pd
+  ) %>% 
+  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
+  mutate(
+    Predictor = factor(
+      Predictor, 
+      levels = c("Time", "Internet", "Mobile")
+    )
+  ) %>% 
+  arrange(Predictor, Outcome)
+
+avg_wb %>% 
+  mutate(
+    Estimate = str_glue("{Estimate} ({pd})"),
+  ) %>% 
+  select(-pd) %>% 
+  pivot_wider(names_from = x, values_from = Estimate) %>% 
+  group_by(Predictor) %>% 
+  mutate(i = 1:n()) %>% 
+  ungroup() %>% 
+  mutate(
+    Predictor = as.character(Predictor),
+    Predictor = if_else(i==1, Predictor, ''),
+    Outcome = str_replace(Outcome, "_", " ")
+  ) %>% 
+  select(-i) %>% 
+  replace_na(list(`Between countries` = '')) %>% 
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
+  apa_table(
+    caption = "Well-being: Population-level estimates",
+    span_text_columns = TRUE,
+    escape = FALSE,
+    note = "Estimates are percentage changes in outcomes associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
+LS: Life satisfaction, NE: Negative experiences, PE: Positive experiences.
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
+  )
+```
+
+We found that, for the average country, life satisfaction had remained relatively stable, whereas both negative and positive experiences had increased (Figure \@ref(fig:fig-gwp-data)B).
+Interestingly, the increase in negative experiences was nearly sixfold to that in positive experiences.
+Although we found a sizeable average increase in negative experiences, these results were mixed and so did not offer convincing evidence for consistent global changes in well-being during this period of global internet technology adoption, as would be expected if the latter had broad negative consequences.
+
+We then turned to our main question; understanding the extent to which internet technology adoption predicted changes in well-being.
+We expanded the model of temporal changes to also predict well-being from within- and between-country centred per capita internet users and mobile broadband subscriptions (Figure \@ref(fig:fig-gwp-data)B, Within-country associations).
+The within-country associations are our key estimates of interest and describe the extent to which a one-percent increase in a country's per capita internet users (or mobile broadband subscriptions) predict that country's well-being and mental health, adjusting for linear temporal trends.
+
+```{r fig-gwp-data}
 #| include: true
-#| out.width: "\\textwidth"
-#| fig.env: "figure*"
-#| fig.height: 5.4
-#| fig.cap: Time courses of per capita internet users (row one), mobile broadband subscriptions (row two), and six psychological well-being and mental health outcomes (rows three to eight).
-Lines indicate countries’ yearly means of the respective variable, aggregated across sex and age.
-An interactive version of this figure is available in the SOM.
-
-# Stack data sets
-# Assume all outcomes are proportions (0-1)
-# Draw small multiples figure, outcomes x regions
-d <- bind_rows(
-  gwp,
-  gbd
-)
-
-itu <- itu %>%
+#| fig.height: !expr ifelse(knitr::is_latex_output(), 7.6, 5)
+#| fig.cap: "\\textbf{A.} Time courses of per capita internet users (row one), mobile broadband subscriptions (row two), and three psychological well-being outcomes (rows three to five).
+Lines indicate countries' yearly means of the respective variable, aggregated across sex and age.
+\\textbf{B.} Posterior probability distributions of population-level associations (green: between countries, red: within countries) between each of three well-being outcomes and time, per capita internet users, and per capita mobile broadband subscriptions.
+Estimates are percentage changes in outcomes associated with a one year or percent increase in the predictor.
+Points and lines indicate posterior means and 95\\%CIs, filled points indicate that zero is not among the 95\\% most credible parameter values."
+
+p1 <- itu %>%
   select(
@@
   # Truncate mobile percentages for figure
-  mutate(Mobile = if_else(Mobile > 1.5, NaN, Mobile)) %>%
+  mutate(Mobile = if_else(Mobile > 150, NaN, Mobile)) %>%
   pivot_longer(
@@
     names_to = "outcome", values_to = "val"
-  )
-
-p1 <- bind_rows(itu, d) %>%
+  ) %>% 
+  bind_rows(gwp) %>%
   mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
@@
     # Display percentages
-    labels = ~. * 100,
     breaks = pretty_breaks(),
@@
     "Year",
-    breaks = make_date(c(2005, 2010, 2015, 2020)),
+    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
     date_labels = "'%y",
@@
     aes(
-      group = interaction(country, outcome), 
-      text = str_glue("{country} {year(year)} ({percent(mean)})")
+      group = interaction(country, outcome)
     ),
-    size = .15
+    size = .05, col = "dodgerblue3"
   ) +
@@
   )
-p1
-
-ggplotly(p1, tooltip = "text") %>% 
-  layout(
-    margin = list(t = 100, r = 100, b = 100, l = 100)
-  ) %>% 
-  saveWidget("Output/Figure-1.html")
-```
-
-Figure \@ref(fig:figure-1) describes these data: Countries’ yearly rates of per capita internet users and mobile broadband subscriptions, and six indicators of psychological well-being and mental health (the latter two averaged over sex and age).
-Figure \@ref(fig:figure-1) shows the universal global penetration of internet technologies in the past two decades, and suggests that in contrast, changes in well-being and mental health are likely to be small or mixed across countries.
-
-```{r table-1}
-#| include: true
-
-tmp <- tab %>% 
-  filter(Country == "World") %>% 
-  # Create a result string for table
-  mutate(
-    raw_result = str_glue(
-      "{number2(raw_mean, pad = TRUE)} [{number2(raw_low)}, {number2(raw_high)}] ({percent2(pd)})"
+
+x <- fits_wb %>% 
+  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
+  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
+  mutate(
+    Predictor = case_when(
+      parameter == "b_year" & model == "1" ~ "Time Within country",
+      parameter == "b_i_cw" ~ "Internet Within country",
+      parameter == "b_m_cw" ~ "Mobile Within country",
+      parameter == "b_i_cb" ~ "Internet Between countries",
+      parameter == "b_m_cb" ~ "Mobile Between countries"
+    )
+  ) %>% 
+  drop_na(Predictor, value) %>% 
+  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
+  mutate(
+    Predictor = factor(
+      Predictor, 
+      levels = c("Time", "Internet", "Mobile")
+    )
+  )
+p2 <- x %>%   
+  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
+  scale_color_brewer(
+    "Association", palette = "Set2", aesthetics = c("fill", "color")
+  ) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_x_continuous(
+    "Estimated linear association",
+    breaks = extended_breaks()
+  ) +
+  stat_halfeye(
+    aes(shape = stat(sign(xmax) == sign(xmin))),
+    position = position_dodge(.15), 
+    normalize = "xy", 
+    height = .8,
+    point_interval = "mean_qi",
+    fatten_point = 3,
+    point_fill = "white",
+    size = .25,
+    slab_alpha = .75,
+    adjust = 1.5,
+    .width = .95
+    ) +
+  facet_wrap(
+    "outcome", 
+    labeller = labeller(
+      .cols = as_labeller(~str_replace(., "_", " "))
     ),
-    scaled_result = str_glue(
-      "{number2(scaled_mean, pad = TRUE)} [{number2(scaled_low)}, {number2(scaled_high)}] ({percent2(rope)})"
-    ),
-    # ROPE doesn't make sense for change over time (it is ROPE)
-    scaled_result = if_else(
-      Predictor == "Time", "", as.character(scaled_result)
-    )
-  ) %>% 
-  select(
-    Predictor, 
-    Outcome, 
-    `Raw association` = raw_result, 
-    `Scaled association` = scaled_result
-  ) %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  ) 
-tmp %>%   
-  apa_table(
-    font_size = "small",
-    span_text_columns = TRUE,
-    note = "Raw associations are percentage changes in outcomes associated with a decade (Time) or 10% (Internet & Mobile) increase in the predictor.
-Numbers indicate posterior means, [95%CI], and (posterior probability of direction).
-Scaled associations are percentage changes in outcomes associated with per-decade change in the predictor ('decade-equivalent' association).
-Numbers indicate posterior means, [95%CI], and (posterior probability inside the region of practical equivalence; i.e.
-probability that the association is smaller than the per-decade change in the respective outcome)."
-  )
-```
-
-Parameter estimates from hierarchical models (Methods, Model 1; Table \@ref(tab:table-1), Time) did not convincingly show that global well-being or mental health had decreased during this period of global internet adoption, as would be expected if internet technologies had broad negative consequences.
-While life satisfaction overall had remained relatively stable, both negative and positive experiences had increased—although the former more so (6.8% [5.4, 8.2] per decade).
-Meta-analytic estimates of rates of anxiety [@vosGlobalBurden3692020] had increased by 0.07% [0.05, 0.08] globally, but depression and self-harm rates had decreased (by 0.09% [0.05, 0.11] and 0.02% [0.01, 0.03], respectively).
-
-We then predicted each outcome from time-lagged and within-country centred per capita internet users and mobile broadband subscriptions (Methods, Model 2; Table \@ref(tab:table-1), Internet & Mobile Raw associations).
-This association is our key estimate of interest and describes the extent to which an increase in a country’s per capita internet users and mobile broadband subscriptions predict that country’s well-being and mental health in the following year.
-Internet adoption did not predict any outcome at the 95% credibility level, but a 10% increase in per capita internet users predicted a 1.1% [-0.09, 2.24] increase in negative experiences for the average country with 96.4% posterior probability of direction.
-Mobile broadband, on the other hand, positively predicted life satisfaction (0.84% [0.20, 1.49]), with greater evidence for direction (99.6%).
-
-We then put the associations in context with simple temporal changes and created "decade-equivalent" associations by dividing the internet and mobile associations by their per-decade changes (Table \@ref(tab:table-1), Scaled associations).
-We then tested whether those associations were practically null at the 95% credibility level, practically meaningful (credibly greater), or inconclusive (not credibly smaller or greater) by comparing them to a region of practical equivalence to zero (ROPE) defined by the estimated (absolute) linear by-decade change in the outcome [@kruschkeBayesianNewStatistics2017].
-This allowed us to quantify evidence toward the null hypothesis of smaller than practically meaningful association.
-While internet adoption did predict increases in negative experiences with a 96.4% certainty of direction, the decade-equivalent association was smaller than a simple change per decade in negative experiences with 98.3% confidence.
-In other words, the magnitude of the predictive association between per capita internet users and negative psychological experiences was smaller than the decade-by-decade change in negative experiences (by about a half).
-This suggested that while internet adoption did predict increases in negative experiences, that magnitude is not practically meaningful when compared to overall temporal trends.
-
-On the other hand, the same reasoning regarding mobile broadband adoption and life satisfaction indicated 99.6% confidence of a global positive predictive association, and a 99.9% certainty that the association was (about 60 times) greater than the simple per-decade change in life satisfaction.
-This indicated that per capita mobile broadband subscriptions were a meaningfully large positive predictor of country-level life satisfaction (5.60% [1.31, 9.94]).
-In sum, the global predictive associations between internet and mobile broadband adoption and well-being and mental health were mixed and, in most cases, supported the null hypothesis of smaller than meaningful association (percentages in rightmost column of Table \@ref(tab:table-1)).
-
-```{r figure-2}
-#| include: true
-#| fig.height: 4
-#| out.width: "\\textwidth"
-#| fig.env: "figure*"
-#| fig.cap: Country-specific changes per decade (top row), and decade-equivalent associations with per capita internet users (middle; see text) and mobile broadband subscriptions (bottom).
-Points and lines indicate posterior means and 95\% CIs.
-Darker blue indicates that the parameter is credibly different from zero (with 95\% confidence).
-Countries are sorted from the greatest decrease to the greatest increase for that outcome.
-# Arrange points within panels such that the order of countries is same in the rows of each column, running from smallest time change to greatest time change.
-This is a rudimentary way to show correlation between the two.
-tmp <- tab %>% 
-  filter(Predictor == "Time", Country != "World") %>% 
-  arrange(raw_mean) %>% 
-  group_by(Outcome) %>% 
-  mutate(x_order = 1:n()) %>% 
-  select(Outcome, Country, x_order) %>% 
-  ungroup()
-
-tab %>% 
-  filter(Country != "World") %>% 
-  left_join(tmp) %>% 
-  # Factor order for colors
-  mutate(
-    color_nhst = recode(d_nhst, Null = "c", Negative = "b", Positive = "b")
-  ) %>% 
-  ggplot(aes(x_order, scaled_mean, col = color_nhst)) +
-  scale_color_brewer(palette = "Paired", direction = -1) +
-  # scale_color_manual(values = c("dodgerblue3", "dodgerblue1", "dodgerblue1")) +
-  scale_x_continuous("Country") +
-  scale_y_continuous(
-    "Estimated linear association (%)"
-  ) +
-  geom_hline(yintercept = 0, lty = 2, size = .2) +
-  geom_linerange(
-    size = .15,
-    aes(ymin = scaled_low, ymax = scaled_high)
+    scales = "free_x"
+  ) +
+  theme(
+    legend.position = "none",
+    axis.title.y = element_blank(),
+    panel.grid.major.x = element_line(
+      color = "black", linetype = "dotted", size = .1
+    )
+  )
+
+(p1 / p2) + 
+  plot_layout(heights = c(8, 2)) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r}
+fits_wb %>% 
+  filter(model != 1) %>% 
+  mutate(
+    sigma = map_dbl(
+      fit,
+      ~mean(as.data.frame(.x, variable = "sigma")$sigma)
+    )
+  )
+itu %>% 
+  pivot_longer(internet:mobile) %>% 
+  group_by(country, name) %>% 
+  mutate(increase = value - lag(value)) %>% 
+  group_by(name) %>% 
+  summarise(mean_yearly_increase = mean(increase, na.rm = TRUE))
+```
+
+Internet adoption did not predict any outcome at the 95% credibility level, but a 1% increase in per capita internet users predicted a `r avg_wb[6, 4]` increase in negative experiences for the average country with `r avg_wb[6, 5]` posterior probability of direction.
+Mobile broadband, on the other hand, positively predicted life satisfaction (`r avg_wb[10, 4]`), with greater evidence for direction (`r avg_wb[10, 5]`).
+In light of substantial residual standard deviations ranging from about 6 to 8 between predictors and outcomes, and average yearly increases in internet technology adoption (internet = 2.7%, mobile = 5.8%) the observed associations were very small.
+
+```{r fig-gwp-country}
+#| cache: false
+figure_country <- function(data) {
+  data %>% 
+    # Show countries and main relations
+    filter(factor == "r_country") %>% 
+    drop_na(Predictor) %>% 
+    # Take out countries with only time association from this figure
+    add_count(outcome, country) %>% 
+    filter(n > 1) %>% 
+    # Arrange per panel
+    group_by(Predictor, outcome) %>% 
+    arrange(Predictor, outcome, Mean) %>% 
+    mutate(y = 1:n()) %>% 
+    ggplot(aes(Mean, y, col = cred)) +
+    scale_color_manual(values = c("dodgerblue1", "dodgerblue3")) +
+    scale_y_discrete(
+      "Country",
+      # Fix country names
+      labels = ~str_replace_all(., "\\.", " ") %>% 
+        str_replace_all(., "’", "'"),
+      expand = expansion(.015)
+    ) +
+    scale_x_continuous(
+      "Estimated linear association",
+      breaks = extended_breaks(6), 
+      expand = expansion(c(0.01))
+    ) +
+    scale_shape_manual(values = c(21, 19)) +
+    scale_linetype_manual(values = c(1, 1, 1)) +
+    geom_linerangeh(
+      size = .1,
+      aes(xmin = CI_low, xmax = CI_high, linetype = cred)
     ) +
     geom_point(
-    size = .2
+      aes(shape = cred), 
+      size = .55, fill = "white", stroke = .2
+    ) +
+    guides(
+      linetype = "none", 
+      shape = "none",
+      color = guide_legend(override.aes = list(size = .5, stroke = 1))
     ) +
     facet_grid2(
-    Predictor~Outcome, 
+      Predictor~outcome,
       scales = "free",
@@
     theme(
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      panel.grid.major.x = element_line(
+        color = "black", linetype = "dotted", size = .1
+      ),
       legend.position = "none"
     )
-```
-
-These global trends and associations are meaningful summaries, but do not represent any specific country.
-Indeed, variability across countries dwarfed the average global trends and associations (Figure \@ref(fig:figure-2) and Table \@ref(tab:table-s1)).
-The first row of Figure \@ref(fig:figure-2) displays country-level trends over time for each of the six outcomes.
-There appear to be no universal trends that apply to all countries.
-The next two rows indicate decade-equivalent associations between well-being and mental health outcomes and per capita internet users and mobile broadband subscriptions, respectively.
-
-To summarize these country-specific associations, we calculated proportions of countries with credibly positive, negative, and null associations (Table \@ref(tab:table-s2)).
-Above we identified that internet adoption predicted modest increases in negative experiences for the average country with 96.4% confidence.
-Table \@ref(tab:table-s2) shows that this association was credibly positive (negative) for 31% (22%) of countries, and practically meaningfully so for 15% (12%).
-The null hypothesis was supported for 13% of countries.
-We observed similar percentages for the other well-being outcomes.
-For mental health outcomes, 92%-100% (across outcomes) of countries’ associations were not credibly negative or positive, and indeed supported the null hypothesis of non-meaningfully large association for 18-54% countries.
-This lack of consistent associations across countries, and support for the null hypothesis for many countries, should qualify any inferences concerning global associations and is evidence against the idea that the adoption of internet or mobile broadband have uniform global negative effects on well-being and mental health.
-
-These global and country-specific analyses are informative but shed no light on how internet and mobile broadband adoption might have different effects for different demographic groups.
-So we then examined variation across age and sex (for the average country) in the relations linking internet and mobile broadband adoption to psychological well-being and mental health.
-Table \@ref(tab:table-s1) shows that there was modest variation in the associations across age groups, and the variation was always smaller than the variation across countries.
-Age- and sex-specific estimates, for the average country, are shown in Figure \@ref(fig:figure-3).
-Notable cases where demography-specific trends emerged were life satisfaction, whose association with mobile broadband adoption was credibly positive for all but the youngest group of individuals (although variation in the age groups was modest; Table \@ref(tab:table-s1)); negative experiences, which had increased more for older age groups, and whose association with internet adoption was credibly positive for most age groups between 20 to 59; and positive experiences, which had increased more for females and the youngest and oldest age groups.
-
-```{r figure-3}
-#| include: true
-#| fig.height: 5
-#| out.width: "\\textwidth"
-#| fig.env: "figure*"
-#| fig.cap: Age- and sex-specific changes in well-being and mental health outcomes (top row), and their decade-equivalent (see text) associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row).
-Circles indicate females and triangles males.
-Darker blue indicates that the parameter is credibly different from zero (with 95\% confidence).
-summarise_demographics <- function(outcome) {
-
-  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
-  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
-  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))
-
-  out_outcome_year <- spread_draws(
-    fit1, 
-    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
-  ) %>% 
-    ungroup() %>% 
-    mutate(
-      World_Female = b_val_year + `b_val_year:sex1`*1,
-      World_Male = b_val_year + `b_val_year:sex1`*-1,
-      Age_Female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
-      Age_Male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
-    ) %>% 
-    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
-    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
-    pivot_longer(-.draw, names_to = "Variable") %>% 
-    # Throws a warning for Age cells in World rows (value doesn't exist)
-    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
-    mutate(Age = str_replace_all(Age, "\\.", " "))
-
-  out_outcome_internet <- spread_draws(
-    fit3, 
-    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
-  ) %>% 
-    ungroup() %>% 
-    mutate(
-      World_Female = b_i1_cw + `b_i1_cw:sex1`*1,
-      World_Male = b_i1_cw + `b_i1_cw:sex1`*-1,
-      Age_Female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
-      Age_Male = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
-    ) %>% 
-    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
-    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
-    pivot_longer(-.draw, names_to = "Variable") %>% 
-    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
-    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
-    # Rescale effect to "decade-equivalent"
-    bind_cols(
-      scaling_factors %>% 
-        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
-        select(scaling)
-    ) %>% 
-    mutate(value = value * scaling) %>% 
-    select(-scaling)
-
-  out_outcome_mobile <- spread_draws(
-    fit4, 
-    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
-  ) %>% 
-    ungroup() %>% 
-    mutate(
-      World_Female = b_m1_cw + `b_m1_cw:sex1`*1,
-      World_Male = b_m1_cw + `b_m1_cw:sex1`*-1,
-      Age_Female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
-      Age_Male = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
-    ) %>% 
-    select(.draw, age, starts_with("World_"), starts_with("Age_")) %>% 
-    pivot_wider(names_from = age, values_from = starts_with("Age_")) %>% 
-    pivot_longer(-.draw, names_to = "Variable") %>% 
-    separate(Variable, into = c("Level", "Sex", "Age"), sep = "_") %>% 
-    mutate(Age = str_replace_all(Age, "\\.", " ")) %>% 
-    # Rescale effect to "decade-equivalent"
-    bind_cols(
-      scaling_factors %>% 
-        filter(y == "Internet", country == "World", outcome == {{outcome}}) %>% 
-        select(scaling)
-    ) %>% 
-    mutate(value = value * scaling) %>% 
-    select(-scaling)
-
-  out <- bind_rows(
-    "Time" = out_outcome_year,
-    "Internet" = out_outcome_internet,
-    "Mobile" = out_outcome_mobile,
-    .id = "Predictor"
-  ) %>% 
-    mutate(Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")))
-
-  # Scaling factors are invariant to demography
-  out <- scaling_factors %>% 
-    filter(country == "World") %>% 
-    filter(outcome == {{outcome}}) %>% 
-    select(Predictor = y, scaling) %>% 
-    right_join(out) %>% 
-    mutate(scaling = if_else(Predictor == "Time", 1, scaling)) %>% 
-    rename(raw = value) %>% 
-    mutate(scaled = raw * scaling) %>% 
-    select(-scaling)
-
-  # Calculate demography-specific change-factors (how much outcome changed)
-  change_factors <- out %>% 
-    filter(Predictor == "Time") %>% 
-    group_by(Level, Sex, Age) %>% 
-    mean_qi(change = raw) %>% 
-    select(Level, Sex, Age, change)
-
-  # Then calculate pd and rope
-
-  # Change associations with internet and mobile to units of 10% not 100%
-  out <- out %>% 
-    mutate(
-      raw = if_else(Predictor == "Time", raw, raw / 10)
-    )
-
-  # Calculate the raw and scaled results for each outcome and predictor
-  out <- out %>% 
-    select(-.draw) %>% 
-    nest(data = c(raw, scaled)) %>% 
-    left_join(change_factors) %>% 
+}
+p_country_wb <- figure_country(tab_wb)
+```
+
+```{r gwp-demographics}
+wb_demo <- fits_wb %>% 
+  mutate(
+    x = factor(model, labels = c("year", "i_cw", "m_cw")),
+  ) %>% 
   mutate(
     out = map2(
-        data, change,
-        ~describe_posterior(
+      fit, x, 
+      ~bind_rows(
+        world = hypothesis(
           .x, 
-          centrality = "mean", 
-          ci_method = "eti",
-          rope_range = c(-.y, .y), 
-          rope_ci = 1
-        )
-      )
-    ) %>% 
-    transmute(
-      Predictor = factor(Predictor, levels = c("Time", "Internet", "Mobile")), 
-      Level, Sex, Age, out
-    ) %>% 
-    arrange(Predictor) %>% 
+          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0")
+        )$hypothesis,
+        age = hypothesis(
+          .x, 
+          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0"),
+          scope = "coef", group = "age"
+        )$hypothesis
+      )
+    )
+  ) %>% 
+  select(-fit) %>% 
   unnest(out) %>% 
-    # Clean the names a bit
-    rename(
-      rope = ROPE_Percentage,
-      mean = Mean,
-      low = CI_low,
-      high = CI_high
-    ) %>% 
-    # Put raw and scaled results on one row
-    pivot_wider(
-      names_from = Parameter,
-      values_from = c(mean, low, high, pd, rope),
-      names_glue = "{Parameter}_{.value}"
-    ) %>% 
-    # Leave symmetric ROPE limit in table
-    mutate(rope_limit = abs(ROPE_low)) %>% 
-    select(
-      Predictor, 
-      Level, Sex, Age,
-      starts_with("raw_"), 
-      starts_with("scaled_"),
-      # pd is common to raw and scaled values, rope only applies to scaled values
-      pd = raw_pd,
-      rope = scaled_rope,
-      rope_limit,
-      -raw_rope, 
-      -scaled_pd
-    )
-
-  # Calculate decision based on pd and rope
-  out %>% 
-    mutate(
-      d_nhst = case_when(
-        pd < 0.975 ~ "Null",
-        pd >= 0.975 & sign(raw_mean) == -1 ~ "Negative",
-        pd >= 0.975 & sign(raw_mean) == 1 ~ "Positive"
-      ),
-      d_rope = case_when(
-        scaled_high < rope_limit*-1 ~ "Negative",
-        scaled_low > rope_limit ~ "Positive",
-        rope > 0.95 ~ "Null",
-        TRUE ~ "Inconclusive"
-      )
-    )
-}
-summarise_demographics <- memoise(summarise_demographics, cache = cd)
-
-out <- fits %>% 
-  mutate(
-    out = map(
-      outcome,
-      ~summarise_demographics(.x)
-    )
-  )
-
-out %>% 
-  unnest(out) %>% 
-  # We'll use Age on the y axis, but also want to show the sex averages
-  mutate(Age = if_else(is.na(Age), Sex, Age)) %>% 
-  mutate(
-    Age = factor(
-      Age,
-      levels = c(
-        sort(levels(dat$age), decreasing = TRUE),
-        "Male", "Female"
-      )
-    )
-  ) %>%
-  mutate(
-    color_nhst = recode(d_nhst, Null = "a", Negative = "b", Positive = "b")
-  ) %>% 
-  ggplot(aes(scaled_mean, Age, col = color_nhst, shape = Sex)) +
-  scale_color_brewer(palette = "Paired") +
-  geom_vline(xintercept = 0, lty = 2, size = .2) +
+  mutate(Sex = if_else(str_detect(Hypothesis, "-1"), "Male", "Female")) %>% 
+  mutate(Group = if_else(is.na(Group), Sex, Group)) %>% 
+  mutate(
+    predictor = factor(
+      model, 
+      levels = 1:3, 
+      labels = c("Time", "Internet", "Mobile")
+    )
+  ) %>% 
+  mutate(cred = sign(CI.Lower) == sign(CI.Upper)) %>% 
+  mutate(
+    Group = factor(Group, levels = c("Female", "Male", levels(dat$age)))
+  )
+```
+
+```{r fig-gwp-demographics}
+#| cache: false
+figure_demographics <- function(data) {
+  data %>% 
+    ggplot(aes(Estimate, fct_rev(Group), col = Sex, shape = cred)) +
+    scale_color_brewer(palette = "Set2") +
+    scale_shape_manual(values = c(21, 19)) +
+    # Ensure zero shows
+    geom_blank(aes(x = 0)) +
     scale_x_continuous(
-    "Estimated linear association (%)",
+      "Estimated linear association",
       breaks = extended_breaks(5),
-    expand = expansion(.2)
-  ) +
-  geom_linerange(
-    aes(xmin = scaled_low, xmax = scaled_high),
+      expand = expansion(.15)
+    ) +
+    geom_linerangeh(
+      aes(xmin = CI.Lower, xmax = CI.Upper),
       size = .3,
@@
     geom_point(
-    size = .9,
+      size = 0.9,
+      fill = "white",
       position = position_dodge2v(
@@
     ) +
-  facet_grid(
-    rows = vars(Predictor),
+    guides(shape = "none") +
+    facet_grid2(
+      rows = vars(predictor),
       cols = vars(outcome),
-    scales = "free_x",
+      scales = "free_x", independent = "x",
       labeller = as_labeller(~str_replace(., "_", " "))
@@
       axis.title.y = element_blank(),
+      legend.position = "none",
+      panel.grid.major.x = element_line(
+        color = "black", linetype = "dotted", size = .1
+      )
+    )
+}
+
+p_demo_wb <- figure_demographics(wb_demo)
+```
+
+Our model also measured the extent to which internet technology adoption predicted well-being between countries.
+These between-country associations indicated, with high confidence, that countries with greater average levels of internet and mobile broadband adoption tended to report greater average levels of life satisfaction and positive experiences, and lower average levels of negative experiences (Figure \@ref(fig:fig-gwp-data)B, Between-country associations).
+However, this pattern is likely to reflect multiple other causes impinging on both well-being and internet technology adoption.
+
+These trends and associations are meaningful summaries of the average country among the `r length(unique(gwp$country))` examined, but do not represent specific countries which might have unique patterns of associations.
+Figure \@ref(fig:fig-gwp-parameters)A describes the country-level trends over time and associations linking per capita internet users and mobile broadband subscriptions to each of the three outcomes.
+There appeared to be no universal temporal trends that apply to all countries, whose estimates varied from significant decreases to substantial increases in well-being.
+Moreover, the associations between internet technology adoption and well-being varied significantly across countries, with some reporting substantial positive associations, and others large negative associations.
+
+```{r fig-gwp-parameters}
+#| cache: false
+#| include: true
+#| fig.height: !expr ifelse(knitr::is_latex_output(), 8.5, 6.8)
+#| fig.env: "figure*"
+#| fig.cap: "\\textbf{A.} Country-specific yearly changes in three well-being outcomes (Time), and their associations with per capita internet users (Internet) and mobile broadband subscriptions (Mobile).
+Points and lines indicate individual countries' posterior means and 95\\% CIs.
+Countries are sorted from the most negative to most positive estimate.
+Filled points indicate that the parameter's 95\\% credibility interval excludes zero (in both panels).
+We include a table of all countries' estimates in the online materials.
+\\textbf{B.} Age- and sex-specific (green: female, red: male) changes in three well-being outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row)."
+((p_country_wb /
+  p_demo_wb + theme(axis.text.y = element_text(size = rel(0.6)))) &
+  theme(text = element_text(size = 8))) +
+  plot_layout(heights = c(5.5, 4.5)) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r tab-sds}
+#| include: true
+#| eval: false
+tab_wb %>% 
+  filter(str_starts(factor, "sd_")) %>% 
+  separate(factor, c("factor", "term"), sep = "__") %>% 
+  filter(factor %in% c("sd_age", "sd_country")) %>% 
+  filter(
+    model == "1" & term == "year" | 
+      model != "1" & str_ends(term, "_cw")
+  ) %>% 
+  mutate(
+    # years, percentages
+    across(c(Mean:CI_high), ~if_else(model=="1", ., ./100)),
+    across(c(Mean:CI_high), ~number(., .001)),
+    res = as.character(str_glue("{Mean} [{CI_low}, {CI_high}]")),
+    Outcome = str_replace(outcome, "_", " "),
+    Predictor = factor(model, labels = c("Time", "Internet", "Mobile")),
+    variable = case_when(
+      factor == "sd_age" ~ "SD (age)",
+      factor == "sd_country" ~ "SD (country)"
+    )
+  ) %>% 
+  select(
+    Predictor, Outcome, variable, res
+  ) %>% 
+  pivot_wider(names_from = variable, values_from = res) %>% 
+  mutate(Outcome = fct_inorder(Outcome)) %>% 
+  select(Predictor, Outcome, `SD (country)`, everything()) %>% 
+  arrange(Predictor, Outcome) %>% 
+  mutate(
+    Predictor = as.character(Predictor),
+    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
+  ) %>%
+  apa_table(
+    font_size = "scriptsize",
+    placement = "htb",
+    span_text_columns = FALSE,
+    note = "Numbers indicate the standard deviations [95%CI] of the distributions of associations in the population of all countries."
+  )
+```
+
+```{r tab-gwp-props}
+wb_props <- tab_wb %>% 
+  filter(factor == "r_country") %>% 
+  drop_na(Predictor) %>% 
+  mutate(
+    Outcome = str_replace(outcome, "_", " "),
+    # Predictor = as.character(Predictor),
+    # Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
+  )
+wb_props2 <- wb_props %>% 
+  mutate(
+    x = case_when(
+      cred & sign(Mean)==-1 ~ "Negative",
+      cred & sign(Mean)==1 ~ "Positive",
+      TRUE ~ "Null"
+    )
+  ) %>% 
+  count(Outcome, Predictor, x) %>% 
+  arrange(Predictor, Outcome) %>% 
+  group_by(Outcome, Predictor) %>% 
+  mutate(n = str_glue("{n} ({percent(n/sum(n), 1)})")) %>%  
+  pivot_wider(names_from = x, values_from = n) %>% 
+  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%"))) %>% 
+  select(Predictor, Outcome, Negative, Null, Positive)
+wb_props2 %>%   
+  group_by(Predictor) %>% 
+  mutate(i = 1:n()) %>% 
+  ungroup() %>% 
+  mutate(
+    Predictor = as.character(Predictor),
+    Predictor = if_else(i==1, Predictor, '')
+  ) %>% 
+  select(-i) %>% 
+  apa_table(
+    placement = "htb",
+    span_text_columns = FALSE,
+    caption = "Well-being: Country-specific test summary",
+    note = "Numbers indicate counts and (percentages) of countries with different sign test results. Percentages may not add up to 100% because of rounding."
+  )
+```
+
+To summarize these country-specific associations, we calculated proportions of countries with credibly positive and negative associations.
+Above we identified that internet adoption predicted small increases in negative experiences for the average country with `r avg_wb$pd[6]` confidence.
+Table \@ref(tab:tab-gwp-props) shows that this association was credibly positive (negative) for `r str_sub(wb_props2[5,5], 1, 2)` (`r str_sub(wb_props2[5,3], 1, 2)`) countries.
+`r str_sub(wb_props2[4,5], 1, 2)` (`r str_sub(wb_props2[4,3], 1, 2)`) countries had positive (negative) associations between life satisfaction and per capita internet users.
+The associations linking positive experiences to per capita internet users were more often inconclusive.
+We observed similar numbers regarding associations linking well-being to per capita mobile broadband subscriptions: `r str_sub(wb_props2[7,5], 1, 2)` (`r str_sub(wb_props2[7,3], 1, 2)`) countries had a positive (negative) association between mobile broadband adoption and life satisfaction, whereas the numbers were only `r str_sub(wb_props2[8,5], 1, 2)` (`r str_sub(wb_props2[8,3], 1, 2)`) and `r str_sub(wb_props2[9,5], 1, 2)` (`r str_sub(wb_props2[9,3], 1, 1)`) for negative and positive experiences, respectively.
+This heterogeneity and lack of consistent associations across countries should qualify any inferences concerning global associations and is evidence against the idea that the adoption of internet or mobile broadband has had uniform global negative effects on well-being.
+
+These global and country-specific analyses are informative but shed no light on how internet and mobile broadband adoption might be differently associated with well-being across demographic groups.
+So we then examined variation across age and sex (for the average country) in the relations linking internet and mobile broadband adoption to psychological well-being.
+Age- and sex-specific estimates, for the average country, are shown in Figure \@ref(fig:fig-gwp-parameters)B.
+
+```{r}
+tmp <- tab_wb %>% 
+  filter(
+    Effects == "fixed", 
+    str_detect(parameter, ":sex1"), 
+    !(parameter=="year:sex1" & model != 1)
+  ) %>% 
+  mutate(
+    x = str_glue(
+      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
+      ), 
+    .keep = "unused"
+  ) %>% 
+  select(outcome, parameter, x, pd)
+tmp
+```
+
+We found that, for the average country, life satisfaction had increased more for females (`r tmp$x[1]`), and that both per capita internet users and mobile broadband subscriptions predicted slightly greater increases in life satisfaction for females than males (Internet: `r tmp$x[2]`; Mobile: `r tmp$x[3]`).
+Negative experiences had increased the least for youngest age group in our data, but slightly more overall for females than males (`r tmp$x[4]`).
+Similarly, positive experiences had increased most for the youngest and oldest age groups, and somewhat more overall for females (`r tmp$x[7]`).
+Overall, these demography-specific trends and associations indicated no clear patterns specific to a particular demographic group.
+Neither did they support the commonly offered narrative that young individuals, particularly young women, have experienced disproportionately large decrements in well-being in association with the adoption of internet technologies.
+
+## Discussion
+
+We examined the extent to which three indicators of psychological well-being had changed over time and in association with per capita internet users and mobile broadband subscriptions.
+Across 168 countries and 16 years, we found mixed support for changes in well-being over time and in association with internet technology adoption.
+Whereas life satisfaction, on average, had not changed over time or as a function of either per capita internet users, it was positively predicted by per capita mobile broadband subscriptions.
+We found that both negative and positive experiences had increased, but that their associations with internet technology adoption were not credibly different from zero at the 95% confidence level.
+Furthermore, there were large variations among these patterns of results between the countries studied, suggesting no consistent connection between internet technology adoption and country-level well-being.
+Finally, while some sex- and age-based differences emerged, none supported the idea that young individuals, or young women particularly, were the most at-risk group.
+Nevertheless, this analysis was necessarily constrained to a limited range of available outcomes reflecting subjective well-being [e.g.
+@jebbSubjectiveWellBeingWorld2020].
+In Study 2, we extended our investigation to mental health outcomes.
+
+# Study 2: Mental health
+
+In the second study we extended our investigation to focus on mental health, using meta-analytic rates of anxiety, depression, and self-harm from 2000 to 2019 among 202 countries, and their associations with internet technology adoption, in place of self-reported measures of psychological well-being.
+
+## Methods
+
+### Mental health outcomes
+
+We studied meta-analytic prevalence rates (per 100,000 individuals) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0) in 204 countries from 2000 to 2019 as estimated by the Institute for Health Metrics and Evaluation's (IHME) Global Burden of Disease 2019 (GBD) study [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020].
+The GBD collates heterogeneous data from all WHO member states' censuses, household surveys, civil registration and vital statistics, disease registries, health service use statistics, disease notifications, and other sources.
+It then aggregates data from these sources with bayesian meta-regression to produce country-specific yearly prevalence estimates.
+
+The GBD 2019 prevalence rate estimates are based on 19,773 data sources with varying coverage for individual countries; for details of the GBD 2019 methodology, see [@vosGlobalBurden3692020] and especially Appendix 1 therein.
+The prevalence rates are estimated for females and males in 5-year age groups, and are provided as the IHME meta-regression model's predicted rates and 95% credibility intervals; we converted the latter to approximate standard errors for our meta-analytic modelling strategy (see Study 1, Methods).
+
+We emphasize that the GBD estimates are not observed data, and therefore are accurate only to the extent that the GBD's data collection methods and modelling strategies are valid.
+We have compared the GBD estimates to the CDC's estimates of self-harm in the United States [@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources.
+We nevertheless argue that because the GBD provides the most comprehensive dataset of global mental health, studying these estimates is informative, but emphasize this caveat.
+The sample size for our analyses (combinations of country, year, sex, and age) was 130,560.
+
+### Data analysis
+
+We analysed the data in the same manner as in Study 1, but did not include varying parameters over the age by country interaction because the models did not converge due to invariance in the data.
+We also set the observed standard errors in the outcomes to zero for models of self-harm due to convergence problems.
+
+```{r gbd-model-diagnostics}
+if (length(list.files("diagnostics/mh")) == 0) {
+  rhats <- fits_mh %>% 
+    mutate(
+      out = map(
+        fit, 
+        ~describe_posterior(
+          .x, 
+          ci_method = "eti", 
+          test = NULL, 
+          effects = "all",
+          parameters = "^cor_|^sd_|^b_"
+        ) %>% 
+          as_tibble() %>% 
+          select(Parameter, Rhat, ESS)
+      )
+    ) %>% 
+    select(-fit) %>% 
+    unnest(out)
+
+  # Show a table of bad rhats
+  rhats %>%
+    filter(!near(Rhat, 1, tol = .01))
+
+  # Draw a scatterplot of parameters with 9 worst rhats
+  # Create a tabset of this in HTML output
+  rhats_sum <- rhats %>% 
+    group_by(outcome, model) %>% 
+    arrange(outcome, model, desc(abs(Rhat))) %>% 
+    slice(1:9) %>% 
+    summarise(v = list(str_c(Parameter))) %>% 
+    ungroup() %>% 
+    right_join(fits_mh)
+
+  dir.create("diagnostics/mh", FALSE, recursive = TRUE)
+  for (i in 1:nrow(rhats_sum)) {
+    x <- slice(rhats_sum, i)
+    path <- str_glue("diagnostics/mh/{x$outcome}-{x$model}.png")
+    png(path, width = 1200, height = 1200, res = 120)
+    pairs(x$fit[[1]]$fit, pars = x$v[[1]])
+    dev.off()
+
+  }
+}
+```
+
+```{r gbd-model-process}
+# Extract the relevant parameters' summaries from the models
+
+tab_mh <- fits_mh %>% 
+  mutate(
+    out = map(
+      fit,
+      ~describe_posterior(
+        .x, 
+        effects = "all", 
+        centrality = "mean", 
+        ci = 0.95, 
+        ci_method = "ETI", 
+        test = "pd",
+        diagnostic = NULL
+      )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  select(-CI)
+tab_mh <- tab_mh %>% 
+  # Clean parameter names
+  separate(
+    Parameter, 
+    into = c("factor", "country", "parameter"), 
+    sep = "\\[|\\]|,"
+  ) %>%
+  mutate(
+    parameter = if_else(
+      Effects == "fixed",
+      str_remove(factor, "^b_"),
+      parameter
+    ),
+    # Clean predictor name
+    Predictor = case_when(
+      parameter == "year" & model == "1" ~ "Time",
+      parameter == "i_cw" ~ "Internet",
+      parameter == "m_cw" ~ "Mobile"
+    ) %>% factor(., levels = c("Time", "Internet", "Mobile"))
+  ) %>% 
+  mutate(
+    cred = pd > .975
+  )
+
+```
+
+## Results
+
+```{r tab-gbd-estimates}
+avg_mh <- tab_mh %>% 
+  filter(Effects == "fixed") %>%
+  mutate(
+    Predictor = case_when(
+      factor == "b_year" & model == "1" ~ "Time Within country",
+      factor == "b_i_cw" ~ "Internet Within country",
+      factor == "b_m_cw" ~ "Mobile Within country",
+      factor == "b_i_cb" ~ "Internet Between countries",
+      factor == "b_m_cb" ~ "Mobile Between countries"
+    ) %>% fct_inorder
+  ) %>% 
+  drop_na(Predictor) %>% 
+  # Models were estimated with percentages, change to rates per 100k
+  mutate(
+    across(Mean:CI_high, ~ . * 1000)
+  ) %>% 
+  # Create a result string for table
+  mutate(
+    Estimate = str_glue(
+      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
+    ),
+    pd = percent2(pd)
+  ) %>% 
+  select(
+    Predictor, 
+    Outcome = outcome, 
+    Estimate,
+    pd
+  ) %>% 
+  arrange(Predictor, Outcome) %>% 
+  separate(Predictor, c("Predictor", "x"), extra = "merge")
+
+avg_mh %>% 
+  mutate(
+    Estimate = str_glue("{Estimate} ({pd})"),
+  ) %>% 
+  select(-pd) %>% 
+  pivot_wider(names_from = x, values_from = Estimate) %>% 
+  group_by(Predictor) %>% 
+  mutate(i = 1:n()) %>% 
+  ungroup() %>% 
+  mutate(
+    Predictor = as.character(Predictor),
+    Predictor = if_else(i==1, Predictor, ''),
+    Outcome = str_replace(Outcome, "_", " ")
+  ) %>% 
+  select(-i) %>% 
+  mutate(Outcome = str_replace(Outcome, "Selfharm", "Self-harm")) %>% 
+  replace_na(list(`Between countries` = '')) %>% 
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
+  apa_table(
+    # col.names = c("X", "Y", "Within country", "Between country"),
+    caption = "Mental health: Population-level estimates",
+    span_text_columns = TRUE,
+    # font_size = "scriptsize",
+    escape = FALSE,
+    note = "Estimates are changes in outcome rates associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
+  )
+```
+
+Because Study 2 concerned GBD's meta-analytic estimates of mental health rates, we observed much less variation in the variables over time than was the case with the well-being outcomes (Figure \@ref(fig:fig-gbd-data)A).
+Our results showed that rates of anxiety had increased (`r avg_mh$Estimate[1]`), whereas those of depression (`r avg_mh$Estimate[2]`) and self-harm (`r avg_mh$Estimate[3]`) had decreased, and the model certainty in each of these average trends was high (>99.9%).
+
+```{r fig-gbd-data}
+#| include: true
+#| fig.height: !expr ifelse(knitr::is_latex_output(), 6.6, 5)
+#| fig.cap: "\\textbf{A.} Time courses of GBD's meta-analytic country-specific estimates of rates of anxiety, depression, and self-harm.
+Lines indicate countries' yearly means of the respective variable, aggregated across sex and age.
+\\textbf{B.} Posterior probability distributions of population-level associations (green: between countries, red: within countries) between each of three mental health outcomes and time, per capita internet users, and per capita mobile broadband subscriptions.
+Estimates are percentage changes in outcomes associated with a one year or percent increase in the predictor.
+Points and lines indicate posterior means and 95\\%CIs, filled points indicate that zero is not among the 95\\% most credible parameter values."
+
+p1 <- gbd %>% 
+  mutate(outcome = fct_inorder(outcome)) %>%
+  group_by(region, country, year, outcome) %>%
+  summarise(mean = mean(val, na.rm = TRUE)) %>%
+  ungroup() %>% 
+  mutate(year = make_date(year)) %>%
+  mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm")) %>% 
+  ggplot(aes(year, mean)) +
+  scale_y_continuous(
+    "Rate per 100k individuals",
+    # From percentages in model to rates per 100k
+    labels = ~ number(. * 1000, big.mark = ","),
+    breaks = pretty_breaks(5),
+    expand = expansion(.05)
+  ) +
+  scale_x_date(
+    "Year",
+    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
+    date_labels = "'%y",
+    expand = expansion(.02)
+  ) +
+  geom_line(
+    aes(
+      group = interaction(country, outcome)
+    ),
+    size = .05, col = "dodgerblue3"
+  ) +
+  facet_grid(
+    outcome ~ region,
+    scales = "free_y",
+    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
+  ) +
+  theme(
     legend.position = "none"
   )
-```
-
-Rates of anxiety were negatively associated with per capita mobile broadband subscriptions for the youngest and oldest males and no other group.
-Both depression and self-harm had decreased overall, but those decreases were smallest for the youngest age groups.
-Self-harm was most positively associated with internet adoption and mobile broadband subscriptions for the youngest age groups, particularly for males in the latter case, a finding that runs contrary to the prevailing narrative of young females being most at risk.
-(In fact we observed no particularly negative associations for this group; Figure \@ref(fig:figure-3).)
-
-Up to this point we have examined associations linking internet and mobile broadband adoption to well-being and mental health within countries.
-It is also possible that countries with greater levels of internet technology adoption show lower levels of well-being and mental health if the former are adversely affecting the latter.
-Our models indexed these between-country associations with separate parameters (Methods), summarised in Table \@ref(tab:table-s3).
-We found that, across countries, greater average levels of per capita internet users and mobile broadband subscriptions were associated with greater levels of life satisfaction, positive experiences, anxiety, and self-harm, and lower levels of negative experiences and depression.
-Furthermore, countries with greatest increases in per capita internet users were not countries where well-being and mental health declined the most.
-To the contrary, increases in internet technology adoption were negatively correlated with increases in negative experiences, and positively correlated with increases in life satisfaction and positive experiences.
-That is, countries where internet and mobile broadband penetration was most rapid in this period were also those where well-being increased the most.
-Complementary to our patterns of findings regarding predictive associations within-countries, the cross-country associations between internet technology adoption and well-being and mental health did not lend support to the idea that the former has had worldwide (negative) impacts on the latter.
-
-The idea that the rapid and global penetration of the internet, and technologies enabled by it, is affecting well-being and mental health is compelling but not adequately tested.
-We tested the extent to which countries’ per-capita internet users and mobile broadband subscriptions predict levels of well-being and mental health, and found that, overall, there were few if any meaningfully large associations.
-In all cases but one—mobile broadband adoption predicted life satisfaction positively—these associations were smaller than the corresponding total changes in the outcomes over time (Table \@ref(tab:table-1)).
-The small observed associations were also qualified by substantive variability across countries (Figure \@ref(fig:figure-2)) and demographics (Figure \@ref(fig:figure-3)).
-Furthermore, countries where internet technologies were more widely or rapidly adopted were not those with lowest levels of, or fastest declines in, well-being and mental health.
-
-Our results do not support the view that the internet, and technologies enabled by it such as smartphones with internet access, are actively harming well-being or mental health globally, nor that adolescents, and females in particular, are vulnerable to a greater degree.
-Nevertheless, data and theory required to address this question at the causal level are absent.
-Consequently, our analyses cannot account for potential time-varying confounders.
-Our descriptions, therefore, are suggestive but do not provide strong evidence for, or against, causal relations.
-In addition, our results regarding mental health, while comprehensive, are necessarily and considerably less certain than those on well-being, due to the lack of diverse global data and our own reliance on GBD estimates of mental health.
+
+x <- fits_mh %>% 
+  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
+  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
+  mutate(
+    Predictor = case_when(
+      parameter == "b_year" & model == "1" ~ "Time Within country",
+      parameter == "b_i_cw" ~ "Internet Within country",
+      parameter == "b_m_cw" ~ "Mobile Within country",
+      parameter == "b_i_cb" ~ "Internet Between countries",
+      parameter == "b_m_cb" ~ "Mobile Between countries"
+    )
+  ) %>% 
+  drop_na(Predictor, value) %>% 
+  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
+  mutate(
+    Predictor = factor(
+      Predictor, 
+      levels = c("Time", "Internet", "Mobile")
+    )
+  )
+p2 <- x %>%   
+  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
+  scale_color_brewer(
+    "Association", palette = "Set2", aesthetics = c("fill", "color")
+  ) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_x_continuous(
+    "Estimated linear association",
+    breaks = extended_breaks(),
+    # From percentages in model to rates per 100k
+    labels = ~ . * 1000,
+  ) +
+  stat_halfeye(
+    aes(shape = stat(sign(xmax) == sign(xmin))),
+    position = position_dodge(.15), 
+    normalize = "xy", 
+    height = .8,
+    point_interval = "mean_qi",
+    fatten_point = 3,
+    point_fill = "white",
+    size = .25,
+    slab_alpha = .75,
+    adjust = 1.5,
+    .width = .95
+    ) +
+  facet_wrap(
+    "outcome", 
+    labeller = labeller(
+      .cols = as_labeller(~str_replace(., "_", " "))
+    ),
+    scales = "free_x"
+  ) +
+  theme(
+    legend.position = "none",
+    axis.title.y = element_blank(),
+    panel.grid.major.x = element_line(
+      color = "black", linetype = "dotted", size = .1
+    )
+  )
+
+(p1 / p2) + 
+  plot_layout(heights = c(7, 3)) +
+  plot_annotation(tag_levels = "A")
+```
+
+Then, to answer our primary research question, we examined the within-country predictive associations between internet technology adoption and mental health.
+We observed no credible (at the 95% level) associations between internet adoption and either anxiety, depression, or self-harm (Figure \@ref(fig:fig-gbd-data)B).
+Similarly, per capita mobile broadband subscriptions were not credible predictors of mental health for the average country, although the model indicated `r avg_mh$pd[10]` certainty of a negative association between mobile broadband adoption and rates of anxiety.
+
+We also examined the between-country associations linking internet technology adoption with mental health.
+Countries with greater levels of per capita internet users, on average, tended to be those with lower levels of depression, and higher levels of self-harm (Figure \@ref(fig:fig-gbd-data)B, Between country estimates).
+Similarly, per capita mobile broadband subscriptions predicted lower rates of both anxiety and depression, but higher rates of self-harm.
+
+We then examined the heterogeneity in the associations between countries.
+Although there were considerable differences in changes in anxiety, depression, and self-harm between countries, the associations varied less (Figure \@ref(fig:fig-gbd-parameters)A).
+We found that internet adoption was positively (negatively) associated with anxiety for three (seven) countries, with depression for one (zero) countries, and self-harm for seven (ten) countries (Table \@ref(tab:tab-gbd-props)).
+We include all countries' estimates in the online materials.
+
+```{r fig-gbd-country}
+#| cache: false
+p_country_mh <- figure_country(
+  tab_mh %>% 
+    mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm"))
+) +
+  scale_x_continuous(
+    "Estimated linear association",
+    # From percentages in model to rates per 100k
+    labels = ~ . * 1000,
+    breaks = extended_breaks(6), 
+    expand = expansion(c(0.01))
+  )
+```
+
+```{r gbd-demographics}
+mh_demo <- fits_mh %>% 
+  mutate(
+    x = factor(model, levels = 1:3, labels = c("year", "i_cw", "m_cw")),
+  ) %>% 
+  mutate(
+    out = map2(
+      fit, x, 
+      ~bind_rows(
+        world = hypothesis(
+          .x, 
+          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0")
+        )$hypothesis,
+        age = hypothesis(
+          .x, 
+          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0"),
+          scope = "coef", group = "age"
+        )$hypothesis
+      )
+    )
+  ) %>% 
+  select(-fit) %>% 
+  unnest(out) %>% 
+  mutate(Sex = if_else(str_detect(Hypothesis, "-1"), "Male", "Female")) %>% 
+  mutate(Group = if_else(is.na(Group), Sex, Group)) %>% 
+  mutate(
+    predictor = factor(
+      model, 
+      levels = 1:3, 
+      labels = c("Time", "Internet", "Mobile")
+    )
+  ) %>% 
+  mutate(cred = sign(CI.Lower) == sign(CI.Upper)) %>% 
+  mutate(
+    Group = factor(Group, levels = c("Female", "Male", levels(dat$age)))
+  ) %>% 
+  mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm"))
+```
+
+```{r fig-gbd-parameters}
+#| include: true
+#| #| cache: false
+#| fig.height: !expr ifelse(knitr::is_latex_output(), 8.5, 6.8)
+#| fig.env: "figure*"
+#| fig.cap: "\\textbf{A.} Country-specific yearly changes in three mental health outcomes (Time), and their associations with per capita internet users (Internet) and mobile broadband subscriptions (Mobile).
+Points and lines indicate individual countries' posterior means and 95\\% CIs.
+Countries are sorted from the most negative to most positive estimate.
+Filled points indicate that the parameter's 95\\% credibility interval excludes zero (in both panels).
+We include a table of all countries' estimates in the online materials.
+\\textbf{B.} Age- and sex-specific (green: female, red: male) changes in three mental health outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row)."
+p_demo_mh <- figure_demographics(mh_demo) +
+  # Adjust x-axes
+  scale_x_continuous(
+    "Estimated linear association",
+    breaks = extended_breaks(5),
+    expand = expansion(.1),
+    labels = ~. * 1000
+  )
+
+((p_country_mh /
+  p_demo_mh + theme(axis.text.y = element_text(size = rel(0.6)))) &
+  theme(text = element_text(size = 8))) +
+  plot_layout(heights = c(5.5, 4.5)) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r tab-gbd-props}
+mh_props <- tab_mh %>% 
+  filter(factor == "r_country") %>% 
+  drop_na(Predictor) %>% 
+  mutate(
+    Outcome = str_replace(outcome, "_", " "),
+    # Predictor = as.character(Predictor),
+    # Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
+  ) %>% 
+  mutate(outcome = str_replace(Outcome, "Selfharm", "Self-harm"))
+mh_props2 <- mh_props %>% 
+  mutate(
+    x = case_when(
+      cred & sign(Mean)==-1 ~ "Negative",
+      cred & sign(Mean)==1 ~ "Positive",
+      TRUE ~ "Null"
+    )
+  ) %>% 
+  count(Outcome, Predictor, x) %>% 
+  arrange(Predictor, Outcome) %>% 
+  group_by(Outcome, Predictor) %>% 
+  mutate(n = str_glue("{n} ({percent(n/sum(n), 1)})")) %>%  
+  pivot_wider(names_from = x, values_from = n) %>% 
+  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%"))) %>% 
+  select(Predictor, Outcome, Negative, Null, Positive)
+mh_props2 %>%   
+  group_by(Predictor) %>% 
+  mutate(i = 1:n()) %>% 
+  ungroup() %>% 
+  mutate(
+    Predictor = as.character(Predictor),
+    Predictor = if_else(i==1, Predictor, '')
+  ) %>% 
+  select(-i) %>% 
+  apa_table(
+    placement = "htb",
+    span_text_columns = FALSE,
+    caption = "Mental health: Country-specific test summary",
+    note = "Numbers indicate counts and (percentages) of countries with different sign test results. Percentages may not add up to 100% because of rounding."
+  )
+```
+
+```{r}
+tmp <- tab_mh %>% 
+  filter(
+    Effects == "fixed", 
+    str_detect(parameter, ":sex1"), 
+    !(parameter=="year:sex1" & model != 1)
+  ) %>% 
+  mutate(
+    x = str_glue("{percent(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"), 
+    .keep = "unused"
+  ) %>% 
+  select(outcome, parameter, x, pd)
+tmp
+```
+
+We then turned to our third research question, and studied how the associations linking internet technology adoption and mental health varied across demographic groups.
+Changes in the rates of anxiety showed a complex pattern, whereby older males rates of anxiety increased more than younger males, except the very youngest age group (Figure \@ref(fig:fig-gbd-parameters)B).
+For females, on the other hand, rates of anxiety increased least for the oldest and youngest groups.
+Overall, the difference in changes in anxiety between males and females was not credibly different from zero.
+Depression had decreased more for females than males (`r tmp$x[4]`), and for the middle age groups vs.
+the youngest and oldest groups.
+Self-harm had decreased slightly more for females, but the difference was not credibly different from zero, and for older groups vs.
+younger.
+
+Overall, the demography-based differences in the mental health-internet adoption associations were smaller than within the mental health trends (Figure \@ref(fig:fig-gbd-parameters)B).
+There were no sex differences in associations linking either per capita internet users or mobile broadband subscriptions to either mental health outcome that were credibly different from zero.
+Age-based differences in links with anxiety were small.
+However, depression was negatively and credibly associated with internet adoption for older age groups, but positively and credibly associated with per capita mobile broadband subscriptions for both sexes in the 10 to 14 and 15 to 19 year-old age brackets.
+Similarly, per capita internet users predicted self-harm negatively for older age groups in the 65 to 89 year-old brackets, but positively in the 10 to 34 year-old brackets.
+These results indicated some support for the idea that younger individuals' mental health may be more negatively associated with the adoption of internet technologies, although this finding was not consistent across the two different predictors or three different mental health outcomes.
+
+## Discussion
+
+In Study 2, we replicated the analyses regarding well-being in Study 1 using three mental health outcomes from a different dataset.
+We found mixed results regarding changes in the rates of mental health problems, whereby rates of anxiety had increased, but rates of depression and self-harm decreased, for the average country.
+Importantly, demography-based differences emerged: Younger age groups' rates of depression and self-harm were more positively predicted by both per capita internet users and mobile broadband subscriptions.
+
+# General discussion
+
+The idea that the rapid and global penetration of the internet, and technologies enabled by it, is affecting psychological well-being and mental health is compelling but not adequately tested.
+In two studies, we focused on the degree to which well-being and mental health had changed in the past two decades across most world countries, and found mixed results: Both negative and positive experiences had increased, as had meta-analytic rates of anxiety.
+Depression and self-harm, conversely, had decreased.
+These results align with other results that tend to be mixed or find few changes over time [@borAreChildAdolescent2014; @collishawAnnualResearchReview2015; @cosmaCrossNationalTimeTrends2020; @keyesRecentIncreasesDepressive2019].
+In addition, although previous reports have suggested increasing mental health problems specific to young females [e.g.
+@borAreChildAdolescent2014], we did not find support for such changes for the average country.
+
+We then measured the extent to which countries' per capita internet users and mobile broadband subscriptions predicted those countries' levels of well-being and mental health.
+We found that, overall, there were few if any meaningfully large average associations.
+In all cases but one---mobile broadband adoption predicted life satisfaction positively---these associations were not credibly different from zero (Figure \@ref(fig:fig-gwp-data)B).
+The small observed associations were also qualified by substantive variability across countries (Figure \@ref(fig:fig-gwp-parameters)A) and demographics (Figure \@ref(fig:fig-gwp-parameters)B).
+Furthermore, countries where internet technologies were more widely adopted overall were not those with lowest levels of well-being and mental health.
+
+Finally, we found large age-based differences in associations linking internet technology adoption and mental health outcomes.
+Both depression and self-harm were more positively associated with per capita internet users and mobile broadband subscriptions in the younger age brackets---including the youngest studied here at 10 to 14 years---than they were for older age groups.
+Studies on the association between internet technology use and mental health across wide age ranges are scarce.
+Nevertheless, while we found few gender differences, our results are in line with one study reporting that cross-sectional associations between social media use and life satisfaction are more negative at specific time windows in adolescence [@orbenWindowsDevelopmentalSensitivity2022].
+
+Our results do not provide evidence supporting the view that the internet, and technologies enabled by it such as smartphones with internet access, are actively promoting or harming either well-being or mental health globally.
+Our results also suggest that age- and sex-based differences in associations linking internet technology adoption and well-being are small.
+However, we did find evidence suggesting that internet technology adoption is more negatively associated with young individuals' mental health than older groups' (whose associations were, in some cases, positive).
+
+It is important to note that the data and theory required to address this question at the causal level are absent.
+Consequently, our analyses cannot account for potential confounders in the associations linking mental health and well-being to internet technology adoption.
+Our descriptions, therefore, are suggestive but are not intended to provide evidence for, or against, causal relations.
+Although the first to study this topic within a global perspective, future studies should investigate other potential differences based on demographic, economic, and cultural factors, which we could not address here.
+In addition, our results regarding mental health, while comprehensive, are necessarily and considerably less certain than those on well-being, due to the lack of diverse global data and our own reliance on GBD estimates in place of objective measurements of mental health.
 
@@
 
+# Material availability and ethics
+
+All the data-analytic code and a synthetic GWP dataset to facilitate the verification, extension, and critique of our procedures are available at <https://doi.org/10.5281/zenodo.7004053>.
+The ITU data, along with a complete list of years, countries, and sources of data are freely available at <https://www.itu.int/en/ITU-D/Statistics/Pages/stat/default.aspx>.
+The GWP data are available to subscribing institutions through Gallup.
+The GBD data are freely available at <http://ghdx.healthdata.org/gbd-results-tool>.
+
+This study and methods therein were approved by the University of Oxford Central University Research Ethics Committee (SSH_OII_CIA_21_084).
+
+# Author contributions
+
+MV: Conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing - original draft preparation, writing - review & editing.
+AKP: Conceptualization, funding acquisition, investigation, methodology, project administration, resources, supervision, visualization, writing - original draft preparation, writing - review & editing.
+
+# Conflicts of interest
+
+The authors declare no competing interests. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
+
+# Acknowledgements
+
+We thank Niklas Johannes for feedback on this work.
+The authors would like to acknowledge the use of the University of Oxford Advanced Research Computing (ARC) facility in carrying out this work http://dx.doi.org/10.5281/zenodo.22558.
+
+# Funding
+
+This research was supported by the Huo Family Foundation and Economic and Social Research Council Grant ES/T008709/1.
+
 # References
@@
 
-# Methods
-
-## Internet adoption
-
-We identified the International Telecommunication Union’s (ITU) database of information and communications technology (ICT) as the most comprehensive country-level source of time-series data on internet adoption [@ituITUICTStatistics2021].
-The ITU has collated, from 222 countries’ statistical and telecommunications agencies, the yearly percentages of population using the internet from 2000 to 2020, and yearly per capita broadband subscriptions from 2007 to 2020.
-Our analyses used 3,857 yearly internet percentages and 2,260 broadband subscription rates; we imputed 95 (70 mobile) intermediate missing values to this dataset using linear interpolation without extrapolation.
-Our online analysis supplement contains a complete list of years, countries, and sources of data underlying the ITU ICT data.
-The ITU ICT data are freely available at <https://www.itu.int/en/ITU-D/Statistics/Pages/stat/default.aspx>.
-
-## Subjective well-being
-
-We examined subjective well-being indicators from the Gallup World Poll (GWP), a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from 164 countries from 2005 to 2021.
-The surveys are conducted face-to-face or via telephone, in the respondents’ native language and by local interviewers.
-For details on the GWP sampling and survey methodology, see [@gallupGallupWorldPoll2020; @gallupHowDoesGallup2014].
-GWP measures subjective well-being with the Positive (PE) and Negative Experience (NE) indices.
-The PE and NE indices measure respondents’ experienced well-being on the day before the survey with five items each.
-For PE, these items are:
-
-- Did you feel well-rested yesterday?
-- Were you treated with respect all day yesterday?
-- Did you smile or laugh a lot yesterday?
-- Did you learn or do something interesting yesterday?
-- (Did you experience the following feelings during a lot of the day yesterday?) How about enjoyment?
-
-And for NE, the items are responses to "Did you experience the following feelings during a lot of the day yesterday?":
-
-- How about physical pain?
-- How about worry?
-- How about sadness?
-- How about stress?
-- How about anger?
-
-We aggregated both scales for each respondent by taking a mean of the five items.
-Life satisfaction in the moment was measured with one 11-step Likert item, "Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
-The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you.
-On which step of the ladder would you say you personally feel you stand at this time?", similar to the Cantril self-anchoring scale [@cantril1965pattern; @kapteynDimensionsSubjectiveWellbeing2015].
-For analyses, we converted these variables to percentages, and aggregated the 2,359,264 individuals’ data to means and standard errors for each country, year, sex, and age (5-year age groups from 15 to 89 years) combination (58,379 cells).
-The GWP data are available to subscribing institutions through Gallup.
-
-## Mental health
-
-We studied prevalence rates (per 100 population; hereafter percentages) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0) in 204 countries from 2000 to 2019 as estimated by the Institute for Health Metrics and Evaluation’s (IHME) Global Burden of Disease 2019 study (GBD; [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020]).
-The GBD collates heterogeneous data from all WHO member states’ censuses, household surveys, civil registration and vital statistics, disease registries, health service use, disease notifications, and other sources.
-It then aggregates data from these sources with Bayesian meta-regression to produce country-specific yearly prevalence estimates.
-
-The GBD 2019 prevalence rate estimates are based on 19,773 data sources with varying coverage for individual countries; for details of the GBD 2019 methodology, see [@vosGlobalBurden3692020] and especially Appendix 1 therein.
-The prevalence rates are estimated for females and males in 5-year age groups, and are provided as the IHME meta-regression model’s predicted means and 95% credibility intervals; we converted the latter to approximate standard errors for our meta-analytic modelling strategy (see below).
-
-We emphasize that the GBD estimates are not observed data, and therefore are accurate only to the extent that the GBD’s data collection methods and modelling strategies are valid.
-We have compared the GBD estimates to the CDC’s estimates of self-harm in the United States[@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources.
-We nevertheless argue that because the GBD provides the most comprehensive dataset of global mental health, studying these estimates is informative, but emphasize this caveat.
-The sample size for our analyses (combinations of country, year, sex, and age) was 130,560.
-The GBD data are freely available at <http://ghdx.healthdata.org/gbd-results-tool>.
-
-## Material availability and ethics
-
-The supplementary online materials (SOM) of this manuscript contain all the data-analytic code, GBD and ITU data, and a synthetic GWP dataset to facilitate the verification, extension, and critique of our procedures (<https://digital-wellbeing.github.io/global-wbmh/>).
-This study and methods therein were approved by the University of Oxford Central University Research Ethics Committee (SSH_OII_CIA_21_084).
-
-## Data analysis
-
-We analysed the data with meta-analytic bayesian hierarchical regression models [@burknerBrmsPackageBayesian2017; @gelmanDataAnalysisUsing2007; @standevelopmentteamStanModelingLanguage2021].
-Our first research question focused on changes over time in the mental health and well-being outcomes and internet adoption metrics.
-For each well-being and mental health outcome $y$ (e.g.
-life satisfaction) and internet adoption metric $x$ (e.g.
-per capita mobile broadband subscriptions), we specified a multivariate model of $y$ and $x$ on population level intercepts ($\alpha_0$; we centred time on the year 2010), contrasts of time (in decades, $\alpha_1$), sex (-1: Female; 1: Male; $\alpha_2$), and their interaction ($\alpha_3$).
-We allowed all coefficients to vary across countries, age groups, and the age by country interactions for models of the well-being outcomes.
-We did not include the age by country interaction for the GBD mental health outcomes because the models did not converge due to invariance in the data.
-
-The multivariate normal distributions of the country-level deviations were shared across models of $y$ and $x$, allowing examining the extent to which country-level deviations from the average in levels (intercepts) and changes (slopes) of well-being and mental health correlated with the corresponding levels and changes in internet and mobile broadband adoption.
-Because we modelled aggregated data (GWP) and model estimates (GBD), we incorporated the observed standard errors in the model.
-We set this standard error to zero for models of self-harm due to convergence problems.
-We treated all outcomes as normally distributed.
-We specified Model 1 as
-
-\begin{align*}
-y_i &\sim \text{Normal}(\mu^y_i, \sigma^{y2}v_i) \\
-x_i &\sim \text{Normal}(\mu^x_i, \sigma^{x2}) \\ 
-\mu^y_i &= \alpha^{y}_{0} + \beta^{y}_{0\text{country}[i]} + \gamma^{y}_{0\text{age}[i]} + \delta^{y}_{0\text{age:country}[i]} + \\ 
-&\quad\ (\alpha^{y}_{1} + \beta^{y}_{1\text{country}[i]} + \gamma^{y}_{1\text{age}[i]} + \delta^{y}_{1\text{age:country}[i]})\text{Time}_i + \\
-&\quad\ (\alpha^{y}_{2} + \beta^{y}_{2\text{country}[i]} + \gamma^{y}_{2\text{age}[i]} + \delta^{y}_{2\text{age:country}[i]})\text{Sex}_i + \\
-&\quad\ (\alpha^{y}_{3} + \beta^{y}_{3\text{country}[i]} + \gamma^{y}_{3\text{age}[i]} + \delta^{y}_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i \\
-\mu^x_i &= \alpha^{x}_{0} + \beta^{x}_{0\text{country}[i]} + (\alpha^x_{1} + \beta^{x}_{1\text{country}[i]})\text{Time}_i \\
-\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}) \\
-\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}) \\
-\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country})
-\end{align*}
-
-where $i$ indexes rows in the data and $v_i$ are the known sampling variances.
-Because we incorporated deviations from the average parameters (intercept, linear change (Time), sex, and the change by sex interaction) for each country, age, and age by country interactions, we obtained shrinkage estimates specific to countries, age groups, and age groups within countries that are robust to multiple comparisons [@gelmanWhyWeUsually2012].
-Of particular interest are the $\rho_{\beta_0^y\beta_0^x}$ and $\rho_{\beta_1^y\beta_1^x}$) correlations in $\Sigma^\text{country}$, indicating the correlations between country-level deviations in the levels and changes in internet and mobile broadband adoption, and well-being and mental health.
-
-Aggregating the well-being outcomes to means ($y_i$) and sampling variances ($v_i$) for each country-year-sex-age group facilitated the Hamiltonian Monte Carlo [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021] computations on otherwise large data and enabled applying the same models to the well-being and mental health outcomes, the latter of which are meta-analytic estimates for these groupings.
-Allowing the coefficients to vary randomly across age groups (and their interactions with countries) allowed inferences to and contrasts between age groups that were robust to multiple comparisons [@gelmanAnalysisVarianceWhy2005; @gelmanWhyWeUsually2012].
-Specifying the country-level deviations across parameters on $y$ and $x$ in the same distributions allowed assessing their correlations that accounted for uncertainty in the country-level estimates.
-
-Importantly, we note that because we model unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g.
-population size.
-This means that our inferences pertain to (demographics within) countries, and not to individual people.
-
-Our second research question asked whether changes in internet adoption predicted changes in well-being within countries.
-To answer, we expanded Model 1 to include the 1-year-lagged value of internet or mobile broadband adoption, within-country-centred, and its interaction with sex as predictors of the well-being outcome.
-We specified Model 2 as
-
-\begin{align*} 
-y_i &\sim \text{Normal}(\mu_i, \sigma^{y2}v_i) \\
-\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
-&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
-&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
-&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
-&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{Internet}^{\text{t-1}}_i + \\
-&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{Internet}^{\text{t-1}}_i + \\
-&\quad\ \alpha_6 \text{Internet}^{\text{t-1[CB]}}_i
-\\
-\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}) \\
-\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}) \\
-\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country})
-\end{align*}
-
-where $\text{Internet}^{\text{t-1[CB]}}_i$ is the country-specific grand-mean centred mean of the lagged internet / mobile broadband adoption value for the country on row $i$.
-
-We chose to use a lagged predictor to take a first step in moving this inquiry toward examining causal associations.
-Because our hypothesized treatment, per capita internet users and mobile broadband subscriptions, is at the country-level, it is likely that any possible effect mediated by the group rather than the individuals themselves would manifest only over time and not immediately.
-Therefore, a lagged association would capture potential causal effects better than a contemporary association, but we highlight that this is only an initial step toward examining causality: We do not make the necessary strong assumptions required for identifying causal effects.
-For instance, we don’t adjust for either time-invariant (Model 1) or time-varying (Model 2) confounders, which could bias observed between-country and within-country associations, respectively.
-Nevertheless, including time as a predictor gives some preliminary adjustment for simple temporal trends.
-In addition, we within-country centred the lagged internet adoption so that we could isolate within-country associations from between-country associations.
-We believe the latter are much more likely to be confounded, and the former to better approximate causal associations (keeping in mind the above caveats.)
-
-Our third research question asked whether any trends in well-being and mental health or their associations with internet or mobile broadband adoption were specific to adolescents.
-To answer, the models above allowed all parameters to vary randomly across the age groups and the age by country interaction.
-Therefore, each age group, on average and within each country, received their own partially pooled estimates [@gelmanDataAnalysisUsing2007].
-This bayesian approach to estimating age-specific associations is beneficial, given that the large number of age groups, especially within countries, would otherwise present difficulties with uncertain estimates and multiple comparisons.
-Instead, partial pooling allowed us to do any desired comparison, such as comparing younger age groups to older age groups, with confidence and without additional post-hoc adjustment procedures [@gelmanWhyWeUsually2012].
-
-We conducted all data analyses with the R language for statistical computing [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan’s Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
-We used default noninformative priors, 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations; we report all parameters with their posterior means and 95% credible intervals (posterior 2.5 and 97.5 percentiles; CI), and other posterior probabilities as indicated in text.
-
-# Acknowledgements
-
-We thank Niklas Johannes for feedback on this work.
-The authors would like to acknowledge the use of the University of Oxford Advanced Research Computing (ARC) facility in carrying out this work http://dx.doi.org/10.5281/zenodo.22558.
-
-# Author Contributions
-
-A.K.P.: Conceptualization, Data curation, Funding acquisition, Investigation, Methodology, Project administration, Resources, Supervision, Visualization, Writing - original draft, and Writing - review & editing.
-M.V.: Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Project administration, Software, Validation, Visualization, Writing - original draft, and Writing - review & editing.
-
-# Competing Interests Declaration
-
-The authors declare no competing interests. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
-
-# Supplementary analyses
-
-<!-- Prepend table numbers with S and reset counter -->
+\clearpage
+\onecolumn
+
+\begin{center}
+\textbf{Supplementary online material to \emph{Global well-being and mental health in the internet age} (Vuorre \& Przybylski)}
+\end{center}
+
+<!-- Prepend table & figure numbers with S and reset counters -->
+\setcounter{page}{1}
 \setcounter{table}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-
-```{r table-s1}
-#| include: true
-get_het_pars <- function(outcome, predictor, model) {
-  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
-  draws <- as_draws_df(
-    x,
-    variable = c(
-      str_glue("^b_{predictor}$"),
-      str_glue("^sd_age__{predictor}$"),
-      str_glue("^sd_country__{predictor}$"),
-      str_glue("^sd_age:country__{predictor}$")
+\setcounter{figure}{0}
+\renewcommand{\thetable}{SOM\arabic{table}}
+\renewcommand{\thefigure}{SOM\arabic{figure}}
+
+## Well-being: Country-specific parameters
+
+```{r, tab-gwp-props}
+#| include: !expr knitr::is_latex_output()
+```
+
+```{r}
+#| include: !expr knitr::is_latex_output()
+table_of_countries <- function(data, x) {
+
+  # Display MH as rates per 100k individuals
+  m <- if_else(x == "Mental health", 1000, 1)
+
+  data %>% 
+    filter(factor == "r_country") %>% 
+    drop_na(Predictor) %>% 
+    mutate(
+      across(Mean:CI_high, ~. * m),
+      Estimate = str_glue(
+        "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}] ({percent2(pd)})"
       ),
-    regex = TRUE
-  ) %>% 
-    select(-c(.chain, .iteration, .draw)) %>% 
-    # From 100% to 10% units for associations
-    mutate(across(-contains("val_year"), ~ ./10)) %>% 
-    rename_with(~str_remove(., str_glue("{predictor}")))
-  draws
+      outcome = str_replace(outcome, "_", " ")
+    ) %>% 
+    select(
+      Outcome = outcome,
+      Predictor, 
+      Country = country,
+      Estimate
+    ) %>% 
+    pivot_wider(names_from = Outcome, values_from = Estimate) %>% 
+    mutate(
+      across(
+        2:5, 
+        ~if_else(
+          str_starts(., "-"), 
+          ., 
+          paste0("\\phantom{-}", .)
+        )
+      ),
+      across(2:5, ~ifelse(is.na(.), "", .))
+    ) %>% 
+    arrange(Predictor, Country) %>% 
+    mutate(Country = str_replace_all(Country, "\\.(?!\\.)", " ")) %>% 
+    apa_table(
+      longtable = TRUE, 
+      escape = FALSE,
+      font_size = "scriptsize",
+      caption = str_glue("{x}: Country-specific estimates"),
+      note = "Estimates are changes in the outcome associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
+    )
 }
-
-get_het_pars <- memoise(get_het_pars, cache = cd)
-
-het_pars <- fits %>% 
-  crossing(
-    nesting(predictor = c("val_year", "i1_cw", "m1_cw"), model = c(1, 3, 4))
-  ) %>%
-  mutate(
-    out = pmap(
-      list(outcome, predictor, model), 
-      ~get_het_pars(..1, ..2, ..3))
-  )
-het_tab <- het_pars %>% 
-  unnest(out) %>%
-  select(-model) %>% 
-  rename(
-    Association = b_,
-    `SD (age)` = sd_age__,
-    `SD (country)` = sd_country__,
-    `SD (age * country)` = `sd_age:country__`,
-  ) %>%
-  group_by(outcome, predictor) %>% 
-  summarise_draws(mean, ~quantile2(., probs = c(.025, .975))) %>% 
-  ungroup() %>% 
-  mutate(
-    across(c(mean, q2.5, q97.5), ~number(., .001)),
-    res = as.character(str_glue("{mean} [{q2.5}, {q97.5}]")),
-    Outcome = str_replace(outcome, "_", " "),
-    Predictor = case_when(
-      predictor == "val_year" ~ "Time",
-      predictor == "i1_cw" ~ "Internet",
-      predictor == "m1_cw" ~ "Mobile"
-    ) %>% factor(levels = c("Time", "Internet", "Mobile"))
-  ) %>% 
-  select(
-    Predictor, Outcome, variable, res
-  ) %>% 
-  mutate(res = if_else(res == "NA [NA, NA]", "", res)) %>% 
-  pivot_wider(names_from = variable, values_from = res) %>% 
-  mutate(Outcome = fct_inorder(Outcome)) %>% 
-  select(Predictor, Outcome, Association, `SD (country)`, everything()) %>% 
-  arrange(Predictor, Outcome)
-
-het_tab %>% 
-  select(-Association) %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  ) %>% 
-  apa_table(
-    font_size = "small",
-    placement = "htb",
-    span_text_columns = TRUE,
-    note = "Numbers indicate the standard deviations [95%CI] of the distributions of associations in the population of all countries."
-  )
-```
-
-In the main manuscript, we focus on within-country associations between per capita internet users and mobile broadband subscriptions, and well-being and mental health outcomes.
-Critically, in addition to averages—which describe the within-country associations for the average country—our models describe variabilities in the trends and associations across countries, age groups, and their interaction (variability of age groups within countries).
-To put the average global estimates (Table \@ref(tab:table-1)) in context, we present their standard deviations in Table \@ref(tab:table-s1).
-This table shows that for all outcomes, i) the associations varied most across countries, compared to age groups and the age by country interaction; and ii) the average associations reported in Table \@ref(tab:table-1) should be qualified by the substantial variability across countries.
-These variabilities speak against a universal negative impact of internet technologies on well-being and mental health, to the extent that it is accurately represented in our models, which assume no time-varying confounders.
-
-```{r table-s2}
-#| include: true
-t1 <- tab %>% 
-  filter(Country != "World") %>% 
-  count(Predictor, Outcome, d_nhst) %>% 
-  group_by(Outcome, Predictor) %>% 
-  mutate(sum = sum(n), p = n / sum) %>% 
-  transmute(
-    Predictor,
-    Outcome,
-    Decision = d_nhst,
-    p = percent(p, 1)
-  ) %>% 
-  pivot_wider(names_from = Decision, values_from = p) %>% 
-  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))
-
-t2 <- tab %>% 
-  filter(Country != "World", Predictor != "Time") %>% 
-  count(Predictor, Outcome, d_rope) %>% 
-  group_by(Outcome, Predictor) %>% 
-  mutate(sum = sum(n), p = n / sum) %>% 
-  transmute(
-    Predictor,
-    Outcome,
-    Decision = d_rope,
-    p = percent(p, 1)
-  ) %>% 
-  pivot_wider(names_from = Decision, values_from = p) %>% 
-  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%")))
-
-left_join(t1, t2, by = c("Predictor", "Outcome"), suffix = c("", " ")) %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  ) %>% 
-  replace_na(
-    list(Inconclusive = "", `Negative ` = "", `Null ` = "", `Positive ` = "")
-  ) %>% 
-  apa_table(
-    font_size = "small",
-    placement = "htb",
-    span_text_columns = TRUE,
-    note = "Numbers may not add up to 100% because of rounding.",
-    col_spanners = list("Sign test" = c(3, 5), "ROPE test" = c(6, 9))
-  )
-
-# Save interactive table
-tab %>% 
-  mutate(
-    Country = relevel(factor(Country), ref = "World"),
-    d_nhst = factor(d_nhst),
-    d_rope = factor(d_rope)
-  ) %>% 
-  datatable(filter = "top", rownames = FALSE) %>% 
-  formatRound(4:12, 3) %>% 
-  saveWidget("Output/Table-S2.html", title = "Country-specific parameters")
-```
-
-Another way in which this variability can be summarised is to calculate proportions of countries where the association between internet adoption / mobile broadband adoption and well-being / mental health was credible negative, positive, or neither (null), or whether it was credibly outside the region of practical equivalence (ROPE) to zero as defined by the simple linear change in the outcome.
-The latter test allows quantifying evidence for four distinct propositions: Support for a credibly negative association, support for a credibly positive association, support for the null hypothesis (of smaller than meaningful association), and not enough support for either of the three alternatives (inconclusive) [@kruschkeBayesianNewStatistics2017].
-We present these numbers in Table \@ref(tab:table-s2), which further highlights substantive between-country differences in well-being associations, and the fact that most associations were not credibly positive or negative at the country level—especially for mental health outcomes.
-Indeed, quantified in this manner, we find the null hypothesis in excess of 95% credibility for 8-15% of countries for the well-being outcomes, and 18-54% of countries for the mental health outcomes.
-
-```{r table-s3}
-#| include: true
-get_cor_pars <- function(outcome, predictor, model) {
-  x <- readRDS(str_glue("models-small/brm-{outcome}-{model}.rds"))
-  as_draws_df(
-    x,
-    variable = c(
-      str_glue("b_{predictor}_Intercept"),
-      "b_val_Intercept",
-      str_glue("b_{predictor}_year"),
-      "b_val_year",
-      str_glue("sd_country__{predictor}_Intercept"),
-      "sd_country__val_Intercept",
-      str_glue("sd_country__{predictor}_year"),
-      "sd_country__val_year",
-      str_glue("cor_country__{predictor}_year__val_year"),
-      str_glue("cor_country__{predictor}_Intercept__val_Intercept")
-    )
-  )
-}
-get_cor_pars <- memoise(get_cor_pars, cache = cd)
-
-cor_pars_brm <- fits %>%
-  mutate(
-    internet = map(outcome, ~get_cor_pars(.x, "internet", "1")),
-    mobile = map(outcome, ~get_cor_pars(.x, "mobile", "2"))
-  )
-
-cor_sum <- cor_pars_brm %>% 
-  mutate(
-    across(
-      internet:mobile, 
-      ~map(., ~describe_posterior(., centrality = "mean", test = "pd"))
-    )
-  )
-cor_sum %>% 
-  pivot_longer(-outcome, names_to = "Predictor") %>% 
-  unnest(value) %>% 
-  filter(str_detect(Parameter, "cor_")) %>% 
-  mutate(
-    Mean = number2(Mean, .01, pad = TRUE),
-    across(CI_low:CI_high, ~number(., .01)), 
-    pd = percent2(pd, .1)
-  ) %>% 
-  transmute(
-    Predictor = str_to_title(Predictor),
-    Correlation = if_else(
-      str_detect(Parameter, "Intercept"), "Intercepts", "Slopes"
-    ),
-    Outcome = str_replace(outcome, "_", " "),
-    Summary = str_glue("{Mean} [{CI_low}, {CI_high}] ({pd})")
-  ) %>% 
-  pivot_wider(names_from = Predictor, values_from = Summary) %>% 
-  mutate(Outcome = factor(Outcome, levels = str_replace(oo, "_", " "))) %>% 
-  arrange(Correlation, Outcome) %>% 
-  mutate(
-    Correlation = if_else(Outcome == "Life satisfaction", Correlation, "")
-  ) %>% 
-  apa_table(
-    font_size = "small",
-    placement = "htb",
-    span_text_columns = TRUE,
-    note = "Numbers indicate the correlations [95%CI] between the intercepts and slopes of time of the corresponding outcome and internet / mobile broadband adoption."
-  )
-```
-
-Our main analyses concerned within-country associations between internet / mobile broadband adoption and well-being / mental health.
-To test this association from another perspective, we also examined correlations in countries’ average levels of well-being and mental health on the one hand, and average levels of internet / mobile broadband adoption on the other.
-The first six rows of Table \@ref(tab:table-s3) ("Averages") shows that, between countries, internet and mobile broadband adoption positively predict life satisfaction, positive experiences, anxiety, and self-harm, and negatively predict negative experiences and depression.
-
-An arguably stronger test of the idea that changes in internet / mobile broadband adoption predict changes in well-being and mental health is to correlate the country-specific rates of changes in the variables: Are countries with more rapid internet adoption also those countries where well-being declined faster?
-The answer in these data is in the negative (Table \@ref(tab:table-s3) ("Slopes")).
-Countries' slopes of internet adoption were negatively correlated with slopes of negative experiences, indicating that countries where internet penetration was fastest were also those where negative experiences decreased the most.
-In addition, slopes of mobile broadband adoption were positively correlated with slopes of life satisfaction and positive experiences, and negatively correlated with slopes of negative experiences, indicating that countries where mobile broadband penetration was most rapid were those where life satisfaction and positive experiences increased the most, and negative experiences increased the least.
+table_of_countries(tab_wb, "Well-being" )
+```
+
+## Mental health: Country-specific parameters
+
+```{r, tab-gbd-props}
+#| include: !expr knitr::is_latex_output()
+```
+
+```{r}
+#| include: !expr knitr::is_latex_output()
+table_of_countries(tab_mh, "Mental health" )
+```

### 2022-10-26 models.R

@@ -13,17 +13,15 @@ library(tidyr)
 library(brms)
 
 # MCMC settings
-(ncores <- min(parallel::detectCores(logical = FALSE), 12))
-nchains <- 4
 options(brms.backend = "rstan")
 hmc <- list(
-  save_pars = save_pars(c("age", "country")),
-  chains = nchains,
-  cores = nchains,
-  # threads = min(ncores %/% nchains, 3),
-  iter = 3000,
-  warmup = 1500,
+  save_pars = save_pars(group = c("age", "country")),
+  chains = 4,
+  cores = 4,
+  iter = 4000,
+  warmup = 2000,
   refresh = 100,
+  init = 0,
   control = list(adapt_delta = .95, max_treedepth = 10)
 )
 
@@ -85,7 +83,7 @@ bf_m <- bf(
     ((year + m_cw) * sex | age:country),
   family = gaussian()
 )
-bf_m.s <- update(bf_m, ~ . -((year + mm_cw) * sex | age:country))
+bf_m.s <- update(bf_m, ~ . -((year + m_cw) * sex | age:country))
 
 # Pick the row to fit
 fits <- fits %>%
@@ -105,11 +103,46 @@ fits <- fits %>%
   ) %>%
   arrange(outcome, model)
 
+# Priors
+p1 <- prior(normal(0, 1), class = "b") +
+  prior(normal(0, 3), class = "b", coef = "sex1")
+p2 <- prior(normal(0, 1), class = "b") +
+  prior(normal(0, 3), class = "b", coef = "sex1") +
+  prior(normal(0, 0.5), class = "sd", coef = "i_cw", group = "age") +
+  prior(lkj(1), class = "cor", group = "age")
+p3 <- prior(normal(0, 1), class = "b") +
+  prior(normal(0, 3), class = "b", coef = "sex1") +
+  prior(normal(0, 0.5), class = "sd", coef = "m_cw", group = "age") +
+  prior(lkj(1), class = "cor", group = "age")
+
+
+# Center predictors -------------------------------------------------------
+
+# Centering predictors within and between countries
+fits$data[[1]] <- fits$data[[1]] %>%
+  drop_na(val) %>%
+  rename(i = internet, m = mobile) %>%
+  group_by(country) %>%
+  mutate(
+    # Between
+    i_cb = mean(i, na.rm = TRUE),
+    m_cb = mean(m, na.rm = TRUE),
+    # Within
[…]

### 2022-10-26 submit.sh

@@ -4,7 +4,7 @@
 # Submit on cluster with: sbatch --array=1-18 submit.sh
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
-#SBATCH --cpus-per-task=12
+#SBATCH --cpus-per-task=4
 #SBATCH --mem-per-cpu=3G
 #SBATCH --time=7-00:00:00
 #SBATCH --job-name=DWG-Global

### 2023-01-30 ms.Rmd
Updates

@@
 The broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes.
-However, associations between internet technology adoption and depression and self-harm were strongest for individuals aged between 10 and 34.
+However, associations between internet technology adoption and depression and self-harm were strongest (albeit still small) for individuals aged between 10 and 34.
 Further investigation of this topic requires transparent study of online behaviours where they occur, namely on online platforms.
@@
 We first asked how the well-being outcomes had changed over time.
+Bayesian methods are especially suitable to our reserch questions, because they involve many potential contrasts between e.g.
+countries and ages.
+Using bayesian hierarchical models allowed us to accurately quantify uncertainty at different levels of analyses while avoiding problems with multiple comparisons (see below).
 To answer, we modelled each outcome (e.g.
@@
 This bayesian approach to estimating age-specific associations is beneficial, given that the large number of age groups, especially within countries, would otherwise present difficulties with uncertain estimates and multiple comparisons.
+In addition, bayesian methods allowed quantifying uncertainties at different levels of analysis, rather than providing e.g.
+only point estimates of country-specific quantities.
 Therefore, we could compare younger age groups to older age groups, and investigate other contrasts, with confidence and without additional post-hoc adjustment procedures [@gelmanWhyWeUsually2012].
@@
 In light of substantial residual standard deviations ranging from about 6 to 8 between predictors and outcomes, and average yearly increases in internet technology adoption (internet = 2.7%, mobile = 5.8%) the observed associations were very small.
+
+```{r}
+tmpr <- fits_wb %>% 
+  filter(model > 1) %>% 
+  mutate(
+    sdx = map_dbl(fit, ~sd(.x$data[,4])),
+    sdy = map_dbl(fit, ~sd(.x$data[,1]))
+  ) %>% 
+  mutate(
+    x = map(
+      fit, 
+      ~as_draws_df(.x, variable = "b_[i|m]_cw$", regex = TRUE) %>% 
+        rename(b = 1) %>% 
+        mutate(r = b * (sd(.x$data[,4]) / sd(.x$data[,1])), .keep = "unused") %>% 
+        describe_posterior(
+          centrality = "mean", 
+          ci = 0.95, 
+          ci_method = "ETI", 
+          test = "pd",
+          diagnostic = NULL
+        ) %>% 
+        as_tibble())
+  ) %>% 
+  mutate(model = factor(model, labels = c("Internet", "Mobile"))) %>% 
+  unnest(x) %>% 
+  mutate(
+    result = str_glue(
+      "{number(Mean, .001)} [{number(CI_low, .001)}, {number(CI_high, .001)}]"
+    ),
+    .keep = "unused"
+  ) %>% 
+  select(outcome, model, result)
+tmpr
+```
+
+In addition to these recommended raw associations [@baguleyStandardizedSimpleEffect2009], we also computed the standardized average associations ($\alpha_4(\frac{\sigma_x}{\sigma_y})$).
+In line with the unstandardized coefficients reported above, the standardized associations were small according to common guidelines: (life satisfaction & internet = `r tmpr$result[1]`, life satisfaction & mobile = `r tmpr$result[2]`, negative experiences & internet = `r tmpr$result[3]`, negative experiences & mobile = `r tmpr$result[4]`, positive experiences & internet = `r tmpr$result[5]`, positive experiences & mobile = `r tmpr$result[6]`).
 
@@
 These between-country associations indicated, with high confidence, that countries with greater average levels of internet and mobile broadband adoption tended to report greater average levels of life satisfaction and positive experiences, and lower average levels of negative experiences (Figure \@ref(fig:fig-gwp-data)B, Between-country associations).
-However, this pattern is likely to reflect multiple other causes impinging on both well-being and internet technology adoption.
+However, this pattern is likely to reflect multiple other causes, such as socioeconomic factors and levels of inequality, impinging on both well-being and internet technology adoption.
+For example while wealthier nations are likely to have greater internet coverage, they also tend to have greater healthcare coverage, which in turn is likely to affect levels of well-being.
 
@@
 Similarly, per capita mobile broadband subscriptions were not credible predictors of mental health for the average country, although the model indicated `r avg_mh$pd[10]` certainty of a negative association between mobile broadband adoption and rates of anxiety.
+
+```{r}
+tmpr <- fits_mh %>% 
+  filter(model > 1) %>% 
+  mutate(
+    sdx = map_dbl(fit, ~sd(.x$data[,4])),
+    sdy = map_dbl(fit, ~sd(.x$data[,1]))
+  ) %>% 
+  mutate(
+    x = map(
+      fit, 
+      ~as_draws_df(.x, variable = "b_[i|m]_cw$", regex = TRUE) %>% 
+        rename(b = 1) %>% 
+        mutate(r = b * (sd(.x$data[,4]) / sd(.x$data[,1])), .keep = "unused") %>% 
+        describe_posterior(
+          centrality = "mean", 
+          ci = 0.95, 
+          ci_method = "ETI", 
+          test = "pd",
+          diagnostic = NULL
+        ) %>% 
+        as_tibble())
+  ) %>% 
+  mutate(model = factor(model, labels = c("Internet", "Mobile"))) %>% 
+  unnest(x) %>% 
+  mutate(
+    result = str_glue(
+      "{number(Mean, .001)} [{number(CI_low, .001)}, {number(CI_high, .001)}]"
+    ),
+    .keep = "unused"
+  ) %>% 
+  select(outcome, model, result)
+tmpr
+```
+
+Although numerically greater than the unstandardized coefficients reported above, the standardized associations were small according to common guidelines: (anxiety & internet = `r tmpr$result[1]`, anxiety & mobile = `r tmpr$result[2]`, depression & internet = `r tmpr$result[3]`, depression & mobile = `r tmpr$result[4]`, depression & internet = `r tmpr$result[5]`, depression & mobile = `r tmpr$result[6]`).
 
@@
 However, we did find evidence suggesting that internet technology adoption is more negatively associated with young individuals' mental health than older groups' (whose associations were, in some cases, positive).
+Nevertheless, these associations, although sometimes credibly different from zero, appeared small in magnitude.
+Because of their apparently small magnitude and the fact that the data are not at the individual level, we highlight that these contrasts do not speak to whether the associations might be clinically relevant.
 
@@
 In addition, our results regarding mental health, while comprehensive, are necessarily and considerably less certain than those on well-being, due to the lack of diverse global data and our own reliance on GBD estimates in place of objective measurements of mental health.
+In addition, the data aggregation necessary to link internet adoption and well-being at the national level preclude investigating other important and relevant questions, such as comorbidities.
 

### 2023-05-10 ms.Rmd
Update authors

@@
   - name: Matti Vuorre
-    affiliation: 1
-    address: Oxford Internet Institute, University of Oxford
-    email: matti.vuorre@oii.ox.ac.uk
+    affiliation: "1,2"
+    address: Tilburg University
+    email: m.j.vuorre@tilburguniversity.edu
   - name: Andrew K. Przybylski
-    affiliation: 1
+    affiliation: "2"
     corresponding: yes
-    address: Oxford Internet Institute, University of Oxford
     email: andy.przybylski@oii.ox.ac.uk
@@
   - id: 1
+    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
+  - id: 2
     institution: Oxford Internet Institute, University of Oxford

### 2023-05-10 ms.Rmd
Use after_stat()

@@
   stat_halfeye(
-    aes(shape = stat(sign(xmax) == sign(xmin))),
+    aes(shape = after_stat(sign(xmax) == sign(xmin))),
     position = position_dodge(.15), 

### 2023-05-23 ms.Rmd
Edit figures for presentation

@@
   # Truncate mobile percentages for figure
-  mutate(Mobile = if_else(Mobile > 150, NaN, Mobile)) %>%
+  mutate(
+    Mobile = if_else(Mobile > 150, NaN, Mobile),
+    ) %>%
   pivot_longer(
@@
   mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
+  filter(region != "Oceania", year >= 2005) %>% 
+  filter(outcome %in% c("Internet", "Mobile", "Life_satisfaction")) %>% 
   mutate(year = make_date(year)) %>%
-  ggplot(aes(year, mean)) +
+  mutate(country = fct_relevel(country, "Netherlands") %>% fct_rev()) %>%
+  ggplot(
+    aes(
+      year, 
+      mean, 
+      size = country == "Netherlands", 
+      color = region == "Europe"
+    )
+  ) +
+  scale_size_manual(values = c(0.25, 0.25)) +
+  scale_color_manual(values = c("white", "white")) +
   scale_y_continuous(
     "Value (%)",
-    # Display percentages
     breaks = pretty_breaks(),
@@
       group = interaction(country, outcome)
-    ),
-    size = .05, col = "dodgerblue3"
+    )
   ) +
@@
   theme(
+    text = element_text(size = 18), 
+    panel.spacing = unit(10, "pt"),
+    axis.title.x = element_blank(),
     legend.position = "none"
   )
-
+p1
 x <- fits_wb %>% 
@@
 p2 <- x %>% 
-  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
-  scale_color_brewer(
-    "Association", palette = "Set2", aesthetics = c("fill", "color")
+  filter(outcome == "Life_satisfaction") %>% 
+  filter(Predictor != "Time") %>% 
+  ggplot(aes(value, fct_rev(Predictor), fill = x, color = x)) +
+  scale_color_manual(
+    "Association", 
+    values = c("#fc8d62", "#66c2a5"), 
+    aesthetics = c("fill", "color", "interval_color")
   ) +
@@
   ) +
-  stat_halfeye(
+  scale_y_discrete(
+    expand = expansion(c(0.001, .01)),
+    drop = FALSE
+  ) +
+  stat_slabinterval(
     aes(shape = after_stat(sign(xmax) == sign(xmin))),
-    position = position_dodge(.15), 
+    position = position_dodge(-.1),
     normalize = "xy", 
-    height = .8,
+    height = .9,
     point_interval = "mean_qi",
-    fatten_point = 3,
+    interval_size_range = c(.25, 1),
+    fatten_point = 4,
     point_fill = "white",
-    size = .25,
     slab_alpha = .75,
@@
   ) +
+  geom_vline(xintercept = 0, linewidth = .25) +
   facet_wrap(
@@
   ) +
+  guides(shape = "none") +
   theme(
-    legend.position = "none",
+    legend.position = "bottom",
     axis.title.y = element_blank(),
-    panel.grid.major.x = element_line(
-      color = "black", linetype = "dotted", size = .1
-    )
-  )
-
-(p1 / p2) + 
-  plot_layout(heights = c(8, 2)) +
-  plot_annotation(tag_levels = "A")
+    text = element_text(size = 18), 
+    panel.spacing = unit(10, "pt")
+  )
+p2
 ```
@@
     geom_linerangeh(
-      size = .1,
+      size = .3,
       aes(xmin = CI_low, xmax = CI_high, linetype = cred)
@@
       aes(shape = cred), 
-      size = .55, fill = "white", stroke = .2
+      size = 1, fill = "white", stroke = .3
     ) +
@@
     theme(
+      text = element_text(size = 18), 
       axis.text.y = element_blank(),
@@
 }
-p_country_wb <- figure_country(tab_wb)
+p_country_wb <- figure_country(tab_wb %>% filter(outcome == "Life_satisfaction"))
+p_country_wb
 ```

### 2023-05-30 ms.Rmd
Add reference

--- 2023-05-10 ms.Rmd
@@
 Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020].
-Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2021], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
+Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [ghaiLackSampleDiversity2023; @ghaiSocialMediaAdolescent2022], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
 A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted.

### 2023-05-30 submit.sh
Use newer R on cluster

@@ -10,6 +10,6 @@
 #SBATCH --job-name=DWG-Global
 
 module purge
-module load R/4.1.2-foss-2021b-ARC
+module load R/4.2.2-foss-2022a-ARC
 
 Rscript models.R $SLURM_ARRAY_TASK_ID

### 2023-05-30 meta-regression-weights.qmd
Include cell Ns as weights

---
title: "Meta-regression weighting"
format: html
---

Confirming how brms syntax works re meta-regression.

```{r}
library(brms)
library(janitor)
library(posterior)
library(ggstance)
library(tidyverse)
```

Get a snippet of data

```{r}
dat <- read_rds("data-raw/Gallup/gwp-processed.rds") %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  ) %>% 
  filter(country == "United States", year == 2015) %>% 
  select(sex, age, Life_satisfaction) %>% 
  filter(age <= 89) %>% 
  mutate(
    age = cut(
      age,
      breaks = seq(15, 90, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
    ) %>% as.character()
  )
dat_sum <- dat %>% 
  summarise(
    n = sum(!is.na(Life_satisfaction)),
    sd = sd(Life_satisfaction, na.rm = TRUE),
    se = sd / sqrt(n),
    Life_satisfaction = mean(Life_satisfaction, na.rm = TRUE), 
    .by = c(age, sex)
    )
```

Specify models

```{r}
# Raw data
f1 <- brm(
  Life_satisfaction ~ 0 + age %in% sex,
  data = dat,
  backend = "cmdstanr",
  cores = 4
)

# With SEs
f2.1 <- brm(
  Life_satisfaction | se(se, sigma = TRUE) ~ 0 + age %in% sex,
  data = dat_sum,
  backend = "cmdstanr",
  cores = 4
)
f2.2 <- brm(
  Life_satisfaction | se(se, sigma = TRUE) + weights(n) ~ 0 + age %in% sex,
  data = dat_sum,
  backend = "cmdstanr",
  cores = 4
)

# With SDs
f3.1 <- brm(
  Life_satisfaction | se(sd, sigma = TRUE) ~ 0 + age %in% sex,
  data = dat_sum,
  backend = "cmdstanr",
  cores = 4
)
f3.2 <- brm(
  Life_satisfaction | se(sd, sigma = TRUE) + weights(n) ~ 0 + age %in% sex,
  data = dat_sum,
  backend = "cmdstanr",
  cores = 4
)
```

Compare estimates

```{r}
bind_rows(
  as_draws_df(f1) %>% 
    summarize_draws(),
  as_draws_df(f2.1) %>% 
    summarize_draws(),
  as_draws_df(f2.2) %>% 
    summarize_draws(),
  as_draws_df(f3.1) %>% 
    summarize_draws(),
  as_draws_df(f3.2) %>% 
    summarize_draws(),
  .id = "Model"
) %>% 
  mutate(
    Model = factor(Model, labels = c("1", "2.1", "2.2", "3.1", "3.2")),
    sex = factor(str_detect(variable, "sexFemale"), labels = c("Male", "Female"))
  ) %>% 
  filter(str_starts(variable, "b_")) %>% 
  ggplot(aes(mean, variable, col = Model)) +
  geom_pointrangeh(
    aes(xmin = q5, xmax = q95),
    position = position_dodgev(.75)
  ) +
  facet_wrap("sex", scales = "free_y")
```

Standardizing

```{r}
f1.2 <- brm(
  scale(Life_satisfaction) ~ 0 + age %in% sex,
  data = dat,
  backend = "cmdstanr",
  cores = 4
)
```

```{r}
bind_rows(
  as_draws_df(f1) %>% 
    summarize_draws(),
  as_draws_df(f1.2) %>% 
    summarize_draws(),
  .id = "Model"
) %>% 
  filter(str_starts(variable, "b_")) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~if_else(
        Model == 1, 
        (. - mean(dat$Life_satisfaction, na.rm = TRUE)) / sd(dat$Life_satisfaction, na.rm = TRUE), 
        .
      )
    )
  ) %>% 
  ggplot(aes(mean, variable, col = Model)) +
  geom_pointrangeh(
    aes(xmin = q5, xmax = q95),
    position = position_dodgev(1)
  )
```

### 2023-05-30 models.R

@@ -13,7 +13,7 @@ library(tidyr)
 library(brms)
 
 # MCMC settings
-options(brms.backend = "rstan")
+options(brms.backend = "cmdstanr")
 hmc <- list(
   save_pars = save_pars(group = c("age", "country")),
   chains = 4,
@@ -53,7 +53,7 @@ fits <- dat %>%
 
 # Time only
 bf_t <- bf(
-  val | se(se, sigma = TRUE) + subset(!is.na(val)) ~
+  val | se(sd, sigma = TRUE) + weights(n) + subset(!is.na(val)) ~
     year * sex +
     (year * sex | country) +
     (year * sex | age) +
@@ -61,29 +61,49 @@ bf_t <- bf(
   family = gaussian()
 )
 # Simplified model for mental health outcomes
-bf_t.s <- update(bf_t, ~ . -(year * sex | age:country))
+bf_t.s <- bf(
+  val | se(sd, sigma = TRUE) + subset(!is.na(val)) ~
+    year * sex +
+    (year * sex | country) +
+    (year * sex | age),
+  family = gaussian()
+)
 
-# Univariate outcome on time and internet
+# Time and internet
 bf_i <- bf(
-  val | se(se, sigma = TRUE) ~
+  val | se(sd, sigma = TRUE) + weights(n) ~
     (year + i_cw) * sex + i_cb +
     ((year + i_cw) * sex | country) +
     ((year + i_cw) * sex | age) +
     ((year + i_cw) * sex | age:country),
   family = gaussian()
 )
-bf_i.s <- update(bf_i, ~ . -((year + i_cw) * sex | age:country))
+# Simplified model for mental health outcomes
+bf_i.s <- bf(
+  val | se(sd, sigma = TRUE) ~
+    (year + i_cw) * sex + i_cb +
+    ((year + i_cw) * sex | country) +
+    ((year + i_cw) * sex | age),
+  family = gaussian()
+)
 
-# Univariate outcome on time and mobile
+# Time and mobile
 bf_m <- bf(
-  val | se(se, sigma = TRUE) ~
+  val | se(sd, sigma = TRUE) + weights(n) ~
     (year + m_cw) * sex + m_cb +
     ((year + m_cw) * sex | country) +
     ((year + m_cw) * sex | age) +
     ((year + m_cw) * sex | age:country),
   family = gaussian()
 )
[…]

### 2023-05-30 ms.Rmd
Clarify meta-regression weighting

@@
 footnotelist: no
-# header-includes:
 csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
@@
 
+# Pivot outcomes to long format
 gwp <- gwp %>%
@@
     names_to = "outcome", values_to = "val"
-  ) %>%
-  group_by(country, year, sex, age, outcome) %>%
+  )
+
+# Aggregate outcomes
+gwp <- gwp %>% 
   summarise(
     n = n(),
-    se = sd(val, na.rm = TRUE) / sqrt(n),
-    val = mean(val, na.rm = TRUE)
-  ) %>%
-  ungroup()
-
-# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
+    sd = sd(val, na.rm = TRUE),
+    val = mean(val, na.rm = TRUE),
+    .by = c(country, year, sex, age, outcome)
+  )
+
+# Assign N of 1 cells a standard deviation of zero
 gwp <- gwp %>% 
-  mutate(
-    se = if_else(is.na(se) | se == 0, 0.5, se)
-  )
+  mutate(sd = if_else(is.na(sd), 0, sd))
 
@@
 gbd <- gbd %>%
-  mutate(se = (upper - lower) / (1.96 * 2)) %>%
+  mutate(sd = (upper - lower) / (1.96 * 2)) %>%
   select(-c(upper, lower))
@@
 
-# Selfharm models don't converge with SEs
-dat <- dat %>% 
-  mutate(se = if_else(outcome == "Selfharm", 0, se))
-
 # Save data for models
@@
 
-Before modelling the data, we aggregated the individual-level well-being values to means and standard errors for each country-year-age-sex combination, in order to facilitate the Hamiltonian Monte Carlo computations on large data, and to harmonise the analyses and inferences between Studies 1 and 2.
+Before modelling the data, we aggregated the individual-level well-being values to means, standard deviations, and counts for each country-year-age-sex combination, in order to facilitate the Hamiltonian Monte Carlo computations on large data, and to harmonise the analyses and inferences between Studies 1 and 2.
 Importantly, we note that because we modelled unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g.
@@
 \begin{align*} 
-y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{se}^2_i}), \\
+y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{sd}^2_i}), \\
 \mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
@@
 
-where $i$ indexes rows in the data and $\text{se}_i$ are the known standard errors.
+where $i$ indexes rows in the data and $\text{sd}_i$ are the known standard deviations.
 $\text{X}^{\text{CW}}_i$ and $\text{X}^{\text{CB}}_i$ are the within- and between-country centred internet technology adoption predictor (per capita internet users or mobile broadband subscriptions, in separate models), respectively.
-We used default noninformative priors on all parameters except the following population-level coefficients, that were modelled as
-
-\begin{align*}
-\alpha_{1,3-6} &\sim \text{Normal}(0, 1), \\
-\alpha_{2} &\sim \text{Normal}(0, 3), \\
-\sigma_{\gamma_4} &\sim \text{Normal}^+(0, 0.5).
-\end{align*}
-
-We used these priors to help model convergence, and on the assumption that differences in well-being between males and females are likely greater than differences associated with years, one-percent increases in technology adoption predictors, or the interaction terms.
+In addition to the standard deviations, we weighted each observation by the number of respondents in that cell, to adjust for varying sample sizes across cells.
+We used default noninformative priors on all parameters.
 
@@
 We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
-We ran 4 HMC chains with 3,000 iterations and first 1,500 as warmup for 6,000 total iterations.
+We ran 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations.
 We ensured that all population-level parameters' had converged using numeric diagnostics (all Rhats were within 0.01 of 1) and visual inspection of parameters' scatterplot matrices.

### 2023-07-17 models.R
Clarify code

@@ -13,16 +13,16 @@ library(tidyr)
 library(brms)
 
 # MCMC settings
-options(brms.backend = "cmdstanr")
+options(brms.backend = "rstan") # rstan to save subsets of parameters
 hmc <- list(
   save_pars = save_pars(group = c("age", "country")),
   chains = 4,
   cores = 4,
-  iter = 4000,
-  warmup = 2000,
+  iter = 5000,
+  warmup = 2500,
   refresh = 100,
-  init = 0,
-  control = list(adapt_delta = .95, max_treedepth = 10)
+  # init = 0,
+  control = list(adapt_delta = .99, max_treedepth = 10)
 )
 
 # Create directory for intermediate files
@@ -53,7 +53,7 @@ fits <- dat %>%
 
 # Time only
 bf_t <- bf(
-  val | se(sd, sigma = TRUE) + weights(n) + subset(!is.na(val)) ~
+  val | se(se, sigma = TRUE) ~
     year * sex +
     (year * sex | country) +
     (year * sex | age) +
@@ -62,7 +62,7 @@ bf_t <- bf(
 )
 # Simplified model for mental health outcomes
 bf_t.s <- bf(
-  val | se(sd, sigma = TRUE) + subset(!is.na(val)) ~
+  val | se(se, sigma = FALSE) ~
     year * sex +
     (year * sex | country) +
     (year * sex | age),
@@ -71,37 +71,37 @@ bf_t.s <- bf(
 
 # Time and internet
 bf_i <- bf(
-  val | se(sd, sigma = TRUE) + weights(n) ~
-    (year + i_cw) * sex + i_cb +
-    ((year + i_cw) * sex | country) +
-    ((year + i_cw) * sex | age) +
-    ((year + i_cw) * sex | age:country),
+  val | se(se, sigma = TRUE) ~
+    (i_cw + year) * sex + i_cb +
+    ((i_cw + year) * sex | country) +
+    ((i_cw + year) * sex | age) +
+    ((i_cw + year) * sex | age:country),
   family = gaussian()
 )
 # Simplified model for mental health outcomes
 bf_i.s <- bf(
-  val | se(sd, sigma = TRUE) ~
-    (year + i_cw) * sex + i_cb +
-    ((year + i_cw) * sex | country) +
-    ((year + i_cw) * sex | age),
+  val | se(se, sigma = FALSE) ~
+    (i_cw + year) * sex + i_cb +
[…]

### 2023-07-17 submit.sh

@@ -5,8 +5,8 @@
 
 #SBATCH --constraint='cpu_frq:2.90GHz'
 #SBATCH --cpus-per-task=4
-#SBATCH --mem-per-cpu=3G
-#SBATCH --time=7-00:00:00
+#SBATCH --mem-per-cpu=2G
+#SBATCH --time=8-00:00:00
 #SBATCH --job-name=DWG-Global
 
 module purge

### 2023-07-17 ms.Rmd
Move a bunch of stuff to a separate file

@@
     corresponding: yes
+    address: Oxford Internet Institute
     email: andy.przybylski@oii.ox.ac.uk
@@
 abstract: | 
-  In the last two decades the rise of internet technologies have impacted nearly all domains of human life and inspired concern that their widespread adoption has impacted mental health and psychological well-being.
+  In the last two decades the widespread adoption of internet technologies has inspired concern that they have negatively impacted mental health and psychological well-being.
 However, research on the topic is contested and hampered by methodological shortcomings leaving the broader consequences of internet adoption unknown.
-We show that the past two decades have seen small and inconsistent changes in global well-being and mental health.
-The broadest available health and internet technology data does not support the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes.
-However, associations between internet technology adoption and depression and self-harm were strongest (albeit still small) for individuals aged between 10 and 34.
+We show that the past two decades have seen only small and inconsistent changes in global well-being and mental health that are not suggestive of the idea that the adoption of internet and mobile broadband is consistently linked to negative psychological outcomes.
 Further investigation of this topic requires transparent study of online behaviours where they occur, namely on online platforms.
@@
     number_sections: false
-    keep_tex: false
+    keep_tex: true
   papaja::apa6_docx: 
@@
   chunk_output_type: console
-always_allow_html: true
 ---
@@
 library(papaja)
-library(readxl)
-library(imputeTS)
 library(scales)
-library(janitor)
-library(haven)
-library(labelled)
 library(tidybayes)
 library(ggdist)
-library(countrycode)
 library(lubridate)
@@
 library(knitr)
-library(ggstance)
+library(posterior)
 library(bayestestR)
-library(ggh4x)
 library(tidyverse)
@@
   warning = FALSE,
+  error = TRUE,
   dpi = 300,
@@
 )
-# For tables: Show NAs as blanks
-options(knitr.kable.NA = '')
-
-# Create directory for intermediate files
-dir.create("data", FALSE)
 
@@
   theme_linedraw(
-    base_size = if_else(knitr::is_latex_output(), 9, 8)
+    base_size = if_else(knitr::is_latex_output(), 8, 7)
   ) +
@@
       strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
-      axis.text = element_text(size = rel(0.75)),
-      axis.ticks = element_line(size = rel(0.3))
-    )
+      axis.text = element_text(size = rel(0.7)),
+      axis.ticks = element_line(size = rel(0.2))
+    )
+)
+dir.create("cache", FALSE)
+```
+
+```{r data}
+dat <- read_rds("data/data-all.rds")
+gwp <- read_rds("data/gwp.rds")
+itu <- read_rds("data/itu.rds")
+gbd <- read_rds("data/gbd.rds")
+z <- read_rds("data/scaling-factors.rds")
+coefficients <- read_rds("cache/coefficients.rds")
+epred <- read_rds("cache/epred.rds")
+```
+
+```{r variables}
+# For ordering outcome factor
+oo <- c(
+  "Life_satisfaction", 
+  "Negative_experiences", 
+  "Positive_experiences",
+  "Anxiety", "Depression", "Selfharm"
 )
@@
 
-```{r data-clean}
-## # Understand variables & values
-## # Codes NOTE 1: yes 2: no!
-## read_spss(
-##   "data-raw/Gallup/The_Gallup_101521.sav",
-##   n_max = 1,
-##   col_select = c(
-##     WPID, WP1219,
-##     WP16,
-##     WP60, WP61, WP63, WP65, WP67,
-##     WP68, WP69, WP70, WP71, WP74
-##   )
-## ) %>%
-##   generate_dictionary()
-
-# First liberate the data from the slow SPSS file and save to disk
-gwp_path <- "data-raw/Gallup/gwp-processed.rds"
-if (!file.exists(gwp_path)) {
-  gwp <- read_spss(
-    "data-raw/Gallup/The_Gallup_101521.sav",
-    col_select = c(
-      YEAR_CALENDAR,
-      COUNTRYNEW,
-      WPID, WP1220, WP1219,
-      WP16,
-      WP60, WP61, WP63, WP65, WP67,
-      WP68, WP69, WP70, WP71, WP74
-    )
-  )
-  # Get rid of SPSS attributes
-  gwp <- gwp %>%
-    zap_labels() %>%
-    zap_label() %>%
-    zap_widths() %>%
-    zap_formats()
-  # Save into a good format
-  write_rds(gwp, gwp_path)
-} else {
-  gwp <- read_rds(gwp_path)
-}
-
-# Rename and recode variables
-gwp <- gwp %>%
-  clean_names() %>%
-  transmute(
-    country = countrynew,
-    year = year_calendar,
-    id = wpid,
-    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
-    age = wp1220,
-    # Don't know, refused, and missing values
-    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
-    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
-    # Also reverse the weird 1: yes 2: no coding here
-    across(wp60:wp74, ~ 3 - .)
-  )
-
-# Scale scores note rescaling to percentages
-gwp <- gwp %>%
-  mutate(
-    Life_satisfaction = Life_satisfaction * 10,
-    Negative_experiences =
-      (rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1) * 100,
-    Positive_experiences =
-      (rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1) * 100
-  ) %>%
-  select(-c(wp60:wp74))
-
-# Categorize ages
-gwp <- filter(gwp, age <= 89)
-gwp <- gwp %>%
-  mutate(
-    age = cut(
-      age,
-      breaks = seq(15, 90, by = 5),
-      include.lowest = TRUE,
-      right = FALSE,
-      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
-    ) %>% as.character()
-  )
-
-# There is one 13 year old which resulted in a NA and we drop it
-gwp <- drop_na(gwp, age)
-
-# Some sex values are missing, drop those
-gwp <- drop_na(gwp, sex)
-
-# Pivot outcomes to long format
-gwp <- gwp %>%
-  pivot_longer(
-    c(
-      Life_satisfaction,
-      Negative_experiences,
-      Positive_experiences
-    ),
-    names_to = "outcome", values_to = "val"
-  )
-
-# Aggregate outcomes
-gwp <- gwp %>% 
-  summarise(
-    n = n(),
-    sd = sd(val, na.rm = TRUE),
-    val = mean(val, na.rm = TRUE),
-    .by = c(country, year, sex, age, outcome)
-  )
-
-# Assign N of 1 cells a standard deviation of zero
-gwp <- gwp %>% 
-  mutate(sd = if_else(is.na(sd), 0, sd))
-
-# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising
-
-# Harmonise old names and replace only if harmonised name found
-gwp <- gwp %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  # Prevent north cyprus from becoming cyprus
-  mutate(
-    country_harmonised = ifelse(
-      country == "Northern Cyprus",
-      "Northern Cyprus",
-      country_harmonised
-    )
-  ) %>%
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-gwp_mock_path <- "data-raw/gwp-MOCK.rds"
-if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
-  library(synthpop)
-  gwp_syn <- gwp %>% 
-    drop_na()
-  gwp_syn <- syn(
-    gwp_syn, 
-    method = c("", "", "", "", "", "", "normrank", "normrank"),
-    maxfaclevels = 168
-  )
-  gwp_syn <- tibble(gwp_syn$syn)
-  saveRDS(gwp_syn, gwp_mock_path)
-}
-
-# Load if actual data doesn't exist
-if (!dir.exists("data-raw/Gallup")) {
-  cat("Using synthetic GWP data.")
-  gwp <- read_rds(gwp_mock_path)
-} else {
-  cat("Using actual GWP data.")
-}
-
-# Load data files and merge to one table
-gbd <- list.files(
-  "data-raw/GBD/",
-  pattern = ".zip", full.names = TRUE, recursive = TRUE
-) %>%
-  read_csv()
-
-# First step is to clean names and remove unnecessary variables
-gbd <- clean_names(gbd)
-# distinct(gbd, measure, metric)
-gbd <- select(gbd, -measure, -metric)
-
-# Rates to percentages
-gbd <- gbd %>%
-  mutate(across(c(val, upper, lower), ~ .x / 1000))
-
-# Clean cause names
-# distinct(gbd, cause)
-gbd <- gbd %>%
-  mutate(
-    cause = case_when(
-      cause == "Anxiety disorders" ~ "Anxiety",
-      cause == "Depressive disorders" ~ "Depression",
-      cause == "Self-harm" ~ "Selfharm"
-    )
-  )
-
-# Harmonise variable names with other datasets
-gbd <- gbd %>%
-  rename(country = location, outcome = cause)
-
-# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
-gbd <- gbd %>%
-  mutate(sd = (upper - lower) / (1.96 * 2)) %>%
-  select(-c(upper, lower))
-
-# Harmonise old names and replace only if harmonised name found
-gbd <- gbd %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Download data sets from the ITU website if not yet downloaded
-if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
-  dir.create("data-raw/ITU")
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/July/PercentIndividualsUsingInternet.xlsx",
-    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
-  )
-  download.file(
-    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/July/MobileBroadbandSubscriptions_2007-2021.xlsx",
-    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
-  )
-}
-
-# Read and reshape mobile broadband data
-itu_mobile <- read_xlsx(
-  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
-  sheet = 2,
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Economy)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(mobile = as.numeric(value)) %>%
-  select(country = Economy, year, mobile)
-
-# Percent using internet
-itu_percent <- read_xlsx(
-  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
-  col_types = "text"
-) %>%
-  pivot_longer(-c(Indicator, Economy)) %>%
-  separate(name, into = c("year", "variable")) %>%
-  pivot_wider(names_from = variable) %>%
-  mutate(internet = as.numeric(value)) %>%
-  select(country = Economy, year, internet)
-
-# Merge to one table in wide format (oldest on left to include all years)
-itu <- reduce(list(itu_percent, itu_mobile), left_join)
-
-# years to numbers
-itu <- itu %>%
-  mutate(year = as.numeric(year))
-
-# Drop tables
-rm(itu_mobile, itu_percent)
-
-# Harmonise old names and replace only if harmonised name found
-itu <- itu %>%
-  mutate(
-    country_harmonised = countryname(
-      country,
-      destination = "cldr.short.en"
-    )
-  ) %>%
-  # This picks the harmonised name if exists, otherwise original name
-  mutate(country = coalesce(country_harmonised, country)) %>%
-  select(-country_harmonised)
-
-# Drop countries that don't exist in outcomes
-itu <- itu %>%
-  filter(
-    country %in% unique(gbd$country) | country %in% unique(gwp$country)
-  )
-
-# Drop countries that don't have any actual internet data
-itu_zeros <- itu %>%
-  group_by(country) %>%
-  summarise(s = sum(internet, na.rm = TRUE)) %>%
-  filter(s == 0)
-
-itu <- itu %>%
-  filter(!(country %in% itu_zeros$country))
-rm(itu_zeros)
-
-# Reshape to easily impute all variables
-itu_long <- itu %>%
-  pivot_longer(c(internet, mobile))
-
-# Impute by country and variable
-itu_long <- itu_long %>%
-  group_by(country, name) %>%
-  # Find first and last year with this variable in each country
-  # so as to prevent extrapolation
-  mutate(
-    min_year = year[min(which(!is.na(value)))],
-    max_year = year[max(which(!is.na(value)))]
-  ) %>%
-  # Interpolate values linearly
-  # use possibly() to avoid errors for countries with no data
-  mutate(
-    across(
-      value,
-      .fns = list(
-        i = possibly(
-          function(x) na_interpolation(x, maxgap = Inf),
-          otherwise = NaN
-        )
-      )
-    )
-  ) %>%
-  # Take out projected (non-intermediate) imputed values
-  mutate(
-    value_i = if_else(
-      between(year, unique(min_year), unique(max_year)),
-      value_i,
-      NaN
-    )
-  ) %>%
-  ungroup() %>%
-  select(-min_year, -max_year)
-
-# Summary
-itu_sum <- itu_long %>%
-  filter(!(name=="mobile" & year < 2007)) %>% 
-  group_by(Metric = name) %>%
-  summarise(
-    total = n(), 
-    total_not_missing = sum(!is.na(value)),
-    missing = sum(is.na(value)),
-    imputed = sum(is.na(value) & !is.na(value_i))
-  )
-
-# We then replace the original values with the imputed ones
-itu <- itu_long %>%
-  # Pick non-missing value, from original and imputed
-  mutate(value = coalesce(value, value_i)) %>%
-  select(-value_i) %>%
-  pivot_wider()
-rm(itu_long)
-
-regions <- bind_rows(
-  distinct(itu, country),
-  distinct(gbd, country),
-  distinct(gwp, country)
-) %>% 
-  distinct() %>% 
-  mutate(
-    region = countrycode(
-      country, 
-      origin = "country.name", 
-      destination = "continent"
-    )
-  )
-
-# Manually fix two countries
-regions <- regions %>% 
-  mutate(
-    region = if_else(country == "Kosovo", "Europe", region),
-    region = if_else(country == "Nagorno Karabakh", "Asia", region)
-  )
-
-# Add regions to data tables
-itu <- left_join(itu, regions)
-gbd <- left_join(gbd, regions)
-gwp <- left_join(gwp, regions)
-
-# Stack outcome data
-dat <- bind_rows(gwp, gbd)
-
-# Merge predictors to outcomes
-dat <- left_join(dat, itu)
-
-# Center year
-dat <- dat %>%
-  mutate(year = (year - 2010))
-
-# Ensure that categorical variables are factors
-dat <- dat %>%
-  mutate(across(c(sex, age), factor))
-
-# Arrange on outcome
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-dat <- dat %>%
-  mutate(outcome = factor(outcome, levels = oo)) %>% 
-  arrange(outcome, country, region, year)
-
-# Save data for models
-saveRDS(dat, "data/data-all.rds")
-```
-
 In 2005, an estimated 17% of the global population used the internet, but by 2020 this number was already 59% [@ituITUICTStatistics2021].
 Accompanying the rapid spread of the internet, worries have proliferated that its broad adoption—and technologies enabled by it such as online games, smartphones, and social media—is actively harming its users, particularly adolescents [@carrShallowsHowInternet2010; @turkleAloneTogetherWhy2011].
-As a response, users and a growing number of national governments have acted in limiting access to online technologies [@buckleyChinaTightensLimits2021; @departmentfordigitalculturemedia&sportDraftOnlineSafety2021; @kattulaGamePoliciesContexts2021].
+As a response, users and a growing number of national governments have acted in limiting access to online technologies [@buckleyChinaTightensLimits2021; @departmentfordigitalculturemediasportDraftOnlineSafety2021; @kattulaGamePoliciesContexts2021].
 
@@
 Initial reports of internet-facilitated harms have been challenged by later work informed by many methodologies including longitudinal [@jensenYoungAdolescentsDigital2019], specification curve analyses [@orbenAssociationAdolescentWellbeing2019], meta-analyses [@appelAreSocialMedia2020], and systematic reviews [@bestOnlineCommunicationSocial2014; @dickson2018screen; @odgersAnnualResearchReview2020; @ophirNewMediaScreenTime2020].
-Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [ghaiLackSampleDiversity2023; @ghaiSocialMediaAdolescent2022], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
+Reviews indicate early research has been hampered by inaccurate measurements of engagement with internet and related technologies [@davidsonFuzzyConstructsTechnology2022; @parrySystematicReviewMetaanalysis2021; @scharkowAccuracySelfReportedInternet2016], biased convenience samples drawn predominantly from countries in the Global North [@ghaiLackSampleDiversity2023; @ghaiSocialMediaAdolescent2022], studying a limited range of well-being outcomes [@orbenSocialMediaEnduring2019], and reliance on self-reported evaluations in place of clinical estimates of important mental health outcomes [@campbellInternetUseSocially2006].
 A comprehensive test of the overall association between internet adoption and well-being and mental health, broadly defined, has therefore not been conducted.
@@
 
-```{r gwp-data-summaries}
+```{r data-summary-wb}
 gwp_sum <- gwp %>% 
@@
   mutate(across(n:cells, ~number(., big.mark = ",")))
+gwp_sum
 ```
@@
 
+```{r data-summary-itu}
+itu %>% 
+  summarise(
+    i = sum(!is.na(internet)),
+    m = sum(!is.na(mobile))
+  )
+```
+
 We identified the International Telecommunication Union's (ITU) database of information and communications technology (ICT) as the most comprehensive country-level source of time-series data on internet adoption [@ituITUICTStatistics2021].
-The ITU has collated, from 222 countries' statistical and telecommunications agencies, the yearly percentages of population using the internet from 2000 to `r max(itu$year)`, and yearly per capita broadband subscriptions from 2007 to `r max(itu$year)`.
-Our analyses used `r number(itu_sum[1, 3, drop = TRUE], big.mark = ",")` yearly internet percentages and `r number(itu_sum[2, 3, drop = TRUE], big.mark = ",")` broadband subscription rates; we imputed `r number(itu_sum[1, 5, drop = TRUE], big.mark = ",")` (`r number(itu_sum[2, 5, drop = TRUE], big.mark = ",")` mobile) intermediate missing values to this dataset using linear interpolation without extrapolation.
+The ITU has collated, from 222 countries' statistical and telecommunications agencies, the yearly percentages of population using the internet from 2000 to 2021, and yearly per capita mobile broadband subscriptions from 2007 to 2021.
+Our analyses used 4,200 yearly internet percentages and 2,466 broadband subscription rates.
 
@@
 
-We examined subjective well-being indicators from the Gallup World Poll (GWP), a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from `r length(unique(gwp$country))` countries from 2005 to 2021.
+We examined subjective well-being indicators from the Gallup World Poll (GWP), a nationally representative annual survey of 1,000 civilian, non-institutionalised individuals aged 15 years or older from `r length(unique(gwp$country))` countries from 2005 to 2022.
 The surveys are conducted face-to-face or via telephone, in the respondents' native language and by local interviewers.
@@
 
-We analysed the data with meta-analytic bayesian hierarchical regression models [@burknerBrmsPackageBayesian2017; @gelmanDataAnalysisUsing2007; @standevelopmentteamStanModelingLanguage2021].
-We first asked how the well-being outcomes had changed over time.
+We analysed the data with meta-analytic bayesian hierarchical regression models [@burknerBrmsPackageBayesian2017; @gelmanDataAnalysisUsing2007; @standevelopmentteamStanModelingLanguage2022].
 Bayesian methods are especially suitable to our reserch questions, because they involve many potential contrasts between e.g.
@@
 Using bayesian hierarchical models allowed us to accurately quantify uncertainty at different levels of analyses while avoiding problems with multiple comparisons (see below).
+
+We first asked how the well-being outcomes had changed over time.
 To answer, we modelled each outcome (e.g.
-life satisfaction) on population level intercepts (we centred time on 2010), contrasts of time (in continuous years), sex (Female: 1, Male: -1), and their interaction.
+life satisfaction) on population level intercepts (we centred time on 2010), contrasts of time (in continuous years), sex (Male: -1, Female: 1), and their interaction.
 We allowed all coefficients to vary across countries, age groups, and the age by country interactions, and treated all outcomes as normally distributed.
@@
 
-We specified the model as
+More formally, we specified the model as
 
 \begin{align*} 
-y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{sd}^2_i}), \\
+y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{se}^2_i}), \\
 \mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
@@
 
-where $i$ indexes rows in the data and $\text{sd}_i$ are the known standard deviations.
+where $i$ indexes rows in the data and $\text{se}_i$ are the known standard errors.
 $\text{X}^{\text{CW}}_i$ and $\text{X}^{\text{CB}}_i$ are the within- and between-country centred internet technology adoption predictor (per capita internet users or mobile broadband subscriptions, in separate models), respectively.
-In addition to the standard deviations, we weighted each observation by the number of respondents in that cell, to adjust for varying sample sizes across cells.
-We used default noninformative priors on all parameters.
+We used default noninformative priors [@burknerBrmsPackageBayesian2017] on all parameters except the following population-level coefficients, that we modelled as
+
+\begin{align*}
+\alpha_{1,3-6} &\sim \text{Normal}(0, 1), \\
+\alpha_{2} &\sim \text{Normal}(0, 3).
+\end{align*}
+
+We used these priors to help model convergence, and on the assumption that differences in well-being between males and females are likely greater than differences associated with years, one-percent increases in technology adoption predictors, or the interaction terms.
 
@@
 
-We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021].
-We ran 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations.
-We ensured that all population-level parameters' had converged using numeric diagnostics (all Rhats were within 0.01 of 1) and visual inspection of parameters' scatterplot matrices.
+We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2022] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2022].
+
+Our main descriptive focus was on raw regression coefficients, which indicate contrasts in the outcomes on the percentage scale [@cohenProblemUnitsCircumstance1999] as a function of one unit (year / percent) increase in the predictor.
+We report these parameters' 95% Credibility Intervals (CI) and posterior probabilities of direction ($p^d$).
+The latter indicate the degree of certainty in the observed direction of a coefficient, and are sometimes numerically similar to one minus a one-sided *p*-value.
+
+In addition, on a reviewer's request we report standardized coefficients to describe the magnitudes in an alternative context.
+These standardized coefficients indicate contrasts in the z-scored outcomes (life satisfaction SD: `r number(z$val_sd[1], .1)`; negative experiences: `r number(z$val_sd[4], .1)`; positive experiences: `r number(z$val_sd[7], .1)`) as a function of the average year-on-year changes in internet (`r number(z$xdev[2], .1)`%) or mobile broadband (`r number(z$xdev[3], .1)`%) adoption.
+To determine the practical significance of the standardized associations, we report posterior probabilities that their magnitudes exceed the region of practical equivalence to zero ($p^{\text{ROPE}}$) [@kruschkeRejectingAcceptingParameter2018] as defined by [-0.1, 0.1] [@fergusonProvidingLowerboundEstimate2021].
 
@@
 
-```{r data-describe}
-gwp %>% 
-  group_by(outcome) %>% 
-  summarise(n=sum(n)) %>% 
-  summarise(N=comma(median(n))) %>% 
-  pull(N)
-
-bind_rows(
-  "GWP" = gwp,
-  "GBD" = gbd,
-  .id = "Dataset"
-) %>% 
-  mutate(Dataset = fct_inorder(Dataset)) %>% 
-  count(Dataset, outcome) %>% 
-  bind_rows(
-    itu %>% 
-      select(internet, mobile) %>% 
-      pivot_longer(everything(), names_to = "outcome") %>% 
-      drop_na(value) %>% 
-      count(outcome) %>% 
-      mutate(Dataset = "ITU")
-  )
-
-# Individuals using the internet per 100 inhabitants | World
-if (!file.exists(
-  "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")) {
-  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")
-}
-read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
-```
-
-```{r models-load}
-# Create a table of outcomes in appropriate order, so can map functions over this
-oo <- c(
-  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
-  "Anxiety", "Depression", "Selfharm"
-)
-
-fits <- tibble(
-  path = list.files("models", pattern = "brm-", full.names = TRUE),
-  outcome = basename(path)
-) %>%
-  separate(outcome, c("discard", "outcome", "model"), sep = "-") %>% 
-  mutate(model = str_extract(model, "[0-9]")) %>% 
-  filter(outcome %in% oo) %>% 
-  mutate(fit = map(path, readRDS)) %>% 
-  select(-c(path, discard)) %>% 
-  mutate(outcome = factor(outcome, levels = oo))
-fits_wb <- fits %>% 
-  filter(outcome %in% oo[1:3])
-fits_mh <- fits %>% 
-  filter(outcome %in% oo[4:6])
-rm(fits)
-```
-
-```{r gwp-model-diagnostics}
-if (length(list.files("diagnostics/wb")) == 0) {
-  rhats <- fits_wb %>% 
-    mutate(
-      out = map(
-        fit, 
-        ~describe_posterior(
-          .x, 
-          ci_method = "eti", 
-          test = NULL, 
-          effects = "all",
-          parameters = "^cor_|^sd_|^b_"
-        ) %>% 
-          as_tibble() %>% 
-          select(Parameter, Rhat, ESS)
-      )
-    ) %>% 
-    select(-fit) %>% 
-    unnest(out)
-
-  # Show a table of bad rhats
-  rhats %>%
-    filter(!near(Rhat, 1, tol = .01))
-
-  # Draw a scatterplot of parameters with 9 worst rhats
-  # Create a tabset of this in HTML output
-  rhats_sum <- rhats %>% 
-    group_by(outcome, model) %>% 
-    arrange(outcome, model, desc(abs(Rhat))) %>% 
-    slice(1:9) %>% 
-    summarise(v = list(str_c(Parameter))) %>% 
-    ungroup() %>% 
-    right_join(fits_wb)
-
-  dir.create("diagnostics/wb", FALSE, recursive = TRUE)
-  for (i in 1:nrow(rhats_sum)) {
-    x <- slice(rhats_sum, i)
-    path <- str_glue("diagnostics/wb/{x$outcome}-{x$model}.png")
-    png(path, width = 1200, height = 1200, res = 120)
-    pairs(x$fit[[1]]$fit, pars = x$v[[1]])
-    dev.off()
-
-  }
-}
-```
-
-```{r gwp-model-process}
-# Extract the relevant parameters' summaries from the models
-tab_wb <- fits_wb %>% 
-  mutate(
-    out = map(
-      fit,
-      ~describe_posterior(
-        .x, 
-        effects = "all", 
-        centrality = "mean", 
-        ci = 0.95, 
-        ci_method = "ETI", 
-        test = "pd",
-        diagnostic = NULL
-      )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  select(-CI)
-tab_wb <- tab_wb %>% 
-  # Clean parameter names
-  separate(
-    Parameter, 
-    into = c("factor", "country", "parameter"), 
-    sep = "\\[|\\]|,"
-  ) %>%
-  mutate(
-    parameter = if_else(
-      Effects == "fixed",
-      str_remove(factor, "^b_"),
-      parameter
-    ),
-    # Clean predictor name
-    Predictor = case_when(
-      parameter == "year" & model == "1" ~ "Time",
-      parameter == "i_cw" ~ "Internet",
-      parameter == "m_cw" ~ "Mobile"
-    ) %>% factor(., levels = c("Time", "Internet", "Mobile"))
-  ) %>% 
-  mutate(
-    cred = pd > .975
-  )
-
-```
-
-Figure \@ref(fig:fig-gwp-data)A describes the levels of internet and mobile broadband adoption, and the three well-being variables over time averaged over sex and age.
-Figure \@ref(fig:fig-gwp-data)A shows the universal global penetration of internet technologies in the past two decades, and suggests that in contrast, changes in well-being are likely to be small.
-
-```{r tab-gwp-estimates}
-avg_wb <- tab_wb %>% 
-  filter(Effects == "fixed") %>%
-  mutate(
-    Predictor = case_when(
-      factor == "b_year" & model == "1" ~ "Time Within country",
-      factor == "b_i_cw" ~ "Internet Within country",
-      factor == "b_m_cw" ~ "Mobile Within country",
-      factor == "b_i_cb" ~ "Internet Between countries",
-      factor == "b_m_cb" ~ "Mobile Between countries"
-    )
-  ) %>% 
-  drop_na(Predictor) %>% 
-  # Create a result string for table
-  mutate(
-    Estimate = str_glue(
-      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
-    ),
-    pd = percent2(pd)
+Figure \@ref(fig:fig-means-wb)A describes the levels of internet and mobile broadband adoption, and the three well-being variables over time averaged over sex and age.
+Figure \@ref(fig:fig-means-wb)A shows the universal global penetration of internet technologies in the past two decades, and suggests that in contrast, changes in well-being are likely to be small.
+
+```{r tbl-avg-wb}
+#| include: true
+
+tbl_average <- coefficients %>% 
+  filter(
+    level == "average",
+    sex == "average"
   ) %>% 
   select(
-    Predictor, 
+    Predictor = predictor, 
     Outcome = outcome, 
-    Estimate,
-    pd
-  ) %>% 
-  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
-  mutate(
-    Predictor = factor(
-      Predictor, 
-      levels = c("Time", "Internet", "Mobile")
-    )
-  ) %>% 
-  arrange(Predictor, Outcome)
-
-avg_wb %>% 
-  mutate(
-    Estimate = str_glue("{Estimate} ({pd})"),
-  ) %>% 
-  select(-pd) %>% 
-  pivot_wider(names_from = x, values_from = Estimate) %>% 
-  group_by(Predictor) %>% 
-  mutate(i = 1:n()) %>% 
-  ungroup() %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(i==1, Predictor, ''),
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  )
+
+tbl_average %>% 
+  filter(Outcome %in% oo[1:3]) %>% 
+  mutate(
+    Predictor = if_else(Outcome %in% oo[c(1, 4)], Predictor, ''),
     Outcome = str_replace(Outcome, "_", " ")
   ) %>% 
-  select(-i) %>% 
-  replace_na(list(`Between countries` = '')) %>% 
+  # Justify considering negative estimates
   mutate(
@@
     span_text_columns = TRUE, 
+    font_size = "small",
     escape = FALSE,
-    note = "Estimates are percentage changes in outcomes associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
-LS: Life satisfaction, NE: Negative experiences, PE: Positive experiences.
-Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
-  )
-```
-
-We found that, for the average country, life satisfaction had remained relatively stable, whereas both negative and positive experiences had increased (Figure \@ref(fig:fig-gwp-data)B).
-Interestingly, the increase in negative experiences was nearly sixfold to that in positive experiences.
-Although we found a sizeable average increase in negative experiences, these results were mixed and so did not offer convincing evidence for consistent global changes in well-being during this period of global internet technology adoption, as would be expected if the latter had broad negative consequences.
-
-We then turned to our main question; understanding the extent to which internet technology adoption predicted changes in well-being.
-We expanded the model of temporal changes to also predict well-being from within- and between-country centred per capita internet users and mobile broadband subscriptions (Figure \@ref(fig:fig-gwp-data)B, Within-country associations).
-The within-country associations are our key estimates of interest and describe the extent to which a one-percent increase in a country's per capita internet users (or mobile broadband subscriptions) predict that country's well-being and mental health, adjusting for linear temporal trends.
-
-```{r fig-gwp-data}
+    note = "Raw estimates are contrasts in outcome percentages associated with a one year or percentage increase in the predictor.
+Numbers indicate posterior means, [95\\%CIs], and ($p^d$; posterior probabilities of direction).
+Standardized estimates refer to contrasts in the z-scored outcome as function of the average year-on-year change in the predictor.
+The latter percentages indicate posterior probabilities inside a region of practical equivalence to zero ([-0.1, 0.1]; $p^{\\text{ROPE}}$)."
+  )
+```
+
+### Trends
+
+We found that, for the average country, life satisfaction had remained relatively stable, whereas both negative and positive experiences had increased (Table \@ref(tab:tbl-avg-wb); blue lines and ribbons in Figure \@ref(fig:fig-means-wb)A).
+Interestingly, the increase in negative experiences (second row in Table \@ref(tab:tbl-avg-wb)) was approximately fivefold to that in positive experiences.
+However, simple sign tests do not inform about the practical significance of magnitudes of changes.
+On the standardized scale, the coefficients were small ("Standardized estimate" in Table \@ref(tab:tbl-avg-wb)), and in all cases practically equivalent to zero with very high confidence.
+Because these trends were mixed across outcomes, and practically equivalent to zero in all cases, these results do not offer convincing evidence for consistent or meaningfully large global changes in well-being during this period of global internet technology adoption, as would be expected---all else being equal---if the latter had broad negative consequences.
+
+### Average associations
+
+We then turned to our main question; understanding to what extent internet technology adoption predicted changes in well-being.
+We expanded the model of temporal changes to also predict well-being from within- and between-country centred per capita internet users or mobile broadband subscriptions (Table \@ref(tab:tbl-avg-wb), "Internet" and "Mobile").
+The raw coefficients describe the extent to which a one-percent increase in within-country centered per capita internet users (or mobile broadband subscriptions) predict that country's well-being, adjusting for linear temporal trends.
+The standardized estimates describe the same quantities, but in terms of contrasts in the z-scored outcomes and average year-on-year percentage changes in the outcomes.
+
+```{r fig-wb-ce}
+#| cache: false
+# Conditional effects plots
+
+draw_double_axes <- function(pdata, predictor, ys = 1, ym = 0, xs = 1, outcome) {
+  ylab <- str_replace(outcome, "_", " ")
+
+  # pct_to_rate <- if_else(outcome %in% oo[1:3], 1, 1000)
+
+  p <- pdata %>% 
+    ggplot(aes(effect1__, estimate__)) +
+    geom_ribbon(
+      aes(ymin = lower__, ymax = upper__),
+      alpha = .2, fill = "dodgerblue1"
+    ) +
+    geom_line(
+      color = "dodgerblue3",
+      linewidth = 0.75
+    ) + 
+    scale_y_continuous(
+      ylab,
+      expand = expansion(mult = 1),
+      breaks = extended_breaks(),
+      sec.axis = sec_axis(
+        trans = ~ (. - ym) / ys, 
+        breaks = extended_breaks(7),
+        name = str_glue("{ylab}\n(standardized)")
+        )
+    ) +
+    scale_x_continuous(
+      predictor,
+      breaks = extended_breaks(7),
+      minor_breaks = seq(-50, 50, by = 5),
+      sec.axis = sec_axis(
+        trans = ~ . / xs, 
+        breaks = extended_breaks(7),
+        name = str_glue("{predictor} (scaled)")
+      )
+    )
+  if (predictor == "Year") {
+    p <- p + 
+      scale_x_continuous(
+        "Year",
+        minor_breaks = seq(-5, 12, by = 1),
+        labels = ~ . + 2010
+      )
+  }
+  if (predictor %in% c("Internet", "Mobile")) {
+    p <- p %+% filter(p$data, between(effect1__, -30, 30))
+  }
+
+  p
+}
+epred <- epred %>% 
+  mutate(
+    p = pmap(
+      list(pdata, predictor, val_sd, val_mean, xdev, outcome),
+      ~draw_double_axes(..1, ..2, ..3, ..4, ..5, ..6))
+  )
+```
+
+```{r fig-means-wb}
 #| include: true
-#| fig.height: !expr ifelse(knitr::is_latex_output(), 7.6, 5)
-#| fig.cap: "\\textbf{A.} Time courses of per capita internet users (row one), mobile broadband subscriptions (row two), and three psychological well-being outcomes (rows three to five).
-Lines indicate countries' yearly means of the respective variable, aggregated across sex and age.
-\\textbf{B.} Posterior probability distributions of population-level associations (green: between countries, red: within countries) between each of three well-being outcomes and time, per capita internet users, and per capita mobile broadband subscriptions.
-Estimates are percentage changes in outcomes associated with a one year or percent increase in the predictor.
-Points and lines indicate posterior means and 95\\%CIs, filled points indicate that zero is not among the 95\\% most credible parameter values."
-
-p1 <- itu %>%
+#| fig.height: 6
+#| fig.width: 8
+#| fig.env: "figure*"
+#| fig.cap: \emph{A}.
+Time courses of per capita internet users, mobile broadband subscriptions, and three psychological well-being outcomes.
+Thin dark lines indicate countries' yearly means, aggregated across sex and age.
+Blue lines and ribbons indicate model-implied regression lines (exploratory generalized additive model fits for Internet and Mobile broadband adoption.) \emph{B-D}.
+Estimated conditional means of three well-being metrics on within-country centered per-capita internet users.
+Primary x- (bottom) and y-axes (left) display raw predictor and outcome values, secondary axes (top, right) display z-scored outcomes and average year-on-year scaled within-country internet adoption.
+\emph{E-G}.
+Same as B-D but for mobile broadband adoption.
+
+p1_data <- itu %>%
   select(
-    region, country, year,
+    country, year,
     Internet = internet,
@@
   ) %>%
-  # Truncate mobile percentages for figure
-  mutate(Mobile = if_else(Mobile > 150, NaN, Mobile)) %>%
   pivot_longer(
@@
   ) %>% 
-  bind_rows(gwp) %>%
-  mutate(outcome = fct_inorder(str_replace(outcome, "_", "_"))) %>%
-  group_by(region, country, year, outcome) %>%
+  bind_rows(gwp, gbd) %>%
+  group_by(country, year, outcome) %>%
   summarise(mean = mean(val, na.rm = TRUE)) %>%
@@
   mutate(outcome = factor(outcome, levels = c("Internet", "Mobile", oo))) %>% 
-  mutate(year = make_date(year)) %>%
+  drop_na(mean)
+
+p1_data_model <- epred %>% 
+  filter(predictor == "Year") %>% 
+  select(predictor, outcome, pdata) %>% 
+  unnest(pdata)
+
+fig_ce_wb <- wrap_plots(
+  wrap_plots(epred$p[c(2, 5, 8)]),
+  wrap_plots(epred$p[c(3, 6, 9)]),
+  ncol = 1
+) & theme(
+  panel.grid.major = element_line(linewidth = .1, color = "grey50")
+)
+
+p1 <- p1_data %>% 
+  filter(!(outcome %in% oo[4:6])) %>% 
   ggplot(aes(year, mean)) +
@@
     breaks = pretty_breaks(),
-    expand = expansion(.05)
-  ) +
-  scale_x_date(
+    expand = expansion(.01)
+  ) +
+  scale_x_continuous(
     "Year",
-    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
-    date_labels = "'%y",
+    breaks = c(2000, 2005, 2010, 2015, 2020),
+    labels = c("'00", "'05", "'10", "'15", "'20"),
     expand = expansion(.02)
+  ) +
+  coord_cartesian(ylim = c(0, 100)) +
+  geom_smooth(
+    data = filter(p1_data, outcome %in% c("Internet", "Mobile")),
+    method = "gam",
+    col = "dodgerblue3",
+    fill = alpha("dodgerblue1", .3),
+    linewidth = 0.7
+  ) +
+  geom_lineribbon(
+    data = p1_data_model %>% filter(outcome %in% oo[1:3]),
+    aes(y = estimate__, ymin = lower__, ymax = upper__, x = year + 2010),
+    col = "dodgerblue3",
+    fill = alpha("dodgerblue1", .3),
+    linewidth = 0.7
   ) +
@@
     ),
-    size = .05, col = "dodgerblue3"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
+    linewidth = .02, alpha = .2
+  ) +
+  facet_wrap(
+    "outcome",
+    scales = "free_x",
+    nrow = 1,
     labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
@@
   )
-
-x <- fits_wb %>% 
-  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
-  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
-  mutate(
-    Predictor = case_when(
-      parameter == "b_year" & model == "1" ~ "Time Within country",
-      parameter == "b_i_cw" ~ "Internet Within country",
-      parameter == "b_m_cw" ~ "Mobile Within country",
-      parameter == "b_i_cb" ~ "Internet Between countries",
-      parameter == "b_m_cb" ~ "Mobile Between countries"
-    )
-  ) %>% 
-  drop_na(Predictor, value) %>% 
-  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
-  mutate(
-    Predictor = factor(
-      Predictor, 
-      levels = c("Time", "Internet", "Mobile")
-    )
-  )
-p2 <- x %>%   
-  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
-  scale_color_brewer(
-    "Association", palette = "Set2", aesthetics = c("fill", "color")
-  ) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_x_continuous(
-    "Estimated linear association",
-    breaks = extended_breaks()
-  ) +
-  stat_halfeye(
-    aes(shape = after_stat(sign(xmax) == sign(xmin))),
-    position = position_dodge(.15), 
-    normalize = "xy", 
-    height = .8,
-    point_interval = "mean_qi",
-    fatten_point = 3,
-    point_fill = "white",
-    size = .25,
-    slab_alpha = .75,
-    adjust = 1.5,
-    .width = .95
-    ) +
-  facet_wrap(
-    "outcome", 
-    labeller = labeller(
-      .cols = as_labeller(~str_replace(., "_", " "))
-    ),
-    scales = "free_x"
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title.y = element_blank(),
-    panel.grid.major.x = element_line(
-      color = "black", linetype = "dotted", size = .1
-    )
-  )
-
-(p1 / p2) + 
-  plot_layout(heights = c(8, 2)) +
+(p1 / fig_ce_wb) +
+  plot_layout(heights = c(22, 78)) +
   plot_annotation(tag_levels = "A")
@@
 
-```{r}
-fits_wb %>% 
-  filter(model != 1) %>% 
-  mutate(
-    sigma = map_dbl(
-      fit,
-      ~mean(as.data.frame(.x, variable = "sigma")$sigma)
-    )
-  )
-itu %>% 
-  pivot_longer(internet:mobile) %>% 
-  group_by(country, name) %>% 
-  mutate(increase = value - lag(value)) %>% 
-  group_by(name) %>% 
-  summarise(mean_yearly_increase = mean(increase, na.rm = TRUE))
-```
-
-Internet adoption did not predict any outcome at the 95% credibility level, but a 1% increase in per capita internet users predicted a `r avg_wb[6, 4]` increase in negative experiences for the average country with `r avg_wb[6, 5]` posterior probability of direction.
-Mobile broadband, on the other hand, positively predicted life satisfaction (`r avg_wb[10, 4]`), with greater evidence for direction (`r avg_wb[10, 5]`).
-In light of substantial residual standard deviations ranging from about 6 to 8 between predictors and outcomes, and average yearly increases in internet technology adoption (internet = 2.7%, mobile = 5.8%) the observed associations were very small.
-
-```{r}
-tmpr <- fits_wb %>% 
-  filter(model > 1) %>% 
-  mutate(
-    sdx = map_dbl(fit, ~sd(.x$data[,4])),
-    sdy = map_dbl(fit, ~sd(.x$data[,1]))
-  ) %>% 
-  mutate(
-    x = map(
-      fit, 
-      ~as_draws_df(.x, variable = "b_[i|m]_cw$", regex = TRUE) %>% 
-        rename(b = 1) %>% 
-        mutate(r = b * (sd(.x$data[,4]) / sd(.x$data[,1])), .keep = "unused") %>% 
-        describe_posterior(
-          centrality = "mean", 
-          ci = 0.95, 
-          ci_method = "ETI", 
-          test = "pd",
-          diagnostic = NULL
-        ) %>% 
-        as_tibble())
-  ) %>% 
-  mutate(model = factor(model, labels = c("Internet", "Mobile"))) %>% 
-  unnest(x) %>% 
-  mutate(
-    result = str_glue(
-      "{number(Mean, .001)} [{number(CI_low, .001)}, {number(CI_high, .001)}]"
-    ),
-    .keep = "unused"
-  ) %>% 
-  select(outcome, model, result)
-tmpr
-```
-
-In addition to these recommended raw associations [@baguleyStandardizedSimpleEffect2009], we also computed the standardized average associations ($\alpha_4(\frac{\sigma_x}{\sigma_y})$).
-In line with the unstandardized coefficients reported above, the standardized associations were small according to common guidelines: (life satisfaction & internet = `r tmpr$result[1]`, life satisfaction & mobile = `r tmpr$result[2]`, negative experiences & internet = `r tmpr$result[3]`, negative experiences & mobile = `r tmpr$result[4]`, positive experiences & internet = `r tmpr$result[5]`, positive experiences & mobile = `r tmpr$result[6]`).
-
-```{r fig-gwp-country}
-#| cache: false
-figure_country <- function(data) {
-  data %>% 
-    # Show countries and main relations
-    filter(factor == "r_country") %>% 
-    drop_na(Predictor) %>% 
-    # Take out countries with only time association from this figure
-    add_count(outcome, country) %>% 
-    filter(n > 1) %>% 
+Per capita internet users did not credibly predict any of the three well-being metrics: A one percent increase in per capita internet users predicted small increases in life satisfaction (Figure \@ref(fig:fig-means-wb)B), negative experiences (Figure \@ref(fig:fig-means-wb)C), and positive experiences (Figure \@ref(fig:fig-means-wb)D) for the average country, but the probabilities of direction ($p^d$) did not exceed the 95% threshold.
+Thus, based on simple sign tests, per-capita internet adoption was not a credible predictor of well-being.
+Moreover, in standardized terms, all three associations were squarely within the [-0.1, 0.1] ROPE: An average year-on-year increase in internet adoption predicted smaller than [-0.1, 0.1] changes in life satisfaction, negative and positive experiences with greater than 99.9% posterior probability.
+Thus, there was evidence against a practically meaningfully large association between per capita internet adoption and all three well-being metrics.
+
+In addition, (within country centered) per capita mobile broadband subscriptions were at best weak predictors of well-being.
+While per capita mobile broadband subscriptions predicted life satisfaction positively (0.06%, $p^d$ > 99.9%; Figure \@ref(fig:fig-means-wb)E), this association was negative and not credibly different from zero for negative (Figure \@ref(fig:fig-means-wb)F) or positive experiences (Figure \@ref(fig:fig-means-wb)G).
+In standardized terms, all three associations between per capita mobile broadband adoption and well-being were credibly equivalent to zero (Table \@ref(tab:tbl-avg-wb), "Standardized estimate").
+
+In sum, we found that internet technology adoption did not predict life satisfaction, or negative or positive experiences to a meaningfully large degree.
+
+### Countries
+
+```{r tbl-cb-wb}
+coefficients %>% 
+  filter(
+    outcome %in% oo[1:3],
+    level == "cb",
+    predictor != "Year"
+  ) %>% 
+  mutate(
+    predictor = if_else(outcome == "Life_satisfaction", predictor, ''),
+    outcome = str_replace(outcome, "_", " ")
+  ) %>% 
+  select(
+    Predictor = predictor, 
+    Outcome = outcome, 
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  ) %>% 
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
+  apa_table(
+    caption = "Well-being: Between-country associations",
+    span_text_columns = TRUE,
+    font_size = "small",
+    escape = FALSE,
+    placement = "htb",
+    note = "Raw estimates are contrasts in outcome percentages associated with a one percentage increase in the predictor.
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).
+Standardized estimates refer to contrasts in the z-scored outcome as function of the average year-on-year change in the predictor.
+The latter percentages indicate posterior probabilities inside a region of practical equivalence to zero ([-0.1, 0.1])."
+  )
+```
+
+Our model also assessed the extent to which internet technology adoption predicted well-being between countries.
+These between-country associations indicated, with high confidence, that countries with greater average levels of internet and mobile broadband adoption tended to report greater average levels of life satisfaction and positive experiences, and lower average levels of negative experiences (Table \@ref(tab:tbl-cb-wb)).
+However, based on standardized magnitudes and ROPE tests, only the positive association between mobile broadband adoption and life satisfaction was credibly different from zero with >90% confidence.
+Other between-country associations were equivalent to zero on the standardized scale.
+To be clear, between-country associations are likely to reflect multiple other causes, such as socioeconomic factors and levels of inequality, impinging on both well-being and internet technology adoption.
+For example while wealthier nations are likely to have greater internet coverage, they also tend to have greater healthcare coverage, which in turn is likely to affect levels of well-being.
+
+```{r fig-country-wb}
+#| cache: true
+#| include: true
+#| fig.height: 6.4
+#| fig.width: 8
+#| fig.env: "figure*"
+#| fig.cap: "Country-specific yearly changes in three well-being outcomes (top row), and their associations with per capita internet users (second row) and mobile broadband subscriptions (third row).
+Points and lines indicate individual countries' posterior means and 95\\% CIs.
+Countries are sorted from the most negative to most positive estimate.
+Filled points indicate that the parameter's 95\\% credibility interval excludes zero (in both panels).
+Raw associations (bottom x-axes) indicate changes in the outcome percentage as function of percentage (or one year) change in the predictor.
+Scaled associations (top x-axes) indicate changes in standardized outcome as function of the average year-on-year change in the predictor.
+"
+
+figure_country <- function(y = "Life_satisfaction", x = "Year") {
+
+  d <- coefficients %>% 
+    filter(outcome == y, predictor == x, level == "country", sex == "average") %>% 
+    left_join(z)
+
+  p <- d %>% 
     # Arrange per panel
-    group_by(Predictor, outcome) %>% 
-    arrange(Predictor, outcome, Mean) %>% 
+    group_by(predictor, outcome) %>% 
+    arrange(predictor, outcome, mean) %>% 
     mutate(y = 1:n()) %>% 
-    ggplot(aes(Mean, y, col = cred)) +
+    ggplot(aes(mean, y, col = pd > .975)) +
+    geom_vline(xintercept = 0, linewidth = .33, linetype = "dashed", col = "grey70") +
     scale_color_manual(values = c("dodgerblue1", "dodgerblue3")) +
@@
       "Country",
-      # Fix country names
-      labels = ~str_replace_all(., "\\.", " ") %>% 
-        str_replace_all(., "’", "'"),
       expand = expansion(.015)
@@
     scale_x_continuous(
-      "Estimated linear association",
+      "Raw association",
       breaks = extended_breaks(6), 
-      expand = expansion(c(0.01))
+      expand = expansion(c(0.01)),
+      sec.axis = sec_axis(
+        trans = ~ . * unique(d$zfactor), 
+        breaks = extended_breaks(7),
+        name = "Scaled association"
+      )
     ) +
@@
     scale_linetype_manual(values = c(1, 1, 1)) +
-    geom_linerangeh(
-      size = .1,
-      aes(xmin = CI_low, xmax = CI_high, linetype = cred)
-    ) +
-    geom_point(
-      aes(shape = cred), 
-      size = .55, fill = "white", stroke = .2
+    geom_pointinterval(
+      aes(xmin = q2.5, xmax = q97.5, shape = pd > 0.975),
+      fill = "white",
+      interval_size_range = c(.1, .1),
+      fatten_point = 8,
+      stroke = .2
     ) +
@@
       color = guide_legend(override.aes = list(size = .5, stroke = 1))
-    ) +
-    facet_grid2(
-      Predictor~outcome,
-      scales = "free",
-      independent = "all",
-      labeller = labeller(
-        .cols = as_labeller(~str_replace(., "_", " "))
-      )
     ) +
@@
     )
+
+  if (y %in% oo[c(3, 6)]) {
+    p <- p +
+      facet_grid(
+        rows = vars(predictor), scales = "free_y",
+        labeller = as_labeller(~str_replace(., "_", " "))
+      ) +
+      theme(
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()
+        )
   }
-p_country_wb <- figure_country(tab_wb)
-```
-
-```{r gwp-demographics}
-wb_demo <- fits_wb %>% 
-  mutate(
-    x = factor(model, labels = c("year", "i_cw", "m_cw")),
-  ) %>% 
-  mutate(
-    out = map2(
-      fit, x, 
-      ~bind_rows(
-        world = hypothesis(
-          .x, 
-          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0")
-        )$hypothesis,
-        age = hypothesis(
-          .x, 
-          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0"),
-          scope = "coef", group = "age"
-        )$hypothesis
-      )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(Sex = if_else(str_detect(Hypothesis, "-1"), "Male", "Female")) %>% 
-  mutate(Group = if_else(is.na(Group), Sex, Group)) %>% 
-  mutate(
-    predictor = factor(
-      model, 
-      levels = 1:3, 
-      labels = c("Time", "Internet", "Mobile")
-    )
-  ) %>% 
-  mutate(cred = sign(CI.Lower) == sign(CI.Upper)) %>% 
-  mutate(
-    Group = factor(Group, levels = c("Female", "Male", levels(dat$age)))
-  )
-```
-
-```{r fig-gwp-demographics}
-#| cache: false
-figure_demographics <- function(data) {
-  data %>% 
-    ggplot(aes(Estimate, fct_rev(Group), col = Sex, shape = cred)) +
-    scale_color_brewer(palette = "Set2") +
-    scale_shape_manual(values = c(21, 19)) +
-    # Ensure zero shows
-    geom_blank(aes(x = 0)) +
-    scale_x_continuous(
-      "Estimated linear association",
-      breaks = extended_breaks(5),
-      expand = expansion(.15)
-    ) +
-    geom_linerangeh(
-      aes(xmin = CI.Lower, xmax = CI.Upper),
-      size = .3,
-      position = position_dodge2v(
-        height = .8,
-        padding = 1,
-        reverse = TRUE
-      )
-    ) +
-    geom_point(
-      size = 0.9,
-      fill = "white",
-      position = position_dodge2v(
-        height = .8,
-        padding = 1,
-        reverse = TRUE
-      )
-    ) +
-    guides(shape = "none") +
-    facet_grid2(
+
+  if (y %in% oo[c(2, 5)]) {
+    p <- p +
+      theme(
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()
+        )
+  }
+  if (x == "Year") {
+    p <- p +
+      facet_grid(
+        cols = vars(outcome), scales = "free_y",
+        labeller = as_labeller(~str_replace(., "_", " "))
+      )
+  }
+  if (y %in% oo[c(3, 6)] & x == "Year") {
+    p <- p +
+      facet_grid(
         rows = vars(predictor),
         cols = vars(outcome),
-      scales = "free_x", independent = "x",
+        scales = "free_y",
         labeller = as_labeller(~str_replace(., "_", " "))
+      )
+  }
+
+  p
+}
+tmp <- distinct(coefficients, outcome, predictor) %>% 
+  distinct(outcome, predictor) %>% 
+  filter(outcome %in% oo[1:3]) %>% 
+  arrange(predictor, outcome) %>% 
+  mutate(p = map2(outcome, predictor, ~figure_country(.x, .y))) %>% 
+  pull(p)
+wrap_plots(tmp)
+```
+
+```{r}
+tmp <- coefficients %>% 
+  filter(
+    predictor == "Year", 
+    outcome == "Life_satisfaction", 
+    level == "country", 
+    sex == "average"
+  ) %>% 
+  arrange(mean)
+tmp$Raw[[1]]
+tmp$Raw[[nrow(tmp)]]
+```
+
+While these trends and associations are meaningful summaries of the average country among the 168 examined, or associations between them, they do not represent specific countries which might have unique patterns of associations.
+Figure \@ref(fig:fig-country-wb) describes the country-level trends over time (top row) and associations linking per capita internet users (middle row) and mobile broadband subscriptions (bottom row) to each of the three outcomes (columns).
+We observed that all three were highly variable across countries.
+
+First, there appeared to be no universal temporal trend that applied to all countries.
+Instead, the country-specific estimates varied from substantial decreases (greatest decrease in e.g.
+life satisfaction: `r tmp$Raw[[1]]`) to large increases in well-being (greatest increase in e.g.
+life satisfaction: `r tmp$Raw[[nrow(tmp)]]`).
+We observed similar variability in country-specific associations linking well-being to internet adoption and to mobile broadband adoption (Figure \@ref(fig:fig-country-wb)).
+
+```{r tbl-country-prop-wb}
+tbl_props <- coefficients %>% 
+  filter(level == "country", sex == "average") %>% 
+  mutate(
+    Sign = case_when(
+      pd > .975 & sign(mean)==-1 ~ "Negative",
+      pd > .975 & sign(mean)==1 ~ "Positive",
+      TRUE ~ "Indecisive"
+    ),
+    ROPE = case_when(
+      rope < .05 & sign(mean)==-1 ~ "Negative",
+      rope < .05 & sign(mean)==1 ~ "Positive",
+      rope > .95 ~ "Null",
+      TRUE ~ "Indecisive"
+    )
+  ) %>% 
+  select(predictor, outcome, group, Sign, ROPE) %>% 
+  pivot_longer(c(Sign, ROPE)) %>% 
+  count(predictor, outcome, name, value) %>% 
+  mutate(
+    n = str_glue("{n} ({percent(n/sum(n), 1)})"), 
+    .by = c(outcome, predictor, name)
+  ) %>% 
+  pivot_wider(names_from = value, values_from = n) %>% 
+  mutate(across(c(Indecisive, Negative, Null, Positive), ~replace_na(., "0 (0%)"))) %>% 
+  rename(Predictor = predictor, Outcome = outcome, Test = name) %>% 
+  arrange(Predictor, Outcome, desc(Test)) %>%
+  pivot_wider(
+    names_from = Test, 
+    values_from = c(Indecisive, Negative, Null, Positive), 
+    names_vary = "slowest"
+  ) %>% 
+  select(-Null_Sign)
+
+tbl_props %>% 
+  filter(Outcome %in% oo[1:3]) %>% 
+    mutate(
+    Outcome = fct_inorder(str_replace(Outcome, "_", " "))
+  ) %>% 
+  as.data.frame() %>% 
+  setNames(str_remove(names(.), "_ROPE") %>% str_remove("_Sign")) %>% 
+  apa_table(
+    placement = "htb",
+    span_text_columns = TRUE,
+    col_spanners = list(` ` = c(1, 2), `Sign test` = c(3, 5), `ROPE` = c(6, 9)),
+    font_size = "small",
+    caption = "Well-being: Country-specific test summary",
+    note = "Numbers indicate counts and (percentages) of countries with different decisions either based on a sign test or a ROPE of [-0.1, 0.1] on the standardized scale."
+  )
+```
+
+To summarize these country-specific associations, we calculated proportions of countries with credibly positive, negative, null, and inconclusive associations based on either simple sign tests on the raw scale ($p^d$ > 97.5%), or ROPE tests on the standardized scale ($p^{\text{ROPE}}$ > 95%).
+Table \@ref(tab:tbl-country-prop-wb) shows that the association between internet adoption and life satisfaction was credibly positive, based on sign tests, for `r tbl_props$Positive_Sign[7]` countries, negative for `r tbl_props$Negative_Sign[7]` countries, and indecisive for `r tbl_props$Indecisive_Sign[7]` countries.
+Evaluated against a region of practical equivalence (to zero) of [-0.1, 0.1], `r tbl_props$Null_ROPE[7]` countries showed credibly null associations between internet adoption and life satisfaction, whereas the result was indecisive for `r tbl_props$Indecisive_ROPE[7]` countries, positive for `r tbl_props$Positive_ROPE[7]` and negative for `r tbl_props$Negative_ROPE[7]` countries.
+The country-specific associations between negative and positive experiences and per capita internet adoption were broadly similar to those with life satisfaction: When evaluated against a ROPE on the standardized scale, the majority of associations were either indecisive or credibly null.
+Moreover, the results regarding country-specific associations between mobile broadband adoption and well-being were broadly similar: The majority of associations were either indecisive or credibly null.
+
+This heterogeneity and lack of consistent associations across countries should qualify any inferences concerning associations for the average country, and is further evidence against the idea that the adoption of internet or mobile broadband has had uniform global negative effects on well-being.
+
+### Demographics
+
+```{r fig-demographics-wb}
+#| cache: true
+#| include: true
+#| fig.height: 6.4
+#| fig.width: 8
+#| fig.env: "figure*"
+#| fig.cap: "Age- and sex-specific (green: female, red: male) changes in three well-being outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row).
+Bottom x-axes indicate raw associations; top x-axes are scaled associations."
+
+figure_demo <- function(x = "Year", y = "Life_satisfaction") {
+
+  # Get coefficients for males and females for average and each age
+  d <- coefficients %>% 
+    filter(
+      outcome == y, 
+      predictor == x, 
+      level %in% c("average", "age"), 
+      sex %in% c("male", "female")
+    ) %>%
+    mutate(group = if_else(group == "Average", str_to_title(sex), group)) %>% 
+    left_join(z) %>% 
+    mutate(
+      group = fct_rev(fct_relevel(group, "Female", "Male"))
+    )
+
+  p <- d %>% 
+    ggplot(aes(mean, group, col = sex, shape = pd > 0.975)) +
+    geom_vline(xintercept = 0, linewidth = .2, linetype = "dashed", col = "grey70") +
+    scale_color_brewer(palette = "Set2") +
+    scale_shape_manual(values = c(21, 19), breaks = c(FALSE, TRUE)) +
+    geom_pointinterval(
+      aes(xmin = q2.5, xmax = q97.5),
+      fill = "white",
+      interval_size_range = c(.4, .4),
+      fatten_point = 3,
+      stroke = .75,
+      position = position_dodgejust()
+    ) +
+    guides(shape = "none") +
+    scale_x_continuous(
+      "Raw association",
+      breaks = extended_breaks(6), 
+      expand = expansion(c(0.05)),
+      sec.axis = sec_axis(
+        trans = ~ . / unique(d$val_sd) * unique(d$xdev), 
+        breaks = extended_breaks(),
+        name = "Scaled association"
+      )
     ) +
@@
       axis.title.y = element_blank(),
-      legend.position = "none",
-      panel.grid.major.x = element_line(
+      panel.grid.major = element_line(
         color = "black", linetype = "dotted", size = .1
-      )
+      ),
+      legend.position = "none"
+    )
+
+  if (y %in% oo[c(3, 6)]) {
+    p <- p +
+      facet_grid(
+        rows = vars(predictor),
+        labeller = as_labeller(~str_replace(., "_", " "))
+      ) +
+      theme(
+        # axis.title.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()
         )
@@
 
-p_demo_wb <- figure_demographics(wb_demo)
-```
-
-Our model also measured the extent to which internet technology adoption predicted well-being between countries.
-These between-country associations indicated, with high confidence, that countries with greater average levels of internet and mobile broadband adoption tended to report greater average levels of life satisfaction and positive experiences, and lower average levels of negative experiences (Figure \@ref(fig:fig-gwp-data)B, Between-country associations).
-However, this pattern is likely to reflect multiple other causes, such as socioeconomic factors and levels of inequality, impinging on both well-being and internet technology adoption.
-For example while wealthier nations are likely to have greater internet coverage, they also tend to have greater healthcare coverage, which in turn is likely to affect levels of well-being.
-
-These trends and associations are meaningful summaries of the average country among the `r length(unique(gwp$country))` examined, but do not represent specific countries which might have unique patterns of associations.
-Figure \@ref(fig:fig-gwp-parameters)A describes the country-level trends over time and associations linking per capita internet users and mobile broadband subscriptions to each of the three outcomes.
-There appeared to be no universal temporal trends that apply to all countries, whose estimates varied from significant decreases to substantial increases in well-being.
-Moreover, the associations between internet technology adoption and well-being varied significantly across countries, with some reporting substantial positive associations, and others large negative associations.
-
-```{r fig-gwp-parameters}
-#| cache: false
-#| include: true
-#| fig.height: !expr ifelse(knitr::is_latex_output(), 8.5, 6.8)
-#| fig.env: "figure*"
-#| fig.cap: "\\textbf{A.} Country-specific yearly changes in three well-being outcomes (Time), and their associations with per capita internet users (Internet) and mobile broadband subscriptions (Mobile).
-Points and lines indicate individual countries' posterior means and 95\\% CIs.
-Countries are sorted from the most negative to most positive estimate.
-Filled points indicate that the parameter's 95\\% credibility interval excludes zero (in both panels).
-We include a table of all countries' estimates in the online materials.
-\\textbf{B.} Age- and sex-specific (green: female, red: male) changes in three well-being outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row)."
-((p_country_wb /
-  p_demo_wb + theme(axis.text.y = element_text(size = rel(0.6)))) &
-  theme(text = element_text(size = 8))) +
-  plot_layout(heights = c(5.5, 4.5)) +
-  plot_annotation(tag_levels = "A")
-```
-
-```{r tab-sds}
-#| include: true
-#| eval: false
-tab_wb %>% 
-  filter(str_starts(factor, "sd_")) %>% 
-  separate(factor, c("factor", "term"), sep = "__") %>% 
-  filter(factor %in% c("sd_age", "sd_country")) %>% 
-  filter(
-    model == "1" & term == "year" | 
-      model != "1" & str_ends(term, "_cw")
-  ) %>% 
-  mutate(
-    # years, percentages
-    across(c(Mean:CI_high), ~if_else(model=="1", ., ./100)),
-    across(c(Mean:CI_high), ~number(., .001)),
-    res = as.character(str_glue("{Mean} [{CI_low}, {CI_high}]")),
-    Outcome = str_replace(outcome, "_", " "),
-    Predictor = factor(model, labels = c("Time", "Internet", "Mobile")),
-    variable = case_when(
-      factor == "sd_age" ~ "SD (age)",
-      factor == "sd_country" ~ "SD (country)"
-    )
-  ) %>% 
-  select(
-    Predictor, Outcome, variable, res
-  ) %>% 
-  pivot_wider(names_from = variable, values_from = res) %>% 
-  mutate(Outcome = fct_inorder(Outcome)) %>% 
-  select(Predictor, Outcome, `SD (country)`, everything()) %>% 
-  arrange(Predictor, Outcome) %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  ) %>%
-  apa_table(
-    font_size = "scriptsize",
-    placement = "htb",
-    span_text_columns = FALSE,
-    note = "Numbers indicate the standard deviations [95%CI] of the distributions of associations in the population of all countries."
-  )
-```
-
-```{r tab-gwp-props}
-wb_props <- tab_wb %>% 
-  filter(factor == "r_country") %>% 
-  drop_na(Predictor) %>% 
-  mutate(
-    Outcome = str_replace(outcome, "_", " "),
-    # Predictor = as.character(Predictor),
-    # Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  )
-wb_props2 <- wb_props %>% 
-  mutate(
-    x = case_when(
-      cred & sign(Mean)==-1 ~ "Negative",
-      cred & sign(Mean)==1 ~ "Positive",
-      TRUE ~ "Null"
-    )
-  ) %>% 
-  count(Outcome, Predictor, x) %>% 
-  arrange(Predictor, Outcome) %>% 
-  group_by(Outcome, Predictor) %>% 
-  mutate(n = str_glue("{n} ({percent(n/sum(n), 1)})")) %>%  
-  pivot_wider(names_from = x, values_from = n) %>% 
-  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%"))) %>% 
-  select(Predictor, Outcome, Negative, Null, Positive)
-wb_props2 %>%   
-  group_by(Predictor) %>% 
-  mutate(i = 1:n()) %>% 
-  ungroup() %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(i==1, Predictor, '')
-  ) %>% 
-  select(-i) %>% 
-  apa_table(
-    placement = "htb",
-    span_text_columns = FALSE,
-    caption = "Well-being: Country-specific test summary",
-    note = "Numbers indicate counts and (percentages) of countries with different sign test results. Percentages may not add up to 100% because of rounding."
-  )
-```
-
-To summarize these country-specific associations, we calculated proportions of countries with credibly positive and negative associations.
-Above we identified that internet adoption predicted small increases in negative experiences for the average country with `r avg_wb$pd[6]` confidence.
-Table \@ref(tab:tab-gwp-props) shows that this association was credibly positive (negative) for `r str_sub(wb_props2[5,5], 1, 2)` (`r str_sub(wb_props2[5,3], 1, 2)`) countries.
-`r str_sub(wb_props2[4,5], 1, 2)` (`r str_sub(wb_props2[4,3], 1, 2)`) countries had positive (negative) associations between life satisfaction and per capita internet users.
-The associations linking positive experiences to per capita internet users were more often inconclusive.
-We observed similar numbers regarding associations linking well-being to per capita mobile broadband subscriptions: `r str_sub(wb_props2[7,5], 1, 2)` (`r str_sub(wb_props2[7,3], 1, 2)`) countries had a positive (negative) association between mobile broadband adoption and life satisfaction, whereas the numbers were only `r str_sub(wb_props2[8,5], 1, 2)` (`r str_sub(wb_props2[8,3], 1, 2)`) and `r str_sub(wb_props2[9,5], 1, 2)` (`r str_sub(wb_props2[9,3], 1, 1)`) for negative and positive experiences, respectively.
-This heterogeneity and lack of consistent associations across countries should qualify any inferences concerning global associations and is evidence against the idea that the adoption of internet or mobile broadband has had uniform global negative effects on well-being.
+  if (y %in% oo[c(2, 5)]) {
+    p <- p +
+      theme(
+        axis.title.y = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()
+        )
+  }
+
+  if (x == "Year") {
+    p <- p +
+      facet_grid(
+        cols = vars(outcome),
+        labeller = as_labeller(~str_replace(., "_", " "))
+      )
+  }
+  if (y %in% oo[c(3, 6)] & x == "Year") {
+    p <- p +
+      facet_grid(
+        rows = vars(predictor),
+        cols = vars(outcome),
+        labeller = as_labeller(~str_replace(., "_", " "))
+      )
+  }
+
+  p
+}
+
+tmp <- coefficients %>% 
+  distinct(predictor, outcome) %>% 
+  filter(outcome %in% oo[1:3]) %>% 
+  arrange(predictor, outcome) %>% 
+  mutate(p = map2(predictor, outcome, ~figure_demo(.x, .y))) %>% 
+  pull(p)
+wrap_plots(tmp) &
+  ylab("Demographic group")
+```
 
@@
 So we then examined variation across age and sex (for the average country) in the relations linking internet and mobile broadband adoption to psychological well-being.
-Age- and sex-specific estimates, for the average country, are shown in Figure \@ref(fig:fig-gwp-parameters)B.
+Age- and sex-specific estimates, for the average country, are shown in Figure \@ref(fig:fig-demographics-wb).
 
 ```{r}
-tmp <- tab_wb %>% 
+tmp <- coefficients %>% 
+  filter(sex == "female-male", outcome == "Life_satisfaction", level == "average")
+```
+
+We found that, for the average country, life satisfaction had increased more for females (`r tmp$Raw[[1]]`), but, on the standardized scale, this interaction term was very small and practically equivalent to zero with near absolute certainty (`r tmp$Scaled[[1]]`).
+Increases in negative and positive experiences were also greater for females, and while the sign test indicated greater increases in negative experiences for women, both interaction terms were within the ROPE with near absolute certainty.
+We present these results in detail in Table \@ref(tab:tbl-sex1-wb).
+
+```{r tbl-sex1-wb}
+coefficients %>% 
   filter(
-    Effects == "fixed", 
-    str_detect(parameter, ":sex1"), 
-    !(parameter=="year:sex1" & model != 1)
-  ) %>% 
-  mutate(
-    x = str_glue(
-      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
-      ), 
-    .keep = "unused"
-  ) %>% 
-  select(outcome, parameter, x, pd)
-tmp
-```
-
-We found that, for the average country, life satisfaction had increased more for females (`r tmp$x[1]`), and that both per capita internet users and mobile broadband subscriptions predicted slightly greater increases in life satisfaction for females than males (Internet: `r tmp$x[2]`; Mobile: `r tmp$x[3]`).
-Negative experiences had increased the least for youngest age group in our data, but slightly more overall for females than males (`r tmp$x[4]`).
-Similarly, positive experiences had increased most for the youngest and oldest age groups, and somewhat more overall for females (`r tmp$x[7]`).
-Overall, these demography-specific trends and associations indicated no clear patterns specific to a particular demographic group.
-Neither did they support the commonly offered narrative that young individuals, particularly young women, have experienced disproportionately large decrements in well-being in association with the adoption of internet technologies.
-
-## Discussion
-
-We examined the extent to which three indicators of psychological well-being had changed over time and in association with per capita internet users and mobile broadband subscriptions.
-Across 168 countries and 16 years, we found mixed support for changes in well-being over time and in association with internet technology adoption.
-Whereas life satisfaction, on average, had not changed over time or as a function of either per capita internet users, it was positively predicted by per capita mobile broadband subscriptions.
-We found that both negative and positive experiences had increased, but that their associations with internet technology adoption were not credibly different from zero at the 95% confidence level.
-Furthermore, there were large variations among these patterns of results between the countries studied, suggesting no consistent connection between internet technology adoption and country-level well-being.
-Finally, while some sex- and age-based differences emerged, none supported the idea that young individuals, or young women particularly, were the most at-risk group.
-Nevertheless, this analysis was necessarily constrained to a limited range of available outcomes reflecting subjective well-being [e.g.
-@jebbSubjectiveWellBeingWorld2020].
-In Study 2, we extended our investigation to mental health outcomes.
-
-# Study 2: Mental health
-
-In the second study we extended our investigation to focus on mental health, using meta-analytic rates of anxiety, depression, and self-harm from 2000 to 2019 among 202 countries, and their associations with internet technology adoption, in place of self-reported measures of psychological well-being.
-
-## Methods
-
-### Mental health outcomes
-
-We studied meta-analytic prevalence rates (per 100,000 individuals) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0) in 204 countries from 2000 to 2019 as estimated by the Institute for Health Metrics and Evaluation's (IHME) Global Burden of Disease 2019 (GBD) study [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020].
-The GBD collates heterogeneous data from all WHO member states' censuses, household surveys, civil registration and vital statistics, disease registries, health service use statistics, disease notifications, and other sources.
-It then aggregates data from these sources with bayesian meta-regression to produce country-specific yearly prevalence estimates.
-
-The GBD 2019 prevalence rate estimates are based on 19,773 data sources with varying coverage for individual countries; for details of the GBD 2019 methodology, see [@vosGlobalBurden3692020] and especially Appendix 1 therein.
-The prevalence rates are estimated for females and males in 5-year age groups, and are provided as the IHME meta-regression model's predicted rates and 95% credibility intervals; we converted the latter to approximate standard errors for our meta-analytic modelling strategy (see Study 1, Methods).
-
-We emphasize that the GBD estimates are not observed data, and therefore are accurate only to the extent that the GBD's data collection methods and modelling strategies are valid.
-We have compared the GBD estimates to the CDC's estimates of self-harm in the United States [@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources.
-We nevertheless argue that because the GBD provides the most comprehensive dataset of global mental health, studying these estimates is informative, but emphasize this caveat.
-The sample size for our analyses (combinations of country, year, sex, and age) was 130,560.
-
-### Data analysis
-
-We analysed the data in the same manner as in Study 1, but did not include varying parameters over the age by country interaction because the models did not converge due to invariance in the data.
-We also set the observed standard errors in the outcomes to zero for models of self-harm due to convergence problems.
-
-```{r gbd-model-diagnostics}
-if (length(list.files("diagnostics/mh")) == 0) {
-  rhats <- fits_mh %>% 
-    mutate(
-      out = map(
-        fit, 
-        ~describe_posterior(
-          .x, 
-          ci_method = "eti", 
-          test = NULL, 
-          effects = "all",
-          parameters = "^cor_|^sd_|^b_"
-        ) %>% 
-          as_tibble() %>% 
-          select(Parameter, Rhat, ESS)
-      )
-    ) %>% 
-    select(-fit) %>% 
-    unnest(out)
-
-  # Show a table of bad rhats
-  rhats %>%
-    filter(!near(Rhat, 1, tol = .01))
-
-  # Draw a scatterplot of parameters with 9 worst rhats
-  # Create a tabset of this in HTML output
-  rhats_sum <- rhats %>% 
-    group_by(outcome, model) %>% 
-    arrange(outcome, model, desc(abs(Rhat))) %>% 
-    slice(1:9) %>% 
-    summarise(v = list(str_c(Parameter))) %>% 
-    ungroup() %>% 
-    right_join(fits_mh)
-
-  dir.create("diagnostics/mh", FALSE, recursive = TRUE)
-  for (i in 1:nrow(rhats_sum)) {
-    x <- slice(rhats_sum, i)
-    path <- str_glue("diagnostics/mh/{x$outcome}-{x$model}.png")
-    png(path, width = 1200, height = 1200, res = 120)
-    pairs(x$fit[[1]]$fit, pars = x$v[[1]])
-    dev.off()
-
-  }
-}
-```
-
-```{r gbd-model-process}
-# Extract the relevant parameters' summaries from the models
-
-tab_mh <- fits_mh %>% 
-  mutate(
-    out = map(
-      fit,
-      ~describe_posterior(
-        .x, 
-        effects = "all", 
-        centrality = "mean", 
-        ci = 0.95, 
-        ci_method = "ETI", 
-        test = "pd",
-        diagnostic = NULL
-      )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  select(-CI)
-tab_mh <- tab_mh %>% 
-  # Clean parameter names
-  separate(
-    Parameter, 
-    into = c("factor", "country", "parameter"), 
-    sep = "\\[|\\]|,"
-  ) %>%
-  mutate(
-    parameter = if_else(
-      Effects == "fixed",
-      str_remove(factor, "^b_"),
-      parameter
-    ),
-    # Clean predictor name
-    Predictor = case_when(
-      parameter == "year" & model == "1" ~ "Time",
-      parameter == "i_cw" ~ "Internet",
-      parameter == "m_cw" ~ "Mobile"
-    ) %>% factor(., levels = c("Time", "Internet", "Mobile"))
-  ) %>% 
-  mutate(
-    cred = pd > .975
-  )
-
-```
-
-## Results
-
-```{r tab-gbd-estimates}
-avg_mh <- tab_mh %>% 
-  filter(Effects == "fixed") %>%
-  mutate(
-    Predictor = case_when(
-      factor == "b_year" & model == "1" ~ "Time Within country",
-      factor == "b_i_cw" ~ "Internet Within country",
-      factor == "b_m_cw" ~ "Mobile Within country",
-      factor == "b_i_cb" ~ "Internet Between countries",
-      factor == "b_m_cb" ~ "Mobile Between countries"
-    ) %>% fct_inorder
-  ) %>% 
-  drop_na(Predictor) %>% 
-  # Models were estimated with percentages, change to rates per 100k
-  mutate(
-    across(Mean:CI_high, ~ . * 1000)
-  ) %>% 
-  # Create a result string for table
-  mutate(
-    Estimate = str_glue(
-      "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"
-    ),
-    pd = percent2(pd)
+    level == "average",
+    sex == "female-male",
+    outcome %in% oo[1:3]
+  ) %>% 
+  mutate(
+    predictor = if_else(outcome == "Life_satisfaction", predictor, ''),
+    outcome = str_replace(outcome, "_", " ")
   ) %>% 
   select(
-    Predictor, 
+    Predictor = predictor, 
     Outcome = outcome, 
-    Estimate,
-    pd
-  ) %>% 
-  arrange(Predictor, Outcome) %>% 
-  separate(Predictor, c("Predictor", "x"), extra = "merge")
-
-avg_mh %>% 
-  mutate(
-    Estimate = str_glue("{Estimate} ({pd})"),
-  ) %>% 
-  select(-pd) %>% 
-  pivot_wider(names_from = x, values_from = Estimate) %>% 
-  group_by(Predictor) %>% 
-  mutate(i = 1:n()) %>% 
-  ungroup() %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(i==1, Predictor, ''),
-    Outcome = str_replace(Outcome, "_", " ")
-  ) %>% 
-  select(-i) %>% 
-  mutate(Outcome = str_replace(Outcome, "Selfharm", "Self-harm")) %>% 
-  replace_na(list(`Between countries` = '')) %>% 
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  ) %>% 
+  # Justify considering negative estimates
   mutate(
@@
   apa_table(
-    # col.names = c("X", "Y", "Within country", "Between country"),
+    caption = "Well-being: Predictor-sex interactions",
+    span_text_columns = TRUE,
+    placement = "htb",
+    font_size = "small",
+    escape = FALSE,
+    note = "Parameter estimates indicate differences between males and females."
+  )
+```
+
+There were no further differences in associations linking well-being and (mobile) broadband adoption between men and women when evaluated either with sign tests (Table \@ref(tab:tbl-sex1-wb), "Raw estimate") or equivalence tests against [-0.1, 0.1] (Table \@ref(tab:tbl-sex1-wb), "Standardized estimate").
+Overall, these demography-specific trends and associations indicated no clear patterns specific to a particular demographic group.
+Neither did they support the commonly offered narrative that young individuals, particularly young women, have experienced disproportionately large decrements in well-being in association with the adoption of internet technologies.
+
+## Discussion
+
+We examined the extent to which three indicators of psychological well-being had changed over time and in association with per capita internet users and mobile broadband subscriptions.
+Across 168 countries and 16 years, we found little to no support for changes in well-being over time and in association with internet technology adoption.
+Although we found that both negative and positive experiences had increased, based on simple sign tests, these changes were small enough to be credibly practically equivalent to zero when evaluated against a smallest association magnitude of 0.1 on the standardized scale.
+
+Moreover, although mobile broadband adoption did positively predict life satisfaction, when evaluated against ROPE on a standardized scale, this association, like all others, was credibly equivalent to zero.
+
+We then examined variation in trends and associations across countries: Variability in sign and magnitude was large, suggesting no consistent connection between internet technology adoption and country-level well-being.
+Finally, our analysis of differences across demographic groups did not support the idea that young individuals, or young women particularly, were the most at-risk group.
+Nevertheless, this analysis was necessarily constrained to a limited range of available outcomes reflecting subjective well-being [e.g.
+@jebbSubjectiveWellBeingWorld2020].
+In Study 2, we extended our investigation to mental health outcomes.
+
+# Study 2: Mental health
+
+In the second study we extended our investigation to focus on mental health, using meta-analytic rates of anxiety, depression, and self-harm from 2000 to 2019 among 202 countries, and their associations with internet technology adoption, in place of self-reported measures of psychological well-being.
+
+## Methods
+
+### Mental health outcomes
+
+We studied meta-analytic prevalence rates (per 100,000 individuals) of anxiety disorders (ICD10 F40-F44.9, F93-F93.2), depressive disorders (ICD10 F32-F33.9, F34.1), and self-harm (ICD10 X60-X64.9, X66-X84.9, Y87.0) in 204 countries from 2000 to 2019 as estimated by the Institute for Health Metrics and Evaluation's (IHME) Global Burden of Disease 2019 (GBD) study [@jamesGlobalRegionalNational2018; @vosGlobalBurden3692020].
+The GBD collates heterogeneous data from all WHO member states' censuses, household surveys, civil registration and vital statistics, disease registries, health service use statistics, disease notifications, and other sources.
+It then aggregates data from these sources with bayesian meta-regression to produce country-specific yearly prevalence estimates.
+
+The GBD 2019 prevalence rate estimates are based on 19,773 data sources with varying coverage for individual countries; for details of the GBD 2019 methodology, see [@vosGlobalBurden3692020] and especially Appendix 1 therein.
+The prevalence rates are estimated for females and males in 5-year age groups, and are provided as the IHME meta-regression model's predicted rates and 95% credibility intervals; we converted the latter to approximate standard errors for our meta-analytic modelling strategy (see Study 1, Methods).
+
+```{r}
+gbd %>% 
+  count(outcome)
+```
+
+We emphasize that the GBD estimates are not observed data, and therefore are accurate only to the extent that the GBD's data collection methods and modelling strategies are valid.
+We have compared the GBD estimates to the CDC's estimates of self-harm in the United States [@u.s.centersfordiseasecontrolandpreventionWISQARSFatalInjury2022], and found that they are likely to deviate in systematic ways from other authoritative information sources.
+We nevertheless argue that because the GBD provides the most comprehensive dataset of global mental health, studying these estimates is informative, but emphasize this caveat.
+The sample size for our analyses (combinations of country, year, sex, and age) was 130,560.
+
+### Data analysis
+
+Before analyses, we converted the GBD meta-analytic rates (per 100k population) to percentages, for consistency with Study 1.
+Otherwise, we analysed the data in the same manner as in Study 1, but did not include varying parameters over the age by country interaction because the models did not converge due to invariance in the data.
+As above, we report coefficients on the raw scale, with 95%CIs and $p^d$, as well as coefficients scaled by the ratio of the predictor's standard deviation to the standard deviation in the outcome.
+We test the latter for practically large coefficients with a ROPE of [-0.1, 0.1].
+
+## Results
+
+```{r tbl-avg-mh}
+#| include: true
+
+tbl_average_mh <- coefficients %>% 
+  filter(
+    level == "average",
+    sex == "average",
+    outcome %in% oo[4:6]
+  ) %>% 
+  left_join(z) %>% 
+  mutate(
+    Raw = str_glue(
+      "{number(mean, .0001)} [{number(q2.5, .0001)},",
+      "{number(q97.5, .0001)}] ({percent2(pd, .1)})"
+    ),
+    Scaled = str_glue(
+      "{number(zmean, .0001)} [{number(zq2.5, .0001)},",
+      "{number(zq97.5, .0001)}] ({percent2(rope, .1)})"
+    )
+  ) %>% 
+  select(
+    Predictor = predictor, 
+    Outcome = outcome, 
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  )
+tbl_average_mh %>% 
+  mutate(
+    Predictor = if_else(Outcome %in% oo[c(1, 4)], Predictor, ''),
+    Outcome = str_replace(Outcome, "_", " ")
+  ) %>% 
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
+  apa_table(
     caption = "Mental health: Population-level estimates",
     span_text_columns = TRUE,
-    # font_size = "scriptsize",
+    font_size = "small",
     escape = FALSE,
-    note = "Estimates are changes in outcome rates associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
-Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
-  )
-```
-
-Because Study 2 concerned GBD's meta-analytic estimates of mental health rates, we observed much less variation in the variables over time than was the case with the well-being outcomes (Figure \@ref(fig:fig-gbd-data)A).
-Our results showed that rates of anxiety had increased (`r avg_mh$Estimate[1]`), whereas those of depression (`r avg_mh$Estimate[2]`) and self-harm (`r avg_mh$Estimate[3]`) had decreased, and the model certainty in each of these average trends was high (>99.9%).
-
-```{r fig-gbd-data}
+    note = "Raw estimates are contrasts in outcome percentages associated with a one year or percentage increase in the predictor.
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).
+Standardized estimates refer to contrasts in the z-scored outcome as function of the average year-on-year change in the predictor.
+The latter percentages indicate posterior probabilities inside a region of practical equivalence to zero ([-0.1, 0.1])."
+  )
+```
+
+### Trends
+
+Because Study 2 concerned the Global Burden of Disease's meta-analytic estimates of mental health rates, we observed less variation in the variables over time than was the case with the well-being outcomes in Study 1 (Figure \@ref(fig:fig-data-mh)A).
+Our results showed that rates of anxiety had increased (`r tbl_average_mh[["Raw estimate"]][[1]]`; Table \@ref(tab:tbl-avg-mh), "Raw estimate"), whereas those of depression (`r tbl_average_mh[["Raw estimate"]][[2]]`) and self-harm (`r tbl_average_mh[["Raw estimate"]][[3]]`) had decreased, and the model certainty in the directions of these average trends was high (>99.9%).
+However, evaluated against a ROPE of [-0.1, 0.1] on the standardized scale, all three trends were credibly equivalent to zero (Table \@ref(tab:tbl-avg-mh), "Standardized estimate").
+Thus, similarly to well-being trends, although sign tests suggested credibly non-null changes in mental health over time, when evaluated against the [-0.1, 0.1] ROPE on the standardized scale, there was evidence in support of smaller than meaningfully large associations.
+
+```{r fig-data-mh}
 #| include: true
-#| fig.height: !expr ifelse(knitr::is_latex_output(), 6.6, 5)
-#| fig.cap: "\\textbf{A.} Time courses of GBD's meta-analytic country-specific estimates of rates of anxiety, depression, and self-harm.
-Lines indicate countries' yearly means of the respective variable, aggregated across sex and age.
-\\textbf{B.} Posterior probability distributions of population-level associations (green: between countries, red: within countries) between each of three mental health outcomes and time, per capita internet users, and per capita mobile broadband subscriptions.
-Estimates are percentage changes in outcomes associated with a one year or percent increase in the predictor.
-Points and lines indicate posterior means and 95\\%CIs, filled points indicate that zero is not among the 95\\% most credible parameter values."
-
-p1 <- gbd %>% 
-  mutate(outcome = fct_inorder(outcome)) %>%
-  group_by(region, country, year, outcome) %>%
-  summarise(mean = mean(val, na.rm = TRUE)) %>%
-  ungroup() %>% 
-  mutate(year = make_date(year)) %>%
-  mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm")) %>% 
+#| fig.height: 6
+#| fig.width: 8
+#| fig.env: "figure*"
+#| fig.cap: \emph{A}.
+Time courses of three mental health outcomes.
+Thin dark lines indicate countries' yearly means, aggregated across sex and age.
+Blue lines and ribbons indicate model-implied regression lines.
+\emph{B-D}.
+Estimated conditional means of three mental health metrics on within-country centered per-capita internet users.
+Primary x- (bottom) and y-axes (left) display raw predictor and outcome values, secondary axes (top, right) display z-scored outcomes and average year-on-year scaled within-country internet adoption.
+\emph{E-G}.
+Same as B-D but for mobile broadband adoption.
+
+fig_ce_mh <- wrap_plots(
+  wrap_plots(epred$p[c(11, 14, 17)]),
+  wrap_plots(epred$p[c(12, 15, 18)]),
+  ncol = 1
+) & theme(
+  panel.grid.major = element_line(linewidth = .1, color = "grey50")
+)
+
+p1 <- p1_data %>% 
+  filter(outcome %in% oo[4:6]) %>% 
   ggplot(aes(year, mean)) +
   scale_y_continuous(
-    "Rate per 100k individuals",
-    # From percentages in model to rates per 100k
-    labels = ~ number(. * 1000, big.mark = ","),
-    breaks = pretty_breaks(5),
-    expand = expansion(.05)
-  ) +
-  scale_x_date(
+    "Value (%)",
+    # Display percentages
+    breaks = pretty_breaks(),
+    expand = expansion(.01)
+  ) +
+  scale_x_continuous(
     "Year",
-    breaks = make_date(c(2000, 2005, 2010, 2015, 2020)),
-    date_labels = "'%y",
+    breaks = c(2000, 2005, 2010, 2015, 2020),
+    labels = c("'00", "'05", "'10", "'15", "'20"),
     expand = expansion(.02)
+  ) +
+  # coord_cartesian(ylim = c(0, 100)) +
+  geom_lineribbon(
+    data = p1_data_model %>% filter(outcome %in% oo[4:6]),
+    aes(y = estimate__, ymin = lower__, ymax = upper__, x = year + 2010),
+    col = "dodgerblue3",
+    fill = alpha("dodgerblue1", .25),
+    linewidth = 0.6
   ) +
@@
     ),
-    size = .05, col = "dodgerblue3"
-  ) +
-  facet_grid(
-    outcome ~ region,
-    scales = "free_y",
+    linewidth = .025, alpha = .2
+  ) +
+  facet_wrap(
+    "outcome",
+    scales = "free",
+    nrow = 1,
     labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
@@
   )
-
-x <- fits_mh %>% 
-  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
-  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
-  mutate(
-    Predictor = case_when(
-      parameter == "b_year" & model == "1" ~ "Time Within country",
-      parameter == "b_i_cw" ~ "Internet Within country",
-      parameter == "b_m_cw" ~ "Mobile Within country",
-      parameter == "b_i_cb" ~ "Internet Between countries",
-      parameter == "b_m_cb" ~ "Mobile Between countries"
-    )
-  ) %>% 
-  drop_na(Predictor, value) %>% 
-  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
-  mutate(
-    Predictor = factor(
-      Predictor, 
-      levels = c("Time", "Internet", "Mobile")
-    )
-  )
-p2 <- x %>%   
-  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
-  scale_color_brewer(
-    "Association", palette = "Set2", aesthetics = c("fill", "color")
-  ) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_x_continuous(
-    "Estimated linear association",
-    breaks = extended_breaks(),
-    # From percentages in model to rates per 100k
-    labels = ~ . * 1000,
-  ) +
-  stat_halfeye(
-    aes(shape = after_stat(sign(xmax) == sign(xmin))),
-    position = position_dodge(.15), 
-    normalize = "xy", 
-    height = .8,
-    point_interval = "mean_qi",
-    fatten_point = 3,
-    point_fill = "white",
-    size = .25,
-    slab_alpha = .75,
-    adjust = 1.5,
-    .width = .95
-    ) +
-  facet_wrap(
-    "outcome", 
-    labeller = labeller(
-      .cols = as_labeller(~str_replace(., "_", " "))
-    ),
-    scales = "free_x"
-  ) +
-  theme(
-    legend.position = "none",
-    axis.title.y = element_blank(),
-    panel.grid.major.x = element_line(
-      color = "black", linetype = "dotted", size = .1
-    )
-  )
-
-(p1 / p2) + 
-  plot_layout(heights = c(7, 3)) +
+(p1 / fig_ce_mh) +
+  plot_layout(heights = c(22, 78)) +
   plot_annotation(tag_levels = "A")
@@
 
-Then, to answer our primary research question, we examined the within-country predictive associations between internet technology adoption and mental health.
-We observed no credible (at the 95% level) associations between internet adoption and either anxiety, depression, or self-harm (Figure \@ref(fig:fig-gbd-data)B).
-Similarly, per capita mobile broadband subscriptions were not credible predictors of mental health for the average country, although the model indicated `r avg_mh$pd[10]` certainty of a negative association between mobile broadband adoption and rates of anxiety.
-
-```{r}
-tmpr <- fits_mh %>% 
-  filter(model > 1) %>% 
-  mutate(
-    sdx = map_dbl(fit, ~sd(.x$data[,4])),
-    sdy = map_dbl(fit, ~sd(.x$data[,1]))
-  ) %>% 
-  mutate(
-    x = map(
-      fit, 
-      ~as_draws_df(.x, variable = "b_[i|m]_cw$", regex = TRUE) %>% 
-        rename(b = 1) %>% 
-        mutate(r = b * (sd(.x$data[,4]) / sd(.x$data[,1])), .keep = "unused") %>% 
-        describe_posterior(
-          centrality = "mean", 
-          ci = 0.95, 
-          ci_method = "ETI", 
-          test = "pd",
-          diagnostic = NULL
-        ) %>% 
-        as_tibble())
-  ) %>% 
-  mutate(model = factor(model, labels = c("Internet", "Mobile"))) %>% 
-  unnest(x) %>% 
-  mutate(
-    result = str_glue(
-      "{number(Mean, .001)} [{number(CI_low, .001)}, {number(CI_high, .001)}]"
-    ),
-    .keep = "unused"
-  ) %>% 
-  select(outcome, model, result)
-tmpr
-```
-
-Although numerically greater than the unstandardized coefficients reported above, the standardized associations were small according to common guidelines: (anxiety & internet = `r tmpr$result[1]`, anxiety & mobile = `r tmpr$result[2]`, depression & internet = `r tmpr$result[3]`, depression & mobile = `r tmpr$result[4]`, depression & internet = `r tmpr$result[5]`, depression & mobile = `r tmpr$result[6]`).
+### Average associations
+
+Then, to answer our primary research question, we examined the within-country associations between internet technology adoption and mental health.
+We observed no credible (at the 95% level) associations between internet adoption and either anxiety, depression, or self-harm (Figure \@ref(fig:fig-data-mh)B), evaluated either against a point null on the raw scale (anxiety: `r tbl_average_mh[["Raw estimate"]][[4]]`; depression: `r tbl_average_mh[["Raw estimate"]][[5]]`; self-harm: `r tbl_average_mh[["Raw estimate"]][[6]]`), or against a ROPE of [-0.1, 0.1] on the standardized scale (Table \@ref(tab:tbl-avg-mh), "Standardized estimate")).
+Similarly, per capita mobile broadband subscriptions were not credible predictors of either anxiety, depression, or self-harm (Table \@ref(tab:tbl-avg-mh)).
+These results suggested that, all else being equal, country-level (mobile) internet adoption does not predict mental health.
 
 We also examined the between-country associations linking internet technology adoption with mental health.
-Countries with greater levels of per capita internet users, on average, tended to be those with lower levels of depression, and higher levels of self-harm (Figure \@ref(fig:fig-gbd-data)B, Between country estimates).
+Countries with greater levels of per capita internet users, on average, tended to be those with lower levels of depression, and higher levels of self-harm (Figure \@ref(fig:fig-data-mh)B, Between country estimates).
 Similarly, per capita mobile broadband subscriptions predicted lower rates of both anxiety and depression, but higher rates of self-harm.
+However, all of these between-country associations were within the region of practical equivalence to zero with very high confidence (>99.9%).
+
+### Countries
+
+```{r tbl-country-prop-mh}
+tbl_props_mh <- tbl_props %>% 
+  filter(Outcome %in% oo[4:6]) %>% 
+  mutate(
+    Outcome = fct_inorder(str_replace(Outcome, "_", " "))
+  )
+tbl_props_mh %>% 
+  as.data.frame() %>% 
+  setNames(str_remove(names(.), "_ROPE") %>% str_remove("_Sign")) %>% 
+  apa_table(
+    placement = "htb",
+    span_text_columns = TRUE,
+    col_spanners = list(` ` = c(1, 2), `Sign test` = c(3, 5), `ROPE` = c(6, 9)),
+    font_size = "small",
+    caption = "Mental health: Country-specific test summary",
+    note = "Numbers indicate counts and (percentages) of countries with different decisions either based on a sign test or a ROPE of [-0.1, 0.1] on the standardized scale."
+  )
+```
 
 We then examined the heterogeneity in the associations between countries.
-Although there were considerable differences in changes in anxiety, depression, and self-harm between countries, the associations varied less (Figure \@ref(fig:fig-gbd-parameters)A).
-We found that internet adoption was positively (negatively) associated with anxiety for three (seven) countries, with depression for one (zero) countries, and self-harm for seven (ten) countries (Table \@ref(tab:tab-gbd-props)).
-We include all countries' estimates in the online materials.
-
-```{r fig-gbd-country}
-#| cache: false
-p_country_mh <- figure_country(
-  tab_mh %>% 
-    mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm"))
-) +
-  scale_x_continuous(
-    "Estimated linear association",
-    # From percentages in model to rates per 100k
-    labels = ~ . * 1000,
-    breaks = extended_breaks(6), 
-    expand = expansion(c(0.01))
-  )
-```
-
-```{r gbd-demographics}
-mh_demo <- fits_mh %>% 
-  mutate(
-    x = factor(model, levels = 1:3, labels = c("year", "i_cw", "m_cw")),
-  ) %>% 
-  mutate(
-    out = map2(
-      fit, x, 
-      ~bind_rows(
-        world = hypothesis(
-          .x, 
-          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0")
-        )$hypothesis,
-        age = hypothesis(
-          .x, 
-          str_glue("{.y} + {.y}:sex1 * {c(-1, 1)} = 0"),
-          scope = "coef", group = "age"
-        )$hypothesis
-      )
-    )
-  ) %>% 
-  select(-fit) %>% 
-  unnest(out) %>% 
-  mutate(Sex = if_else(str_detect(Hypothesis, "-1"), "Male", "Female")) %>% 
-  mutate(Group = if_else(is.na(Group), Sex, Group)) %>% 
-  mutate(
-    predictor = factor(
-      model, 
-      levels = 1:3, 
-      labels = c("Time", "Internet", "Mobile")
-    )
-  ) %>% 
-  mutate(cred = sign(CI.Lower) == sign(CI.Upper)) %>% 
-  mutate(
-    Group = factor(Group, levels = c("Female", "Male", levels(dat$age)))
-  ) %>% 
-  mutate(outcome = str_replace(outcome, "Selfharm", "Self-harm"))
-```
-
-```{r fig-gbd-parameters}
+Although there were considerable differences in changes in anxiety, depression, and self-harm between countries, the associations varied less (Figure \@ref(fig:fig-country-mh)).
+To summarize these country-level trends and associations, we calculated proportions of countries with negative, positive, null, and indecisive results based on both sign tests and ROPE tests, as in Study 1 (Table \@ref(tab:tbl-country-prop-mh)).
+First, we find that the vast majority of country-specific trends and associations were indecisive when evaluated against a point null hypothesis (Table \@ref(tab:tbl-country-prop-mh)).
+Moreover, when evaluated against a ROPE of [-0.1, 0.1] all country-level coefficients were credibly equivalent to zero.
+
+Thus, analyses of country-specific associations provided stronger evidence that (mobile) internet penetration does not meaningfully predict fluctuations in countries' mental health.
+
+```{r tbl-cb-mh}
+coefficients %>% 
+  filter(
+    outcome %in% oo[4:6],
+    level == "cb",
+    predictor != "Year"
+  ) %>% 
+  mutate(
+    predictor = if_else(outcome %in% oo[c(1, 4)], predictor, ''),
+    outcome = str_replace(outcome, "_", " ")
+  ) %>% 
+  select(
+    Predictor = predictor, 
+    Outcome = outcome, 
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  ) %>% 
+  # Justify considering negative estimates
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
+  apa_table(
+    caption = "Mental health: Between-country associations",
+    span_text_columns = TRUE,
+    font_size = "small",
+    escape = FALSE,
+    placement = "htb",
+    note = "Raw estimates are contrasts in outcome percentages associated with a one percentage increase in the predictor.
+Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction).
+Standardized estimates refer to contrasts in the z-scored outcome as function of the average year-on-year change in the predictor.
+The latter percentages indicate posterior probabilities inside a region of practical equivalence to zero ([-0.1, 0.1])."
+  )
+```
+
+```{r fig-country-mh}
+#| cache: true
 #| include: true
-#| #| cache: false
-#| fig.height: !expr ifelse(knitr::is_latex_output(), 8.5, 6.8)
+#| fig.height: 6.4
+#| fig.width: 8
 #| fig.env: "figure*"
-#| fig.cap: "\\textbf{A.} Country-specific yearly changes in three mental health outcomes (Time), and their associations with per capita internet users (Internet) and mobile broadband subscriptions (Mobile).
+#| fig.cap: "Country-specific yearly changes in three mental health outcomes (top row), and their associations with per capita internet users (second row) and mobile broadband subscriptions (third row).
 Points and lines indicate individual countries' posterior means and 95\\% CIs.
@@
 Filled points indicate that the parameter's 95\\% credibility interval excludes zero (in both panels).
-We include a table of all countries' estimates in the online materials.
-\\textbf{B.} Age- and sex-specific (green: female, red: male) changes in three mental health outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row)."
-p_demo_mh <- figure_demographics(mh_demo) +
-  # Adjust x-axes
-  scale_x_continuous(
-    "Estimated linear association",
-    breaks = extended_breaks(5),
-    expand = expansion(.1),
-    labels = ~. * 1000
-  )
-
-((p_country_mh /
-  p_demo_mh + theme(axis.text.y = element_text(size = rel(0.6)))) &
-  theme(text = element_text(size = 8))) +
-  plot_layout(heights = c(5.5, 4.5)) +
-  plot_annotation(tag_levels = "A")
-```
-
-```{r tab-gbd-props}
-mh_props <- tab_mh %>% 
-  filter(factor == "r_country") %>% 
-  drop_na(Predictor) %>% 
-  mutate(
-    Outcome = str_replace(outcome, "_", " "),
-    # Predictor = as.character(Predictor),
-    # Predictor = if_else(Outcome == "Life satisfaction", Predictor, "")
-  ) %>% 
-  mutate(outcome = str_replace(Outcome, "Selfharm", "Self-harm"))
-mh_props2 <- mh_props %>% 
-  mutate(
-    x = case_when(
-      cred & sign(Mean)==-1 ~ "Negative",
-      cred & sign(Mean)==1 ~ "Positive",
-      TRUE ~ "Null"
-    )
-  ) %>% 
-  count(Outcome, Predictor, x) %>% 
-  arrange(Predictor, Outcome) %>% 
-  group_by(Outcome, Predictor) %>% 
-  mutate(n = str_glue("{n} ({percent(n/sum(n), 1)})")) %>%  
-  pivot_wider(names_from = x, values_from = n) %>% 
-  mutate(across(c(Negative, Null, Positive), ~replace_na(., "0%"))) %>% 
-  select(Predictor, Outcome, Negative, Null, Positive)
-mh_props2 %>%   
-  group_by(Predictor) %>% 
-  mutate(i = 1:n()) %>% 
-  ungroup() %>% 
-  mutate(
-    Predictor = as.character(Predictor),
-    Predictor = if_else(i==1, Predictor, '')
-  ) %>% 
-  select(-i) %>% 
+Raw associations (bottom x-axes) indicate changes in the outcome percentage as function of percentage (or one year) change in the predictor.
+Scaled associations (top x-axes) indicate changes in standardized outcome as function of the average year-on-year change in the predictor.
+"
+
+tmp <- distinct(coefficients, outcome, predictor) %>% 
+  distinct(outcome, predictor) %>% 
+  filter(outcome %in% oo[4:6]) %>% 
+  arrange(predictor, outcome) %>% 
+  mutate(p = map2(outcome, predictor, ~figure_country(.x, .y))) %>% 
+  pull(p)
+wrap_plots(tmp)
+```
+
+### Demographics
+
+```{r fig-demographics-mh}
+#| cache: true
+#| include: true
+#| fig.height: 6.6
+#| fig.width: 8
+#| fig.env: "figure*"
+#| fig.cap: "Age- and sex-specific (green: female, red: male) changes in three mental health outcomes (top row), and their associations with per capita internet users (middle row) and mobile broadband subscriptions (bottom row).
+Bottom x-axes indicate raw associations; top x-axes are scaled associations."
+
+tmp <- coefficients %>% 
+  distinct(predictor, outcome) %>% 
+  filter(outcome %in% oo[4:6]) %>% 
+  arrange(predictor, outcome) %>% 
+  mutate(p = map2(predictor, outcome, ~figure_demo(.x, .y))) %>% 
+  pull(p)
+wrap_plots(tmp) &
+  ylab("Demographic group")
+```
+
+We then turned to our third research question, and studied how trends in mental health, or its associations with internet technology adoption varied across demographic groups.
+Changes in rates of anxiety showed a complex pattern, whereby older males' rates of anxiety increased more than younger males', except the very youngest age group (Figure \@ref(fig:fig-demographics-mh)).
+For females, on the other hand, rates of anxiety increased least for the oldest and youngest groups.
+Overall, the difference in changes in anxiety between males and females was credibly null (Table \@ref(tab:tbl-sex1-mh)).
+Depression had decreased more for females than males (Table \@ref(tab:tbl-sex1-mh)), and for the middle age groups vs.
+the youngest and oldest groups.
+There were no average sex differences in rates of decline of self-harm (Table \@ref(tab:tbl-sex1-mh)), but the declines were greater for older than younger age groups (Figure \@ref(fig:fig-demographics-mh)).
+
+Overall, the demography-based differences in the mental health-internet adoption associations were smaller than within the mental health trends (Figure \@ref(fig:fig-demographics-mh)).
+There were no sex differences in associations linking either per capita internet users or mobile broadband subscriptions to either mental health outcome that were credibly different from zero.
+Tested against a ROPE of [-0.1, 0.1], all sex differences were credibly null.
+Age-based differences in links with anxiety were small.
+However, depression was negatively and credibly associated with internet adoption for older age groups, but positively and credibly associated with per capita mobile broadband subscriptions for both sexes in the 10 to 14 and 15 to 19 year-old age brackets, based on sign tests.
+The magnitudes of these associations were very small, and supported null associations on the standardized scale.
+Similarly, per capita internet users predicted self-harm negatively for older age groups in the 65 to 89 year-old brackets, but positively in the 10 to 34 year-old brackets.
+These results indicated some support for the idea that younger individuals' mental health may be more negatively associated with the adoption of internet technologies, although this finding was not consistent across the two different predictors or three different mental health outcomes, and in fact null when considered in the context of a ROPE of [-0.1, 0.1] on the standardized scale.
+
+```{r tbl-sex1-mh}
+coefficients %>% 
+  filter(
+    level == "average",
+    sex == "female-male",
+    outcome %in% oo[4:6]
+  ) %>% 
+  mutate(
+    predictor = if_else(outcome %in% oo[c(1, 4)], predictor, ''),
+    outcome = str_replace(outcome, "_", " ")
+  ) %>% 
+  select(
+    Predictor = predictor, 
+    Outcome = outcome, 
+    `Raw estimate` = Raw, 
+    `Standardized estimate` = Scaled
+  ) %>% 
+  # Justify considering negative estimates
+  mutate(
+    across(
+      3:4, 
+      ~if_else(
+        str_starts(., "-"), 
+        ., 
+        paste0("\\phantom{-}", .)
+      )
+    )
+  ) %>% 
   apa_table(
+    caption = "Mental health: Predictor-sex interactions",
+    span_text_columns = TRUE,
     placement = "htb",
-    span_text_columns = FALSE,
-    caption = "Mental health: Country-specific test summary",
-    note = "Numbers indicate counts and (percentages) of countries with different sign test results. Percentages may not add up to 100% because of rounding."
-  )
-```
-
-```{r}
-tmp <- tab_mh %>% 
-  filter(
-    Effects == "fixed", 
-    str_detect(parameter, ":sex1"), 
-    !(parameter=="year:sex1" & model != 1)
-  ) %>% 
-  mutate(
-    x = str_glue("{percent(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}]"), 
-    .keep = "unused"
-  ) %>% 
-  select(outcome, parameter, x, pd)
-tmp
-```
-
-We then turned to our third research question, and studied how the associations linking internet technology adoption and mental health varied across demographic groups.
-Changes in the rates of anxiety showed a complex pattern, whereby older males rates of anxiety increased more than younger males, except the very youngest age group (Figure \@ref(fig:fig-gbd-parameters)B).
-For females, on the other hand, rates of anxiety increased least for the oldest and youngest groups.
-Overall, the difference in changes in anxiety between males and females was not credibly different from zero.
-Depression had decreased more for females than males (`r tmp$x[4]`), and for the middle age groups vs.
-the youngest and oldest groups.
-Self-harm had decreased slightly more for females, but the difference was not credibly different from zero, and for older groups vs.
-younger.
-
-Overall, the demography-based differences in the mental health-internet adoption associations were smaller than within the mental health trends (Figure \@ref(fig:fig-gbd-parameters)B).
-There were no sex differences in associations linking either per capita internet users or mobile broadband subscriptions to either mental health outcome that were credibly different from zero.
-Age-based differences in links with anxiety were small.
-However, depression was negatively and credibly associated with internet adoption for older age groups, but positively and credibly associated with per capita mobile broadband subscriptions for both sexes in the 10 to 14 and 15 to 19 year-old age brackets.
-Similarly, per capita internet users predicted self-harm negatively for older age groups in the 65 to 89 year-old brackets, but positively in the 10 to 34 year-old brackets.
-These results indicated some support for the idea that younger individuals' mental health may be more negatively associated with the adoption of internet technologies, although this finding was not consistent across the two different predictors or three different mental health outcomes.
+    font_size = "small",
+    escape = FALSE,
+    note = "Parameter estimates indicate differences between males and females."
+  )
+```
 
@@
 In Study 2, we replicated the analyses regarding well-being in Study 1 using three mental health outcomes from a different dataset.
-We found mixed results regarding changes in the rates of mental health problems, whereby rates of anxiety had increased, but rates of depression and self-harm decreased, for the average country.
-Importantly, demography-based differences emerged: Younger age groups' rates of depression and self-harm were more positively predicted by both per capita internet users and mobile broadband subscriptions.
+We found mixed results regarding changes in the rates of mental health problems, whereby rates of anxiety had increased, but rates of depression and self-harm decreased, for the average country and when tested against a point null hypothesis.
+However, when tested against a ROPE of [-0.1, 0.1] on a standardized scales, all associations were credibly equivalent to that null interval.
+Similar to the average contrasts, country-, age-, and sex-specific coefficients were all credibly equivalent to zero.
+With the important caveat that the Global Burden of Disease mental health rates analysed here are noisy meta-analytic estimates, our results suggested only small if any average changes in mental health globally, and moreover no associations between mental health and internet technology adoption.
 
@@
 The idea that the rapid and global penetration of the internet, and technologies enabled by it, is affecting psychological well-being and mental health is compelling but not adequately tested.
-In two studies, we focused on the degree to which well-being and mental health had changed in the past two decades across most world countries, and found mixed results: Both negative and positive experiences had increased, as had meta-analytic rates of anxiety.
-Depression and self-harm, conversely, had decreased.
+In two studies, we focused on the degree to which well-being and mental health had changed in the past two decades across most world countries.
+Based on sign tests, we found mostly mixed and inconclusive results; based on ROPE tests and a smallest coefficient size of interest of 0.1, we found evidence against meaningfully large changes in well-being and mental health.
 These results align with other results that tend to be mixed or find few changes over time [@borAreChildAdolescent2014; @collishawAnnualResearchReview2015; @cosmaCrossNationalTimeTrends2020; @keyesRecentIncreasesDepressive2019].
@@
 
-We then measured the extent to which countries' per capita internet users and mobile broadband subscriptions predicted those countries' levels of well-being and mental health.
-We found that, overall, there were few if any meaningfully large average associations.
-In all cases but one---mobile broadband adoption predicted life satisfaction positively---these associations were not credibly different from zero (Figure \@ref(fig:fig-gwp-data)B).
-The small observed associations were also qualified by substantive variability across countries (Figure \@ref(fig:fig-gwp-parameters)A) and demographics (Figure \@ref(fig:fig-gwp-parameters)B).
+We then measured the extent to which per capita internet users and mobile broadband subscriptions predicted levels of well-being and mental health (within countries).
+Although confidence for direction of these coefficients exceeded 95% in one case out of twelve, on a standardized scale all 12 associations were practically equivalent to zero with very high confidence.
+The small associations were also qualified by variability across countries and demographics.
 Furthermore, countries where internet technologies were more widely adopted overall were not those with lowest levels of well-being and mental health.
 
-Finally, we found large age-based differences in associations linking internet technology adoption and mental health outcomes.
-Both depression and self-harm were more positively associated with per capita internet users and mobile broadband subscriptions in the younger age brackets---including the youngest studied here at 10 to 14 years---than they were for older age groups.
+We also examined the moderating roles of sex and age: Both depression and self-harm were more positively associated with per capita internet users and mobile broadband subscriptions in the younger age brackets---including the youngest studied here at 10 to 14 years---than they were for older age groups.
+However, evaluated against a smallest association of interest, all sex- and age-based associations provided evidence for null associations.
 Studies on the association between internet technology use and mental health across wide age ranges are scarce.
@@
 Our results also suggest that age- and sex-based differences in associations linking internet technology adoption and well-being are small.
-However, we did find evidence suggesting that internet technology adoption is more negatively associated with young individuals' mental health than older groups' (whose associations were, in some cases, positive).
-Nevertheless, these associations, although sometimes credibly different from zero, appeared small in magnitude.
+However, we did find some evidence suggesting that internet technology adoption is more negatively associated with young individuals' mental health than older groups' (whose associations were, in some cases, positive).
+Nevertheless, these associations, although sometimes credibly different from zero, appeared small in magnitude and were credibly in the null region when evaluated against a SESOI of 0.1 on the standardized scale.
 Because of their apparently small magnitude and the fact that the data are not at the individual level, we highlight that these contrasts do not speak to whether the associations might be clinically relevant.
@@
 
-All the data-analytic code and a synthetic GWP dataset to facilitate the verification, extension, and critique of our procedures are available at <https://doi.org/10.5281/zenodo.7004053>.
+All the data-analytic code and a synthetic GWP dataset to facilitate verification, extension, and critique of our procedures are available at <https://doi.org/10.5281/zenodo.7004053>.
 The ITU data, along with a complete list of years, countries, and sources of data are freely available at <https://www.itu.int/en/ITU-D/Statistics/Pages/stat/default.aspx>.
@@
 
-\begin{center}
-\textbf{Supplementary online material to \emph{Global well-being and mental health in the internet age} (Vuorre \& Przybylski)}
-\end{center}
-
-<!-- Prepend table & figure numbers with S and reset counters -->
+<!-- Prepend table & figure numbers with A and reset counters -->
 \setcounter{page}{1}
@@
 \setcounter{figure}{0}
-\renewcommand{\thetable}{SOM\arabic{table}}
-\renewcommand{\thefigure}{SOM\arabic{figure}}
-
-## Well-being: Country-specific parameters
-
-```{r, tab-gwp-props}
-#| include: !expr knitr::is_latex_output()
-```
-
-```{r}
-#| include: !expr knitr::is_latex_output()
-table_of_countries <- function(data, x) {
-
-  # Display MH as rates per 100k individuals
-  m <- if_else(x == "Mental health", 1000, 1)
-
-  data %>% 
-    filter(factor == "r_country") %>% 
-    drop_na(Predictor) %>% 
-    mutate(
-      across(Mean:CI_high, ~. * m),
-      Estimate = str_glue(
-        "{number(Mean, .01)} [{number(CI_low, .01)}, {number(CI_high, .01)}] ({percent2(pd)})"
-      ),
-      outcome = str_replace(outcome, "_", " ")
-    ) %>% 
-    select(
-      Outcome = outcome,
-      Predictor, 
-      Country = country,
-      Estimate
-    ) %>% 
-    pivot_wider(names_from = Outcome, values_from = Estimate) %>% 
-    mutate(
-      across(
-        2:5, 
-        ~if_else(
-          str_starts(., "-"), 
-          ., 
-          paste0("\\phantom{-}", .)
-        )
-      ),
-      across(2:5, ~ifelse(is.na(.), "", .))
-    ) %>% 
-    arrange(Predictor, Country) %>% 
-    mutate(Country = str_replace_all(Country, "\\.(?!\\.)", " ")) %>% 
-    apa_table(
-      longtable = TRUE, 
-      escape = FALSE,
-      font_size = "scriptsize",
-      caption = str_glue("{x}: Country-specific estimates"),
-      note = "Estimates are changes in the outcome associated with a one unit increase in the predictor (Time: one year; Internet and Mobile: one percent).
-Numbers indicate posterior means, [95\\%CIs], and (posterior probabilities of direction)."
-    )
-}
-table_of_countries(tab_wb, "Well-being" )
-```
-
-## Mental health: Country-specific parameters
-
-```{r, tab-gbd-props}
-#| include: !expr knitr::is_latex_output()
-```
-
-```{r}
-#| include: !expr knitr::is_latex_output()
-table_of_countries(tab_mh, "Mental health" )
-```
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\clearpage
+# Appendix 1
+
+```{r tbl-cb-wb}
+#| include: true
+```
+
+```{r tbl-country-prop-wb}
+#| include: true
+```
+
+```{r tbl-sex1-wb}
+#| include: true
+```
+
+\clearpage
+
+```{r tbl-cb-mh}
+#| include: true
+```
+
+```{r tbl-country-prop-mh}
+#| include: true
+```
+
+```{r tbl-sex1-mh}
+#| include: true
+```

### 2023-07-17 supplement.qmd
Move a bunch of stuff to a separate file

---
title: Global well-being and mental health in the internet age
subtitle: Online analysis supplement
author:
  - name: Matti Vuorre
    orcid: 0000-0001-5052-066X
    email: mjvuorre@uvt.nl
    url: https://vuorre.netlify.app
    affiliation:
      - name: Tilburg University
        url: https://www.tilburguniversity.edu/staff/m-j-vuorre
  - name: Andrew K. Przybylski
    orcid: 0000-0001-5547-2185
    affiliation:
      - name: University of Oxford
format:
  html:
    toc: true
    toc-depth: 2
    toc-title: Contents
    theme: materia
    mainfont: LibertinusSansRegular
    monofont: FiraCodeRegular
    code-fold: true
    # code-link: true # Slow
    code-tools: true
    header-includes: |
      <link rel="stylesheet" media="screen" href="https://fontlibrary.org//face/fira-code" type="text/css"/>
      <link rel="stylesheet" media="screen" href="https://fontlibrary.org//face/libertinus-sans" type="text/css"/> 
bibliography: references.bib
---

This repository contains the code and synthetic datasets required to reproduce all analyses reported in *Global well-being and mental health in the internet age* (Vuorre & Przybylski).

# Preface

## Materials {.unnumbered .unlisted}

- [Preprint](https://doi.org/10.31234/osf.io/9tbjy)  
  - A publicly available version of our manuscript in advance of peer-review and formal publication
- [GitHub repository](https://github.com/digital-wellbeing/global-wbmh)  
  - A version controlled repository containing all the raw data and code in this project
- [Zenodo](https://doi.org/10.5281/zenodo.7004054)
  - An archived permanent copy of the GitHub repository

## Reproducibility {.unnumbered .unlisted}

The analyses were conducted in R; steps to reproduce are

1. Clone the [github repo](https://github.com/digital-wellbeing/global-wbmh)
  - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
    OR
  - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2. Run the analyses and render manuscript
  - Terminal: `make`

The project repo includes the GBD dataset, code to download the ITU dataset, and a synthetic mock version of the GWP dataset to enable reproducing all our computations. **The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason, `make` will fail after having cleaned the data. Then, run `models.R` with settings specific to your environment/cluster. Once that is done you can `make` again and it should work.

If you encounter problems, please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).

# Data cleaning

```{r setup}
#| include: false
knitr::opts_chunk$set(
  cache = TRUE,
  include = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  dpi = 300,
  fig.align = "center"
)
```

```{r packages}
#| cache: false
library(haven)
library(labelled)
library(janitor)
library(readxl)
library(countrycode)
library(tidybayes)
library(ggdist)
library(brms)
library(scales)
library(gt)
library(latex2exp)
library(distributional)
library(patchwork)
library(knitr)
library(posterior)
library(bayestestR)
library(tidyverse)

# Create directories for intermediate files
dir.create("data", FALSE)
dir.create("cache", FALSE)

theme_set(
  theme_linedraw(
    base_size = 12
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt")),
      axis.text = element_text(size = rel(0.7)),
      axis.ticks = element_line(size = rel(0.2))
    )
)
```

```{r functions}
# Function to replace extreme percentages
percent2 <- function(x, accuracy = .1) {
  x <- percent(x, accuracy = accuracy)
  x <- if_else(x == "100.0%", ">99.9%", x)
  x <- if_else(x == "0.0%", "<0.1%", x)
  x
}
```

## Gallup world poll

### Codebook

```{r gallup-codebook}
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/World_Poll_Methodology and Guides_101521/The_Gallup_042722.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) |>
  generate_dictionary() |>
  select(-pos, -col_type, -missing) |>
  lookfor_to_long_format() |> 
  select(-levels)
```

```{r gallup-spss-to-rds}
gwp_path <- "data-raw/Gallup/gwp-processed.rds"
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    "data-raw/Gallup/World_Poll_Methodology and Guides_101521/The_Gallup_042722.sav",
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )
  # Get rid of SPSS attributes
  gwp <- gwp |>
    zap_labels() |>
    zap_label() |>
    zap_widths() |>
    zap_formats()
  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}
```

```{r gallup-rename-recode}
# Rename and recode variables
gwp <- gwp |>
  clean_names() |>
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )
gwp
```

```{r gallup-demographics}
# Categorize ages
gwp <- filter(gwp, between(age, 15, 89))
gwp <- gwp |>
  mutate(
    age = cut(
      age,
      breaks = seq(15, 90, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 85, by = 5), "to", seq(19, 89, by = 5))
    ) |> as.character()
  )

# Some sex values are missing, drop those
gwp <- drop_na(gwp, sex)

# Summarise cells
gwp |> 
  count(year, country, sex, age) |> 
  ggplot(aes(age, n)) +
  scale_y_log10() +
  geom_boxplot()
```

```{r gallup-scale-scoring}
# Scale scores note rescaling to percentages
gwp <- gwp |>
  mutate(
    Life_satisfaction = Life_satisfaction * 10,
    Negative_experiences =
      (rowMeans(select(gwp, wp68:wp74), na.rm = TRUE) - 1) * 100,
    Positive_experiences =
      (rowMeans(select(gwp, wp60:wp67), na.rm = TRUE) - 1) * 100
  ) |>
  select(-c(wp60:wp74))
saveRDS(gwp, "data-raw/gwp-raw.rds")
```

```{r gallup-aggregate}
# Pivot outcomes to long format
gwp <- gwp |>
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  )

# Aggregate outcomes
gwp <- gwp |>
  summarise(
    n = n(),
    sd = sd(val, na.rm = TRUE),
    val = mean(val, na.rm = TRUE),
    .by = c(country, year, sex, age, outcome)
  )
gwp <- gwp |> 
  mutate(
    # Fix N=1 and SD=0 cells
    sd = if_else(n == 1 | sd == 0, median(sd), sd),
    se = sd / sqrt(n),
  )
```

```{r gallup-harmonize}
# Harmonise old names and replace only if harmonised name found
gwp <- gwp |>
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) |>
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) |>
  mutate(country = coalesce(country_harmonised, country)) |>
  select(-country_harmonised)
```

```{r gallup-mock-data}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp |>
    drop_na()
  gwp_syn <- syn(
    gwp_syn,
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  gwp_syn <- tibble(gwp_syn$syn)
  saveRDS(gwp_syn, gwp_mock_path)
}
```

Check if synthetic data is used

```{r gallup-mock-data-check}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

Save data for analysis

```{r gallup-save}
saveRDS(gwp, "data/gwp.rds")
```

## Global Burden of Disease

```{r gbd-process}
# Load GBD data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/",
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) |>
  read_csv()

# First step is to clean names and remove unnecessary variables
gbd <- clean_names(gbd)
# distinct(gbd, measure, metric)
gbd <- select(gbd, -measure, -metric)

# Limit to same upper age as GWP
# gbd <- filter(gbd, !(age %in% c("80 to 84", "85 to 89")))

# Rates to percentages
gbd <- gbd |>
  mutate(across(c(val, upper, lower), ~ .x / 1000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd |>
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd |>
  rename(country = location, outcome = cause)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd |>
  mutate(se = (upper - lower) / (1.96 * 2)) |>
  select(-c(upper, lower))

# Harmonise old names and replace only if harmonised name found
gbd <- gbd |>
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) |>
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) |>
  select(-country_harmonised)
```

Save data for analyses

```{r gbd-save}
saveRDS(gbd, "data/gbd.rds")
```

## ITU

```{r itu-download}
# Download data sets from the ITU website if not yet downloaded
if (!dir.exists("data-raw/ITU")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/December/PercentIndividualsUsingInternet.xlsx",
    "data-raw/ITU/per-capita-internet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2022/December/MobileBroadbandSubscriptions_2007-2021.xlsx",
    "data-raw/ITU/per-capita-mobile.xlsx"
  )
}
```

```{r itu-merge}
# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/per-capita-internet.xlsx",
  col_types = "text"
) |>
  pivot_longer(-c(Indicator, Economy)) |>
  separate(name, into = c("year", "variable")) |>
  pivot_wider(names_from = variable) |>
  mutate(internet = as.numeric(value)) |>
  select(country = Economy, year, internet)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/per-capita-mobile.xlsx",
  sheet = 2,
  col_types = "text"
) |>
  pivot_longer(-c(Indicator, Economy)) |>
  separate(name, into = c("year", "variable")) |>
  pivot_wider(names_from = variable) |>
  mutate(mobile = as.numeric(value)) |>
  select(country = Economy, year, mobile)

# Merge to one table in wide format (oldest on left to include all years)
itu <- left_join(itu_percent, itu_mobile)
rm(itu_percent, itu_mobile)
```

```{r itu-clean}
# years to numbers
itu <- itu |>
  mutate(year = as.numeric(year))

# Harmonise old names and replace only if harmonised name found
itu <- itu |>
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) |>
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) |>
  select(-country_harmonised)

# Drop countries that don't exist in outcomes
itu <- itu |>
  filter(
    country %in% unique(gbd$country) | country %in% unique(gwp$country)
  )

# Drop countries that don't have any actual internet data
itu_zeros <- itu |>
  summarise(s = sum(internet, na.rm = TRUE), .by = country) |>
  filter(s == 0)

itu <- itu |>
  filter(!(country %in% itu_zeros$country))
rm(itu_zeros)
```

Save data for analyses

```{r itu-save}
saveRDS(itu, "data/itu.rds")
```

## Merge

```{r merge}
# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center year
dat <- dat |>
  mutate(year = (year - 2010))

# Ensure that categorical variables are factors
dat <- dat |>
  mutate(across(c(sex, age, country, outcome), factor))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat |>
  mutate(outcome = factor(outcome, levels = oo)) |>
  arrange(outcome, country, year)

# Save data for models
saveRDS(dat, "data/data-all.rds")
```

```{r data-describe}
library(scales)
gwp |> 
  group_by(outcome) |> 
  summarise(n=sum(n)) |> 
  summarise(N=comma(median(n))) |> 
  pull(N)

bind_rows(
  "GWP" = gwp,
  "GBD" = gbd,
  .id = "Dataset"
) |> 
  mutate(Dataset = fct_inorder(Dataset)) |> 
  count(Dataset, outcome) |> 
  bind_rows(
    itu |> 
      select(internet, mobile) |> 
      pivot_longer(everything(), names_to = "outcome") |> 
      drop_na(value) |> 
      count(outcome) |> 
      mutate(Dataset = "ITU")
  )

# Individuals using the internet per 100 inhabitants | World
if (!file.exists(
  "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")) {
  download.file("https://www.itu.int/en/ITU-D/Statistics/Documents/facts/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", "data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx")
}
read_excel("data-raw/ITU/ITU_regional_global_Key_ICT_indicator_aggregates_rev1_Jan_2022.xlsx", range = "T85:AI86")
```

## Scaling factors

```{r scaling-factors}
# Table for scaling coefficients
z <- dat |> 
  summarise(
    val_sd = sd(val, na.rm = TRUE),
    val_mean = mean(val, na.rm = TRUE),
    .by = outcome
  ) |> 
  bind_cols(
    itu |> 
      mutate(year = year - 2010) %>% 
      summarise(
        Year = 1,
        Internet = coef(lm(internet ~ year, data = .))[2],
        Mobile = coef(lm(mobile ~ year, data = .))[2]
      )
  )
z <- z |> 
  pivot_longer(c(Year, Internet, Mobile), names_to = "predictor", values_to = "xdev") |> 
  mutate(
    predictor = factor(
      predictor, 
      levels = c("Year", "Internet", "Mobile"), 
      labels = c("Year", "Internet", "Mobile")
    )
  )

z <- z |> 
  mutate(zfactor = xdev/val_sd)
write_rds(z, "data/scaling-factors.rds")
```

# Models

## Tests

```{r}
options(mc.cores = 4, brms.backend = "cmdstanr")
z <- read_rds("data/scaling-factors.rds")
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))
```

### Modelling aggregate data

Our main analyses model aggregated country-year-demographic level data. Here we verify that we get the correct brms syntax for such a model.

```{r}
dat <- read_rds("data-raw/gwp-raw.rds") |> 
  filter(
    country == "United States", 
    sex == "Female", 
    age == "30 to 34"
  ) |> 
  mutate(year = year - min(year)) |> 
  rename(val = Life_satisfaction)
dat_sum <- dat |> 
  summarise(
    n = sum(!is.na(val)),
    sd = sd(val, na.rm = TRUE),
    se = sd / sqrt(n),
    val = mean(val, na.rm = TRUE),
    .by = c(year, country)
  )
```

```{r brms-syntax}
# Raw data
f1 <- brm(
  val ~ year,
  data = dat,
  iter = 10000,
  control = list(adapt_delta = .99),
  file = "cache/test-brm-1"
)

f2 <- brm(
  val | se(se, sigma = FALSE) ~ year,
  data = dat_sum,
  iter = 10000,
  control = list(adapt_delta = .99),
  file = "cache/test-brm-2"
)

f3 <- brm(
  val | se(se, sigma = TRUE) ~ year,
  data = dat_sum,
  iter = 10000,
  control = list(adapt_delta = .99),
  file = "cache/test-brm-3"
)
```

Compare estimates

```{r brms-syntax-figure}
list(f1, f2, f3) |> 
  map(
    ~as_draws_df(., variable = c("b_", "sigma"), regex = TRUE) |> 
      pivot_longer(
        c("b_Intercept", "b_year", "sigma"), 
        names_to = "variable", values_to = "value"
      )
  ) |> 
  bind_rows(.id = "Model") |> 
  ggplot(aes(value, variable, col = Model, fill = Model)) +
  scale_color_brewer(
    "Model",
    palette = "Set1",
    labels = map(list(f1, f2, f3), ~.$formula[1]),
    aesthetics = c("color", "fill")
  ) +
  stat_slabinterval(
    position = position_dodgejust(),
    slab_alpha = .33,
    normalize = "panels"
  ) +
  guides(
    color = guide_legend(reverse = TRUE),
    fill = guide_legend(reverse = TRUE)
  ) +
  facet_wrap("variable", scales = "free", ncol = 1)
```

So we see that brms expects to be passed the standard error and no additional residual deviation. We are also not able to get models to converge with the additional deviation.

### Post-hoc standardizing

Our primary inference concerns raw regression coefficients which are directly interpretable on the percentage / percentage scales. We also post-hoc standardize these, and here confirm their equivalence (in simple regressions).

```{r post-hoc-stdz}
library(broom)
# Raw model fit
fit_raw <- lm(mpg ~ drat, data = mtcars)

# Standardized model fit
fit_scaled <- lm(scale(mpg) ~ scale(drat), data = mtcars)

# Correspondence: Multiply raw slope with ratio of sd(x) / sd(y)
x_sd <- sd(mtcars$drat)
y_sd <- sd(mtcars$mpg)
near(
  coef(fit_scaled)[2], 
  coef(fit_raw)[2] * (x_sd / y_sd), .00001
)
```

## Diagnostics

```{r models-load}
#| cache: false

# Create a table of outcomes in appropriate order, so can map functions over this
oo <- c(
  "Life_satisfaction", 
  "Negative_experiences", 
  "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)

fits <- tibble(
  path = list.files("models", pattern = "brm-", full.names = TRUE)
) |>
  mutate(fit = map(path, readRDS)) |>
  mutate(path = basename(path)) |>
  separate(path, c("discard", "outcome", "model"), sep = "-") |>
  mutate(
    x = factor(str_extract(model, "[0-9]"), labels = c("year", "i_cw", "m_cw")),
    predictor = factor(x, labels = c("Year", "Internet", "Mobile"))
  ) |>
  select(outcome, x, predictor, fit) |>
  mutate(outcome = factor(outcome, levels = oo)) |>
  arrange(outcome, x)

fits <- fits |> 
  left_join(z)
```

### Rhats

Show all suspicious rhats

```{r rhats}
fits |>
  select(predictor, outcome, fit) |> 
  mutate(
    out = map(
      fit,
      ~as_draws_df(.x, variable = c("b_", "sd_", "cor_"), regex = TRUE) |> 
        summarise_draws(rhat)
    )
  ) |>
  select(-fit) |>
  unnest(out) |> 
  filter(!near(rhat, 1, tol = .025)) |> 
  arrange(predictor, outcome, rhat) |> 
  gt()
```

### Traceplots

```{r traceplots}
#| fig.height: 6
#| fig.width: 8
#| fig.dpi: 72
#| column: page
#| panel: tabset
#| output: asis

traceplot <- function(fit, outcome, predictor) {
  fit |> 
    as_draws_df(variable = c("b_", "sd_"), regex = TRUE) |> 
    pivot_longer(contains("_")) |> 
    ggplot(aes(.iteration, value, col = factor(.chain))) +
    scale_color_brewer(palette = "Set1") +
    labs(caption = str_replace(fit$formula[1], 'val', as.character(outcome))) +
    geom_line(linewidth = .33, alpha = .5) +
    facet_wrap("name", scales = "free_y", ncol = 3) +
    theme(
      legend.position = "none"
    )
}

if (FALSE) {
  for (i in 1:18) {
    cat(str_glue("\n## {fits$outcome[[i]]} ~ {fits$predictor[[i]]}\n\n"))
    print(traceplot(fits$fit[[i]], fits$outcome[[i]], fits$predictor[[i]]))
    cat("\n\n")
  }
}
```

## Model output

```{r process-models}
# Functions to obtain quantities of interest
summary_function <- function(samples, zfactor) {
  samples %>%
    summarize_draws(
      mean, 
      sd,
      ~quantile2(.x, probs = c(0.025, 0.975)),
      pd = ~pd(as.numeric(.x)),
      zmean = ~mean(.x * zfactor),
      zsd = ~sd(.x * zfactor),
      z = ~quantile2(
        .x * zfactor, probs = c(0.025, 0.975)
      ) %>% 
        setNames(., c("zq2.5", "zq97.5")),
      rope = ~rope(
        as.numeric(.x * zfactor), rope_ci = 1, rope_range = c(-0.1, 0.1)
      )$ROPE_Percentage
    )
}

hypothesis_function <- function(model, variable, zfactor) {

  hypotheses <- c(
    average = str_glue("{variable} = 0"),
    female = str_glue("{variable} + {variable}:sex1 * 1 = 0"),
    male = str_glue("{variable} + {variable}:sex1 * -1 = 0"),
    `female-male` = str_glue("{variable} + {variable}:sex1 * 1 = {variable} + {variable}:sex1 * -1")
  )

  average <- hypothesis(model, hypotheses)
  names(average$samples) <- str_glue("{average$hypothesis$Hypothesis}_Average")

  country <- hypothesis(model, hypotheses, scope = "coef", group = "country")
  names(country$samples) <- str_glue("{country$hypothesis$Hypothesis}_{country$hypothesis$Group}")

  age <- hypothesis(model, hypotheses, scope = "coef", group = "age")
  names(age$samples) <- str_glue("{age$hypothesis$Hypothesis}_{age$hypothesis$Group}")

  xcb <- str_replace(variable, 'cw', 'cb')
  xcb_h <- c(cb = str_glue("{xcb} = 0"))
  cb <- hypothesis(model, xcb_h)
  names(cb$samples) <- str_glue("{cb$hypothesis$Hypothesis}_Average")

  list(average$samples, country$samples, age$samples, cb$samples) %>% 
    setNames(c("average", "country", "age", "cb")) %>%
    map(~summary_function(.x, zfactor)) %>%
    bind_rows(.id = "level")
}

path <- "cache/coefficients.rds"
if (!file.exists(path)) {
  coefficients <- fits |> 
    mutate(
      coef = pmap(
        list(model = fit, variable = x, zfactor = zfactor),
        ~hypothesis_function(..1, ..2, ..3)
      )
    ) |> 
    select(outcome, predictor, coef) |> 
    unnest(coef)

  coefficients <- separate(coefficients, variable, c("sex", "group"), sep = "_")

  # Create pretty strings with lots of digits for MH outcomes
  coefficients <- coefficients |> 
    mutate(
      digits = if_else(outcome %in% oo[1:3], .01, .0001)
    ) |> 
    mutate(
      Raw = str_glue(
        "{number(mean, digits)} [{number(q2.5, digits)}, ",
        "{number(q97.5, digits)}] ({percent2(pd, .1)})"
      ),
      Scaled = str_glue(
        "{number(zmean, digits)} [{number(zq2.5, digits)}, ",
        "{number(zq97.5, digits)}] ({percent2(rope, .1)})"
      )
    )

  coefficients <- coefficients |> 
    arrange(predictor, outcome) |> 
    select(predictor, everything())

  write_rds(coefficients, path)
} else {coefficients <- read_rds(path)}

path <- "cache/epred.rds"
if (!file.exists(path)) {
  epred <- fits |> 
    mutate(
      pdata = map2(
        fit, x, 
        ~conditional_effects(
          .x, .y, conditions = tibble(sex = NA), robust = FALSE
          )[[1]]
      )
    ) |> 
    select(-fit)
  write_rds(epred, path)
} else {epred <- read_rds(path)}
```

# Inference

```{r}
z <- read_rds("data/scaling-factors.rds")
coefficients <- read_rds("cache/coefficients.rds")
```

## Parameter scaling

```{r}
tmp <- coefficients |> 
  filter(
    outcome == "Life_satisfaction",
    predictor == "Internet",
    level == "average",
    sex == "average"
    ) |> 
  left_join(z)
```

In the manuscript, we describe magnitudes of the estimated associations on two scales. The raw scale describes changes in the outcome percentage as a function of one percent change in the predictor. To provide additional context to those raw associations, we also describe our results in standardized terms. This standard scale is in units of the grand average year-on-year change (YoY) in the predictor and standardized outcomes. In words, this scale describes changes in the outcome, in standard deviations, as function of an average year-on-year change in the predictor. Thus, we transform raw coefficients to standardized coefficients with $\beta_{\text{scaled}} = \beta_{\text{raw}}(\frac{\text{YoY}_x}{\sigma_y})$. For example, the YoY for per capita internet adoption is `r number(tmp$xdev, .1)`%, and the standard deviation of life satisfaction across countries, years, and demographics is `r number(tmp$val_sd, .1)`%. The raw association between the percentages is approximately `r number(tmp$mean, .1)`. Thus the scaled association is `r number(tmp$mean, .1)` * (`r number(tmp$xdev, .1)` / `r number(tmp$val_sd, .1)`) = `r number(tmp$zmean, .1)`.

## Probabilistic inference

In this work, we eschew null hypothesis significance testing in favor of two alternative bayesian methods of determining whether a parameter is considered credibly different from zero. First, we focus on posterior probabilities of direction ($p^d$). Although numerically identical to a one sided *p*-value [@marsmanThreeInsightsBayesian2016], $p^d$ describes the degree of confidence, as a percentage, that the estimated effect is in the observed direction. Figure \@ref(fig:fig-pd)A illustrates the posterior probability distribution of the average country's association between internet adoption and life satisfaction in raw percentage on percentage units. The dark shaded area indicates $p^d$; the proportion of this area under the curve that is above zero. In other words, given our modelling assumptions, per capita internet adoption predicts life satisfaction positively with a 78.9% probability.

While $p^d$ does not depend on how the predictors or outcomes are scaled, our second inference metric does. To assess whether parameters are credibly greater than some smallest effect size of interest (e.g. @anvariUsingAnchorbasedMethods2021), we define a region of practical equivalence (ROPE) to zero [@kruschkeDoingBayesianData2014] as [-0.1, 0.1] on the standardized scale.

```{r fig-pd}
#| fig.cap: Panel **A**. Posterior distribution of the parameter describing the association between per capita internet adoption and life satisfaction. Units indicate differences in life satisfaction percentage as function of one percent change in per capita internet adoption. The x-axis on the top of the figure converts this raw coefficient value to the scaled metric. The point and interval in the bottom of the figure indicates the posterior mean and 95\%CI limits, the latter also shown numerically. Shaded blue area indicates $p^d$; the posterior probability that the association is positive. **B**. As A. but in the standardized metric; units indicate z-score changes in life satisfaction as function of an average year-on-year change in per capita internet adoption. Shaded green area indicates $p^{\text{ROPE}}$; posterior probability that the coefficient is within ROPE. In this example, virtually the entire distribution is within ROPE.
#| fig.height: 3.4
#| fig.width: 8
#| include: true

tmp <- tmp |> 
  mutate(
    d = dist_normal(mean, sd),
    pd = (1 - cdf(d, 0)) |> percent(.1),
    ds = dist_normal(0.07 * zfactor, 0.087 * zfactor),
    prope = percent(cdf(ds, 0.1) - cdf(ds, -0.1), .1)
  )

p1 <- tmp |>   
  ggplot() +
  coord_cartesian(xlim = c(-0.1/tmp$zfactor, 0.1/tmp$zfactor)) +
  aes(xdist = d, slab_fill = after_stat(x > 0)) +
  scale_fill_brewer(
    TeX(r'($p^d$)'),
    aesthetics = "slab_fill",
    breaks = TRUE,
    labels = c(tmp$pd),
    palette = "Pastel1"
  ) +
  scale_y_discrete(
    "Density",
    expand = expansion(c(0, .025))
  ) +
  stat_slabinterval(
    .width = .95,
    p_limits = c(.0001, .9999),
    slab_color = "grey40",
    slab_linewidth = .33
  ) +
  stat_interval(
    .width = .95,
    geom = "text",
    aes(
      label = number(after_stat(xmax), .01),
      x = after_stat(xmax)
    ),
    y = -Inf, 
    vjust = -1,
    show.legend = FALSE
  ) +
  stat_interval(
    .width = .95,
    geom = "text",
    aes(
      label = number(after_stat(xmin), .01),
      x = after_stat(xmin)
    ),
    y = -Inf, 
    vjust = -1,
    show.legend = FALSE
  ) +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
p2 <- p1 + 
  coord_cartesian(xlim = c(-0.1, 0.1)) +
  geom_vline(
    xintercept = c(-0.1, 0.1),
    linewidth = .33, 
    linetype = "dashed"
  ) +
  aes(xdist = ds, slab_fill = after_stat(between(x, -0.1, 0.1))) +
  scale_fill_brewer(
    TeX(r'($p^{rope}$)'),
    aesthetics = "slab_fill",
    breaks = TRUE,
    labels = c(tmp$prope),
    palette = "Accent"
  ) +
  scale_x_continuous(
    "Scaled association",
    sec.axis = sec_axis(~ . / tmp$zfactor, name = "Raw association")
  )
p1 <- p1 +
  scale_x_continuous(
    "Raw association",
    sec.axis = sec_axis(~ . * tmp$zfactor, name = "Scaled association")
  )
(p1 | p2) &
  theme(legend.position = c(0.8, 0.75)) &
  plot_annotation(tag_levels = "A")
```

Because there is a paucity of critical theory to guide smallest effect sizes of interest, or ROPEs, on the raw scales, we define our ROPE as [-0.1, .1] on this standardized scale (see e.g. @fergusonProvidingLowerboundEstimate2021). Then using this ROPE, our second inference metric is the probability that the coefficient is in the region of practical equivalence to zero ($p^{\text{ROPE}}$). We consider this a quantification of credibility in the proposition that the coefficient of interest is not meaningfully large; that it is credibly equivalent to zero.

On this standardized scale, the 95%CI of the association between per capita internet adoption and life satisfaction ranges from -0.02 to 0.05. Figure \@ref(fig:fig-pd)B illustrates this posterior distribution in context of the ROPE: While the point estimate is positive, and $p^d$ = 78.9%, $p^{\text{ROPE}}$ = 100% and we are then very confident that the association is equivalent to zero; that it is not meaningfully large.

# Country-specific parameters

```{r}
#| label: tbl-countries
#| tbl-cap: Country-specific parameters for the average age and sex

coefficients |>
  filter(outcome == "Life_satisfaction", level == "country", sex == "average") |> 
  select(outcome, predictor, country = group, Raw, Scaled) |> 
  rename_with(~str_to_sentence(.)) |>
  mutate(Outcome = str_replace(Outcome, "_", " ")) |> 
  arrange(Outcome, Predictor, Country) |> 
  gt() |> 
  cols_align("left") |> 
  tab_style(
    style = cell_text(size = "x-small"),
    locations = cells_body()
  ) |> 
  opt_stylize(3) |> 
  tab_options(container.height = "400px")
```

# References
